### 2019-09-16 draft.tex
first commit (unstable)

\documentclass{llncs}

\usepackage{xcolor}
\usepackage{amssymb} 
\usepackage{tikz}
\usepackage[autostyle]{csquotes}

\usetikzlibrary{positioning}
\usetikzlibrary{arrows,automata}

\title{Handling String-number Conversion in String Constraint Solving}
\author{}
\institute{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\hide}[1]{}

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\sti}[1]{\mbox{\textbf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textbf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_n$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_s$}}
\newcommand{\cvar}{\mbox{$\mathbb{X}$}}
\newcommand{\modelof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}

\newcommand{\enc}[1]{Enc(#1)}
\newcommand{\ch}[1]{\mbox{`#1'}}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{section:introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{Why this problem is important? Need to say it is used often, e.g., read 
from text file or user input. Why this problem is challenging? It is undecidable. Some tricky cases 
using string as array index. Bounded SAT-based encoding might not work even for 
very simple constraints. e.g., $y=str2int(x) \wedge y>9999999$, if $x$ is a 
ASCII string, then XXX boolean variables are required. Or we can just propose 
an example that all major solver fails. Maybe we still say our approach is still over-approximation + under-approximation, in this case, need to think how to present the over-approximation part. Maybe no CEGAR is fine.}

In this paper, we propose an approach that handles string constraints with string-number conversion efficiently. The approach combines techniques from both automata theory and SMT solving to explore the model space of a string constraint systematically. More specifically, instead of allowing the variable domain to be arbitrary strings from a finite alphabet, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern. By adjusting the parameters, one can easily enlarge or prune out the potential solution space. In paper, we propose to use patterns defined by \emph{symbolic flat automata}, the automata are very expressive yet allows very efficiently manipulation. For example, it avoids the alphabet 
explosion problem that the approach in~\cite{PLDI2017} suffers.

Based on the symbolic flat automata encoding, we manage to convert the 
string-number function to a constraint consisting of both 
polynomials and exponentials. To the best of our knowledge, the satisfiability 
problem of a mix of polynomials and exponentials is still open. For the 
particular case with only one number variable exponent, the satisfiability can 
be decided using the algorithm in~\cite{POPL2019}. However, the algorithm involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence is not scalable to large instances.  \todo{check correctness of the above statement} For bounded numbers, our approach converts string-number function to a linear integer constraint.
To ease presentation, in the main text, we only consider string constraints consisting of \emph{equality constraints (a.k.a. word equation)}, \emph{length constraints}, and \emph{string-number conversion} functions. We describe the extension to support transducer and membership constraints in the appendix.

\hide{
suggest restricting the string domain to $0^*[0-9]^k$, where $k$ is the maximum 
digit allowed in the corresponding number value. In programming languages 
such  as JavaScript or Python, a number with $k$ digits can be converted from a 
string of length arbitrarily longer than $k$. For example, $12 = 
str2int(``0000012")$. That is why we use $0^*$ at the beginning of the pattern.
Under this domain, we can convert the string-number conversion constraints to 
linear integer constraints, which is much easier to solve. In our experience, 
usually, it suffices to find a solution using a small $k$ for a satisfiable 
constraint. Note that a 64-bit integer number corresponds to a string with 
$k\leq 21$.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preliminary} \label{section:preliminary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
use $|w|$ to denote its length. We $\epsilon$ to denote an empty string and use $w_1\cdot w_2$ to denote the concatenation of strings $w_1$ and $w_2$. Let $S$ be a finite set of symbols. We use $S^+$ to denote the set of string over $S$ and $S^* = S^+\cup \{\epsilon\}$. We define $S_\epsilon =S\cup\{\epsilon\}$. A language 
$L$ over $S$ is a set of strings in $S^*$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{String Constraints} \label{section:sc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Fix a finite alphabet $\Sigma \subseteq \mathbb{N}$, a finite set of string variables $\vars$ ranging over $\Sigma^*$, and a finite set of natural number variables $\varn$. Note that here we assume the alphabet is a finite subset of natural numbers. Essentially, we try to capture the numerical encoding of symbols (e.g., in ASCII, `A' is encoded as $65$) in computers. We write $[n,m]$ for the set of numbers (or symbols in $\Sigma$) $\{k\mid n\leq k \leq m\}$. A \emph{term} is an element in $(\vars\cup \Sigma)^*$. An \emph{interpretation} is a mapping from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$. We lift 
it to terms by defining $I: (\vars\cup \Sigma)^* \rightarrow \Sigma^*$ with $I(a) =a$ for $a\in \Sigma$ and $I(t_1 \cdot t_2) = I(t_1)\cdot I(t_2)$.

The \emph{string-number conversion function} $\sti{x}$ is defined as follows. For $x\in [0,9]^+$ and $a\in [0,9]$, we have $\sti{a}=a$ and $\sti{x\cdot a} = 10\times \sti{x}+a$. For $x\notin [0,9]^+$, $\sti{x}=-1$.

For a number $n=a_n*10^n+a_{n-1}*10^{n-1}+\ldots+a_0$ for $a_i\in [0,9], i\in [0,n]$, the \emph{number-string conversion function} $\its{n}=a_ia_{i-1}\ldots a_0$~\footnote{Notice that only positive integer is supported in this semantics. This is the semantics used by most of the SMT solvers, and hence we follow it in this paper. This is not a restriction, since conversing from negative integer can still be encoded using the positive only version.}.

A \emph{equality constraint} $\phi$ is of the form $t_1 = t_2$ where $t_1, 
t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi$ is the set of interpretations $\modelof{\phi}=\{I\mid 
I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
t_2$ and is interpreted analogously.

An \emph{integer constraint} $\phi$ is a linear constraint over the variables in $\varn$, numerical values of strings $\sti{x}$, and length of a string $|x|$, for all string variables $x$ in $\vars$.
%Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$. We define $\modelof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
We define  $\modelof{\phi}= \{I \mid I(\phi)= \true \}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Symbolic Flat Automata} \label{section:sfa}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A \emph{finite-state automaton} (FA) is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times \Sigma\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state. The semantics of FSA is defined in the standard manner. We use $L(A)$ to denote the language, i.e., set of accepted strings, of a FA $A$.

Fix a finite set of character variables $\cvar$ ranging over $\Sigma_\epsilon$.
We call a string over $\cvar$ a symbolic string.
A interpretation $I$ over $\cvar$ is a mapping from $\cvar$ to $\Sigma_\epsilon$.
For a symbolic string $x= x_1x_2\cdots x_k$ over $\cvar$, $I(x)$ is defined as $I(x_1)\cdot I(x_2)\cdot \ldots \cdot I(x_k)$.

We introduce \emph{symbolic flat automata} (SFA) $(Q,T,\cvar_\epsilon,q_0,q_m)$ that will be used to define patterns for the variable domain restriction. SFA is a finite-state automaton operating over the alphabet $\cvar_\epsilon$ and with additional structural constraints.
\begin{enumerate}
	\item the initial state $q_0$ and final state $q_m$ are connected by a straight-line structure, i.e., $(q_i,x_i,q_i+1) \in T$ and states $q_i \in Q$  for $i\in[0,m-1]$.
	\item  each state $q_i$ may be included to an unique simple cycle, i.e. $q_i^j \in Q$ and $(q_i, x_i^0, q_i^1), (q_j, x_i^j, q_i^{j+1}), (q_i^l, x_i^l, q_i) \in T$ for $i\in [0,n]$ and $j\in [1,l-1]$. 
	\item each variable in $\cvar$ appears in at most one transition (but $\epsilon$ transition can appear multiple times). 
\end{enumerate} 
Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.

\begin{figure}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
	\begin{tikzpicture} 
		\node[state,initial] (q0)  {$q_0$};
		\node[state] (q1) [right = 3cm of q0] {$q_1$};
		\node (q2) [right = 1.8cm of q1]{};
		\node (q3) [right = 1cm of q2]{};
		\node[state,accepting] (qm) [right = 1.8cm of q3] {$q_m$};

		\node[state] (q01) [above left = 0.6cm of q0] {$q_0^1$};
		\node[state] (q02) [above = 1cm of q0] {$q_0^2$};
		\node[state] (q03) [above right = 0.6cm of q0] {$q_0^3$};

		\node[state] (q11) [above left = 0.8cm of q1] {$q_1^1$};
		\node[state] (q12) [above right = 0.8cm of q1] {$q_1^2$};

		\node[state] (qm1) [above left = 0.6cm of qm] {$q_m^1$};
		\node[state] (qm2) [above = 1cm of qm] {$q_m^2$};
		\node[state] (qm3) [above right = 0.6cm of qm] {$q_m^3$};

  		\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
  		\draw[->] (q01) edge [bend left] node [left]{$x_0^1$} (q02) ;
  		\draw[->] (q02) edge [bend left] node [right]{$x_0^2$} (q03) ;
  		\draw[->] (q03) edge [bend left] node [right]{$x_0^3$} (q0) ;

  		\draw[->] (q0) edge node [below]{$x_0$} (q1) ;
  		\draw[->] (q1) edge node [below]{$x_1$} (q2) ;
  		\draw[dotted] (q2) edge (q3) ;
  		\draw[->] (q3) edge node [below]{$x_{m-1}$} (qm) ;

  		\draw[->] (qm) edge [bend left] node [left]{$x_m^0$} (qm1) ;
		\draw[->] (qm1) edge [bend left] node [left]{$x_m^1$} (qm2) ;
		\draw[->] (qm2) edge [bend left] node [right]{$x_m^2$} (qm3) ;
		\draw[->] (qm3) edge [bend left] node [right]{$x_m^3$} (qm) ;

  		\draw[->] (q1) edge [bend left] node [left]{$x_1^0$} (q11) ;
		\draw[->] (q11) edge [bend left] node [above]{$x_1^1$} (q12) ;
		\draw[->] (q12) edge [bend left] node [right]{$x_1^2$} (q1) ;
	\end{tikzpicture} 
	\caption{An example of a symbolic flat automaton}
\end{figure}

We say the FA $D=(Q,T',\Sigma_\epsilon,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar_\epsilon,q_0,q_m)$, if there exists an interpretation $I: \cvar_\epsilon \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$. We write $I(S)$ to denote the instance of $S$ wrt. $I$. The language of $S$ is defined as $L(S)= \cup\{L(D) \mid D \mbox{ is an instance of } S\}$. Notice that $L(S)$ is regular because every SFA has only finitely many instance and the finite union of regular languages are also regular.

For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting string. For example, if the string $x_1x_2x_1x_2$ is accepted, then all other strings with $\#(x_1)=\#(x_2)=2$ are not accepted. Moreover, from $\#(x_1)=\#(x_2)=2$, we can derive the accepted string $x_1x_2x_1x_2$ by exploring the automata structure. \todo{add Presburger constraints to allow more expressive power.}

\begin{lemma}
	Symbolic flat automata are closed under concatenation.
\end{lemma}

\todo{Mention NDD when talk about our practical bounded encoding for str2int}

\section{Handling Equality and Disequality Constraint} \label{section:eq}
Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some SFA with disjunct alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.

For example, for the constraint $xy = yx$, if we restrict the domains of $x$ and $y$ to the SFA in Figure~\ref{fig:sfa} (a) and (b), respectively. We can then construct the SFA for $xy$ (Figure~\ref{fig:sfa} (c)) and $yx$ (Figure~\ref{fig:sfa} (d)).

\begin{figure}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}

 	\begin{minipage}[t]{0.15\textwidth} 
	\begin{tikzpicture}
	\node[state,initial,accepting] (q0)  {$q_0$};

	\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};

	\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
	\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;
	\end{tikzpicture}

	\centering
	(a) $x$
	\end{minipage}
 	\begin{minipage}[t]{0.15\textwidth} 
	\begin{tikzpicture} 
	\node[state,initial,accepting] (q0)  {$q_1$};

	\node[state] (q01) [above = 0.5cm of q0] {$q_1^1$};

	\draw[->] (q0) edge [bend left] node [left]{$y_0^0$} (q01) ;
	\draw[->] (q01) edge [bend left] node [right]{$y_0^1$} (q0) ;
	\end{tikzpicture}

	\centering
	(b) $y$
	\end{minipage}
	\ \ \ \ \ \ \ 
	\begin{minipage}[t]{0.28\textwidth}
	\begin{tikzpicture} 
	\node[state,initial] (q0)  {$q_0$};
	\node[state,accepting] (q1) [right = 1cm of q0] {$q_1$};

	\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};

	\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
	\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;

	\node[state] (q11) [above = 0.5cm of q1] {$q_1^1$};

	\draw[->] (q1) edge [bend left] node [left]{$y_0^0$} (q11) ;
	\draw[->] (q11) edge [bend left] node [right]{$y_0^1$} (q1) ;
	\draw[->] (q0) edge  node [below]{$\epsilon$} (q1) ;
	\end{tikzpicture}

	\centering
	(c) $xy$
	\end{minipage}
	\begin{minipage}[t]{0.28\textwidth}
	\begin{tikzpicture} 
	\node[state,accepting] (q0)  {$q_0$};
	\node[state,initial] (q1) [left = 1cm of q0] {$q_1$};

	\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};

	\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
	\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;

	\node[state] (q11) [above = 0.5cm of q1] {$q_1^1$};

	\draw[->] (q1) edge [bend left] node [left]{$y_0^0$} (q11) ;
	\draw[->] (q11) edge [bend left] node [right]{$y_0^1$} (q1) ;
	\draw[->] (q1) edge  node [below]{$\epsilon$} (q0) ;
	\end{tikzpicture}

	\centering
	(d) $yx$
	\end{minipage}

	\caption{Symbolic flat automata of $x$, $y$, $xy$ and $yx$}
	\label{fig:sfa}
\end{figure}

Assume that $S_n=(Q,T,\cvar_\epsilon,q_i,q_f)$ is the SFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(Q',T',\cvar_\epsilon,q'_i,q'_f)$ is the SFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$. Our next task is to find a model for $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$ under the domain restriction specified by $S_n$ and $S_m$.

This is equivalent to finding a common interpretation $I$ such that the languages of $I(S_n)$ and $I(S_m)$ are not disjoint. In order to find such an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to force the two input automata sharing the same interpretation.

Such product automaton uses $Q\times Q'$ as the set of states and $\cvar_\epsilon \times \cvar_\epsilon$ as the alphabet. If a transition $((q_1,q'_1), (x_1,x'_1),(q_2,q'_2))$ is taken, it means the character variable $x_1$ and $x'_1$ should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $q'_1$ to $q'_2$.

More precisely, the product automaton $P$ is a tuple $(Q\times Q', T^2, \cvar_\epsilon \times \cvar_\epsilon, (q_i,q'_i),(q_f,q'_f))$, where the transition relation $T'$ is the minimal set satisfying the following.

\begin{itemize}
\item If $(q_1,x,q_2) \in T$, then for all $q'\in Q',((q_1,q'),(x,\epsilon),(q_2,q'))\in T^2$.
\item If $(q'_1,x,q'_2) \in T'$, then for all $q\in Q,((q,q'_1),(\epsilon,x),(q,q'_2))\in T^2$.
\item If $(q_1,x,q_2) \in T$ and $(q'_1,x',q'_2) \in T'$, then $((q_1,q'_1),(x,x'),(q_2,q'_2))\in T^2$.
\end{itemize}	
The first two cases correspond to the situation when the character variable $x$ is assigned $\epsilon$. In such cases, only one automaton changes its state.

The product automaton corresponds to $xy=yx$ can be found in Figure~\ref{}.

\begin{figure}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}

	\begin{minipage}[t]{0.28\textwidth}
		\begin{tikzpicture} 
		\node[state,initial] (q0)  {$q_0,q_1$};
		\node[state,accepting] (q1) [right = 1cm of q0] {$q_1$};

		\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};

		\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
		\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;

		\node[state] (q11) [above = 0.5cm of q1] {$q_1^1$};

		\draw[->] (q1) edge [bend left] node [left]{$y_0^0$} (q11) ;
		\draw[->] (q11) edge [bend left] node [right]{$y_0^1$} (q1) ;
		\draw[->] (q0) edge  node [below]{$\epsilon$} (q1) ;
		\end{tikzpicture}
	\end{minipage}

	\caption{Product automaton of $xy=yx$}
	\label{fig:sfa}
\end{figure}

Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string.

We first build a product automata $\mathcal{P}=(Q\times P, T, \cvar\times \cvar, (q_i,p_i), (q_f,p_f))$, where $((q,p),(x,y), (q',p'))\in T$ iff $(q,x,q')\in T_Q \wedge (p,y,p')\in T_P$. Then the following formula characterizes all models of the equality constraint $Parikh(\mathcal{P}) \wedge \#(x,y) > 0 \rightarrow \enc{x} = \enc{y}$.

In practice, building the product automata is an expensive operation. In practice, we consider SFA of special shape that allows more efficient translation from equality constraint to linear integer constraint.

We define $(p,q)$-SFA as a SFA consisting of $p$ simple loops of length $q$, connected by epsilon transitions. Formally,

\todo{Maybe talk about the heuristic that we merge the list elements into one}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Handling String-Integer Conversion} \label{section:s2i}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We begin the discussion with the conversion between bounded integers (e.g., 64-bits) and strings. Notice that even for bounded integer, the corresponding string can be of unbounded length. For example, the formula $\sti{x}=10 \wedge |x|=5$ is in fact satisfiable when $x=``00010"$. To handle the bounded integer case $y=\sti{x}$, we propose to restrict the domain of $x$ to a SFA of the form $(\{q_0,\ldots,q_k\},T,\cvar, q_0,q_k)$, where $k$ is the number of digits allowed in the bounded integer, $T = \{(q_0,x_0,q_0)\} \cup \{(q_i,x_{i+1},q_{i+1})\mid 0\leq i <k\}$, with additional numerical constraints $\enc{x_0}=\enc{\ch{0}}$ and $\wedge_{i\in [1,9]} \enc{\ch{0}}\leq \enc{x_i} \leq \enc{\ch{9}}$ to force the domain of the string to those corresponding to positive integers. Under this domain restriction, we obtain $y=\Sigma_{i\in [1,9]} 10^{k-i}\times (\enc{x_i}-\enc{\ch{0}})$.

\todo{Add an example: $\sti{x}=\sti{y} \wedge x= y\cdot y$. Do product construction informally here.}

This approach can be extended to unbounded string using more sophisticated pattern. For example, we can extend the bounded pattern that uses two loops, by changing the transition relation $T$ to $\{(q_0,x_0,q_0), (q_0,\epsilon,q_1), (q_k,x_1,q_1)\} \cup \{(q_i,x_{i+1},q_{i+1})\mid 0< i <k\}$. In this pattern, one can describe string that corresponds arbitrarily large integer. Taking the case $k=2$, $\enc{x_2}=\enc{\ch{3}}$, $\enc{x_1}=\enc{\ch{5}}$ as an example, any number in the form of $353535\ldots35$ can be expressed. Formally, the relation between $y$ and $x$ can be described in the following formula:
$$y= (10*(\enc{x_2}-\enc{\ch{0}})+(\enc{x_1}-\enc{\ch{0}}))\times \frac{100^{\#(x_1)}-1}{100-1}$$

where $\#(x_1)$ is the number of occurrence of $x_1$ in the corresponding symbolic string and is treated as a variable in this case. To solve the satisfiability of this formula, one need to solve an exponential constraint. From the results of POPL2019, this problem is decidable if ....

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-25 draft.tex
first commit (unstable)
some update

@@
 \newcommand{\vars}{\mbox{$\mathbb{V}_s$}}
-\newcommand{\cvar}{\mbox{$\mathbb{X}$}}
+\newcommand{\cvar}{\mbox{$\mathbb{C}$}}
 \newcommand{\modelof}[1]{[\![#1]\!]}
@@
 integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
-use $|w|$ to denote its length.
+use $|w|$ to denote its length and $|w|_a$ to denote the number of occurrences of $a$ in $w$.
 We $\epsilon$ to denote an empty string and use $w_1\cdot w_2$ to denote the concatenation of strings $w_1$ and $w_2$.
@@
 $L$ over $S$ is a set of strings in $S^*$.
+
+A \emph{finite-state automaton} (FA) is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times \Sigma\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
+The semantics of FSA is defined in the standard manner.
+We use $L(A)$ to denote the regular language, i.e., set of accepted strings, of a FA $A$.
+
+Given a FA $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$.
+Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A \emph{finite-state automaton} (FA) is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times \Sigma\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
-The semantics of FSA is defined in the standard manner.
-We use $L(A)$ to denote the language, i.e., set of accepted strings, of a FA $A$.
 
@@
 A interpretation $I$ over $\cvar$ is a mapping from $\cvar$ to $\Sigma_\epsilon$.
-For a symbolic string $x= x_1x_2\cdots x_k$ over $\cvar$, $I(x)$ is defined as $I(x_1)\cdot I(x_2)\cdot \ldots \cdot I(x_k)$.
+For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 
@@
 \begin{enumerate}
-	\item the initial state $q_0$ and final state $q_m$ are connected by a straight-line structure, i.e., $(q_i,x_i,q_i+1) \in T$ and states $q_i \in Q$  for $i\in[0,m-1]$.
+	\item the initial state $q_0$ and final state $q_m$ are connected by a straight-line structure, i.e., $(q_i,v_i,q_i+1) \in T$ and states $q_i \in Q$ for $i\in[0,m-1]$.
 	\item  each state $q_i$ may be included to an unique simple cycle, i.e.
-$q_i^j \in Q$ and $(q_i, x_i^0, q_i^1), (q_j, x_i^j, q_i^{j+1}), (q_i^l, x_i^l, q_i) \in T$ for $i\in [0,n]$ and $j\in [1,l-1]$.
+$q_i^j \in Q$ and $(q_i, v_i^0, q_i^1), (q_j, v_i^j, q_i^{j+1}), (q_i^l, v_i^l, q_i) \in T$ for $i\in [0,n]$ and $j\in [1,l-1]$.
 	\item each variable in $\cvar$ appears in at most one transition (but $\epsilon$ transition can appear multiple times). 
@@
 
-  		\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
-  		\draw[->] (q01) edge [bend left] node [left]{$x_0^1$} (q02) ;
-  		\draw[->] (q02) edge [bend left] node [right]{$x_0^2$} (q03) ;
-  		\draw[->] (q03) edge [bend left] node [right]{$x_0^3$} (q0) ;
+  		\draw[->] (q0) edge [bend left] node [left]{$v_0^0$} (q01) ;
+  		\draw[->] (q01) edge [bend left] node [left]{$v_0^1$} (q02) ;
+  		\draw[->] (q02) edge [bend left] node [right]{$v_0^2$} (q03) ;
+  		\draw[->] (q03) edge [bend left] node [right]{$v_0^3$} (q0) ;
 
-  		\draw[->] (q0) edge node [below]{$x_0$} (q1) ;
-  		\draw[->] (q1) edge node [below]{$x_1$} (q2) ;
+  		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
+  		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
   		\draw[dotted] (q2) edge (q3) ;
-  		\draw[->] (q3) edge node [below]{$x_{m-1}$} (qm) ;
+  		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
 
-  		\draw[->] (qm) edge [bend left] node [left]{$x_m^0$} (qm1) ;
-		\draw[->] (qm1) edge [bend left] node [left]{$x_m^1$} (qm2) ;
-		\draw[->] (qm2) edge [bend left] node [right]{$x_m^2$} (qm3) ;
-		\draw[->] (qm3) edge [bend left] node [right]{$x_m^3$} (qm) ;
+  		\draw[->] (qm) edge [bend left] node [left]{$v_m^0$} (qm1) ;
+		\draw[->] (qm1) edge [bend left] node [left]{$v_m^1$} (qm2) ;
+		\draw[->] (qm2) edge [bend left] node [right]{$v_m^2$} (qm3) ;
+		\draw[->] (qm3) edge [bend left] node [right]{$v_m^3$} (qm) ;
 
-  		\draw[->] (q1) edge [bend left] node [left]{$x_1^0$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [above]{$x_1^1$} (q12) ;
-		\draw[->] (q12) edge [bend left] node [right]{$x_1^2$} (q1) ;
+  		\draw[->] (q1) edge [bend left] node [left]{$v_1^0$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [above]{$v_1^1$} (q12) ;
+		\draw[->] (q12) edge [bend left] node [right]{$v_1^2$} (q1) ;
 	\end{tikzpicture} 
+	\label{fig:sfa_def}
 	\caption{An example of a symbolic flat automaton}
@@
 
-We say the FA $D=(Q,T',\Sigma_\epsilon,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar_\epsilon,q_0,q_m)$, if there exists an interpretation $I: \cvar_\epsilon \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
+A FA $D=(Q,T',\Sigma_\epsilon,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar_\epsilon,q_0,q_m)$, if there exists an interpretation $I: \cvar_\epsilon \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
 We write $I(S)$ to denote the instance of $S$ wrt.
@@
 For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting string.
-For example, if the string $x_1x_2x_1x_2$ is accepted, then all other strings with $\#(x_1)=\#(x_2)=2$ are not accepted.
-Moreover, from $\#(x_1)=\#(x_2)=2$, we can derive the accepted string $x_1x_2x_1x_2$ by exploring the automata structure.
+For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
+Moreover, from $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$, we can derive $w=v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ by exploring the automata structure.
 \todo{add Presburger constraints to allow more expressive power.}
@@
 \section{Handling Equality and Disequality Constraint} \label{section:eq}
-Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some SFA with disjunct alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.
+Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some SFA with disjoint alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.
+We rename the variables on the transitions of SFA's for different occurrences of the same variable in one equality constraint.
+Later we will use some arithmetic constraints to enforce that all occurrences of the variants of the same variable will be assigned the same value.
+For notational convenience, the renaming is done by adding a version number to the variable.
+For example, we can rename $v_1$ to $v_1^{(0)}$, $v_1^{(1)}$, $\ldots$.
 
-For example, for the constraint $xy = yx$, if we restrict the domains of $x$ and $y$ to the SFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-We can then construct the SFA for $xy$ (Figure~\ref{fig:sfa} (c)) and $yx$ (Figure~\ref{fig:sfa} (d)).
+For the constraint $xy = yx$, we first restrict the domains of $x$ and $y$ to the SFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+In the construction of the SFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the SFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$.
 
@@
 
-	\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};
+	\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
 
-	\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
-	\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;
+	\draw[->] (q0) edge [bend left] node [left]{$v_0$} (q01) ;
+	\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
 	\end{tikzpicture}
@@
 	\centering
-	(a) $x$
+	(a) $A_x$
 	\end{minipage}
@@
 	\begin{tikzpicture} 
-	\node[state,initial,accepting] (q0)  {$q_1$};
+	\node[state,initial,accepting] (q0)  {$p_0$};
 
-	\node[state] (q01) [above = 0.5cm of q0] {$q_1^1$};
+	\node[state] (q01) [above = 0.5cm of q0] {$p_1$};
 
-	\draw[->] (q0) edge [bend left] node [left]{$y_0^0$} (q01) ;
-	\draw[->] (q01) edge [bend left] node [right]{$y_0^1$} (q0) ;
+	\draw[->] (q0) edge [bend left] node [left]{$v_2$} (q01) ;
+	\draw[->] (q01) edge [bend left] node [right]{$v_3$} (q0) ;
 	\end{tikzpicture}
@@
 	\centering
-	(b) $y$
+	(b) $A_y$
 	\end{minipage}
-	\ \ \ \ \ \ \ 
 	\begin{minipage}[t]{0.28\textwidth}
@@
 	\node[state,initial] (q0)  {$q_0$};
-	\node[state,accepting] (q1) [right = 1cm of q0] {$q_1$};
+	\node[state,accepting] (q1) [right = 1.3cm of q0] {$p_0$};
 
-	\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};
+	\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
 
-	\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
-	\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;
+	\draw[->] (q0) edge [bend left] node [left]{$v_0^{(0)}$} (q01) ;
+	\draw[->] (q01) edge [bend left] node [right]{$v_1^{(0)}$} (q0) ;
 
-	\node[state] (q11) [above = 0.5cm of q1] {$q_1^1$};
+	\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
 
-	\draw[->] (q1) edge [bend left] node [left]{$y_0^0$} (q11) ;
-	\draw[->] (q11) edge [bend left] node [right]{$y_0^1$} (q1) ;
+	\draw[->] (q1) edge [bend left] node [left]{$v_2^{(0)}$} (q11) ;
+	\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
 	\draw[->] (q0) edge  node [below]{$\epsilon$} (q1) ;
@@
 	\centering
-	(c) $xy$
+	(c) $A_{xy}$
 	\end{minipage}
+	\ \ \ 
 	\begin{minipage}[t]{0.28\textwidth}
@@
 	\node[state,accepting] (q0)  {$q_0$};
-	\node[state,initial] (q1) [left = 1cm of q0] {$q_1$};
+	\node[state,initial] (q1) [left = 1.3cm of q0] {$p_0$};
 
-	\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};
+	\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
 
-	\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
-	\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;
+	\draw[->] (q0) edge [bend left] node [left]{$v_0^{(1)}$} (q01) ;
+	\draw[->] (q01) edge [bend left] node [right]{$v_1^{(1)}$} (q0) ;
 
-	\node[state] (q11) [above = 0.5cm of q1] {$q_1^1$};
+	\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
 
-	\draw[->] (q1) edge [bend left] node [left]{$y_0^0$} (q11) ;
-	\draw[->] (q11) edge [bend left] node [right]{$y_0^1$} (q1) ;
+	\draw[->] (q1) edge [bend left] node [left]{$v_2^{(1)}$} (q11) ;
+	\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
 	\draw[->] (q1) edge  node [below]{$\epsilon$} (q0) ;
@@
 	\centering
-	(d) $yx$
+	(d) $A_{yx}$
 	\end{minipage}
@@
 
-Assume that $S_n=(Q,T,\cvar_\epsilon,q_i,q_f)$ is the SFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(Q',T',\cvar_\epsilon,q'_i,q'_f)$ is the SFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
+Assume that $S_n=(Q,T,\cvar^1_\epsilon,q_i,q_f)$ is the SFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvar^2_\epsilon,p_i,p_f)$ is the SFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
 Our next task is to find a model for $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$ under the domain restriction specified by $S_n$ and $S_m$.
 
-This is equivalent to finding a common interpretation $I$ such that the languages of $I(S_n)$ and $I(S_m)$ are not disjoint.
-In order to find such an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to force the two input automata sharing the same interpretation.
+This is equivalent to finding a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and a common interpretation $I$ such that 
+\begin{enumerate}
+	\item $I(w_n)=I(w_m)$
+	\item $I$ assign to variants of the same variable the same value. For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}$ and $v_0^{(1)}$ should be assigned the same value.
+	\item variants of the same variable should occurs equally often in $w_n\cdot w_m$.
+For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_0^{(1)}v_1^{(1)}v_0^{(1)}v_1^{(1)}$ is a pair of symbolic strings satisfying this condition.
+The number of occurrences of $v_i^{(0)}$ is the same to $v_i^{(1)}$ for $i\in[0,1]$ in the concatenation of the two symbolic strings .
+	But the pair $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_2^{(0)}v_3^{(0)}v_2^{(0)}v_3^{(0)}$ does not satisfy the condition. Observe that $v_0^{(0)}$ occurs twice, but $v_0^{(1)}$ is not there.
+\end{enumerate}
 
-Such product automaton uses $Q\times Q'$ as the set of states and $\cvar_\epsilon \times \cvar_\epsilon$ as the alphabet.
-If a transition $((q_1,q'_1), (x_1,x'_1),(q_2,q'_2))$ is taken, it means the character variable $x_1$ and $x'_1$ should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $q'_1$ to $q'_2$.
+In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
 
-More precisely, the product automaton $P$ is a tuple $(Q\times Q', T^2, \cvar_\epsilon \times \cvar_\epsilon, (q_i,q'_i),(q_f,q'_f))$, where the transition relation $T'$ is the minimal set satisfying the following.
+Such product automaton uses $Q\times P$ as the set of states and $\cvar^1_\epsilon \times \cvar^2_\epsilon$ as the alphabet.
+If a transition $((q_1,p_1), (x_{i,j},x'_{i',j'}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $x_{i,j}$ and $y_{i',j'}$ should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
+
+More precisely, the product automaton is a tuple $(Q\times P, T^2, \cvar^1_\epsilon \times \cvar^2_\epsilon, (q_i,p_i),(q_f,p_f))$, where the transition relation $T^2$ is the minimal set satisfying the following.
 
 \begin{itemize}
-\item If $(q_1,x,q_2) \in T$, then for all $q'\in Q',((q_1,q'),(x,\epsilon),(q_2,q'))\in T^2$.
-\item If $(q'_1,x,q'_2) \in T'$, then for all $q\in Q,((q,q'_1),(\epsilon,x),(q,q'_2))\in T^2$.
-\item If $(q_1,x,q_2) \in T$ and $(q'_1,x',q'_2) \in T'$, then $((q_1,q'_1),(x,x'),(q_2,q'_2))\in T^2$.
+\item If $(q_1,x_{i,j},q_2) \in T$, then for all $p\in P,((q_1,p),(x_{i,j},\epsilon),(q_2,p))\in T^2$.
+\item If $(p_1,x_{i,j},p_2) \in T'$, then for all $q\in Q,((q,p_1),(\epsilon,x_{i,j}),(q,p_2))\in T^2$.
+\item If $(q_1,x_{i,j},q_2) \in T$ and $(p_1,x'_{i',j'},p_2) \in T'$, then $((q_1,p_1),(x_{i,j},x'_{i',j'}),(q_2,p_2))\in T^2$.
 \end{itemize}	
-The first two cases correspond to the situation when the character variable $x$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
+The first two cases correspond to the situation when the character variable $x_{i,j}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
 
-The product automaton corresponds to $xy=yx$ can be found in Figure~\ref{}.
+For example, in the product automaton $A_{xy=yx}$ corresponds to $xy=yx$, we have the following transitions
+\begin{itemize}
+	\item $((q_0,p_0), (x_{0,0},\epsilon),(q_1,p_0))$, because $(q_0,x_{0,0},q_1)$ is a transition of $A_{xy}$.
+	\item $((q_0,p_0), (\epsilon,y_{1,0}),(q_0,p_1))$, because $(p_0,y_{1,0},p_1)$ is a transition of $A_{yx}$.
+	\item $((q_0,p_0), (x_{0,0},y_{1,0}),(q_1,q_1))$, because $(q_0,x_{0,0},q_1)$ is a transition of $A_{xy}$ and $(p_0,y_{1,0},p_1)$ is a transition of $A_{yx}$.
+\end{itemize}
 
-\begin{figure}
-	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
-			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section\ref{section:sfa}) and for any FA we can construct a Presburger formula characterizing its Parikh image (Section\ref{section:preliminary}).
+For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{v_{(x,y)}\mid (x,y) \in \cvar_\epsilon \times \cvar_\epsilon\}$ characterizing the Parikh image of $A$.
+Then we add the following linear constraints.
 
-	\begin{minipage}[t]{0.28\textwidth}
-		\begin{tikzpicture} 
-		\node[state,initial] (q0)  {$q_0,q_1$};
-		\node[state,accepting] (q1) [right = 1cm of q0] {$q_1$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_0^1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$x_0^0$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$x_0^1$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$q_1^1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$y_0^0$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$y_0^1$} (q1) ;
-		\draw[->] (q0) edge  node [below]{$\epsilon$} (q1) ;
-		\end{tikzpicture}
-	\end{minipage}
-
-	\caption{Product automaton of $xy=yx$}
-	\label{fig:sfa}
-\end{figure}
-
-Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string.
+\begin{enumerate}
+	\item for any $(x_{i,j},y_{i',j'}) \in \cvar^1_\epsilon \times \cvar^2_\epsilon$, $v_{(x_{i,j},y_{i',j'})}>0 \rightarrow (x_j=y_{j})$. We use $-1$ to encode $\epsilon$.
+	\item for all $x \in \cvar$, $|x| =\sum_{y \in \cvar_\epsilon} (v_{(x,y)}+v_{(y,x)})$
+\end{enumerate}
+Those constraints enforce that the two size of the equality of the word equation sharing the same interpretation.
 

### 2019-09-26 draft.tex
some update

@@
 Such product automaton uses $Q\times P$ as the set of states and $\cvar^1_\epsilon \times \cvar^2_\epsilon$ as the alphabet.
-If a transition $((q_1,p_1), (x_{i,j},x'_{i',j'}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $x_{i,j}$ and $y_{i',j'}$ should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
+If a transition $((q_1,p_1), (v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $v_i$ and $v_{i'}$ (and so all of their indexed variants) should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
 
@@
 \begin{itemize}
-\item If $(q_1,x_{i,j},q_2) \in T$, then for all $p\in P,((q_1,p),(x_{i,j},\epsilon),(q_2,p))\in T^2$.
-\item If $(p_1,x_{i,j},p_2) \in T'$, then for all $q\in Q,((q,p_1),(\epsilon,x_{i,j}),(q,p_2))\in T^2$.
-\item If $(q_1,x_{i,j},q_2) \in T$ and $(p_1,x'_{i',j'},p_2) \in T'$, then $((q_1,p_1),(x_{i,j},x'_{i',j'}),(q_2,p_2))\in T^2$.
+\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all $p\in P,((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in T^2$.
+\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all $q\in Q,((q,p_1),(\epsilon,v_i^{(j)}),(q,p_2))\in T^2$.
+\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in T^2$.
 \end{itemize}	
-The first two cases correspond to the situation when the character variable $x_{i,j}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
+The first two cases correspond to the situation when the character variable $v_i^{(j)}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
 
@@
 \begin{itemize}
-	\item $((q_0,p_0), (x_{0,0},\epsilon),(q_1,p_0))$, because $(q_0,x_{0,0},q_1)$ is a transition of $A_{xy}$.
-	\item $((q_0,p_0), (\epsilon,y_{1,0}),(q_0,p_1))$, because $(p_0,y_{1,0},p_1)$ is a transition of $A_{yx}$.
-	\item $((q_0,p_0), (x_{0,0},y_{1,0}),(q_1,q_1))$, because $(q_0,x_{0,0},q_1)$ is a transition of $A_{xy}$ and $(p_0,y_{1,0},p_1)$ is a transition of $A_{yx}$.
+	\item $((q_0,p_0), (v_0^{(0)},\epsilon),(q_1,p_0))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$.
+	\item $((q_0,p_0), (\epsilon,v_2^{(1)}),(q_0,p_1))$, because $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
+	\item $((q_0,p_0), (v_0^{(0)},v_2^{(1)}),(q_1,q_1))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$ and $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
 \end{itemize}
@@
 Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section\ref{section:sfa}) and for any FA we can construct a Presburger formula characterizing its Parikh image (Section\ref{section:preliminary}).
-For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{v_{(x,y)}\mid (x,y) \in \cvar_\epsilon \times \cvar_\epsilon\}$ characterizing the Parikh image of $A$.
+For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{P{(v_i^{(j)},v_{i'}^{(j')})}\mid (v_i^{(j)},v_{i'}^{(j')}) \in \cvar^1_\epsilon \times \cvar^2_\epsilon\}$ characterizing the Parikh image of $A$.
+We use $P(v_i)$ and $P(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
+Then if $v_i^{(j)} \in \cvar^1$, then
+\begin{enumerate}
+	\item $P(v_i^{(j)}) = \sum_{v \in \cvar^2_\epsilon} P{(v_i^{j},v)}$, if $v_i^{(j)} \in \cvar^1$  
+	\item $P(v_i^{(j)}) = \sum_{v \in \cvar^1_\epsilon} P{(v,v_i^{j})}$, if $v_i^{(j)} \in \cvar^2$ 
+\end{enumerate}
+Note that $\cvar^1 \cap \cvar^2 =\emptyset$, because all variables will be renamed to some fresh variable. 
 Then we add the following linear constraints.
@@
 \begin{enumerate}
-	\item for any $(x_{i,j},y_{i',j'}) \in \cvar^1_\epsilon \times \cvar^2_\epsilon$, $v_{(x_{i,j},y_{i',j'})}>0 \rightarrow (x_j=y_{j})$. We use $-1$ to encode $\epsilon$.
-	\item for all $x \in \cvar$, $|x| =\sum_{y \in \cvar_\epsilon} (v_{(x,y)}+v_{(y,x)})$
+	\item For any $(v_i^{(j)},v_{i'}^{(j')}) \in \cvar^1 \times \cvar^2$, 
+	\begin{enumerate}
+		\item $P{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$,
+		\item $P{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and
+		\item $P{(\epsilon,v_{i'}^{(j')})}>0 \rightarrow (v_{i'}=\epsilon)$.
 	\end{enumerate}
-Those constraints enforce that the two size of the equality of the word equation sharing the same interpretation.
-
-We first build a product automata $\mathcal{P}=(Q\times P, T, \cvar\times \cvar, (q_i,p_i), (q_f,p_f))$, where $((q,p),(x,y), (q',p'))\in T$ iff $(q,x,q')\in T_Q \wedge (p,y,p')\in T_P$.
-Then the following formula characterizes all models of the equality constraint $Parikh(\mathcal{P}) \wedge \#(x,y) > 0 \rightarrow \enc{x} = \enc{y}$.
-
-In practice, building the product automata is an expensive operation.
-In practice, we consider SFA of special shape that allows more efficient translation from equality constraint to linear integer constraint.
-
-We define $(p,q)$-SFA as a SFA consisting of $p$ simple loops of length $q$, connected by epsilon transitions. Formally,
+	\item $P(v_i) = P(v_i^{(j)})$, for all $v_i\in \cvar$ and all different version numbers $j$ for $v_i$.
+\end{enumerate}
+The first constraint enforces the condition 1.
+and 2.
+and the second constraint enforces the condition 3.
+required for the pair of symbolic string $(w_n, w_m)$ and $I$.
+From the model $M$ of the linear constraints, we can obtain $w_n$, $w_m$, and $I$.
+$I(v)=M(v)$ for all $v\in \cvar$.
+Assume that the SFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{P(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{P(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{P(v_m^0)}$$
+One can construct $w_m$ in a similar way.
 

### 2019-09-26 draft.tex
some update

@@
 \newcommand{\true}{\mbox{$\mathsf{true}$}}
+\newcommand{\false}{\mbox{$\mathsf{false}$}}
 
-\newcommand{\enc}[1]{Enc(#1)}
-\newcommand{\ch}[1]{\mbox{`#1'}}
 \maketitle
@@
 In this paper, we propose an approach that handles string constraints with string-number conversion efficiently.
-The approach combines techniques from both automata theory and SMT solving to explore the model space of a string constraint systematically.
+From a theoretical point of view, this problem is already proven to be undecidable~\cite{vijay_rp}, and in practice, in our experiments, all of the state-of-the-art string constraint solvers do not support string-number conversion correctly.
+Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:experiment} for detailed explanation).
+Here we propose a strategy that uses both over and under-approximation of the string constraints.
+The over-approximation is for proving UNSAT and the under-approximation is for proving SAT of the string constraint.
+Both over and under-approximation should fail in a decidable fragment of string constraints and can be efficiently solved.
+
+For over-approximation, there are a few existing algorithms~\cite{atva2019,z3}, our strategy does not set any restriction on which algorithm to be used.
+In our experiences, the UNSAT instances in all available benchmarks are not that difficult and many approaches can handle all of them almost perfectly.
+The battle field is in fact those SAT instances.
+
 More specifically, instead of allowing the variable domain to be arbitrary strings from a finite alphabet, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
@@
 constraint. Note that a 64-bit integer number corresponds to a string with 
-$k\leq 21$.}
+$k\leq 21$.
+
+Given a formula that is a boolean combination of different types of string constraints, e.g., $\phi=(|x| = |y| \vee \sti{x} = \sti{y})\wedge x = y$, an SMT solver based on the DPLL(T) algorithm~\cite{} treats each string constraint $|x| = |y|$, $\sti{x} = \sti{y}$, $xy=yx$ as a boolean variable, and systematically guesses possible solutions without considering their semantics as string constraints.
+E.g., the solver may guess $\neg(|x| = |y|)$, $(\sti{x} = \sti{y})$, and $(x =y)$.
+This is a valid guess if all the string constraints are just interpreted as boolean variables, but invalid when their semantics as string constraints are considered, because it cannot be the case that $x$ and $y$ are the same string $(x =y)$, but they are of different lengths $( \neg (|x| = |y|))$.
+
+The approach combines techniques from both automata theory and SMT solving to explore the model space of a string constraint systematically.
+More specifically, an SMT solver based on the DPLL(T) algorithm~\cite{} is used to convert the satisfiability of a string constraint, which is an arbitrary boolean combination of string predicates, to the satisfiability problem of a set of string constraints in the form of conjunctions of string predicates.
+
+}
 
@@
 For example, the formula $\sti{x}=10 \wedge |x|=5$ is in fact satisfiable when $x=``00010"$.
-To handle the bounded integer case $y=\sti{x}$, we propose to restrict the domain of $x$ to a SFA of the form $(\{q_0,\ldots,q_k\},T,\cvar, q_0,q_k)$, where $k$ is the number of digits allowed in the bounded integer, $T = \{(q_0,x_0,q_0)\} \cup \{(q_i,x_{i+1},q_{i+1})\mid 0\leq i <k\}$, with additional numerical constraints $\enc{x_0}=\enc{\ch{0}}$ and $\wedge_{i\in [1,9]} \enc{\ch{0}}\leq \enc{x_i} \leq \enc{\ch{9}}$ to force the domain of the string to those corresponding to positive integers.
-Under this domain restriction, we obtain $y=\Sigma_{i\in [1,9]} 10^{k-i}\times (\enc{x_i}-\enc{\ch{0}})$.
+To handle the bounded integer case $y=\sti{x}$, we propose to restrict the domain of $x$ to a SFA of the form $(\{q_0,\ldots,q_k\},T,\{v_0,\ldots,v_k\}, q_0,q_k)$, where $k$ is the number of digits allowed in the bounded integer, $T = \{(q_0,v_0,q_0)\} \cup \{(q_i,v_{i+1},q_{i+1})\mid 0\leq i <k\}$, with additional numerical constraints $v_0=0$ and $\wedge_{i\in [1,k]} 0 \leq v_i \leq 9$ to force the domain of the string to those corresponding to positive integers.
+Under this domain restriction, we obtain $y=\Sigma_{i\in [1,k]} 10^{k-i}\times v_i$.
+
+\todo{Add a figure of the SFA above.}
 
@@
 This approach can be extended to unbounded string using more sophisticated pattern.
-For example, we can extend the bounded pattern that uses two loops, by changing the transition relation $T$ to $\{(q_0,x_0,q_0), (q_0,\epsilon,q_1), (q_k,x_1,q_1)\} \cup \{(q_i,x_{i+1},q_{i+1})\mid 0< i <k\}$.
+For example, we can extend the bounded pattern that uses two loops, by changing the transition relation $T$ to $\{(q_0,v_0,q_0), (q_0,\epsilon,q_1), (q_1,v_1,q_1)\}$.
 In this pattern, one can describe string that corresponds arbitrarily large integer.
-Taking the case $k=2$, $\enc{x_2}=\enc{\ch{3}}$, $\enc{x_1}=\enc{\ch{5}}$ as an example, any number in the form of $353535\ldots35$ can be expressed.
-Formally, the relation between $y$ and $x$ can be described in the following formula:
-$$y= (10*(\enc{x_2}-\enc{\ch{0}})+(\enc{x_1}-\enc{\ch{0}}))\times \frac{100^{\#(x_1)}-1}{100-1}$$
+More specifically, any number in the form of $v_1v_1\ldots v_1$ can be expressed.
+Formally, if $y=\sti{x}$ or $x=\its{y}$ the relation between $y$ and $x$ can be described in the following formula:
+$$y= (v_1)\times \frac{10^{P(v_1)}-1}{10-1}$$
 
-where $\#(x_1)$ is the number of occurrence of $x_1$ in the corresponding symbolic string and is treated as a variable in this case.
-To solve the satisfiability of this formula, one need to solve an exponential constraint.
+If we consider a more general form, e.g., using the flat automata in Figure~\ref{fig:sfa_def} to restrict the domain of $x$, then we should add integer constraints to restrict the character variables domain to be in $[0,9]$ and then using the formula below to describe the relation between $x$ and $y$.
+
+\[\begin{array}{lcl}
+	y & = & (v_m^0\times 10^3 + v_m^1 \times 10^2 + v_m^2 \times 10 +v_m^3 )\times \frac{10000^{P(v_m^0)}-1}{10000-1}+v_{m-1}\times 10000^{P(v_m^0)}\\
+
+	  &   &+\ldots+ \\
+
+	  &   &v_1\times10000^{P(v_m^0)} \times \ldots \times 1000^{P(v_1^0)}+\\
+	  &   &(v_0^0\times 10^3 + v_0^1 \times 10^2 + v_0^2 \times 10 +v_0^3 )\times \frac{10000^{P(v_0^0)}-1}{10000-1} \times 10000^{P(v_m^0)} \times \ldots \times \\
+	  &   &1000^{P(v_1^0)} \times 10
+\end{array}\]
+
+Recall that $P(x_1)$ is the number of occurrence of $v_1$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
+
 From the results of POPL2019, this problem is decidable if ....
+
+Recall that for equality constraint, we allow to restrict the domain of variables to arbitrary SFA.
+Under this framework, if $\sti{x}$ has occurred as a part of the formulae, then we always choose the SFAs described in this section to restrict the domain of $x$.
 

### 2019-10-01 draft.tex
update

@@
 
-\title{Handling String-number Conversion in String Constraint Solving}
+\title{Handling String-Number Conversion in String Constraint Solving}
 \author{}
@@
 \newcommand{\its}[1]{\mbox{\textbf{toStr}($#1$)}}
-\newcommand{\varn}{\mbox{$\mathbb{V}_n$}}
-\newcommand{\vars}{\mbox{$\mathbb{V}_s$}}
-\newcommand{\cvar}{\mbox{$\mathbb{C}$}}
+\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
+\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
+\newcommand{\cvar}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
+\newcommand{\cvarone}{\mbox{$\mathbb{V}^1_{\Sigma_\epsilon}$}}
+\newcommand{\cvartwo}{\mbox{$\mathbb{V}^2_{\Sigma_\epsilon}$}}
 \newcommand{\modelof}[1]{[\![#1]\!]}
@@
 \newcommand{\false}{\mbox{$\mathsf{false}$}}
+\newcommand{\enc}[1]{[\![#1]\!]}
 
@@
 very simple constraints. e.g., $y=str2int(x) \wedge y>9999999$, if $x$ is a 
-ASCII string, then XXX boolean variables are required. Or we can just propose 
+ASCII string, then XXX Boolean variables are required. Or we can just propose 
 an example that all major solver fails.
@@
 In this paper, we propose an approach that handles string constraints with string-number conversion efficiently.
-From a theoretical point of view, this problem is already proven to be undecidable~\cite{vijay_rp}, and in practice, in our experiments, all of the state-of-the-art string constraint solvers do not support string-number conversion correctly.
+This is a very challenging problem.
+From the theoretical point of view, this problem is already proven to be undecidable~\cite{vijay_rp}.
+In practice, in our experiments, all of the state-of-the-art string constraint solvers do not support string-number conversion correctly.
 Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:experiment} for detailed explanation).
-Here we propose a strategy that uses both over and under-approximation of the string constraints.
+Here we propose a framework that uses both over and under-approximation of the string constraints.
 The over-approximation is for proving UNSAT and the under-approximation is for proving SAT of the string constraint.
-Both over and under-approximation should fail in a decidable fragment of string constraints and can be efficiently solved.
+Both over and under-approximation should fail in a decidable fragment of string constraints that can be efficiently solved.
 
-For over-approximation, there are a few existing algorithms~\cite{atva2019,z3}, our strategy does not set any restriction on which algorithm to be used.
+For over-approximation, there are a few existing algorithms~\cite{atva2019,z3}, our framework does not set any restriction on which algorithm to be used.
 In our experiences, the UNSAT instances in all available benchmarks are not that difficult and many approaches can handle all of them almost perfectly.
 The battle field is in fact those SAT instances.
+In our prototype tool, we implement the algorithm presented in~\cite{atva2019}, in addition with some additional axioms, to handle the over-approximation of string constraints with number-string conversion.
 
-More specifically, instead of allowing the variable domain to be arbitrary strings from a finite alphabet, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
+For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
 By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
-In paper, we propose to use patterns defined by \emph{symbolic flat automata}, the automata are very expressive yet allows very efficiently manipulation.
+In paper, we propose to use patterns defined by \emph{symbolic flat automata} (SFA), the automata are very expressive yet allows very efficiently manipulation.
 For example, it avoids the alphabet
@@
 
-Based on the symbolic flat automata encoding, we manage to convert the 
-string-number function to a constraint consisting of both 
-polynomials and exponentials. To the best of our knowledge, the satisfiability 
-problem of a mix of polynomials and exponentials is still open. For the 
-particular case with only one number variable exponent, the satisfiability can 
-be decided using the algorithm in~\cite{POPL2019}.
-However, the algorithm involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence is not scalable to large instances.
-\todo{check correctness of the above statement} For bounded numbers, our approach converts string-number function to a linear integer constraint.
+Based on the SFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
+Thus the problem is significantly simplified.
+We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to a integer constraint consisting of both polynomials and exponentials (formula~\ref{formula:str_int}).
+To the best of our knowledge, the satisfiability prolem of integer constraints with a mix of polynomials and exponentials is still open.
+
+For the particular case with only one integer variable, the satisfiability can be decided using the algorithm in~\cite{POPL2019}.
+However, the algorithm involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence cannot handle large instances.
+
+For efficiency reason, we propose to use \emph{SFA with only one loop} to handle string-number conversion function.
+That is, if we encountered a constraint $y=\sti{x}$, then we always restrict the domain of $x$ to some SFA with one loop, instead of arbitrary SFAs.
+This allows us to convert a string constraint with string-number conversion function to a equisatisfiable linear integer constraint, which can be solved very efficiently.
+
+\todo{Talk about experiments}
+
 To ease presentation, in the main text, we only consider string constraints consisting of \emph{equality constraints (a.k.a.
@@
 
-A \emph{finite-state automaton} (FA) is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times \Sigma\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
-The semantics of FSA is defined in the standard manner.
-We use $L(A)$ to denote the regular language, i.e., set of accepted strings, of a FA $A$.
+A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
+The semantics of finite automaton is defined in the standard manner.
+We use $L(A)$ to denote the regular language, i.e., set of accepted strings, of a finite automaton $A$.
 
-Given a FA $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$.
-Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$.
+In this paper, we fix a finite alphabet $\Sigma \subseteq \mathbb{N}$.
+Note that here we assume the alphabet is a finite subset of natural numbers.
+Essentially, we try to capture the numerical encoding of the corresponding symbols in computers (e.g., in ASCII, `A' is encoded as $65$).
+We assume there is a one-one mapping between numbers in $\Sigma$ and the character it encodes.
+For simplicity of presentation, we assume the character `$0$' is mapped to number $0$, `$1$' to $1$,$\ldots$, and `$9$' to $9$.
+For other character $c$, we use $\enc{c}$ to denote the number that it maps to.
+Notice that this approach is general enough to support any finite set of characters.
+We write $[n,m]$ for the set of numbers (or symbols in $\Sigma$) $\{k\mid n\leq k \leq m\}$.
+A \emph{term} is an element in $(\vars\cup \Sigma)^*$.
+
+Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$.
+Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{peter}.
+
+We use $\vars$ to denote a finite set of string variables ranging over $\Sigma^*$, $\varn$ to denote a finite set of integer variables ranging over $\mathbb{Z}$, and $\cvar$ to denote a finite set of character variables  ranging over $\Sigma_\epsilon$.
+Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$.
+We call a string over $\cvar$ a \emph{symbolic string}. 
+For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$, $x^1$) its \emph{variants}.  
+In this paper, we use $x,y$ or their variants to denote variables in $\vars$, $n$ or its variants to denote variables in $\varn$, and $v$ and its variants for variables in $\cvar$.
+
+An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
+We lift $i$ to terms by defining $I: (\vars\cup \Sigma)^* \rightarrow \Sigma^*$ with $I(a) =a$ for $a\in \Sigma$ and $I(t_1 \cdot t_2) = I(t_1)\cdot I(t_2)$.
+An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
+For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Fix a finite alphabet $\Sigma \subseteq \mathbb{N}$, a finite set of string variables $\vars$ ranging over $\Sigma^*$, and a finite set of natural number variables $\varn$.
-Note that here we assume the alphabet is a finite subset of natural numbers.
-Essentially, we try to capture the numerical encoding of symbols (e.g., in ASCII, `A' is encoded as $65$) in computers.
-We write $[n,m]$ for the set of numbers (or symbols in $\Sigma$) $\{k\mid n\leq k \leq m\}$.
-A \emph{term} is an element in $(\vars\cup \Sigma)^*$.
-An \emph{interpretation} is a mapping from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
-We lift
-it to terms by defining $I: (\vars\cup \Sigma)^* \rightarrow \Sigma^*$ with $I(a) =a$ for $a\in \Sigma$ and $I(t_1 \cdot t_2) = I(t_1)\cdot I(t_2)$.
-
 The \emph{string-number conversion function} $\sti{x}$ is defined as follows.
-For $x\in [0,9]^+$ and $a\in [0,9]$, we have $\sti{a}=a$ and $\sti{x\cdot a} = 10\times \sti{x}+a$.
+For $a\in [0,9]$, we have $\sti{a}=a$ and for $x \cdot a \in [0,9]^+$, $\sti{x\cdot a} = 10\times \sti{x}+a$.
 For $x\notin [0,9]^+$, $\sti{x}=-1$.
 
-For a number $n=a_n*10^n+a_{n-1}*10^{n-1}+\ldots+a_0$ for $a_i\in [0,9], i\in [0,n]$, the \emph{number-string conversion function} $\its{n}=a_ia_{i-1}\ldots a_0$~\footnote{Notice that only positive integer is supported in this semantics.
+Notice that only positive integer is supported in this semantics.
 This is the semantics used by most of the SMT solvers, and hence we follow it in this paper.
-This is not a restriction, since conversing from negative integer can still be encoded using the positive only version.}.
+The encoding has a benefit that only can also handle the case where $x$ is ``not a number'', using the condition $sti{x} = -1$.
+
+Supporting only positive integer is not a strong restriction, since conversing from negative integer can still be encoded using the positive only version.
+More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number'', which can also be encoded using more conditions):
+
+$$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
+Recall that $\enc{-}$ is the integer encoding of the minus symbol `$-$'. The \emph{number-string conversion function} $\its{n}$ is defined symmetrically. We have $x = \its{n}$ iff $y= \sti{n}$.
 
@@
 
-An \emph{integer constraint} $\phi$ is a linear constraint over the variables in $\varn$, numerical values of strings $\sti{x}$, and length of a string $|x|$, for all string variables $x$ in $\vars$.
+An \emph{integer constraint} $\phi$ is a linear constraint over the variables in $\varn$ and length of a string $|x|$ for all $x \in \vars$.
 %Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{The Over-Approximation and Under-Approximation Framework} \label{section:framework}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Symbolic Flat Automata} \label{section:sfa}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\st}[2]{q_{#1}^{#2}}
+\newcommand{\sym}[2]{v_{#1}^{#2}}
 
-Fix a finite set of character variables $\cvar$ ranging over $\Sigma_\epsilon$.
-We call a string over $\cvar$ a symbolic string.
-A interpretation $I$ over $\cvar$ is a mapping from $\cvar$ to $\Sigma_\epsilon$.
-For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-
-We introduce \emph{symbolic flat automata} (SFA) $(Q,T,\cvar_\epsilon,q_0,q_m)$ that will be used to define patterns for the variable domain restriction.
-SFA is a finite-state automaton operating over the alphabet $\cvar_\epsilon$ and with additional structural constraints.
+We introduce \emph{symbolic flat automata} (SFA) $(Q,T,\cvar,\st{0}{0},\st{m}{0})$ that will be used to define patterns for the string variable domain restriction.
+SFA is a finite automaton operating over the alphabet $\cvar$ in addition with the following structural constraints.
 \begin{enumerate}
-	\item the initial state $q_0$ and final state $q_m$ are connected by a straight-line structure, i.e., $(q_i,v_i,q_i+1) \in T$ and states $q_i \in Q$ for $i\in[0,m-1]$.
-	\item  each state $q_i$ may be included to an unique simple cycle, i.e.
-$q_i^j \in Q$ and $(q_i, v_i^0, q_i^1), (q_j, v_i^j, q_i^{j+1}), (q_i^l, v_i^l, q_i) \in T$ for $i\in [0,n]$ and $j\in [1,l-1]$.
+	\item the initial state $\st{0}{0}$ and final state $\st{m}{0}$ are connected by a straight-line structure, i.e., $(\st{i}{0},v_i,\st{i+1}{0}) \in T$ and states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+	\item  each state $\st{i}{0}$ may be included to an unique simple cycle.
+Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$), then we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$, for $j\in [1,l_i]$.
 	\item each variable in $\cvar$ appears in at most one transition (but $\epsilon$ transition can appear multiple times). 
@@
 	\begin{tikzpicture} 
-		\node[state,initial] (q0)  {$q_0$};
-		\node[state] (q1) [right = 3cm of q0] {$q_1$};
+		\node[state,initial] (q0)  {$\st{0}{0}$};
+		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
 		\node (q2) [right = 1.8cm of q1]{};
 		\node (q3) [right = 1cm of q2]{};
-		\node[state,accepting] (qm) [right = 1.8cm of q3] {$q_m$};
+		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
 
-		\node[state] (q01) [above left = 0.6cm of q0] {$q_0^1$};
-		\node[state] (q02) [above = 1cm of q0] {$q_0^2$};
-		\node[state] (q03) [above right = 0.6cm of q0] {$q_0^3$};
+		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
+		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
+		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
 
-		\node[state] (q11) [above left = 0.8cm of q1] {$q_1^1$};
-		\node[state] (q12) [above right = 0.8cm of q1] {$q_1^2$};
+		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
+		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
 
-		\node[state] (qm1) [above left = 0.6cm of qm] {$q_m^1$};
-		\node[state] (qm2) [above = 1cm of qm] {$q_m^2$};
-		\node[state] (qm3) [above right = 0.6cm of qm] {$q_m^3$};
+		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
+		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
+		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
 
-  		\draw[->] (q0) edge [bend left] node [left]{$v_0^0$} (q01) ;
-  		\draw[->] (q01) edge [bend left] node [left]{$v_0^1$} (q02) ;
-  		\draw[->] (q02) edge [bend left] node [right]{$v_0^2$} (q03) ;
-  		\draw[->] (q03) edge [bend left] node [right]{$v_0^3$} (q0) ;
+  		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
+  		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
+  		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
+  		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
 
@@
 
-  		\draw[->] (qm) edge [bend left] node [left]{$v_m^0$} (qm1) ;
-		\draw[->] (qm1) edge [bend left] node [left]{$v_m^1$} (qm2) ;
-		\draw[->] (qm2) edge [bend left] node [right]{$v_m^2$} (qm3) ;
-		\draw[->] (qm3) edge [bend left] node [right]{$v_m^3$} (qm) ;
+  		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
+		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
+		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
+		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
 
-  		\draw[->] (q1) edge [bend left] node [left]{$v_1^0$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [above]{$v_1^1$} (q12) ;
-		\draw[->] (q12) edge [bend left] node [right]{$v_1^2$} (q1) ;
+  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
+		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
 	\end{tikzpicture} 
@@
 
-A FA $D=(Q,T',\Sigma_\epsilon,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar_\epsilon,q_0,q_m)$, if there exists an interpretation $I: \cvar_\epsilon \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
+A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
 We write $I(S)$ to denote the instance of $S$ wrt.
@@
 
-For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting string.
+For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
 For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
@@
 
-Assume that $S_n=(Q,T,\cvar^1_\epsilon,q_i,q_f)$ is the SFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvar^2_\epsilon,p_i,p_f)$ is the SFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
+Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the SFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the SFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
 Our next task is to find a model for $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$ under the domain restriction specified by $S_n$ and $S_m$.
+Note that $\cvarone \cap \cvartwo =\emptyset$, because all variables will be renamed to some fresh variable.
 
@@
 	\item $I$ assign to variants of the same variable the same value. For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}$ and $v_0^{(1)}$ should be assigned the same value.
-	\item variants of the same variable should occurs equally often in $w_n\cdot w_m$.
-For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_0^{(1)}v_1^{(1)}v_0^{(1)}v_1^{(1)}$ is a pair of symbolic strings satisfying this condition.
-The number of occurrences of $v_i^{(0)}$ is the same to $v_i^{(1)}$ for $i\in[0,1]$ in the concatenation of the two symbolic strings .
+	\item different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
+For example, in Figure~\ref{fig:sfa} (c) and (d), $w_{xy}=v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $w_{yx}=v_0^{(1)}v_1^{(1)}v_0^{(1)}v_1^{(1)}$ is a pair of symbolic strings satisfying this condition.
+The number of occurrences of $v_i^{(0)}$ is the same to $v_i^{(1)}$ for $i\in[0,1]$ in the concatenation $w_{xy}\cdot w_{yx}$.
 	But the pair $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_2^{(0)}v_3^{(0)}v_2^{(0)}v_3^{(0)}$ does not satisfy the condition. Observe that $v_0^{(0)}$ occurs twice, but $v_0^{(1)}$ is not there.
@@
 
-Such product automaton uses $Q\times P$ as the set of states and $\cvar^1_\epsilon \times \cvar^2_\epsilon$ as the alphabet.
+Such product automaton uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
 If a transition $((q_1,p_1), (v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $v_i$ and $v_{i'}$ (and so all of their indexed variants) should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
 
-More precisely, the product automaton is a tuple $(Q\times P, T^2, \cvar^1_\epsilon \times \cvar^2_\epsilon, (q_i,p_i),(q_f,p_f))$, where the transition relation $T^2$ is the minimal set satisfying the following.
+More precisely, the product automaton is a tuple $(Q\times P, T^2, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $T^2$ is the minimal set satisfying the following.
 
@@
 	\item $((q_0,p_0), (v_0^{(0)},\epsilon),(q_1,p_0))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$.
-	\item $((q_0,p_0), (\epsilon,v_2^{(1)}),(q_0,p_1))$, because $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
+	\item $((q_0,p_0), (\epsilon,\epsilon),(q_0,q_0))$, because $(p_0,\epsilon,q_0)$ is a transition of $A_{yx}$.
 	\item $((q_0,p_0), (v_0^{(0)},v_2^{(1)}),(q_1,q_1))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$ and $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
@@
 
-Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section\ref{section:sfa}) and for any FA we can construct a Presburger formula characterizing its Parikh image (Section\ref{section:preliminary}).
-For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{P{(v_i^{(j)},v_{i'}^{(j')})}\mid (v_i^{(j)},v_{i'}^{(j')}) \in \cvar^1_\epsilon \times \cvar^2_\epsilon\}$ characterizing the Parikh image of $A$.
-We use $P(v_i)$ and $P(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
-Then if $v_i^{(j)} \in \cvar^1$, then
+Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section~\ref{section:sfa}) and for any finite automaton we can construct a Presburger formula characterizing its Parikh image (Section~\ref{section:preliminary}).
+For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{\#{(v_i^{(j)},v_{i'}^{(j')})}\mid (v_i^{(j)},v_{i'}^{(j')}) \in \cvarone \times \cvartwo\}$ characterizing the Parikh image of $A$.
+We use $\#(v_i)$ and $\#(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
+The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product automaton.
 \begin{enumerate}
-	\item $P(v_i^{(j)}) = \sum_{v \in \cvar^2_\epsilon} P{(v_i^{j},v)}$, if $v_i^{(j)} \in \cvar^1$  
-	\item $P(v_i^{(j)}) = \sum_{v \in \cvar^1_\epsilon} P{(v,v_i^{j})}$, if $v_i^{(j)} \in \cvar^2$ 
+	\item for all $v_i^{(j)} \in \cvarone$, $\#(v_i^{(j)}) = \sum_{v \in {\cvartwo \cup \{\epsilon\}}} \#{(v_i^{j},v)}$   
+	\item for all $v_i^{(j)} \in \cvartwo$, $\#(v_i^{(j)}) = \sum_{v \in {\cvarone \cup \{\epsilon\}}} \#{(v,v_i^{j})}$ 
 \end{enumerate}
-Note that $\cvar^1 \cap \cvar^2 =\emptyset$, because all variables will be renamed to some fresh variable. 
-Then we add the following linear constraints.
 
+Then we add the following linear constraints to enforce  condition 1.
+and 2.
+required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
 \begin{enumerate}
-	\item For any $(v_i^{(j)},v_{i'}^{(j')}) \in \cvar^1 \times \cvar^2$, 
-	\begin{enumerate}
-		\item $P{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$,
-		\item $P{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and
-		\item $P{(\epsilon,v_{i'}^{(j')})}>0 \rightarrow (v_{i'}=\epsilon)$.
+	\item for all $v_i^{(j)}\in \cvarone$ and $v_{i'}^{(j')}\in \cvartwo$, $\#{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$, 
+	\item for all $v_i^{(j)}\in \cvarone$, $\#{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and
+	\item for all $v_{i'}^{(j')}\in \cvartwo$,$\#{(\epsilon,v_{i'}^{(j')})}>0 \rightarrow (v_{i'}=\epsilon)$.
 \end{enumerate}
-	\item $P(v_i) = P(v_i^{(j)})$, for all $v_i\in \cvar$ and all different version numbers $j$ for $v_i$.
-\end{enumerate}
-The first constraint enforces the condition 1.
-and 2.
-and the second constraint enforces the condition 3.
-required for the pair of symbolic string $(w_n, w_m)$ and $I$.
+We then add the linear constraints $\#(v_i) = \#(v_i^{(j)})$, for all $v_i\in \cvar$ and all different version numbers $j$ for $v_i$, to enforce condition 3, which says different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
+
 From the model $M$ of the linear constraints, we can obtain $w_n$, $w_m$, and $I$.
-$I(v)=M(v)$ for all $v\in \cvar$.
-Assume that the SFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{P(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{P(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{P(v_m^0)}$$
+The interpretation $I$ is defined as $I(v)=M(v)$ for all $v\in (\cvarone \cup \cvartwo)$.
+The symbolic words $w_n$ and $w_m$ can be obtained by traverse the SFAs following the number of occurrences of each character variables.
+More specifically, assume that the SFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{\#(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{\#(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{\#(v_m^0)}$$
+Note that $\#(v_0^0)=\#(v_0^1)=\#(v_0^2)=\#(v_0^3)$, so we just use $\#(v_0^0)$ to denote the number of times of first loop traversal.
 One can construct $w_m$ in a similar way.
+Using the same approach, one can derive the assignment to variables in $\vars$ using the corresponding count and values of variables in $\cvar$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this section, we discuss how to handle the constraint $n=\sti{x}$ by restrict the domain of $x$ to some SFA.
+Let us begin with a simple example, assume that we use the SFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
+Then we know that when $0\leq v_0,v_1 \leq 9$, then $n$ is a positive integer value, and otherwise $n =-1$.
+So we should first add the constraint $ ((0\leq v_0\leq 9) \wedge (0\leq v_1\leq 9)) \vee n=-1 $.
+
+For the case that $n$ is a positive integer, the value of $n$ can be characterized by a linear constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})$.
+Observe that when $\#(v_0)=1$, the loop is taken only once and we have $n=v_0\times 10+ v_1$. When $\#(v_0)=2$, the loop is taken twice and we have 
+$n=(v_0\times 10+ v_1) + ( v_0\times 10+ v_1)\times 100$.
+
 We begin the discussion with the conversion between bounded integers (e.g., 64-bits) and strings.
 Notice that even for bounded integer, the corresponding string can be of unbounded length.
-For example, the formula $\sti{x}=10 \wedge |x|=5$ is in fact satisfiable when $x=``00010"$.
+For example, the formula $\sti{x}=10 \wedge |x|=5$ is satisfiable when $x=``00010"$.
 To handle the bounded integer case $y=\sti{x}$, we propose to restrict the domain of $x$ to a SFA of the form $(\{q_0,\ldots,q_k\},T,\{v_0,\ldots,v_k\}, q_0,q_k)$, where $k$ is the number of digits allowed in the bounded integer, $T = \{(q_0,v_0,q_0)\} \cup \{(q_i,v_{i+1},q_{i+1})\mid 0\leq i <k\}$, with additional numerical constraints $v_0=0$ and $\wedge_{i\in [1,k]} 0 \leq v_i \leq 9$ to force the domain of the string to those corresponding to positive integers.

### 2019-10-02 draft.tex
update

@@
-\documentclass{llncs}
+\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
 
@@
 \author{}
-\institute{}
 
@@
 
-\begin{figure}
+\begin{figure*}
 	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
@@
 	\caption{An example of a symbolic flat automaton}
-\end{figure}
+\end{figure*}
 
@@
 	\label{fig:sfa}
-\end{figure}
+\end{figure*}
 
@@
 \begin{itemize}
-\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all $p\in P,((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in T^2$.
-\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all $q\in Q,((q,p_1),(\epsilon,v_i^{(j)}),(q,p_2))\in T^2$.
-\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in T^2$.
+\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in T^2$.
+\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in T^2$.
+\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in T^2$.
 \end{itemize}	
@@
 
-For the case that $n$ is a positive integer, the value of $n$ can be characterized by a linear constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})$.
-Observe that when $\#(v_0)=1$, the loop is taken only once and we have $n=v_0\times 10+ v_1$. When $\#(v_0)=2$, the loop is taken twice and we have 
-$n=(v_0\times 10+ v_1) + ( v_0\times 10+ v_1)\times 100$.
+For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)}}{100-1}$.
+The constraint uses $\#(v_0)$ to capture the total number of loop traversal.
 

### 2019-10-04 draft.tex
update

@@
 We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to a integer constraint consisting of both polynomials and exponentials (formula~\ref{formula:str_int}).
-To the best of our knowledge, the satisfiability prolem of integer constraints with a mix of polynomials and exponentials is still open.
+To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
 
@@
 
-For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)}}{100-1}$.
+For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)+1}-1}{100-1}$.
 The constraint uses $\#(v_0)$ to capture the total number of loop traversal.
+
+However, this constraint contains an exponential component $100^{\#(v_0)}$.
+To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
+For a more general form, if we restrict the domain of $x$ to the SFA in Figure~\ref{fig:sfa_def}, for the case when $n$ is positive, we have the following relation.
+
+\[\begin{array}{lcl}
+y & = & (v_m^0\times 10^3 + v_m^1 \times 10^2 + v_m^2 \times 10 +v_m^3 )\times\\
+&   & \frac{10000^{\#(v_m^0)+1}-1}{10000-1}+\\
+&  & v_{m-1}\times 10000^{\#(v_m^0)+1}\\
+
+&   &+\ldots+ \\
+
+&   &v_1\times10000^{\#(v_m^0)} \times \ldots \times 10000^{\#(v_1^0)}+\\
+&   &(v_0^0\times 10^3 + v_0^1 \times 10^2 + v_0^2 \times 10 +v_0^3 )\times\\
+&   &\frac{10000^{\#(v_0^0)}-1}{10000-1} \times 10000^{\#(v_m^0)} \times \ldots \times  10000^{\#(v_1^0)} \times 10
+\end{array}\]
+
+Recall that $\#(x_1)$ is the number of occurrence of $v_1$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
+
+For the particular case with only one integer variable, the satisfiability of integer constraints with a mix of polynomials and exponentials can be decided using the algorithm in~\cite{POPL2019}.
+However, the algorithm involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence cannot handle large instances.
 
@@
 
-\[\begin{array}{lcl}
-	y & = & (v_m^0\times 10^3 + v_m^1 \times 10^2 + v_m^2 \times 10 +v_m^3 )\times \frac{10000^{P(v_m^0)}-1}{10000-1}+v_{m-1}\times 10000^{P(v_m^0)}\\
-
-	  &   &+\ldots+ \\
-
-	  &   &v_1\times10000^{P(v_m^0)} \times \ldots \times 1000^{P(v_1^0)}+\\
-	  &   &(v_0^0\times 10^3 + v_0^1 \times 10^2 + v_0^2 \times 10 +v_0^3 )\times \frac{10000^{P(v_0^0)}-1}{10000-1} \times 10000^{P(v_m^0)} \times \ldots \times \\
-	  &   &1000^{P(v_1^0)} \times 10
-\end{array}\]
-
-Recall that $P(x_1)$ is the number of occurrence of $v_1$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
-
 From the results of POPL2019, this problem is decidable if ....

### 2019-10-06 draft.tex
new version

@@
 Thus the problem is significantly simplified.
-We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to a integer constraint consisting of both polynomials and exponentials (formula~\ref{formula:str_int}).
+We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to a integer constraint consisting of both polynomials and exponentials.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 This is the semantics used by most of the SMT solvers, and hence we follow it in this paper.
-The encoding has a benefit that only can also handle the case where $x$ is ``not a number'', using the condition $sti{x} = -1$.
+The encoding has a benefit that only can also handle the case where $x$ is ``not a number'', using the condition $\sti{x} = -1$.
 
@@
 	\end{tikzpicture}
+
+	\caption{An example of a symbolic flat automaton}
 	\label{fig:sfa_def}
-	\caption{An example of a symbolic flat automaton}
 \end{figure*}
@@
 The constraint uses $\#(v_0)$ to capture the total number of loop traversal.
+Notice that the constraint above contains an exponential component $100^{\#(v_0)}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
 
-However, this constraint contains an exponential component $100^{\#(v_0)}$.
+For a more general form, if we restrict the domain of $x$ to the SFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0^{(0)}\times 10+ v_1^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{v_0^{(0)}-1})\times 100^{v_2^{(0)}}+(v_2^{(0)}\times 10+ v_3^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{v_2^{(0)}-1}) =  (v_0^{(0)}\times 10+ v_1^{(0)}) \times \frac{100^{\#(v_0^{(0)})+1}-1}{100-1}\times 100^{v_2^{(0)}} + (v_2^{(0)}\times 10+ v_3^{(0)}) \times \frac{100^{\#(v_2^{(0)})+1}-1}{100-1}$.
+Observe that the formula has even more exponential components.
+
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
-For a more general form, if we restrict the domain of $x$ to the SFA in Figure~\ref{fig:sfa_def}, for the case when $n$ is positive, we have the following relation.
-
-\[\begin{array}{lcl}
-y & = & (v_m^0\times 10^3 + v_m^1 \times 10^2 + v_m^2 \times 10 +v_m^3 )\times\\
-&   & \frac{10000^{\#(v_m^0)+1}-1}{10000-1}+\\
-&  & v_{m-1}\times 10000^{\#(v_m^0)+1}\\
-
-&   &+\ldots+ \\
-
-&   &v_1\times10000^{\#(v_m^0)} \times \ldots \times 10000^{\#(v_1^0)}+\\
-&   &(v_0^0\times 10^3 + v_0^1 \times 10^2 + v_0^2 \times 10 +v_0^3 )\times\\
-&   &\frac{10000^{\#(v_0^0)}-1}{10000-1} \times 10000^{\#(v_m^0)} \times \ldots \times  10000^{\#(v_1^0)} \times 10
-\end{array}\]
-
-Recall that $\#(x_1)$ is the number of occurrence of $v_1$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
 
@@
 
-We begin the discussion with the conversion between bounded integers (e.g., 64-bits) and strings.
-Notice that even for bounded integer, the corresponding string can be of unbounded length.
+In order to handle the under-approximation of string-integer conversion efficiently, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.
+
+The SFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such SFA.
+With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
+Notice that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
 For example, the formula $\sti{x}=10 \wedge |x|=5$ is satisfiable when $x=``00010"$.
-To handle the bounded integer case $y=\sti{x}$, we propose to restrict the domain of $x$ to a SFA of the form $(\{q_0,\ldots,q_k\},T,\{v_0,\ldots,v_k\}, q_0,q_k)$, where $k$ is the number of digits allowed in the bounded integer, $T = \{(q_0,v_0,q_0)\} \cup \{(q_i,v_{i+1},q_{i+1})\mid 0\leq i <k\}$, with additional numerical constraints $v_0=0$ and $\wedge_{i\in [1,k]} 0 \leq v_i \leq 9$ to force the domain of the string to those corresponding to positive integers.
-Under this domain restriction, we obtain $y=\Sigma_{i\in [1,k]} 10^{k-i}\times v_i$.
 
-\todo{Add a figure of the SFA above.}
+\begin{figure}
+	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+	\begin{tikzpicture} 
+	\node[state,initial] (q0)  {$q_0$};
+	\node[state] (q1) [right = 1cm of q0] {$q_1$};
+	\node (q2) [right = 0.8cm of q1]{};
+	\node (q3) [right = 1cm of q2]{};
+	\node[state,accepting] (qm) [right = 1cm of q3] {$q_m$};
+
+	\draw[->] (q0) edge node [below]{$v_1$} (q1) ;
+	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
+	\draw[dotted] (q2) edge (q3) ;
+	\draw[->] (q3) edge node [below]{$v_m$} (qm) ;
+	\path (q0) edge [loop above] node {$v_0$} (q0);
+	\end{tikzpicture}
+
+	\caption{An example of a symbolic flat automaton}
+	\label{fig:sfa_its}
+\end{figure}
+
+Such SFA handles bounded integers (e.g., 10-digits or 64-bits) precisely and under-approximate the possible values of unbounded integers.
+It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
+Remember that the character variables can be assigned $\epsilon$.
+In order to handle such cases efficiently, we use an encoding that if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j,m]$, i.e., we shift all the $\epsilon$-transitions to the least significant digits.
+More specifically, we first define two functions:
+
+$$\mathsf{epsAfter(k)}::= (0\leq v_0,\ldots, v_k\leq 9) \wedge v_{k+1}=\ldots =v_m = -1$$
+$$\mathsf{toNumber(k)}::= (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})$$
+
+Then we can specify the relation between $n$ and the character variables as follows:
+$$(n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+
+The length of $x$ can be specified by the following formula.
+
+$\begin{array}{ccc}
+	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\wedge \\
+	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\wedge \\
+	& &\ldots\\
+	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\wedge\\
+	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
+\end{array}$
 
@@
 
-This approach can be extended to unbounded string using more sophisticated pattern.
-For example, we can extend the bounded pattern that uses two loops, by changing the transition relation $T$ to $\{(q_0,v_0,q_0), (q_0,\epsilon,q_1), (q_1,v_1,q_1)\}$.
-In this pattern, one can describe string that corresponds arbitrarily large integer.
-More specifically, any number in the form of $v_1v_1\ldots v_1$ can be expressed.
-Formally, if $y=\sti{x}$ or $x=\its{y}$ the relation between $y$ and $x$ can be described in the following formula:
-$$y= (v_1)\times \frac{10^{P(v_1)}-1}{10-1}$$
+\section{Evaluation}
 
-If we consider a more general form, e.g., using the flat automata in Figure~\ref{fig:sfa_def} to restrict the domain of $x$, then we should add integer constraints to restrict the character variables domain to be in $[0,9]$ and then using the formula below to describe the relation between $x$ and $y$.
-
-From the results of POPL2019, this problem is decidable if ....
-
-Recall that for equality constraint, we allow to restrict the domain of variables to arbitrary SFA.
-Under this framework, if $\sti{x}$ has occurred as a part of the formulae, then we always choose the SFAs described in this section to restrict the domain of $x$.
+\todo{copy a few tables from our test site to here}
 

### 2019-10-17 draft.tex
intro

@@
 \usepackage[autostyle]{csquotes}
+\usepackage{listings}
 
@@
 
+\lstdefinelanguage{JavaScript}{
+	keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
+	keywordstyle=\color{blue}\bfseries,
+	ndkeywords={class, export, boolean, throw, implements, import, this},
+	ndkeywordstyle=\color{darkgray}\bfseries,
+	identifierstyle=\color{black},
+	sensitive=false,
+	comment=[l]{//},
+	morecomment=[s]{/*}{*/},
+	commentstyle=\color{purple}\ttfamily,
+	stringstyle=\color{red}\ttfamily,
+	morestring=[b]',
+	morestring=[b]"
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{Why this problem is important? Need to say it is used often, e.g., read 
+\hide{Why this problem is important? Need to say it is used often, e.g., read 
 from text file or user input. Why this problem is challenging? It is undecidable. Some tricky cases 
@@
 
-In this paper, we propose an approach that handles string constraints with string-number conversion efficiently.
-This is a very challenging problem.
+String data type is omnipresent in modern programming languages.
+In such programs, \textit{string-number conversion function} is frequently used.
+For example, often that programs read plain string input from text files (e.g., in csv format), partition it according to some predefined separator symbols (e.g., the comma symbol), and then convert each string partition to the desired data type (often integers).
+In the reverse direction, programs also convert values in other data type back to string and store them as text files.
+
+Incorrect handling of string-number conversion can cause very subtle bugs.
+For example, in JavaScript, variables are untyped and (implicit) type conversion happens automatically to the stored values. Consider the program below
+
+\begin{lstlisting}[breaklines=true,language=JavaScript]
+var arr = [1,...,M];
+var input = //from user
+if(0<=input<M-1){
+	document.write(arr[input])
+}
+\end{lstlisting}
+
+The program reads input value from users and use it as the array index.
+This program works perfectly no matter the input is in string form (e.g., ``1'', ``3'') or numerical form (e.g., $1$, $3$).
+Both of them can pass though the range test (when the input is a string, it will be first convert to integer and then compared with $0$ and $M$).
+However, the programmer may find later that he wants to shift the index value by one, say, change \texttt{document.write(arr[input])} to \texttt{document.write(arr[input+1])}.
+In such case, the program will behave incorrectly if the type of the value stored in \texttt{input} is string.
+For example, when \texttt{input=="5"}, the \texttt{+} operator in \texttt{input+1} will be interpreted as string concatenation and the value $1$ will be converted to a string.
+Therefore, the program will output \texttt{arr["51"]} instead of \texttt{arr["6"]}.
+If one searches CVE (Common Vulnerabilities and Exposures), he/she can find a number of vulnerabilities (e.g., clauses array-out-of-bound) due to incorrect handling of string-number conversion.
+
+For the example above, we can detect the potential array-out-of-bound problem that happens when \texttt{input} stores a string value by checking the satisfiability of the string constraint below (the case \texttt{input} stores a integer value can be check by another formula).
+
+$$
+\begin{array}{c}
+0 \leq \sti{input}<M-1 \wedge \\
+\neg(index = input\cdot \its{1} \wedge 0 \leq \sti{index} <M-1)
+\end{array}
+$$
+
+Such constraint contains \textit{string-number conversion} functions (e.g., $\sti{input}$ and $\sti{index}$), \textit{equality constraints} (e.g., $index = input\cdot \its{1}$), and \textit{integer constraints} (e.g., $0 \leq \sti{input}<M$).
+Solving constraint of this kind is a very challenging problem.
 From the theoretical point of view, this problem is already proven to be undecidable~\cite{vijay_rp}.
@@
 Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:experiment} for detailed explanation).
-Here we propose a framework that uses both over and under-approximation of the string constraints.
+In this paper, we propose a framework that handles string constraints with string-number conversion efficiently.
+Our framework uses both over and under-approximation of the string constraints.
 The over-approximation is for proving UNSAT and the under-approximation is for proving SAT of the string constraint.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For proving UNSAT, our strategy first over-approximates string-number conversion function $n=\its{x}$ as an uninterpreted function with an additional axiom $n\leq 0 \rightarrow \sti{\its{n}}=n$.
+
+and then solve the entire constraint with a procedure that is similar to the one in ATVA 2019.
 

### 2019-10-18 draft.tex
fix intro, add references

@@
 String data type is omnipresent in modern programming languages.
-In such programs, \textit{string-number conversion function} is frequently used.
-For example, often that programs read plain string input from text files (e.g., in csv format), partition it according to some predefined separator symbols (e.g., the comma symbol), and then convert each string partition to the desired data type (often integers).
-In the reverse direction, programs also convert values in other data type back to string and store them as text files.
+Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.
+As a results, in the past, a significant amount of research efforts have been investigated to symbolic execution and test case generation of string manipulating programs~\cite{saxena2010symbolic,artzi2011framework,huang2004securing,sen2013jalangi}.
+The core enabling technology for these approaches is string constraint solving~\cite{kiezun2009hampi,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2}.
+However, all these modern solvers fall short when \textit{string-number conversion function} occurs in the program.
+
+String-number conversion function is very frequently used in string-manipulating programs.
+For example, often that programs read plain string input from text files, partition it according to some predefined separator symbol (e.g., the comma symbol), and then convert each string partition to the desired data type (often integers).
+In the reverse direction, programs also convert values in numerical data type back to string and store them as text files.
 
 Incorrect handling of string-number conversion can cause very subtle bugs.
-For example, in JavaScript, variables are untyped and (implicit) type conversion happens automatically to the stored values. Consider the program below
+For example, in JavaScript, variables are untyped and (implicit) type conversion happens automatically to the stored values. Consider the following simple program
 
@@
 However, the programmer may find later that he wants to shift the index value by one, say, change \texttt{document.write(arr[input])} to \texttt{document.write(arr[input+1])}.
-In such case, the program will behave incorrectly if the type of the value stored in \texttt{input} is string.
+In such case, the program is still correct if \texttt{input} is a number, but will behave incorrectly if \texttt{input} is a string.
 For example, when \texttt{input=="5"}, the \texttt{+} operator in \texttt{input+1} will be interpreted as string concatenation and the value $1$ will be converted to a string.
@@
 
-For the example above, we can detect the potential array-out-of-bound problem that happens when \texttt{input} stores a string value by checking the satisfiability of the string constraint below (the case \texttt{input} stores a integer value can be check by another formula).
+In the example above, we can detect the array-out-of-bound problem (that happens when \texttt{input} is a string) by checking the satisfiability of the string constraint below\footnote{The case \texttt{input} stores a integer value can be check by another formula.}.
 
@@
 Solving constraint of this kind is a very challenging problem.
-From the theoretical point of view, this problem is already proven to be undecidable~\cite{vijay_rp}.
+From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
 In practice, in our experiments, all of the state-of-the-art string constraint solvers do not support string-number conversion correctly.
-Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:experiment} for detailed explanation).
+Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:evaluation} for detailed explanation).
 In this paper, we propose a framework that handles string constraints with string-number conversion efficiently.
@@
 
-For over-approximation, there are a few existing algorithms~\cite{atva2019,z3}, our framework does not set any restriction on which algorithm to be used.
+For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3}, our framework does not set any restriction on which algorithm to be used.
 In our experiences, the UNSAT instances in all available benchmarks are not that difficult and many approaches can handle all of them almost perfectly.
 The battle field is in fact those SAT instances.
-In our prototype tool, we implement the algorithm presented in~\cite{atva2019}, in addition with some additional axioms, to handle the over-approximation of string constraints with number-string conversion.
+In our prototype tool, we implement the algorithm presented in~\cite{parosh2019chain}, in addition with some additional axioms, to handle the over-approximation of string constraints with number-string conversion.
 
@@
 By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
-In paper, we propose to use patterns defined by \emph{symbolic flat automata} (SFA), the automata are very expressive yet allows very efficiently manipulation.
-For example, it avoids the alphabet
-explosion problem that the approach in~\cite{PLDI2017} suffers.
+In paper, we propose to use patterns defined by \emph{symbolic flat automata} (SFA).
+The approach based on SFA is very flexible yet allows very efficiently manipulation.
+One can pick SFA of arbitrary structure for the search space restriction and reduce the string constraint solving problem to an integer constraint solving problem.
+For efficiency, it avoids the alphabet
+explosion problem that the approach in~\cite{abdulla2017flatten} suffers.
 
@@
 Thus the problem is significantly simplified.
-We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to a integer constraint consisting of both polynomials and exponentials.
-To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
-
-For the particular case with only one integer variable, the satisfiability can be decided using the algorithm in~\cite{POPL2019}.
-However, the algorithm involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence cannot handle large instances.
-
+We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to an integer constraint consisting of both polynomials and exponentials.
+Solving such kind of constraints is a very difficult task.
+For simpler cases where the variables are real numbers, decision procedures for different subclass polynomial-exponential equations exists~\cite{gan2015decidability,kincaid2019closed,achatz2008deciding}.
+To the best of our knowledge, the satisfiability problem of polynomial-exponential equations is still open.
 For efficiency reason, we propose to use \emph{SFA with only one loop} to handle string-number conversion function.
@@
 
-To ease presentation, in the main text, we only consider string constraints consisting of \emph{equality constraints (a.k.a.
+To ease presentation, in the paper, we only consider string constraints consisting of \emph{equality constraints (a.k.a.
 word equation)}, \emph{length constraints}, and \emph{string-number conversion} functions.
-We describe the extension to support transducer and membership constraints in the appendix.
+In fact, the approach can be easily extended to support transducer and membership constraints.
+The extension is implemented in our prototype tool \textsf{z3-Trau}.
 
@@
 \section{Evaluation}
-
+ \label{section:evaluation}
 \todo{copy a few tables from our test site to here}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{refs}
 

### 2019-10-18 draft.tex
add disequality

@@
 As a results, in the past, a significant amount of research efforts have been investigated to symbolic execution and test case generation of string manipulating programs~\cite{saxena2010symbolic,artzi2011framework,huang2004securing,sen2013jalangi}.
-The core enabling technology for these approaches is string constraint solving~\cite{kiezun2009hampi,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2}.
+The core enabling technology for these approaches is string constraint solving~\cite{kiezun2009hampi,abdulla2014string,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2}.
 However, all these modern solvers fall short when \textit{string-number conversion function} occurs in the program.
@@
 
-\section{Handling Equality and Disequality Constraint} \label{section:eq}
+\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
+
 Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some SFA with disjoint alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.
@@
 
+Disquality constraint $x_1\cdot x_2 \cdots x_n \neq x_{n+1}\cdot x_{n+2} \cdots x_m$ can be converted to equal-satisfiable equality constraints in the standard way~\cite{abdulla2015norn}.
+We replace it with the following constraints.
+
+$$
+\begin{array}{c}
+(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
+\left(
+	\begin{array}{cccc}
+
+	 y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
+	 y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
+	|y_2|&=&|y'_2|=1
+	\end{array}
+
+\right)
+\end{array}
+$$
+
+The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
+In an more efficient implementation, one just project $y_2$ and $y'_2$ to a SFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the SFA has no loop and only one transition).
+
 \todo{Maybe talk about the heuristic that we merge the list elements into one}

### 2019-11-05 draft.tex
some bug fix

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+String constraint solving has received considerable attention in the constraint solving community, with solvers such as CVC4 and Z3 implmenting solvers of ever-increasing sophistication.
+Operations such as substring and string length are widely supported, and recent solvers such as Z3-str3 have shown impressive results.
+However, these solvers have limited for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
+When there is support, it is often limited to ground terms, i.e.
+at least one side of the conversion must be a constant.
+Thus, $v = string2int("5")$ or $v = int2string(5)$ are handled but $v_1 = int2string(v_2)$ will fail.
+
+As solvers such Z3 are applied to symbolic execution of programming languages, this is increasingly becoming a severe limitation.
+For many languages such as Java, conversion between integers and strings is a niche operation, and much symbolic execution can be done without supporting it; however, this is not true of some scripting languages, of which JavaScript is the most notable.
+JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with nodejs---and it has conversions between strings and integers embedded in the core of its semantics.
+
+\begin{verbatim}
+function resetArray(arr) {
+  for(var i = 0; i < arr.length; i++) {
+    arr[i] = 0
+  }
+}
+\end{verbatim}
+
+A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: all array indices act like strings, and numeric indices are converted to strings.
+Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that uses {\tt{resetArray}}, with the value of {\tt{x}} shown on the right:
+
+\begin{tabular}{l|c}
+	{\tt{x = [0, 1, 2, 3, 4, 5]}} & [0, 1, 2, 3, 4, 5] \\
+	{\tt{resetArray(x)}} & [0, 0, 0, 0, 0, 0] \\
+	{\tt{x["3"] = 5}} & [0, 0, 0, 5, 0, 0] \\
+	{\tt{x["12"] = 7}} & [0, 0, 0, 5, 0, 0, , , , , , 7] \\
+	{\tt{resetArray(x)}} & [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0] \\
+\end{tabular}
+
+In this code, string and integer values access the same array elements interchangeably, necessitating conversions between string and integers to faithfully model JavaScript semantics.
+This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+
+Now observe that {\tt{resetArray}} assigns to the array in a loop of which the size cannot, in general, be known a priori; as such, falls into the case where neither the string nor the integer in a conversion are constant and hence most SMT solvers will not be able to handle it.
+But this is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+
+\todo{The end of Julian's current writing}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Overview} \label{section:overview}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For proving UNSAT, our strategy first over-approximates string-number conversion function $n=\its{x}$ as an uninterpreted function with an additional axiom $n\leq 0 \rightarrow \sti{\its{n}}=n$.
+
+and then solve the entire constraint with a procedure that is similar to the one in ATVA 2019.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Preliminary} \label{section:preliminary}
@@
 The semantics of finite automaton is defined in the standard manner.
-We use $L(A)$ to denote the regular language, i.e., set of accepted strings, of a finite automaton $A$.
+We use $L(A)$ to denote the regular language, i.e., set of accepted strings, of the automaton $A$.
 
@@
 
-Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$.
+Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
 Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{peter}.
@@
 We define  $\modelof{\phi}= \{I \mid I(\phi)= \true \}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Over-Approximation and Under-Approximation Framework} \label{section:framework}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-For proving UNSAT, our strategy first over-approximates string-number conversion function $n=\its{x}$ as an uninterpreted function with an additional axiom $n\leq 0 \rightarrow \sti{\its{n}}=n$.
-
-and then solve the entire constraint with a procedure that is similar to the one in ATVA 2019.
 

### 2019-11-05 draft.tex
some bug fix

@@
 \newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
-\newcommand{\cvar}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
-\newcommand{\cvarone}{\mbox{$\mathbb{V}^1_{\Sigma_\epsilon}$}}
-\newcommand{\cvartwo}{\mbox{$\mathbb{V}^2_{\Sigma_\epsilon}$}}
+\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
+\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
+\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
 \newcommand{\modelof}[1]{[\![#1]\!]}
@@
 
-In this paper, we fix a finite alphabet $\Sigma \subseteq \mathbb{N}$.
+Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
+Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{SeidlSMH04}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{String Constraints} \label{section:sc}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this section, we formally define string constraints and the decision problem we want to solve.
+We fix a finite alphabet $\Sigma \subseteq \mathbb{N}$.
 Note that here we assume the alphabet is a finite subset of natural numbers.
@@
 
-Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
-Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{peter}.
+We call $\vars$ the set of \emph{string variables} (ranging over $\Sigma^*$) and $\varn$ the set of \emph{integer variables} (ranging over $\mathbb{Z}$).
+For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$, $x^1$) its \emph{variants}.
+In this paper, we use $x,y$ (or their variants) to denote string variables and $n$ (or its variants) to denote integer variables.
 
-We use $\vars$ to denote a finite set of string variables ranging over $\Sigma^*$, $\varn$ to denote a finite set of integer variables ranging over $\mathbb{Z}$, and $\cvar$ to denote a finite set of character variables  ranging over $\Sigma_\epsilon$.
-Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$.
-We call a string over $\cvar$ a \emph{symbolic string}. 
-For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$, $x^1$) its \emph{variants}.  
-In this paper, we use $x,y$ or their variants to denote variables in $\vars$, $n$ or its variants to denote variables in $\varn$, and $v$ and its variants for variables in $\cvar$.
-
-An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
-We lift $i$ to terms by defining $I: (\vars\cup \Sigma)^* \rightarrow \Sigma^*$ with $I(a) =a$ for $a\in \Sigma$ and $I(t_1 \cdot t_2) = I(t_1)\cdot I(t_2)$.
-An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
-For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{String Constraints} \label{section:sc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The \emph{string-number conversion function} $\sti{x}$ is defined as follows.
@@
 This is the semantics used by most of the SMT solvers, and hence we follow it in this paper.
-The encoding has a benefit that only can also handle the case where $x$ is ``not a number'', using the condition $\sti{x} = -1$.
+The encoding has a benefit that it can also handle the case where $x$ is ``not a number'', using the condition $\sti{x} = -1$.
 
@@
 
+An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
+We lift $I$ to terms (i.e., an element in $(\vars\cup \Sigma)^*$) in the standard manner.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\sym}[2]{v_{#1}^{#2}}
+We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$.
+Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$.
+We use $v$ and its variants for character variables.
+We call a string over $\cvar$ (character variables) a \emph{symbolic string}.
+An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
+For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 

### 2019-11-05 draft.tex
synctex
polish the definition of string constraints

@@
 
-In this section, we formally define string constraints and the decision problem we want to solve.
-We fix a finite alphabet $\Sigma \subseteq \mathbb{N}$.
+In this section, we formally define string constraints.
+To begin with, we fix an finite alphabet $\Sigma \subseteq \mathbb{N}$.
 Note that here we assume the alphabet is a finite subset of natural numbers.
 Essentially, we try to capture the numerical encoding of the corresponding symbols in computers (e.g., in ASCII, `A' is encoded as $65$).
-We assume there is a one-one mapping between numbers in $\Sigma$ and the character it encodes.
-For simplicity of presentation, we assume the character `$0$' is mapped to number $0$, `$1$' to $1$,$\ldots$, and `$9$' to $9$.
+We assume there is an one-one mapping between numbers in $\Sigma$ and the character it encodes.
+For the simplicity of presentation, we assume the character `$0$' is mapped to the number $0$, `$1$' to $1$,$\ldots$, and `$9$' to $9$.
 For other character $c$, we use $\enc{c}$ to denote the number that it maps to.
@@
 We write $[n,m]$ for the set of numbers (or symbols in $\Sigma$) $\{k\mid n\leq k \leq m\}$.
-A \emph{term} is an element in $(\vars\cup \Sigma)^*$.
 
-We call $\vars$ the set of \emph{string variables} (ranging over $\Sigma^*$) and $\varn$ the set of \emph{integer variables} (ranging over $\mathbb{Z}$).
-For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$, $x^1$) its \emph{variants}.
+We call $\vars$ the set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ the set of \emph{integer variables} ranging over $\mathbb{Z}$.
+For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$) its \emph{variants}.
 In this paper, we use $x,y$ (or their variants) to denote string variables and $n$ (or its variants) to denote integer variables.
 
-The \emph{string-number conversion function} $\sti{x}$ is defined as follows.
-For $a\in [0,9]$, we have $\sti{a}=a$ and for $x \cdot a \in [0,9]^+$, $\sti{x\cdot a} = 10\times \sti{x}+a$.
-For $x\notin [0,9]^+$, $\sti{x}=-1$.
+An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
+A \emph{term} is an element in $(\vars\cup \Sigma)^*$.
+We lift the interpretation $I$ to terms and linear constraints in the standard manner.
 
-Notice that only positive integer is supported in this semantics.
+An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
+t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelof{\phi_e}=\{I\mid 
+I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
+t_2$ and is interpreted analogously.
+
+An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a string $|x|$ for all $x \in \vars$.
+%Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
+We define $\modelof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
+We define  $\modelof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.
+
+The \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
+For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$.
+For $s\notin [0,9]^+$, $\sti{s}=-1$.
+We define  $\modelof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.
+
+A \emph{string constraint} $\phi$ is in the form of $\bigwedge_{\pi \in \Pi} \pi$, where $\Pi$ is a set of the above three kinds of constraints.
+We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelof{\pi}$ is not empty.
+
+Notice that only positive integer is supported in the string-number conversion function.
 This is the semantics used by most of the SMT solvers, and hence we follow it in this paper.
@@
 More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number'', which can also be encoded using more conditions):
-
 $$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
 Recall that $\enc{-}$ is the integer encoding of the minus symbol `$-$'. The \emph{number-string conversion function} $\its{n}$ is defined symmetrically. We have $x = \its{n}$ iff $y= \sti{n}$.
-
-A \emph{equality constraint} $\phi$ is of the form $t_1 = t_2$ where $t_1, 
-t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi$ is the set of interpretations $\modelof{\phi}=\{I\mid 
-I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
-t_2$ and is interpreted analogously.
-
-An \emph{integer constraint} $\phi$ is a linear constraint over the variables in $\varn$ and length of a string $|x|$ for all $x \in \vars$.
-%Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
-We define $\modelof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
-We define  $\modelof{\phi}= \{I \mid I(\phi)= \true \}$.
-
-An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
-We lift $I$ to terms (i.e., an element in $(\vars\cup \Sigma)^*$) in the standard manner.
 

### 2019-11-05 draft.tex
changes in prelims and in flat automata defs

--- 2019-11-05 draft.tex
@@
 \usepackage{listings}
+\synctex=1
 
@@
 \newcommand{\todo}[1]{{\color{blue}TODO: #1}}
+\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
 \newcommand{\sti}[1]{\mbox{\textbf{toInt}($#1$)}}
@@
 \newcommand{\enc}[1]{[\![#1]\!]}
+\newcommand{\parikh}{\mathit{Parikh}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminary} \label{section:preliminary}
+\section{Preliminaries} \label{section:preliminary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
-integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
-use $|w|$ to denote its length and $|w|_a$ to denote the number of occurrences of $a$ in $w$.
+%We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
+%integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
+%use $|w|$ to denote its length and $|w|_a$ to denote the number of occurrences of $a$ in $w$.
 We $\epsilon$ to denote an empty string and use $w_1\cdot w_2$ to denote the concatenation of strings $w_1$ and $w_2$.
@@
 A language
-$L$ over $S$ is a set of strings in $S^*$.
-
-A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
+%$L$ over $S$ is a set of strings in $S^*$. 
+%
+%A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
 The semantics of finite automaton is defined in the standard manner.
@@
 
-Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
+%Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
 Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{SeidlSMH04}.
+
+We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers (including 0) and 
+integers. For a set $A$, we use $|A|$ to denote its size. 
+An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{string} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty string}.
+We use $w_1\cdot w_2$ to denote the \emph{concatenation} of strings $w_1$ and $w_2$.
+$\Sigma^*$ is the set of all strings over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, and 
+A \emph{language} over $\Sigma$ is a subset $L$ of $\Sigma^*$.  
+%
+We use $|w|$ to denote the lenght of $w$ and $|w|_a$ to denote the number of occurrences of the character $a\in \Sigma$ in $w$.  
+The \emph{Parikh image} of $w$ is the assignment 
+%$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
+$\parikh(w)$ that maps every character $a\in\Sigma$ to the number of its occurences in $w$, i.e., $\parikh(a) = |w|_a$. 
+The Parikh image of a language $L$ is the set of Parikh images $\parikh(L) = \{\parikh(w) \mid w \in  L\}$.
+
+A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}.
+%The semantics of finite automaton is defined in the standard manner. 
+We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
+\lh{If we later start technical talking about tings like runs then we should include this definition.}
 
@@
 \newcommand{\sym}[2]{v_{#1}^{#2}}
-We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$.
-Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$.
-We use $v$ and its variants for character variables.
-We call a string over $\cvar$ (character variables) a \emph{symbolic string}.
-An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
+%We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
+%Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$. 
+%We use $v$ and its variants for character variables. We call a string over $\cvar$ (character variables) a \emph{symbolic string}.
+%An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
 For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 
-We introduce \emph{symbolic flat automata} (SFA) $(Q,T,\cvar,\st{0}{0},\st{m}{0})$ that will be used to define patterns for the string variable domain restriction.
-SFA is a finite automaton operating over the alphabet $\cvar$ in addition with the following structural constraints.
+We introduce \emph{symbolic flat automata} (SFA) that will be used to define patterns 
+%for the string variable domain restriction. 
+used by the underapproximation module to restrict the domain of string variables. 
+Namely, an SFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
+and satisfying the following structural constraints:
 \begin{enumerate}
-	\item the initial state $\st{0}{0}$ and final state $\st{m}{0}$ are connected by a straight-line structure, i.e., $(\st{i}{0},v_i,\st{i+1}{0}) \in T$ and states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
-	\item  each state $\st{i}{0}$ may be included to an unique simple cycle.
-Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$), then we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$, for $j\in [1,l_i]$.
-	\item each variable in $\cvar$ appears in at most one transition (but $\epsilon$ transition can appear multiple times). 
+	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a stright path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+%, with pairwise distiand states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+	\item  
+Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
+Notice that case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
+%Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$). 
+%For each $j\in [1,l_i]$, we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$. 
+%(where $l_i = 0$ means that there is no cycle on $q_i$)
+	\item Each variable in $\cvar$ appears on at most one transition (but $\epsilon$ transition can appear multiple times). 
 \end{enumerate} 
-Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
+%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
+Symbolic automata accept strings over $\cvar$, called \emph{symbolic strings}. 
+Each symbolic string may be interpeted as a string over $\Sigma$, given an assignment of characters to its character variables.  
+%
+Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 
@@
 
-A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
+%A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
 We write $I(S)$ to denote the instance of $S$ wrt.
@@
 
-For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
+The purpose of the structural restrictions of SFA is to ensure that the words of $L(A)$ are uniquelly determined by their Parikh images, as formalised by the following lemma.
+
+\begin{lemma}
+%Distict words from the language of an SFA must have distinct Parikh images.  
+For an SFA $A$ and $x,y\in L(A)$ if $\parikh(x) = \parikh(y)$ then $x = y$. 
+%Distict words from the language of an SFA have distinct Parikh images.  
+\end{lemma}
+Indeed, notice that each accepted symbolic string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
+Since every variable appears on at most one transition, 
+the number of repetitions of each cyclce equals the value each variable on the edges of the cycle has assigned by $\parikh(x)$ (notice also that $\parikh(x)$ must assign to all variables appearing within the same cycle the same value).
+
+%For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
 For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
@@
 
+\lh{so far not sure about how and where to present this:}
 \begin{lemma}
@@
 \end{lemma}
-
-\todo{Mention NDD when talk about our practical bounded encoding for str2int}
 

### 2019-11-06 draft.tex
little things

@@
 \newcommand{\enc}[1]{[\![#1]\!]}
-\newcommand{\parikh}{\mathit{Parikh}}
+\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
 
@@
 %$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
-$\parikh(w)$ that maps every character $a\in\Sigma$ to the number of its occurences in $w$, i.e., $\parikh(a) = |w|_a$. 
-The Parikh image of a language $L$ is the set of Parikh images $\parikh(L) = \{\parikh(w) \mid w \in  L\}$.
+$\parikhof w$ that maps every character $a\in\Sigma$ to the number of its occurences in $w$, i.e., $\parikhof w (a) = |w|_a$. 
+The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
 
@@
 
-The purpose of the structural restrictions of SFA is to ensure that the words of $L(A)$ are uniquelly determined by their Parikh images, as formalised by the following lemma.
+The purpose of the structural restrictions of SFA is to ensure that the words of $L(A)$ are uniquely determined by their Parikh images, as formalised by the following lemma.
 
 \begin{lemma}
-%Distict words from the language of an SFA must have distinct Parikh images.  
-For an SFA $A$ and $x,y\in L(A)$ if $\parikh(x) = \parikh(y)$ then $x = y$. 
+%Distinct words from the language of an SFA must have distinct Parikh images.  
+For an SFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
 %Distict words from the language of an SFA have distinct Parikh images.  
@@
 Indeed, notice that each accepted symbolic string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
-Since every variable appears on at most one transition, 
-the number of repetitions of each cyclce equals the value each variable on the edges of the cycle has assigned by $\parikh(x)$ (notice also that $\parikh(x)$ must assign to all variables appearing within the same cycle the same value).
+Since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
+%
+The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$.
 
-%For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
-For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
-Moreover, from $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$, we can derive $w=v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ by exploring the automata structure.
+For example, in the example of Figure~\ref{fig:sfa_def}, 
+from $\parikhof x(v_0) = \parikhof x(v_1) = \cdots = \parikhof x(v_{m-1})=1$ and $\parikhof x(v^0_1)=\parikhof x(v^1_1)=\parikhof x(v^2_1)=2$, then $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
 \todo{add Presburger constraints to allow more expressive power.}

### 2019-11-06 draft.tex
evaluation section: initial
polish the definition of string constraints

@@
 \usepackage{listings}
-\synctex=1
 
@@
 \newcommand{\todo}[1]{{\color{blue}TODO: #1}}
-\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
-\newcommand{\sti}[1]{\mbox{\textbf{toInt}($#1$)}}
-\newcommand{\its}[1]{\mbox{\textbf{toStr}($#1$)}}
+\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
+\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
 \newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
@@
 \newcommand{\enc}[1]{[\![#1]\!]}
-\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminaries} \label{section:preliminary}
+\section{Preliminary} \label{section:preliminary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
-%integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
-%use $|w|$ to denote its length and $|w|_a$ to denote the number of occurrences of $a$ in $w$.
+We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
+integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
+use $|w|$ to denote its length and $|w|_a$ to denote the number of occurrences of $a$ in $w$.
 We $\epsilon$ to denote an empty string and use $w_1\cdot w_2$ to denote the concatenation of strings $w_1$ and $w_2$.
@@
 A language
-%$L$ over $S$ is a set of strings in $S^*$. 
-%
-%A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
+$L$ over $S$ is a set of strings in $S^*$.
+
+A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
 The semantics of finite automaton is defined in the standard manner.
@@
 
-%Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
+Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in  L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
 Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{SeidlSMH04}.
-
-We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers (including 0) and 
-integers. For a set $A$, we use $|A|$ to denote its size. 
-An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{string} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty string}.
-We use $w_1\cdot w_2$ to denote the \emph{concatenation} of strings $w_1$ and $w_2$.
-$\Sigma^*$ is the set of all strings over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, and 
-A \emph{language} over $\Sigma$ is a subset $L$ of $\Sigma^*$.  
-%
-We use $|w|$ to denote the lenght of $w$ and $|w|_a$ to denote the number of occurrences of the character $a\in \Sigma$ in $w$.  
-The \emph{Parikh image} of $w$ is the assignment 
-%$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
-$\parikhof w$ that maps every character $a\in\Sigma$ to the number of its occurences in $w$, i.e., $\parikhof w (a) = |w|_a$. 
-The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
-
-A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}.
-%The semantics of finite automaton is defined in the standard manner. 
-We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
-\lh{If we later start technical talking about tings like runs then we should include this definition.}
 
@@
 \newcommand{\sym}[2]{v_{#1}^{#2}}
-%We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
-%Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$. 
-%We use $v$ and its variants for character variables. We call a string over $\cvar$ (character variables) a \emph{symbolic string}.
-%An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
+We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$.
+Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$.
+We use $v$ and its variants for character variables.
+We call a string over $\cvar$ (character variables) a \emph{symbolic string}.
+An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
 For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 
-We introduce \emph{symbolic flat automata} (SFA) that will be used to define patterns 
-%for the string variable domain restriction. 
-used by the underapproximation module to restrict the domain of string variables. 
-Namely, an SFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
-and satisfying the following structural constraints:
+We introduce \emph{symbolic flat automata} (SFA) $(Q,T,\cvar,\st{0}{0},\st{m}{0})$ that will be used to define patterns for the string variable domain restriction.
+SFA is a finite automaton operating over the alphabet $\cvar$ in addition with the following structural constraints.
 \begin{enumerate}
-	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a stright path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
-%, with pairwise distiand states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
-	\item  
-Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
-Notice that case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
-%Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$). 
-%For each $j\in [1,l_i]$, we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$. 
-%(where $l_i = 0$ means that there is no cycle on $q_i$)
-	\item Each variable in $\cvar$ appears on at most one transition (but $\epsilon$ transition can appear multiple times). 
+	\item the initial state $\st{0}{0}$ and final state $\st{m}{0}$ are connected by a straight-line structure, i.e., $(\st{i}{0},v_i,\st{i+1}{0}) \in T$ and states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+	\item  each state $\st{i}{0}$ may be included to an unique simple cycle.
+Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$), then we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$, for $j\in [1,l_i]$.
+	\item each variable in $\cvar$ appears in at most one transition (but $\epsilon$ transition can appear multiple times). 
 \end{enumerate} 
-%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
-Symbolic automata accept strings over $\cvar$, called \emph{symbolic strings}. 
-Each symbolic string may be interpeted as a string over $\Sigma$, given an assignment of characters to its character variables.  
-%
-Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
 
@@
 
-%A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
+A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
 We write $I(S)$ to denote the instance of $S$ wrt.
@@
 
-The purpose of the structural restrictions of SFA is to ensure that the words of $L(A)$ are uniquely determined by their Parikh images, as formalised by the following lemma.
-
-\begin{lemma}
-%Distinct words from the language of an SFA must have distinct Parikh images.  
-For an SFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
-%Distict words from the language of an SFA have distinct Parikh images.  
-\end{lemma}
-Indeed, notice that each accepted symbolic string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
-Since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
-%
-The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$.
-
-For example, in the example of Figure~\ref{fig:sfa_def}, 
-from $\parikhof x(v_0) = \parikhof x(v_1) = \cdots = \parikhof x(v_{m-1})=1$ and $\parikhof x(v^0_1)=\parikhof x(v^1_1)=\parikhof x(v^2_1)=2$, then $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
+For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
+For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
+Moreover, from $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$, we can derive $w=v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ by exploring the automata structure.
 \todo{add Presburger constraints to allow more expressive power.}
 
-\lh{so far not sure about how and where to present this:}
 \begin{lemma}
@@
 \end{lemma}
+
+\todo{Mention NDD when talk about our practical bounded encoding for str2int}
 

### 2019-11-06 draft.tex
some misc changes

--- 2019-11-06 draft.tex
@@
 \newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
+\newcommand{\parikhwof}[2]{|#1|_{#2}}
 
@@
 For example, in the example of Figure~\ref{fig:sfa_def}, 
-from $\parikhof x(v_0) = \parikhof x(v_1) = \cdots = \parikhof x(v_{m-1})=1$ and $\parikhof x(v^0_1)=\parikhof x(v^1_1)=\parikhof x(v^2_1)=2$, then $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
+from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
+\todo{add Presburger constraints to allow more expressive power.}
+
+%For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
+For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
+Moreover, from $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$, we can derive $w=v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ by exploring the automata structure.
 \todo{add Presburger constraints to allow more expressive power.}
@@
 
-\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
+%\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
+\section{Flat Underapproximation for Equalities and Regular Constraints} \label{section:eq}
 

### 2019-11-06 evaluation.tex

\section{Evaluation}
\label{section:evaluation}

\todo{Organize/Revise the context; Revise tables; Discussions}

{\bf General description}:
In this section, we report and discuss our experiments. As a base result, we compare z3-Trau to SMT tools z3 and CVC4 on PyEx benchmark which is widely used for testing SMT string solvers to show the performance of z3-Trau in general. Then we do the same comparison on our string\_to\_int benchmarks to evaluate our approach.

{\bf How we obtained our (str\_int) benchmark}:
For experiments, we prepared our own str\_int benchmark\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}. It is collected from two sources of Python programs: Leetcode solutions written in Python and Python core libraries. These Python programs are concolic tested by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs. The SMT queries during the concolic testing are collected to the benchmark. The benchmark has two versions: full\_str\_int and filtered\_str\_int. full\_str\_int is the original benchmark we collected; filtered\_str\_int is that we filtered out cases that cvc4 says unsat while the unsat corers are not containing \texttt{str.to.int} or \texttt{int.to.str}.

{\bf The environment of experiments}:
The experiments are conducted under machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. Since the large amount of problems in these benchmarks, we use containers to run these experiments in several machines with the same environment. The timeout is set to 10 seconds.

{\bf Some annotations in tables}:
\texttt{u.k.} stands for ``unknown''. \texttt{t.o.} stands for ``timeout''. \texttt{error} means that the execution is stopped with an error or exception such as segmental fault. \texttt{misc} means that the execution ends without expected (including errors) output.

{\bf Tabales}:
Table~\ref{table:pyex} shows the comparison on PyEx benchmark. The total amount of cases in PyEx (PyEx\_unsat, PyEx\_sat, PyEx\_todo) is 25421.

\begin{table}[]
\caption{Results of z3-Trau, cvc4, and z3 on PyEx benchmark}
\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
z3-Trau		& 19655 & 3851 & 0 & 1915 & 0 & 0 \\ 
cvc4		& 19763 & 3834 & 0 & 0 & 0 & 1824 \\ 
z3seq		& 16578 & 3832 & 0 & 5011 & 0 & 0 \\ 
z3str3		& 3023 & 3835 & 9 & 16717 & 1125 & 712 \\ \hline
\end{tabular}
\label{table:pyex}
\end{table}

Table~\ref{table:full_str_int} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
\begin{table}[]
\caption{Results of z3-Trau, cvc4, and z3 on full\_str\_int benchmark}
\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
z3-Trau		& 3289 & 17089 & 0 & 1195 & 0 & 0 \\ 
cvc4		& 2185 & 16377 & 0 & 3011 & 0 & 0 \\ 
z3seq		& 2716 & 16831 & 0 & 2026 & 0 & 0 \\ 
z3str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
\end{tabular}
\label{table:full_str_int}
\end{table}

Table~\ref{table:filtered_str_int} shows the comparison on filtered\_str\_int.  The total amount of cases in filtered\_str\_int is 7396.

\begin{table}[]
\caption{Results of z3-Trau, cvc4, and z3 on filtered\_str\_int benchmark}
\begin{tabular}{|r|r|r|r|r|r|r|}
\hline
Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
z3-Trau		& 3281 & 2912 & 0 & 1203 & 0 & 0 \\ 
cvc4		& 2210 & 2211 & 0 & 2975 & 0 & 0 \\ 
z3seq		& 2729 & 2655 & 0 & 2012 & 0 & 0 \\ 
z3str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
\end{tabular}
\label{table:filtered_str_int}
\end{table}

### 2019-11-07 draft.tex
polish str-int conv encoding

@@
 \newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
-\newcommand{\sti}[1]{\mbox{\textbf{toInt}($#1$)}}
-\newcommand{\its}[1]{\mbox{\textbf{toStr}($#1$)}}
+\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
+\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
 \newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
@@
 %
-We use $|w|$ to denote the lenght of $w$ and $|w|_a$ to denote the number of occurrences of the character $a\in \Sigma$ in $w$.  
+We use $|w|$ to denote the length of $w$ and $|w|_a$ to denote the number of occurrences of the character $a\in \Sigma$ in $w$.  
 The \emph{Parikh image} of $w$ is the assignment 
 %$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
-$\parikhof w$ that maps every character $a\in\Sigma$ to the number of its occurences in $w$, i.e., $\parikhof w (a) = |w|_a$. 
+$\parikhof w$ that maps every character $a\in\Sigma$ to the number of its occurrences in $w$, i.e., $\parikhof w (a) = |w|_a$. 
 The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
@@
 %for the string variable domain restriction. 
-used by the underapproximation module to restrict the domain of string variables. 
+used by the under-approximation module to restrict the domain of string variables. 
 Namely, an SFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
@@
 	\item  
-Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
+Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
 Notice that case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
@@
 Symbolic automata accept strings over $\cvar$, called \emph{symbolic strings}. 
-Each symbolic string may be interpeted as a string over $\Sigma$, given an assignment of characters to its character variables.  
+Each symbolic string may be interpreted as a string over $\Sigma$, given an assignment of characters to its character variables.  
 %
@@
 %\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
-\section{Flat Underapproximation for Equalities and Regular Constraints} \label{section:eq}
+\section{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}
 
@@
 
-Disquality constraint $x_1\cdot x_2 \cdots x_n \neq x_{n+1}\cdot x_{n+2} \cdots x_m$ can be converted to equal-satisfiable equality constraints in the standard way~\cite{abdulla2015norn}.
+Disequality constraint $x_1\cdot x_2 \cdots x_n \neq x_{n+1}\cdot x_{n+2} \cdots x_m$ can be converted to equal-satisfiable equality constraints in the standard way~\cite{abdulla2015norn}.
 We replace it with the following constraints.
@@
 
-In this section, we discuss how to handle the constraint $n=\sti{x}$ by restrict the domain of $x$ to some SFA.
+In this section, we discuss how to handle the constraint $n=\sti{x}$ by restricting the domain of $x$ to some SFA.
 Let us begin with a simple example, assume that we use the SFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
@@
 
-For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)+1}-1}{100-1}$.
+For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)}-1}{100-1}$.
 The constraint uses $\#(v_0)$ to capture the total number of loop traversal.
-Notice that the constraint above contains an exponential component $100^{\#(v_0)}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
+Notice that the constraint above contains an exponential component $\frac{100^{\#(v_0)}}{100-1}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
 
-For a more general form, if we restrict the domain of $x$ to the SFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0^{(0)}\times 10+ v_1^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{v_0^{(0)}-1})\times 100^{v_2^{(0)}}+(v_2^{(0)}\times 10+ v_3^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{v_2^{(0)}-1}) =  (v_0^{(0)}\times 10+ v_1^{(0)}) \times \frac{100^{\#(v_0^{(0)})+1}-1}{100-1}\times 100^{v_2^{(0)}} + (v_2^{(0)}\times 10+ v_3^{(0)}) \times \frac{100^{\#(v_2^{(0)})+1}-1}{100-1}$.
-Observe that the formula has even more exponential components.
+Let us have a look at another example.
+If we restrict the domain of $x$ to the SFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0^{(0)}\times 10+ v_1^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0^{(0)})-1})\times 100^{\#(v_2^{(0)})}+(v_2^{(0)}\times 10+ v_3^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_2^{(0)})-1}) =  (v_0^{(0)}\times 10+ v_1^{(0)}) \times \frac{100^{\#(v_0^{(0)})}-1}{100-1}\times 100^{\#(v_2^{(0)})} + (v_2^{(0)}\times 10+ v_3^{(0)}) \times \frac{100^{\#(v_2^{(0)})}-1}{100-1}$.
+Observe that the formula has two exponential components $\frac{100^{\#(v_0^{(0)})}\times 100^{\#(v_2^{(0)})} }{100-1}$ and $\frac{100^{\#(v_2^{(0)})} }{100-1}$.
 
+It is not difficult to observe that, for the case of an arbitrary SFA of $m$ loops, the formula to define $n$ contains $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
+As said in the introduction, the problem is difficult even for the case that variables are real numbers.
+For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence cannot handle large instances.
+So we do not expect that this constraint can be solved efficiently.
 
-For the particular case with only one integer variable, the satisfiability of integer constraints with a mix of polynomials and exponentials can be decided using the algorithm in~\cite{POPL2019}.
-However, the algorithm involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence cannot handle large instances.
-
+\todo{talk about the design principle}
 In order to handle the under-approximation of string-integer conversion efficiently, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.
@@
 $\begin{array}{ccc}
-	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\wedge \\
-	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\wedge \\
+	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\vee \\
+	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\vee \\
 	& &\ldots\\
-	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\wedge\\
+	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\vee\\
 	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
@@
 
-\section{Evaluation}
- \label{section:evaluation}
-\todo{copy a few tables from our test site to here}
+% \section{Evaluation}
+%  \label{section:evaluation}
+% \todo{copy a few tables from our test site to here}
+\input{evaluation}
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-11-07 draft.tex
add new paper structure

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\todo{Some non-technical text to explain how the approach solves a toy problem}
 For proving UNSAT, our strategy first over-approximates string-number conversion function $n=\its{x}$ as an uninterpreted function with an additional axiom $n\leq 0 \rightarrow \sti{\its{n}}=n$.
@@
 
+\section{Under-approximation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Symbolic Flat Automata} \label{section:sfa}
+\subsection{Symbolic Flat Automata} \label{section:sfa}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
-\section{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}
+\subsection{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Handling String-Integer Conversion} \label{section:s2i}
+\subsection{Handling String-Integer Conversion} \label{section:s2i}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\todo{talk about the design principle}
-In order to handle the under-approximation of string-integer conversion efficiently, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.
+\paragraph{SFA that allows efficient string-integer conversion: } In the previous discussion, we know that it is unlikely to use arbitrary SFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
+The problem is that each loop in the SFA creates an exponential component.
+An immediate idea would be that maybe we can restrict the variable to some specific SFA that allow more efficient constraint solving.
+At the same time, we want to keep some good property, i.e., the search space covers all integers with at most $m$-digits.
 
+Our first attempt is a SFA with no loop, i.e., a straight line structure (e.g., the SFA in Fig~\ref{fig:sfa_its} without the self-loop at $q_0$).
+The corresponding integer constraint does not have exponential components.
+However, it does not ensure the property that all numbers with at most $m$-digits are covered.
+Consider the example $\sti{x}=10 \wedge |x|=5$.
+The number $10$ has only $2$-digits, at the first glance, a straight-line SFA with two transitions, i.e., the SFA \scalebox{0.5}{\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+	\begin{tikzpicture} 
+	\node[state,initial] (q0)  {$q_0$};
+	\node[state] (q1) [right = 1cm of q0] {$q_1$};
+	\node[state,accepting] (q2) [right = 1cm of q1] {$q_2$};
+
+	\draw[->] (q0) edge node [below]{$v_1$} (q1) ;
+	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
+	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$. If we do so, we will conclude that the formula is unsatisfiable under this domain restriction.
+
+However, the formula is satisfiable when $x=``00010"$.
+The point is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
+In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.
 The SFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such SFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
-Notice that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
-For example, the formula $\sti{x}=10 \wedge |x|=5$ is satisfiable when $x=``00010"$.
+Although this SFA still has a loop, but it will not create any exponential component because the loop only represents a sequence of `0' that occurs in the prefix of $x$.
+It will not affect the integer value of $n=\sti{x}$.
 
@@
 In order to handle such cases efficiently, we use an encoding that if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j,m]$, i.e., we shift all the $\epsilon$-transitions to the least significant digits.
+In order to explain this encoding, we first define two macro function:
+
 More specifically, we first define two functions:

### 2019-11-07 draft.tex
dont what I am doing
polish str-int conv. subsection

@@
 	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
-	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$. If we do so, we will conclude that the formula is unsatisfiable under this domain restriction.
+	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$.
+If we do so, we will conclude that the formula is unsatisfiable, because the length of $x$ cannot be $5$  under this domain restriction.
 
 However, the formula is satisfiable when $x=``00010"$.
-The point is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
+Observe that $\sti{``00010"}=10$.
+The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
 In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.
@@
 
-More specifically, we first define two functions:
+$$\begin{array}{rl}
+\mathsf{epsilonAfter(k)}::=& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
+&v_{k+1}=\ldots =v_m = -1\\
+\mathsf{toNumber(k)}::=& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
+\end{array}
+$$
 
-$$\mathsf{epsAfter(k)}::= (0\leq v_0,\ldots, v_k\leq 9) \wedge v_{k+1}=\ldots =v_m = -1$$
-$$\mathsf{toNumber(k)}::= (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})$$
-
+The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$.
+Recall that we use $-1$ to represent $\epsilon$.
+The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
 Then we can specify the relation between $n$ and the character variables as follows:
 $$(n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$ .
 
@@
 % \todo{copy a few tables from our test site to here}
+
+\section{Implementation}
 \input{evaluation}

### 2019-11-07 draft.tex

--- 2019-11-07 draft.tex
@@
 \newcommand{\enc}[1]{[\![#1]\!]}
-\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
+%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
+\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
 \newcommand{\parikhwof}[2]{|#1|_{#2}}
+\newcommand{\semof}[1]{||#1||}
+\newcommand{\decode}{\mathit{decode}}
+\newcommand{\pformulaof}[1]{\Phi_{#1}}
 
@@
 %$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
-$\parikhof w$ that maps every character $a\in\Sigma$ to the number of its occurrences in $w$, i.e., $\parikhof w (a) = |w|_a$. 
+$\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$, i.e., $\parikhof w (\#a) = |w|_a$. 
 The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
@@
 
-We introduce \emph{symbolic flat automata} (SFA) that will be used to define patterns 
+We introduce \emph{parametric flat automata} (SFA) that will be used to define patterns 
 %for the string variable domain restriction. 
@@
 \end{enumerate} 
-%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
-Symbolic automata accept strings over $\cvar$, called \emph{symbolic strings}. 
-Each symbolic string may be interpreted as a string over $\Sigma$, given an assignment of characters to its character variables.  
-%
-Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-
+\lh{TODO: decide whether we want epsilon trans, or perhaps additional constraints saying that a var equals epsilon or a character}
 \begin{figure*}
@@
 
-	\caption{An example of a symbolic flat automaton}
+	\caption{An example of a parametric flat automaton}
 	\label{fig:sfa_def}
@@
 
-\begin{lemma}
-%Distinct words from the language of an SFA must have distinct Parikh images.  
+\begin{lemma}\label{lemma:parikh}
 For an SFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
-%Distict words from the language of an SFA have distinct Parikh images.  
 \end{lemma}
-Indeed, notice that each accepted symbolic string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
+Indeed, notice that each accepted parametric string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
 Since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
@@
 from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
+
+%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
+Symbolic automata accept strings over $\cvar$, called \emph{parametric strings}, but we still use them as representations of languages over $\Sigma$. 
+%
+Namely, string over $\cvar$ are interpreted as strings over $\Sigma$ given an assignment of characters to its character variables.  
+%
+Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a parametric string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+%
+We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V_\Sigma$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an SFA is the semantics of its language.
+
+The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulae and handled by an SMT solver, allowing to circumvent more costly automata algorithms and decision procedures.
+\lh{concretize and justify this better?}
+%
+To be more concrete, every word $w \in \semof{A}$ can be identified by a parametric string $x\in L(A)$ and an interpretation of character varriables $I$ such that $w = I(x)$. 
+Moreover, every parametric string $x\in L(A)$ is uniquelly determined by its Parikh image $\parikhof{x}$. 
+Hence the united assignment $I \cup \parikhof{x}$ encodes $w$. 
+Notice that there might be more united assignments encoding $w$, but different words over $\Sigma$ must have different encodings by Lemma~\ref{lemma:parikh}. 
+We may hence define the decoding function $\decode$ such that $\decode(I\cup \parikhof{x}) = w$. 
+It is well known that $\parikhof{A}$ can be computed in a form of linear arithmetic formula \cite{} $\pformulaof{A}$ such that $\modelsof{\pformulaof A} = \parikhof{A}$.
+
 \todo{add Presburger constraints to allow more expressive power.}
@@
 
-%\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
 \subsection{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}

### 2019-11-07 draft.tex
making mess

@@
 \newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
-\newcommand{\modelof}[1]{[\![#1]\!]}
+\newcommand{\modelsof}[1]{[\![#1]\!]}
 \newcommand{\true}{\mbox{$\mathsf{true}$}}
@@
 An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
-t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelof{\phi_e}=\{I\mid 
+t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
 I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
@@
 %Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
-We define $\modelof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
-We define  $\modelof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.
+We define $\modelsof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
+We define  $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.
 
@@
 For $s\notin [0,9]^+$, $\sti{s}=-1$.
-We define  $\modelof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.
+We define  $\modelsof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.
 
 A \emph{string constraint} $\phi$ is in the form of $\bigwedge_{\pi \in \Pi} \pi$, where $\Pi$ is a set of the above three kinds of constraints.
-We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelof{\pi}$ is not empty.
+We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelsof{\pi}$ is not empty.
 

### 2019-11-07 draft.tex
polish str-int conv. subsection

--- 2019-11-07 draft.tex
@@
 \newcommand{\enc}[1]{[\![#1]\!]}
-%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
-\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
+\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
 \newcommand{\parikhwof}[2]{|#1|_{#2}}
-\newcommand{\semof}[1]{||#1||}
-\newcommand{\decode}{\mathit{decode}}
-\newcommand{\pformulaof}[1]{\Phi_{#1}}
 
@@
 %$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
-$\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$, i.e., $\parikhof w (\#a) = |w|_a$. 
+$\parikhof w$ that maps every character $a\in\Sigma$ to the number of its occurrences in $w$, i.e., $\parikhof w (a) = |w|_a$. 
 The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
@@
 
-We introduce \emph{parametric flat automata} (SFA) that will be used to define patterns 
+We introduce \emph{symbolic flat automata} (SFA) that will be used to define patterns 
 %for the string variable domain restriction. 
@@
 \end{enumerate} 
-\lh{TODO: decide whether we want epsilon trans, or perhaps additional constraints saying that a var equals epsilon or a character}
+%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
+Symbolic automata accept strings over $\cvar$, called \emph{symbolic strings}. 
+Each symbolic string may be interpreted as a string over $\Sigma$, given an assignment of characters to its character variables.  
+%
+Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+
 \begin{figure*}
@@
 
-	\caption{An example of a parametric flat automaton}
+	\caption{An example of a symbolic flat automaton}
 	\label{fig:sfa_def}
@@
 
-\begin{lemma}\label{lemma:parikh}
+\begin{lemma}
+%Distinct words from the language of an SFA must have distinct Parikh images.  
 For an SFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
+%Distict words from the language of an SFA have distinct Parikh images.  
 \end{lemma}
-Indeed, notice that each accepted parametric string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
+Indeed, notice that each accepted symbolic string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
 Since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
@@
 from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
-
-%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
-Symbolic automata accept strings over $\cvar$, called \emph{parametric strings}, but we still use them as representations of languages over $\Sigma$. 
-%
-Namely, string over $\cvar$ are interpreted as strings over $\Sigma$ given an assignment of characters to its character variables.  
-%
-Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a parametric string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-%
-We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V_\Sigma$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an SFA is the semantics of its language.
-
-The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulae and handled by an SMT solver, allowing to circumvent more costly automata algorithms and decision procedures.
-\lh{concretize and justify this better?}
-%
-To be more concrete, every word $w \in \semof{A}$ can be identified by a parametric string $x\in L(A)$ and an interpretation of character varriables $I$ such that $w = I(x)$. 
-Moreover, every parametric string $x\in L(A)$ is uniquelly determined by its Parikh image $\parikhof{x}$. 
-Hence the united assignment $I \cup \parikhof{x}$ encodes $w$. 
-Notice that there might be more united assignments encoding $w$, but different words over $\Sigma$ must have different encodings by Lemma~\ref{lemma:parikh}. 
-We may hence define the decoding function $\decode$ such that $\decode(I\cup \parikhof{x}) = w$. 
-It is well known that $\parikhof{A}$ can be computed in a form of linear arithmetic formula \cite{} $\pformulaof{A}$ such that $\modelsof{\pformulaof A} = \parikhof{A}$.
-
 \todo{add Presburger constraints to allow more expressive power.}
@@
 
+%\section{Handling Equality and Disequality Constraint Symbolically} \label{section:eq}
 \subsection{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}
@@
 
-The length of $x$ can be specified by the following formula.
+\hide{The length of $x$ can be specified by the following formula.
 
@@
 	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
-\end{array}$
+\end{array}$}
 

### 2019-11-07 draft.tex
sketch of the product construction

--- 2019-11-07 draft.tex
@@
 \newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
+\newcommand{\cvars}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
+\newcommand{\pvars}{\mbox{$\mathbb{V}_{\sharp}$}}
 \newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
@@
 \newcommand{\parikhwof}[2]{|#1|_{#2}}
-\newcommand{\semof}[1]{||#1||}
+%\newcommand{\semof}[1]{||#1||}
+\newcommand{\semof}[1]{\modelsof{#1}}
 \newcommand{\decode}{\mathit{decode}}
 \newcommand{\pformulaof}[1]{\Phi_{#1}}
+\newcommand{\pim}{\alpha}
+\newcommand{\syncof}[2]{A \Cap B}
+\newcommand{\nat}{\mathbb{N}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Symbolic Flat Automata} \label{section:sfa}
+\subsection{Parametric Flat Automata} \label{section:sfa}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\sym}[2]{v_{#1}^{#2}}
+\todo{add Presburger constraints to allow more expressive power.}
 %We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
@@
 
-We introduce \emph{parametric flat automata} (SFA) that will be used to define patterns 
+We introduce \emph{parametric flat automata} (PFA) that will be used to define patterns 
 %for the string variable domain restriction. 
 used by the under-approximation module to restrict the domain of string variables. 
-Namely, an SFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
+Namely, an PFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
 and satisfying the following structural constraints:
@@
 
-%A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a SFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
+%A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a PFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
 We write $I(S)$ to denote the instance of $S$ wrt.
@@
 The language of $S$ is defined as $L(S)= \cup\{L(D) \mid D \mbox{ is an instance of } S\}$.
-Notice that $L(S)$ is regular because every SFA has only finitely many instance and the finite union of regular languages are also regular.
-
-The purpose of the structural restrictions of SFA is to ensure that the words of $L(A)$ are uniquely determined by their Parikh images, as formalised by the following lemma.
-
-\begin{lemma}\label{lemma:parikh}
-For an SFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
-\end{lemma}
-Indeed, notice that each accepted parametric string $x$ is determined by the numbers of repetitions of individual cycles in the accepting run of $A$ over $x$.
-Since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
-%
-The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$.
-
-For example, in the example of Figure~\ref{fig:sfa_def}, 
-from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
+Notice that $L(S)$ is regular because every PFA has only finitely many instance and the finite union of regular languages are also regular.
 
 %Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
-Symbolic automata accept strings over $\cvar$, called \emph{parametric strings}, but we still use them as representations of languages over $\Sigma$. 
+Parametric automata accept strings over $\cvar$, called \emph{parametric strings}, but we still use them as representations of languages over $\Sigma$. 
 %
@@
 %
-We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V_\Sigma$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an SFA is the semantics of its language.
+We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V_\Sigma$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an PFA is the semantics of its language.
 
@@
 %
-To be more concrete, every word $w \in \semof{A}$ can be identified by a parametric string $x\in L(A)$ and an interpretation of character varriables $I$ such that $w = I(x)$. 
-Moreover, every parametric string $x\in L(A)$ is uniquelly determined by its Parikh image $\parikhof{x}$. 
-Hence the united assignment $I \cup \parikhof{x}$ encodes $w$. 
-Notice that there might be more united assignments encoding $w$, but different words over $\Sigma$ must have different encodings by Lemma~\ref{lemma:parikh}. 
-We may hence define the decoding function $\decode$ such that $\decode(I\cup \parikhof{x}) = w$. 
-It is well known that $\parikhof{A}$ can be computed in a form of linear arithmetic formula \cite{} $\pformulaof{A}$ such that $\modelsof{\pformulaof A} = \parikhof{A}$.
+Achieving this was the purpose of introducing the structural constraints of PFA. 
+Their implication central for our method is that every parametric string $x\in L(A)$ is uniquelly determined by its Parikh image $\parikhof{x}$, as formalised by the following lemma.
 
-\todo{add Presburger constraints to allow more expressive power.}
+\begin{lemma}\label{lemma:parikh}
+For an PFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
+\end{lemma}
+%
+Indeed, since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
+%
+The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. \lh{say precisely how?}
+%
+For example, in the example of Figure~\ref{fig:sfa_def}, 
+from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
+We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode$ such that $\decode(\parikhof x) = x$.
+It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\pformulaof{A}$ such that $\modelsof{\pformulaof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
+\begin{lemma}\label{lemma:decx}
+For a PFA $A$, $L(A) = \{\decode(\pim) \mid \pim\in\semof{\pformulaof A}\}$.
+\end{lemma}
 
-%For such kind of automata, the number of occurrence of each symbol in $\cvar$ uniquely characterize an accepting symbolic string.
-For example, in the example of Figure~\ref{fig:sfa_def}, if the string $v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ is accepted, then all other strings $w$ with $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and also $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$ are not accepted.
-Moreover, from $|w|_{v_0}=|w|_{v_1}=\ldots=|w|_{v_{m-1}}=1$ and $|w|_{v^0_1}=|w|_{v^1_1}=|w|_{v^2_1}=2$, we can derive $w=v_0(v^0_1v^1_1v^2_1)^2v_1v_{m-1}$ by exploring the automata structure.
-\todo{add Presburger constraints to allow more expressive power.}
+Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode(\parikhof x)$,
+we may say that the united assignment $I \cup \parikhof x$ encodes $w$.
+Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments, and hence we may extend the decoding function $\decode$ to united assignments so that $\decode(I \cup x) = w$.
+Encodings of strings in $\semof{A}$ are encodings of strings of $L(A)$ paired with arbitrary interpretations of $\cvar$, 
+hence $\semof A$ is characterised by $\parikhof A$ interpreted over variables $\cvar\cup\pvars$: 
+%\begin{lemma}\ref{lemma:decw}
+%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\pformulaof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
+%\end{lemma}
+\begin{lemma}
+For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid I\cup\pim\in\semof{\pformulaof A}_{\cvar\cup\pvars}\}$.
+\end{lemma}
 
-\lh{so far not sure about how and where to present this:}
+\paragraph{Synchronisation of PFA}
+The following construction of the so called synchronisation formula of two PFA $A$ and $B$ is a crucial component of bulding overapproximations of string constraints. 
+Synchronisation formula is a formula $\syncof A B$ over $\pvars\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof B$.
+Besides the intersection, it contains a more precise information about the synchronisation of $A$ and $B$,
+namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof B$ such that 
+$\decode(I\cup \pim) = \decode(I'\cup \pim')$ which constitute the intersection.
+
+Assume that $A$ and $B$ are over disjoint sets of variables. 
+We build so called asynchronous product machine of $A$ and $B$ and then extract the formula from its Parikh image.
+%
+The product machine uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
+If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
+
+More precisely, the product machine is a tuple $M = (Q\times P, T^2, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $T^2$ is the minimal set satisfying the following.
+
+\begin{itemize}
+\item If $(q_1,v,q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v,\epsilon),(q_2,p))\in T^2$.
+\item If $(p_1,v,p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v),(q,p_2))\in T^2$.
+\item If $(q_1,v,q_2) \in T$ and $(p_1,v',p_2) \in T'$, then we have $((q_1,p_1),(v,v'),(q_2,p_2))\in T^2$.
+\end{itemize}	
+The first two cases correspond to the situation when the character variable $v$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
+%
+We compute a Presburger formula $\pformulaof M$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone \times \cvartwo\}$ of the product machine. 
+%We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively. 
+The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product machine.
+\begin{enumerate}
+	\item for all $v \in \cvarone$, $\#(v) = \sum_{v' \in {\cvartwo \cup \{\epsilon\}}} \#{(v,v')}$   
+	\item for all $v \in \cvartwo$, $\#(v) = \sum_{v' \in {\cvarone \cup \{\epsilon\}}} \#{(v',v)}$ 
+\end{enumerate}
+
+Then we add the following linear constraints to enforce  condition 1.
+and 2.
+required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
+\begin{enumerate}
+	\item for all $v\in \cvarone$ and $v'\in \cvartwo$, $\#{(v,v')}>0 \rightarrow (v=v')$, 
+	\item for all $v\in \cvarone$, $\#{(v,\epsilon)}>0 \rightarrow (v=\epsilon)$, and
+	Mitem for all $v\in \cvartwo$,$\#{(\epsilon,v)}>0 \rightarrow (v=\epsilon)$.
+\end{enumerate}
+
+The correctness of this construction is expressed by the following lemma
+\begin{lemma}
+For $\pim:\pvars\rightarrow \nat$, $\pim':\pvars\rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
+we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof \Psi$ if and only if $\decode(I\cup\pim) = \decode(I'\cup\pim')$.
+\end{lemma}
+We actually have even something stronger, namely, that, $\Psi$ has all possible allignments. How do I say this ... or do I have to say this?
+
 \begin{lemma}
@@
 
-Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some SFA with disjoint alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.
-We rename the variables on the transitions of SFA's for different occurrences of the same variable in one equality constraint.
+Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some PFA with disjoint alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.
+We rename the variables on the transitions of PFA's for different occurrences of the same variable in one equality constraint.
 Later we will use some arithmetic constraints to enforce that all occurrences of the variants of the same variable will be assigned the same value.
@@
 
-For the constraint $xy = yx$, we first restrict the domains of $x$ and $y$ to the SFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-In the construction of the SFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the SFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$.
+For the constraint $xy = yx$, we first restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$.
 
@@
 \begin{enumerate}
-	\item for all $v_i^{(j)}\in \cvarone$ and $v_{i'}^{(j')}\in \cvartwo$, $\#{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$, 
+	\item for all $v_i^{(j)}\in \cvarone$ and $v_{i'}^{(j')}\in \cvartwo$, $\#{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$,\lh{typo?} 
 	\item for all $v_i^{(j)}\in \cvarone$, $\#{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and

### 2019-11-08 draft.tex
before removoving epsilons from product constr

@@
 
+\newcommand{\nat}{\mathbb{N}}
 \newcommand{\todo}[1]{{\color{blue}TODO: #1}}
@@
 \newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
-\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
-\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
+%\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
+%\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
+\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
+\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
 \newcommand{\modelsof}[1]{[\![#1]\!]}
@@
 \newcommand{\pim}{\alpha}
-\newcommand{\syncof}[2]{A \Cap B}
-\newcommand{\nat}{\mathbb{N}}
+\newcommand{\syncop}{\Cap}
+\newcommand{\syncof}[2]{A \syncop B}
+\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
+\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
+\newcommand{\syncT}{T_\syncop}
 
@@
 Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode(\parikhof x)$,
-we may say that the united assignment $I \cup \parikhof x$ encodes $w$.
-Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments, and hence we may extend the decoding function $\decode$ to united assignments so that $\decode(I \cup x) = w$.
+we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encode $w$.
+Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode$ to united assignments so that $\decode(I \cup x) = w$.
 Encodings of strings in $\semof{A}$ are encodings of strings of $L(A)$ paired with arbitrary interpretations of $\cvar$, 
-hence $\semof A$ is characterised by $\parikhof A$ interpreted over variables $\cvar\cup\pvars$: 
+hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvars$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them):
 %\begin{lemma}\ref{lemma:decw}
@@
 The following construction of the so called synchronisation formula of two PFA $A$ and $B$ is a crucial component of bulding overapproximations of string constraints. 
-Synchronisation formula is a formula $\syncof A B$ over $\pvars\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof B$.
+Synchronisation formula is a formula $\syncfof A B$ over $\pvars\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof B$.
 Besides the intersection, it contains a more precise information about the synchronisation of $A$ and $B$,
@@
 
-Assume that $A$ and $B$ are over disjoint sets of variables. 
-We build so called asynchronous product machine of $A$ and $B$ and then extract the formula from its Parikh image.
+Assume that $A = (Q,T,\cvarone,q_i,q_f)$ and $B = (P,T',\cvartwo,p_i,p_f)$ are two SFA over disjoint sets of variables, $\cvarone \cap \cvartwo = \emptyset$. 
+We build so called asynchronous product automaton $\syncof A B$ of $A$ and $B$ and then extract the formula $\syncfof A B$ from its Parikh image.
 %
-The product machine uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
-If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
+The product automaton uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
+If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
 
-More precisely, the product machine is a tuple $M = (Q\times P, T^2, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $T^2$ is the minimal set satisfying the following.
+More precisely, the product automaton is a tuple $\syncof A B = (Q\times P, \syncT, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $\syncT$ is the minimal set satisfying the following.
 
 \begin{itemize}
-\item If $(q_1,v,q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v,\epsilon),(q_2,p))\in T^2$.
-\item If $(p_1,v,p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v),(q,p_2))\in T^2$.
-\item If $(q_1,v,q_2) \in T$ and $(p_1,v',p_2) \in T'$, then we have $((q_1,p_1),(v,v'),(q_2,p_2))\in T^2$.
+\item If $(q_1,v,q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v,\epsilon),(q_2,p))\in \syncT$.
+\item If $(p_1,v,p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v),(q,p_2))\in \syncT$.
+\item If $(q_1,v,q_2) \in T$ and $(p_1,v',p_2) \in T'$, then we have $((q_1,p_1),(v,v'),(q_2,p_2))\in \syncT$.
 \end{itemize}	
@@
 %
-We compute a Presburger formula $\pformulaof M$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone \times \cvartwo\}$ of the product machine. 
+We compute a Presburger formula $\pformulaof {\syncof A B}$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone \times \cvartwo\}$ of the product automaton. 
 %We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively. 
-The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product machine.
+The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product automaton.
 \begin{enumerate}
@@
 For $\pim:\pvars\rightarrow \nat$, $\pim':\pvars\rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
-we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof \Psi$ if and only if $\decode(I\cup\pim) = \decode(I'\cup\pim')$.
+we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof \syncofof A B$ if and only if $\decode(I\cup\pim) = \decode(I'\cup\pim')$.
 \end{lemma}
-We actually have even something stronger, namely, that, $\Psi$ has all possible allignments. How do I say this ... or do I have to say this?
+We actually have even something stronger, namely, that, $\syncofof A B$ has all possible allignments. How do I say this ... or do I have to say this?
 
@@
 
-Such product automaton uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
-If a transition $((q_1,p_1), (v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $v_i$ and $v_{i'}$ (and so all of their indexed variants) should be assigned the same value and this value leads $S_n$ from state $q_1$ to state $q_2$ and $S_m$ from $p_1$ to $p_2$.
+Such product automaton uses $Q\times P$ as the set of states and 
+§$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
+If a transition $((q_1,p_1), (v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $v_i$ and $v_{i'}$ (and so all of their indexed variants) should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
 
-More precisely, the product automaton is a tuple $(Q\times P, T^2, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $T^2$ is the minimal set satisfying the following.
+More precisely, the product automaton is a tuple $\syncof A B = (Q\times P, \syncT, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $\syncT$ is the minimal set satisfying the following.
 
 \begin{itemize}
-\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in T^2$.
-\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in T^2$.
-\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in T^2$.
+\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in \syncT$.
+\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in \syncT$.
+\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in \syncT$.
 \end{itemize}	

### 2019-11-08 evaluation.tex
evaluation: revised tables.

@@
 {\bf Tabales}:
-Table~\ref{table:pyex} shows the comparison on PyEx benchmark. The total amount of cases in PyEx (PyEx\_unsat, PyEx\_sat, PyEx\_todo) is 25421.
+Table~\ref{table:base_benchmark} shows the comparison on several string benchmarks that are used by other tools. The total amount of cases in PyEx is 25421.
 
-\begin{table}[]
-\caption{Results of z3-Trau, cvc4, and z3 on PyEx benchmark}
-\begin{tabular}{|r|r|r|r|r|r|r|}
+\begin{table*}[]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
+\begin{tabular}{l | r r r | r r r | r r r | r r r}
 \hline
-Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
-z3-Trau		& 19655 & 3851 & 0 & 1915 & 0 & 0 \\ 
-cvc4		& 19763 & 3834 & 0 & 0 & 0 & 1824 \\ 
-z3seq		& 16578 & 3832 & 0 & 5011 & 0 & 0 \\ 
-z3str3		& 3023 & 3835 & 9 & 16717 & 1125 & 712 \\ \hline
+\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
+			& sat & unsat & $\times$ & sat & unsat & $\times$ & sat & unsat & $\times$ & sat & unsat & $\times$ \\ \hline
+PyEx		& 19655 & 3851 & 1915 & 19763 & 3834 & 1824 & 16578 & 3832 & 5011 & 3023 & 3835 & 18563 \\ 
+APLAS		&   128 &  287 &  185 & 205 & 221 & 174 & 13 & 100 & 487 & 36 & 112 &  452 \\ 
+LeetCode	&  &  &  &  &  &  &  &  &  &  &  &  \\ 
+StringFuzz	&  &  &  &  &  &  &  &  &  &  &  &  \\ 
+cvc4\textsubscript{pred}	&  &  &  &  &  &  &  &  &  &  &  &  \\ 
+cvc4\textsubscript{term}	&  &  &  &  &  &  &  &  &  &  &  &  \\ \hline
 \end{tabular}
-\label{table:pyex}
-\end{table}
+\label{table:base_benchmark}
+\end{table*}
 
-Table~\ref{table:full_str_int} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
+Table~\ref{table:str_int_benchmark} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
+\begin{table*}[]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
+\begin{tabular}{l | r r r | r r r | r r r | r r r}
+\hline
+\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
+			& sat & unsat & $\times$ & sat & unsat & $\times$ & sat & unsat & $\times$ & sat & unsat & $\times$ \\ \hline
+full\_str\_int		& 3289 & 17089 & 1195 & 2185 & 16377 & 3011 & 2716 & 16831 & 2026 & 422 & 16034 & 5117 \\ 
+filtered\_str\_int	& 3281 & 2912 & 1203 & 2210 & 2211 & 2975 & 2729 & 2655 & 2012 & 424 & 1944 & 5028 \\ \hline
+\end{tabular}
+\label{table:str_int_benchmark}
+\end{table*}
+
+\hide{
 \begin{table}[]
@@
 \end{table}
+}

### 2019-11-08 evaluation.tex
evaluations: tables filled.

--- 2019-11-06 evaluation.tex
@@
 {\bf Tabales}:
-Table~\ref{table:pyex} shows the comparison on PyEx benchmark. The total amount of cases in PyEx (PyEx\_unsat, PyEx\_sat, PyEx\_todo) is 25421.
+Table~\ref{table:base_benchmark} shows the comparison on several string benchmarks that are used by other tools. The total amount of cases in PyEx is 25421.
 
-\begin{table}[]
-\caption{Results of z3-Trau, cvc4, and z3 on PyEx benchmark}
-\begin{tabular}{|r|r|r|r|r|r|r|}
+\begin{table*}[]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
+\begin{tabular}{l | r r r | r r r | r r r | r r r}
 \hline
-Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
-z3-Trau		& 19655 & 3851 & 0 & 1915 & 0 & 0 \\ 
-cvc4		& 19763 & 3834 & 0 & 0 & 0 & 1824 \\ 
-z3seq		& 16578 & 3832 & 0 & 5011 & 0 & 0 \\ 
-z3str3		& 3023 & 3835 & 9 & 16717 & 1125 & 712 \\ \hline
+\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
+			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
+PyEx		& 19655 & 3851 & 1915/0 & 19763 & 3834 & 0/1824 & 16578 & 3832 & 5011/0 & 3023 & 3835 & 16717/1846 \\ 
+APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 36 & 112 & 105/347 \\ 
+LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 676 & 1780 &  70/140 \\ 
+StringFuzz	& 504 & 295 & 264/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
+cvc4\textsubscript{pred}	& 16 & 184 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
+cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 2021 & 19/0 & 16 & 958 & 53/18 \\ \hline
 \end{tabular}
-\label{table:pyex}
-\end{table}
+\label{table:base_benchmark}
+\end{table*}
 
-Table~\ref{table:full_str_int} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
+Table~\ref{table:str_int_benchmark} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
+\begin{table*}[]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
+\begin{tabular}{l | r r r | r r r | r r r | r r r}
+\hline
+\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
+			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
+full\_str\_int		& 3289 & 17089 & 1195/0 & 2185 & 16377 & 3011/0 & 2716 & 16831 & 2026/0 & 422 & 16034 & 4131/986 \\ 
+filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
+\end{tabular}
+\label{table:str_int_benchmark}
+\end{table*}
+
+\hide{
 \begin{table}[]

### 2019-11-08 draft.tex
evaluation: revised tables.
working on product

@@
 \newcommand{\pvars}{\mbox{$\mathbb{V}_{\sharp}$}}
-\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
-%\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
-%\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
-\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
-\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
+%\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
+%\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
+%\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
+\newcommand{\cvarone}{V}
+\newcommand{\cvartwo}{V'}
+\newcommand{\cvar}{V}
+\newcommand{\pvar}{V_\#}
+\newcommand{\pvarone}{V_\#}
+\newcommand{\pvartwo}{V'_\#}
 \newcommand{\modelsof}[1]{[\![#1]\!]}
@@
 \newcommand{\semof}[1]{\modelsof{#1}}
-\newcommand{\decode}{\mathit{decode}}
-\newcommand{\pformulaof}[1]{\Phi_{#1}}
+\newcommand{\decode}[1]{\mathit{decode_{#1}}}
+\newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
 \newcommand{\pim}{\alpha}
 \newcommand{\syncop}{\Cap}
-\newcommand{\syncof}[2]{A \syncop B}
-\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
+\newcommand{\syncof}[2]{#1 \syncop #2}
 \newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
@@
 
-A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}.
+A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}.
 %The semantics of finite automaton is defined in the standard manner. 
+A run of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_i)$
 We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
@@
 used by the under-approximation module to restrict the domain of string variables. 
-Namely, an PFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
+Namely, an PFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over an alphabet $\cvar$ of \emph{character variables}, 
 and satisfying the following structural constraints:
@@
 %(where $l_i = 0$ means that there is no cycle on $q_i$)
-	\item Each variable in $\cvar$ appears on at most one transition (but $\epsilon$ transition can appear multiple times). 
+	\item Each variable in $\cvar$ appears on at most one transition.% (but $\epsilon$ transition can appear multiple times). 
 \end{enumerate} 
@@
 from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
-We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode$ such that $\decode(\parikhof x) = x$.
-It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\pformulaof{A}$ such that $\modelsof{\pformulaof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
+We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
+It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
 \begin{lemma}\label{lemma:decx}
-For a PFA $A$, $L(A) = \{\decode(\pim) \mid \pim\in\semof{\pformulaof A}\}$.
+For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
 \end{lemma}
 
-Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode(\parikhof x)$,
-we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encode $w$.
-Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode$ to united assignments so that $\decode(I \cup x) = w$.
-Encodings of strings in $\semof{A}$ are encodings of strings of $L(A)$ paired with arbitrary interpretations of $\cvar$, 
-hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvars$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them):
+Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$,
+we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encodes $w$.
+Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
+Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, 
+hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them), we may say that
 %\begin{lemma}\ref{lemma:decw}
-%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\pformulaof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
+%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\parikhfof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
 %\end{lemma}
+ $$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$$
+where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}.
+
+\paragraph{Synchronisation of PFA}
+The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
+Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
+Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$,
+namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
+$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.
+
+Assume that $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ are two SFA over disjoint sets of variables, $\cvarone \cap \cvartwo = \emptyset$. 
+We build so called asynchronous product automaton $\syncof A {A'}$ of $A$ and ${A'}$ and then extract the formula $\syncfof A {A'}$ from its Parikh image.
+%
+Such product automaton uses $Q\times Q'$ as the set of states and 
+%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
+$\cvarone_\epsilon\times\cvartwo_\epsilon$
+as the alphabet. 
+%
+Every accepting run of $\syncof A {A'}$ \lh{define run as a sequence of transitions etc} corresponds to an accepting run of $A$ and an accepting run of ${A'}$, and the word accepted by the run of $\syncof A {A'}$ implies a set of constraints on $\pvarone\cup\pvartwo\cup\cvarone\cup\cvartwo$ under which the word accepted by $A$ has the same semantics as the word accepted by ${A'}$.
+%
+Particularly, if a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and ${A'}$ from $q_1'$ to $q_2'$.
+%
+If a transition $((q_1,q_1'), (v,\epsilon),(q_2,q_1'))$ is taken, then it means that the character variable $v$ should be assigned $\epsilon$, $A$ may transition under $v$ to $q_1$ and ${A'}$ stays in the same state, as a response to $A$s reading epsilon may as well be taking no action.
+Symmetrically, ${A'}$ might read a variable $v$ assigned $\epsilon$ and $A$ may stay.
+
+Formally, the product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'))$, where the transition relation $\syncT$ is the minimal set satisfying the following:
+%
+\begin{itemize}
+\item If $(q_1,v,q_2) \in T$ and $(q_1',v',q_2') \in T'$, then we have $((q_1,q_1'),(v,v'),(q_2,q_2'))\in \syncT$.
+\item If $(q_1,v,q_2) \in T$, then for all states $q'\in Q'$, we have $((q_1,q'),(v,\epsilon),(q_2,q'))\in \syncT$.
+\item If $(q_1',v',q_2') \in T'$, then for all states $q\in Q$, we have $((q,q_1'),(\epsilon,v'),(q,q_2'))\in \syncT$.
+\end{itemize}	
+%
+Next, we define the set of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
+We start with the Parikh formula $\parikhfof {\syncof A {A'}}$ of $\syncof A {A'}$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone_\epsilon \times \cvartwo_\epsilon\}$ of the product automaton and conjoin it with the following restricting constraints.
+%We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
+
+The first restricting constraint establishes the relation of between the Parikh image of a word accepted by $\syncof A {A'}$ and the Parikh images of the corresponding parametric strings accepted by $A$ and ${A'}$:
+$$ \Psi_{\#} = 
+\left(\bigwedge_{v\in\cvarone}\#v = \sum_{x' \in \cvartwo_\epsilon} \#{(v,x')}\right)
+\land
+\left(\bigwedge_{v'\in\cvartwo} \#v' = \sum_{x \in \cvarone_\epsilon} \#{(x,v')}\right)
+$$
+Notice that $x,x'$ are either variables or $\epsilon$.
+%\begin{enumerate}
+%	\item for all $v \in \cvarone$, $\#(v) = \sum_{v' \in \cvartwo} \#{(v,v')}$   
+%	\item for all $v \in \cvartwo$, $\#(v) = \sum_{v' \in \cvarone} \#{(v',v)}$ 
+%\end{enumerate}
+
+Then we add the following linear constraints to enforce that the decodings of the models are indeed the same, 
+% condition 1.
+and 2.
+required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
+$$ \Psi_= =
+\bigwedge_{x\in\cvarone_\epsilon,x'\in\cvartwo_\epsilon} \#(x,x')>0 \rightarrow (x=x')
+$$
+%\begin{enumerate}
+%	\item for all $v\in \cvarone$ and $v'\in \cvartwo$, $\#{(v,v')}>0 \rightarrow (v=v')$, 
+%	\item for all $v\in \cvarone$, $\#{(v,\epsilon)}>0 \rightarrow (v=\epsilon)$, and
+%	\item for all $v\in \cvartwo$,$\#{(\epsilon,v')}>0 \rightarrow (v'=\epsilon)$.
+%\end{enumerate}
+
+The synchronisation formula is the conjunction 
+$$
+\syncfof A {A'} = \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
+$$
+The correctness of this construction is expressed by the following lemma
+%\begin{lemma}
+%For $\pim:\pvarone\rightarrow \nat$, $\pim':\pvartwo \rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
+%we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof {\syncfof A {A'}}$ if and only if $\decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')$.
+%\end{lemma}
+
 \begin{lemma}
-For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid I\cup\pim\in\semof{\pformulaof A}_{\cvar\cup\pvars}\}$.
+ $\semof {\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
 \end{lemma}
 
-\paragraph{Synchronisation of PFA}
-The following construction of the so called synchronisation formula of two PFA $A$ and $B$ is a crucial component of bulding overapproximations of string constraints. 
-Synchronisation formula is a formula $\syncfof A B$ over $\pvars\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof B$.
-Besides the intersection, it contains a more precise information about the synchronisation of $A$ and $B$,
-namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof B$ such that 
-$\decode(I\cup \pim) = \decode(I'\cup \pim')$ which constitute the intersection.
-
-Assume that $A = (Q,T,\cvarone,q_i,q_f)$ and $B = (P,T',\cvartwo,p_i,p_f)$ are two SFA over disjoint sets of variables, $\cvarone \cap \cvartwo = \emptyset$. 
-We build so called asynchronous product automaton $\syncof A B$ of $A$ and $B$ and then extract the formula $\syncfof A B$ from its Parikh image.
-%
-The product automaton uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
-If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
-
-More precisely, the product automaton is a tuple $\syncof A B = (Q\times P, \syncT, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $\syncT$ is the minimal set satisfying the following.
-
-\begin{itemize}
-\item If $(q_1,v,q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v,\epsilon),(q_2,p))\in \syncT$.
-\item If $(p_1,v,p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v),(q,p_2))\in \syncT$.
-\item If $(q_1,v,q_2) \in T$ and $(p_1,v',p_2) \in T'$, then we have $((q_1,p_1),(v,v'),(q_2,p_2))\in \syncT$.
-\end{itemize}	
-The first two cases correspond to the situation when the character variable $v$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
-%
-We compute a Presburger formula $\pformulaof {\syncof A B}$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone \times \cvartwo\}$ of the product automaton. 
-%We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively. 
-The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product automaton.
-\begin{enumerate}
-	\item for all $v \in \cvarone$, $\#(v) = \sum_{v' \in {\cvartwo \cup \{\epsilon\}}} \#{(v,v')}$   
-	\item for all $v \in \cvartwo$, $\#(v) = \sum_{v' \in {\cvarone \cup \{\epsilon\}}} \#{(v',v)}$ 
-\end{enumerate}
-
-Then we add the following linear constraints to enforce  condition 1.
-and 2.
-required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
-\begin{enumerate}
-	\item for all $v\in \cvarone$ and $v'\in \cvartwo$, $\#{(v,v')}>0 \rightarrow (v=v')$, 
-	\item for all $v\in \cvarone$, $\#{(v,\epsilon)}>0 \rightarrow (v=\epsilon)$, and
-	Mitem for all $v\in \cvartwo$,$\#{(\epsilon,v)}>0 \rightarrow (v=\epsilon)$.
-\end{enumerate}
-
-The correctness of this construction is expressed by the following lemma
-\begin{lemma}
-For $\pim:\pvars\rightarrow \nat$, $\pim':\pvars\rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
-we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof \syncofof A B$ if and only if $\decode(I\cup\pim) = \decode(I'\cup\pim')$.
-\end{lemma}
-We actually have even something stronger, namely, that, $\syncofof A B$ has all possible allignments. How do I say this ... or do I have to say this?
+We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?
 
@@
 Such product automaton uses $Q\times P$ as the set of states and 
-§$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet.
-If a transition $((q_1,p_1), (v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $v_i$ and $v_{i'}$ (and so all of their indexed variants) should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
+%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
+$\cvarone\times\cvartwo$
+as the alphabet.
+If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
 

### 2019-11-08 draft.tex
def of runs and accepting of autoamta

@@
 \usepackage{listings}
+\usepackage{multirow}
 \synctex=1
@@
 %The semantics of finite automaton is defined in the standard manner. 
-A run of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_i)$
-We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
-\lh{If we later start technical talking about tings like runs then we should include this definition.}
+A \emph{run} of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$.
+The run  is \emph{accepting} if $q_0 = q_i$ and $q_i = q_f$ and $w$ then is \emph{accepted}.
+The \emph{language} of $A$ is the set $L(A)$ of all accepted words.
 

### 2019-11-08 draft.tex
a little thing

@@
 
-A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}.
+A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_i$ is the \emph{initial state}, and $q_f$ is the \emph{final state}.
 %The semantics of finite automaton is defined in the standard manner. 

### 2019-11-08 draft.tex
P(A) defined

@@
 %
-For example, in the example of Figure~\ref{fig:sfa_def}, 
+For example, in the automaton of Figure~\ref{fig:sfa_def}, 
 from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
 We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
-It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
+It is well known that the Parikh image of the language of $A$ can be efficiently computed in the form of linear arithmetic formula.
+We will use $\parikhof{A}$ as a shorthand for $\parikhof{L(A)}$.
+
+\begin{lemma}[\cite{PeterParikh}]
+$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
+\end{lemma}
+
 \begin{lemma}\label{lemma:decx}
@@
 Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, 
-hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them), we may say that
+hence $\semof A$ is characterised by models of $\parikhof {A}$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof {A}$ does not constraint them), we may say that
 %\begin{lemma}\ref{lemma:decw}
@@
 Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$,
-namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
+namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {L(A')}$ such that 
 $\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.

### 2019-11-08 draft.tex
parikh of FA to prelims
add a comment

@@
 \newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
+\newcommand{\yfc}[1]{{\color{blue}YFC: #1}}
+\newcommand{\petr}[1]{{\color{pink}Petr: #1}}
 \newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
@@
 
+It is well known that the Parikh image of the language of $A$ can be efficiently computed in the form of linear arithmetic formula.
+We will use $\parikhof{A}$ as a shorthand for $\parikhof{L(A)}$.
+
+\begin{lemma}[\cite{PeterParikh}]
+$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
+\end{lemma}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
-It is well known that the Parikh image of the language of $A$ can be efficiently computed in the form of linear arithmetic formula.
-We will use $\parikhof{A}$ as a shorthand for $\parikhof{L(A)}$.
-
-\begin{lemma}[\cite{PeterParikh}]
-$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
-\end{lemma}
 
@@
  $$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$$
-where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}.
+where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}\yfc{I totally agree}.
 

### 2019-11-08 draft.tex
don't know

--- 2019-11-08 draft.tex
@@
 Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$,
-namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {L(A')}$ such that 
+namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
 $\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.
@@
 The synchronisation formula is the conjunction 
-$$
+$$\label{lemma:synccorrect}
 \syncfof A {A'} = \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
 $$
-The correctness of this construction is expressed by the following lemma
+The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. Informally,
+the
+
+\begin{lemma}
+ $\semof {\exists .\,\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
+\end{lemma}
+
+%We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?
 %\begin{lemma}
@@
 
-\begin{lemma}
- $\semof {\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
-\end{lemma}
-
-We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?
+\lh{TODO: put this somewhere and explain}
 

### 2019-11-08 draft.tex
add a comment

--- 2019-11-08 draft.tex
@@
 \paragraph{Synchronisation of PFA}
-The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
+The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations \yfc{under-approximation} of string constraints. 
 Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.

### 2019-11-08 draft.tex
add an introduction paragraph for underapproximation

@@
 t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
-I(t_1)=I(t_2)\}$. A \emph{disequality constraint} is of the form $t_1 \neq 
+I(t_1)=I(t_2)\}$. A \emph{disequality constraint} $\phi_d$ is of the form $t_1 \neq 
 t_2$ and is interpreted analogously.
@@
 
+A \emph{membership constraint} $\phi_m$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
+The \emph{model} of $\phi_m$ is the set of interpretations $\modelsof{\phi_m}=\{I\mid
+I(x) \in L(A) \}$.
+
 The \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
@@
 
-A \emph{string constraint} $\phi$ is in the form of $\bigwedge_{\pi \in \Pi} \pi$, where $\Pi$ is a set of the above three kinds of constraints.
-We say that $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \Pi} \modelsof{\pi}$ is not empty.
+A \emph{string constraint} is a constraint of the above form. We say that a set of string constraint $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \phi} \modelsof{\pi}$ is not empty.
 
@@
 \section{Under-approximation}
+In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_s$ to a set of equisatisfiable linear integer constraints $\phi_I$ in polynomial-time.
+We first pick a PFA for each variable in $\vars$ and then construct the set of linear integer constraints in a stepwise manner.
+In each step, we take a string constraint from $\phi_s$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints.
+The procedure for equality, disequality, and membership constraints is in Section~\ref{section:eq} and the one for string/integer conversion is in Section~\ref{section:s2i}.
+
+\yfc{say handling membership constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
 

### 2019-11-08 draft.tex
under

--- 2019-11-08 draft.tex
@@
 \newcommand{\cvar}{V}
-\newcommand{\pvar}{V_\#}
-\newcommand{\pvarone}{V_\#}
-\newcommand{\pvartwo}{V'_\#}
 \newcommand{\modelsof}[1]{[\![#1]\!]}
@@
 \newcommand{\syncT}{T_\syncop}
+\newcommand{\pvarsof}[1]{\#(#1)}
+\newcommand{\pvar}{\pvarsof V}
+\newcommand{\pvarone}{\pvarsof V}
+\newcommand{\pvartwo}{\pvarsof {V'}}
 
@@
 We use $|w|$ to denote the length of $w$ and $|w|_a$ to denote the number of occurrences of the character $a\in \Sigma$ in $w$.
-The \emph{Parikh image} of $w$ is the assignment 
-%$\parikh(w) = \{a_1 \mapsto |w|_{a_1},\ldots, a_n \mapsto |w|_{a_n}\}$ that maps every symbol in $w$ to the number of its occurences in $w$. 
-$\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$, i.e., $\parikhof w (\#a) = |w|_a$. 
-The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
 
@@
 
-It is well known that the Parikh image of the language of $A$ can be efficiently computed in the form of linear arithmetic formula.
-We will use $\parikhof{A}$ as a shorthand for $\parikhof{L(A)}$.
+The \emph{Parikh image} of a wore $w\in \Sigma^*$ is the assignment 
+$\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$.
+Formally, let $\pvarsof S$ denote the set of Parikh variables $\{\#s \mid s\in S\}$ obtained from a set $S$. 
+The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$. 
+The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$ and the Parikh image of an FA $A$ is Parikh image of its language, $\parikhof{A} = \parikhof{L(A)}$.
+%
+It is well known that $\parikhof A$ can be efficiently computed in the form of linear interger arithmetic formula:
 
-\begin{lemma}[\cite{PeterParikh}]
-$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
+\begin{lemma}[\cite{SeidlSMH04}]
+$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear interger arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
 \end{lemma}
@@
 \todo{add Presburger constraints to allow more expressive power.}
+\lh{TODO: solve the where to add $-1$ problem}
 %We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
@@
 %\end{lemma}
- $$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$$
+$$
+\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}
+$$
 where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}\yfc{I totally agree}.
@@
 \paragraph{Synchronisation of PFA}
-The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
+The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building underapproximations of string constraints. 
 Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
@@
 %
-Every accepting run of $\syncof A {A'}$ \lh{define run as a sequence of transitions etc} corresponds to an accepting run of $A$ and an accepting run of ${A'}$, and the word accepted by the run of $\syncof A {A'}$ implies a set of constraints on $\pvarone\cup\pvartwo\cup\cvarone\cup\cvartwo$ under which the word accepted by $A$ has the same semantics as the word accepted by ${A'}$.
+Every accepting run of $\syncof A {A'}$ corresponds to an accepting run of $A$ and an accepting run of ${A'}$, and the word accepted by the run of $\syncof A {A'}$ implies a set of constraints on $\pvarone\cup\pvartwo\cup\cvarone\cup\cvartwo$ under which the word accepted by $A$ has the same semantics as the word accepted by ${A'}$.
 %
@@
 Next, we define the set of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
-We start with the Parikh formula $\parikhfof {\syncof A {A'}}$ of $\syncof A {A'}$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone_\epsilon \times \cvartwo_\epsilon\}$ of the product automaton and conjoin it with the following restricting constraints.
+We start with computing the Parikh formula $\parikhfof {\syncof A {A'}}$ of $\syncof A {A'}$ over the set of variables $\pvarsof{\cvarone_\epsilon\times\cvartwo_\epsilon}$ and then conjoin it with the following restricting constraints.
 %We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
@@
 $$\label{lemma:synccorrect}
-\syncfof A {A'} = \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
+%\syncfof A {A'} = \exists \pvarsof{\cvarone\times\cvartwo}\exists {(\cvarone\times\cvartwo)}.\,\parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
+\syncfof A {A'} = {(\cvarone\times\cvartwo)}.\,\parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
 $$
@@
 \begin{lemma}
- $\semof {\exists .\,\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
+ $\semof {\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
 \end{lemma}

### 2019-11-09 draft.tex
add overview

--- 2019-11-08 draft.tex
@@
 
+Our string constraint solving produce can be used as a theory solver in a \emph{satisfiability module theory (SMT)} solver.
+In this way, we can describe and solve complex constraints like those appeared in the introduction.
+Further details of the combination as well as some other implementation details can be found in Section~\ref{section:implementation}.
+
 \todo{Talk about experiments}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\todo{Some non-technical text to explain how the approach solves a toy problem}
-For proving UNSAT, our strategy first over-approximates string-number conversion function $n=\its{x}$ as an uninterpreted function with an additional axiom $n\leq 0 \rightarrow \sti{\its{n}}=n$.
 
-and then solve the entire constraint with a procedure that is similar to the one in ATVA 2019.
+Here we try to explain the approach using a toy example $\phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^*\}$.
+Notice that $\phi$ is satisfiable.
+E.g., it has a model $x=``12''$ and $y=``1212''$.
+
+For proving UNSAT, our framework does not set any restriction on which decision procedure to use.
+One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
+For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and remove the constraint $n=\sti{x}$.
+This produce new formulas that over-approximate the original ones and fall in the acyclic fragment~\cite{abdulla2014string}, which is decidable.
+
+Since $\phi$ is satisfiable, so the over-approximation module will not return UNSAT.
+Then our procedure will pick patterns to restrict the domain of each string variables.
+More precisely, we use the so-called \emph{parametric flat automata} (PFA) to define such patterns (will be defined in Section~\ref{section:sfa}).
+An example of PFA can be found in Figure~\ref{fig:sfa}.
+The major benefit of project the domain of string variables to PFA is that then the satisfiability problem of string constraints can be reduced to the satisfiability of linear formulas in polynomial time.
+For most string constraints (e.g., $xy=yx$, $y \in (12)^*$ ), we can reduce them to linear constraint with arbitrary PFA for domain restriction (see Section~\ref{section:eq}) and reduce them to linear formulas.
+However, this does not work for \emph{string-number conversion constraints} $n = \sti{x}$.
+We will explain in Section~\ref{section:s2i} that restricting $x$ to general PFA reduces the string-number conversion constraint to an exponential-polynomial formula, which is unlikely to be solved efficiently~\cite{achatz2008deciding}.
+In this paper, we suggest that whenever $x$ is involved in a string-number conversion function, then we only use PFA in the form of the one in Figure~\ref{fig:sfa_its}.
+This allows us to obtain a reduction to linear formula even for string-number conversion constraints.
+If a model is found, then the procedure concludes SAT.
+If not, one can step-wisely change the PFA to more expressive ones (by adding more states and transitions) and hope the solution can be found at some point.
 
@@
 
-\section{Under-approximation}
+\section{Under-approximation} \label{section:under_approximate}
 In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_s$ to a set of equisatisfiable linear integer constraints $\phi_I$ in polynomial-time.
@@
 
-\section{Implementation}
+\section{Implementation}\label{section:implementation}
 \input{evaluation}

### 2019-11-09 evaluation.tex

@@
 
-\todo{Organize/Revise the context; Revise tables; Discussions}
+\todo{Organize/Revise the context; Add references of benchmarks; Revise tables; Discussions}
 
-{\bf General description}:
-In this section, we report and discuss our experiments.
-As a base result, we compare z3-Trau to SMT tools z3 and CVC4 on PyEx benchmark which is widely used for testing SMT string solvers to show the performance of z3-Trau in general.
-Then we do the same comparison on our string\_to\_int benchmarks to evaluate our approach.
-
-{\bf How we obtained our (str\_int) benchmark}:
-For experiments, we prepared our own str\_int benchmark\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}.
-It is collected from two sources of Python programs: Leetcode solutions written in Python and Python core libraries.
-These Python programs are concolic tested by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs.
-The SMT queries during the concolic testing are collected to the benchmark.
-The benchmark has two versions: full\_str\_int and filtered\_str\_int.
-full\_str\_int is the original benchmark we collected; filtered\_str\_int is that we filtered out cases that cvc4 says unsat while the unsat corers are not containing \texttt{str.to.int} or \texttt{int.to.str}.
-
-{\bf The environment of experiments}:
-The experiments are conducted under machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS.
-Since the large amount of problems in these benchmarks, we use containers to run these experiments in several machines with the same environment.
-The timeout is set to 10 seconds.
-
-{\bf Some annotations in tables}:
-\texttt{u.k.} stands for ``unknown''.
-\texttt{t.o.} stands for ``timeout''.
-\texttt{error} means that the execution is stopped with an error or exception such as segmental fault.
-\texttt{misc} means that the execution ends without expected (including errors) output.
-
-{\bf Tabales}:
-Table~\ref{table:base_benchmark} shows the comparison on several string benchmarks that are used by other tools. The total amount of cases in PyEx is 25421.
-
-\begin{table*}[]
+\begin{table*}[t]
 \centering
@@
 StringFuzz	& 504 & 295 & 264/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
-cvc4\textsubscript{pred}	& 16 & 184 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
+cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
 cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 2021 & 19/0 & 16 & 958 & 53/18 \\ \hline
@@
 
-Table~\ref{table:str_int_benchmark} shows the comparison on full\_str\_int. The total amount of cases in full\_str\_int is 21573.
-\begin{table*}[]
+\begin{table*}[t]
 \centering
@@
 \end{table*}
+
+In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation.
+To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[];
+LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[].
+Table~\ref{table:base_benchmark} shows the result of the comparison.
+The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS.
+We set the timeout is to 10 seconds.
+Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster.
+The results are either sat, unsat, timeout, or $\times$.
+$\times$ may be unknown, error, or exception.
+
+\textbf{Comparison according to Table 1......}
+
+To evaluate our strategy for string-number/number-string conversion, we also prepared a benchmark \texttt{str\_int}\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}.
+It is collected from two sources of Python programs that use ttexttt{int()} function: Leetcode solutions written in Python and Python core libraries.
+We concolic tested these Python programs by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs.
+The SMT queries during the concolic testing are collected as our benchmark.
+To be more precise in evalutation, we have two versions of \texttt{str\_int} benchmark: \texttt{full\_str\_int} and \texttt{filtered\_str\_int}.
+\texttt{full\_str\_int} is the original benchmark we collected (i.e.
+from Python programs using \texttt{int()}); \texttt{filtered\_str\_int} is a subset of \texttt{fill\_str\_int}.
+We filtered out problems that cvc4 says unsat while the unsat cores do not contain \texttt{str.to.int} or \texttt{int.to.str}.
+The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}.
+The experiments are conducted under the same condition as the experiments on other benchmarks.
+
+\textbf{Comparison according to Table 2.....}
 

### 2019-11-09 draft.tex
I am done, and Yu-Fang promissed that he will not bother me from this point on.

--- 2019-11-08 draft.tex
@@
 \newcommand{\pim}{\alpha}
-\newcommand{\syncop}{\Cap}
+%\newcommand{\syncop}{\Cap}
+\newcommand{\syncop}{\times}
 \newcommand{\syncof}[2]{#1 \syncop #2}
@@
 \newcommand{\syncT}{T_\syncop}
-\newcommand{\pvarsof}[1]{\#(#1)}
+\newcommand{\pvarsof}[1]{\#{#1}}
 \newcommand{\pvar}{\pvarsof V}
@@
 \newcommand{\pvartwo}{\pvarsof {V'}}
+\newcommand{\defeq}{::=}
 
@@
 integers. For a set $A$, we use $|A|$ to denote its size. 
+For $n,m\in\nat$, we write $[n,m]$ for the set of natural numbers 
+%(or symbols in $\Sigma$) 
+$\{k\mid n\leq k \leq m\}$. 
 An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{string} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty string}.
 We use $w_1\cdot w_2$ to denote the \emph{concatenation} of strings $w_1$ and $w_2$.
-$\Sigma^*$ is the set of all strings over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, and 
+$\Sigma^*$ is the set of all strings over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$, and 
 A \emph{language} over $\Sigma$ is a subset $L$ of $\Sigma^*$.  
@@
 The \emph{language} of $A$ is the set $L(A)$ of all accepted words.
+
+Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.   
+Given a linear formula $\phi$, a set of variables $V$ that includes all variables occurring in $\phi$, and an \emph{interpretation} of $V$, a function $I:V\rightarrow \nat$, 
+we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a model of $\phi$ over $V$.
+We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
+We drop the reference to $V$ and write just ``model of $\phi$'',  $\modelsof \phi$, and $\models$ when no confusion may arise.
 
@@
 Notice that this approach is general enough to support any finite set of characters.
-We write $[n,m]$ for the set of numbers (or symbols in $\Sigma$) $\{k\mid n\leq k \leq m\}$.
 
@@
 \end{enumerate} 
-\lh{TODO: decide whether we want epsilon trans, or perhaps additional constraints saying that a var equals epsilon or a character}
 \begin{figure*}
@@
 \begin{lemma}\label{lemma:parikh}
-For an PFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
+For an PFA $A$ and $x,y\in L(A)$, if $\parikhof x = \parikhof y$ then $x = y$. 
 \end{lemma}
@@
 Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
-Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, 
-hence $\semof A$ is characterised by models of $\parikhof {A}$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof {A}$ does not constraint them), we may say that
-%\begin{lemma}\ref{lemma:decw}
-%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\parikhfof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
-%\end{lemma}
-$$
-\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}
-$$
-where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}\yfc{I totally agree}.
+Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all modesl of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated byt the following collolary of Lemma~\ref{lemma:decx}:
+%
+\begin{corollary}
+For an PFA $A$ over character variables $V$,
+$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$.
+\end{corollary}
+%
+A minor technical difficulty is that we wish to work with pure arithmetic formulae, 
+but we may also wish to specify when a character variable is assigned $\epsilon$, which is not a number. 
+Hence, to allow purely arithmetic formulae to talk about the value $\epsilon$, we encode $\epsilon$ as $-1$.
+In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulae constraining interpretations of character variables.
 
 \paragraph{Synchronisation of PFA}
-The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building underapproximations of string constraints. 
-Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
-Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$,
-namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
+The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ over character variables $V$ and $V'$, respectively, is a crucial component of building underapproximations of string constraints.
+Synchronisation formula is a formula $\syncfof A {A'}$ over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
+Its representation of the intersection includes an additional information about the synchronisation of $A$ and ${A'}$, also needed for building underapproximations of string constraints.
+Namely, it characterises the set of pairs of string encoding encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
 $\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.
 
-Assume that $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ are two SFA over disjoint sets of variables, $\cvarone \cap \cvartwo = \emptyset$. 
-We build so called asynchronous product automaton $\syncof A {A'}$ of $A$ and ${A'}$ and then extract the formula $\syncfof A {A'}$ from its Parikh image.
+Let $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
+We will build their asynchronous product, an automaton $\syncof A {A'}$, 
+and then extract the synchronisation formula $\syncfof A {A'}$ from it.
 %
-Such product automaton uses $Q\times Q'$ as the set of states and 
-%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
+The product automaton uses $Q\times Q'$ as the set of states and 
 $\cvarone_\epsilon\times\cvartwo_\epsilon$
@@
 %
-Every accepting run of $\syncof A {A'}$ corresponds to an accepting run of $A$ and an accepting run of ${A'}$, and the word accepted by the run of $\syncof A {A'}$ implies a set of constraints on $\pvarone\cup\pvartwo\cup\cvarone\cup\cvartwo$ under which the word accepted by $A$ has the same semantics as the word accepted by ${A'}$.
+Every accepting run of $\syncof A {A'}$ will correspond to a pair of accepting runs, 
+a run of $A$ over a parametric string $x$ and a run of ${A'}$ over a parametric string $x'$. 
+The word accepted by the run of $\syncof A {A'}$ will induce the constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric strings have the same interpretation, i.e.
+$I(x) = I(x')$.
+
+Intuitively, when $\syncof A {A'}$ takes a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$, 
+it means the character variable $v$ and $v'$ should be assigned the same value,
+$A$ transitions under $v$ from state $q_1$ to state $q_2$ and ${A'}$ from $q_1'$ to $q_2'$ under $v'$.
 %
-Particularly, if a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and ${A'}$ from $q_1'$ to $q_2'$.
-%
-If a transition $((q_1,q_1'), (v,\epsilon),(q_2,q_1'))$ is taken, then it means that the character variable $v$ should be assigned $\epsilon$, $A$ may transition under $v$ to $q_1$ and ${A'}$ stays in the same state, as a response to $A$s reading epsilon may as well be taking no action.
+When $\syncof A {A'}$ takes a transition $((q_1,q_1'), (v,\epsilon),(q_2,q_1'))$, 
+it means that the character variable $v$ should be assigned $\epsilon$, 
+$A$ transitions under $v$ to $q_1$, and ${A'}$ takes no action, since no action is needed to match $A$s reading $\epsilon$ (hence not reading the input word).
 Symmetrically, ${A'}$ might read a variable $v$ assigned $\epsilon$ and $A$ may stay.
@@
 %
-Next, we define the set of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
-We start with computing the Parikh formula $\parikhfof {\syncof A {A'}}$ of $\syncof A {A'}$ over the set of variables $\pvarsof{\cvarone_\epsilon\times\cvartwo_\epsilon}$ and then conjoin it with the following restricting constraints.
-%We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
-
-The first restricting constraint establishes the relation of between the Parikh image of a word accepted by $\syncof A {A'}$ and the Parikh images of the corresponding parametric strings accepted by $A$ and ${A'}$:
-$$ \Psi_{\#} = 
+%The we define of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
+The core part of the synchronisation formula is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all its runs.
+%
+To extract form a run of $\syncof A {A'}$ the corresponding run of $A$ and of $A'$, we use the following constraint:
+$$ \Psi_{\#} \defeq 
 \left(\bigwedge_{v\in\cvarone}\#v = \sum_{x' \in \cvartwo_\epsilon} \#{(v,x')}\right)
@@
 %\end{enumerate}
-
-Then we add the following linear constraints to enforce that the decodings of the models are indeed the same, 
+Finally, to ensure that the interpretations of the parametric strings accepted by $A$ and $A'$ are the same, the following constraint is used:
 % condition 1.
@@
 required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
-$$ \Psi_= =
+$$ \Psi_= \defeq
 \bigwedge_{x\in\cvarone_\epsilon,x'\in\cvartwo_\epsilon} \#(x,x')>0 \rightarrow (x=x')
@@
 %\end{enumerate}
-
 The synchronisation formula is the conjunction 
@@
 %\syncfof A {A'} = \exists \pvarsof{\cvarone\times\cvartwo}\exists {(\cvarone\times\cvartwo)}.\,\parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
-\syncfof A {A'} = {(\cvarone\times\cvartwo)}.\,\parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
+\syncfof A {A'} \defeq \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
 $$
-The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. Informally,
-the
-
+The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. 
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
 \begin{lemma}
- $\semof {\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
+%$\semof {\exists V_\times .
+\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
+$\semof {\exists V_\times . \syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
 \end{lemma}
+%
+Informally, the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{B}$, that constitute the intersection $\semof{A} \cap \semof{B}$.
+A minor technical difficulty is that the modes of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $V_\times = (\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$, hence in the lemma we have to restrict the models only to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$, which we achieve by quantifying out $V_\times$.
 

### 2019-11-09 draft.tex
polishing 5.1

@@
 \newcommand{\sym}[2]{v_{#1}^{#2}}
-\todo{add Presburger constraints to allow more expressive power.}
-\lh{TODO: solve the where to add $-1$ problem}
+\todo{additional presburget constraints to encode $\epsilon$ added at translation to a formula}
 %We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
@@
 
-The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulae and handled by an SMT solver, allowing to circumvent more costly automata algorithms and decision procedures.
-\lh{concretize and justify this better?}
+The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulae and handled efficiently by an SMT solver. 
+\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
 %
@@
 \paragraph{Synchronisation of PFA}
-The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ over character variables $V$ and $V'$, respectively, is a crucial component of building underapproximations of string constraints.
-Synchronisation formula is a formula $\syncfof A {A'}$ over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
-Its representation of the intersection includes an additional information about the synchronisation of $A$ and ${A'}$, also needed for building underapproximations of string constraints.
-Namely, it characterises the set of pairs of string encoding encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
-$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.
+The following construction is an important step in building underapproximations of string constraints. 
+For two PFA $A$ and $A'$ over character variables $V$ and $V'$, respectively, 
+it builds \emph{synchronisation formula} $\syncfof A {A'}$, a linear formula over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. 
+Besides the intersection itself, it also represents the set of all pairs of string encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
+$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$ which constitute the intersection.
 
-Let $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
-We will build their asynchronous product, an automaton $\syncof A {A'}$, 
-and then extract the synchronisation formula $\syncfof A {A'}$ from it.
+Particularly, a synchronisation formula is build for two PFA  
+$A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
 %
-The product automaton uses $Q\times Q'$ as the set of states and 
+It is extracted from the asynchronous product of $A$ and $A'$, an automaton $\syncof A {A'}$. 
+%
+The asynchronour product is an automaton that uses $Q\times Q'$ as the set of states and 
 $\cvarone_\epsilon\times\cvartwo_\epsilon$
@@
 %
-Every accepting run of $\syncof A {A'}$ will correspond to a pair of accepting runs, 
+Every accepting run of $\syncof A {A'}$ corresponds to a pair of accepting runs, 
 a run of $A$ over a parametric string $x$ and a run of ${A'}$ over a parametric string $x'$. 
-The word accepted by the run of $\syncof A {A'}$ will induce the constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric strings have the same interpretation, i.e.
+The word accepted by the run of $\syncof A {A'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric strings have the same interpretation, i.e.
 $I(x) = I(x')$.
@@
 
-Formally, the product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'))$, where the transition relation $\syncT$ is the minimal set satisfying the following:
+Formally, the asynchronous product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'))$, where the transition relation $\syncT$ is the minimal set satisfying the following:
 %
@@
 %The we define of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
-The core part of the synchronisation formula is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all its runs.
+The synchronisation formula $\syncof A {A'}$ is extracted from $\syncof A {A'}$ as follows.
+Its first, core part is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all runs of the product.
 %
-To extract form a run of $\syncof A {A'}$ the corresponding run of $A$ and of $A'$, we use the following constraint:
+The second part is a constraint that extracts from a run of $\syncof A {A'}$ the corresponding runs of $A$ and of $A'$:
 $$ \Psi_{\#} \defeq 
@@
 %\end{enumerate}
-Finally, to ensure that the interpretations of the parametric strings accepted by $A$ and $A'$ are the same, the following constraint is used:
+Finally, the third part forces the interpretations of the parametric strings accepted by $A$ and $A'$ be the same:
 % condition 1.
@@
 The synchronisation formula is the conjunction 
-$$\label{lemma:synccorrect}
+$$
 %\syncfof A {A'} = \exists \pvarsof{\cvarone\times\cvartwo}\exists {(\cvarone\times\cvartwo)}.\,\parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
@@
 $$
-The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. 
+The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. The Lemma can also be understood as a precise specification the semantics of the synchronisation formula. 
 %
 %\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
-\begin{lemma}
+\begin{lemma}\label{lemma:synccorrect}
 %$\semof {\exists V_\times .
@@
 %
-Informally, the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{B}$, that constitute the intersection $\semof{A} \cap \semof{B}$.
-A minor technical difficulty is that the modes of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $V_\times = (\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$, hence in the lemma we have to restrict the models only to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$, which we achieve by quantifying out $V_\times$.
+Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{B}$, that constitute the intersection $\semof{A} \cap \semof{B}$.
+A minor technical difficulty is that the modes of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $V_\times = (\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
+Hence in the lemma, we have to restrict the models to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
+This is  achieve by quantifying out the variables of $V_\times$.
 
@@
 
-\lh{TODO: put this somewhere and explain}
+\lh{removed the closed under concatenation lemma, no more true due to epsilons}
 
-\begin{lemma}
-	Symbolic flat automata are closed under concatenation.
-\end{lemma}
+%\begin{lemma}
+%	Symbolic flat automata are closed under concatenation.
+%\end{lemma}
 

### 2019-11-09 draft.tex
little things

@@
 %
-It is extracted from the asynchronous product of $A$ and $A'$, an automaton $\syncof A {A'}$. 
+It is extracted from the \emph{asynchronous product} of $A$ and $A'$. 
 %
-The asynchronour product is an automaton that uses $Q\times Q'$ as the set of states and 
+The asynchronous product is an automaton that uses $Q\times Q'$ as the set of states and 
 $\cvarone_\epsilon\times\cvartwo_\epsilon$
@@
 %The we define of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
-The synchronisation formula $\syncof A {A'}$ is extracted from $\syncof A {A'}$ as follows.
-Its first, core part is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all runs of the product.
+The synchronisation formula $\syncfof{A} {A'}$ is extracted from $\syncof A {A'}$ as follows.
+Its first part is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all runs of the product.
 %
@@
 %\end{enumerate}
-The synchronisation formula is the conjunction 
+The synchronisation formula is then the conjunction 
 $$
@@
 $$
-The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect}. The Lemma can also be understood as a precise specification the semantics of the synchronisation formula. 
+
+The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect} below.
+The lemma can also be understood as a precise specification the semantics of the synchronisation formula, on which we rely for correctness of the construction of underapproximations of string constraints.
 %

### 2019-11-11 evaluation.tex
evalutaion: update tables

@@
 			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
-PyEx		& 19655 & 3851 & 1915/0 & 19763 & 3834 & 0/1824 & 16578 & 3832 & 5011/0 & 3023 & 3835 & 16717/1846 \\ 
-APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 36 & 112 & 105/347 \\ 
-LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 676 & 1780 &  70/140 \\ 
-StringFuzz	& 504 & 295 & 264/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
+PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
+APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
+LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
+StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
 cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
-cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 2021 & 19/0 & 16 & 958 & 53/18 \\ \hline
+cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
 \end{tabular}
@@
 			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
-full\_str\_int		& 3289 & 17089 & 1195/0 & 2185 & 16377 & 3011/0 & 2716 & 16831 & 2026/0 & 422 & 16034 & 4131/986 \\ 
+full\_str\_int		& 3294 & 17088 & 1191/0 & 2185 & 16377 & 3011/0 & 422 & 16034 & 4131/986 & 2731 & 16832 & 2010/0 \\ 
 filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
@@
 The results are either sat, unsat, timeout, or $\times$.
-$\times$ may be unknown, error, or exception.
+In case $\times$, the result may be unknown, error, or exception.
 

### 2019-11-11 evaluation.tex
attempt to improve the experimental section, part 1

@@
 
+We have implemented the proposed approach in a prototype tool \textsf{z3-Trau} as a part of the Z3 theorem prover.
+This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to parse input formulae.
+
+We compare \textsf{z3-Trau} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
+We do not compare with Sloth \cite{sloth} since it does not support length constraints.
+We present data on two benchmark groups (see Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}) that demonstrate two points.
+First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories.
+Second, we show that our tool is competitive on well-known benchmarks that can be effectively handled by other existing solvers.
+All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS.
+The timeout was set to 10s for each test.
+The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
+Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulae.
+Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported invalid answer or crashed.
+
+\hide{
 In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation.
@@
 In case $\times$, the result may be unknown, error, or exception.
+}
 

### 2019-11-11 evaluation.tex
added a note about the validator to the experimental section

@@
 We do not compare with Sloth \cite{sloth} since it does not support length constraints.
-We present data on two benchmark groups (see Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}) that demonstrate two points.
+We present data on two benchmark groups that demonstrate two points.
 First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories.
 Second, we show that our tool is competitive on well-known benchmarks that can be effectively handled by other existing solvers.
+The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
 All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS.
 The timeout was set to 10s for each test.
-The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
 Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulae.
-Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported invalid answer or crashed.
+Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported incorrect answer or crashed.
+
+Occasionally, during the experiments, there was a case where a solver reported a different answer to a test than the other solvers.
+To decide which solver reported the incorrect answer, we have developed our own validator.
+Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test.
+The modified test is re-evaluated by solvers and if the solvers decide that the modified test is satisfiable, the answer of the solvers that originally reported unsat is evaluated as incorrect.
 

### 2019-11-11 draft.tex
try to merge the intro made by Julain and the original one

@@
 
-String constraint solving has received considerable attention in the constraint solving community, with solvers such as CVC4 and Z3 implmenting solvers of ever-increasing sophistication.
+String constraint solving has received considerable attention in the constraint solving community, with solvers such as CVC4 and Z3 implementing solvers of ever-increasing sophistication.
 Operations such as substring and string length are widely supported, and recent solvers such as Z3-str3 have shown impressive results.
@@
 at least one side of the conversion must be a constant.
-Thus, $v = string2int("5")$ or $v = int2string(5)$ are handled but $v_1 = int2string(v_2)$ will fail.
+Thus, $n = \sti{x}$ or $x = \its{5}$ are handled but $n = \sti{x}$ will fail.
 
@@
 	{\tt{resetArray(x)}} & [0, 0, 0, 0, 0, 0] \\
-	{\tt{x["3"] = 5}} & [0, 0, 0, 5, 0, 0] \\
+	{\tt{x[3] = 5}} & [0, 0, 0, 5, 0, 0] \\
 	{\tt{x["12"] = 7}} & [0, 0, 0, 5, 0, 0, , , , , , 7] \\
@@
 This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+On the other hand, the size of an array ({\tt{arr.length}} in the example) is defined as the ``largest integer index plus one'', so the integer value of element expression can affect the array size.
 
-Now observe that {\tt{resetArray}} assigns to the array in a loop of which the size cannot, in general, be known a priori; as such, falls into the case where neither the string nor the integer in a conversion are constant and hence most SMT solvers will not be able to handle it.
-But this is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+Now observe that {\tt{resetArray}} assigns to the array in a loop of which the size cannot, in general, be known a priori; as such, falls into the case where neither the string nor the integer in a conversion is constant and hence most SMT solvers will not be able to handle it.
+More specifically, in some program the assignment {\tt{x[k] = 5}} can happen before calling {\tt{resetArray(x)}}, where {\tt{k}} is an user input string.
+One would need to know the value of $\sti{k}$ and hence whether it will affect the size of the array {\tt{x}}.
+This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
 
-\todo{The end of Julian's current writing}
+For the purpose of program analysis, string solver also needs to support \emph{equality constraints} (e.g.
+$x.y = y.x$), \emph{membership constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$).
+Most of the standard string operations can be encoded using the above three types of constraints\footnote{Except a few exceptions, such as {\tt{replaceALL}}, {\tt{reverse}}, and string-number conversions.}.
+Those are also the type of constraints supported by most state-of-the-art string constraint solvers such as Z3, CVC4, Z3Str3, and Trau+.
+
+Indeed, the analysis of string manipulating program is becoming more and more important nowadays.
+Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string input values.
+In the past, a significant amount of research efforts have been investigated to symbolic execution and test case generation of string manipulating programs~\cite{saxena2010symbolic,artzi2011framework,huang2004securing,sen2013jalangi} and string constraint solving~\cite{kiezun2009hampi,abdulla2014string,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2} is the core enabling technology.
 
@@
 Maybe we still say our approach is still over-approximation + under-approximation, in this case, need to think how to present the over-approximation part.
-Maybe no CEGAR is fine.}
+Maybe no CEGAR is fine.
 
@@
 Such constraint contains \textit{string-number conversion} functions (e.g., $\sti{input}$ and $\sti{index}$), \textit{equality constraints} (e.g., $index = input\cdot \its{1}$), and \textit{integer constraints} (e.g., $0 \leq \sti{input}<M$).
+}
+
 Solving constraint of this kind is a very challenging problem.
@@
 Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:evaluation} for detailed explanation).
+
 In this paper, we propose a framework that handles string constraints with string-number conversion efficiently.

### 2019-11-11 draft.tex
try to merge the intro made by Julain and the original one

@@
 Those are also the type of constraints supported by most state-of-the-art string constraint solvers such as Z3, CVC4, Z3Str3, and Trau+.
+\yfc{maybe more concrete example?}\\
 
+\yfc{I am not sure how to add other examples here in a nice way, one reason is we are very specifically focused on Javascript, but other examples, e.g., the credit card one, is very general.}
+
+\hide{
 Indeed, the analysis of string manipulating program is becoming more and more important nowadays.
@@
 In the past, a significant amount of research efforts have been investigated to symbolic execution and test case generation of string manipulating programs~\cite{saxena2010symbolic,artzi2011framework,huang2004securing,sen2013jalangi} and string constraint solving~\cite{kiezun2009hampi,abdulla2014string,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2} is the core enabling technology.
+}
 
@@
 
-Solving constraint of this kind is a very challenging problem.
+Solving string constraint with string-number conversion is a very challenging problem.
 From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
@@
 Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:evaluation} for detailed explanation).
+\yfc{add concrete evidence}
 
-In this paper, we propose a framework that handles string constraints with string-number conversion efficiently.
-Our framework uses both over and under-approximation of the string constraints.
+In this paper, we adopt a framework that handles string constraints with string-number conversion efficiently.
+Due to the high complexity of solving the problem exactly, our framework uses both over and under-approximation of the string constraints.
 The over-approximation is for proving UNSAT and the under-approximation is for proving SAT of the string constraint.
@@
 
-For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3}, our framework does not set any restriction on which algorithm to be used.
-In our experiences, the UNSAT instances in all available benchmarks are not that difficult and many approaches can handle all of them almost perfectly.
-The battle field is in fact those SAT instances.
-In our prototype tool, we implement the algorithm presented in~\cite{parosh2019chain}, in addition with some additional axioms, to handle the over-approximation of string constraints with number-string conversion.
+For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
+In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
+In our implementation, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
 
+The battle field is in fact those SAT instances, for which we develop solutions based on under-approximation.
 For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
 By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
-In paper, we propose to use patterns defined by \emph{symbolic flat automata} (SFA).
-The approach based on SFA is very flexible yet allows very efficiently manipulation.
-One can pick SFA of arbitrary structure for the search space restriction and reduce the string constraint solving problem to an integer constraint solving problem.
-For efficiency, it avoids the alphabet
-explosion problem that the approach in~\cite{abdulla2017flatten} suffers.
+In paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA).
+The approach based on PFA is very flexible yet allows very efficiently manipulation.
+One can pick PFA of arbitrary structure for the search space restriction and reduce the string constraint solving problem to an integer constraint solving problem.
+For efficiency, it avoids the \textit{alphabet
+explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.\yfc{maybe explaina a bit somewhere the alphabet explosion problem of PLDI 2017}
 
-Based on the SFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
+Based on the PFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
 Thus the problem is significantly simplified.
-We show that if we restrict the variable to arbitrary symbolic flat automata, one can convert the a string constraint with string-number function to an integer constraint consisting of both polynomials and exponentials.
+We show that if we restrict the variable to arbitrary PFA, one can convert the a string constraint with string-number function to an integer constraint consisting of both polynomials and exponentials.
 Solving such kind of constraints is a very difficult task.
@@
 To the best of our knowledge, the satisfiability problem of polynomial-exponential equations is still open.
-For efficiency reason, we propose to use \emph{SFA with only one loop} to handle string-number conversion function.
-That is, if we encountered a constraint $y=\sti{x}$, then we always restrict the domain of $x$ to some SFA with one loop, instead of arbitrary SFAs.
-This allows us to convert a string constraint with string-number conversion function to a equisatisfiable linear integer constraint, which can be solved very efficiently.
+For efficiency reason, we propose to use PFA with specific structural constraint to handle string-number conversion function.
+That is, if we encountered a constraint $y=\sti{x}$, then we always restrict the domain of $x$ to some specific kind of PFA, instead of allowing arbitrary PFAs.
+This allows us to convert a string constraint with string-number conversion function to an equisatisfiable linear formula, which can be solved very efficiently.
 
@@
 
+\hide{
 To ease presentation, in the paper, we only consider string constraints consisting of \emph{equality constraints (a.k.a.
-word equation)}, \emph{length constraints}, and \emph{string-number conversion} functions.
-In fact, the approach can be easily extended to support transducer and membership constraints.
-The extension is implemented in our prototype tool \textsf{z3-Trau}.
+word equation)}, \emph{membership constraints}, \emph{length constraints}, and \emph{string-number conversion} functions.
 
-\hide{
 suggest restricting the string domain to $0^*[0-9]^k$, where $k$ is the maximum 
@@
 
-Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the SFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the SFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
+Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the PFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the PFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
 Our next task is to find a model for $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$ under the domain restriction specified by $S_n$ and $S_m$.
@@
 We use $\#(v_i)$ and $\#(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
-The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product automaton.
+The following formulae establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
 \begin{enumerate}
@@
 The interpretation $I$ is defined as $I(v)=M(v)$ for all $v\in (\cvarone \cup \cvartwo)$.
-The symbolic words $w_n$ and $w_m$ can be obtained by traverse the SFAs following the number of occurrences of each character variables.
-More specifically, assume that the SFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{\#(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{\#(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{\#(v_m^0)}$$
+The symbolic words $w_n$ and $w_m$ can be obtained by traverse the PFAs following the number of occurrences of each character variables.
+More specifically, assume that the PFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{\#(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{\#(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{\#(v_m^0)}$$
 Note that $\#(v_0^0)=\#(v_0^1)=\#(v_0^2)=\#(v_0^3)$, so we just use $\#(v_0^0)$ to denote the number of times of first loop traversal.
@@
 The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
-In an more efficient implementation, one just project $y_2$ and $y'_2$ to a SFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the SFA has no loop and only one transition).
+In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
 
@@
 
-In this section, we discuss how to handle the constraint $n=\sti{x}$ by restricting the domain of $x$ to some SFA.
-Let us begin with a simple example, assume that we use the SFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
+In this section, we discuss how to handle the constraint $n=\sti{x}$ by restricting the domain of $x$ to some PFA.
+Let us begin with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
 Then we know that when $0\leq v_0,v_1 \leq 9$, then $n$ is a positive integer value, and otherwise $n =-1$.
@@
 Let us have a look at another example.
-If we restrict the domain of $x$ to the SFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0^{(0)}\times 10+ v_1^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0^{(0)})-1})\times 100^{\#(v_2^{(0)})}+(v_2^{(0)}\times 10+ v_3^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_2^{(0)})-1}) =  (v_0^{(0)}\times 10+ v_1^{(0)}) \times \frac{100^{\#(v_0^{(0)})}-1}{100-1}\times 100^{\#(v_2^{(0)})} + (v_2^{(0)}\times 10+ v_3^{(0)}) \times \frac{100^{\#(v_2^{(0)})}-1}{100-1}$.
+If we restrict the domain of $x$ to the PFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0^{(0)}\times 10+ v_1^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0^{(0)})-1})\times 100^{\#(v_2^{(0)})}+(v_2^{(0)}\times 10+ v_3^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_2^{(0)})-1}) =  (v_0^{(0)}\times 10+ v_1^{(0)}) \times \frac{100^{\#(v_0^{(0)})}-1}{100-1}\times 100^{\#(v_2^{(0)})} + (v_2^{(0)}\times 10+ v_3^{(0)}) \times \frac{100^{\#(v_2^{(0)})}-1}{100-1}$.
 Observe that the formula has two exponential components $\frac{100^{\#(v_0^{(0)})}\times 100^{\#(v_2^{(0)})} }{100-1}$ and $\frac{100^{\#(v_2^{(0)})} }{100-1}$.
 
-It is not difficult to observe that, for the case of an arbitrary SFA of $m$ loops, the formula to define $n$ contains $m$ exponential components, one for each loop.
+It is not difficult to observe that, for the case of an arbitrary PFA of $m$ loops, the formula to define $n$ contains $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 
-\paragraph{SFA that allows efficient string-integer conversion: } In the previous discussion, we know that it is unlikely to use arbitrary SFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
-The problem is that each loop in the SFA creates an exponential component.
-An immediate idea would be that maybe we can restrict the variable to some specific SFA that allow more efficient constraint solving.
+\paragraph{PFA that allows efficient string-integer conversion: } In the previous discussion, we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
+The problem is that each loop in the PFA creates an exponential component.
+An immediate idea would be that maybe we can restrict the variable to some specific PFA that allow more efficient constraint solving.
 At the same time, we want to keep some good property, i.e., the search space covers all integers with at most $m$-digits.
 
-Our first attempt is a SFA with no loop, i.e., a straight line structure (e.g., the SFA in Fig~\ref{fig:sfa_its} without the self-loop at $q_0$).
+Our first attempt is a PFA with no loop, i.e., a straight line structure (e.g., the PFA in Fig~\ref{fig:sfa_its} without the self-loop at $q_0$).
 The corresponding integer constraint does not have exponential components.
@@
 Consider the example $\sti{x}=10 \wedge |x|=5$.
-The number $10$ has only $2$-digits, at the first glance, a straight-line SFA with two transitions, i.e., the SFA \scalebox{0.5}{\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+The number $10$ has only $2$-digits, at the first glance, a straight-line PFA with two transitions, i.e., the PFA \scalebox{0.5}{\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
 			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
@@
 The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
-In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a SFA in Figure~\ref{fig:sfa_its}.
-The SFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such SFA.
+In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a PFA in Figure~\ref{fig:sfa_its}.
+The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such PFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
-Although this SFA still has a loop, but it will not create any exponential component because the loop only represents a sequence of `0' that occurs in the prefix of $x$.
+Although this PFA still has a loop, but it will not create any exponential component because the loop only represents a sequence of `0' that occurs in the prefix of $x$.
 It will not affect the integer value of $n=\sti{x}$.
@@
 
-Such SFA handles bounded integers (e.g., 10-digits or 64-bits) precisely and under-approximate the possible values of unbounded integers.
+Such PFA handles bounded integers (e.g., 10-digits or 64-bits) precisely and under-approximate the possible values of unbounded integers.
 It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.

### 2019-11-12 draft.tex
polish intro and overview

@@
 
+\usepackage{fancyvrb}
 \usepackage{xcolor}
@@
 \newcommand{\hide}[1]{}
+\newcommand{\tool}{{\textsf{Z3-pfa}}}
 
@@
 $x.y = y.x$), \emph{membership constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$).
-Most of the standard string operations can be encoded using the above three types of constraints\footnote{Except a few exceptions, such as {\tt{replaceALL}}, {\tt{reverse}}, and string-number conversions.}.
+Most of the standard string operations can be encoded using the above three types of constraints.
+For instance, $y=x.charAt(i)$ can be encoded as $x=x_1.x_2.x_3 \wedge |x_1| = i \wedge |x_2| =1 \wedge y= x_2$.
 Those are also the type of constraints supported by most state-of-the-art string constraint solvers such as Z3, CVC4, Z3Str3, and Trau+.
-\yfc{maybe more concrete example?}\\
 
@@
 In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
-In our implementation, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
+In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
 
-The battle field is in fact those SAT instances, for which we develop solutions based on under-approximation.
+The battle field is in fact those SAT instances, for which we develop solutions using under-approximation.
 For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
 By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
-In paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA).
+In paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA) (will be defined formally in Section~\ref{section:sfa}).
 The approach based on PFA is very flexible yet allows very efficiently manipulation.
-One can pick PFA of arbitrary structure for the search space restriction and reduce the string constraint solving problem to an integer constraint solving problem.
-For efficiency, it avoids the \textit{alphabet
-explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.\yfc{maybe explaina a bit somewhere the alphabet explosion problem of PLDI 2017}
+One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
+Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.\yfc{maybe explain a bit somewhere the alphabet explosion problem of PLDI 2017} In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation, in general,  still encodes possibility an infinite number of models.
+Such symbolic encoding based on PFA is the key to handle string-number conversion.
+In our under-approximation approach, the original undecidable fragment, i.e., string constraint with string-number conversion, is converted to linear formulas and can be solved efficiently in a systematic manner.
 
-Based on the PFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
+More concretely, based on the PFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
 Thus the problem is significantly simplified.
@@
 
-Our string constraint solving produce can be used as a theory solver in a \emph{satisfiability module theory (SMT)} solver.
-In this way, we can describe and solve complex constraints like those appeared in the introduction.
+Our string constraint solving produce can be easily integrated in a \emph{satisfiability module theory (SMT)} solver as a theory solver.
+The integration allows us to express string operations that cannot be reduced to the type of constraints (membership, equality, integer, string-number conversion) supported by our procedure.
+For example, we can encode \texttt{split} using the code fragment in Figure~\ref{fig:smt_string}.
+Other functions such as \texttt{replaceAll} and \texttt{reverse} can be encoded in a similar manner.
+The performance of such encoding might not be as good as those that provide direct support to those operations, but at least it works for some cases in our experiments.
 Further details of the combination as well as some other implementation details can be found in Section~\ref{section:implementation}.
+
+\begin{figure}
+	\begin{Verbatim}[fontsize=\scriptsize,xleftmargin=-4cm]
+				(define-fun-rec split ((x String)(y String)(xIdx Int)(aIdx Int)) 
+				(Array Int String)
+				(ite (= xIdx (str.len x))
+				  (store ((as const (Array Int String)) "") aIdx x)
+				  (ite (= y (str.at x xIdx)) 
+				    (store 
+				      (split (str.substr x (+ xIdx 1) (- (str.len x) 1) ) 
+				      0 (+ aIdx 1) y) 
+				      aIdx
+				      (str.substr str 0 xIdx)
+				    )
+				    (split x (+ xIdx 1) aIdx y)
+				  )
+				)
+			\end{Verbatim}
+
+	 	\caption{Encoding \texttt{Split(x,y)} using recursive functions and the array theory.
+The recursive function \texttt{split (x y 0 0)} returns an array of type \texttt{(Array Int String)} that maps an index $i$ to the $i$th component (separated by the character $y$ ) of $x$.}
+	 	\label{fig:smt_string}
+\end{figure}
 
@@
 
-Here we try to explain the approach using a toy example $\phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^*\}$.
+Here we try to explain the approach using a toy example $\phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$.
 Notice that $\phi$ is satisfiable.
@@
 This produce new formulas that over-approximate the original ones and fall in the acyclic fragment~\cite{abdulla2014string}, which is decidable.
+Since $\phi$ is satisfiable, the over-approximation module will not return UNSAT.
 
-Since $\phi$ is satisfiable, so the over-approximation module will not return UNSAT.
-Then our procedure will pick patterns to restrict the domain of each string variables.
-More precisely, we use the so-called \emph{parametric flat automata} (PFA) to define such patterns (will be defined in Section~\ref{section:sfa}).
-An example of PFA can be found in Figure~\ref{fig:sfa}.
-The major benefit of project the domain of string variables to PFA is that then the satisfiability problem of string constraints can be reduced to the satisfiability of linear formulas in polynomial time.
-For most string constraints (e.g., $xy=yx$, $y \in (12)^*$ ), we can reduce them to linear constraint with arbitrary PFA for domain restriction (see Section~\ref{section:eq}) and reduce them to linear formulas.
-However, this does not work for \emph{string-number conversion constraints} $n = \sti{x}$.
-We will explain in Section~\ref{section:s2i} that restricting $x$ to general PFA reduces the string-number conversion constraint to an exponential-polynomial formula, which is unlikely to be solved efficiently~\cite{achatz2008deciding}.
-In this paper, we suggest that whenever $x$ is involved in a string-number conversion function, then we only use PFA in the form of the one in Figure~\ref{fig:sfa_its}.
-This allows us to obtain a reduction to linear formula even for string-number conversion constraints.
-If a model is found, then the procedure concludes SAT.
-If not, one can step-wisely change the PFA to more expressive ones (by adding more states and transitions) and hope the solution can be found at some point.
+Then our procedure will restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and convert them to equisatisfiable linear formula.
+The details of the under-approximation component will be described in Section~\ref{section:under_approximate}.
+Here we try to explain what the linear formula looks like by an example.
+Assume that we project the domain of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.
+One special treatment we do in this paper is that we encoding characters as natural numbers.
+So $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
+For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
+
+The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$,  as well as, the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+Each model of the linear formula encodes a model of the string constraint.
+For example, $x=``12''$ and $y=``1212''$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
+
+If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the strings variables.
+If not, our procedure step-wisely change the PFA to more expressive ones (by adding more states and transitions) to systematically search for the solution.
+Depending on the implementation, one may choose to report unknown after some certain steps.
 
@@
 \begin{enumerate}
-	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a stright path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a straight path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
 %, with pairwise distiand states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
@@
 Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
-Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all modesl of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated byt the following collolary of Lemma~\ref{lemma:decx}:
+Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all modesl of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated byt the following corollary of Lemma~\ref{lemma:decx}:
 %

### 2019-11-12 draft.tex
polish prelimeary

@@
 
-A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_i$ is the \emph{initial state}, and $q_f$ is the \emph{final state}.
+A \emph{finite automaton} (FA) is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_i$ is the \emph{initial state}, and $q_f$ is the \emph{final state}.
 %The semantics of finite automaton is defined in the standard manner. 
@@
 
-Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.   
-Given a linear formula $\phi$, a set of variables $V$ that includes all variables occurring in $\phi$, and an \emph{interpretation} of $V$, a function $I:V\rightarrow \nat$, 
-we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a model of $\phi$ over $V$.
+Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
+Given a linear formula $\phi$, a set of variables $V$ that includes all variables occurring in $\phi$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
+we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$.
 We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
 We drop the reference to $V$ and write just ``model of $\phi$'',  $\modelsof \phi$, and $\models$ when no confusion may arise.
+For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
 
-The \emph{Parikh image} of a wore $w\in \Sigma^*$ is the assignment 
+The \emph{Parikh image} of a string $w\in \Sigma^*$ is the assignment 
 $\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$.
@@
 %
-It is well known that $\parikhof A$ can be efficiently computed in the form of linear interger arithmetic formula:
+It is well known that $\parikhof A$ can be efficiently computed in the form of linear formula:
 
 \begin{lemma}[\cite{SeidlSMH04}]
-$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear interger arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
+$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} =_\Sigma \parikhof{A}$, in time linear to the size of $A$.
 \end{lemma}
@@
 
-The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulae and handled efficiently by an SMT solver. 
+The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulas and handled efficiently by an SMT solver. 
 \lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
@@
 %
-A minor technical difficulty is that we wish to work with pure arithmetic formulae, 
+A minor technical difficulty is that we wish to work with pure arithmetic formulas, 
 but we may also wish to specify when a character variable is assigned $\epsilon$, which is not a number. 
-Hence, to allow purely arithmetic formulae to talk about the value $\epsilon$, we encode $\epsilon$ as $-1$.
-In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulae constraining interpretations of character variables.
+Hence, to allow purely arithmetic formulas to talk about the value $\epsilon$, we encode $\epsilon$ as $-1$.
+In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulas constraining interpretations of character variables.
 
@@
 We use $\#(v_i)$ and $\#(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
-The following formulae establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
+The following formulas establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
 \begin{enumerate}

### 2019-11-12 draft.tex
polish under-approx

@@
 \begin{lemma}[\cite{SeidlSMH04}]
-$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} =_\Sigma \parikhof{A}$, in time linear to the size of $A$.
+$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A}_{\#\Sigma} = \parikhof{A}$, in time linear to the size of $A$.
 \end{lemma}
@@
 %
-We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V_\Sigma$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an PFA is the semantics of its language.
+We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an PFA is the semantics of its language.
 
-The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear integer arithmetic formulas and handled efficiently by an SMT solver. 
-\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
+The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver. 
+\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}\yfc{The two sentences below read a bit strange, maybe need to rephrase it.}
 %
 Achieving this was the purpose of introducing the structural constraints of PFA. 
-Their implication central for our method is that every parametric string $x\in L(A)$ is uniquelly determined by its Parikh image $\parikhof{x}$, as formalised by the following lemma.
+Their implication central for our method is that every parametric string $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, as formalized by the following lemma.
 
@@
 
-Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$,
+\yfc{Maybe we use things like $I_{\#}$ to replace $\pim$?
+It reads a bit strange when you put together $I$ and $\pim$, one is greek symbol and the other is roman, but both of them are interpretations.}
+
+Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character variables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$,
 we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encodes $w$.
-Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
-Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all modesl of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated byt the following corollary of Lemma~\ref{lemma:decx}:
+Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$.
+Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
 %
@@
 
-\paragraph{Synchronisation of PFA}
-The following construction is an important step in building underapproximations of string constraints. 
+\paragraph{Synchronization of PFA}
+The following construction is an important step in building under-approximations of string constraints. 
 For two PFA $A$ and $A'$ over character variables $V$ and $V'$, respectively, 
-it builds \emph{synchronisation formula} $\syncfof A {A'}$, a linear formula over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. 
+it builds \emph{synchronization formula} $\syncfof A {A'}$, a linear formula over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. 
 Besides the intersection itself, it also represents the set of all pairs of string encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
@@
 
-Particularly, a synchronisation formula is build for two PFA  
+Particularly, a synchronization formula is build for two PFA  
 $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
@@
 %The we define of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
-The synchronisation formula $\syncfof{A} {A'}$ is extracted from $\syncof A {A'}$ as follows.
+The synchronization formula $\syncfof{A} {A'}$ is extracted from $\syncof A {A'}$ as follows.
 Its first part is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all runs of the product.
@@
 %\end{enumerate}
-The synchronisation formula is then the conjunction 
+The synchronization formula is then the conjunction 
 $$
@@
 The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect} below.
-The lemma can also be understood as a precise specification the semantics of the synchronisation formula, on which we rely for correctness of the construction of underapproximations of string constraints.
+The lemma can also be understood as a precise specification the semantics of the synchronization formula, on which we rely for correctness of the construction of underapproximations of string constraints.
 %

### 2019-11-12 draft.tex
polish pfa

@@
 \newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
-\newcommand{\pim}{\alpha}
+\newcommand{\pim}{I_{\#}}
 %\newcommand{\syncop}{\Cap}
@@
 usually, it suffices to find a solution using a small $k$ for a satisfiable 
-constraint. Note that a 64-bit integer number corresponds to a string with 
+constraint. Note that a 64-bit integer number corresponds to a word with 
 $k\leq 21$.
@@
 
-If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the strings variables.
+If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
 If not, our procedure step-wisely change the PFA to more expressive ones (by adding more states and transitions) to systematically search for the solution.
@@
 $\{k\mid n\leq k \leq m\}$. 
-An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{string} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty string}.
-We use $w_1\cdot w_2$ to denote the \emph{concatenation} of strings $w_1$ and $w_2$.
-$\Sigma^*$ is the set of all strings over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$, and 
+An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{word} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty word}.
+We use $w_1\cdot w_2$ to denote the \emph{concatenation} of words $w_1$ and $w_2$.
+$\Sigma^*$ is the set of all words over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$, and 
 A \emph{language} over $\Sigma$ is a subset $L$ of $\Sigma^*$.  
@@
 
-The \emph{Parikh image} of a string $w\in \Sigma^*$ is the assignment 
+The \emph{Parikh image} of a word $w\in \Sigma^*$ is the assignment 
 $\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$.
@@
 
-An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a string $|x|$ for all $x \in \vars$.
+An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a word $|x|$ for all $x \in \vars$.
 %Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
@@
 In each step, we take a string constraint from $\phi_s$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints.
-The procedure for equality, disequality, and membership constraints is in Section~\ref{section:eq} and the one for string/integer conversion is in Section~\ref{section:s2i}.
+The procedure for equality, disequality, and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.
 
@@
 %Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
-Parametric automata accept strings over $\cvar$, called \emph{parametric strings}, but we still use them as representations of languages over $\Sigma$. 
+Parametric automata accept words over $\cvar$, called \emph{parametric words}, but we still use them as representations of languages over $\Sigma$. 
 %
-Namely, string over $\cvar$ are interpreted as strings over $\Sigma$ given an assignment of characters to its character variables.  
+Namely, word over $\cvar$ are interpreted as words over $\Sigma$ given an assignment of characters to its character variables.  
 %
-Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a parametric string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 %
@@
 Achieving this was the purpose of introducing the structural constraints of PFA. 
-Their implication central for our method is that every parametric string $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, as formalized by the following lemma.
+Their implication central for our method is that every parametric word $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, as formalized by the following lemma.
 
@@
 
-\yfc{Maybe we use things like $I_{\#}$ to replace $\pim$?
-It reads a bit strange when you put together $I$ and $\pim$, one is greek symbol and the other is roman, but both of them are interpretations.}
-
-Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character variables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$,
-we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encodes $w$.
-Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$.
-Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
+Since every word $w \in \semof{A}$ is obtained from a parametric word $x\in L(A)$ and an interpretation of character variables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$,
+we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric word $x$ encodes $w$.
+Lemma~\ref{lemma:parikh} also implies that two different words are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$.
+Encodings of words in $\semof{A}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
 %
@@
 \paragraph{Synchronization of PFA}
-The following construction is an important step in building under-approximations of string constraints. 
 For two PFA $A$ and $A'$ over character variables $V$ and $V'$, respectively, 
 it builds \emph{synchronization formula} $\syncfof A {A'}$, a linear formula over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
-Besides the intersection itself, it also represents the set of all pairs of string encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
-$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$ which constitute the intersection.
+The synchronization formula will be used in, e.g., the decision procedure of equality constraints $t_1=t_2$ to find a common interpretation of $t_1$ and $t_2$.
+More precisely, the models of the synchronization formula $\syncfof A {A'}$ correspond to the set of all pairs of word encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that
+$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$, which constitute the intersection.
 
@@
 Every accepting run of $\syncof A {A'}$ corresponds to a pair of accepting runs, 
-a run of $A$ over a parametric string $x$ and a run of ${A'}$ over a parametric string $x'$. 
-The word accepted by the run of $\syncof A {A'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric strings have the same interpretation, i.e.
+a run of $A$ over a parametric word $x$ and a run of ${A'}$ over a parametric word $x'$. 
+The word accepted by the run of $\syncof A {A'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric words have the same interpretation, i.e.
 $I(x) = I(x')$.
 
-Intuitively, when $\syncof A {A'}$ takes a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$, 
+Intuitively, when the product automaton $\syncof A {A'}$ takes a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$, 
 it means the character variable $v$ and $v'$ should be assigned the same value,
@@
 it means that the character variable $v$ should be assigned $\epsilon$, 
-$A$ transitions under $v$ to $q_1$, and ${A'}$ takes no action, since no action is needed to match $A$s reading $\epsilon$ (hence not reading the input word).
+$A$ transitions under $v$ to $q_1$, and ${A'}$ takes no action, since no action is needed to match $A$'s reading of $\epsilon$ (hence consumes no symbol from the input word).
 Symmetrically, ${A'}$ might read a variable $v$ assigned $\epsilon$ and $A$ may stay.
@@
 %\end{enumerate}
-Finally, the third part forces the interpretations of the parametric strings accepted by $A$ and $A'$ be the same:
+Finally, the third part forces the interpretations of the parametric words accepted by $A$ and $A'$ to be the same:
 % condition 1.
@@
 The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect} below.
-The lemma can also be understood as a precise specification the semantics of the synchronization formula, on which we rely for correctness of the construction of underapproximations of string constraints.
+The lemma can also be understood as a precise specification the semantics of the synchronization formula, on which we rely for correctness of the construction of under-approximations of string constraints.
 %
@@
 \syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
-$\semof {\exists V_\times . \syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
+$\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
 \end{lemma}
 %
-Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{B}$, that constitute the intersection $\semof{A} \cap \semof{B}$.
+Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{A'}$, that constitute the intersection $\semof{A} \cap \semof{A'}$.
 A minor technical difficulty is that the modes of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $V_\times = (\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
 Hence in the lemma, we have to restrict the models to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
-This is  achieve by quantifying out the variables of $V_\times$.
+%This is  achieve by quantifying out the variables of $V_\times$.
 

### 2019-11-12 evaluation.tex
a note about PyEx

@@
 This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports.
-Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to parse input formulae.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.
 
@@
 Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test.
-The modified test is re-evaluated by solvers and if the solvers decide that the modified test is satisfiable, the answer of the solvers that originally reported unsat is evaluated as incorrect.
+The modified test is re-evaluated by solvers.
+If the solvers decide that the modified test is satisfiable, the answer of the solvers that initially reported unsat is evaluated as incorrect.
+
+\paragraph{A Comparison with other tools on well-known benchmarks.}
+In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in many cases even better.
+This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that was created by others and that contain a very few formulae with constraints of string-number and number-string conversion.
+
+The first benchmark is called PyEx according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing.
+This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests.
+PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.
+Although this benchmark was created by cvc4 group and cvc4 solved more SAT cases than the other tools, z3-trau was behind by less than 1\textperthousand\ of cases and moreover managed to solve the most UNSAT cases.
 

### 2019-11-13 draft.tex
polish a bit intro and under-approximation

@@
 
-	 	\caption{Encoding \texttt{Split(x,y)} using recursive functions and the array theory.
+	 	\caption{Encoding \texttt{Split(x,y)} to an SMTLIB2 formula using recursive functions and the array theory.
 The recursive function \texttt{split (x y 0 0)} returns an array of type \texttt{(Array Int String)} that maps an index $i$ to the $i$th component (separated by the character $y$ ) of $x$.}
@@
 \section{Under-approximation} \label{section:under_approximate}
-In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_s$ to a set of equisatisfiable linear integer constraints $\phi_I$ in polynomial-time.
-We first pick a PFA for each variable in $\vars$ and then construct the set of linear integer constraints in a stepwise manner.
-In each step, we take a string constraint from $\phi_s$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints.
-The procedure for equality, disequality, and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.
+In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_I$ to a set of equisatisfiable linear formulas $\phi_O$ in polynomial-time.
+We assume all disequality constraint $t_1 \neq t2 \in \phi_d$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
+
+We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
+In each step, we take a string constraint from $\phi_I$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\phi_O$.
+
+More concretely, at the beginning, we move all integer constraints in $\phi_I$ to the output linear formulas $\phi_O$.
+After this step, $\phi_I$ is the union of the three sets of constraints $\phi_e$ (equality), $\phi_m$ (membership), and $\phi_s$ (string-number conversion).
+For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x} \in \phi_s$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA and we do not set any restriction to the selection of PFA for other string variables, i.e., the selection is an implementation decision.
+We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
+
+After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\phi_I$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\phi_O$.
+The procedure for equality and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.
+
+\hide{We replace it with the following constraints.
+
+	$$
+	\begin{array}{c}
+	(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
+	\left(
+	\begin{array}{cccc}
+
+	y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
+	y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
+	|y_2|&=&|y'_2|=1
+	\end{array}
+
+	\right)
+	\end{array}
+	$$
+
+	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
+In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
+}
 
@@
 
-\subsection{Flat Under-approximation for Equalities and Regular Constraints} \label{section:eq}
+\subsection{Handling Equalities and Regular Constraints Symbolically} \label{section:eq}
 
@@
 
-Disequality constraint $x_1\cdot x_2 \cdots x_n \neq x_{n+1}\cdot x_{n+2} \cdots x_m$ can be converted to equal-satisfiable equality constraints in the standard way~\cite{abdulla2015norn}.
-We replace it with the following constraints.
-
-$$
-\begin{array}{c}
-(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
-\left(
-	\begin{array}{cccc}
-
-	 y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
-	 y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
-	|y_2|&=&|y'_2|=1
-	\end{array}
-
-\right)
-\end{array}
-$$
-
-The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
-In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
-
 \todo{Maybe talk about the heuristic that we merge the list elements into one}

### 2019-11-13 evaluation.tex
description to benchmarks

@@
 
-\paragraph{A Comparison with other tools on well-known benchmarks.}
-In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in many cases even better.
-This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that was created by others and that contain a very few formulae with constraints of string-number and number-string conversion.
+\paragraph{A Comparison with other tools on conversion-less benchmarks.}
+This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups.
+In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in some cases even better.
 
-The first benchmark is called PyEx according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing.
+The first benchmark is called PyEx~\cite{pyex} according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing.
 This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests.
 PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.
-Although this benchmark was created by cvc4 group and cvc4 solved more SAT cases than the other tools, z3-trau was behind by less than 1\textperthousand\ of cases and moreover managed to solve the most UNSAT cases.
+
+The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}.
+The benchmark includes a total of 600 hand-drafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.
+
+The next benchmark is called LeetCode~\cite{LeetCode} that was obtained by extracting constraints from Python's testing solutions provided by LeetCode platform.
+They provide many programming examples and their solutions gathered from technical interviews for companies.
+Leetcode consists of 881 satisfiable and 1785 unsatisfiable tests that, like PyEx, contain diverse string constraints.
+
+StringFuzz is our next bechmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
+We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.
+
+The last two benchmarks, called $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$, are obtained from cvc4 group~\cite{termEQ}.
+This set of benchmarks consists of the verification of term equivalences over strings and includes various string constraints including string-number and number-string conversion constraints.
 

### 2019-11-13 draft.tex
polish 5.2, still need membership constraints

@@
 
-Here we try to explain the approach using a toy example $\phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$.
-Notice that $\phi$ is satisfiable.
+Here we try to explain the approach using a toy example $\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$.
+Notice that $\Phi$ is satisfiable.
 E.g., it has a model $x=``12''$ and $y=``1212''$.
@@
 This produce new formulas that over-approximate the original ones and fall in the acyclic fragment~\cite{abdulla2014string}, which is decidable.
-Since $\phi$ is satisfiable, the over-approximation module will not return UNSAT.
+Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
 
@@
 
-A \emph{string constraint} is a constraint of the above form. We say that a set of string constraint $\phi$ is \emph{satisfiable}  iff $\bigcap_{\pi \in \phi} \modelsof{\pi}$ is not empty.
+A \emph{string constraint} is a constraint of the above form. We say that a set of string constraint $\Phi$ is \emph{satisfiable}  iff $\bigcap_{\phi \in \Phi} \modelsof{\phi}$ is not empty.
 
@@
 \section{Under-approximation} \label{section:under_approximate}
-In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\phi_I$ to a set of equisatisfiable linear formulas $\phi_O$ in polynomial-time.
-We assume all disequality constraint $t_1 \neq t2 \in \phi_d$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
+In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\Phi_I$ to a set of equisatisfiable linear formulas $\Phi_O$ in polynomial-time.
+We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
 
 We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
-In each step, we take a string constraint from $\phi_I$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\phi_O$.
+In each step, we take a string constraint from $\Phi_I$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\Phi_O$.
 
-More concretely, at the beginning, we move all integer constraints in $\phi_I$ to the output linear formulas $\phi_O$.
-After this step, $\phi_I$ is the union of the three sets of constraints $\phi_e$ (equality), $\phi_m$ (membership), and $\phi_s$ (string-number conversion).
-For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x} \in \phi_s$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA and we do not set any restriction to the selection of PFA for other string variables, i.e., the selection is an implementation decision.
+More concretely, at the beginning, we move all integer constraints in $\Phi_I$ to the output linear formulas $\Phi_O$.
+After this step, $\Phi_I$ is the union of the three sets of constraints: the equality constraints, the membership constraints, and the string-number conversion constraints.
+For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA.
+We do not set any restriction to the selection of PFA for other string variables.
+The selection is an implementation decision.
 We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
 
-After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\phi_I$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\phi_O$.
+After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\Phi_I$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\Phi_O$.
 The procedure for equality and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.
@@
 
-The correctness of this construction is expressed by Lemma~\ref{lemma:synccorrect} below.
+The correctness of this construction is stated in Lemma~\ref{lemma:synccorrect} below.
 The lemma can also be understood as a precise specification the semantics of the synchronization formula, on which we rely for correctness of the construction of under-approximations of string constraints.
@@
 
-\lh{removed the closed under concatenation lemma, no more true due to epsilons}
+\yfc{we need to define \#{V} somewhere}
 
@@
 %\end{lemma}
-
-\subsection{Handling Equalities and Regular Constraints Symbolically} \label{section:eq}
-
-Given an equality constraint $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, we restrict the domain of all variables to some PFA with disjoint alphabet and then connect the final state and initial state of two consecutive variables with an epsilon transition.
-We rename the variables on the transitions of PFA's for different occurrences of the same variable in one equality constraint.
-Later we will use some arithmetic constraints to enforce that all occurrences of the variants of the same variable will be assigned the same value.
-For notational convenience, the renaming is done by adding a version number to the variable.
-For example, we can rename $v_1$ to $v_1^{(0)}$, $v_1^{(1)}$, $\ldots$.
-
-For the constraint $xy = yx$, we first restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$.
 
@@
 		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
-	\draw[->] (q0) edge  node [below]{$\epsilon$} (q1) ;
+		\draw[->] (q0) edge  node [below]{$v_{\epsilon_0}$} (q1) ;
 		\end{tikzpicture}
@@
 		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
-	\draw[->] (q1) edge  node [below]{$\epsilon$} (q0) ;
+		\draw[->] (q1) edge  node [below]{$v_{\epsilon_1}$ }(q0) ;
 		\end{tikzpicture}
@@
 
-	\caption{Symbolic flat automata of $x$, $y$, $xy$ and $yx$}
+	\caption{Parametric flat automata of $x$, $y$, $xy$ and $yx$}
 	\label{fig:sfa}
@@
 
+\subsection{Handling Equalities and Membership Constraints Symbolically} \label{section:eq}
+
+Assume that the constraint we take from $\Phi_I$ is an equality constraint $\phi_e= x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, where each string variable $x_i$ is restricted to a PFA $A_{i}$ with the set of character variables $V_{i}$, for $i\in[1,m]$.
+We first build two PFAs that encode the left-hand side term and the right-hand side term of the equality constraint.
+Intuitively, this can be achieved by connecting the PFAs of the string variables with epsilon transitions.
+However, there are two minor technical issues.
+First, our definition of PFA does not allow epsilon transition.
+Second, some string variable might occur multiple times in a equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
+
+We circumvent the first problem by introducing some fresh characters variables, say $v_{\epsilon_n}$, and forcing its value to be $\epsilon$ by adding new linear formulas, say $v_{\epsilon_n}= -1$, to the output linear formulas $\phi_O$.
+Then we can connect the final state and initial state of two consecutive variables with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_n}$.
+We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
+
+For the second problem, we rename the variables on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
+The renaming is done by adding a version number to the variable.
+We call variables before and after renaming the \emph{original variable} and the \emph{renamed variable}.
+For example, we can rename $v_1$ to $v_1^{(0)}$, $v_1^{(1)}$, etc.
+In this case, $v_1$ is the original variable and both $v_1^{(0)}$ and $v_1^{(1)}$ are the renamed variables.
+For an original variable $v$, we use $R_v$ to denote the set of variables renamed from $v$.
+Later we will add arithmetic constraints to enforce that variables obtained from the same original variable are assigned the same value.
+
+Here we give a concrete example.
+For the equality constraint $xy = yx$, assume that we restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon'' transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
+
+Now let $A$ and $A'$ over character variables $V$ and $V'$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$.
+We then construct the synchronization formula $\syncfof A {A'}$ and add it to $\phi_O$.
+Recall that from Lemma~\ref{lemma:synccorrect}, each model of $\syncfof A {A'}$ corresponds to a pair of words in $\semof{A}$ and $\semof{A'}$.
+However, this does not directly correspond to a model of the equality constraint $\phi_e$.
+The reason is that difference occurrence of the same string variables can be assigned different values in $\semof{A}$ and $\semof{A'}$.
+To avoid this problem, we need to add more constraints to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
+
+$$ \Psi_r \defeq
+\bigwedge_{v\in V_x, v'\in R_v} v=v' \wedge \#v = \#v'
+$$
+Here $V_x$ is the set of all character variables occurred in the PFAs of $x_1,x_2,\ldots,x_m$, i.e., $V_x=\bigcup_{i\in [1,m]}{V_{i}}$.
+
+The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect}.
+
+\begin{lemma}\label{lemma:eqcorrect}
+	%$\semof {\exists V_\times .
+\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
+	$\semof {\syncfof A {A'}  \wedge \Psi_r}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo \setminus V_{\epsilon}} = \{\bigcup_{i\in[1,m]}(I^i\cup\pim^i)\mid w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m \wedge \bigwedge_{i\in [1,m]}w_i=\decode A_{i}(I^i\cup\pim^i) \}$.
+\end{lemma}
+
+\hide{
 Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the PFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the PFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
@@
 \todo{Maybe talk about the heuristic that we merge the list elements into one}
+
+}
 

### 2019-11-13 draft.tex
polish 5.2 and 5.3

@@
 For the purpose of program analysis, string solver also needs to support \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{membership constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$).
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$).
 Most of the standard string operations can be encoded using the above three types of constraints.
@@
 Our string constraint solving produce can be easily integrated in a \emph{satisfiability module theory (SMT)} solver as a theory solver.
-The integration allows us to express string operations that cannot be reduced to the type of constraints (membership, equality, integer, string-number conversion) supported by our procedure.
+The integration allows us to express string operations that cannot be reduced to the type of constraints (regular, equality, integer, string-number conversion) supported by our procedure.
 For example, we can encode \texttt{split} using the code fragment in Figure~\ref{fig:smt_string}.
@@
 To ease presentation, in the paper, we only consider string constraints consisting of \emph{equality constraints (a.k.a.
-word equation)}, \emph{membership constraints}, \emph{length constraints}, and \emph{string-number conversion} functions.
+word equation)}, \emph{regular constraints}, \emph{length constraints}, and \emph{string-number conversion} functions.
 
@@
 
-A \emph{membership constraint} $\phi_m$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
+A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
 The \emph{model} of $\phi_m$ is the set of interpretations $\modelsof{\phi_m}=\{I\mid
@@
 More concretely, at the beginning, we move all integer constraints in $\Phi_I$ to the output linear formulas $\Phi_O$.
-After this step, $\Phi_I$ is the union of the three sets of constraints: the equality constraints, the membership constraints, and the string-number conversion constraints.
+After this step, $\Phi_I$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
 For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA.
@@
 After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\Phi_I$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\Phi_O$.
-The procedure for equality and membership constraints is in Section~\ref{section:eq} and the one for string-number conversion is in Section~\ref{section:s2i}.
+The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
 
@@
 
-\yfc{say handling membership constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
+\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
 
@@
 %\end{lemma}
+In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
 
@@
 
-\subsection{Handling Equalities and Membership Constraints Symbolically} \label{section:eq}
-
-Assume that the constraint we take from $\Phi_I$ is an equality constraint $\phi_e= x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$, where each string variable $x_i$ is restricted to a PFA $A_{i}$ with the set of character variables $V_{i}$, for $i\in[1,m]$.
+\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
+Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
+Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
+First we create a PFA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
+The set of transitions $T'$ and character variables $V'$ can be obtained by the following procedure.
+Initially, both $V'$ and $T'$ are empty sets.
+For each transition $(q, a, q') \in T$, we add a fresh character variable $v$ to $V'$, add the transition $(q,v,q')$ to $T'$, and add the constraint $v = \modelsof{a}$ to $\Phi_O$.
+Recall that $\modelsof{a}$ is the numerical encoding of the character $a$.
+After $A'$ is built, we add the synchronization formula $\syncfof {A_x }{A'}$ to $\Phi_O$.
+
+The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+\begin{lemma}\label{lemma:memcorrect}
+	%$\semof {\exists V_\times .
+\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
+	${\semof {\syncfof {A_x }{A'}}}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
+
+\subsection{Handling Equality Constraints Symbolically} \label{section:eq}
+
+Assume that the constraint we take from $\Phi_I$ is an equality constraint $\phi_e\defeq x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$.
 We first build two PFAs that encode the left-hand side term and the right-hand side term of the equality constraint.
@@
 Then we can connect the final state and initial state of two consecutive variables with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_n}$.
-We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
+%We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
 
@@
 Now let $A$ and $A'$ over character variables $V$ and $V'$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$.
-We then construct the synchronization formula $\syncfof A {A'}$ and add it to $\phi_O$.
+We then construct the synchronization formula $\syncfof A {A'}$ and add it to $\Phi_O$.
 Recall that from Lemma~\ref{lemma:synccorrect}, each model of $\syncfof A {A'}$ corresponds to a pair of words in $\semof{A}$ and $\semof{A'}$.
@@
 The reason is that difference occurrence of the same string variables can be assigned different values in $\semof{A}$ and $\semof{A'}$.
-To avoid this problem, we need to add more constraints to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
+To avoid this problem, we need to add the constraint $\Psi_r$ below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
 
 $$ \Psi_r \defeq
-\bigwedge_{v\in V_x, v'\in R_v} v=v' \wedge \#v = \#v'
+\bigwedge_{v\in V_X, v'\in R_v} v=v' \wedge \#v = \#v'
 $$
-Here $V_x$ is the set of all character variables occurred in the PFAs of $x_1,x_2,\ldots,x_m$, i.e., $V_x=\bigcup_{i\in [1,m]}{V_{i}}$.
+Here $V_X$ is the set of all character variables occurred in the PFAs of $x_1,x_2,\ldots,x_m$, i.e., $V_X=\bigcup_{i\in [1,m]}{V_{x_i}}$.
 
@@
 \begin{lemma}\label{lemma:eqcorrect}
-	%$\semof {\exists V_\times .
-\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
-	$\semof {\syncfof A {A'}  \wedge \Psi_r}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo \setminus V_{\epsilon}} = \{\bigcup_{i\in[1,m]}(I^i\cup\pim^i)\mid w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m \wedge \bigwedge_{i\in [1,m]}w_i=\decode A_{i}(I^i\cup\pim^i) \}$.
+	$\semof {\syncfof A {A'}  \wedge \Psi_r}_{V_X \cup \#V_X} = \{\bigcup_{i\in[1,m]}(I^i\cup\pim^i)\mid w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m \wedge \bigwedge_{i\in [1,m]}w_i=\decode A_{x_i}(I^i\cup\pim^i) \}$.
 \end{lemma}

### 2019-11-14 draft.tex
fix a compile bug
property of product, just for discussion
another version of Lemma 5.4 for PA x PA
typo
note below another version of L 5.4

@@
 %
-\begin{corollary}
+\begin{corollary}\label{corollary:pfa}
 For an PFA $A$ over character variables $V$,
@@
 %
-%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
 \begin{lemma}\label{lemma:synccorrect}
@@
 %
+Another version:
+\begin{lemma}
+$
+\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = 
+\{
+(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
+x\in L(A), x'\in L(A'), I(x) = I(x')
+\}
+$
+\end{lemma}
+Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then $\semof A \cap \semof {A'}$ can be still decoded from $\semof {\syncfof A {A'}}$ due to Corollary~\ref{corollary:pfa}, 
+namely in the form of\\ $\semof A \cap \semof {A'} = \{\decode A(I\cup x) \mid \exists J.((I\cup x) \cup J) \in \semof{\syncfof A {A'}}\}$.  
+\bigskip
+
 Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{A'}$, that constitute the intersection $\semof{A} \cap \semof{A'}$.
@@
 
-\todo{Add an example: $\sti{x}=\sti{y} \wedge x= y\cdot y$. Do product construction informally here.}
-
 % \section{Evaluation}

### 2019-11-14 draft.tex
some  minor update

--- 2019-11-13 draft.tex
@@
 
-\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
-Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
-Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
-First we create a PFA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
-The set of transitions $T'$ and character variables $V'$ can be obtained by the following procedure.
-Initially, both $V'$ and $T'$ are empty sets.
-For each transition $(q, a, q') \in T$, we add a fresh character variable $v$ to $V'$, add the transition $(q,v,q')$ to $T'$, and add the constraint $v = \modelsof{a}$ to $\Phi_O$.
-Recall that $\modelsof{a}$ is the numerical encoding of the character $a$.
-After $A'$ is built, we add the synchronization formula $\syncfof {A_x }{A'}$ to $\Phi_O$.
-
-The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
-%
-%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
-\begin{lemma}\label{lemma:memcorrect}
-	%$\semof {\exists V_\times .
-\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
-	${\semof {\syncfof {A_x }{A'}}}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
-\end{lemma}
-
 \subsection{Handling Equality Constraints Symbolically} \label{section:eq}
@@
 
+\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
+
+\yfc{The version here is buggy, but fixable.
+I am not sure what is the best fix, so for now I just leave it here.
+The problem is we cannot synchronize a PFA and a general parametric automaton (which can be non-flat)}
+Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
+Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
+First we create a PFA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
+The set of transitions $T'$ and character variables $V'$ is defined as follows:
+
+\begin{itemize}
+	\item $V' = \{ v_{(q,a,q')} \mid (q,a,q')\in T\}$
+	\item $T' = \{ (q, v_{(q,a,q'), q') } \mid (q,a,q')\in T\}$
+\end{itemize}
+We use the linear formula $\phi_c \defeq \bigwedge_{(q,a,q')\in T} {v_{(q,a,q')} = a}$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
+The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
+
+\begin{lemma}\label{lemma:fa_pfa}
+	$L(A) = ( {\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
+
+Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
+
+The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+\begin{lemma}\label{lemma:memcorrect}
+	$({\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this section, we discuss how to handle the constraint $n=\sti{x}$ by restricting the domain of $x$ to some PFA.
-Let us begin with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
+Assume that the constraint we take from $\Phi_I$ is a string-number conversion constraint  $\phi_s \defeq n=\sti{x}$. We will discuss how to make the corresponding linear formulas in this section.
+
+Let us begin the discussion with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
 Then we know that when $0\leq v_0,v_1 \leq 9$, then $n$ is a positive integer value, and otherwise $n =-1$.
@@
 
-Our first attempt is a PFA with no loop, i.e., a straight line structure (e.g., the PFA in Fig~\ref{fig:sfa_its} without the self-loop at $q_0$).
+Our first attempt is a PFA with no loop, i.e., a straight line structure.
 The corresponding integer constraint does not have exponential components.
@@
 	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
-	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$.
+	\end{tikzpicture}} should be sufficient for the domain restriction of $x$.
 If we do so, we will conclude that the formula is unsatisfiable, because the length of $x$ cannot be $5$  under this domain restriction.
@@
 In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a PFA in Figure~\ref{fig:sfa_its}.
-The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such PFA.
+The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $v_0=0$ to $\Phi_O$ for such PFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
@@
 Remember that the character variables can be assigned $\epsilon$.
-In order to handle such cases efficiently, we use an encoding that if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j,m]$, i.e., we shift all the $\epsilon$-transitions to the least significant digits.
-In order to explain this encoding, we first define two macro function:
+In order to simplify the construction, we an encoding to shift all the $\epsilon$-transitions to the least significant digits, i.e., if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j+1,m]$.
+To explain this encoding, we first define two macro function:
 
 $$\begin{array}{rl}
-\mathsf{epsilonAfter(k)}::=& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
+\mathsf{epsilonAfter(k)}\defeq& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
 &v_{k+1}=\ldots =v_m = -1\\
-\mathsf{toNumber(k)}::=& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
+\mathsf{toNumber(k)}\defeq& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
 \end{array}
@@
 Then we can specify the relation between $n$ and the character variables as follows:
-$$(n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
-It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$ .
+$$\phi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$.
+
+\yfc{add a Lemma for correctness}
 
@@
 \input{evaluation}
-
+\newpage
 \bibliographystyle{ACM-Reference-Format}

### 2019-11-14 draft.tex
some  minor update

@@
 We introduce \emph{parametric flat automata} (PFA) that will be used to define patterns 
-%for the string variable domain restriction. 
 used by the under-approximation module to restrict the domain of string variables. 
-Namely, an PFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over an alphabet $\cvar$ of \emph{character variables}, 
-and satisfying the following structural constraints:
+A \emph{parametric automaton} (PA) is a finite automaton operating over an alphabet $\cvar$ of \emph{character variables}. 
+A parametric flat automaton is a parametric automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ satisfying the following structural constraints:
 \begin{enumerate}
@@
 
-\paragraph{Synchronization of PFA}
-For two PFA $A$ and $A'$ over character variables $V$ and $V'$, respectively, 
+\paragraph{Synchronization of PAs}
+For two PAs $A$ and $A'$ over character variables $V$ and $V'$, respectively, 
 it builds \emph{synchronization formula} $\syncfof A {A'}$, a linear formula over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
@@
 
-Particularly, a synchronization formula is build for two PFA  
+Particularly, a synchronization formula is build for two PAs  
 $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
@@
 %
+\hide{
 \begin{lemma}\label{lemma:synccorrect}
@@
 %
-Another version:
-\begin{lemma}
+Another version:}
+\begin{lemma}\label{lemma:synccorrect}
 $
@@
 Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then $\semof A \cap \semof {A'}$ can be still decoded from $\semof {\syncfof A {A'}}$ due to Corollary~\ref{corollary:pfa}, 
-namely in the form of\\ $\semof A \cap \semof {A'} = \{\decode A(I\cup x) \mid \exists J.((I\cup x) \cup J) \in \semof{\syncfof A {A'}}\}$.  
-\bigskip
+namely in the form of $\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.
 
@@
 %\end{lemma}
+
+\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
+
+Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
+Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
+First we create a PA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
+The set of transitions $T'$ and character variables $V'$ is defined as follows:
+
+\begin{itemize}
+	\item $V' = \{ v_{(q,a,q')} \mid (q,a,q')\in T\}$
+	\item $T' = \{ (q, v_{(q,a,q'), q') } \mid (q,a,q')\in T\}$
+\end{itemize}
+We use the linear formula $\phi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
+The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
+
+\begin{lemma}\label{lemma:fa_pfa}
+	$L(A) =  \{  \decode {A'}(I\cup\pim) \mid (I\cup\pim)\in  {\semof {\parikhfof {A'} \wedge \phi_c}} _{V' \cup \#V'} \}$. 
+\end{lemma}
+
+Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
+
+The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+\begin{lemma}\label{lemma:memcorrect}
+	$({\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
 
@@
 
-\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
-
-\yfc{The version here is buggy, but fixable.
-I am not sure what is the best fix, so for now I just leave it here.
-The problem is we cannot synchronize a PFA and a general parametric automaton (which can be non-flat)}
-Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
-Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
-First we create a PFA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
-The set of transitions $T'$ and character variables $V'$ is defined as follows:
-
-\begin{itemize}
-	\item $V' = \{ v_{(q,a,q')} \mid (q,a,q')\in T\}$
-	\item $T' = \{ (q, v_{(q,a,q'), q') } \mid (q,a,q')\in T\}$
-\end{itemize}
-We use the linear formula $\phi_c \defeq \bigwedge_{(q,a,q')\in T} {v_{(q,a,q')} = a}$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
-The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
-
-\begin{lemma}\label{lemma:fa_pfa}
-	$L(A) = ( {\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
-\end{lemma}
-
-Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
-
-The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
-%
-%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
-\begin{lemma}\label{lemma:memcorrect}
-	$({\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
-\end{lemma}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\paragraph{PFA that allows efficient string-integer conversion: } In the previous discussion, we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
+\paragraph{PFA that allows efficient string-number conversion: } In the previous discussion, we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
 The problem is that each loop in the PFA creates an exponential component.

### 2019-11-14 draft.tex
don't know

--- 2019-11-14 draft.tex
@@
 Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then $\semof A \cap \semof {A'}$ can be still decoded from $\semof {\syncfof A {A'}}$ due to Corollary~\ref{corollary:pfa}, 
-namely in the form of\\ $\semof A \cap \semof {A'} = \{\decode A(I\cup x) \mid \exists J.((I\cup x) \cup J) \in \semof{\syncfof A {A'}}\}$.  
+namely in the form of\\ $\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid \exists J.((I\cup \pim) \cup J) \in \semof{\syncfof A {A'}}\}$.  
 \bigskip
@@
 \end{figure*}
+
+\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
+Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
+Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
+First we create a PFA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
+The set of transitions $T'$ and character variables $V'$ can be obtained by the following procedure.
+Initially, both $V'$ and $T'$ are empty sets.
+For each transition $(q, a, q') \in T$, we add a fresh character variable $v$ to $V'$, add the transition $(q,v,q')$ to $T'$, and add the constraint $v = \modelsof{a}$ to $\Phi_O$.
+Recall that $\modelsof{a}$ is the numerical encoding of the character $a$.
+After $A'$ is built, we add the synchronization formula $\syncfof {A_x }{A'}$ to $\Phi_O$.
+
+The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+\begin{lemma}\label{lemma:memcorrect}
+	%$\semof {\exists V_\times .
+\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
+	${\semof {\syncfof {A_x }{A'}}}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
 
@@
 
-Assume that the constraint we take from $\Phi_I$ is a string-number conversion constraint  $\phi_s \defeq n=\sti{x}$. We will discuss how to make the corresponding linear formulas in this section.
-
-Let us begin the discussion with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
+In this section, we discuss how to handle the constraint $n=\sti{x}$ by restricting the domain of $x$ to some PFA.
+Let us begin with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
 Then we know that when $0\leq v_0,v_1 \leq 9$, then $n$ is a positive integer value, and otherwise $n =-1$.
@@
 
-Our first attempt is a PFA with no loop, i.e., a straight line structure.
+Our first attempt is a PFA with no loop, i.e., a straight line structure (e.g., the PFA in Fig~\ref{fig:sfa_its} without the self-loop at $q_0$).
 The corresponding integer constraint does not have exponential components.
@@
 	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
-	\end{tikzpicture}} should be sufficient for the domain restriction of $x$.
+	\end{tikzpicture}}, should be sufficient for the domain restriction of $x$.
 If we do so, we will conclude that the formula is unsatisfiable, because the length of $x$ cannot be $5$  under this domain restriction.
@@
 In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a PFA in Figure~\ref{fig:sfa_its}.
-The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $v_0=0$ to $\Phi_O$ for such PFA.
+The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we always add a constraint $v_0=0$ for such PFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
@@
 Remember that the character variables can be assigned $\epsilon$.
-In order to simplify the construction, we an encoding to shift all the $\epsilon$-transitions to the least significant digits, i.e., if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j+1,m]$.
-To explain this encoding, we first define two macro function:
+In order to handle such cases efficiently, we use an encoding that if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j,m]$, i.e., we shift all the $\epsilon$-transitions to the least significant digits.
+In order to explain this encoding, we first define two macro function:
 
 $$\begin{array}{rl}
-\mathsf{epsilonAfter(k)}\defeq& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
+\mathsf{epsilonAfter(k)}::=& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
 &v_{k+1}=\ldots =v_m = -1\\
-\mathsf{toNumber(k)}\defeq& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
+\mathsf{toNumber(k)}::=& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
 \end{array}
@@
 Then we can specify the relation between $n$ and the character variables as follows:
-$$\phi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
-It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$.
-
-\yfc{add a Lemma for correctness}
+$$(n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$ .
 
@@
 \input{evaluation}
-\newpage
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-11-14 draft.tex
some update to 5.3

--- 2019-11-14 draft.tex
@@
 \end{itemize}
-We use the linear formula $\phi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
+We use the linear formula $\Psi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
+We add both $\syncfof {A_x }{A'} $ and $\Psi_c$ to $\Phi_O$.
 The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
@@
 \begin{lemma}\label{lemma:fa_pfa}
-	$L(A) =  \{  \decode {A'}(I\cup\pim) \mid (I\cup\pim)\in  {\semof {\parikhfof {A'} \wedge \phi_c}} _{V' \cup \#V'} \}$. 
+	$L(A)=	\{  I(x) \mid  I\in  \semof {\Psi_c} \wedge x \in L(A') \} $. 
 \end{lemma}
 
-Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
-
-The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
+The correctness of this procedure is expressed in Lemma~\ref{lemma:memcorrect} below. 
 %
@@
 \begin{lemma}\label{lemma:memcorrect}
-	$({\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+	$\semof {\syncfof {A_x }{A'} \wedge \Psi_c}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
 \end{lemma}
+
+Lemma~\ref{lemma:memcorrect} follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}, and Lemma~\ref{lemma:fa_pfa}.
+Informally, the lemma says the models of the formula we add to $\Phi_O$, i.e.
+$\syncfof {A_x }{A'} \wedge \Psi_c$, characterize exactly the models of $x \in  L(A)$ under the restriction of $A_x$.
 
@@
 Then we can specify the relation between $n$ and the character variables as follows:
-$$\phi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+$$\Psi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
 It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
-
-\yfc{add a Lemma for correctness}
+We add $\Psi_n$ to $\Phi_O$.
+
+The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect_pos} and Lemma~\ref{lemma:sticorrect_neg} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$. 
+\yfc{The correctness lemmas are still buggy}
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+\begin{lemma}\label{lemma:sticorrect_pos}
+	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n\neq -1) }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
+\end{lemma}
+In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
+
+\begin{lemma}\label{lemma:sticorrect_neg}
+	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = \{I_n\mid (I_n(n) = -1\} \times \semof {\parikhfof {A_x} \wedge (v_0 = 0) }_{V_x \cup \#V_x} $
+\end{lemma}
+In this case, $x$
 

### 2019-11-14 draft.tex
some fix 5.4 and add 5.5 to handle string length

@@
 
-\todo{Maybe talk about the heuristic that we merge the list elements into one}
-
 }
@@
 $$\begin{array}{rl}
-\mathsf{epsilonAfter(k)}\defeq& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
+\mathsf{epsilonAfter(k)}\defeq& (0\leq v_1,\ldots, v_k\leq 9) \wedge\\
 &v_{k+1}=\ldots =v_m = -1\\
-\mathsf{toNumber(k)}\defeq& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
+\mathsf{toNumber(k)}\defeq& (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
 \end{array}
@@
 The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
+\yfc{say shifting $\epsilon$ to the right will not change the language}
+
+The condition that when $x$ is ``not a number'' is specified by the following formula.
+
+$$\Psi_{NaN} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
+
 Then we can specify the relation between $n$ and the character variables as follows:
-$$\Psi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+$$\Psi_n\defeq  (n=-1 \wedge \Psi_{NaN})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
 It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
@@
 \begin{lemma}\label{lemma:sticorrect_neg}
-	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = \{I_n\mid (I_n(n) = -1\} \times \semof {\parikhfof {A_x} \wedge (v_0 = 0) }_{V_x \cup \#V_x} $
+	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
+	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \in [0,9]^+  \}$
 \end{lemma}
-In this case, $x$
+In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.
+
+\subsection{Handling the lengths of variables}
+After the set $\Phi_I$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
+To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
+
+$$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
+
+More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\Phi_O$.
+
+$$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
 

### 2019-11-14 draft.tex

--- 2019-11-14 draft.tex
@@
 \newcommand{\decode}[1]{\mathit{decode_{#1}}}
-\newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
+%\newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
+\newcommand{\parikhfof}[1]{\Phi_{\mathbb{P}}(#1)} %shouldn't it be something that takes automaton as parameter and returns formula?
 \newcommand{\pim}{I_{\#}}
@@
 Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
-Given a linear formula $\phi$, a set of variables $V$ that includes all variables occurring in $\phi$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
+Given a linear formula $\phi$, a set of variables $V$ \lh{remove this?: that includes all variables occurring in $\phi$}, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
 we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$.
+\lh{Our use of indexing by $V$ in the text later is not very nice.
+Add this for clarity?: If $V$ contain additional variables not present in $\phi$, the these might be assigned arbitrary values by $I$.
+If $V$ is missing some of the variables of $\phi$, then it must be possible to complete $I$ with assignment of the missing variables into a satisfying assignment of $\phi$ (as in existential quantification).}
 We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
@@
 The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver. 
-\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}\yfc{The two sentences below read a bit strange, maybe need to rephrase it.}
-%
-Achieving this was the purpose of introducing the structural constraints of PFA. 
-Their implication central for our method is that every parametric word $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, as formalized by the following lemma.
+\lh{, allowing to circumvent more costly automata algorithms and decision procedures.
+Concretize and justify this better?}\yfc{The two sentences below read a bit strange, maybe need to rephrase it.}\lh{made an attempt}
+%
+This is facilitated by the structural constraints of PFA, which guarantee that 
+every parametric word $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, as formalized by the following lemma.
 
@@
 %
-The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. \lh{say precisely how?}
+The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. 
 %
@@
 We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
+%
 
@@
 For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
+\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
 \end{lemma}
+%
+\begin{proof}
+The function $\decode A$ can particularly be implemented as follows. Given $\pim:\pvars\rightarrow\nat$,
+and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m-1}$, 
+$\decode A(\pim)$ is constructed as the word $x_0 v_{0} \ldots v_{m-1} x_{m-1}$ where for each $i\in [0,m-1]$,
+$x_i = (v_i^0 \cdots v_i^{l_{i-1}})^{\pvarsof {v_i^0}}$ if $l_i >0$ and $x_i = \epsilon$ if $l_i = 0$. 
+\end{proof}
 
@@
 $\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$.
+%$\semof{A} = \{I(\decode A(\pim)) \mid \pim\in\semof{\parikhfof A},I:\cvars\rightarrow\Sigma_\epsilon\}$.
 \end{corollary}
@@
 \paragraph{Synchronization of PAs}
-For two PAs $A$ and $A'$ over character variables $V$ and $V'$, respectively, 
-it builds \emph{synchronization formula} $\syncfof A {A'}$, a linear formula over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$.
+\ \lh{changed the formulation of the next two paragraphs a bit, is it ok?}
+We will now discuss a construction of the \emph{synchronization formula} for two PAs $A$ and $A'$. 
+%over character variables $V$ and $V'$. 
+It is a linear formula $\syncfof A {A'}$ 
+%over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ 
+that specifies how each word in the semantic intersection $\semof A \cap \semof {A'}$ is encoded by $A$ and by $A'$.
+%
+More precisely, the models of $\syncfof A {A'}$ represent pairs of word
+encodings $(I\cup \parikhof{x})$ and $(I'\cup \parikhof{x'})$ such that $x\in L(A)$, $x'\in L(A')$, and 
+$I(x) = I'(x')$.
+% \in \semof{A}\cap\semof{A'}$.
 The synchronization formula will be used in, e.g., the decision procedure of equality constraints $t_1=t_2$ to find a common interpretation of $t_1$ and $t_2$.  
-More precisely, the models of the synchronization formula $\syncfof A {A'}$ correspond to the set of all pairs of word encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that
-$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$, which constitute the intersection.
-
-Particularly, a synchronization formula is build for two PAs  
+%More precisely, the models of the synchronization formula $\syncfof A {A'}$ correspond to the set of all pairs of word
+%encodings $(I\cup \parikhof{x})$ and $(I'\cup \parikhof{x'})$ such that $x\in L(A)$, $x'\in L(A')$, and 
+%$I(x) = I'(x') \in \semof{A}\cap\semof{A'}$.%, which constitute the intersection.
+% encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
+%$I(\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$, which constitute the intersection.
+
+Particularly, the synchronization formula is build for two PAs  
 $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
@@
 The word accepted by the run of $\syncof A {A'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric words have the same interpretation, i.e.
-$I(x) = I(x')$.
+$I(x) = I'(x')$.
 
@@
 The correctness of this construction is stated in Lemma~\ref{lemma:synccorrect} below.
-The lemma can also be understood as a precise specification the semantics of the synchronization formula, on which we rely for correctness of the construction of under-approximations of string constraints.
+The lemma can also be understood as a precise specification of the semantics of the synchronization formula, on which we rely for correctness of the construction of under-approximations of string constraints in Sections~\ref{section:mem}, \ref{section:eq}, and \ref{section:s2i}.
 %
@@
 \end{lemma}
-Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then $\semof A \cap \semof {A'}$ can be still decoded from $\semof {\syncfof A {A'}}$ due to Corollary~\ref{corollary:pfa}, 
-namely in the form of $\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.
-
 Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{A'}$, that constitute the intersection $\semof{A} \cap \semof{A'}$.
-A minor technical difficulty is that the modes of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $V_\times = (\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
+A minor technical difficulty is that the models of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
 Hence in the lemma, we have to restrict the models to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
 %This is  achieve by quantifying out the variables of $V_\times$.
+
+Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then the semantic intersection $\semof A \cap \semof {A'}$ can be still decoded from the synchronisation formula $\semof {\syncfof A {A'}}$.
+Namely, due to Corollary~\ref{corollary:pfa}, we have that $\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.
 
@@
 %\end{lemma}
+
+\lh{this following sentence appears to be in a wrong place here. Would be nicer in some introductory part to the underapproximation which talks about this, but I don't know where it should be.}
 In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
@@
 \yfc{we need to define \#{V} somewhere}
-
-%\begin{lemma}
-%	Symbolic flat automata are closed under concatenation.
-%\end{lemma}
+\lh{it is in prelims next to Parikh im. definition}
 
@@
 	\item $V' = \{ v_{(q,a,q')} \mid (q,a,q')\in T\}$
-	\item $T' = \{ (q, v_{(q,a,q'), q') } \mid (q,a,q')\in T\}$
+	\item $T' = \{ (q, v_{(q,a,q')}, q')  \mid (q,a,q')\in T\}$
 \end{itemize}
-We use the linear formula $\Psi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
-We add both $\syncfof {A_x }{A'} $ and $\Psi_c$ to $\Phi_O$.
+We use the linear formula $\phi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
 The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
@@
 \begin{lemma}\label{lemma:fa_pfa}
-	$L(A)=	\{  I(x) \mid  I\in  \semof {\Psi_c} \wedge x \in L(A') \} $. 
+	$L(A) =  \{  \decode {A'}(I\cup\pim) \mid (I\cup\pim)\in  {\semof {\parikhfof {A'} \wedge \phi_c}} _{V' \cup \#V'} \}$. 
 \end{lemma}
 
-The correctness of this procedure is expressed in Lemma~\ref{lemma:memcorrect} below. 
+Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
+
+The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
 %
@@
 \begin{lemma}\label{lemma:memcorrect}
-	$\semof {\syncfof {A_x }{A'} \wedge \Psi_c}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+	$({\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
 \end{lemma}
 
-Lemma~\ref{lemma:memcorrect} follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}, and Lemma~\ref{lemma:fa_pfa}.
-Informally, the lemma says the models of the formula we add to $\Phi_O$, i.e.
-$\syncfof {A_x }{A'} \wedge \Psi_c$, characterize exactly the models of $x \in  L(A)$ under the restriction of $A_x$.
+\lh{Simplified version:
+Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$. 
+%Assume that $A=(Q,T,\Sigma,q_i,q_f)$. 
+We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\phi_A$. 
+The PA $A'$ operates over fresh character variables $v_a, a\in\Sigma_\epsilon$, and is obtained from $A$ by replacing every occurrence of each character $a\in\Sigma_{\epsilon}$ on a transition by the variable $v_a$.
+The formula $\phi_A$ then binds the fresh variables to the characters they represent, 
+namely, $\phi_A = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
+The resultinng overapproximation of $\phi_r$ is then the formula $\syncfof{A_x} {A'} \land \phi_A$.
+
+The following lemma states the correctness of this construction: Intuitively, the resulting constraint represents presicely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$.
+%
+\begin{lemma}\label{lemma:memcorrect}
+	${\semof {\syncfof {A_x }{A'} \land \phi_A} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
+}
 
@@
 Second, some string variable might occur multiple times in a equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
+\lh{the second is maybe not a minor technical issue}
 
@@
 Later we will add arithmetic constraints to enforce that variables obtained from the same original variable are assigned the same value.
+\lh{I did not find those, are they somewhere or forgoten?}
 
@@
 $$
-Here $V_X$ is the set of all character variables occurred in the PFAs of $x_1,x_2,\ldots,x_m$, i.e., $V_X=\bigcup_{i\in [1,m]}{V_{x_i}}$.
+Here $V_X$ is the set of all character variables occurred in the PFAs of $x_1,x_2,\ldots,x_m$, i.e., $V_X=\bigcup_{i\in [1,m]}{V_{x_i}}$. \lh{what is $R_v$?}
 
@@
 \begin{lemma}\label{lemma:eqcorrect}
-	$\semof {\syncfof A {A'}  \wedge \Psi_r}_{V_X \cup \#V_X} = \{\bigcup_{i\in[1,m]}(I^i\cup\pim^i)\mid w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m \wedge \bigwedge_{i\in [1,m]}w_i=\decode A_{x_i}(I^i\cup\pim^i) \}$.
+	$\semof {\syncfof A {A'}  \wedge \Psi_r}_{V_X \cup \#V_X} = \{\bigcup_{i\in[1,m]}(I^i\cup\pim^i)\mid w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m \wedge \bigwedge_{i\in [1,m]}w_i=\decode A_{x_i}(I^i\cup\pim^i) \}$.\lh{aaarrrghhh ...
+}
 \end{lemma}
@@
 Then we can specify the relation between $n$ and the character variables as follows:
-$$\Psi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+$$\phi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
 It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$.
-We add $\Psi_n$ to $\Phi_O$.
-
-The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect_pos} and Lemma~\ref{lemma:sticorrect_neg} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$. 
-\yfc{The correctness lemmas are still buggy}
-%
-%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
-\begin{lemma}\label{lemma:sticorrect_pos}
-	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n\neq -1) }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
-\end{lemma}
-In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
-
-\begin{lemma}\label{lemma:sticorrect_neg}
-	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = \{I_n\mid (I_n(n) = -1\} \times \semof {\parikhfof {A_x} \wedge (v_0 = 0) }_{V_x \cup \#V_x} $
-\end{lemma}
-In this case, $x$
+
+\yfc{add a Lemma for correctness}
 

### 2019-11-14 evaluation.tex
fix a compile bug

@@
 
-StringFuzz is our next bechmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
+StringFuzz is our next bechmark that is named after a fuzzer~\cite{blotsky2018stringfuzz} for automatically generating SMT-LIB string constraints.
 We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.
@@
 The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}.
-The experiments are conducted under the same condition as the experiments on other benchmarks.
+The experiments are conducted under the same condition as those one other benchmarks.
 

### 2019-11-14 draft.tex

@@
 \begin{lemma}\label{lemma:fa_pfa}
-	$L(A) =  \{  \decode {A'}(I\cup\pim) \mid (I\cup\pim)\in  {\semof {\parikhfof {A'} \wedge \phi_c}} _{V' \cup \#V'} \}$. 
+	$L(A)=	\{  I(x) \mid  I\in  \semof {\Psi_c} \wedge x \in L(A') \} $. 
 \end{lemma}
 
-Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
+%<<<<<<< HEAD
+%Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
 
 The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
+%=======
+%The correctness of this procedure is expressed in Lemma~\ref{lemma:memcorrect} below. 
+%>>>>>>> 67b962e5df2a0689e472f2525f44d512d2c23dbd
 %
@@
 \begin{lemma}\label{lemma:memcorrect}
-	$({\semof {\syncfof {A_x }{A'}} \cap \bigcap_{\phi\in\Phi_C} \semof {\phi} } )_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+	$\semof {\syncfof {A_x }{A'} \wedge \Psi_c}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$.
+
 \end{lemma}
+
+Lemma~\ref{lemma:memcorrect} follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}, and Lemma~\ref{lemma:fa_pfa}.
+Informally, the lemma says the models of the formula we add to $\Phi_O$, i.e.
+$\syncfof {A_x }{A'} \wedge \Psi_c$, characterize exactly the models of $x \in  L(A)$ under the restriction of $A_x$.
 
@@
 Using the same approach, one can derive the assignment to variables in $\vars$ using the corresponding count and values of variables in $\cvar$.
-
-\todo{Maybe talk about the heuristic that we merge the list elements into one}
 
@@
 The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
+\yfc{say shifting $\epsilon$ to the right will not change the language}
+
+The condition that when $x$ is ``not a number'' is specified by the following formula.
+
+$$\Psi_{NaN} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
+
 Then we can specify the relation between $n$ and the character variables as follows:
-$$\phi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
+$$\Psi_n\defeq  (n=-1 \wedge \Psi_{NaN})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
 It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
-
-\yfc{add a Lemma for correctness}
+We add $\Psi_n$ to $\Phi_O$.
+
+The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect_pos} and Lemma~\ref{lemma:sticorrect_neg} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$. 
+\yfc{The correctness lemmas are still buggy}
+%
+%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+\begin{lemma}\label{lemma:sticorrect_pos}
+	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n\neq -1) }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
+\end{lemma}
+In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
+
+\begin{lemma}\label{lemma:sticorrect_neg}
+	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
+	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \in [0,9]^+  \}$
+\end{lemma}
+In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.
+
+\subsection{Handling the lengths of variables}
+After the set $\Phi_I$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
+To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
+
+$$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
+
+More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\Phi_O$.
+
+$$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
 

### 2019-11-14 draft.tex
littel changes in the sketch

@@
 We use the linear formula $\Psi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
-We add both $\syncfof {A_x }{A'} $ and $\Psi_c$ to $\Phi_O$.
+\lh{why  the name $\Psi_c$?} We add both $\syncfof {A_x }{A'} $ and $\Psi_c$ to $\Phi_O$.
 The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
@@
 
-\lh{Simplified version:
+\lh{Sketch of a simplified version:
 Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$. 
 %Assume that $A=(Q,T,\Sigma,q_i,q_f)$. 
-We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\phi_A$. 
+We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\Psi_c$. 
 The PA $A'$ operates over fresh character variables $v_a, a\in\Sigma_\epsilon$, and is obtained from $A$ by replacing every occurrence of each character $a\in\Sigma_{\epsilon}$ on a transition by the variable $v_a$.
-The formula $\phi_A$ then binds the fresh variables to the characters they represent, 
-namely, $\phi_A = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
-The resultinng overapproximation of $\phi_r$ is then the formula $\syncfof{A_x} {A'} \land \phi_A$.
-
-The following lemma states the correctness of this construction: Intuitively, the resulting constraint represents presicely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$.
+The formula $\Psi_c$ then binds the fresh variables to the characters they represent, 
+namely, $\Psi_c = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
+The resultinng overapproximation of $\Psi_r$ is then the formula $\syncfof{A_x} {A'} \land \Psi_c$.
+
+The following lemma states the correctness of this construction, and it follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}. 
+Intuitively, it says that the resulting constraint represents presicely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
+%
+
 %
 \begin{lemma}\label{lemma:memcorrect}
-	${\semof {\syncfof {A_x }{A'} \land \phi_A} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+	${\semof {\syncfof {A_x }{A'} \land \Psi_c} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
 \end{lemma}

### 2019-11-15 draft.tex
address the comments from Lukas

@@
 Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
-Given a linear formula $\phi$, a set of variables $V$ \lh{remove this?: that includes all variables occurring in $\phi$}, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
+Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
 we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$.
@@
 The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
+In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
 
@@
 The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver. 
-\lh{, allowing to circumvent more costly automata algorithms and decision procedures.
-Concretize and justify this better?}\yfc{The two sentences below read a bit strange, maybe need to rephrase it.}\lh{made an attempt}
+\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
 %
@@
 \lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
+\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
 \end{lemma}
@@
 \paragraph{Synchronization of PAs}
-\ \lh{changed the formulation of the next two paragraphs a bit, is it ok?}
 We will now discuss a construction of the \emph{synchronization formula} for two PAs $A$ and $A'$. 
@@
 % \in \semof{A}\cap\semof{A'}$.
-The synchronization formula will be used in, e.g., the decision procedure of equality constraints $t_1=t_2$ to find a common interpretation of $t_1$ and $t_2$.  
+The synchronization formula will be used in, e.g., the decision procedure of equality constraints $t_1=t_2$ to find a common interpretation~of~$t_1$~and~$t_2$.  
 %More precisely, the models of the synchronization formula $\syncfof A {A'}$ correspond to the set of all pairs of word
@@
 
-Particularly, the synchronization formula is build for two PAs  
+Particularly, the synchronization formula is built for two PAs  
 $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
@@
 %
-\hide{
-\begin{lemma}\label{lemma:synccorrect}
-%$\semof {\exists V_\times .
-\syncfof A {A'}}\restrict{\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$.
-$\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
-\end{lemma}
-%
-Another version:}
 \begin{lemma}\label{lemma:synccorrect}
@@
 
-\lh{this following sentence appears to be in a wrong place here. Would be nicer in some introductory part to the underapproximation which talks about this, but I don't know where it should be.}
-In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
-
-\yfc{we need to define \#{V} somewhere}
-\lh{it is in prelims next to Parikh im. definition}
-
 \subsection{Handling Regular Constraints Symbolically} \label{section:mem}
 
-Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$.
-Assume that $A=(Q,T,\Sigma,q_i,q_f)$.
-First we create a PA $A' = (Q,T', V',q_i,q_f)$ that has exactly the same set of states as $A$.
-The set of transitions $T'$ and character variables $V'$ is defined as follows:
-
-\begin{itemize}
-	\item $V' = \{ v_{(q,a,q')} \mid (q,a,q')\in T\}$
-	\item $T' = \{ (q, v_{(q,a,q')}, q')  \mid (q,a,q')\in T\}$
-\end{itemize}
-We use the linear formula $\Psi_c \defeq \bigwedge\limits_{(q,a,q')\in T} (v_{(q,a,q')} = a)$ to remember the relation between the fresh character variables in $V'$ and the symbol it represents.
-\lh{why  the name $\Psi_c$?} We add both $\syncfof {A_x }{A'} $ and $\Psi_c$ to $\Phi_O$.
-The relation between $A$ and $A'$ is expressed in Lemma~\ref{lemma:fa_pfa}.
-
-\begin{lemma}\label{lemma:fa_pfa}
-	$L(A)=	\{  I(x) \mid  I\in  \semof {\Psi_c} \wedge x \in L(A') \} $. 
-\end{lemma}
-
-%<<<<<<< HEAD
-%Intuitively, we create a new character variable for each transition in $T$, later we will add the relation $v_{(q,a,q')}  = a$ to $\Phi_O$.
-
-The correctness of this construction is expressed in Lemma~\ref{lemma:memcorrect} below. 
-%=======
-%The correctness of this procedure is expressed in Lemma~\ref{lemma:memcorrect} below. 
-%>>>>>>> 67b962e5df2a0689e472f2525f44d512d2c23dbd
-%
-%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
-\begin{lemma}\label{lemma:memcorrect}
-	$\semof {\syncfof {A_x }{A'} \wedge \Psi_c}_{V_x \cup \#V_x} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$.
-
-\end{lemma}
-
-Lemma~\ref{lemma:memcorrect} follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}, and Lemma~\ref{lemma:fa_pfa}.
-Informally, the lemma says the models of the formula we add to $\Phi_O$, i.e.
-$\syncfof {A_x }{A'} \wedge \Psi_c$, characterize exactly the models of $x \in  L(A)$ under the restriction of $A_x$.
-
-\lh{Sketch of a simplified version:
 Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$. 
 %Assume that $A=(Q,T,\Sigma,q_i,q_f)$. 
-We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\Psi_c$. 
+We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\Psi_{char}$. 
 The PA $A'$ operates over fresh character variables $v_a, a\in\Sigma_\epsilon$, and is obtained from $A$ by replacing every occurrence of each character $a\in\Sigma_{\epsilon}$ on a transition by the variable $v_a$.
-The formula $\Psi_c$ then binds the fresh variables to the characters they represent, 
-namely, $\Psi_c = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
-The resultinng overapproximation of $\Psi_r$ is then the formula $\syncfof{A_x} {A'} \land \Psi_c$.
+The formula $\Psi_{char}$ then binds the fresh character variables to the character values they represent, 
+namely, $\Psi_{char} = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
+The resulting under-approximation of $\Psi_r$ is then the formula $\syncfof{A_x} {A'} \land \Psi_{char}$, which will be added to $\Phi_O$.
 
 The following lemma states the correctness of this construction, and it follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}. 
-Intuitively, it says that the resulting constraint represents presicely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
+Intuitively, it says that the resulting constraint represents precisely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
 %
@@
 \begin{lemma}\label{lemma:memcorrect}
-	${\semof {\syncfof {A_x }{A'} \land \Psi_c} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
 \end{lemma}
-}
 
@@
 Intuitively, this can be achieved by connecting the PFAs of the string variables with epsilon transitions.
-However, there are two minor technical issues.
+However, there are two technical issues.
 First, our definition of PFA does not allow epsilon transition.
-Second, some string variable might occur multiple times in a equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
-\lh{the second is maybe not a minor technical issue}
+The second issue is more severe, some string variable might occur multiple times in an equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
+We will need a way to force that all occurrences of the same string variable are assigned the same value.
 
@@
 
-For the second problem, we rename the variables on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
+For the second issue, we rename the variables on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
 The renaming is done by adding a version number to the variable.
@@
 In this case, $v_1$ is the original variable and both $v_1^{(0)}$ and $v_1^{(1)}$ are the renamed variables.
-For an original variable $v$, we use $R_v$ to denote the set of variables renamed from $v$.
-Later we will add arithmetic constraints to enforce that variables obtained from the same original variable are assigned the same value.
-\lh{I did not find those, are they somewhere or forgoten?}
+We will an add arithmetic constraint $\Psi_{rename}$ (will be defined later) to enforce that variables renamed from the same variable are assigned the same value.
 
@@
 However, this does not directly correspond to a model of the equality constraint $\phi_e$.
-The reason is that difference occurrence of the same string variables can be assigned different values in $\semof{A}$ and $\semof{A'}$.
-To avoid this problem, we need to add the constraint $\Psi_r$ below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
-
-$$ \Psi_r \defeq
-\bigwedge_{v\in V_X, v'\in R_v} v=v' \wedge \#v = \#v'
+The reason is that different occurrences of the same string variables can be assigned different values in $\semof{A}$ and $\semof{A'}$.
+To avoid this problem, we need to add the constraint $\Psi_{rename}$ that is defined below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
+
+$$ \Psi_{rename} \defeq
+\bigwedge_{v\in V_{x_1} \cup\ldots\cup V_{x_m} , v'\in R_v} v=v' \wedge \#v = \#v'
 $$
-Here $V_X$ is the set of all character variables occurred in the PFAs of $x_1,x_2,\ldots,x_m$, i.e., $V_X=\bigcup_{i\in [1,m]}{V_{x_i}}$. \lh{what is $R_v$?}
-
-The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect}.
+Here $R_v$ is the set of variables renamed from the the original variable $v$. 
+The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect} below.
+In the lemma, each tuple of words $(w_1,\ldots, w_m) \in \semof{A_{x_1}}\times\ldots\times\semof{A_{x_m}}$ represents a model of the equality constraint.
+Each tuple $(w_1,\ldots, w_m)$ satisfies the condition that if $x_i$ and $x_j$ are the same variable, then $w_i$ and $w_j$ should be the same word.
 
 \begin{lemma}\label{lemma:eqcorrect}
-	$\semof {\syncfof A {A'}  \wedge \Psi_r}_{V_X \cup \#V_X} = \{\bigcup_{i\in[1,m]}(I^i\cup\pim^i)\mid w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m \wedge \bigwedge_{i\in [1,m]}w_i=\decode A_{x_i}(I^i\cup\pim^i) \}$.\lh{aaarrrghhh ...
-}
+	$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \\
+	    \left\{\begin{array}{c|cl}
+			(I^1\cup\pim^1)\ \cup&w_1=\decode A_{x_1}(I^1\cup\pim^1) & \wedge \\
+			(I^2\cup\pim^2)\ \cup&w_2=\decode A_{x_2}(I^2\cup\pim^2) & \wedge \\
+			\ldots&\ldots\\
+%			(I^{m-1}\cup\pim^{m-1}) &\cup&w_{m-1}=\decode A_{x_{m-1}}(I^{m-1}\cup\pim^{m-1}) & \wedge \\
+			(I^m\cup\pim^m)      &w_m=\decode A_{x_m}(I^m\cup\pim^m) & \wedge \\
+			&w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m & \wedge \\
+			&\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j &  \\
+        \end{array}\right\}
+	$
 \end{lemma}

### 2019-11-15 evaluation.tex
added description of new benchmarks

--- 2019-11-13 evaluation.tex
@@
 
-We have implemented the proposed approach in a prototype tool \textsf{z3-Trau} as a part of the Z3 theorem prover.
+We have implemented the proposed approach in a prototype tool \tool as a part of the Z3 theorem prover.
 This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports.
@@
 
-We compare \textsf{z3-Trau} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
+We compare \tool with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints.
@@
 First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories.
-Second, we show that our tool is competitive on well-known benchmarks that can be effectively handled by other existing solvers.
+Second, we show that our tool is competitive on conversion-less benchmarks as well.
 The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
@@
 
+\paragraph{A Comparison on benchmarks containing string-number and number-string constrains.}
+Our second group of benchmarks was created in order that we could compare our proposed approach for solving string-number and number-string conversions with existing approaches.
+This group contains a total of 3 benchmarks: full\_str\_int, filtered\_str\_int and rec\_fun.
+None of these benchmarks were artificially generated but were created from real Python's and javascript's codes.
+
+The first benchmark in the group is full\_str\_int, which is a collection of SMT queries.
+This collection was generated by applying a tool for concolic testing to Python codes selected from the previously mentioned LeetCode platform and from Python core libraries.
+All selected Python codes use the \texttt{int()} function, which converts a string into a number system based on the specified base.
+The Benchmark consists of 21573 tests in total.
+
+The second benchmark, called filtered\_str\_int, is a subset of the previous full\_str\_int benchmark.
+The filtered\_str\_int benchmark was created by removing tests where cvc4 reported UNSAT and where cvc4's returned unsat core contained no conversion constraint.
+This benchmark was created in order that we better compare individual conversion approaches.
+A total of 7396 tests were left.
+
+The last benchmark in the group is rec\_fun, which is a collection of javascript functions that were handcrafted encoded into smt2 format using recursive functions.
+Besides running examples from the introduction, the benchmark also includes \texttt{split} and \texttt{replaceAll} functions.
+In total, we managed to create 43 tests that combine several SMT theory and contain conversion constrains.
+
 \hide{
@@
 In case $\times$, the result may be unknown, error, or exception.
-}
 
@@
 \textbf{Comparison according to Table 2.....}
+}
 

### 2019-11-15 draft.tex
address the comments from Lukas

@@
 In each step, we take a string constraint from $\Phi_I$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\Phi_O$.
+We also add constraints to $\Phi_O$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
 
@@
 
-Assume that the constraint we take from $\Phi_I$ is a string-number conversion constraint  $\phi_s \defeq n=\sti{x}$. We will discuss how to make the corresponding linear formulas in this section.
-
-Let us begin the discussion with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
+Assume that the constraint we take from $\Phi_I$ is a string-number conversion constraint  $\phi_s \defeq n=\sti{x}$. In this section, we how to make the corresponding linear formulas for $\Phi_O$.
+
+We begin the discussion with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
 Then we know that when $0\leq v_0,v_1 \leq 9$, then $n$ is a positive integer value, and otherwise $n =-1$.
-So we should first add the constraint $ ((0\leq v_0\leq 9) \wedge (0\leq v_1\leq 9)) \vee n=-1 $.
+So we should first add the constraint $ ((0\leq v_0\leq 9) \wedge (0\leq v_1\leq 9)) \vee (n=-1 \wedge (v_0 >9 \vee v_1 >9))$.
 
@@
 
-\paragraph{PFA that allows efficient string-number conversion: } In the previous discussion, we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
-The problem is that each loop in the PFA creates an exponential component.
-An immediate idea would be that maybe we can restrict the variable to some specific PFA that allow more efficient constraint solving.
-At the same time, we want to keep some good property, i.e., the search space covers all integers with at most $m$-digits.
-
-Our first attempt is a PFA with no loop, i.e., a straight line structure.
+\paragraph{PFA that allows efficient string-number conversion: } Now we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
+The cause of the problem is that each loop in the PFA creates an exponential component in the constraint.
+An immediate idea would be that maybe we can pick some specific PFA that allow more efficient constraint solving.
+At the same time, we want to keep a good property, that is, the search space covers all integers up to $m$-digits.
+
+Our first attempt is a PFA without loop, i.e., a straight line structure 
+\scalebox{0.5}{\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+	\begin{tikzpicture} 
+		\node[state,initial] (q0)  {$q_0$};
+		\node[state] (q1) [right = 1cm of q0] {$q_1$};
+		\node (q2) [right = 0.8cm of q1]{};
+		\node (q3) [right = 1cm of q2]{};
+		\node[state,accepting] (qm) [right = 1cm of q3] {$q_m$};
+
+		\draw[->] (q0) edge node [below]{$v_1$} (q1) ;
+		\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
+		\draw[dotted] (q2) edge (q3) ;
+		\draw[->] (q3) edge node [below]{$v_m$} (qm) ;
+	\end{tikzpicture}}
+.
 The corresponding integer constraint does not have exponential components.
-However, it does not ensure the property that all numbers with at most $m$-digits are covered.
+However, it does cover all numbers with at most $m$-digits.
 Consider the example $\sti{x}=10 \wedge |x|=5$.
-The number $10$ has only $2$-digits, at the first glance, a straight-line PFA with two transitions, i.e., the PFA \scalebox{0.5}{\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+The number $10$ has only $2$-digits, at the first glance, a straight-line PFA with two transitions, i.e., the PFA
+    \scalebox{0.5}{\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
 			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
@@
 	\draw[->] (q1) edge node [below]{$v_2$} (q2) ;
-	\end{tikzpicture}} should be sufficient for the domain restriction of $x$.
-If we do so, we will conclude that the formula is unsatisfiable, because the length of $x$ cannot be $5$  under this domain restriction.
+	\end{tikzpicture}
+	} should be sufficient for the domain restriction of $x$. If we do so, we will conclude that the formula is unsatisfiable, because the length of $x$ cannot be $5$  under this domain restriction.
 
@@
 The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
-In order to handle all number with at most $m$ digits, we propose to restrict the domain of $x$ to a PFA in Figure~\ref{fig:sfa_its}.
-The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $v_0=0$ to $\Phi_O$ for such PFA.
+In order to handle all numbers with up to $m$-digits, we propose to restrict the domain of $x$ to a PFA in Figure~\ref{fig:sfa_its}.
+The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $\Psi_{v_0}\defeq v_0=0$ to $\Phi_O$ for such PFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
-Although this PFA still has a loop, but it will not create any exponential component because the loop only represents a sequence of `0' that occurs in the prefix of $x$.
+Although this PFA still has a loop, it will not create any exponential component because the loop only represents a sequence of ``0'' at the front of $x$.
 It will not affect the integer value of $n=\sti{x}$.
@@
 
-	\caption{An example of a symbolic flat automaton}
+	\caption{PFA for string-number conversion constraints}
 	\label{fig:sfa_its}
@@
 Remember that the character variables can be assigned $\epsilon$.
-In order to simplify the construction, we an encoding to shift all the $\epsilon$-transitions to the least significant digits, i.e., if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j+1,m]$.
+In order to simplify the construction, we use an encoding to shift all the $\epsilon$-transitions to the least significant digits, i.e., if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j+1,m]$.
 To explain this encoding, we first define two macro function:
@@
 
-The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect_pos} and Lemma~\ref{lemma:sticorrect_neg} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$. 
-\yfc{The correctness lemmas are still buggy}
+The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$.
+
 %
 %\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
+
+\begin{lemma}\label{lemma:sticorrect}
+
+	The interpretation $(I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} $ if and only if 
+	\begin{center}
+	 $\left(\begin{array}{c} 
+	 I_n(n)= \sti{\decode {A_x}(I\cup\pim)} \ \wedge \\
+	 I(v_i)=-1 \wedge i<j \Longrightarrow  I(v_j)=-1
+	 \end{array}\right)$\\ or\\
+	 $\left(\begin{array}{c} 
+	 I_n(n)= -1\ \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+
+	 \end{array}\right)$
+	\end{center}
+
+\end{lemma}
+\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
+
+\hide{
 \begin{lemma}\label{lemma:sticorrect_pos}
-	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n\neq -1) }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
+	$\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
 \end{lemma}
@@
 	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
-	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \in [0,9]^+  \}$
+	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+  \}$
 \end{lemma}
-In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.
+In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}
 

### 2019-11-15 draft.tex
add an alternative way to describe correctness lemmas

@@
 %
-
-%
-\begin{lemma}\label{lemma:memcorrect}
-	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\begin{lemma}\label{lemma:memcorrect}  ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+\end{lemma}
+%
+(An alternative description)
+\begin{lemma}\label{lemma:memcorrect} For all $w\in \semof{A_x}$, %$(I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ such that $w =\decode {A_x}(I\cup\pim)$ if and only if $w \in L(A)$.
+%	$$\exists (I\cup\pim) \in {\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}. w =\decode {A_x}(I\cup\pim)$$
+	\begin{center}
+	$\exists (I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ s.t. $w =\decode {A_x}(I\cup\pim)$\\
+		iff\\
+		$w \in L(A)$.
+	\end{center}
+%	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
 \end{lemma}
@@
 	$
+\end{lemma}
+
+(An alternative description)
+
+\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$, we have
+
+	\begin{center}
+		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t.
+$w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
+		iff\\
+		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$ and\\
+		$\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$.
+	\end{center}
 \end{lemma}
@@
 \yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
-
+(An alternative description)
+\begin{lemma}\label{lemma:sticorrect}
+	For all $w \in \semof{A_{x}}$ and $c \in \mathbb{Z}$, we have 
+	\begin{center}
+		$\exists (I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}}$ s.t. $w=\decode {A_x}(I\cup\pim)$ and $I_n(n)=c$\\
+		iff\\
+		$c= \sti{w}$.
+	\end{center}
+
+\end{lemma}
 \hide{

### 2019-11-15 draft.tex
add an alternative way to describe correctness lemmas
Encode functions to formulate lemmas

@@
 For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
+\lh{or really have just an equivalence of semantics indexed by variables?}
 
@@
 \yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
+
+\newcommand{\encode}[1]{\mathit{encode}_{#1}}
+\lh{What about to put this somewhere, it will simplify formulation of the correctness lemmas. Roughly, formulation need to be polished a and explained:}
+Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$ encodings of $L\cap \semof A$ as
+the set $\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$.
+%
+A domain restriction $R$ for a string contraint $\phi$ over variables $X$ is a mapping that assigns to every variable $x\in X$ a PFA $R(x)$ such that for different variables $x,y \in X$, $R(x)$ and $R(y)$ have disjoint sets of variables.
+%
+For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$, and we left this notation to sets of interpretation in the standard manner, i.e.
+$\encode R J = \bigcup_{I \in J}\encode R (I)$.
+%
+In the following section, we will discuss how, given a string contraint $\phi$ and a domain restriction $R$,
+to build an arithmetic formula $\Psi$ such that $\semof\Psi_{V_R\cup\#V_R} = \encode R(\semof{\phi})$. 
+Tha is, formula $\Psi$ will capture $R$-encodings of soltuions of $\phi$ under the domain restriction given by $R$.
 
@@
 
+\lh{
+\begin{lemma}
+${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \encode {A_x}(L(A))$
+\end{lemma}
+}
+
 \begin{figure*}
@@
 
-\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$, we have
+\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$ satisfying $\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$, we have
 
@@
 		iff\\
-		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$ and\\
-		$\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$.
+		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$.
 	\end{center}
 \end{lemma}
+
+\lh{Assume that we were working with a domain restriction $R:[x_i]_1^m\rightarrow \text{PFAs}$.
+\begin{lemma}
+$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \encode R (\semof{\phi_e})$.
+\end{lemma}
+Also, we could denote by $V_R$ the varsiables $V_{x_1} \cup\ldots\cup V_{x_m}$ (these are the variables used by the domain restriction), 
+and use $\# V_R$, so the lemma becomes \\ 
+$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_R \cup \# V_R} = \encode R (\semof{\phi_e})$.
+
+}
 
@@
 \end{lemma}
+
 In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}
+
+\lh{
+\begin{lemma}
+$
+\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \encode  R(\semof{\phi_s})
+$
+\end{lemma}
+The $n$ must somehow be handled properly by $\encode  R(\phi_s)$, I did not have time to think about it yet.
+}
 

### 2019-11-15 draft.tex
little thing

@@
 If $V$ is missing some of the variables of $\phi$, then it must be possible to complete $I$ with assignment of the missing variables into a satisfying assignment of $\phi$ (as in existential quantification).}
+\lh{or really have just an equivalence of semantics indexed by variables?}
 We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
@@
 For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
-\lh{or really have just an equivalence of semantics indexed by variables?}
 

### 2019-11-16 draft.tex
version with R and encode R, in progress

--- 2019-11-15 draft.tex
@@
 \newcommand{\nat}{\mathbb{N}}
+\newcommand{\integers}{\mathbb{Z}}
 \newcommand{\todo}[1]{{\color{blue}TODO: #1}}
@@
 \newcommand{\defeq}{::=}
+\newcommand{\encode}[1]{\mathit{encode}_{#1}}
+\newcommand{\eqwrt}[1]{=_{#1}}
+\newcommand{\iequiv}{\equiv}
+\newcommand{\restrict}[2]{#1{\restriction_{#2}}}
+\newcommand{\underf}[2]{\mathit{under}_#1(#2)}
 
@@
 $\{k\mid n\leq k \leq m\}$. 
+The function $f$ with the domain restricted to $D$ is denoted by $\restrict f D$,
+and a set of functions $F$ restricted to $D$ is $\restrict F D = \{\restrict f D \mid f \in F\}$.
 An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{word} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty word}.
@@
 
-Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
-Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
-we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$.
-\lh{Our use of indexing by $V$ in the text later is not very nice.
+%Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
+%Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
+%we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$. 
+%
+%\lh{Our use of indexing by $V$ in the text later is not very nice.
 Add this for clarity?: If $V$ contain additional variables not present in $\phi$, the these might be assigned arbitrary values by $I$.
 If $V$ is missing some of the variables of $\phi$, then it must be possible to complete $I$ with assignment of the missing variables into a satisfying assignment of $\phi$ (as in existential quantification).}
-We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
-We drop the reference to $V$ and write just ``model of $\phi$'',  $\modelsof \phi$, and $\models$ when no confusion may arise.
+%We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
+%We drop the reference to $V$ and write just ``model of $\phi$'',  $\modelsof \phi$, and $\models$ when no confusion may arise.
 For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
+
+Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.   
+Given a linear formula $\phi$ over variables $V$ and an \emph{integer interpretation} of $V$, a function $I:V\rightarrow \integers$, 
+we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
+We use $\modelsof \phi$ to denote the set all models of $\phi$. 
+%
+%Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
+%We say that $J$ and $J'$ are \emph{equivalent}, written $J\iequiv J'$, if their interpretations restricted to the common variables are the same, that is, if 
+%$\{\restrict I {V\cap V'} \mid I \in J\} = \{\restrict {I'} {V\cap V'} \mid I' \in J'\}$. We may write $J\eqwrt{V\cap V'} J'$ if we wish to made the common variables explicit.
 
@@
 The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$. 
-The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$ and the Parikh image of an FA $A$ is Parikh image of its language, $\parikhof{A} = \parikhof{L(A)}$.
-%
-It is well known that $\parikhof A$ can be efficiently computed in the form of linear formula:
+The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in  L\}$.
+%and the Parikh image of an FA $A$ is Parikh image of its language, $\parikhof{A} = \parikhof{L(A)}$.
+%
+It is well known that $\parikhof {L(A)}$ can be efficiently computed in the form of linear formula:
 
 \begin{lemma}[\cite{SeidlSMH04}]
-$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A}_{\#\Sigma} = \parikhof{A}$, in time linear to the size of $A$.
+$\parikhof{L(A)}$ of an FA $A$ can be computed in the form of a linear formula  $\parikhfof{A}$ such that 
+%$\modelsof{\parikhfof A}_{\#\Sigma} = \parikhof{L(A)}$, 
+$\modelsof{\parikhfof A} = \parikhof{L(A)}$, 
+in time linear to the size of $A$.
 \end{lemma}
@@
 This is facilitated by the structural constraints of PFA, which guarantee that 
-every parametric word $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, as formalized by the following lemma.
+every parametric word $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, i.e., $\decode A (\parikhof x)) = x$, and analogously for the entire language of $A$, as formalized by the following lemma.
 
@@
 from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
-We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
-%
+We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$, and we lift the function to sets of integer assignments in the standard manner.
+%
+
+%\begin{lemma}\label{lemma:decx}
+%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
+%\end{lemma}
+%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
+%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
 
 \begin{lemma}\label{lemma:decx}
-For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
-\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
-\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
+%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in \parikhof A\}$.
+For a PFA $A$, $L(A) = \decode A(\parikhof{L(A)}$.
 \end{lemma}
+%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
+%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
 %
@@
 Lemma~\ref{lemma:parikh} also implies that two different words are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$.
-Encodings of words in $\semof{A}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
-%
+The following corrolary of Lemma~\ref{lemma:decx} states that encodings of words in $\semof{A}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$:%, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
+%
+%\begin{corollary}\label{corollary:pfa}
+%For an PFA $A$ over character variables $V$,
+%$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$.
+%%$\semof{A} = \{I(\decode A(\pim)) \mid \pim\in\semof{\parikhfof A},I:\cvars\rightarrow\Sigma_\epsilon\}$.
+%\end{corollary}
+
 \begin{corollary}\label{corollary:pfa}
 For an PFA $A$ over character variables $V$,
-$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$.
-%$\semof{A} = \{I(\decode A(\pim)) \mid \pim\in\semof{\parikhfof A},I:\cvars\rightarrow\Sigma_\epsilon\}$.
+%$\semof{A} = \{(\decode A(I\cup\pim)) \mid \pim\in\parikhof A,I:\cvars\rightarrow\Sigma_\epsilon\}$.
+$\semof A = \decode A \{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I:\cvars\rightarrow\Sigma_\epsilon\}$
 \end{corollary}
@@
 %
+%\begin{lemma}\label{lemma:synccorrect}
+%$
+%\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = 
+%\{
+%(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
+%x\in L(A), x'\in L(A'), I(x) = I(x')
+%\}
+%$
+%\end{lemma}
+
+%\begin{lemma}\label{lemma:synccorrect}
+%$
+%\semof {\syncfof A {A'}} \iequiv
+%\{
+%(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
+%x\in L(A), x'\in L(A'), I(x) = I(x')
+%\}
+%$
+%\end{lemma}
+
 \begin{lemma}\label{lemma:synccorrect}
@@
 \semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{
-(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
-x\in L(A), x'\in L(A'), I(x) = I(x')
-\}
+%\semof {\syncfof A {A'}} \iequiv
+\{(I\cup I_\#)\cup (I' \cup I'_\#)\mid (I\cup I_\#) \in \encode A (w), (I' \cup I'_\#)\in\encode {A'} (w),w\in\semof A \cap \semof {A'}\} 
 $
 \end{lemma}
+
 Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{A'}$, that constitute the intersection $\semof{A} \cap \semof{A'}$.
 A minor technical difficulty is that the models of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
-Hence in the lemma, we have to restrict the models to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
+Hence in the lemma, we use $\iequiv$ instead of $=$ to restrict the models to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
 %This is  achieve by quantifying out the variables of $V_\times$.
@@
 Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then the semantic intersection $\semof A \cap \semof {A'}$ can be still decoded from the synchronisation formula $\semof {\syncfof A {A'}}$.
-Namely, due to Corollary~\ref{corollary:pfa}, we have that $\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.
+Namely, due to Corollary~\ref{corollary:pfa}, we have that 
+%$\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.  
+$$\semof A \cap \semof {A'} = \decode A (\semof{\syncfof A {A'}}_{\cvarone\cup \pvarone})$$
 
@@
 
-\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
-
-Assume that the constraint we take from $\Phi_I$ is a regular constraint $\phi_r \defeq x \in L(A)$. 
+\subsection{Flat Domain Restriction}
+Let us now give a precise definition of how we restrict the domain of string constraints using flat automata. 
+A \emph{flat domain restriction} for a string contraint $\phi$ over variables $X$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
+For technical reasons that will be apparent further in this section, we require that if $x\neq  y$, then $R(x)$ and $R(y)$ have disjoint sets of character variables.
+We will use $V_R$ to denote the union of character variables of all $R(x),x\in X$.
+
+The semantics of a string contraint $\Phi_I$ over a set of variables $X$ restricted by $R$ is defined as 
+$\semof\phi^R = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{R(x)}\}$. 
+In the rest of this section, we will show how to build an \emph{underapproximating formula} representing the semantics $\semof{\Psi_I}^R$ of an input string constraint, that is, a formula $\Psi_O$ such that
+$\{\decode R (\semof {\Psi_O})\} = \semof{\Psi_I}_R$.
+
+The formula $\Psi_O$ is build intuctively to the structure of $\Psi_O$.
+Namely, in the followin subsections we show how to build a formula $\underf R {\phi}$ for every atomic string constraint $\phi$, and for a Boolean combination of 
+string constraints we have $\underf R {\phi \land \phi'} = \underf R {\phi} \land \underf R {\phi'}$ and $\underf R {\neg\phi} = \neg\underf R{\phi}$.
+The underapproximation formula is then in the form $\Psi_O \defeq \underf R {\Psi_I}$.
+
+The correctness of this construction, that is, that 
+$$\decode R (\semof {\Psi_O}) = \semof{\Psi_I}^R$$ can be proved by induction to the structure of $\Psi_I$.
+However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf R \phi$.
+Particularly, we will need to
+%pay attention to how $\underf R \phi$ atually encodes the models of $\phi$, and
+ ensure that $\underf R \phi$ captures exactly all $R$-encodings of $\semof \phi^R$.
+
+%
+To this end, we define the following notation.
+Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$ encodings of $L\cap \semof A$ as $\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$.
+%
+For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$.
+We left this notation to sets of interpretation in the standard manner, i.e., $\encode R J = \bigcup_{I \in J}\encode R (I)$ for a set of interpretation $J$.
+%
+The needed inductive argument of the correctness of the construction can be expressed as that 
+$$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
+We restrict need to restrict here interpretations of $\underf R \phi$ since its construction uses some additional variables.
+
+%\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
+\subsection{Underapproximation of Regular Constraints} \label{section:mem}
+
+Let us first describe the construction of $\underf R {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
 %Assume that $A=(Q,T,\Sigma,q_i,q_f)$. 
-We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\Psi_{char}$. 
+We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\Psi_{\mathit{char}}$. 
 The PA $A'$ operates over fresh character variables $v_a, a\in\Sigma_\epsilon$, and is obtained from $A$ by replacing every occurrence of each character $a\in\Sigma_{\epsilon}$ on a transition by the variable $v_a$.
-The formula $\Psi_{char}$ then binds the fresh character variables to the character values they represent, 
-namely, $\Psi_{char} = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
-The resulting under-approximation of $\Psi_r$ is then the formula $\syncfof{A_x} {A'} \land \Psi_{char}$, which will be added to $\Phi_O$.
+The formula $\Psi_{\mathit{char}}$ then binds the fresh character variables to the character values they represent, 
+namely, $\Psi_{\mathit{char}} = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
+%The resulting under-approximation of $\Psi_r$ is then the formula $\syncfof{A_x} {A'} \land \Psi_{char}$, which will be added to $\Phi_O$.
+Then 
+$$\underf R {\phi_r} = \syncfof{A_x} {A'} \land \Psi_{\mathit{char}}$$ 
+%, which will be added to $\Phi_O$.
 
 The following lemma states the correctness of this construction, and it follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}. 
-Intuitively, it says that the resulting constraint represents precisely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
-%
-\begin{lemma}\label{lemma:memcorrect}  ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+%Intuitively, it says that the resulting constraint represents precisely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
+\begin{lemma}\label{lemma:memcorrect}  $\semof {\underf R {\phi_r}}_{V_R \cup V_{\#R}} = \encode {R} (\semof{\phi_r})$ . 
 \end{lemma}
-%
-(An alternative description)
-\begin{lemma}\label{lemma:memcorrect} For all $w\in \semof{A_x}$, %$(I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ such that $w =\decode {A_x}(I\cup\pim)$ if and only if $w \in L(A)$.
-%	$$\exists (I\cup\pim) \in {\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}. w =\decode {A_x}(I\cup\pim)$$
-	\begin{center}
-	$\exists (I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ s.t. $w =\decode {A_x}(I\cup\pim)$\\
-		iff\\
-		$w \in L(A)$.
-	\end{center}
-%	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
-\end{lemma}
+
+%
+%\begin{lemma}\label{lemma:memcorrect}  ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+%\end{lemma}
+%
+%(An alternative description)
+%\begin{lemma}\label{lemma:memcorrect} For all $w\in \semof{A_x}$, %$(I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ such that $w =\decode {A_x}(I\cup\pim)$ if and only if $w \in L(A)$.
+%%	$$\exists (I\cup\pim) \in {\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}. w =\decode {A_x}(I\cup\pim)$$
+%	\begin{center}
+%	$\exists (I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ s.t. $w =\decode {A_x}(I\cup\pim)$\\
+%		iff\\
+%		$w \in L(A)$.
+%	\end{center}
+%%	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
+%\end{lemma}
+%
+%\lh{
+%\begin{lemma}
+%${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \encode {A_x}(L(A))$
+%\end{lemma}
+%}
 
@@
 \subsection{Handling Equality Constraints Symbolically} \label{section:eq}
-
-Assume that the constraint we take from $\Phi_I$ is an equality constraint $\phi_e\defeq x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$.
-We first build two PFAs that encode the left-hand side term and the right-hand side term of the equality constraint.
-Intuitively, this can be achieved by connecting the PFAs of the string variables with epsilon transitions.
+\newcommand{\leftA}{A^{\mathit{left}}}
+\newcommand{\rightA}{A^{\mathit{right}}}
+\newcommand{\leftV}{V^{\mathit{left}}}
+\newcommand{\rightV}{V^{\mathit{right}}}
+
+We now describe the construction of $\underf R {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$.
+We first build two PFAs $\leftA$ and $\rightA$ that encode the left-hand side term and the right-hand side term of the equality constraint.
+Intuitively, this can be achieved by connecting the PFAs restricting the string variables with epsilon transitions.
 However, there are two technical issues.
 First, our definition of PFA does not allow epsilon transition.
-The second issue is more severe, some string variable might occur multiple times in an equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
+%The second issue is more severe,
+Second,
+some string variable might occur multiple times in an equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
 We will need a way to force that all occurrences of the same string variable are assigned the same value.
 
-We circumvent the first problem by introducing some fresh characters variables, say $v_{\epsilon_n}$, and forcing its value to be $\epsilon$ by adding new linear formulas, say $v_{\epsilon_n}= -1$, to the output linear formulas $\phi_O$.
-Then we can connect the final state and initial state of two consecutive variables with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_n}$.
+We circumvent the first problem by fresh character variables $v_{\epsilon_1},\ldots,v_{\epsilon_m}$, and forcing their value to be $\epsilon$ by adding the linear formula 
+$$
+\Psi_\epsilon \defeq \bigwedge_{1\leq i \leq m} v_{\epsilon_i} = -1
+$$ % , to the output linear formulas $\phi_O$. 
+Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_i}$.
 %We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
 
-For the second issue, we rename the variables on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
+\newcommand\renvars{V_R^\mathsf{ver}}
+For the second issue, we rename the variables of $V_R$ on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
 The renaming is done by adding a version number to the variable.
-We call variables before and after renaming the \emph{original variable} and the \emph{renamed variable}.
-For example, we can rename $v_1$ to $v_1^{(0)}$, $v_1^{(1)}$, etc.
-In this case, $v_1$ is the original variable and both $v_1^{(0)}$ and $v_1^{(1)}$ are the renamed variables.
-We will an add arithmetic constraint $\Psi_{rename}$ (will be defined later) to enforce that variables renamed from the same variable are assigned the same value.
+Namely, we can rename $v_1$ to $v_1^{(0)}$, $v_1^{(1)}$, etc.
+In this case, $v_1$ is the \emph{original} variable and both $v_1^{(0)}$ and $v_1^{(1)}$ are \emph{version variables}.
+The set of all used version variables is denoted $\renvars$.
+We will later define an arithmetic constraint $\Psi_{\mathit{rename}}$ to enforce that versions of the same variable are assigned the same value as the original.
 
@@
 
-Now let $A$ and $A'$ over character variables $V$ and $V'$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$.
-We then construct the synchronization formula $\syncfof A {A'}$ and add it to $\Phi_O$.
-Recall that from Lemma~\ref{lemma:synccorrect}, each model of $\syncfof A {A'}$ corresponds to a pair of words in $\semof{A}$ and $\semof{A'}$.
+Now let $\leftA$ and $\rightA$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$, over character variables $\leftV$ and $\rightV$, respectively. 
+The underapproximation formula for $\phi_e$ will be based on the synchronisation formula $\syncfof {\leftA} {\rightA}$ for $\leftA$ and $\rightA$ conjoined with $\Psi_\epsilon$.
+Recall that from Lemma~\ref{lemma:synccorrect}, each model of $\syncfof {\leftA} {\rightA}$ corresponds to a pair of words in $\semof{\leftA}$ and $\semof{\rightA}$.
 However, this does not directly correspond to a model of the equality constraint $\phi_e$.
-The reason is that different occurrences of the same string variables can be assigned different values in $\semof{A}$ and $\semof{A'}$.
-To avoid this problem, we need to add the constraint $\Psi_{rename}$ that is defined below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
-
-$$ \Psi_{rename} \defeq
-\bigwedge_{v\in V_{x_1} \cup\ldots\cup V_{x_m} , v'\in R_v} v=v' \wedge \#v = \#v'
-$$
-Here $R_v$ is the set of variables renamed from the the original variable $v$. 
-The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect} below.
+The reason is that different versions of the same string variable can be assigned different values in $\semof{\leftA}$ and $\semof{\rightA}$.
+We need to add an additional constraint to force all versions of the same variables have the same value and also occur the same number of times in the Parikh image.
+%avoid this problem, we need to add the constraint $\Psi_{rename}$ that is defined below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
+%$$ \Psi_{rename} \defeq
+%\bigwedge_{v\in V_{x_1} \cup\ldots\cup V_{x_m} , v'\in R_v} v=v' \wedge \#v = \#v'
+%$$
+$$ \Psi_{\mathit{rename}} \defeq
+\bigwedge_{v\in V_R,v^{(i)}\in\renvars} v=v^{(i)} \wedge \#v = \#v^{(i)}
+$$
+The underapproximation of $\phi_e$ is now constructed as
+$$
+\underf R {\phi_2} \defeq \Psi_\epsilon \land \Psi_{\mathit{rename}} \land \syncfof \leftA \rightA
+$$
+
+\begin{lemma}
+$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
+\end{lemma}
+
+%Here $R_v$ is the set of variables renamed from the the original variable $v$. 
+%The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect} below.
 In the lemma, each tuple of words $(w_1,\ldots, w_m) \in \semof{A_{x_1}}\times\ldots\times\semof{A_{x_m}}$ represents a model of the equality constraint.
 Each tuple $(w_1,\ldots, w_m)$ satisfies the condition that if $x_i$ and $x_j$ are the same variable, then $w_i$ and $w_j$ should be the same word.
-
-\begin{lemma}\label{lemma:eqcorrect}
-	$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \\
-	    \left\{\begin{array}{c|cl}
-			(I^1\cup\pim^1)\ \cup&w_1=\decode A_{x_1}(I^1\cup\pim^1) & \wedge \\
-			(I^2\cup\pim^2)\ \cup&w_2=\decode A_{x_2}(I^2\cup\pim^2) & \wedge \\
-			\ldots&\ldots\\
-%			(I^{m-1}\cup\pim^{m-1}) &\cup&w_{m-1}=\decode A_{x_{m-1}}(I^{m-1}\cup\pim^{m-1}) & \wedge \\
-			(I^m\cup\pim^m)      &w_m=\decode A_{x_m}(I^m\cup\pim^m) & \wedge \\
-			&w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m & \wedge \\
-			&\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j &  \\
-        \end{array}\right\}
-	$
-\end{lemma}
-
-(An alternative description)
-
-\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$, we have
-
-	\begin{center}
-		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t.
+%
+%\begin{lemma}\label{lemma:eqcorrect}
+%	$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \\
+%	    \left\{\begin{array}{c|cl}
+%			(I^1\cup\pim^1)\ \cup&w_1=\decode A_{x_1}(I^1\cup\pim^1) & \wedge \\
+%			(I^2\cup\pim^2)\ \cup&w_2=\decode A_{x_2}(I^2\cup\pim^2) & \wedge \\
+%			\ldots&\ldots\\
+%%			(I^{m-1}\cup\pim^{m-1}) &\cup&w_{m-1}=\decode A_{x_{m-1}}(I^{m-1}\cup\pim^{m-1}) & \wedge \\
+%			(I^m\cup\pim^m)      &w_m=\decode A_{x_m}(I^m\cup\pim^m) & \wedge \\
+%			&w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m & \wedge \\
+%			&\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j &  \\
+%        \end{array}\right\}
+%	$
+%\end{lemma}
+%
+%(An alternative description)
+%
+%\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$ satisfying $\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$, we have 
+%	
+%	\begin{center}
+%		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t.
 $w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
-		iff\\
-		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$ and\\
-		$\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$.
-	\end{center}
-\end{lemma}
+%		iff\\
+%		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$.
+%	\end{center}
+%\end{lemma}
+%
+%\lh{Assume that we were working with a domain restriction $R:[x_i]_1^m\rightarrow \text{PFAs}$.
+%\begin{lemma}
+%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \encode R (\semof{\phi_e})$.
+%\end{lemma}
+%Also, we could denote by $V_R$ the varsiables $V_{x_1} \cup\ldots\cup V_{x_m}$ (these are the variables used by the domain restriction), 
+%and use $\# V_R$, so the lemma becomes \\ 
+%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_R \cup \# V_R} = \encode R (\semof{\phi_e})$.
+%
+%}
 
@@
 
-Assume that the constraint we take from $\Phi_I$ is a string-number conversion constraint  $\phi_s \defeq n=\sti{x}$. In this section, we how to make the corresponding linear formulas for $\Phi_O$.
+Last, we decribe the construction of $\underf R {\phi_s}$ for a string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
+%In this section, we how to make the corresponding linear formulas for $\Phi_O$.
 
@@
 The cause of the problem is that each loop in the PFA creates an exponential component in the constraint.
-An immediate idea would be that maybe we can pick some specific PFA that allow more efficient constraint solving.
+An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving.
 At the same time, we want to keep a good property, that is, the search space covers all integers up to $m$-digits.
@@
 The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
-In order to handle all numbers with up to $m$-digits, we propose to restrict the domain of $x$ to a PFA in Figure~\ref{fig:sfa_its}.
-The PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $\Psi_{v_0}\defeq v_0=0$ to $\Phi_O$ for such PFA.
+In order to handle all numbers with up to $m$-digits, we propose to restrict the domain of $x$ to so called \emph{number PFA}, illustrated in Figure~\ref{fig:sfa_its}.
+The number PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $\Psi_{v_0}\defeq v_0=0$ to $\Phi_O$ for such PFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
@@
 
-$$\Psi_{NaN} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
+$$\Psi_{\mathit{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
 
 Then we can specify the relation between $n$ and the character variables as follows:
-$$\Psi_n\defeq  (n=-1 \wedge \Psi_{NaN})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
+$$\Psi_n\defeq  (n=-1 \wedge \Psi_{\mathit{NaN}})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
 It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
-We add $\Psi_n$ to $\Phi_O$.
-
-The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$.
-
+$$
+\underf R {\psi_s} \defeq \Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} 
+$$
+
+%We add $\Psi_n$ to $\Phi_O$.
+%
+%
+%
+%The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$. 
+%
 %
@@
 \end{lemma}
-\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
-(An alternative description)
-\begin{lemma}\label{lemma:sticorrect}
-	For all $w \in \semof{A_{x}}$ and $c \in \mathbb{Z}$, we have 
-	\begin{center}
-		$\exists (I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}}$ s.t. $w=\decode {A_x}(I\cup\pim)$ and $I_n(n)=c$\\
-		iff\\
-		$c= \sti{w}$.
-	\end{center}
-
-\end{lemma}
-\hide{
-\begin{lemma}\label{lemma:sticorrect_pos}
-	$\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
-\end{lemma}
-In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
-
-\begin{lemma}\label{lemma:sticorrect_neg}
-	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
-	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+  \}$
-\end{lemma}
-In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}
+%\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
+%(An alternative description)
+%\begin{lemma}\label{lemma:sticorrect}
+%	For all $w \in \semof{A_{x}}$ and $c \in \mathbb{Z}$, we have 
+%	\begin{center}
+%		$\exists (I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}}$ s.t. $w=\decode {A_x}(I\cup\pim)$ and $I_n(n)=c$\\
+%		iff\\
+%		$c= \sti{w}$.
+%	\end{center}
+%	
+%\end{lemma}
+%\hide{
+%\begin{lemma}\label{lemma:sticorrect_pos}
+%	$\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
+%\end{lemma}
+%In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
+%
+%\begin{lemma}\label{lemma:sticorrect_neg}
+%	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
+%	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+  \}$
+%\end{lemma}
+%
+%In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}
+%
+%\lh{
+%\begin{lemma}
+%$
+%\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \encode  R(\semof{\phi_s})
+%$
+%\end{lemma}
+%The $n$ must somehow be handled properly by $\encode  R(\phi_s)$, I did not have time to think about it yet.
+%}
 

### 2019-11-16 draft_saturday.tex
struggle struggle struggle, bloody lemmas bloody lemmas bloody lemmas

--- 2019-11-15 draft.tex
@@
 \newcommand{\defeq}{::=}
+\newcommand{\encode}[1]{\mathit{encode}_{#1}}
 
@@
 \yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
-
-\newcommand{\encode}[1]{\mathit{encode}_{#1}}
-\lh{What about to put this somewhere, it will simplify formulation of the correctness lemmas. Roughly, formulation need to be polished a and explained:}
-Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$ encodings of $L\cap \semof A$ as
-the set $\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$.
-%
-A domain restriction $R$ for a string contraint $\phi$ over variables $X$ is a mapping that assigns to every variable $x\in X$ a PFA $R(x)$ such that for different variables $x,y \in X$, $R(x)$ and $R(y)$ have disjoint sets of variables.
-%
-For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$, and we left this notation to sets of interpretation in the standard manner, i.e.
-$\encode R J = \bigcup_{I \in J}\encode R (I)$.
-%
-In the following section, we will discuss how, given a string contraint $\phi$ and a domain restriction $R$,
-to build an arithmetic formula $\Psi$ such that $\semof\Psi_{V_R\cup\#V_R} = \encode R(\semof{\phi})$. 
-Tha is, formula $\Psi$ will capture $R$-encodings of soltuions of $\phi$ under the domain restriction given by $R$.
 
@@
 
+\subsection{Flat Domain Restriction}
+
+Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$ encodings of $L\cap \semof A$ as
+the set $\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$.
+%
+A domain restriction $R$ for a string contraint $\phi$ over variables $X$ is a mapping that assigns to every variable $x\in X$ a PFA $R(x)$ such that for different variables $x,y \in X$, $R(x)$ and $R(y)$ have disjoint sets of variables.
+%
+For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$, and we left this notation to sets of interpretation in the standard manner, i.e.
+$\encode R J = \bigcup_{I \in J}\encode R (I)$.
+%
+In the following section, we will discuss how, given a string contraint $\phi$ and a domain restriction $R$,
+to build an arithmetic formula $\Psi$ such that $\semof\Psi_{V_R\cup\#V_R} = \encode R(\semof{\phi})$. 
+Tha is, formula $\Psi$ will capture $R$-encodings of soltuions of $\phi$ under the domain restriction given by $R$.
+
 \subsection{Handling Regular Constraints Symbolically} \label{section:mem}

### 2019-11-17 draft.tex
moving things around in progress

@@
 \newcommand{\underf}[2]{\mathit{under}_#1(#2)}
+\newcommand{\pfaf}{\psi}
+
+\newcommand{\leftA}{A^{\mathit{left}}}
+\newcommand{\rightA}{A^{\mathit{right}}}
+\newcommand{\leftV}{V^{\mathit{left}}}
+\newcommand{\rightV}{V^{\mathit{right}}}
+\newcommand\renvars{V_R^\mathsf{ver}}
+
+\newcommand\insc{\phi_{\mathit{in}}}
+\newcommand\outlf{\Psi_{\mathit{out}}}
 
@@
 
+We will use four types of \emph{atomic string constraint}:
+
 An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
@@
 
-The \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
+A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
 For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$.
@@
 
-A \emph{string constraint} is a constraint of the above form. We say that a set of string constraint $\Phi$ is \emph{satisfiable}  iff $\bigcap_{\phi \in \Phi} \modelsof{\phi}$ is not empty.
+A \emph{string constraint} is then a conjunction of atomic string constraints, with the semantics defined in the standard manner. It is \emph{satisfiable} if its semantics is nonempty.
 
@@
 \section{Under-approximation} \label{section:under_approximate}
-In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\Phi_I$ to a set of equisatisfiable linear formulas $\Phi_O$ in polynomial-time.
+In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulas $\outlf$ in polynomial-time.
 We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
@@
 We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
-In each step, we take a string constraint from $\Phi_I$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\Phi_O$.
-We also add constraints to $\Phi_O$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
-
-More concretely, at the beginning, we move all integer constraints in $\Phi_I$ to the output linear formulas $\Phi_O$.
-After this step, $\Phi_I$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
+In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\outlf$.
+We also add constraints to $\outlf$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
+
+More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$.
+After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
 For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA.
@@
 
-After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\Phi_I$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\Phi_O$.
+After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\insc$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\outlf$.
 The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Parametric Flat Automata} \label{section:sfa}
+\section{Parametric Flat Automata} \label{section:sfa}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We introduce \emph{parametric flat automata} (PFA) that will be used to define patterns 
+We introduce \emph{parametric flat automata} that will be used to define patterns 
 used by the under-approximation module to restrict the domain of string variables.
-A \emph{parametric automaton} (PA) is a finite automaton operating over an alphabet $\cvar$ of \emph{character variables}. 
-A parametric flat automaton is a parametric automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ satisfying the following structural constraints:
+
+\paragraph{Flat automata}
+First, we say that an automaton FA 
+$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is \emph{flat} if it satisfies the following structural constraints:
 \begin{enumerate}
-	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a straight path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
-%, with pairwise distiand states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a straight path of $m-1$ transitions $(\st{i}{0},a_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
 	\item  
-Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
-Notice that case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
-%Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$). 
-%For each $j\in [1,l_i]$, we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$. 
-%(where $l_i = 0$ means that there is no cycle on $q_i$)
-	\item Each variable in $\cvar$ appears on at most one transition.% (but $\epsilon$ transition can appear multiple times). 
+Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, a_{i}^{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
+Notice that the case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
+	\item Each character in $\Sigma$ appears on at most one transition. 
 \end{enumerate}
+
+The crucial feature of flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver. 
+\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
+%
+This is facilitated by flatness, which guarantees that 
+every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$, i.e., $\decode A (\parikhof w)) = w$, and analogously for the entire language of $A$, as formalized by the following lemma.
+
+\begin{lemma}\label{lemma:parikh}
+For an flat FA $A$ and $w,w'\in L(A)$, if $\parikhof w = \parikhof {w'}$ then $w = w'$. 
+\end{lemma}
+%
+Indeed, since every variable appears on at most one transition, then the $\parikhof w$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
+%
+The accepting run on $w$ (and so $w$ itself) can thus be reconstructed from $\parikhof w$.
+
+For example, in the automaton of Figure~\ref{fig:sfa_def}, 
+from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
+
+We may say that $\parikhof w$ is an encoding of $w$, and define the decoding function $\decode A$ such that $\decode A(\parikhof w) = w$, and we lift the function to sets of integer assignments in the standard manner.
+%
+
+%\begin{lemma}\label{lemma:decx}
+%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
+%\end{lemma}
+%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
+%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
+
+\begin{lemma}\label{lemma:decx}
+%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in \parikhof A\}$.
+For a flat FA $A$, $L(A) = \decode A(\parikhof{L(A)}$.
+\end{lemma}
+%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
+%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
+%
+\begin{proof}
+The function $\decode A$ can particularly be implemented as follows. Given $\pim:\pvars\rightarrow\nat$,
+and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m-1}$, 
+$\decode A(\pim)$ is constructed as the word $w_0 a_{0} \ldots a_{m-1} w_{m-1}$ where for each $i\in [0,m-1]$,
+$w_i = (a_i^0 \cdots a_i^{l_{i-1}})^{\pvarsof {a_i^0}}$ if $l_i >0$ and $w_i = \epsilon$ if $l_i = 0$. 
+\end{proof}
+
+\paragraph{Parametric (flat) automata}
+Next we define \emph{parametric automaton} (PA) as a tuple $A = (Q,T,\cvar,\st{0}{0},\st{m}{0},\pfaf)$ where $\pfaf$ is an \emph{interpretation constraint}, a linear formula over $\cvar$, and $(Q,T,\cvar,\st{0}{0},\st{m}{0})$ is an automaton operating over an alphabet $\cvar$ of \emph{character variables}.
+\emph{Parametric flat automaton (PFA)} then is a parametric automaton with its finite automaton flat.
+
 \begin{figure*}
@@
 %
-Namely, word over $\cvar$ are interpreted as words over $\Sigma$ given an assignment of characters to its character variables.  
-%
-Formally, an \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$ and for a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-%
-We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics $\semof A$ of an PFA is the semantics of its language.
-
-The crucial feature of parametric flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver. 
-\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
-%
-This is facilitated by the structural constraints of PFA, which guarantee that 
-every parametric word $x\in L(A)$ is uniquely determined by its Parikh image $\parikhof{x}$, i.e., $\decode A (\parikhof x)) = x$, and analogously for the entire language of $A$, as formalized by the following lemma.
-
-\begin{lemma}\label{lemma:parikh}
-For an PFA $A$ and $x,y\in L(A)$, if $\parikhof x = \parikhof y$ then $x = y$. 
-\end{lemma}
-%
-Indeed, since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
-%
-The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. 
-%
-For example, in the automaton of Figure~\ref{fig:sfa_def}, 
-from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
-We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$, and we lift the function to sets of integer assignments in the standard manner.
-%
-
-%\begin{lemma}\label{lemma:decx}
-%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
-%\end{lemma}
-%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
-%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
-
-\begin{lemma}\label{lemma:decx}
-%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in \parikhof A\}$.
-For a PFA $A$, $L(A) = \decode A(\parikhof{L(A)}$.
-\end{lemma}
-%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
-%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
-%
-\begin{proof}
-The function $\decode A$ can particularly be implemented as follows. Given $\pim:\pvars\rightarrow\nat$,
-and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m-1}$, 
-$\decode A(\pim)$ is constructed as the word $x_0 v_{0} \ldots v_{m-1} x_{m-1}$ where for each $i\in [0,m-1]$,
-$x_i = (v_i^0 \cdots v_i^{l_{i-1}})^{\pvarsof {v_i^0}}$ if $l_i >0$ and $x_i = \epsilon$ if $l_i = 0$. 
-\end{proof}
+Namely, words over $\cvar$ are interpreted as words over $\Sigma$ under an
+\emph{interpretation of $\cvar$}
+%
+a mapping from $I:\cvar\rightarrow$ to $\Sigma_\epsilon$. For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+%
+We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics of an PFA is the semantics of its language restricted by the formula $\pfaf$, that is,  $\semof A = \semof{L(A)}\cap\semof\pfaf$.
 
@@
 we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric word $x$ encodes $w$.
-Lemma~\ref{lemma:parikh} also implies that two different words are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$.
-The following corrolary of Lemma~\ref{lemma:decx} states that encodings of words in $\semof{A}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$:%, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
+Lemma~\ref{lemma:parikh} also implies that two different words are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$, and we again lift the decoding function into sets of interpretations in the standard manner.
+The following corrolary of Lemma~\ref{lemma:decx} states that encodings of words in $\semof{A}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$ that satisfy $\pfaf$:%, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
 %
@@
 \begin{corollary}\label{corollary:pfa}
-For an PFA $A$ over character variables $V$,
+For an PFA $A = (Q,T,\cvarone,q_i,q_f,\pfaf)$,
 %$\semof{A} = \{(\decode A(I\cup\pim)) \mid \pim\in\parikhof A,I:\cvars\rightarrow\Sigma_\epsilon\}$.
-$\semof A = \decode A \{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I:\cvars\rightarrow\Sigma_\epsilon\}$
+\\
+$\semof A = \decode A \{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I\in\semof\pfaf\}$.
 \end{corollary}
 %
-A minor technical difficulty is that we wish to work with pure arithmetic formulas, 
+
+Last, we define the encoding function as a counterpart of the decoding. Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$-encodings of the words in $L$ as 
+$\encode A (L) = \{e \mid \decode A (e) \in L\}$. 
+%
+Notice that only the words from $L\cap \semof A$ have an $A$-encoding, 
+hence $\encode A(L) = \encode A(L\cap\semof A)$, and so due to Corollary~\ref{corollary:pfa}, $\decode A({\encode A}(L)) = L\cap\semof A$.
+%$\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$. 
+%We have that $\decode A \circ \encode A$ equal the identity function.
+%
+
+\section{Flat Domain Restriction}
+Let us now give a precise definition of how we restrict the domain of string constraints using flat automata. 
+A \emph{flat domain restriction} for a string contraint $\insc$ over variables $X$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
+For technical reasons that will be apparent further in this section, we require that if $x\neq  y$, then $R(x)$ and $R(y)$ operate over disjoint sets of character variables.
+We will use $V_R$ to denote the union of character variables of all $R(x),x\in X$.
+
+The semantics of a string constraint $\phi$ restricted by $R$ is then defined as 
+$\semof{\phi}^R = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{R(x)}\}$. 
+In the rest of this section, we will show how to build an \emph{underapproximating formula} representing the semantics $\semof{\insc}^R$ of an input string constraint, that is, a formula $\outlf$ such that
+$\decode R (\semof {\outlf}) = \semof{\insc}_R$.
+
+The formula $\outlf$ is built intuctively to the structure of $\insc$.
+Namely, in the followin subsections we show how to build a formula $\underf R {\phi}$ for every atomic string constraint $\phi$, 
+and for a conjunction of 
+string constraints we have $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
+% and $\underf R {\neg\phi} \defeq \neg\underf R{\phi}$. The underapproximation formula is then in the form $\outlf \defeq \underf R {\insc}$.
+
+The correctness of this construction, that is, that 
+$$\decode R (\semof {\outlf}) = \semof{\insc}^R$$ can be proved by induction to the structure of $\insc$.
+However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf R \phi$.
+Particularly, we will need to
+%pay attention to how $\underf R \phi$ atually encodes the models of $\phi$, and
+ ensure that $\underf R \phi$ captures exactly all $R$-encodings of $\semof \phi^R$
+(indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf R {\phi} \land \underf R {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^R$).
+
+To this end, we define an additional notation.
+For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$.
+We lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
+%
+The inductive argument needed in the proof of the correctness of the underapproximation then reads as
+$$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
+We note that the restriction of the semantics of $\underf R \phi$ here is needed here since it is constructed with some additional variables.
+
+\paragraph{Encoding $\epsilon$}
+A minor technical difficulty is that we wish to build underapproximation in the form of pure arithmetic formulas, 
 but we may also wish to specify when a character variable is assigned $\epsilon$, which is not a number. 
-Hence, to allow purely arithmetic formulas to talk about the value $\epsilon$, we encode $\epsilon$ as $-1$.
+To allow purely arithmetic formulas to talk about $\epsilon$, we encode $\epsilon$ as $-1$.
 In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulas constraining interpretations of character variables.
+
+%\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
+\section{Flattening of basic string constraints}
+By basic string constraints, we mean regular, equality, and lenght constraints.
+First, we discuss operations over PA needed to implement them, synchronisation and concatenation.
 
@@
 Particularly, the synchronization formula is built for two PAs  
-$A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
+$A = (Q,T,\cvarone,q_i,q_f,\pfaf)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f',\pfaf')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
 %
@@
 
-Formally, the asynchronous product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'))$, where the transition relation $\syncT$ is the minimal set satisfying the following:
+Formally, the asynchronous product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'),\pfaf\land\pfaf')$, where the transition relation $\syncT$ is the minimal set satisfying the following:
 %
@@
 \begin{lemma}\label{lemma:synccorrect}
+%$
+%\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = 
+%\{
+%(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
+%x\in L(A), x'\in L(A'), I(x) = I(x')
+%$
+%$
+%\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+%%\semof {\syncfof A {A'}} \iequiv
+%\{(I\cup I_\#)\cup (I' \cup I'_\#)\mid (I\cup I_\#) \in \encode A (w), (I' \cup I'_\#)\in\encode {A'} (w),w\in\semof A \cap \semof {A'}\} 
+%$
 $
 \semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-%\semof {\syncfof A {A'}} \iequiv
-\{(I\cup I_\#)\cup (I' \cup I'_\#)\mid (I\cup I_\#) \in \encode A (w), (I' \cup I'_\#)\in\encode {A'} (w),w\in\semof A \cap \semof {A'}\} 
+\{e\cup e'\mid e \in \encode A (w),\\ e'\in\encode {A'} (w), w\in\semof A \cap \semof {A'}\} 
 $
 \end{lemma}
+%\lh{the lemma is actually true even for two non-flat automata. Notice that in that case, the set of encodings does not correspond to the intersection precisely}
 
@@
 A minor technical difficulty is that the models of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
-Hence in the lemma, we use $\iequiv$ instead of $=$ to restrict the models to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
+Hence in the lemma,
+we use restric the semantics of $\syncfof A {A'}$ to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
 %This is  achieve by quantifying out the variables of $V_\times$.
@@
 $$\semof A \cap \semof {A'} = \decode A (\semof{\syncfof A {A'}}_{\cvarone\cup \pvarone})$$
+
+\paragraph{Concatenation of PFAs}
+Concatenation is another operation over PFAs needed when constructing underapproximations.
+Its implementation is straightforward, connect the final state of the first PFA with the initial state of the second by an $\epsilon$-transition.
+Sinco our automata do not allow $\epsilon$-transition,
+the connecting transition is labeled by a fres variable $v_\epsilon$ and the constraint $v_\epsilon$ is added to the interpretation contraint.
+
+Formally, given PFA $A = (Q,T,\cvarone,q_i,q_f,\pfaf)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f',\pfaf')$ with $Q\cap Q'=\emptyset = \cvarone\cap\cvartwo$, 
+their concatenation is the PFA $A\cdot A' = (Q\cup Q',T\cup T'\cup \{(q_f,v_\epsilon,q_i')\},\cvarone\cup\cvartwo\cup\{v_\epsilon\},q_i,q_f',\pfaf\land\pfaf'\land v_\epsilon = \epsilon)$ where $v_\epsilon$ is fresh, not from $\cvarone\cup\cvartwo$.
+
+\begin{lemma}
+For PFA $A$ and $A'$,  
+%$\encode{A\cdot A'}{\semof{A\cdot A}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+%\{(I\cup I_\#)\cup (I' \cup I'_\#)\mid$ $\\(I\cup I_\#) \in \encode A (w), (I' \cup I'_\#)\in\encode {A'} (w'),w\in\semof A,w'\in \semof {A'}\}$
+$\semof{A\cdot A'} = \semof{A}\cdot\semof{A'}$ and 
+%\begin{multline*}
+$\encode{A\cdot A'}{\semof{A\cdot A}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+\{e \cup e'\mid e \in \encode A (\semof{A}),\\ e' \in\encode {A'} (\semof{A'})\}$.
+%\end{multline*}
+\end{lemma}
+\lh{lemma ugly, unnecesarily complicated. Just remove this lemma?}
+The second part of the lemma states that each pair of encodings is projected to an encoding of a concatenation.
+It is important for the correctness of underapproximation construction in the next section (the first part does suffice).
+
+We are now ready to describe flattening of the basic string constraints.
 
@@
 
-\subsection{Flat Domain Restriction}
-Let us now give a precise definition of how we restrict the domain of string constraints using flat automata. 
-A \emph{flat domain restriction} for a string contraint $\phi$ over variables $X$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
-For technical reasons that will be apparent further in this section, we require that if $x\neq  y$, then $R(x)$ and $R(y)$ have disjoint sets of character variables.
-We will use $V_R$ to denote the union of character variables of all $R(x),x\in X$.
-
-The semantics of a string contraint $\Phi_I$ over a set of variables $X$ restricted by $R$ is defined as 
-$\semof\phi^R = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{R(x)}\}$. 
-In the rest of this section, we will show how to build an \emph{underapproximating formula} representing the semantics $\semof{\Psi_I}^R$ of an input string constraint, that is, a formula $\Psi_O$ such that
-$\{\decode R (\semof {\Psi_O})\} = \semof{\Psi_I}_R$.
-
-The formula $\Psi_O$ is build intuctively to the structure of $\Psi_O$.
-Namely, in the followin subsections we show how to build a formula $\underf R {\phi}$ for every atomic string constraint $\phi$, and for a Boolean combination of 
-string constraints we have $\underf R {\phi \land \phi'} = \underf R {\phi} \land \underf R {\phi'}$ and $\underf R {\neg\phi} = \neg\underf R{\phi}$.
-The underapproximation formula is then in the form $\Psi_O \defeq \underf R {\Psi_I}$.
-
-The correctness of this construction, that is, that 
-$$\decode R (\semof {\Psi_O}) = \semof{\Psi_I}^R$$ can be proved by induction to the structure of $\Psi_I$.
-However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf R \phi$.
-Particularly, we will need to
-%pay attention to how $\underf R \phi$ atually encodes the models of $\phi$, and
- ensure that $\underf R \phi$ captures exactly all $R$-encodings of $\semof \phi^R$.
-
-%
-To this end, we define the following notation.
-Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$ encodings of $L\cap \semof A$ as $\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$.
-%
-For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$.
-We left this notation to sets of interpretation in the standard manner, i.e., $\encode R J = \bigcup_{I \in J}\encode R (I)$ for a set of interpretation $J$.
-%
-The needed inductive argument of the correctness of the construction can be expressed as that 
-$$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
-We restrict need to restrict here interpretations of $\underf R \phi$ since its construction uses some additional variables.
-
-%\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
-\subsection{Underapproximation of Regular Constraints} \label{section:mem}
+\subsection{Flattening of Regular Constraints} \label{section:mem}
 
@@
 
-\subsection{Handling Equality Constraints Symbolically} \label{section:eq}
-\newcommand{\leftA}{A^{\mathit{left}}}
-\newcommand{\rightA}{A^{\mathit{right}}}
-\newcommand{\leftV}{V^{\mathit{left}}}
-\newcommand{\rightV}{V^{\mathit{right}}}
+\subsection{Flattening of Equality Constraints} \label{section:eq}
+%\subsection{Handling Equality Constraints Symbolically, Experimental version} \label{section:eq}
 
 We now describe the construction of $\underf R {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$. 
-We first build two PFAs $\leftA$ and $\rightA$ that encode the left-hand side term and the right-hand side term of the equality constraint.
-Intuitively, this can be achieved by connecting the PFAs restricting the string variables with epsilon transitions.
-However, there are two technical issues.
-First, our definition of PFA does not allow epsilon transition.
-%The second issue is more severe,
-Second,
-some string variable might occur multiple times in an equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
+%
+To simplify the construction, we assume that the varriables are pairwise different, i.e.
+that $i\neq j \implies x_i \neq x_j$.
+We may make this assumption without loss of generality, since whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoing the modified $\phi_e$ with a new equality $x_j = x_j'$.
+%
+
+We first build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side term of the equality constraint, respectively, by concatenating the restrictions of the individual variables.
+That is
+\begin{eqnarray*}
+\leftA \defeq& R(x_1)\cdot\ldots \cdot R(x_n)\\
+\rightA \defeq& R(x_{n+1})\cdot\ldots \cdot R(x_m)
+\end{eqnarray*}
+The underapproximation of $\phi_e$ is then obtained as their synchronisation formula
+$$
+\underf R {\phi_e} = \syncfof \leftA \rightA
+$$
+The correctness of the construction is stated by the lemma:
+\begin{lemma}\label{lemma:eqcorrect}
+$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
+\end{lemma}
+
+\subsection{Handling the lengths of variables}
+After the set $\insc$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
+To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
+
+$$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
+
+More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\outlf$.
+
+$$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
+
+\hide{The length of $x$ can be specified by the following formula.
+
+$\begin{array}{ccc}
+	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\vee \\
+	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\vee \\
+	& &\ldots\\
+	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\vee\\
+	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
+\end{array}$}
+
+%\subsection{Handling Equality Constraints Symbolically, old verion, not updated} \label{section:eq}
+%\subsection{Handling Equality Constraints Symbolically, old verion, not updated} \label{section:eq}
+%
+%We now describe the construction of $\underf R {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$.
+We first build two PFAs $\leftA$ and $\rightA$ that encode the left-hand side term and the right-hand side term of the equality constraint by concatenating the restrictions of the individual variables.
+%% Intuitively, this can be achieved by connecting the PFAs restricting the string variables with epsilon transitions. However, there are two technical issues. 
+%%First, our definition of PFA does not allow epsilon transition. %The second issue is more severe, 
+%Second,
+%some string variable might occur multiple times in an equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
 We will need a way to force that all occurrences of the same string variable are assigned the same value.
-
-We circumvent the first problem by fresh character variables $v_{\epsilon_1},\ldots,v_{\epsilon_m}$, and forcing their value to be $\epsilon$ by adding the linear formula 
-$$
-\Psi_\epsilon \defeq \bigwedge_{1\leq i \leq m} v_{\epsilon_i} = -1
-$$ % , to the output linear formulas $\phi_O$. 
-Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_i}$.
+%
+%We circumvent the first problem by fresh character variables $v_{\epsilon_1},\ldots,v_{\epsilon_m}$, and forcing their value to be $\epsilon$ by adding the linear formula 
+%$$
+%\Psi_\epsilon \defeq \bigwedge_{1\leq i \leq m} v_{\epsilon_i} = -1
+%$$ % , to the output linear formulas $\phi_O$. 
+%Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_i}$.
 %We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
-
-\newcommand\renvars{V_R^\mathsf{ver}}
-For the second issue, we rename the variables of $V_R$ on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
+%
+%For the second issue, we rename the variables of $V_R$ on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
 The renaming is done by adding a version number to the variable.
@@
 The set of all used version variables is denoted $\renvars$.
-We will later define an arithmetic constraint $\Psi_{\mathit{rename}}$ to enforce that versions of the same variable are assigned the same value as the original.
-
-Here we give a concrete example.
+%We will later define an arithmetic constraint $\Psi_{\mathit{rename}}$ to enforce that versions of the same variable are assigned the same value as the original. 
+%
+%
+%Here we give a concrete example.
 For the equality constraint $xy = yx$, assume that we restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
 In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon'' transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
-
-Now let $\leftA$ and $\rightA$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$, over character variables $\leftV$ and $\rightV$, respectively. 
-The underapproximation formula for $\phi_e$ will be based on the synchronisation formula $\syncfof {\leftA} {\rightA}$ for $\leftA$ and $\rightA$ conjoined with $\Psi_\epsilon$.
+%
+%Now let $\leftA$ and $\rightA$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$, over character variables $\leftV$ and $\rightV$, respectively. 
+%The underapproximation formula for $\phi_e$ will be based on the synchronisation formula $\syncfof {\leftA} {\rightA}$ for $\leftA$ and $\rightA$ conjoined with $\Psi_\epsilon$.
 Recall that from Lemma~\ref{lemma:synccorrect}, each model of $\syncfof {\leftA} {\rightA}$ corresponds to a pair of words in $\semof{\leftA}$ and $\semof{\rightA}$.
@@
 We need to add an additional constraint to force all versions of the same variables have the same value and also occur the same number of times in the Parikh image.
-%avoid this problem, we need to add the constraint $\Psi_{rename}$ that is defined below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
-%$$ \Psi_{rename} \defeq
-%\bigwedge_{v\in V_{x_1} \cup\ldots\cup V_{x_m} , v'\in R_v} v=v' \wedge \#v = \#v'
+%%avoid this problem, we need to add the constraint $\Psi_{rename}$ that is defined below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
+%%$$ \Psi_{rename} \defeq
+%%\bigwedge_{v\in V_{x_1} \cup\ldots\cup V_{x_m} , v'\in R_v} v=v' \wedge \#v = \#v'
+%%$$
+%$$ \Psi_{\mathit{rename}} \defeq
+%\bigwedge_{v\in V_R,v^{(i)}\in\renvars} v=v^{(i)} \wedge \#v = \#v^{(i)}
 %$$
-$$ \Psi_{\mathit{rename}} \defeq
-\bigwedge_{v\in V_R,v^{(i)}\in\renvars} v=v^{(i)} \wedge \#v = \#v^{(i)}
-$$
-The underapproximation of $\phi_e$ is now constructed as
-$$
-\underf R {\phi_2} \defeq \Psi_\epsilon \land \Psi_{\mathit{rename}} \land \syncfof \leftA \rightA
-$$
-
-\begin{lemma}
-$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
-\end{lemma}
-
-%Here $R_v$ is the set of variables renamed from the the original variable $v$. 
-%The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect} below.
+%The underapproximation of $\phi_e$ is now constructed as
+%$$
+%\underf R {\phi_e} \defeq \Psi_\epsilon \land \Psi_{\mathit{rename}} \land \syncfof \leftA \rightA
+%$$
+%
+%\begin{lemma}\label{lemma:eqcorrect}
+%$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
+%\end{lemma}
+%
+%
+%%Here $R_v$ is the set of variables renamed from the the original variable $v$. 
+%%The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect} below.
 In the lemma, each tuple of words $(w_1,\ldots, w_m) \in \semof{A_{x_1}}\times\ldots\times\semof{A_{x_m}}$ represents a model of the equality constraint.
 Each tuple $(w_1,\ldots, w_m)$ satisfies the condition that if $x_i$ and $x_j$ are the same variable, then $w_i$ and $w_j$ should be the same word.
-%
-%\begin{lemma}\label{lemma:eqcorrect}
-%	$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \\
-%	    \left\{\begin{array}{c|cl}
-%			(I^1\cup\pim^1)\ \cup&w_1=\decode A_{x_1}(I^1\cup\pim^1) & \wedge \\
-%			(I^2\cup\pim^2)\ \cup&w_2=\decode A_{x_2}(I^2\cup\pim^2) & \wedge \\
-%			\ldots&\ldots\\
-%%			(I^{m-1}\cup\pim^{m-1}) &\cup&w_{m-1}=\decode A_{x_{m-1}}(I^{m-1}\cup\pim^{m-1}) & \wedge \\
-%			(I^m\cup\pim^m)      &w_m=\decode A_{x_m}(I^m\cup\pim^m) & \wedge \\
-%			&w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m & \wedge \\
-%			&\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j &  \\
-%        \end{array}\right\}
-%	$
-%\end{lemma}
-%
-%(An alternative description)
-%
-%\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$ satisfying $\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$, we have 
-%	
-%	\begin{center}
-%		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t.
+%%
+%%\begin{lemma}\label{lemma:eqcorrect}
+%%	$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \\
+%%	    \left\{\begin{array}{c|cl}
+%%			(I^1\cup\pim^1)\ \cup&w_1=\decode A_{x_1}(I^1\cup\pim^1) & \wedge \\
+%%			(I^2\cup\pim^2)\ \cup&w_2=\decode A_{x_2}(I^2\cup\pim^2) & \wedge \\
+%%			\ldots&\ldots\\
+%%%			(I^{m-1}\cup\pim^{m-1}) &\cup&w_{m-1}=\decode A_{x_{m-1}}(I^{m-1}\cup\pim^{m-1}) & \wedge \\
+%%			(I^m\cup\pim^m)      &w_m=\decode A_{x_m}(I^m\cup\pim^m) & \wedge \\
+%%			&w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m & \wedge \\
+%%			&\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j &  \\
+%%        \end{array}\right\}
+%%	$
+%%\end{lemma}
+%%
+%%(An alternative description)
+%%
+%%\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$ satisfying $\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$, we have 
+%%	
+%%	\begin{center}
+%%		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t.
 $w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
-%		iff\\
-%		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$.
-%	\end{center}
-%\end{lemma}
-%
-%\lh{Assume that we were working with a domain restriction $R:[x_i]_1^m\rightarrow \text{PFAs}$.
-%\begin{lemma}
-%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \encode R (\semof{\phi_e})$.
-%\end{lemma}
-%Also, we could denote by $V_R$ the varsiables $V_{x_1} \cup\ldots\cup V_{x_m}$ (these are the variables used by the domain restriction), 
-%and use $\# V_R$, so the lemma becomes \\ 
-%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_R \cup \# V_R} = \encode R (\semof{\phi_e})$.
-%
-%}
-
-\hide{
-Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the PFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the PFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
+%%		iff\\
+%%		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$.
+%%	\end{center}
+%%\end{lemma}
+%%
+%%\lh{Assume that we were working with a domain restriction $R:[x_i]_1^m\rightarrow \text{PFAs}$.
+%%\begin{lemma}
+%%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \encode R (\semof{\phi_e})$.
+%%\end{lemma}
+%%Also, we could denote by $V_R$ the varsiables $V_{x_1} \cup\ldots\cup V_{x_m}$ (these are the variables used by the domain restriction), 
+%%and use $\# V_R$, so the lemma becomes \\ 
+%%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_R \cup \# V_R} = \encode R (\semof{\phi_e})$.
+%%
+%%}
+%
+%
+%\hide{
+%Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the PFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the PFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
 Our next task is to find a model for $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$ under the domain restriction specified by $S_n$ and $S_m$.
-Note that $\cvarone \cap \cvartwo =\emptyset$, because all variables will be renamed to some fresh variable.
-
-This is equivalent to finding a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and a common interpretation $I$ such that 
-\begin{enumerate}
-	\item $I(w_n)=I(w_m)$
-	\item $I$ assign to variants of the same variable the same value. For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}$ and $v_0^{(1)}$ should be assigned the same value.
-	\item different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
+%Note that $\cvarone \cap \cvartwo =\emptyset$, because all variables will be renamed to some fresh variable. 
+%
+%
+%This is equivalent to finding a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and a common interpretation $I$ such that 
+%\begin{enumerate}
+%	\item $I(w_n)=I(w_m)$
+%	\item $I$ assign to variants of the same variable the same value. For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}$ and $v_0^{(1)}$ should be assigned the same value.
+%	\item different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
 For example, in Figure~\ref{fig:sfa} (c) and (d), $w_{xy}=v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $w_{yx}=v_0^{(1)}v_1^{(1)}v_0^{(1)}v_1^{(1)}$ is a pair of symbolic strings satisfying this condition.
 The number of occurrences of $v_i^{(0)}$ is the same to $v_i^{(1)}$ for $i\in[0,1]$ in the concatenation $w_{xy}\cdot w_{yx}$.
-	But the pair $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_2^{(0)}v_3^{(0)}v_2^{(0)}v_3^{(0)}$ does not satisfy the condition. Observe that $v_0^{(0)}$ occurs twice, but $v_0^{(1)}$ is not there.
-\end{enumerate}
-
-In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
-
-Such product automaton uses $Q\times P$ as the set of states and 
-%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
-$\cvarone\times\cvartwo$
-as the alphabet.
+%	But the pair $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_2^{(0)}v_3^{(0)}v_2^{(0)}v_3^{(0)}$ does not satisfy the condition. Observe that $v_0^{(0)}$ occurs twice, but $v_0^{(1)}$ is not there.
+%\end{enumerate}
+%
+%In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
+%
+%Such product automaton uses $Q\times P$ as the set of states and 
+%%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
+%$\cvarone\times\cvartwo$
+%as the alphabet.
 If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
-
-More precisely, the product automaton is a tuple $\syncof A B = (Q\times P, \syncT, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $\syncT$ is the minimal set satisfying the following.
-
-\begin{itemize}
-\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in \syncT$.
-\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in \syncT$.
-\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in \syncT$.
-\end{itemize}	
-The first two cases correspond to the situation when the character variable $v_i^{(j)}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
-
-For example, in the product automaton $A_{xy=yx}$ corresponds to $xy=yx$, we have the following transitions
-\begin{itemize}
-	\item $((q_0,p_0), (v_0^{(0)},\epsilon),(q_1,p_0))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$.
-	\item $((q_0,p_0), (\epsilon,\epsilon),(q_0,q_0))$, because $(p_0,\epsilon,q_0)$ is a transition of $A_{yx}$.
-	\item $((q_0,p_0), (v_0^{(0)},v_2^{(1)}),(q_1,q_1))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$ and $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
-\end{itemize}
-
-Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section~\ref{section:sfa}) and for any finite automaton we can construct a Presburger formula characterizing its Parikh image (Section~\ref{section:preliminary}).
+%
+%More precisely, the product automaton is a tuple $\syncof A B = (Q\times P, \syncT, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $\syncT$ is the minimal set satisfying the following.
+%
+%\begin{itemize}
+%\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in \syncT$.
+%\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in \syncT$.
+%\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in \syncT$.
+%\end{itemize}	
+%The first two cases correspond to the situation when the character variable $v_i^{(j)}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
+%
+%For example, in the product automaton $A_{xy=yx}$ corresponds to $xy=yx$, we have the following transitions
+%\begin{itemize}
+%	\item $((q_0,p_0), (v_0^{(0)},\epsilon),(q_1,p_0))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$.
+%	\item $((q_0,p_0), (\epsilon,\epsilon),(q_0,q_0))$, because $(p_0,\epsilon,q_0)$ is a transition of $A_{yx}$.
+%	\item $((q_0,p_0), (v_0^{(0)},v_2^{(1)}),(q_1,q_1))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$ and $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
+%\end{itemize}
+%
+%Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section~\ref{section:sfa}) and for any finite automaton we can construct a Presburger formula characterizing its Parikh image (Section~\ref{section:preliminary}).
 For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{\#{(v_i^{(j)},v_{i'}^{(j')})}\mid (v_i^{(j)},v_{i'}^{(j')}) \in \cvarone \times \cvartwo\}$ characterizing the Parikh image of $A$.
@@
 The following formulas establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
-\begin{enumerate}
-	\item for all $v_i^{(j)} \in \cvarone$, $\#(v_i^{(j)}) = \sum_{v \in {\cvartwo \cup \{\epsilon\}}} \#{(v_i^{j},v)}$   
-	\item for all $v_i^{(j)} \in \cvartwo$, $\#(v_i^{(j)}) = \sum_{v \in {\cvarone \cup \{\epsilon\}}} \#{(v,v_i^{j})}$ 
-\end{enumerate}
-
-Then we add the following linear constraints to enforce  condition 1.
+%\begin{enumerate}
+%	\item for all $v_i^{(j)} \in \cvarone$, $\#(v_i^{(j)}) = \sum_{v \in {\cvartwo \cup \{\epsilon\}}} \#{(v_i^{j},v)}$   
+%	\item for all $v_i^{(j)} \in \cvartwo$, $\#(v_i^{(j)}) = \sum_{v \in {\cvarone \cup \{\epsilon\}}} \#{(v,v_i^{j})}$ 
+%\end{enumerate}
+%
+%Then we add the following linear constraints to enforce  condition 1.
 and 2.
 required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
-\begin{enumerate}
-	\item for all $v_i^{(j)}\in \cvarone$ and $v_{i'}^{(j')}\in \cvartwo$, $\#{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$,\lh{typo?} 
-	\item for all $v_i^{(j)}\in \cvarone$, $\#{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and
-	\item for all $v_{i'}^{(j')}\in \cvartwo$,$\#{(\epsilon,v_{i'}^{(j')})}>0 \rightarrow (v_{i'}=\epsilon)$.
-\end{enumerate}
-We then add the linear constraints $\#(v_i) = \#(v_i^{(j)})$, for all $v_i\in \cvar$ and all different version numbers $j$ for $v_i$, to enforce condition 3, which says different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
-
-From the model $M$ of the linear constraints, we can obtain $w_n$, $w_m$, and $I$.
+%\begin{enumerate}
+%	\item for all $v_i^{(j)}\in \cvarone$ and $v_{i'}^{(j')}\in \cvartwo$, $\#{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$,\lh{typo?} 
+%	\item for all $v_i^{(j)}\in \cvarone$, $\#{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and
+%	\item for all $v_{i'}^{(j')}\in \cvartwo$,$\#{(\epsilon,v_{i'}^{(j')})}>0 \rightarrow (v_{i'}=\epsilon)$.
+%\end{enumerate}
+%We then add the linear constraints $\#(v_i) = \#(v_i^{(j)})$, for all $v_i\in \cvar$ and all different version numbers $j$ for $v_i$, to enforce condition 3, which says different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
+%
+%From the model $M$ of the linear constraints, we can obtain $w_n$, $w_m$, and $I$.
 The interpretation $I$ is defined as $I(v)=M(v)$ for all $v\in (\cvarone \cup \cvartwo)$.
 The symbolic words $w_n$ and $w_m$ can be obtained by traverse the PFAs following the number of occurrences of each character variables.
-More specifically, assume that the PFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{\#(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{\#(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{\#(v_m^0)}$$
-Note that $\#(v_0^0)=\#(v_0^1)=\#(v_0^2)=\#(v_0^3)$, so we just use $\#(v_0^0)$ to denote the number of times of first loop traversal.
+%More specifically, assume that the PFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{\#(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{\#(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{\#(v_m^0)}$$
+%Note that $\#(v_0^0)=\#(v_0^1)=\#(v_0^2)=\#(v_0^3)$, so we just use $\#(v_0^0)$ to denote the number of times of first loop traversal.
 One can construct $w_m$ in a similar way.
 Using the same approach, one can derive the assignment to variables in $\vars$ using the corresponding count and values of variables in $\cvar$.
-
-}
+%
+%
+%
+%
+%
+%
+%
+%}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Handling String-Integer Conversion} \label{section:s2i}
+%\subsection{Handling String-Integer Conversion} \label{section:s2i}
+\section{Flattening of String-Integer Conversion} \label{section:s2i}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In order to handle all numbers with up to $m$-digits, we propose to restrict the domain of $x$ to so called \emph{number PFA}, illustrated in Figure~\ref{fig:sfa_its}.
-The number PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $\Psi_{v_0}\defeq v_0=0$ to $\Phi_O$ for such PFA.
+The number PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $\Psi_{v_0}\defeq v_0=0$ to $\outlf$ for such PFA.
 With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
@@
 In order to simplify the construction, we use an encoding to shift all the $\epsilon$-transitions to the least significant digits, i.e., if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j+1,m]$.
-To explain this encoding, we first define two macro function:
-
-$$\begin{array}{rl}
-\mathsf{epsilonAfter(k)}\defeq& (0\leq v_1,\ldots, v_k\leq 9) \wedge\\
-&v_{k+1}=\ldots =v_m = -1\\
-\mathsf{toNumber(k)}\defeq& (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
-\end{array}
-$$
-
-The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$.
+
+Consequently, for string variables that appear within string-to-int constraints, such as $x$ within $\phi_s$, we approximate $x$ by a special PFA, 
+called \emph{$m$-digit PFA}. They are of the form $R(x) = (Q,T,\cvarone,q_i,q_f,\pfaf)$ where the automaton is as on Figure~\ref{fig:sfa_its} and the interpretation restriction is the formula
+$$
+\pfaf \defeq  \Psi_{\mathsf{NaN}} \lor \Psi_{\mathsf{Number}}
+$$
+where $\Psi_{\mathsf{NaN}}$ captures the case when $x$ is ``not a number'': 
+$$
+\Psi_{\mathsf{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9
+$$ 
+and $\Psi_{\mathsf{Number}}$ caputures the case when $x$ is a valied encoding of a number.
+$\Psi_{\mathsf{Number}}$ aslo forces $R(x)$ to encode the number in a particular way, namely, the intial self-loop may only generate trailing zeros and %variables that are assigned $\epsilon$ can only be used at the end of the number:
+the first $k$ variables are some numbers and those after $k$ are assigned $\epsilon$. 
+%Recall that we use $-1$ to represent $\epsilon$.
+The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
+\yfc{say shifting $\epsilon$ to the right will not change the language}
+
+$$
+\Psi_{\mathsf{Number}}:= v_0 = 0 \land \bigwedge_{1\leq i \leq m} v_i \neq -1 \implies v_{i-1}\neq -1.
+$$
+
+With the domain restriction for $x$ in the above form,
+we define the underapproximation of $\phi_s$ as
+\begin{multline*}
+\underf R {\psi_s} 
+\defeq 
+\parikhfof{R(x)} 
+\land \\
+\bigl((\Psi_{\mathsf{NaN}} \land n = -1) 
+\lor 
+(\neg\Psi_{\mathsf{NaN}} \land \Psi_{\mathsf{toNumber}})\bigr)
+\end{multline*}
+where $\Psi_{\mathsf{toNumber}}$ si the actual conversion of the string to an integer.
+$$
+\Psi_{\mathsf{toNumber}}\defeq \bigvee_{1\leq k \leq m} \Psi_{\mathsf{last(k)}} \land (n = v_1* 10^{k-1} + v_2* 10^{k-2} + \ldots + v_{k})
+$$
+The function $\Psi_{\mathsf{last(k)}}$ is used above to detect the last variable $v_k$ that encodes a digit (all the variables with a higher index encode $\epsilon$):
+$$
+\Psi_{\mathsf{last(k)}} \defeq (k = m \land v_k \geq 0) \lor (v_{k} \geq 0 \land v_{k+1} = -1)
+$$
+
+Let $I$ be an interpretation of string variables and $I'$ an interpetation of integer variables. We define $\encode R {(I\cup I')}$ as $\{e \cup I' \mid e\in \encode R(I)\}$. 
+The bloody bastard correctness lemma now says that 
+\begin{lemma}
+$
+\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R(\semof{\phi_s})
+$
+\end{lemma}
+
+%
+%
+%$$
+%\mathsf{toNumber(k)}\defeq (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
+%$$
+%
+%
+%
+%
+%$$\Psi_{\mathsf{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
+%where $ $
+%To explain this encoding, we first define two macro function:
+%
+%$$\begin{array}{rl}
+%\mathsf{epsilonAfter(k)}\defeq& (0\leq v_1,\ldots, v_k\leq 9) \wedge\\
+%&v_{k+1}=\ldots =v_m = -1\\
+%\mathsf{toNumber(k)}\defeq& (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
+%\end{array}
+%$$
+
+%The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$.
 Recall that we use $-1$ to represent $\epsilon$.
@@
 
-The condition that when $x$ is ``not a number'' is specified by the following formula.
-
-$$\Psi_{\mathit{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
-
-Then we can specify the relation between $n$ and the character variables as follows:
-$$\Psi_n\defeq  (n=-1 \wedge \Psi_{\mathit{NaN}})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
-It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
-$$
-\underf R {\psi_s} \defeq \Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} 
-$$
+%The condition that when $x$ is ``not a number'' is specified by the following formula.
+%
+%$$
+%\Psi_{\mathit{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
+%
+%Then we can specify the relation between $n$ and the character variables as follows:
+%$$\Psi_n\defeq  (n=-1 \wedge \Psi_{\mathit{NaN}})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
+%It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
+%$$
+%\underf R {\psi_s} \defeq \Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {R(x)} 
+%$$
+%To formulate the correctness lemma similar to Lemmas~\ref{lemma:memcorrect} and \ref{lemma:eqcorrect}, we need to consider a modified semantics of $R(x)$.
+%Namely, we assume that $\semof{R(x)}$ is returns $\decode A(\parikhof{R(x)} \land )$
 
@@
 
-\begin{lemma}\label{lemma:sticorrect}
-
-	The interpretation $(I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} $ if and only if 
-	\begin{center}
-	 $\left(\begin{array}{c} 
-	 I_n(n)= \sti{\decode {A_x}(I\cup\pim)} \ \wedge \\
-	 I(v_i)=-1 \wedge i<j \Longrightarrow  I(v_j)=-1
-	 \end{array}\right)$\\ or\\
-	 $\left(\begin{array}{c} 
-	 I_n(n)= -1\ \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+
-	 \end{array}\right)$
-	\end{center}
-
-\end{lemma}
+%\begin{lemma}\label{lemma:sticorrect}
+%	
+%	The interpretation $(I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} $ if and only if 
+%	\begin{center}
+%	 $\left(\begin{array}{c} 
+%	 I_n(n)= \sti{\decode {A_x}(I\cup\pim)} \ \wedge \\
+%	 I(v_i)=-1 \wedge i<j \Longrightarrow  I(v_j)=-1
+%	 \end{array}\right)$\\ or\\
+%	 $\left(\begin{array}{c} 
+%	 I_n(n)= -1\ \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+
+%	 \end{array}\right)$
+%	\end{center}
+%
+%\end{lemma}
 %\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
@@
 
-\subsection{Handling the lengths of variables}
-After the set $\Phi_I$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
-To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
-
-$$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
-
-More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\Phi_O$.
-
-$$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
-
-\hide{The length of $x$ can be specified by the following formula.
-
-$\begin{array}{ccc}
-	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\vee \\
-	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\vee \\
-	& &\ldots\\
-	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\vee\\
-	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
-\end{array}$}
-
 % \section{Evaluation}

### 2019-11-17 draft.tex
little things

@@
 Its implementation is straightforward, connect the final state of the first PFA with the initial state of the second by an $\epsilon$-transition.
-Sinco our automata do not allow $\epsilon$-transition,
-the connecting transition is labeled by a fres variable $v_\epsilon$ and the constraint $v_\epsilon$ is added to the interpretation contraint.
+Since our automata do not allow transition directly labeled by $\epsilon$,
+the $\epsilon$-transition is labeled by a fresh variable $v_\epsilon$ contrained by the constraint $v_\epsilon = \epsilon$.
 

### 2019-11-18 draft.tex
some updates to intro

@@
 \newcommand{\petr}[1]{{\color{pink}Petr: #1}}
+\newcommand{\chatAt}[2]{\mbox{\textsf{charAt}($#1$, $#2$)}}
+\newcommand{\ite}[3]{\mbox{\textsf{ite}($#1$, $#2$, $#3$)}}
 \newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
@@
 
-String constraint solving has received considerable attention in the constraint solving community, with solvers such as CVC4 and Z3 implementing solvers of ever-increasing sophistication.
+The path feasibility problem is a critical module in the analysis of string-manipulating programs.
+The problem is usually solved by a reduction to a string constraint satisfiability problem.
+Program statements in the path are translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{string constraint solvers}.
+Among all types of program statements, \emph{string-number conversion} is one of the core operations that requires stronger solver support.
+
+The string-number conversion operations are widely used in string manipulating programs and algorithms.
+For example, the program fragment below is an implementation of the Luhn test algorithm that is often used in credit card or personal ID validation.
+
+\begin{verbatim}
+function checkLuhn(value) {
+  var sum = 0;
+  for (var i = value.length - 1; i >= 0; i-=2) {
+    var d = parseInt(value.charAt(i));
+    sum += d;
+  }	
+  for (var i = value.length - 2; i >= 0; i-=2) {
+    var d = parseInt(value.charAt(i));
+    if ((d *= 2) > 9) digit -= 9;
+    sum += d;
+  }
+  var last= sum.toString().charAt(sum.length-1);
+  return last == '0';
+}
+\end{verbatim}
+
+The input \verb|value| is a sequence of digits.
+The algorithm process the digits in the reversed order.
+The value of every odd digit (e.g., 1st, 3rd, etc.) is added to \verb|sum| directly.
+For the value of every even digit, the algorithm (1) doubles its value, (2) substracts its value by $9$ if the doubled-value is bigger than $9$, and (3) adds the final result to \verb|sum|.
+At the end, the input is validated if the string value of \verb|sum| ends in $0$.
+
+To check whether the program path that traverses both loop exactly once and finally passes this test has a valid input, we create the following string constraint:
+
+$$\begin{array}{lc}
+1&	value_0 \in [0,9]^+ \wedge 	sum_0 = 0 \wedge \\
+2&	i_0 = |value_0| -1 \wedge \\
+%	value_0 = prefix_0\cdot charAt_0 \cdot suffix_0 \wedge\\
+%	|prefix_0| = i_0 \wedge |charAt_0| = 1 \wedge \\
+3&	d_0 = \sti{\chatAt{value_0}{i_0}} \wedge \\
+4&	sum_1 = sum_0 + d_0 \wedge\\
+5&	i_1 = |value_0| -2 \wedge \\
+6&	d_1 = \sti{\chatAt{value_0}{i_1}} \wedge \\
+7&	sum_2 = sum_1 + \ite{d_1*2>9}{d_1*2 -9}{d_1*2} \wedge\\
+8&	last_0 = \chatAt{\its{sum_2}}{|\its{sum_2}|-1} \wedge\\
+9&	last_0 ==``0"
+\end{array}$$
+
+\yfc{explain the constraints and say all membership, concatenation, length, string-number conversion are required.}
+
+\hide{String constraint solving has received considerable attention in the constraint solving community, with solvers such as CVC4 and Z3 implementing solvers of ever-increasing sophistication.
 Operations such as substring and string length are widely supported, and recent solvers such as Z3-str3 have shown impressive results.
@@
 at least one side of the conversion must be a constant.
-Thus, $n = \sti{x}$ or $x = \its{5}$ are handled but $n = \sti{x}$ will fail.
+Thus, $n = \sti{"15"}$ or $x = \its{5}$ are handled but $n = \sti{x}$ will fail.}
 

### 2019-11-18 draft.tex

@@
 \newcommand{\ite}[3]{\mbox{\textsf{ite}($#1$, $#2$, $#3$)}}
-\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
+\newcommand{\sti}[1]{\mbox{\textsf{toNum}($#1$)}}
 \newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
@@
 
-The path feasibility problem is a critical module in the analysis of string-manipulating programs.
+The path feasibility problem is a critical module in the symbolic execution of string-manipulating programs.
 The problem is usually solved by a reduction to a string constraint satisfiability problem.
@@
 
-\begin{verbatim}
+\begin{Verbatim}[fontsize=\small]
 function checkLuhn(value) {
@@
 }
-\end{verbatim}
+\end{Verbatim}
 
@@
 $$\begin{array}{lc}
-1&	value_0 \in [0,9]^+ \wedge 	sum_0 = 0 \wedge \\
+1&	value_0 \in [1,9]^+ \wedge 	sum_0 = 0 \wedge \\
 2&	i_0 = |value_0| -1 \wedge \\
@@
 7&	sum_2 = sum_1 + \ite{d_1*2>9}{d_1*2 -9}{d_1*2} \wedge\\
-8&	last_0 = \chatAt{\its{sum_2}}{|\its{sum_2}|-1} \wedge\\
-9&	last_0 ==``0"
+8&  i_2 = 0\\
+9&	last_0 = \chatAt{\its{sum_2}}{|\its{sum_2}|-1} \wedge\\
+10&	last_0 =``0"
 \end{array}$$
 
-\yfc{explain the constraints and say all membership, concatenation, length, string-number conversion are required.}
+Here $value_0$ and $last_0$ are string variables and others are integer variables.
+Line 1 describes the initial condition: \textsf{value} should be a sequence of digits and \textsf{sum} is initially zero.
+Lines 2-4 and lines 5-7 describe one execution of the first and second loop, respectively.
+Line 8 describes the condition of $i_2$ before leaving the loop.
+Finally, Lines 9-10 describe the condition that the last digit of sum is zero.
+Observe that to describe such a program path, we need a solver that supports the following types of constraints:
+\begin{itemize}
+	\item \emph{regular} constraints (e.g., $value_0 \in [0,9]^+$, which says $value_0$ is in the regular language $[0,9]^+$),
+	\item \emph{integer} constraints (e.g., $i_0 = |value_0| -1$, which says $i_0$ equals the length of $value_0$ minus one),
+	\item \emph{equality} constraints (often $y=\chatAt{x}{i}$ is encoded as $x=x_1.x_2.x_3 \wedge |x_1| = i \wedge |x_2| =1 \wedge y= x_2$, which uses equality of string terms $x$ and $x_1.x_2.x_3$), and
+	\item \emph{string-number conversion} (e.g., $\its{sum_2}$, which is the string value of the number $sum_2$).
+\end{itemize}
+
+Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
+Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
 
@@
 
-As solvers such Z3 are applied to symbolic execution of programming languages, this is increasingly becoming a severe limitation.
+As solvers are applied to symbolic execution of programming languages, this is increasingly becoming a severe limitation.
 For many languages such as Java, conversion between integers and strings is a niche operation, and much symbolic execution can be done without supporting it; however, this is not true of some scripting languages, of which JavaScript is the most notable.
-JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with nodejs---and it has conversions between strings and integers embedded in the core of its semantics.
+JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with Node.js---and it has conversions between strings and integers embedded in the core of its semantics.
 
@@
 
-A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: all array indices act like strings, and numeric indices are converted to strings.
+A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
+Moreover, the \textit{length} of an array is defined as the ``largest integer index plus one''.
 Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that uses {\tt{resetArray}}, with the value of {\tt{x}} shown on the right:
@@
 This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
-On the other hand, the size of an array ({\tt{arr.length}} in the example) is defined as the ``largest integer index plus one'', so the integer value of element expression can affect the array size.
 
@@
 
+\hide{
 For the purpose of program analysis, string solver also needs to support \emph{equality constraints} (e.g.
@@
 For instance, $y=x.charAt(i)$ can be encoded as $x=x_1.x_2.x_3 \wedge |x_1| = i \wedge |x_2| =1 \wedge y= x_2$.
-Those are also the type of constraints supported by most state-of-the-art string constraint solvers such as Z3, CVC4, Z3Str3, and Trau+.
-
-\yfc{I am not sure how to add other examples here in a nice way, one reason is we are very specifically focused on Javascript, but other examples, e.g., the credit card one, is very general.}
+Those are also the type of constraints supported by most state-of-the-art string constraint solvers such as Z3, CVC4, Z3Str3, and Trau+.}
 

### 2019-11-18 draft.tex
polish intro

@@
 \begin{itemize}
-	\item \emph{regular} constraints (e.g., $value_0 \in [0,9]^+$, which says $value_0$ is in the regular language $[0,9]^+$),
+	\item \emph{regular} constraints (e.g., $value_0 \in [1,9]^+$, which says $value_0$ is in the regular language $[0,9]^+$),
 	\item \emph{integer} constraints (e.g., $i_0 = |value_0| -1$, which says $i_0$ equals the length of $value_0$ minus one),
@@
 function resetArray(arr) {
-  for(var i = 0; i < arr.length; i++) {
+  for(var i = 0; i < 10; i++) {
     arr[i] = 0
@@
 A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
-Moreover, the \textit{length} of an array is defined as the ``largest integer index plus one''.
-Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that uses {\tt{resetArray}}, with the value of {\tt{x}} shown on the right:
-
-\begin{tabular}{l|c}
-	{\tt{x = [0, 1, 2, 3, 4, 5]}} & [0, 1, 2, 3, 4, 5] \\
-	{\tt{resetArray(x)}} & [0, 0, 0, 0, 0, 0] \\
-	{\tt{x[3] = 5}} & [0, 0, 0, 5, 0, 0] \\
-	{\tt{x["12"] = 7}} & [0, 0, 0, 5, 0, 0, , , , , , 7] \\
-	{\tt{resetArray(x)}} & [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0] \\
+This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
+
+\hspace{-4mm}\begin{tabular}{l|l|c}
+1&	{\tt{x = [0, 0, 0, 0, 0]}} & [0, 0, 0, 0, 0] \\
+2&	{\tt{x[3] = 4}} & [0, 0, 0, 4, 0] \\
+3&	{\tt{x["3"] = 5}} & [0, 0, 0, 5, 0] \\
+4&	{\tt{x["03"] = 7}} & [0, 0, 0, 5, 0] and x["03"] = 7\\
+5&	{\tt{x["03"-1] = 2}} & [0, 0, 2, 5, 0] and x["03"] = 7\\
 \end{tabular}
 
-In this code, string and integer values access the same array elements interchangeably, necessitating conversions between string and integers to faithfully model JavaScript semantics.
-This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+Here both \texttt{x[3]} in line 2 and \texttt{x["3"]} in line 3 denote the array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element.
+So naive idea of modeling array index using integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
+
+If we model array index with strings, then we need to face the second problem -- we need to handle arithmetics in the array index.
+Let us look at the case of line 4, we need to update the value of \texttt{x["03"-1]}.
+The expression \texttt{"03"-1} will be evaluated to $2$, which involves an implicit type conversion from the string \texttt{"03"} to an integer value $3$ due to the \texttt{-} operation.
+Then the number $2$ will be converted back to string \texttt{"2"} and used as array index and hence \texttt{x["03"-1]} is the array element of \texttt{x["2"]}.
+Even for a simple example like this, the conversion between string and number is unavoidable.
+This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+
+\hide{
+
+The Line 4 of the code updates the length of \texttt{x} to $13$ and hence the \texttt{resetArray(x)} will update \texttt{x} to an array with $13$ zeros.
+Now suppose that the Line 4 of the code above is replace to {\tt{x[k] = 5}}, where $\mathtt{k}$ is an user input string and we want to find an input such that $\mathtt{x[15]=0}$.
+In this case, one would need to know the value of $\sti{k}$ and hence whether it will affect the size of the array {\tt{x}}.
+More precisely, in the corresponding string constraint encoding, we use a shadow variable $xLen$ to remember the length of $x$ and update its value after all array assignment.
+For an assignment $\mathtt{x[k] = v}$, we update the array value and length using the following string constraint (combined the $select$ function from SMT array theory): $x_{i+1} = store(x_i,k, v)$ and $xLen_{i+1} = ite( xLen_{i}> \sti{k}, xLen_{i}, \sti{k})$.
+This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+
+}
+
+\hide{In this code, string and integer values access the same array elements interchangeably, necessitating conversions between string and integers to faithfully model JavaScript semantics.
 
@@
 This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+}
 
@@
 From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
-In practice, in our experiments, all of the state-of-the-art string constraint solvers do not support string-number conversion correctly.
-Some of them handles such constraints with only over-approximation of the original formula, and is known to have one-side error (see Section~\ref{section:evaluation} for detailed explanation).
-\yfc{add concrete evidence}
+In practice, in our experiments, the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
 

### 2019-11-18 draft.tex
polish intro

@@
 One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.\yfc{maybe explain a bit somewhere the alphabet explosion problem of PLDI 2017} In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation, in general,  still encodes possibility an infinite number of models.
-Such symbolic encoding based on PFA is the key to handle string-number conversion.
-In our under-approximation approach, the original undecidable fragment, i.e., string constraint with string-number conversion, is converted to linear formulas and can be solved efficiently in a systematic manner.
-
-More concretely, based on the PFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
+Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.
+%In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation still encodes possibility an infinite number of models.
+Such reduction based on PFA is the key to handle string-number conversion efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulas and can be solved efficiently.
+We can step-wisely enrich the PFAs and hence solve the satisfiability problem of string constraints in a systematic manner.
+
+\hide{More concretely, based on the PFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
 Thus the problem is significantly simplified.
@@
 This allows us to convert a string constraint with string-number conversion function to an equisatisfiable linear formula, which can be solved very efficiently.
-
-Our string constraint solving produce can be easily integrated in a \emph{satisfiability module theory (SMT)} solver as a theory solver.
+}
+
+\hide{Our string constraint solving procedure can be easily integrated in a \emph{satisfiability module theory (SMT)} solver as a theory solver.
 The integration allows us to express string operations that cannot be reduced to the type of constraints (regular, equality, integer, string-number conversion) supported by our procedure.
@@
 \end{figure}
+
+}
+
+\todo{Talk about related works}
 

### 2019-11-18 draft.tex

@@
 Here both \texttt{x[3]} in line 2 and \texttt{x["3"]} in line 3 denote the array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element.
-So naive idea of modeling array index using integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
-
-If we model array index with strings, then we need to face the second problem -- we need to handle arithmetics in the array index.
+So na\"ive idea of modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
+
+If array indexes are modeled as strings, we need to face the problem of handling of arithmetics in the array index.
 Let us look at the case of line 4, we need to update the value of \texttt{x["03"-1]}.
-The expression \texttt{"03"-1} will be evaluated to $2$, which involves an implicit type conversion from the string \texttt{"03"} to an integer value $3$ due to the \texttt{-} operation.
-Then the number $2$ will be converted back to string \texttt{"2"} and used as array index and hence \texttt{x["03"-1]} is the array element of \texttt{x["2"]}.
+The evaluation of the expression \texttt{"03"-1} involves an implicit type conversion from the string \texttt{"03"} to an integer value $3$ due to the \texttt{-} (minus) operation.
+The result of the evaluation of \texttt{"03"-1} is the integer $2$, which is then converted back to string \texttt{"2"} and used as the array index.
+Hence \texttt{x["03"-1]} means the array element of \texttt{x["2"]}.
 Even for a simple example like this, the conversion between string and number is unavoidable.

### 2019-11-18 draft.tex
Update draft.tex

@@
 
-The path feasibility problem is a critical module in the symbolic execution of string-manipulating programs.
+Symbolic execution is very popular technique that allows the programmers to check the feasibility of a path in a given program (i.e., determining the value of the inputs under which the given path can be executed) \cite{????}).
+The path feasibility problem is usually solved by a reduction to the satisfiability problem of a formula.
+More precisely, program statements in the path are usually translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{satisfiability module theory (SMT)}  solvers.
+The types of constraints that needed to be solved by the SMT solvers depend on the type of program variables.
+Therefore, there is a need for SMT solvers that support different combinations of theories (i.e., depending on the types of the manipulated variables).
+
+Among all types of program variables, \emph{String data type}  is omnipresent in modern programming languages.
+For many languages such as Java, conversion between integers and strings is a niche operation, and much symbolic execution can be done without supporting it; however, this is not true of some scripting languages, of which JavaScript is the most notable.
+JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with nodejs---and it has conversions between strings and integers embedded in the core of its semantics.
+
+Therefore, string constraint solving has received considerable attention in the constraint solving community.
+Operations such as \emph{equality constraints} (e.g.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as Z3  \cite{?}, CVC4  \cite{?}, Z3Str3  \cite{?}, and Trau+ \cite{?}.
+However, these solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
+When there is support, it is often very limited to ground terms.
+Thus, $n = \sti{"003"}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \sti{n}$ (i.e.,  converting the integer $n$ to the string $x$)
+are ones of the core operations that require stronger solver support.
+
+%The path feasibility problem is a critical module in the symbolic execution of string-manipulating programs.
 The problem is usually solved by a reduction to a string constraint satisfiability problem.
@@
 
-The string-number conversion operations are widely used in string manipulating programs and algorithms.
-For example, the program fragment below is an implementation of the Luhn test algorithm that is often used in credit card or personal ID validation.
+%The path feasibility problem is a critical module in the symbolic execution of string-manipulating programs.
+The problem is usually solved by a reduction to a string constraint satisfiability problem.
+Program statements in the path are translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{string constraint solvers}.
+Among all types of program statements, \emph{string-number conversion} is one of the core operations that requires stronger solver support.
+
+In fact, the string-number conversion operations are widely used in string manipulating programs and algorithms.
+For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 
@@
     var d = parseInt(value.charAt(i));
-    if ((d *= 2) > 9) digit -= 9;
+    if ((d *= 2) > 9) d -= 9;
     sum += d;
@@
 The value of every odd digit (e.g., 1st, 3rd, etc.) is added to \verb|sum| directly.
-For the value of every even digit, the algorithm (1) doubles its value, (2) substracts its value by $9$ if the doubled-value is bigger than $9$, and (3) adds the final result to \verb|sum|.
-At the end, the input is validated if the string value of \verb|sum| ends in $0$.
-
-To check whether the program path that traverses both loop exactly once and finally passes this test has a valid input, we create the following string constraint:
+For the value of every even digit, the algorithm (1) doubles its value, (2) subtracts its value by $9$ if the doubled-value is bigger than $9$, and (3) adds the final result to \verb|sum|.
+At the end, the input is validated if the string value of \verb|sum| ends by an $0$ (i.e., \verb| sum mod 10=0|).
+
+To check whether the program path that traverses both loop exactly once and finally passes this test has a valid input, we create the following (string) constraint:
 
@@
 
-Here $value_0$ and $last_0$ are string variables and others are integer variables.
+Here $value_0$ and $last_0$ are string variables and the others are integer variables.
+The method $\chatAt{x}{i}$ returns the character at the index $i$ in the string $x$ while $n=\ite{b}{e}{e'}$ assigns to $n$ the value of the expression $e$ if $b$ is true and the value of the expression $e'$ otherwise.
 Line 1 describes the initial condition: \textsf{value} should be a sequence of digits and \textsf{sum} is initially zero.

### 2019-11-18 draft.tex
related work from ATVA'19

@@
 
+\paragraph{Related works:} 
+Already in  1946, Quine \cite{Quine46} showed that the first order theory
+of string equations is undecidable.
+%
+An important line of work has been to identify subclasses
+for which decidability can be achieved.
+%
+The pioneering work by Makanin \cite{makanin} proposed a decision
+procedure for quantifier-free word equations, i.e., Boolean combinations of
+equalities and disequalities, where the variables may denote words of 
+arbitrary lengths.
+%
+The decidability and complexity of different subclasses
+have been considered by several works, e.g.
+\cite{Plandowski99,Plandowski06,Matiyasevich08,Robson90,Schulz90,Ganesh13decide,DBLP:journals/corr/GaneshB16}.
+Generalizations of the work of Makanin by adding
+new types of constraints have been difficult to achieve.
+%
+For instance, the satisfiability of word equations combined with length
+constraints of the form $\left|x\right|=\left|y\right|$ is open
+\cite{buchi:definability}.
+%
+Recently, 
+regular and especially relational transducers constraints were identified
+%
+as a strongly desirable feature of string languages 
+%
+especially in the context software analysis with an emphasis on security. 
+%
+Adding these to the mix leads immediately to undecidability \cite{morvan}
+%
+and hence numerous decidable fragments were proposed \cite{string14,BFL13,BL16,Chen:2018,Chen:2019}. 
+%
+From these, the straight line fragment of \cite{BL16} is the most general decidable combination of concatenation and transducers.
+It is however incomparable to the acyclic fragment of \cite{string14} (which does not have transducers but could be extended with them in a straightforward manner).
+%
+Some works add also other syntactic features, such as \cite{Chen:2018,Chen:2019}, 
+but the limit of decidable combinations of the core string features---transducers/regular constraints, length constraints, and concatenation stays at \cite{BL16} and \cite{string14}.
+%
+The weakly chaining decidable fragment present in this paper significantly generalises both these fragments in a practically relevant direction.
+
+The strong practical motivation in string solving led to a rise of a number of SMT solvers that do not always provide completeness guarantees but concentrate on solving practical problem instances, 
+through applying a variety of calculi and algorithms.
+%
+A number of tools handle string constraints by means of {\it length-based under-approximation} and
+translation to
+bit-vectors~\cite{Kiezun09hampi,Saxena10:kaluza,saxena:flax}, assuming
+a fixed upper bound on the length of the possible solutions. 
+%
+Our method on the other hand allows to analyse constraints without a length limit and with completeness guarantees.
+%
+More recently, also {\it DPLL(T)-based} string solvers lift the
+restriction of strings of bounded length; this generation of solvers
+includes Z3-str3 \cite{Berzish2017Z3str3AS}, Z3-str2~\cite{Zheng13z3str}, 
+CVC4~\cite{LiaEtAl-CAV-14}, S3P~\cite{trinh2014:s3,Trinh2016},
+Norn~\cite{norn15}, 
+Trau~\cite{trau18}, 
+Sloth~\cite{sloth}, 
+and 
+Ostrich~\cite{Chen:2019}. DPLL(T)-based solvers
+handle a variety of string constraints, including word equations, regular expression membership, length constraints, and (more rarely)
+regular/rational relations; the solvers are not complete for the full
+combination of those constraints though, and often only decide a (more
+or less well-defined) fragment of the individual constraints. 
+Equality constraints are normally handled by means of splitting into simpler
+sub-cases, in combination with powerful techniques for Boolean
+reasoning to curb the resulting exponential search space. 
+%
+Our implementation is combining strong completeness guarantees of \cite{sloth} extended to handle the fragment proposed in this paper with an efficient approximation techniques of \cite{trau18} 
+and its performance on existing benchmarks compares favourably with the most efficient of the above tools.
+%
+
+A further direction is {\it automata-based} solvers for analyzing
+string-manipulated programs. Stranger~\cite{fangyu:stranger} soundly
+over-approximates string constraints using regular languages, and
+outperforms DPLL(T)-based solvers when checking single execution
+traces, according to some evaluations~\cite{KauslerS14}.  It has
+recently also been observed~\cite{DBLP:conf/cav/WangTLYJ16,sloth} that
+automata-based algorithms can be combined with model checking
+algorithms, in particular IC3/PDR, for more efficient checking of the emptiness for automata. However, many kinds of constraints, including length
+constraints and word equations, cannot be
+handled by automata-based solvers in a complete manner.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-11-18 draft.tex
Update draft.tex

--- 2019-11-18 draft.tex
@@
 
-Among all types of program variables, \emph{String data type}  is omnipresent in modern programming languages.
-For many languages such as Java, conversion between integers and strings is a niche operation, and much symbolic execution can be done without supporting it; however, this is not true of some scripting languages, of which JavaScript is the most notable.
-JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with nodejs---and it has conversions between strings and integers embedded in the core of its semantics.
-
+Among all types of program variables, \emph{string data type}  is omnipresent in modern programming languages.
+Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.
 Therefore, string constraint solving has received considerable attention in the constraint solving community.
@@
 $x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as Z3  \cite{?}, CVC4  \cite{?}, Z3Str3  \cite{?}, and Trau+ \cite{?}.
-However, these solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
-When there is support, it is often very limited to ground terms.
-Thus, $n = \sti{"003"}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \sti{n}$ (i.e.,  converting the integer $n$ to the string $x$)
+ However,   solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
+When there is support, it is often very limited.
+Thus, $n = \sti{\tt{"03"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
 are ones of the core operations that require stronger solver support.
@@
 
-In fact, the string-number conversion operations are widely used in string manipulating programs and algorithms.
+In fact, for many languages such as Java, the string-number conversion operations are is a niche operation, and much symbolic execution can not  be done without supporting it.
 For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
@@
 
-Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
+Currently, even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
+Therefore, there is an urgent need to efficient techniques for solving the combination of above constraints.
+To make matters worse, many scripting languages, of which JavaScript is the most notable ---it powers most interactive content on the Web, and increasingly server-side code with Node.js---, has conversions between strings and integers embedded in the core of its semantics.
+To see how, consider the following program:
+
+%Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
 Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
@@
 
-As solvers are applied to symbolic execution of programming languages, this is increasingly becoming a severe limitation.
+%As solvers are applied to symbolic execution of programming languages, this is increasingly becoming a severe limitation.
 For many languages such as Java, conversion between integers and strings is a niche operation, and much symbolic execution can be done without supporting it; however, this is not true of some scripting languages, of which JavaScript is the most notable.

### 2019-11-18 draft.tex
update the example in intro and also update overview

@@
 \begin{verbatim}
-function resetArray(arr) {
 for(var i = 0; i < 10; i++) {
@@
 }
-}
 \end{verbatim}
@@
 2&	{\tt{x[3] = 4}} & [0, 0, 0, 4, 0] \\
-3&	{\tt{x["3"] = 5}} & [0, 0, 0, 5, 0] \\
-4&	{\tt{x["03"] = 7}} & [0, 0, 0, 5, 0] and x["03"] = 7\\
-5&	{\tt{x["03"-1] = 2}} & [0, 0, 2, 5, 0] and x["03"] = 7\\
+3&	{\tt{x[03] = 2}} & [0, 0, 0, 2, 0] \\
+4&	{\tt{x["3"] = 5}} & [0, 0, 0, 5, 0] \\
+5&	{\tt{x["03"] = 7}} & [0, 0, 0, 5, 0] and x["03"] = 7\\
+6&	{\tt{x["03"-1] = 2}} & [0, 0, 2, 5, 0] and x["03"] = 7\\
 \end{tabular}
 
-Here both \texttt{x[3]} in line 2 and \texttt{x["3"]} in line 3 denote the array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element.
+Here \texttt{x[3]} in line 2,  \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element.
 So na\"ive idea of modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
@@
 If array indexes are modeled as strings, we need to face the problem of handling of arithmetics in the array index.
-Let us look at the case of line 4, we need to update the value of \texttt{x["03"-1]}.
+Let us look at the case of line 6, we need to update the value of \texttt{x["03"-1]}.
 The evaluation of the expression \texttt{"03"-1} involves an implicit type conversion from the string \texttt{"03"} to an integer value $3$ due to the \texttt{-} (minus) operation.
@@
 One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
-For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and remove the constraint $n=\sti{x}$.
-This produce new formulas that over-approximate the original ones and fall in the acyclic fragment~\cite{abdulla2014string}, which is decidable.
+For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+This produce new formulas that over-approximate the original ones and fall in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
+In our implementation \tool, we further add heuristics trying to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
+For instance, assume in some other cases, we can derive the value of $n=12$ from some integer constraints.
+In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
 

### 2019-11-18 draft.tex
Update draft.tex

@@
 
-Symbolic execution is very popular technique that allows the programmers to check the feasibility of a path in a given program (i.e., determining the value of the inputs under which the given path can be executed) \cite{????}).
+Symbolic execution is a very popular technique that allows the programmers to check the feasibility of a path in a given program (i.e., determining the value of the inputs under which the given path can be executed) \cite{????}).
 The path feasibility problem is usually solved by a reduction to the satisfiability problem of a formula.
@@
 When there is support, it is often very limited.
-Thus, $n = \sti{\tt{"03"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
+Thus, $n = \sti{\\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
 are ones of the core operations that require stronger solver support.
@@
 Currently, even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
-Therefore, there is an urgent need to efficient techniques for solving the combination of above constraints.
+Therefore, there is an urgent need for developing efficient techniques for solving the combination of above constraints.
 To make matters worse, many scripting languages, of which JavaScript is the most notable ---it powers most interactive content on the Web, and increasingly server-side code with Node.js---, has conversions between strings and integers embedded in the core of its semantics.
@@
 A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
-This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript \ref{?}requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
 Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
@@
 
-Here \texttt{x[3]} in line 2,  \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element.
+Here \texttt{x[3]} in line 2,  \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
 So na\"ive idea of modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
 
-If array indexes are modeled as strings, we need to face the problem of handling of arithmetics in the array index.
+If array indexes are modelled as strings, we need to face the problem of handling of arithmetics in the array index.
 Let us look at the case of line 6, we need to update the value of \texttt{x["03"-1]}.
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+This is a rather basic array operation in Javascript, and so having only limited capability for handling string-number conversion operations  will cripple any analysis of non-trivial JavaScript code.
 
@@
 For an assignment $\mathtt{x[k] = v}$, we update the array value and length using the following string constraint (combined the $select$ function from SMT array theory): $x_{i+1} = store(x_i,k, v)$ and $xLen_{i+1} = ite( xLen_{i}> \sti{k}, xLen_{i}, \sti{k})$.
-This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
+This is a rather straightforward array operation, and so  having only limited capability for handling str/num conversion. will cripple any model of non-trivial JavaScript code.
 
@@
 From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
-In practice, in our experiments, the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
-
-In this paper, we adopt a framework that handles string constraints with string-number conversion efficiently.
-Due to the high complexity of solving the problem exactly, our framework uses both over and under-approximation of the string constraints.
+In practice, in our experiments (Section \ref{section:evaluation}), the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+
+In this paper, we propose a framework that handles string constraints with string-number conversion efficiently.
+Due to the high complexity of solving the exact problem, our framework uses both over and under-approximation of the string constraints.
 The over-approximation is for proving UNSAT and the under-approximation is for proving SAT of the string constraint.
-Both over and under-approximation should fail in a decidable fragment of string constraints that can be efficiently solved.
+Both over and under-approximation  fall in a decidable fragment of string constraints that can we can efficiently solved.
 

### 2019-11-18 draft.tex
update overview

--- 2019-11-18 draft.tex
@@
 One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
-For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1  \Leftrightarrow x\not\in [0-9]^*$, where $\Leftrightarrow$ means ``if and only if''.
 This produce new formulas that over-approximate the original ones and fall in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
-Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
+Since $\Phi$ is satisfiable, it is expected that the over-approximation module will not return UNSAT and we proceed to the the under-approximation module to prove SAT.
+
 In our implementation \tool, we further add heuristics trying to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some other cases, we can derive the value of $n=12$ from some integer constraints.
-In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
-
-Then our procedure will restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and convert them to equisatisfiable linear formula.
-The details of the under-approximation component will be described in Section~\ref{section:under_approximate}.
+For instance, assume in some other cases, we can derive $n=12$ from some integer constraints.
+In such case, we can further derive that the value of $x$ is in the regular language $(0^*12)$.
+
+For proving SAT, our procedure first restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and then convert the string constraints under the domain restriction to equisatisfiable linear formulas.
 Here we try to explain what the linear formula looks like by an example.
@@
 Depending on the implementation, one may choose to report unknown after some certain steps.
+
+\yfc{maybe add a flowchart later if space allows}
 

### 2019-11-18 draft.tex
Update draft.tex

--- 2019-11-18 draft.tex
@@
 \usetikzlibrary{arrows,automata}
+\sloppy
 
@@
 
+\newcommand{\st}[2]{q_{#1}^{#2}}
+\newcommand{\sym}[2]{v_{#1}^{#2}}
+
 \maketitle
@@
 Among all types of program variables, \emph{string data type}  is omnipresent in modern programming languages.
-Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.
+Various  security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.
 Therefore, string constraint solving has received considerable attention in the constraint solving community.
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as Z3  \cite{?}, CVC4  \cite{?}, Z3Str3  \cite{?}, and Trau+ \cite{?}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4  \cite{?}, OSTRICH \cite{}, Sloth \cite{},   Trau+ \cite{?},  Z3  \cite{?} and Z3Str3  \cite{?}.
  However,   solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
 When there is support, it is often very limited.
-Thus, $n = \sti{\\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
+Thus, $n = \sti{\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
 are ones of the core operations that require stronger solver support.
@@
 
-In fact, for many languages such as Java, the string-number conversion operations are is a niche operation, and much symbolic execution can not  be done without supporting it.
+In fact, for many languages such as Java, the string-number conversion operations are   niche operations, and much symbolic execution can not  be done without supporting them.
 For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
@@
 
-The input \verb|value| is a sequence of digits.
+The input \verb|value|  of the Luhn test algorithm is a sequence of digits.
 The algorithm process the digits in the reversed order.
@@
 
-Currently, even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
-Therefore, there is an urgent need for developing efficient techniques for solving the combination of above constraints.
+Currently, even for a simple constraint like the  one above, most solvers  fail to provide a correct answer.
+Therefore, there is an urgent need for developing efficient techniques for solving such string constraints.
 To make matters worse, many scripting languages, of which JavaScript is the most notable ---it powers most interactive content on the Web, and increasingly server-side code with Node.js---, has conversions between strings and integers embedded in the core of its semantics.
@@
 A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
-This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript \ref{?}requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
 Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic array operation in Javascript, and so having only limited capability for handling string-number conversion operations  will cripple any analysis of non-trivial JavaScript code.
+This is a rather basic array operation in Javascript, and so having only limited capability for handling string-number conversion operations  will cripple any analysis of any non-trivial JavaScript code.
 
@@
 
-In this paper, we propose a framework that handles string constraints with string-number conversion efficiently.
+In this paper, we propose a framework that handles efficiently string constraints with string-number conversion.
 Due to the high complexity of solving the exact problem, our framework uses both over and under-approximation of the string constraints.
-The over-approximation is for proving UNSAT and the under-approximation is for proving SAT of the string constraint.
-Both over and under-approximation  fall in a decidable fragment of string constraints that can we can efficiently solved.
-
-For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
-In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
-In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
-
-The battle field is in fact those SAT instances, for which we develop solutions using under-approximation.
+The over-approximation is for proving UNSAT while the under-approximation is for proving SAT of the string constraint.
+Both over and under-approximation  fall in a decidable fragment of string constraints that can we can efficiently solve.
+
+For ease of presentation, we will use  the following  toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
+
+to explain the main ideas behind our decision procedure. Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``12''$ and $y=``1212''$.
+
+Our decision procedure proceeds in two steps: The first step consists in over-approximating the set of input constraints into a one that  falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+Observe that we can also over-approximate the input constraint to one that falls in the decidable fragment the acyclic fragment~\cite{abdulla2014string} or the straight-line fragment~\cite{chen2019decision}.
+Our choice of the   chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that  the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints as far as we know.
+In our settings, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+The over-approximation module uses also  some heuristics  to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
+For instance, assume in some other cases, we can derive the value of $n=12$ from some integer constraints.
+In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
+Observe that if the over-approximated module returns UNSAT then  our decision procedure   declares that the original formula is also UNSAT and terminates.
+Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
+
+\begin{figure*}
+	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+	\begin{tikzpicture} 
+		\node[state,initial] (q0)  {$\st{0}{0}$};
+		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
+		\node (q2) [right = 1.8cm of q1]{};
+		\node (q3) [right = 1cm of q2]{};
+		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
+
+		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
+		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
+		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
+
+		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
+		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
+
+		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
+		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
+		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
+
+  		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
+  		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
+  		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
+  		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
+
+  		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
+  		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
+  		\draw[dotted] (q2) edge (q3) ;
+  		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
+
+  		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
+		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
+		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
+		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
+
+  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
+		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
+	\end{tikzpicture}
+
+	\caption{An example of a parametric flat automaton}
+	\label{fig:sfa_def}
+\end{figure*}
+
+The second step of our decision procedure is only enabled  if the first step returns SAT.
+In this case,  our decision procedure  restricts the domain of each string variables  to strings that obey some predefined and parameterized pattern.
+By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
+In this paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA).
+A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops each of fixed length (see Figure \ref{fig:sfa_def}).
+The approach based on PFA is very flexible yet allows very efficiently manipulation.
+One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
+Furthermore, we associate for each character a unique natural number.
+This allows us to assume that the input alphabet is a subset of natural numbers.
+To avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers,  we  labeled each transition between two states of a  PFA by a unique  \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
+Such reduction based on PFA is the key to handle string-number conversion efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulas that can  be solved efficiently.
+
+%The battle field is in fact those SAT instances, for which we develop solutions using under-approximation.
 For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
@@
 Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.
-%In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation still encodes possibility an infinite number of models.
-Such reduction based on PFA is the key to handle string-number conversion efficiently.
+%%In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation still encodes possibility an infinite number of models.
+%Such reduction based on PFA is the key to handle string-number conversion efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulas and can be solved efficiently.
+We can step-wisely enrich the PFAs and hence solve the satisfiability problem of string constraints in a systematic manner.
+
+\begin{figure*}
+	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+
+	\begin{minipage}[t]{0.15\textwidth} 
+		\begin{tikzpicture}
+		\node[state,initial,accepting] (q0)  {$q_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_0$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
+		\end{tikzpicture}
+
+		\centering
+		(a) $A_x$
+	\end{minipage}
+	\begin{minipage}[t]{0.15\textwidth} 
+		\begin{tikzpicture} 
+		\node[state,initial,accepting] (q0)  {$p_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$p_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_2$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_3$} (q0) ;
+		\end{tikzpicture}
+
+		\centering
+		(b) $A_y$
+	\end{minipage}
+	\begin{minipage}[t]{0.28\textwidth}
+		\begin{tikzpicture} 
+		\node[state,initial] (q0)  {$q_0$};
+		\node[state,accepting] (q1) [right = 1.3cm of q0] {$p_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(0)}$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(0)}$} (q0) ;
+
+		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
+
+		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(0)}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
+		\draw[->] (q0) edge  node [below]{$v_{\epsilon_0}$} (q1) ;
+		\end{tikzpicture}
+
+		\centering
+		(c) $A_{xy}$
+	\end{minipage}
+	\ \ \ 
+	\begin{minipage}[t]{0.28\textwidth}
+		\begin{tikzpicture} 
+		\node[state,accepting] (q0)  {$q_0$};
+		\node[state,initial] (q1) [left = 1.3cm of q0] {$p_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(1)}$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(1)}$} (q0) ;
+
+		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
+
+		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(1)}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
+		\draw[->] (q1) edge  node [below]{$v_{\epsilon_1}$ }(q0) ;
+		\end{tikzpicture}
+
+		\centering
+		(d) $A_{yx}$
+	\end{minipage}
+
+	\caption{Parametric flat automata of $x$, $y$, $xy$ and $yx$}
+	\label{fig:sfa}
+\end{figure*}
+
+In the following,  we try to explain the construction of the linear formula using the formula $\Phi$ as an example.
+Assume that we project the domain of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.Thus,  $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
+For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
+
+The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$,  as well as, the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+Each model of the linear formula encodes a model of the string constraint.
+For example, $x=``12''$ and $y=``1212''$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
+
+If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
+If not, our procedure step-wisely change the PFA to more expressive ones (by adding more states and transitions) to systematically search for the solution.
+Depending on the implementation, one may choose to report unknown after some certain steps.
+
+%For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
+In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
+In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
+
+%The battle field is in fact those SAT instances, for which we develop solutions using under-approximation.
+For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
+By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
+In paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA) (will be defined formally in Section~\ref{section:sfa}).
+The approach based on PFA is very flexible yet allows very efficiently manipulation.
+One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
+Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.
+%%In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation still encodes possibility an infinite number of models.
+%Such reduction based on PFA is the key to handle string-number conversion efficiently.
 When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulas and can be solved efficiently.
@@
 
-\todo{Talk about related works}
-
+To demonstrate  the usefulness of our approach, we have implemented our decision procedure in an open source solver, called {\sc } ....
 \todo{Talk about experiments}
+
+\smallskip
+
+\noindent
+{\bf Summary of the Contributions}
+
+\begin{itemize}
+
+\item An {\em efficient} procedure  for checking satisfiability
+of string constraints with string-number conversion constraints.
+
+\item The introduction of  the class of \emph{parametric flat automata} which uses character variables as transition labels instead of characters.
+This allows us to avoid  the {alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} when it comes to handle string-number conversion constraints.
+
+\item An algorithm that translates the satisfiability string constraints to the  satisfiability of a linear formula   in polynomial-time when   the search space restricted by PFAs.
+
+\item An open source tool  with experimental
+results that demonstrate the efficiency  of
+our approach on both existing and real-life benchmarks
+\end{itemize}
 
@@
 
-\paragraph{Related works:} 
-Already in  1946, Quine \cite{Quine46} showed that the first order theory
-of string equations is undecidable.
-%
-An important line of work has been to identify subclasses
-for which decidability can be achieved.
-%
-The pioneering work by Makanin \cite{makanin} proposed a decision
-procedure for quantifier-free word equations, i.e., Boolean combinations of
-equalities and disequalities, where the variables may denote words of 
-arbitrary lengths.
-%
-The decidability and complexity of different subclasses
-have been considered by several works, e.g.
-\cite{Plandowski99,Plandowski06,Matiyasevich08,Robson90,Schulz90,Ganesh13decide,DBLP:journals/corr/GaneshB16}.
-Generalizations of the work of Makanin by adding
-new types of constraints have been difficult to achieve.
-%
-For instance, the satisfiability of word equations combined with length
-constraints of the form $\left|x\right|=\left|y\right|$ is open
-\cite{buchi:definability}.
-%
-Recently, 
-regular and especially relational transducers constraints were identified
-%
-as a strongly desirable feature of string languages 
-%
-especially in the context software analysis with an emphasis on security. 
-%
-Adding these to the mix leads immediately to undecidability \cite{morvan}
-%
-and hence numerous decidable fragments were proposed \cite{string14,BFL13,BL16,Chen:2018,Chen:2019}. 
-%
-From these, the straight line fragment of \cite{BL16} is the most general decidable combination of concatenation and transducers.
-It is however incomparable to the acyclic fragment of \cite{string14} (which does not have transducers but could be extended with them in a straightforward manner).
-%
-Some works add also other syntactic features, such as \cite{Chen:2018,Chen:2019}, 
-but the limit of decidable combinations of the core string features---transducers/regular constraints, length constraints, and concatenation stays at \cite{BL16} and \cite{string14}.
-%
-The weakly chaining decidable fragment present in this paper significantly generalises both these fragments in a practically relevant direction.
-
-The strong practical motivation in string solving led to a rise of a number of SMT solvers that do not always provide completeness guarantees but concentrate on solving practical problem instances, 
-through applying a variety of calculi and algorithms.
-%
-A number of tools handle string constraints by means of {\it length-based under-approximation} and
-translation to
-bit-vectors~\cite{Kiezun09hampi,Saxena10:kaluza,saxena:flax}, assuming
-a fixed upper bound on the length of the possible solutions. 
-%
-Our method on the other hand allows to analyse constraints without a length limit and with completeness guarantees.
-%
-More recently, also {\it DPLL(T)-based} string solvers lift the
-restriction of strings of bounded length; this generation of solvers
-includes Z3-str3 \cite{Berzish2017Z3str3AS}, Z3-str2~\cite{Zheng13z3str}, 
-CVC4~\cite{LiaEtAl-CAV-14}, S3P~\cite{trinh2014:s3,Trinh2016},
-Norn~\cite{norn15}, 
-Trau~\cite{trau18}, 
-Sloth~\cite{sloth}, 
-and 
-Ostrich~\cite{Chen:2019}. DPLL(T)-based solvers
-handle a variety of string constraints, including word equations, regular expression membership, length constraints, and (more rarely)
-regular/rational relations; the solvers are not complete for the full
-combination of those constraints though, and often only decide a (more
-or less well-defined) fragment of the individual constraints. 
-Equality constraints are normally handled by means of splitting into simpler
-sub-cases, in combination with powerful techniques for Boolean
-reasoning to curb the resulting exponential search space. 
-%
-Our implementation is combining strong completeness guarantees of \cite{sloth} extended to handle the fragment proposed in this paper with an efficient approximation techniques of \cite{trau18} 
-and its performance on existing benchmarks compares favourably with the most efficient of the above tools.
-%
-
-A further direction is {\it automata-based} solvers for analyzing
-string-manipulated programs. Stranger~\cite{fangyu:stranger} soundly
-over-approximates string constraints using regular languages, and
-outperforms DPLL(T)-based solvers when checking single execution
-traces, according to some evaluations~\cite{KauslerS14}.  It has
-recently also been observed~\cite{DBLP:conf/cav/WangTLYJ16,sloth} that
-automata-based algorithms can be combined with model checking
-algorithms, in particular IC3/PDR, for more efficient checking of the emptiness for automata. However, many kinds of constraints, including length
-constraints and word equations, cannot be
-handled by automata-based solvers in a complete manner.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overview} \label{section:overview}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Here we try to explain the approach using a toy example $\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Overview} \label{section:overview}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%Here we try to explain the approach using a toy example $\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$.
 Notice that $\Phi$ is satisfiable.
 E.g., it has a model $x=``12''$ and $y=``1212''$.
-
-For proving UNSAT, our framework does not set any restriction on which decision procedure to use.
+%
+%For proving UNSAT, our framework does not set any restriction on which decision procedure to use.
 One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
@@
 In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
-
-Then our procedure will restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and convert them to equisatisfiable linear formula.
+%
+%Then our procedure will restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and convert them to equisatisfiable linear formula.
 The details of the under-approximation component will be described in Section~\ref{section:under_approximate}.
@@
 For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
-
-The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$,  as well as, the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+%
+%The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$,  as well as, the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
 Each model of the linear formula encodes a model of the string constraint.
@@
 Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
-
-If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
+%
+%If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
 If not, our procedure step-wisely change the PFA to more expressive ones (by adding more states and transitions) to systematically search for the solution.
 Depending on the implementation, one may choose to report unknown after some certain steps.
+%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\st}[2]{q_{#1}^{#2}}
-\newcommand{\sym}[2]{v_{#1}^{#2}}
+
 \todo{additional presburget constraints to encode $\epsilon$ added at translation to a formula}
@@
 
-\begin{figure*}
-	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
-			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
-	\begin{tikzpicture} 
-		\node[state,initial] (q0)  {$\st{0}{0}$};
-		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
-		\node (q2) [right = 1.8cm of q1]{};
-		\node (q3) [right = 1cm of q2]{};
-		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
-
-		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
-		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
-		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
-
-		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
-		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
-
-		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
-		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
-		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
-
-  		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
-  		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
-  		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
-  		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
-
-  		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
-  		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
-  		\draw[dotted] (q2) edge (q3) ;
-  		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
-
-  		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
-		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
-		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
-		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
-
-  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
-		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
-	\end{tikzpicture}
-
-	\caption{An example of a parametric flat automaton}
-	\label{fig:sfa_def}
-\end{figure*}
-
+%
+%\begin{figure*}
+%	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+%			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+%	\begin{tikzpicture} 
+%		\node[state,initial] (q0)  {$\st{0}{0}$};
+%		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
+%		\node (q2) [right = 1.8cm of q1]{};
+%		\node (q3) [right = 1cm of q2]{};
+%		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
+%		
+%		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
+%		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
+%		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
+%
+%		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
+%		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
+%
+%		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
+%		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
+%		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
+%
+%  		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
+%  		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
+%  		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
+%  		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
+%  		
+%  		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
+%  		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
+%  		\draw[dotted] (q2) edge (q3) ;
+%  		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
+%
+%  		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
+%		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
+%		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
+%		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
+%
+%  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
+%		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
+%		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
+%	\end{tikzpicture} 
+%
+%	\caption{An example of a parametric flat automaton}
+%	\label{fig:sfa_def}
+%\end{figure*}
+%
 %A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a PFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
@@
 %}
-
-\begin{figure*}
-	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
-			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
-
-	\begin{minipage}[t]{0.15\textwidth} 
-		\begin{tikzpicture}
-		\node[state,initial,accepting] (q0)  {$q_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(a) $A_x$
-	\end{minipage}
-	\begin{minipage}[t]{0.15\textwidth} 
-		\begin{tikzpicture} 
-		\node[state,initial,accepting] (q0)  {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$p_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_2$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_3$} (q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(b) $A_y$
-	\end{minipage}
-	\begin{minipage}[t]{0.28\textwidth}
-		\begin{tikzpicture} 
-		\node[state,initial] (q0)  {$q_0$};
-		\node[state,accepting] (q1) [right = 1.3cm of q0] {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(0)}$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(0)}$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(0)}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
-		\draw[->] (q0) edge  node [below]{$v_{\epsilon_0}$} (q1) ;
-		\end{tikzpicture}
-
-		\centering
-		(c) $A_{xy}$
-	\end{minipage}
-	\ \ \ 
-	\begin{minipage}[t]{0.28\textwidth}
-		\begin{tikzpicture} 
-		\node[state,accepting] (q0)  {$q_0$};
-		\node[state,initial] (q1) [left = 1.3cm of q0] {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(1)}$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(1)}$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(1)}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
-		\draw[->] (q1) edge  node [below]{$v_{\epsilon_1}$ }(q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(d) $A_{yx}$
-	\end{minipage}
-
-	\caption{Parametric flat automata of $x$, $y$, $xy$ and $yx$}
-	\label{fig:sfa}
-\end{figure*}
 
@@
 
+\paragraph{Related works:} 
+Already in  1946, Quine \cite{Quine46} showed that the first order theory
+of string equations is undecidable.
+%
+An important line of work has been to identify subclasses
+for which decidability can be achieved.
+%
+The pioneering work by Makanin \cite{makanin} proposed a decision
+procedure for quantifier-free word equations, i.e., Boolean combinations of
+equalities and disequalities, where the variables may denote words of 
+arbitrary lengths.
+%
+The decidability and complexity of different subclasses
+have been considered by several works, e.g.
+\cite{Plandowski99,Plandowski06,Matiyasevich08,Robson90,Schulz90,Ganesh13decide,DBLP:journals/corr/GaneshB16}.
+Generalizations of the work of Makanin by adding
+new types of constraints have been difficult to achieve.
+%
+For instance, the satisfiability of word equations combined with length
+constraints of the form $\left|x\right|=\left|y\right|$ is open
+\cite{buchi:definability}.
+%
+Recently, 
+regular and especially relational transducers constraints were identified
+%
+as a strongly desirable feature of string languages 
+%
+especially in the context software analysis with an emphasis on security. 
+%
+Adding these to the mix leads immediately to undecidability \cite{morvan}
+%
+and hence numerous decidable fragments were proposed \cite{string14,BFL13,BL16,Chen:2018,Chen:2019}. 
+%
+From these, the straight line fragment of \cite{BL16} is the most general decidable combination of concatenation and transducers.
+It is however incomparable to the acyclic fragment of \cite{string14} (which does not have transducers but could be extended with them in a straightforward manner).
+%
+Some works add also other syntactic features, such as \cite{Chen:2018,Chen:2019}, 
+but the limit of decidable combinations of the core string features---transducers/regular constraints, length constraints, and concatenation stays at \cite{BL16} and \cite{string14}.
+%
+The weakly chaining decidable fragment present in this paper significantly generalises both these fragments in a practically relevant direction.
+
+The strong practical motivation in string solving led to a rise of a number of SMT solvers that do not always provide completeness guarantees but concentrate on solving practical problem instances, 
+through applying a variety of calculi and algorithms.
+%
+A number of tools handle string constraints by means of {\it length-based under-approximation} and
+translation to
+bit-vectors~\cite{Kiezun09hampi,Saxena10:kaluza,saxena:flax}, assuming
+a fixed upper bound on the length of the possible solutions. 
+%
+Our method on the other hand allows to analyse constraints without a length limit and with completeness guarantees.
+%
+More recently, also {\it DPLL(T)-based} string solvers lift the
+restriction of strings of bounded length; this generation of solvers
+includes Z3-str3 \cite{Berzish2017Z3str3AS}, Z3-str2~\cite{Zheng13z3str}, 
+CVC4~\cite{LiaEtAl-CAV-14}, S3P~\cite{trinh2014:s3,Trinh2016},
+Norn~\cite{norn15}, 
+Trau~\cite{trau18}, 
+Sloth~\cite{sloth}, 
+and 
+Ostrich~\cite{Chen:2019}. DPLL(T)-based solvers
+handle a variety of string constraints, including word equations, regular expression membership, length constraints, and (more rarely)
+regular/rational relations; the solvers are not complete for the full
+combination of those constraints though, and often only decide a (more
+or less well-defined) fragment of the individual constraints. 
+Equality constraints are normally handled by means of splitting into simpler
+sub-cases, in combination with powerful techniques for Boolean
+reasoning to curb the resulting exponential search space. 
+%
+Our implementation is combining strong completeness guarantees of \cite{sloth} extended to handle the fragment proposed in this paper with an efficient approximation techniques of \cite{trau18} 
+and its performance on existing benchmarks compares favourably with the most efficient of the above tools.
+%
+
+A further direction is {\it automata-based} solvers for analyzing
+string-manipulated programs. Stranger~\cite{fangyu:stranger} soundly
+over-approximates string constraints using regular languages, and
+outperforms DPLL(T)-based solvers when checking single execution
+traces, according to some evaluations~\cite{KauslerS14}.  It has
+recently also been observed~\cite{DBLP:conf/cav/WangTLYJ16,sloth} that
+automata-based algorithms can be combined with model checking
+algorithms, in particular IC3/PDR, for more efficient checking of the emptiness for automata. However, many kinds of constraints, including length
+constraints and word equations, cannot be
+handled by automata-based solvers in a complete manner.
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-11-18 draft.tex
wording

--- 2019-11-18 draft.tex
@@
 
-Symbolic execution is a very popular technique that allows the programmers to check the feasibility of a path in a given program (i.e., determining the value of the inputs under which the given path can be executed) \cite{????}).
-The path feasibility problem is usually solved by a reduction to the satisfiability problem of a formula.
+Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed.
+\cite{????}).
+The path feasibility problem is usually solved by a reduction to the satisfiability of a formula.
 More precisely, program statements in the path are usually translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{satisfiability module theory (SMT)}  solvers.
-The types of constraints that needed to be solved by the SMT solvers depend on the type of program variables.
-Therefore, there is a need for SMT solvers that support different combinations of theories (i.e., depending on the types of the manipulated variables).
-
-Among all types of program variables, \emph{string data type}  is omnipresent in modern programming languages.
-Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.
-Therefore, string constraint solving has received considerable attention in the constraint solving community.
+The types of constraints needed depend on the types of program expressions to be analyzed; therefore, SMT solvers must support different combinations of theories to handle a wide range of types.
+
+In particular, \emph{string data}  is omnipresent in modern programming languages, especially in Web code that gets input as strings.
+Various infamous security vulnerabilities, such as injection and cross-site scripting attack, can be caused by malicious string values.
+Therefore, solving string constraint has received considerable attention in the constraint solving community.
 Operations such as \emph{equality constraints} (e.g.
@@
 Thus, $n = \sti{\\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
-are ones of the core operations that require stronger solver support.
+are core operations that require stronger solver support to handle real code.
 
@@
 
-In fact, for many languages such as Java, the string-number conversion operations are is a niche operation, and much symbolic execution can not  be done without supporting it.
+In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
+However, code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
 For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
@@
 Here $value_0$ and $last_0$ are string variables and the others are integer variables.
-The method $\chatAt{x}{i}$ returns the character at the index $i$ in the string $x$ while $n=\ite{b}{e}{e'}$ assigns to $n$ the value of the expression $e$ if $b$ is true and the value of the expression $e'$ otherwise.
+The method $\chatAt{x}{i}$ returns the character at index $i$ in the string $x$ while $n=\ite{b}{e}{e'}$ assigns to $n$ the value of the expression $e$ if $b$ is true and the value of the expression $e'$ otherwise.
 Line 1 describes the initial condition: \textsf{value} should be a sequence of digits and \textsf{sum} is initially zero.
@@
 Line 8 describes the condition of $i_2$ before leaving the loop.
-Finally, Lines 9-10 describe the condition that the last digit of sum is zero.
+Finally, Lines 9-10 describe the condition that the last digit of $sum$ is zero.
 Observe that to describe such a program path, we need a solver that supports the following types of constraints:
@@
 
-Currently, even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
-Therefore, there is an urgent need for developing efficient techniques for solving the combination of above constraints.
+Currently, even for the above constraint, which is from a simple program, most solvers already fail to provide a correct answer.
+Therefore, there is an urgent need for developing efficient techniques for solving such combinations of constraints.
 To make matters worse, many scripting languages, of which JavaScript is the most notable ---it powers most interactive content on the Web, and increasingly server-side code with Node.js---, has conversions between strings and integers embedded in the core of its semantics.
@@
 One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
-For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1  \Leftrightarrow x\not\in [0-9]^*$, where $\Leftrightarrow$ means ``if and only if''.
+For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
 This produce new formulas that over-approximate the original ones and fall in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
-Since $\Phi$ is satisfiable, it is expected that the over-approximation module will not return UNSAT and we proceed to the the under-approximation module to prove SAT.
-
+Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
 In our implementation \tool, we further add heuristics trying to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some other cases, we can derive $n=12$ from some integer constraints.
-In such case, we can further derive that the value of $x$ is in the regular language $(0^*12)$.
-
-For proving SAT, our procedure first restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and then convert the string constraints under the domain restriction to equisatisfiable linear formulas.
+For instance, assume in some other cases, we can derive the value of $n=12$ from some integer constraints.
+In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
+
+Then our procedure will restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and convert them to equisatisfiable linear formula.
+The details of the under-approximation component will be described in Section~\ref{section:under_approximate}.
 Here we try to explain what the linear formula looks like by an example.
@@
 Depending on the implementation, one may choose to report unknown after some certain steps.
-
-\yfc{maybe add a flowchart later if space allows}
 

### 2019-11-18 draft.tex

--- 2019-11-18 draft.tex
@@
 
-Symbolic execution is a very popular technique that allows the programmers to check the feasibility of a path in a given program (i.e., determining the value of the inputs under which the given path can be executed) \cite{????}).
-The path feasibility problem is usually solved by a reduction to the satisfiability problem of a formula.
+Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed.
+\cite{????}).
+The path feasibility problem is usually solved by a reduction to the satisfiability of a formula.
 More precisely, program statements in the path are usually translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{satisfiability module theory (SMT)}  solvers.
-The types of constraints that needed to be solved by the SMT solvers depend on the type of program variables.
-Therefore, there is a need for SMT solvers that support different combinations of theories (i.e., depending on the types of the manipulated variables).
-
+The types of constraints needed depend on the types of program expressions to be analyzed; therefore, SMT solvers must support different combinations of theories to handle a wide range of types.
+
+In particular, \emph{string data}  is omnipresent in modern programming languages, especially in Web code that gets input as strings.
+Various infamous security vulnerabilities, such as injection and cross-site scripting attack, can be caused by malicious string values.
+Therefore, solving string constraint has received considerable attention in the constraint solving community.
 Among all types of program variables, \emph{string data type}  is omnipresent in modern programming languages.
@@
 Thus, $n = \sti{\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
-are ones of the core operations that require stronger solver support.
+are core operations that require stronger solver support to handle real code.
 
@@
 
-In fact, for many languages such as Java, the string-number conversion operations are   niche operations, and much symbolic execution can not  be done without supporting them.
+In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
+However, code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
 For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
@@
 
-Currently, even for a simple constraint like the  one above, most solvers  fail to provide a correct answer.
-Therefore, there is an urgent need for developing efficient techniques for solving such string constraints.
-To make matters worse, many scripting languages, of which JavaScript is the most notable ---it powers most interactive content on the Web, and increasingly server-side code with Node.js---, has conversions between strings and integers embedded in the core of its semantics.
-To see how, consider the following program:
+Currently, even for the above constraint, which is from a simple program, most solvers already fail to provide a correct answer.
+Therefore, there is an urgent need for developing efficient techniques for solving such combinations of constraints.
+To make matters worse, JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, has conversions between strings and integers embedded in the core of its semantics.
+Other scripting languages do too, but we focus on JavaScript due to its prominence.
+To see how string-integer conversion pervades semantics, consider the following program:
 
@@
 Here \texttt{x[3]} in line 2,  \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
-So na\"ive idea of modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
-
-If array indexes are modelled as strings, we need to face the problem of handling of arithmetics in the array index.
+So na\"ive modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
+
+But if array indices are modelled as strings, we must handle arithmetic somehow.
 Let us look at the case of line 6, we need to update the value of \texttt{x["03"-1]}.
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic array operation in Javascript, and so having only limited capability for handling string-number conversion operations  will cripple any analysis of any non-trivial JavaScript code.
+This is a rather basic array operation in Javascript, and so having only limited capability for handling string-number conversion operations  will cripple any analysis of non-trivial JavaScript code.
 

### 2019-11-19 draft.tex
wording

@@
 
-Currently, even for the above constraint, which is from a simple program, most solvers already fail to provide a correct answer.
+Currently, even for the above constraint, which is from a simple program, most solvers fail to provide a correct answer.
 Therefore, there is an urgent need for developing efficient techniques for solving such combinations of constraints.
@@
 
-A casual glance at the above code reveal no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
+A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
 This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
@@
 The Line 4 of the code updates the length of \texttt{x} to $13$ and hence the \texttt{resetArray(x)} will update \texttt{x} to an array with $13$ zeros.
-Now suppose that the Line 4 of the code above is replace to {\tt{x[k] = 5}}, where $\mathtt{k}$ is an user input string and we want to find an input such that $\mathtt{x[15]=0}$.
+Now suppose that the Line 4 of the code above becomes {\tt{x[k] = 5}}, where $\mathtt{k}$ is an user input string and we want to find an input such that $\mathtt{x[15]=0}$.
 In this case, one would need to know the value of $\sti{k}$ and hence whether it will affect the size of the array {\tt{x}}.
@@
 
-Now observe that {\tt{resetArray}} assigns to the array in a loop of which the size cannot, in general, be known a priori; as such, falls into the case where neither the string nor the integer in a conversion is constant and hence most SMT solvers will not be able to handle it.
+Now observe that {\tt{resetArray}} assigns to the array in a loop of which the size cannot, in general, be known a priori; as such, it falls into the case where neither the string nor the integer in a conversion is constant and hence most SMT solvers will not be able to handle it.
 More specifically, in some program the assignment {\tt{x[k] = 5}} can happen before calling {\tt{resetArray(x)}}, where {\tt{k}} is an user input string.
@@
 
-Solving string constraint with string-number conversion is a very challenging problem.
-From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
-In practice, in our experiments (Section \ref{section:evaluation}), the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
-
-In this paper, we propose a framework that handles efficiently string constraints with string-number conversion.
-Due to the high complexity of solving the exact problem, our framework uses both over and under-approximation of the string constraints.
-The over-approximation is for proving UNSAT while the under-approximation is for proving SAT of the string constraint.
+Solving string constraint with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and, in practice, in our experiments (Section \ref{section:evaluation}), the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+
+In this paper, we propose a framework that efficiently handles string constraints with string-number conversion.
+Due to the diffifulty of solving the problem exactly, our framework combines over and under-approximation of string constraints.
+The over-approximation is for proving UNSAT when possible, while the under-approximation is for proving SAT when possible.
 Both over and under-approximation  fall in a decidable fragment of string constraints that can we can efficiently solve.
@@
 
-Our decision procedure proceeds in two steps: The first step consists in over-approximating the set of input constraints into a one that  falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+Our decision procedure has two steps: the first step is over-approximating the set of input constraints into a one that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Observe that we can also over-approximate the input constraint to one that falls in the decidable fragment the acyclic fragment~\cite{abdulla2014string} or the straight-line fragment~\cite{chen2019decision}.
-Our choice of the   chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that  the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints as far as we know.
+Our choice of the   chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that  the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
 In our settings, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
@@
 A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops each of fixed length (see Figure \ref{fig:sfa_def}).
-The approach based on PFA is very flexible yet allows very efficiently manipulation.
-One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-Furthermore, we associate for each character a unique natural number.
+The approach based on PFA is very flexible yet allows very efficient manipulation.
+One can pick PFA of \emph{arbitrary structure} for search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
+Furthermore, we associate a unique natural number  with each character.
 This allows us to assume that the input alphabet is a subset of natural numbers.
-To avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers,  we  labeled each transition between two states of a  PFA by a unique  \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
+To avoids the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers,  we  label each transition between two states of a  PFA with a unique  \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
 Such reduction based on PFA is the key to handle string-number conversion efficiently.
@@
 
-In the following,  we try to explain the construction of the linear formula using the formula $\Phi$ as an example.
-Assume that we project the domain of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.Thus,  $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
+In the following,  we explain the construction of the linear formula using the formula $\Phi$ as an example.
+Assume that we project the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.
+Thus,  $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
 For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
 
-The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$,  as well as, the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$,  as well as the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
 Each model of the linear formula encodes a model of the string constraint.

### 2019-11-19 draft.tex
fix typos

@@
 
+\yfc{We need an abstract}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed.
-\cite{????}).
+\cite{????}.
 The path feasibility problem is usually solved by a reduction to the satisfiability of a formula.
@@
 
-In particular, \emph{string data}  is omnipresent in modern programming languages, especially in Web code that gets input as strings.
-Various infamous security vulnerabilities, such as injection and cross-site scripting attack, can be caused by malicious string values.
-Therefore, solving string constraint has received considerable attention in the constraint solving community.
 Among all types of program variables, \emph{string data type} is omnipresent in modern programming languages.
@@
 When there is support, it is often very limited.
-Thus, $n = \sti{\texttt{"2"}}$  or $x = \its{5}$  are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and  $x = \its{n}$ (i.e.,  converting the integer $n$ to the string $x$)
-are core operations that require stronger solver support to handle real code.
+Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations that require stronger solver support to handle real code.
 
@@
 The selection is an implementation decision.
-We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
+We will describe the PFA selection strategy of {\tool} in Section~\ref{section:implementation}.
 

### 2019-11-19 evaluation.tex
Update tables in evalutaion

@@
 
-\todo{Organize/Revise the context; Add references of benchmarks; Revise tables; Discussions}
+\todo{Add comparison/discussion; References of benchmarks; Update data; Sepatate categories of str\_int benchmark for discussion}
 
+\begin{table*}[t]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
+\begin{tabular}{l r | r r r r r r r}
+\hline
+\multicolumn{2}{c}{}                   & Z3-Trau & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
+							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
+							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
+							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
+\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
+							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
+							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
+							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
+\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
+							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
+							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
+							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
+\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
+							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
+							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
+							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
+\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
+							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
+							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
+							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
+\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
+							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
+							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
+							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
+\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
+							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
+							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
+							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
+\end{tabular}
+\label{table:base_benchmark}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
+\begin{tabular}{l r | r r r r r r r}
+\hline
+\multicolumn{2}{c}{}                           & Z3-Trau & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
+									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
+									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
+									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
+\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
+									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
+									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
+									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
+\end{tabular}
+\label{table:str_int_benchmark}
+\end{table*}
+
+\hide{
 \begin{table*}[t]
@@
 \end{table*}
+}
 
+\hide{
 \begin{table*}[t]
@@
 \end{table*}
+}
 

### 2019-11-19 evaluation.tex
Update tables

@@
 
+\begin{table*}[t]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
+\begin{tabular}{l r | r r r r r r r}
+\hline
+\multicolumn{2}{c}{}                   & Z3-Trau & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
+							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
+							& $\times$ &  1977*   &  1824* &  3211 &  18558*  & 2444 & 25421 & 24439 \\ \hline
+\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
+							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
+							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
+\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
+							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
+							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
+\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
+							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
+							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\
+\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
+							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
+							& $\times$ &     5*   &     6* &    15 &     55*  & 88 & 76 & 797 \\ \hline
+\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
+							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
+							& $\times$ &     2*   &   101* &    17 &     71*  & 137 & 120 & 978 \\ \hline
+\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
+							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
+							& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\ \hline
+\end{tabular}
+\label{table:base_benchmark}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
+\begin{tabular}{l r | r r r r}
+\hline
+\multicolumn{2}{c}{}                   & Z3-Trau & CVC4   &    Z3  & Z3-str3 \\ \hline
+\multirow{3}{*}{StrInt}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
+							& unsat    &  17088*  & 16377* & 16832* &  16034* \\
+							& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline
+\multirow{3}{*}{leetcode-addStrings}	& sat & 622*  &  330* &  100* &  85* \\ 
+							& unsat    &  1054*  & 780* & 1043* &  634* \\
+							& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
+\multirow{3}{*}{leetcode-add\_Binary}	& sat & 520*  &  530* &  531* &  11* \\ 
+							& unsat    &  1351*  & 1091* & 1091* &  1094* \\
+							& $\times$ &  11*  &  261* &  260* & 777* \\ \hline
+\multirow{3}{*}{leetcode-numDecodings}	& sat & 166*  &  107* &  151* &  50* \\ 
+							& unsat    &  273*  & 269* & 283* &  269* \\
+							& $\times$ &  92*  &  155* &  97* & 212* \\ \hline
+\multirow{3}{*}{leetcode-restoreIpAddresses}	& sat & 811*  &  462* &  864* &  55* \\ 
+							& unsat    &  13648*  & 13540* & 13648* &  13342* \\
+							& $\times$ &  54*  &  511* &  1* & 1116* \\ \hline
+\multirow{3}{*}{leetcode-validIPAddress}	& sat & 54*  &  57* &  58* &  8* \\ 
+							& unsat    &  19*  & 19* & 19* &  19* \\
+							& $\times$ &  4*  &  1* &  0* & 50* \\ \hline
+\multirow{3}{*}{leetcode-validWordAbbreviation}	& sat & 183*  &  193* &  188* &  8* \\ 
+							& unsat    &  24*  & 11* & 21* &  16* \\
+							& $\times$ &  39*  &  42* &  37* & 222* \\ \hline
+\multirow{3}{*}{lib-datetime\_parse\_hh\_mm\_ss\_ff}	& sat &  133*  & 133* &  133* &  88* \\ 
+							& unsat    &  41*  & 41* & 41* &  43* \\
+							& $\times$ &  0*  &  0* &  0* & 43* \\ \hline
+\multirow{3}{*}{lib-datetime\_parse\_isoformat\_date}	& sat & 32*  &  32* &  32* &  23* \\ 
+							& unsat    &  0*  & 0* & 0* &  0* \\
+							& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
+\multirow{3}{*}{lib-distutils\_get\_build\_version}	& sat & 19*  &  19* &  19* &  4* \\ 
+							& unsat    &  24*  & 24* & 24* &  24* \\
+							& $\times$ &  0*  &  0* &  0* & 15* \\ \hline
+\multirow{3}{*}{lib-email\_parsedate\_tz}	& sat & 68*  &  72* &  72* &  30* \\ 
+							& unsat    &  138*  & 138* & 138* &  138* \\
+							& $\times$ &  4*  &  0* &  0* & 42* \\ \hline
+\multirow{3}{*}{lib-http\_parse\_request}	& sat & 24*  &  24* &  24* &  8* \\ 
+							& unsat    &  9*  & 9* & 9* &  7* \\
+							& $\times$ &  0*  &  0* &  0* & 18* \\ \hline
+\multirow{3}{*}{lib-ipaddress\_ip\_int\_from\_string}	& sat & 595*  &  204* &  480* &  18* \\ 
+							& unsat    &  427*  & 373* & 431* &  357* \\
+							& $\times$ &  1006*  &  1451* &  1117* & 1653* \\ \hline
+\multirow{3}{*}{lib-nntplib\_parse\_datetime}	& sat & 4*  &  8* &  0* &  0* \\ 
+							& unsat    &  0*  & 0* & 0* &  0* \\
+							& $\times$ &  4*  &  0* &  8* & 8* \\ \hline
+\multirow{3}{*}{lib-smtpd\_parseargs}	& sat & 27*  &  27* &  27* &  24* \\ 
+							& unsat    &  72*  & 72* & 72* &  66* \\
+							& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
+\multirow{3}{*}{lib-wsgiref\_check\_status}	& sat & 10*  &  10* &  10* &  6* \\ 
+							& unsat    &  9*  & 9* & 9* &  9* \\
+							& $\times$ &  0*  &  0* &  0* & 4* \\ \hline
+% \multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* \\
+% 									& unsat    &   2912*  &  2211* &  2655* &   1944* \\
+% 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
+\end{tabular}
+\label{table:str_int_benchmark}
+\end{table*}
+
+\hide{  % 2nd version of tables
 \begin{table*}[t]
@@
 \end{table*}
+}
 
-\hide{
+\hide{  % 1st version of tables
 \begin{table*}[t]

### 2019-11-19 draft.tex
update implementation and evaluation section

@@
 \newcommand{\hide}[1]{}
-\newcommand{\tool}{{\textsf{Z3-pfa}}}
+\newcommand{\tool}{{\textsf{Z3-PFA}}}
 
@@
 \section{Implementation}\label{section:implementation}
+The tool {\tool} is done by implementing our string constraint solving procedure on top of the SMT solver Z3~\cite{z3} as a theory solver.
+In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
+It also enable us to solve not only formulas over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulas.
+
+In {\tool}, we use the following PFA selection strategy: we select PFA's of size $m$ for string variables occur a number-string conversion constraint and PFA's with $p$ loops of size $q$ for other variables.
+Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required.
+We set an upper bound $7$ for each parameters and report UNKNOWN if a solution cannot be found within the bound.
+\yfc{need to check with Diep for the parameters}.
+
+The way our theory solver and Z3 interacts is almost standard.
+Every time when Z3 asks our theory solver a problem in string theory, our theory solver tries to prove it UNSAT or SAT using the aforementioned procedure.
+For under-approximation, every time when a linear formula for under-approximation is created, we create a new solver for linear integer arithmetic inside Z3 to solve it.
+If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and tries another solution branch.
+If all Z3 completed the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.
+
 \input{evaluation}

### 2019-11-19 evaluation.tex
update implementation and evaluation section

--- 2019-11-19 evaluation.tex
@@
 \label{section:evaluation}
-
-\todo{Add comparison/discussion; References of benchmarks; Update data; Sepatate categories of str\_int benchmark for discussion}
 
@@
 
-We have implemented the proposed approach in a prototype tool \tool as a part of the Z3 theorem prover.
-This approach allows us to efficiently solve not only formulae over string constraints, but also combine string constraints with constraints over other theories that Z3 supports.
-Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.
-
-We compare \tool with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
-We do not compare with Sloth \cite{sloth} since it does not support length constraints.
+We compare {\tool }with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
+We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
 We present data on two benchmark groups that demonstrate two points.
-First, only our tool can efficiently solve formulae that contain string-number and number-string conversion constraints and which can be a combination of constraints over multiple theories.
-Second, we show that our tool is competitive on conversion-less benchmarks as well.
-The summary of experimenting for each benchmark group is given in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
+First, {\tool} is the most efficient tool for formulas that contain string-number conversion constraints.
+Second, {\tool} is among the best tools in on benchmarks without string-number conversion constraints.
+The results of the experiments is summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
 All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS.
 The timeout was set to 10s for each test.
-Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulae.
-Columns with heading \texttt{timeout} indicate the number of times the solver exceeded the time limit and columns with heading $\times$ show numbers of instances for which the particular solver either reported unknown or reported incorrect answer or crashed.
+Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas.
+Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crashed).
 
@@
 Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test.
-The modified test is re-evaluated by solvers.
-If the solvers decide that the modified test is satisfiable, the answer of the solvers that initially reported unsat is evaluated as incorrect.
+The modified test is re-evaluated by multiple solvers.
+If all solvers decide that the modified test is satisfiable, the answer of the solvers that initially reported unsat is evaluated as incorrect.
 

### 2019-11-19 evaluation.tex
add a missing hline in table 2
fix some typos

@@
 \hline
-\multicolumn{2}{c}{}                   & Z3-Trau & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
@@
 							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
-							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\
+							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\\hline
 \multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
@@
 
-\begin{table*}[t]
+\begin{table}[t]
 \centering
-\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
+\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
+\scalebox{0.7}{
 \begin{tabular}{l r | r r r r}
 \hline
-\multicolumn{2}{c}{}                   & Z3-Trau & CVC4   &    Z3  & Z3-str3 \\ \hline
+\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
 \multirow{3}{*}{StrInt}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
@@
 % 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
-\end{tabular}
+\end{tabular}}
 \label{table:str_int_benchmark}
-\end{table*}
+\end{table}
 
@@
 \centering
-\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
+\caption{Results of {\tool}, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
 \begin{tabular}{l r | r r r r r r r}
 \hline
-\multicolumn{2}{c}{}                   & Z3-Trau & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
@@
 \centering
-\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
+\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
 \begin{tabular}{l r | r r r r r r r}
 \hline
-\multicolumn{2}{c}{}                           & Z3-Trau & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
@@
 \centering
-\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
+\caption{Results of {\tool}, cvc4, and z3 on string benchmarks}
 \begin{tabular}{l | r r r | r r r | r r r | r r r}
@@
 
-We compare {\tool }with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.

### 2019-11-19 evaluation.tex
add evaluation

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}.
+Our tool {\tool} is done by implementing the proposed string constraint solving procedure on top of the SMT solver Z3~\cite{z3} as a theory solver.
+In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
+It also enable us to solve not only formulas over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulas.
+
+In {\tool}, we use the following PFA selection strategy: we select PFA's of size $m$ for string variables occur a number-string conversion constraint and PFA's with $p$ loops of size $q$ for other variables.
+Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required.
+We set an upper bound $7$ for each parameters and report UNKNOWN if a solution cannot be found within the bound.
+\yfc{need to check with Diep for the parameters}.
+
+The way our theory solver and Z3 interacts is almost standard.
+Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure.
+For under-approximation, every time when a corresponding linear formula is created, we create a new Z3 solver instance to solve it.
+If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and tries another solution branch.
+If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.
+
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{Z3-str3}~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
-We present data on two benchmark groups that demonstrate two points.
-First, {\tool} is the most efficient tool for formulas that contain string-number conversion constraints.
-Second, {\tool} is among the best tools in on benchmarks without string-number conversion constraints.
-The results of the experiments is summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
-All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS.
-The timeout was set to 10s for each test.
+We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.
+
+We perform two sets of experiments. In the first experiment, we compare with other tools on benchmarks over basic string constraints. We use the following benchmark examples in this experiments:
+\begin{itemize}
+	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
+	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
+	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
+	\item StringFuzz~\cite{StringFuzz}  is generated from the fuzz testing tool of the same name.
+	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}. This benchmark also contains some string-number conversion constraints.
+\end{itemize}
+
+In the second experiment, we compare with tools supporting to string-number conversion on the  benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
+We run it on several examples collected from the LeetCode platform and from Python core libraries.
+
+All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test.
+We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
+Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test.
+To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtained a modified test, and re-evaluates the modified test by multiple solvers.
+If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results.
+Otherwise, we manually simplify and inspect the test until we get a conclusive result.
+
+The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
 Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas.
-Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crashed).
+Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
+From Table~\ref{table:base_benchmark}, we can see that the performance  of {\tool} is as good as the most competitive tools such as CVC4 and Z3 on basic string constraints.
+In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases.
+If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases.
+But we believe this is not very important because both these two cases are artificial, either hand-crafted or randomly produced from a fuzzer.
+The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.
 
-Occasionally, during the experiments, there was a case where a solver reported a different answer to a test than the other solvers.
-To decide which solver reported the incorrect answer, we have developed our own validator.
-Our validator takes the model from the solver who reported that the test is satisfiable and assigns the corresponding values according to the returned model to the variables in the test.
-The modified test is re-evaluated by multiple solvers.
-If all solvers decide that the modified test is satisfiable, the answer of the solvers that initially reported unsat is evaluated as incorrect.
+From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
+The number of failed cases is only a half to Z3, which is ranked the 2nd.
+In fact, most of the failed tests comes from the analysis of {lib-ipaddress\_ip\_int\_from\_string}, which converts an IPv6 address to a number.
+This function has a very long execution path and hence the size of each SMT file from this analysis is roughly 1MB.
+If we exclude results on this benchmark, then {\tool} has only $185$ failed case.
+This is significantly better than the 2nd place tool Z3, which fails $893$ cases.
 
-\paragraph{A Comparison with other tools on conversion-less benchmarks.}
+\hide{
+\paragraph{Basic constraint benchmarks.}
 This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups.
@@
 
-\paragraph{A Comparison on benchmarks containing string-number and number-string constrains.}
+\paragraph{String-number conversion constraint benchmarks.}
 Our second group of benchmarks was created in order that we could compare our proposed approach for solving string-number and number-string conversions with existing approaches.
@@
 In total, we managed to create 43 tests that combine several SMT theory and contain conversion constrains.
+}
 

### 2019-11-19 draft.tex
add evaluation
pass through the technical things

--- 2019-11-19 draft.tex
@@
 \newcommand{\iequiv}{\equiv}
-\newcommand{\restrict}[2]{#1{\restriction_{#2}}}
+\newcommand{\restrict}[2]{#1_{#2}}
 \newcommand{\underf}[2]{\mathit{under}_#1(#2)}
-\newcommand{\pfaf}{\psi}
-
-\newcommand{\leftA}{A^{\mathit{left}}}
-\newcommand{\rightA}{A^{\mathit{right}}}
+\newcommand{\paf}{\psi}
+
+\newcommand\pa{P}
+%\newcommand\pa{\textsc{Pa}}
+%\newcommand\pa{\mathcal{A}}
+\newcommand{\leftA}{\pa^{\mathit{left}}}
+\newcommand{\rightA}{\pa^{\mathit{right}}}
 \newcommand{\leftV}{V^{\mathit{left}}}
@@
 \newcommand\outlf{\Psi_{\mathit{out}}}
+\newcommand\noepsilon{|\!|\epsilon|\!|}
 
@@
 
-\section{Under-approximation} \label{section:under_approximate}
-In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulas $\outlf$ in polynomial-time.
+%\section{Under-approximation} \label{section:under_approximate}
+%In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulas $\outlf$ in polynomial-time.
 We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
-
-We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
+%
+%We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
 In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\outlf$.
 We also add constraints to $\outlf$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
-
-More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$.
+%
+%More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$.
 After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
@@
 The selection is an implementation decision.
-We will describe the PFA selection strategy of {\tool} in Section~\ref{section:implementation}.
-
-After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\insc$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\outlf$.
+We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
+%
+%After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\insc$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\outlf$.
 The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
 In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
-
-\hide{We replace it with the following constraints.
-
-	$$
-	\begin{array}{c}
-	(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
-	\left(
-	\begin{array}{cccc}
-
-	y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
-	y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
-	|y_2|&=&|y'_2|=1
-	\end{array}
-
-	\right)
-	\end{array}
-	$$
-
-	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
+%
+%
+% 
+%
+%
+%
+%\hide{We replace it with the following constraints.
+%	
+%	$$
+%	\begin{array}{c}
+%	(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
+%	\left(
+%	\begin{array}{cccc}
+%	
+%	y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
+%	y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
+%	|y_2|&=&|y'_2|=1
+%	\end{array}
+%	
+%	\right)
+%	\end{array}
+%	$$
+%	
+%	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
 In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
 }
-
-\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
+%
+%
+%\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{additional presburget constraints to encode $\epsilon$ added at translation to a formula}
+%\newcommand{\st}[2]{q_{#1}^{#2}}
+%\newcommand{\sym}[2]{v_{#1}^{#2}}
 %We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
@@
 \paragraph{Flat automata}
-First, we say that an automaton FA 
+First, we say that an FA 
 $A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is \emph{flat} if it satisfies the following structural constraints:
@@
 This is facilitated by flatness, which guarantees that 
-every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$, i.e., $\decode A (\parikhof w)) = w$, and analogously for the entire language of $A$, as formalized by the following lemma.
-
-\begin{lemma}\label{lemma:parikh}
-For an flat FA $A$ and $w,w'\in L(A)$, if $\parikhof w = \parikhof {w'}$ then $w = w'$. 
+every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$. 
+In fact, the the parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquelly decoded:
+%i.e., $\decode A (\parikhof w)) = w$, 
+%and analogously for the entire language of $A$, as formalized by the following lemma.
+
+\begin{lemma}\label{lemma:decoding}
+For an flat FA $A$, there is a function $\decode A$ such that for each $w\in L(A)$, $\decode A(\parikhof w) = w$. 
 \end{lemma}
 %
-Indeed, since every variable appears on at most one transition, then the $\parikhof w$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
+\begin{proof}
+Indeed, since every variable appears on at most one transition, then the $\parikhof w$ value of all variables appearing within the same cycle of $A$ is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
 %
@@
 
-For example, in the automaton of Figure~\ref{fig:sfa_def}, 
-from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
-
-We may say that $\parikhof w$ is an encoding of $w$, and define the decoding function $\decode A$ such that $\decode A(\parikhof w) = w$, and we lift the function to sets of integer assignments in the standard manner.
-%
-
-%\begin{lemma}\label{lemma:decx}
-%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
-%\end{lemma}
-%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
-%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
-
-\begin{lemma}\label{lemma:decx}
-%For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in \parikhof A\}$.
-For a flat FA $A$, $L(A) = \decode A(\parikhof{L(A)}$.
-\end{lemma}
-%\lh{should we replace $\semof{\parikhfof A}$ by $\parikhof{A}$ here and almost everywhere?}
-%\yfc{Is $\parikhof{A}$ defined only over $\#I$? Does this work for Corollary~\ref{corollary:pfa}?}
-%
-\begin{proof}
-The function $\decode A$ can particularly be implemented as follows. Given $\pim:\pvars\rightarrow\nat$,
+More concretely, the function $\decode A$ can be implemented as follows. 
+Given $\pim:\#\cvar\rightarrow\nat$,
 and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m-1}$, 
@@
 \end{proof}
+%
+For example, in the automaton of Figure~\ref{fig:sfa_def}, 
+from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
 
 \paragraph{Parametric (flat) automata}
-Next we define \emph{parametric automaton} (PA) as a tuple $A = (Q,T,\cvar,\st{0}{0},\st{m}{0},\pfaf)$ where $\pfaf$ is an \emph{interpretation constraint}, a linear formula over $\cvar$, and $(Q,T,\cvar,\st{0}{0},\st{m}{0})$ is an automaton operating over an alphabet $\cvar$ of \emph{character variables}.
+Next we define \emph{parametric automaton} (PA) as a pair  $\pa = (A,\paf)$ where 
+$A$ is an automaton operating over an alphabet $\cvar$ of \emph{character variables}  
+and $\paf$ is an \emph{interpretation constraint}, a linear formula over $\cvar$. 
 \emph{Parametric flat automaton (PFA)} then is a parametric automaton with its finite automaton flat.
 
-%
-%\begin{figure*}
-%	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
-%			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
-%	\begin{tikzpicture} 
-%		\node[state,initial] (q0) {$\st{0}{0}$};
-%		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
-%		\node (q2) [right = 1.8cm of q1]{};
-%		\node (q3) [right = 1cm of q2]{};
-%		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
-%		
-%		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
-%		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
-%		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
-%
-%		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
-%		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
-%
-%		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
-%		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
-%		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
-%
-% 		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
-% 		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
-% 		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
-% 		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
-% 		
-% 		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
-% 		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
-% 		\draw[dotted] (q2) edge (q3) ;
-% 		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
-%
-% 		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
-%		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
-%		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
-%		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
-%
-% 		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
-%		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
-%		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
-%	\end{tikzpicture} 
-%
-%	\caption{An example of a parametric flat automaton}
-%	\label{fig:sfa_def}
-%\end{figure*}
-%
+\begin{figure*}
+	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+	\begin{tikzpicture} 
+		\node[state,initial] (q0)  {$\st{0}{0}$};
+		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
+		\node (q2) [right = 1.8cm of q1]{};
+		\node (q3) [right = 1cm of q2]{};
+		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
+
+		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
+		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
+		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
+
+		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
+		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
+
+		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
+		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
+		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
+
+  		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
+  		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
+  		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
+  		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
+
+  		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
+  		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
+  		\draw[dotted] (q2) edge (q3) ;
+  		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
+
+  		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
+		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
+		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
+		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
+
+  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
+		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
+	\end{tikzpicture}
+
+	\caption{An example of a parametric flat automaton}
+	\label{fig:sfa_def}
+\end{figure*}
+
 %A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a PFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
@@
 Namely, words over $\cvar$ are interpreted as words over $\Sigma$ under an
-\emph{interpretation of $\cvar$}
-%
-a mapping from $I:\cvar\rightarrow$ to $\Sigma_\epsilon$. For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-%
-We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics of an PFA is the semantics of its language restricted by the formula $\pfaf$, that is, $\semof A = \semof{L(A)}\cap\semof\pfaf$.
-
-Since every word $w \in \semof{A}$ is obtained from a parametric word $x\in L(A)$ and an interpretation of character variables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$,
-we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric word $x$ encodes $w$.
-Lemma~\ref{lemma:parikh} also implies that two different words are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup \parikhof x) = w$, and we again lift the decoding function into sets of interpretations in the standard manner.
-The following corrolary of Lemma~\ref{lemma:decx} states that encodings of words in $\semof{A}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$ that satisfy $\pfaf$:%, which are precisely all models of the formula $\parikhfof A$ interpreted over $\cvar\cup\pvarsof \cvar$, as formulated by the following corollary of Lemma~\ref{lemma:decx}:
-%
-%\begin{corollary}\label{corollary:pfa}
-%For an PFA $A$ over character variables $V$,
-%$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$.
-%%$\semof{A} = \{I(\decode A(\pim)) \mid \pim\in\semof{\parikhfof A},I:\cvars\rightarrow\Sigma_\epsilon\}$.
-%\end{corollary}
+\emph{interpretation of $\cvar$},
+%
+a mapping $I:\cvar\rightarrow$ to $\Sigma_\epsilon$. 
+For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretaion $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+%
+We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics of a PA is the semantics of its language restricted by the formula $\paf$, that is,
+$\semof {\pa} = \{I(w) \mid w\in L(A),I\in\semof \paf\}$.
+
+Since every word $w \in \semof{\pa}$ is uniquelly determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x$ is uniquelly determined by its Parikh image, i.e.,
+$\decode \pa(\parikhof x)$, 
+we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I:\cvar\rightarrow\nat$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$ \emph{$\pa$-encodes} $w$.
+Lemma~\ref{lemma:decoding} implies such $\pa$-encoding can be uniquelly decoded.
+We may hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ 
+so that $\decode \pa(I \cup \parikhof x) = w$. 
+We again lift the decoding function into sets of united assighnments in the standard manner.
+The following corrolary of Lemma~\ref{lemma:decoding} states that encodings of words in $\semof{\pa}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$ that satisfy $\paf$:
 
 \begin{corollary}\label{corollary:pfa}
-For an PFA $A = (Q,T,\cvarone,q_i,q_f,\pfaf)$,
-%$\semof{A} = \{(\decode A(I\cup\pim)) \mid \pim\in\parikhof A,I:\cvars\rightarrow\Sigma_\epsilon\}$.
+For an PFA $\pa = (A,\paf)$,
 \\
-$\semof A = \decode A \{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I\in\semof\pfaf\}$.
+\centerline{$\semof {\pa} = \decode \pa \{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I\in\semof\paf\}$.}
 \end{corollary}
@@
 
-Last, we define the encoding function as a counterpart of the decoding. Given a PFA $A$, and a language $L\subseteq \Sigma^*$, we define the set of $A$-encodings of the words in $L$ as 
-$\encode A (L) = \{e \mid \decode A (e) \in L\}$. 
-%
-Notice that only the words from $L\cap \semof A$ have an $A$-encoding, 
-hence $\encode A(L) = \encode A(L\cap\semof A)$, and so due to Corollary~\ref{corollary:pfa}, $\decode A({\encode A}(L)) = L\cap\semof A$.
+Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$, and a language $L\subseteq \Sigma^*$, we define the set of $\pa$-encodings of the words in $L$ as 
+$\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
+%
+Notice that only the words from $L\cap \semof \pa$ have an $\pa$-encoding, 
+hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
 %$\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$. 
@@
 
+%\section{Under-approximation} \label{section:under_approximate}
+%In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulas $\outlf$ in polynomial-time.
+We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
+%
+%We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
+In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\outlf$.
+We also add constraints to $\outlf$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
+%
+%More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$.
+After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
+For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA.
+We do not set any restriction to the selection of PFA for other string variables.
+The selection is an implementation decision.
+We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
+%
+%After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\insc$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\outlf$.
+The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
+In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
+%
+%
+% 
+%
+%
+%
+%\hide{We replace it with the following constraints.
+%	
+%	$$
+%	\begin{array}{c}
+%	(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
+%	\left(
+%	\begin{array}{cccc}
+%	
+%	y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
+%	y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
+%	|y_2|&=&|y'_2|=1
+%	\end{array}
+%	
+%	\right)
+%	\end{array}
+%	$$
+%	
+%	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
+In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
+}
+%
+%
+%\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
+
 \section{Flat Domain Restriction}
-Let us now give a precise definition of how we restrict the domain of string constraints using flat automata. 
-A \emph{flat domain restriction} for a string contraint $\insc$ over variables $X$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
-For technical reasons that will be apparent further in this section, we require that if $x\neq y$, then $R(x)$ and $R(y)$ operate over disjoint sets of character variables.
-We will use $V_R$ to denote the union of character variables of all $R(x),x\in X$.
+\label{section:under_approximate}
+
+%
+In this section, we describe formally how to restrict the domain of string variables to patterns defined by PFA, 
+and start the description of the algorithm that converts a string constraint $\insc$ to a linear formula $\outlf$ representing the restricted set of solutions.  
+%
+
+The domain restriction is formally defined by restricting the domain of each string variable to a chosen flat language. 
+%
+Namely, assuming that $X$ is the set of string variables of $\insc$,
+a \emph{flat domain restriction} for $\insc$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
+%
+We require that these PFA operate over pairwise disjoint sets of character variables. 
+%
+The particular choice of a PFA 
+for each variable  depends on the stratedy used in the implementation, and will be discussed in Section~\ref{section:implementation}.
+%
+The formula $\outlf$ will be  built intuctively to the structure of $\insc$.
+Namely, in the followin subsections we show how to build a formula $\underf R {\phi}$ for every atomic string constraint $\phi$, 
+and for a conjunction of string constraints, we let $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
+% and $\underf R {\neg\phi} \defeq \neg\underf R{\phi}$. The underapproximation formula is then in the form $\outlf \defeq \underf R {\insc}$.
 
@@
 $\semof{\phi}^R = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{R(x)}\}$. 
-In the rest of this section, we will show how to build an \emph{underapproximating formula} representing the semantics $\semof{\insc}^R$ of an input string constraint, that is, a formula $\outlf$ such that
+The following sections will be devoded to describing the construction of the formula $\outlf$ representing the $R$-restriction of $\insc$, that is, such that the following theorem holds: 
+The correctness of this construction is expressed by  Theorem~\ref{theorem:correct}:
+\begin{theorem}\label{theorem:correct}
 $\decode R (\semof {\outlf}) = \semof{\insc}_R$. 
-
-The formula $\outlf$ is built intuctively to the structure of $\insc$.
-Namely, in the followin subsections we show how to build a formula $\underf R {\phi}$ for every atomic string constraint $\phi$, 
-and for a conjunction of 
-string constraints we have $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
-% and $\underf R {\neg\phi} \defeq \neg\underf R{\phi}$. The underapproximation formula is then in the form $\outlf \defeq \underf R {\insc}$.
-
-The correctness of this construction, that is, that 
-$$\decode R (\semof {\outlf}) = \semof{\insc}^R$$ can be proved by induction to the structure of $\insc$.
-However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf R \phi$.
+\end{theorem}
+
+The theorem can be proved by induction to the structure of $\insc$,
+however, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf R \phi$ than just equality of their semantics. 
 Particularly, we will need to
-%pay attention to how $\underf R \phi$ atually encodes the models of $\phi$, and
  ensure that $\underf R \phi$ captures exactly all $R$-encodings of $\semof \phi^R$
@@
 To this end, we define an additional notation.
-For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode A(I(x))$.
+For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$.
 We lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
@@
 $$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
-We note that the restriction of the semantics of $\underf R \phi$ here is needed here since it is constructed with some additional variables.
-
-\paragraph{Encoding $\epsilon$}
+%
+In the nexr sections, 
+we will formulate the corresponding lemma for linear formulae constructed from each type of atomic string constraints.
+%
+We note that the restriction of the semantics of $\underf R \phi$ here is needed since $\underf R \phi$ is constructed with some auxiliary variables.
+
+\paragraph{Encoding epsilon.}
 A minor technical difficulty is that we wish to build underapproximation in the form of pure arithmetic formulas, 
-but we may also wish to specify when a character variable is assigned $\epsilon$, which is not a number. 
-To allow purely arithmetic formulas to talk about $\epsilon$, we encode $\epsilon$ as $-1$.
-In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulas constraining interpretations of character variables.
+but we may also wish to specify when a character variable is assigned $\epsilon$, but $\epsilon$ is not a number. 
+Hence, to allow purely arithmetic formulas talk about $\epsilon$, 
+we encode $\epsilon$ as some fixed number $\noepsilon\in\nat\setminus\Sigma$.
+%In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulas constraining interpretations of character variables.
 
 %\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
-\section{Flattening of basic string constraints}
-By basic string constraints, we mean regular, equality, and lenght constraints.
-First, we discuss operations over PA needed to implement them, synchronisation and concatenation.
+\section{Flattening of Basic String Constraints}
+We will first discuss flattening of the basic string contraints, that is,
+regular, equality, and lenght constraints. We start by two needed operations over PA, synchronisation and concatenation.
 
 \paragraph{Synchronization of PAs}
-We will now discuss a construction of the \emph{synchronization formula} for two PAs $A$ and $A'$. 
+We will now discuss a construction of the \emph{synchronization formula} for two PAs $\pa$ and $\pa'$. 
 %over character variables $V$ and $V'$. 
-It is a linear formula $\syncfof A {A'}$ 
+It is a linear formula $\syncfof \pa {\pa'}$ 
 %over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ 
-that specifies how each word in the semantic intersection $\semof A \cap \semof {A'}$ is encoded by $A$ and by $A'$.
-%
-More precisely, the models of $\syncfof A {A'}$ represent pairs of word
-encodings $(I\cup \parikhof{x})$ and $(I'\cup \parikhof{x'})$ such that $x\in L(A)$, $x'\in L(A')$, and 
-$I(x) = I'(x')$.
-% \in \semof{A}\cap\semof{A'}$.
-The synchronization formula will be used in, e.g., the decision procedure of equality constraints $t_1=t_2$ to find a common interpretation~of~$t_1$~and~$t_2$. 
-%More precisely, the models of the synchronization formula $\syncfof A {A'}$ correspond to the set of all pairs of word
-%encodings $(I\cup \parikhof{x})$ and $(I'\cup \parikhof{x'})$ such that $x\in L(A)$, $x'\in L(A')$, and 
-%$I(x) = I'(x') \in \semof{A}\cap\semof{A'}$.%, which constitute the intersection.
-% encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
-%$I(\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$, which constitute the intersection.
-
+that specifies how each word in the semantic intersection $\semof \pa \cap \semof {\pa'}$ is encoded by $\pa$ and by $\pa'$.
+%
+More precisely, the models of $\syncfof \pa {\pa'}$ represent pairs of word
+encodings 
+$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode \pa(w')$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
+%
 Particularly, the synchronization formula is built for two PAs  
-$A = (Q,T,\cvarone,q_i,q_f,\pfaf)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f',\pfaf')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
-%
-It is extracted from the \emph{asynchronous product} of $A$ and $A'$. 
+$\pa = ((Q,T,\cvarone,q_i,q_f),\paf)$ and ${\pa'} = ((Q',T',\cvartwo,q_i',q_f'),\paf')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
+%
+It is extracted from the \emph{asynchronous product} of $\pa$ and $\pa'$. 
 %
@@
 %
-Every accepting run of $\syncof A {A'}$ corresponds to a pair of accepting runs, 
-a run of $A$ over a parametric word $x$ and a run of ${A'}$ over a parametric word $x'$. 
-The word accepted by the run of $\syncof A {A'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric words have the same interpretation, i.e.
+Every accepting run of $\syncof \pa {\pa'}$ corresponds to a pair of accepting runs, 
+a run of $\pa$ over a parametric word $x$ and a run of ${\pa'}$ over a parametric word $x'$. 
+The word accepted by the run of $\syncof \pa {\pa'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric words have the same interpretation, i.e.
 $I(x) = I'(x')$.
 
-Intuitively, when the product automaton $\syncof A {A'}$ takes a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$, 
+Intuitively, when the product automaton $\syncof \pa {\pa'}$ takes a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$, 
 it means the character variable $v$ and $v'$ should be assigned the same value,
-$A$ transitions under $v$ from state $q_1$ to state $q_2$ and ${A'}$ from $q_1'$ to $q_2'$ under $v'$.
-%
-When $\syncof A {A'}$ takes a transition $((q_1,q_1'), (v,\epsilon),(q_2,q_1'))$, 
+$\pa$ transitions under $v$ from state $q_1$ to state $q_2$ and ${\pa'}$ from $q_1'$ to $q_2'$ under $v'$.
+%
+When $\syncof \pa {\pa'}$ takes a transition $((q_1,q_1'), (v,\epsilon),(q_2,q_1'))$, 
 it means that the character variable $v$ should be assigned $\epsilon$, 
-$A$ transitions under $v$ to $q_1$, and ${A'}$ takes no action, since no action is needed to match $A$'s reading of $\epsilon$ (hence consumes no symbol from the input word).
-Symmetrically, ${A'}$ might read a variable $v$ assigned $\epsilon$ and $A$ may stay.
-
-Formally, the asynchronous product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'),\pfaf\land\pfaf')$, where the transition relation $\syncT$ is the minimal set satisfying the following:
+$\pa$ transitions under $v$ to $q_1$, and ${\pa'}$ takes no action, since no action is needed to match $\pa$'s reading of $\epsilon$ (hence consumes no symbol from the input word).
+Symmetrically, ${\pa'}$ might read a variable $v$ assigned $\epsilon$ and $\pa$ may stay.
+
+Formally, the asynchronous product automaton is a tuple $\syncof \pa {\pa'} = ((Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f')),\paf\land\paf')$, where the transition relation $\syncT$ is the minimal set satisfying the following:
 %
@@
 %
-%The we define of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
-The synchronization formula $\syncfof{A} {A'}$ is extracted from $\syncof A {A'}$ as follows.
-Its first part is the Parikh formula $\parikhfof {\syncof A {A'}}$ of the product, which encodes all runs of the product.
-%
-The second part is a constraint that extracts from a run of $\syncof A {A'}$ the corresponding runs of $A$ and of $A'$:
+The synchronization formula $\syncfof{\pa} {\pa'}$ is extracted from $\syncof \pa {\pa'}$ as follows.
+Its first part is the Parikh formula $\parikhfof {\syncof \pa {\pa'}}$ of the product, which encodes all runs of the product.
+%
+The second part is a constraint that extracts from a run of $\syncof \pa {\pa'}$ the corresponding runs of $\pa$ and of $\pa'$:
 $$ \Psi_{\#} \defeq 
@@
 Notice that $x,x'$ are either variables or $\epsilon$.
-%\begin{enumerate}
-%	\item for all $v \in \cvarone$, $\#(v) = \sum_{v' \in \cvartwo} \#{(v,v')}$  
-%	\item for all $v \in \cvartwo$, $\#(v) = \sum_{v' \in \cvarone} \#{(v',v)}$ 
-%\end{enumerate}
-Finally, the third part forces the interpretations of the parametric words accepted by $A$ and $A'$ to be the same:
-% condition 1.
-and 2.
-required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
+Finally, the third part forces the interpretations of the parametric words accepted by $\pa$ and $\pa'$ to be the same:
 $$ \Psi_= \defeq
@@
 $$
-%\begin{enumerate}
-%	\item for all $v\in \cvarone$ and $v'\in \cvartwo$, $\#{(v,v')}>0 \rightarrow (v=v')$, 
-%	\item for all $v\in \cvarone$, $\#{(v,\epsilon)}>0 \rightarrow (v=\epsilon)$, and
-%	\item for all $v\in \cvartwo$,$\#{(\epsilon,v')}>0 \rightarrow (v'=\epsilon)$.
-%\end{enumerate}
 The synchronization formula is then the conjunction 
 $$
-%\syncfof A {A'} = \exists \pvarsof{\cvarone\times\cvartwo}\exists {(\cvarone\times\cvartwo)}.\,\parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
-\syncfof A {A'} \defeq \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
+\syncfof \pa {\pa'} \defeq \parikhfof{\syncof \pa {\pa'}} \land \Psi_{\#} \land \Psi_=
 $$
@@
 The correctness of this construction is stated in Lemma~\ref{lemma:synccorrect} below. 
-The lemma can also be understood as a precise specification of the semantics of the synchronization formula, on which we rely for correctness of the construction of under-approximations of string constraints in Sections~\ref{section:mem}, \ref{section:eq}, and \ref{section:s2i}.
-%
-%\begin{lemma}\label{lemma:synccorrect}
-%$
-%\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = 
-%\{
-%(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
-%x\in L(A), x'\in L(A'), I(x) = I(x')
-%\}
-%$
-%\end{lemma}
-
-%\begin{lemma}\label{lemma:synccorrect}
-%$
-%\semof {\syncfof A {A'}} \iequiv
-%\{
-%(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
-%x\in L(A), x'\in L(A'), I(x) = I(x')
-%\}
-%$
-%\end{lemma}
+The correctness of the construction of under-approximations of equality constraints and regular constarints in Sections~\ref{section:mem}, \ref{section:eq} rely on it. 
+%
 
 \begin{lemma}\label{lemma:synccorrect}
-%$
-%\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} = 
-%\{
-%(I\cup\parikhof{x})\cup(I'\cup\parikhof{x'}) \mid 
-%x\in L(A), x'\in L(A'), I(x) = I(x')
-%$
-%$
-%\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-%%\semof {\syncfof A {A'}} \iequiv
-%\{(I\cup I_\#)\cup (I' \cup I'_\#)\mid (I\cup I_\#) \in \encode A (w), (I' \cup I'_\#)\in\encode {A'} (w),w\in\semof A \cap \semof {A'}\} 
-%$
 $
-\semof {\syncfof A {A'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e\cup e'\mid e \in \encode A (w),\\ e'\in\encode {A'} (w), w\in\semof A \cap \semof {A'}\} 
+\semof {\syncfof \pa {\pa'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+\{e\cup e'\mid e \in \encode \pa (w),\\ e'\in\encode {\pa'} (w), w\in\semof \pa \cap \semof {\pa'}\} 
 $
 \end{lemma}
-%\lh{the lemma is actually true even for two non-flat automata. Notice that in that case, the set of encodings does not correspond to the intersection precisely}
-
-Informally, the lemma states that the models of $\syncfof A {A'}$ encode precisely the pairs of equivalent encodings of words from $\semof{A}$ and $\semof{A'}$, that constitute the intersection $\semof{A} \cap \semof{A'}$.
-A minor technical difficulty is that the models of $\syncfof A {A'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$.
-Hence in the lemma,
-we use restric the semantics of $\syncfof A {A'}$ to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
+
+Informally, the lemma states that the models of $\syncfof \pa {\pa'}$ encode precisely the pairs of equivalent encodings of words from $\semof{\pa}$ and $\semof{\pa'}$, that constitute the intersection $\semof{\pa} \cap \semof{\pa'}$.
+Since that the models of $\syncfof \pa {\pa'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$, the statement of the lemma,
+restrics the semantics of $\syncfof \pa {\pa'}$ to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
 %This is  achieve by quantifying out the variables of $V_\times$.
 
-Notice that if $A$ is flat (or, symmetrically, if $A'$ is flat), then the semantic intersection $\semof A \cap \semof {A'}$ can be still decoded from the synchronisation formula $\semof {\syncfof A {A'}}$.
-Namely, due to Corollary~\ref{corollary:pfa}, we have that 
+Notice that if $\pa$ is flat (or, symmetrically, if $\pa'$ is flat), then the semantic intersection $\semof \pa \cap \semof {\pa'}$ can be still decoded from the synchronisation formula $\semof {\syncfof \pa {\pa'}}$.
+Namely, due to Corollary~\ref{corollary:pfa}, we have that if $\pa$ is a PFA, then
 %$\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.  
-$$\semof A \cap \semof {A'} = \decode A (\semof{\syncfof A {A'}}_{\cvarone\cup \pvarone})$$
+$$\decode \pa (\semof{\syncfof \pa {\pa'}}_{\cvarone\cup \pvarone}) = \semof \pa \cap \semof {\pa'}$$
 
 \paragraph{Concatenation of PFAs}
-Concatenation is another operation over PFAs needed when constructing underapproximations.
+Concatenation of PFAs will be needed when flattening equality constraints.
 Its implementation is straightforward, connect the final state of the first PFA with the initial state of the second by an $\epsilon$-transition.
@@
 
-Formally, given PFA $A = (Q,T,\cvarone,q_i,q_f,\pfaf)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f',\pfaf')$ with $Q\cap Q'=\emptyset = \cvarone\cap\cvartwo$, 
-their concatenation is the PFA $A\cdot A' = (Q\cup Q',T\cup T'\cup \{(q_f,v_\epsilon,q_i')\},\cvarone\cup\cvartwo\cup\{v_\epsilon\},q_i,q_f',\pfaf\land\pfaf'\land v_\epsilon = \epsilon)$ where $v_\epsilon$ is fresh, not from $\cvarone\cup\cvartwo$.
+Formally, given PFA $\pa = ((Q,T,\cvarone,q_i,q_f),\paf)$ and ${\pa'} = ((Q',T',\cvartwo,q_i',q_f'),\paf')$ with $Q\cap Q'=\emptyset = \cvarone\cap\cvartwo$, 
+their concatenation is the PFA $\pa\cdot \pa' = (Q\cup Q',T\cup T'\cup \{(q_f,v_\epsilon,q_i')\},\cvarone\cup\cvartwo\cup\{v_\epsilon\},q_i,q_f',\paf\land\paf'\land v_\epsilon = \epsilon)$ where $v_\epsilon$ is fresh, not from $\cvarone\cup\cvartwo$.
 
 \begin{lemma}
-For PFA $A$ and $A'$, 
-%$\encode{A\cdot A'}{\semof{A\cdot A}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-%\{(I\cup I_\#)\cup (I' \cup I'_\#)\mid$ $\\(I\cup I_\#) \in \encode A (w), (I' \cup I'_\#)\in\encode {A'} (w'),w\in\semof A,w'\in \semof {A'}\}$
-$\semof{A\cdot A'} = \semof{A}\cdot\semof{A'}$ and 
-%\begin{multline*}
-$\encode{A\cdot A'}{\semof{A\cdot A}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e \cup e'\mid e \in \encode A (\semof{A}),\\ e' \in\encode {A'} (\semof{A'})\}$.
-%\end{multline*}
+For PFA $\pa$ and $\pa'$,  
+$\semof{\pa\cdot \pa'} = \semof{\pa}\cdot\semof{\pa'}$ and 
+$\encode{\pa\cdot \pa'}{\semof{\pa\cdot \pa}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+\{e \cup e'\mid e \in \encode \pa (\semof{\pa}),\\ e' \in\encode {\pa'} (\semof{\pa'})\}$.
 \end{lemma}
-\lh{lemma ugly, unnecesarily complicated. Just remove this lemma?}
-The second part of the lemma states that each pair of encodings is projected to an encoding of a concatenation.
-It is important for the correctness of underapproximation construction in the next section (the first part does suffice).
-
-We are now ready to describe flattening of the basic string constraints.
-
-%We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?
-%\begin{lemma}
-%For $\pim:\pvarone\rightarrow \nat$, $\pim':\pvartwo \rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
-%we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof {\syncfof A {A'}}$ if and only if $\decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')$.
-%\end{lemma}
+
+With syncrhonisation and concatenation of PA, we are ready to describe flattening of the basic string constraints.
 
@@
 Let us first describe the construction of $\underf R {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
-%Assume that $A=(Q,T,\Sigma,q_i,q_f)$. 
-We represent the FA $A$ by a pair of a PA $A'$ and linear formula $\Psi_{\mathit{char}}$. 
-The PA $A'$ operates over fresh character variables $v_a, a\in\Sigma_\epsilon$, and is obtained from $A$ by replacing every occurrence of each character $a\in\Sigma_{\epsilon}$ on a transition by the variable $v_a$.
-The formula $\Psi_{\mathit{char}}$ then binds the fresh character variables to the character values they represent, 
-namely, $\Psi_{\mathit{char}} = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$.
-%The resulting under-approximation of $\Psi_r$ is then the formula $\syncfof{A_x} {A'} \land \Psi_{char}$, which will be added to $\Phi_O$.
-Then 
-$$\underf R {\phi_r} = \syncfof{A_x} {A'} \land \Psi_{\mathit{char}}$$ 
-%, which will be added to $\Phi_O$.
-
-The following lemma states the correctness of this construction, and it follows from Corollary~\ref{corollary:pfa}, Lemma~\ref{lemma:synccorrect}. 
-%Intuitively, it says that the resulting constraint represents precisely the restriction of $L(A)$ to the domain $\semof{A_x}$, the $A_x$-encodings of the strings in $L(A)\cap\semof{A_x}$. 
+In order to synchronise the FA $A$ with the PFA $R(x)$, 
+we represent $A$ by a PA $\pa' = (A',\Psi_{\mathit{char}})$.
+The automaton $A'$ of $\pa'$ operates over fresh character variables $v_a, a\in\Sigma_\epsilon$, 
+and is obtained from $A$ by replacing every occurrence of each character $a\in\Sigma_{\epsilon}$ on a transition by the variable $v_a$. 
+The interpretation restriction formula $\Psi_{\mathit{char}}$ of $\pa'$ then binds the fresh character variables to the character values they represent, 
+namely, $\Psi_{\mathit{char}} = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$. Obviously, $L(A) = \semof{\pa'}$. 
+We then let 
+$$\underf R {\phi_r} = \syncfof{R(x)} {\pa'}$$
+
+The following lemma states the correctness of this construction. 
+It follows from Corollary~\ref{corollary:pfa} and Lemma~\ref{lemma:synccorrect}. 
 \begin{lemma}\label{lemma:memcorrect}  $\semof {\underf R {\phi_r}}_{V_R \cup V_{\#R}} = \encode {R} (\semof{\phi_r})$ . 
@@
 
-%
-%\begin{lemma}\label{lemma:memcorrect} ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
-%\end{lemma}
-%
-%(An alternative description)
-%\begin{lemma}\label{lemma:memcorrect} For all $w\in \semof{A_x}$, %$(I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ such that $w =\decode {A_x}(I\cup\pim)$ if and only if $w \in L(A)$.
-%%	$$\exists (I\cup\pim) \in {\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}. w =\decode {A_x}(I\cup\pim)$$
-%	\begin{center}
-%	$\exists (I\cup\pim)$ in ${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}}$ s.t. $w =\decode {A_x}(I\cup\pim)$\\
-%		iff\\
-%		$w \in L(A)$.
-%	\end{center}
-%%	${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \{(I\cup\pim) \mid \decode {A_x}(I\cup\pim) \in L(A)\}$. 
-%\end{lemma}
-%
-%\lh{
-%\begin{lemma}
-%${\semof {\syncfof {A_x }{A'} \land \Psi_{char}} } _{V_x \cup \pvarsof{V_x}} = \encode {A_x}(L(A))$
-%\end{lemma}
-%}
+\begin{figure*}
+	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+
+	\begin{minipage}[t]{0.15\textwidth} 
+		\begin{tikzpicture}
+		\node[state,initial,accepting] (q0)  {$q_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_0$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
+		\end{tikzpicture}
+
+		\centering
+		(a) $A_x$
+	\end{minipage}
+	\begin{minipage}[t]{0.15\textwidth} 
+		\begin{tikzpicture} 
+		\node[state,initial,accepting] (q0)  {$p_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$p_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_2$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_3$} (q0) ;
+		\end{tikzpicture}
+
+		\centering
+		(b) $A_y$
+	\end{minipage}
+	\begin{minipage}[t]{0.28\textwidth}
+		\begin{tikzpicture} 
+		\node[state,initial] (q0)  {$q_0$};
+		\node[state,accepting] (q1) [right = 1.3cm of q0] {$p_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(0)}$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(0)}$} (q0) ;
+
+		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
+
+		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(0)}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
+		\draw[->] (q0) edge  node [below]{$v_{\epsilon_0}$} (q1) ;
+		\end{tikzpicture}
+
+		\centering
+		(c) $A_{xy}$
+	\end{minipage}
+	\ \ \ 
+	\begin{minipage}[t]{0.28\textwidth}
+		\begin{tikzpicture} 
+		\node[state,accepting] (q0)  {$q_0$};
+		\node[state,initial] (q1) [left = 1.3cm of q0] {$p_0$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
+
+		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(1)}$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(1)}$} (q0) ;
+
+		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
+
+		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(1)}$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
+		\draw[->] (q1) edge  node [below]{$v_{\epsilon_1}$ }(q0) ;
+		\end{tikzpicture}
+
+		\centering
+		(d) $A_{yx}$
+	\end{minipage}
+
+	\caption{Parametric flat automata of $x$, $y$, $xy$ and $yx$}
+	\label{fig:sfa}
+\end{figure*}
 
@@
 %
-To simplify the construction, we assume that the varriables are pairwise different, i.e.
+To simplify the presentation, we assume that the varriables are pairwise different, i.e.
 that $i\neq j \implies x_i \neq x_j$.
-We may make this assumption without loss of generality, since whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoing the modified $\phi_e$ with a new equality $x_j = x_j'$.
-%
-
-We first build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side term of the equality constraint, respectively, by concatenating the restrictions of the individual variables.
+We may make this assumption without loss of generality, since multiple occurences of variables in $\phi_e$ can be eliminated: whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoin the modified $\phi_e$ with a new equality $x_j = x_j'$.
+%
+We also that all disequality constraint $t \neq t'$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
+%
+
+Having made these assumptions, we may proceed follows.
+First, we build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side term of the equality constraint $\phi_e$, respectively, by concatenating the restrictions of the individual variables.
 That is
@@
 
-\subsection{Handling the lengths of variables}
-After the set $\insc$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
-To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
-
-$$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
-
-More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\outlf$.
-
-$$\Phi_{|x|} \defeq \Phi_{V_x} \wedge |x| = \sum_{v\in V_x} s_v $$
+\subsection{Encoding Length Constraints}
+Length constraints are not underapproximated by flattenting. 
+Given a length constraint $\phi_l$ with string lenght variables $X$,
+we keep $\phi_l$ as is and add a formula to express the lenghts of strings $|x|$ in terms of character variables $V_x$ and Parikh variables $\# V_x$ of $R(x)$.
+
+For every length variable $|x|\in X$, 
+we add a set of fresh auxiliary variables $\{|v|\mid v\in V_x\}$ to express the length by which $v$ contributes to the lenght of an $R$-encoded word. 
+That is, $|v|$ will be $0$ if $v$ is assigned $\noepsilon$,
+otherwise it will equal the number $\#v$ of its occurrences in the word:
+$$
+\Psi_{\mathsf{|v|}} \defeq (v = \noepsilon \land |v|=0) \lor (v \neq \noepsilon \land |v| = \# v)
+$$
+The lenght of the encoded word $x$ is then the sum of the lenghts contributed by the individual character variables in $V_x$, 
+hence we let 
+$$
+\Psi_{|x|} \defeq |x| = \sum_{v\in V_x} |v| \land  \bigwedge_{v\in V_x} \Psi_{\mathsf{|v|}}\ .
+$$
+Finally, the linear formula created for $\phi_l$ is 
+$$
+\underf R {\phi_{l}} \defeq \phi_l \land \bigwedge_{|x|\in X} \Psi_{|x|}
+$$
+\lh{a correctness lemma would be good here, but it needs some modification of encoding probably, to be done}
 
@@
 
-%\subsection{Handling Equality Constraints Symbolically, old verion, not updated} \label{section:eq}
+%% After the set $\insc$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
+To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
+%% 
+%% $$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
+%% 
+%% 
+%% More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\outlf$. 
+%% 
+%% $$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
+%% 
+%% 
+%% \hide{The length of $x$ can be specified by the following formula.
+%% 
+%% $\begin{array}{ccc}
+%% 	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\vee \\
+%% 	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\vee \\
+%% 	& &\ldots\\
+%% 	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\vee\\
+%% 	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
+%% \end{array}$}
+
 %\subsection{Handling Equality Constraints Symbolically, old verion, not updated} \label{section:eq}
@@
 
-Last, we decribe the construction of $\underf R {\phi_s}$ for a string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
-%In this section, we how to make the corresponding linear formulas for $\Phi_O$.
-
-We begin the discussion with a simple example, assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
+Last, we present a central part of this paper, the construction of $\underf R {\phi_s}$ for a string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
+
+Let us begin with a simple example.
+Assume that we use the PFA in Figure~\ref{fig:sfa} (a) to restrict the domain of $x$.
 Then we know that when $0\leq v_0,v_1 \leq 9$, then $n$ is a positive integer value, and otherwise $n =-1$.
@@
 For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)}-1}{100-1}$.
-The constraint uses $\#(v_0)$ to capture the total number of loop traversal.
+The constraint uses $\#(v_0)$ to capture the total number of loop traversals.
 Notice that the constraint above contains an exponential component $\frac{100^{\#(v_0)}}{100-1}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
@@
 
-It is not difficult to observe that, for the case of an arbitrary PFA of $m$ loops, the formula to define $n$ contains $m$ exponential components, one for each loop.
+It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula to defines the number $n$ contains $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
 As said in the introduction, the problem is difficult even for the case that variables are real numbers.
-For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure, which is double-exponential to the length of the input formula and hence cannot handle large instances.
-So we do not expect that this constraint can be solved efficiently.
-
-\paragraph{PFA that allows efficient string-number conversion: } Now we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
+For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure which is double-exponential to the length of the input formula and hence cannot handle large instances.
+We therefore do not expect that such constraint can be solved efficiently.
+Instead, we will define a special form of the flat restriction $R(x)$ of $x$ that leads to an easies linear formula.
+
+\paragraph{PFA that allows efficient string-number conversion: } 
+%Now we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
 The cause of the problem is that each loop in the PFA creates an exponential component in the constraint.
-An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving.
-At the same time, we want to keep a good property, that is, the search space covers all integers up to $m$-digits.
+%An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving. 
+We will now discuss the special form of $R(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints that leads to efficient underapproximation.
+%
+Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
+We want an ``easy completeness'' property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satifiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+%
+Particularly, we will proceed towards a definition of \emph{number PFA} $(A^m,\paf^m),m\in\nat$ which covers all numerals that encode integers with $m$ digits.
 
@@
 Observe that $\sti{``00010"}=10$.
-The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many `$0$' characters at the front.
-In order to handle all numbers with up to $m$-digits, we propose to restrict the domain of $x$ to so called \emph{number PFA}, illustrated in Figure~\ref{fig:sfa_its}.
-The number PFA has a self-loop transition labeled $v_0$ at $q_0$ and we add a constraint $\Psi_{v_0}\defeq v_0=0$ to $\outlf$ for such PFA.
-With this transition, we can ensure that the under-approximation handles all numbers with at most $m$ digits.
-Although this PFA still has a loop, it will not create any exponential component because the loop only represents a sequence of ``0'' at the front of $x$.
+The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many trailing `$0$'s at the front.
+All numbers with up to $m$-digits can be however still handled without having to solve exponential constraints.
+It is enough to equip the initial state of the PFA with a  $0$-self-loop.
+
+Consequently, the automaton $A^m$ of our number PFA will have the following form illustrated in Figure~\ref{fig:sfa_its}. 
+It has a self-loop on the initial state labeled by the character variable $v_0$, 
+forced by the constraint 
+$$
+\Psi_{v_0}\defeq v_0=0
+$$ 
+to hold the value $0$. 
+This transition ensures that the under-approximation handles all numerals with arbitrary number of trailing zeros.  
+The self-loop is followed by a chain of $m$ transitions $(q_{i-1},v_i,q_{i}),1\leq i \leq m$, leading towards the final state $q_m$.
+The chain encodes at most $m$ meaningful digits (only \emph{at most} because the first variables in the sequence can still be assigned zeros and some variables may be assigned $\epsilon$).
+Hence this PFA covers all numerals that encode numbers with at most $m$ digits.
+Although it still has a loop, it will not create any exponential component defining the value of $n$ because the loop only represents a sequence of ``0'' at the front of $x$.
 It will not affect the integer value of $n=\sti{x}$.
@@
 
-Such PFA handles bounded integers (e.g., 10-digits or 64-bits) precisely and under-approximate the possible values of unbounded integers.
+%Such PFA handles bounded integers (e.g., 10-digits or 64-bits) precisely and under-approximate the possible values of unbounded integers.
 It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
-Remember that the character variables can be assigned $\epsilon$.
-In order to simplify the construction, we use an encoding to shift all the $\epsilon$-transitions to the least significant digits, i.e., if $v_j = \epsilon = -1$ then $v_k = -1$ for all $k\in [j+1,m]$.
-
-Consequently, for string variables that appear within string-to-int constraints, such as $x$ within $\phi_s$, we approximate $x$ by a special PFA, 
-called \emph{$m$-digit PFA}. They are of the form $R(x) = (Q,T,\cvarone,q_i,q_f,\pfaf)$ where the automaton is as on Figure~\ref{fig:sfa_its} and the interpretation restriction is the formula
-$$
-\pfaf \defeq \Psi_{\mathsf{NaN}} \lor \Psi_{\mathsf{Number}}
-$$
-where $\Psi_{\mathsf{NaN}}$ captures the case when $x$ is ``not a number'': 
-$$
-\Psi_{\mathsf{NaN}} \defeq \bigvee_{i\in [1,m]} v_i>9
-$$ 
-and $\Psi_{\mathsf{Number}}$ caputures the case when $x$ is a valied encoding of a number.
-$\Psi_{\mathsf{Number}}$ aslo forces $R(x)$ to encode the number in a particular way, namely, the intial self-loop may only generate trailing zeros and %variables that are assigned $\epsilon$ can only be used at the end of the number:
-the first $k$ variables are some numbers and those after $k$ are assigned $\epsilon$. 
-%Recall that we use $-1$ to represent $\epsilon$.
-The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
-\yfc{say shifting $\epsilon$ to the right will not change the language}
-
-$$
-\Psi_{\mathsf{Number}}:= v_0 = 0 \land \bigwedge_{1\leq i \leq m} v_i \neq -1 \implies v_{i-1}\neq -1.
-$$
-
-With the domain restriction for $x$ in the above form,
-we define the underapproximation of $\phi_s$ as
+Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would easily and completely cover all numerals.
+%
+A last problem still needs to be solved beofe they can be efficient in practice. 
+%
+Recall that the character variables can be assigned $\epsilon$.  
+%
+Therefore, a single chain of $k$ interesting digits, $k\leq m$, can be by $A^m$ represented in $k\choose m$ ways, each corresponding to one possible interleaving of $k$ digits with $m-k$ epsilons. 
+%
+\lh{I am not sure whether it is really impossible to make a smlall formula}
+%
+This would lead to an exponentail expolostion of the size of the linear formula definig the value of $n$.
+%
+In order to eliminate this blow-up in the size of the formula, we add to $\paf^m$ an additional constraint that forces all epsilons to be \emph{shifted} behind the least significant digit, effectively prohibiting all interleavings but one.
+This is the formula
+$$
+\Psi_{\mathsf{shift}}^m \defeq \bigwedge_{1\leq i \leq m} v_i \neq \noepsilon \implies v_{i-1}\neq \noepsilon \ .
+$$
+Last, since this restriction is meanigfull only when the string is indeed numeral,  
+we also define the constraint representing the strings which are not numerals, the formula
+$$
+\Psi_{\mathsf{NaN}}^m \defeq  \bigvee_{i\in [1,m]} v_i>9
+$$ 
+and define the final form of the interpretation restriction used by $A^m$ as 
+$$
+\paf^m \defeq  \Psi_{\mathsf{NaN}}^m \lor (\Psi_{v_0} \land \Psi_{\mathsf{shift}}^m)\ .
+$$
+Consequently, we design our domain restrictions $R$ so that for string variables $x$ that appear within string-integer constraints,  $R(x)$ is a number PFA $(A^m,\paf^m),m\in \nat$.
+
+Assuming that the domain restriction for $x$ is $(A^m,\paf^m)$, 
+the value of the integer $n$ can be extracted from a numeral using the formula
+$$
+\Psi_{\mathsf{toInt}}^m\defeq \bigvee_{1\leq k \leq m} \Psi_{\mathsf{last(k)}}^m \land (n = v_1* 10^{k-1} + v_2* 10^{k-2} + \ldots + v_{k})
+$$
+where $\Psi_{\mathsf{last(k)}}^m$ says that the last variable of $A^m$ assigned a non-$\epsilon$ value is $v_{k}$, namely 
+$$
+\Psi_{\mathsf{last(k)}}^m \defeq (k = m \land v_k \geq 0) \lor (v_{k} \geq 0 \land v_{k+1} = -1)\ .
+$$
+Since we also need to distinguish the case when $x$ is not a number, in which case $n$ should equal $-1$, 
+the formula underapproximating $\phi_s$ is finally constructed as  
 \begin{multline*}
-\underf R {\psi_s} 
+\underf R {\phi_s} 
 \defeq 
-\parikhfof{R(x)} 
+\parikhfof{A^m} 
 \land \\
-\bigl((\Psi_{\mathsf{NaN}} \land n = -1) 
+\bigl((\Psi_{\mathsf{NaN}}^m \land n = -1) 
 \lor 
-(\neg\Psi_{\mathsf{NaN}} \land \Psi_{\mathsf{toNumber}})\bigr)
+(\neg\Psi_{\mathsf{NaN}}^m \land \Psi_{\mathsf{toInt}}^m)\bigr)
 \end{multline*}
-where $\Psi_{\mathsf{toNumber}}$ si the actual conversion of the string to an integer.
-$$
-\Psi_{\mathsf{toNumber}}\defeq \bigvee_{1\leq k \leq m} \Psi_{\mathsf{last(k)}} \land (n = v_1* 10^{k-1} + v_2* 10^{k-2} + \ldots + v_{k})
-$$
-The function $\Psi_{\mathsf{last(k)}}$ is used above to detect the last variable $v_k$ that encodes a digit (all the variables with a higher index encode $\epsilon$):
-$$
-\Psi_{\mathsf{last(k)}} \defeq (k = m \land v_k \geq 0) \lor (v_{k} \geq 0 \land v_{k+1} = -1)
-$$
-
-Let $I$ be an interpretation of string variables and $I'$ an interpetation of integer variables. We define $\encode R {(I\cup I')}$ as $\{e \cup I' \mid e\in \encode R(I)\}$. 
-The bloody bastard correctness lemma now says that 
+The following lemma states correctness of this construction:
 \begin{lemma}
 $
-\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode R(\semof{\phi_s})
+\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R'(\semof{\phi_s})
 $
 \end{lemma}
+The lemma uses the encoding function generalised to assignments of string \emph{and integer} variables. 
+It is defined so that, for an interpretation $I$ of string variables $X$ and an interpetation $I'$ of integer variables $N$, $X\cap N = \emptyset$, 
+$\encode R' {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$, which is then lifted to sets in the standard manner.
 
@@
 
-\section{Implementation}\label{section:implementation}
 \input{evaluation}

### 2019-11-20 draft.tex
edits

--- 2019-11-19 draft.tex
@@
 Here \texttt{x[3]} in line 2, \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
-So na\"ive modeling array index with integers will not work -- it cannot distinguish the indexes \texttt{"3"} and \texttt{"03"}.
+So na\"ive modeling of array indices with integers will not work -- it cannot distinguish the indices \texttt{"3"} and \texttt{"03"}.
 
@@
 
-Solving string constraint with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and, in practice, in our experiments (Section \ref{section:evaluation}), the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+Solving string constraint with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and our experiments (Section \ref{section:evaluation}) show that state-of-the-art string constraint solvers provide only limited support to string-number conversion.
 
@@
 The over-approximation is for proving UNSAT when possible, while the under-approximation is for proving SAT when possible.
-Both over and under-approximation fall in a decidable fragment of string constraints that can we can efficiently solve.
+Both over- and under-approximation fall in a decidable fragment of string constraints that can we can efficiently solve.
 
@@
 
-to explain the main ideas behind our decision procedure. Notice that $\Phi$ is satisfiable. E.g., it has a model $x=``12''$ and $y=``1212''$.
-
-Our decision procedure has two steps: the first step is over-approximating the set of input constraints into a one that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
-Observe that we can also over-approximate the input constraint to one that falls in the decidable fragment the acyclic fragment~\cite{abdulla2014string} or the straight-line fragment~\cite{chen2019decision}.
+to explain the main ideas behind our decision procedure.
+To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is a string of 1's and 2's.
+Notice that $\Phi$ is satisfiable.
+E.g., it has a model $x=``12''$ and $y=``1212''$.
+
+Our decision procedure has two steps: the first step is over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+Observe that we could  over-approximate the input constraint into any decidable fragment, e.g.
+the acyclic fragment~\cite{abdulla2014string} or the straight-line fragment~\cite{chen2019decision}.
 Our choice of the  chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
-In our settings, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
 The over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some other cases, we can derive the value of $n=12$ from some integer constraints.
-In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
-Observe that if the over-approximated module returns UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
+For instance, assume in some case, we could derive the value of $n=12$ from some integer constraints.
+Then we could further derive the value of $x$ is in the regular language $(0^*12)$.
+Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
 Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
@@
 
-The second step of our decision procedure is only enabled if the first step returns SAT.
-In this case, our decision procedure restricts the domain of each string variables to strings that obey some predefined and parameterized pattern.
-By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
+The second step of our decision procedure is only enabled if the over-approximation is SAT.
+In this case, our decision procedure restricts the domain of each string variable to strings that obey some predefined and parameterized pattern.
+Adjusting the parameters enlarges or prunes the potential solution space.
 In this paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA).
-A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops each of fixed length (see Figure \ref{fig:sfa_def}).
+A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
 The approach based on PFA is very flexible yet allows very efficient manipulation.
@@
 Furthermore, we associate a unique natural number with each character.
-This allows us to assume that the input alphabet is a subset of natural numbers.
-To avoids the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers, we label each transition between two states of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
-Such reduction based on PFA is the key to handle string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulas that can be solved efficiently.
+This allows us to assume that the input alphabet is a subset of natural numbers to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers.
+We label each transition between two states of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
+Such reduction based on PFA is the key to handling string-number conversion efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulae and can be solved efficiently.
 
@@
 
-In the following, we explain the construction of the linear formula using the formula $\Phi$ as an example.
+In the following, we explain the construction of the linear formula using $\Phi$ as an example.
 Assume that we project the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
@@
 
-The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$, as well as the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$, as well as the number of occurrences of each character variable $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
 Each model of the linear formula encodes a model of the string constraint.
@@
 If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure step-wisely change the PFA to more expressive ones (by adding more states and transitions) to systematically search for the solution.
+If not, our procedure changes the PFA instages to be more expressive (by adding more states and transitions) to systematically search for the solution.
 Depending on the implementation, one may choose to report unknown after some certain steps.

### 2019-11-20 evaluation.tex
Update evaluation.tex
update evaluation and minor update to intro

@@
 
-\begin{table*}[t]
+\begin{table}[h]
 \centering
-\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
-\begin{tabular}{l r | r r r r r r r}
+\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
+\scalebox{0.7}{
+\begin{tabular}{|l r | r r r r r r r|}
 \hline
-\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
@@
 							& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\ \hline
-\end{tabular}
+							\hline
+\multirow{3}{*}{Total}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
+& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
+& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\\hline
+\end{tabular}}
 \label{table:base_benchmark}
-\end{table*}
+\end{table}
 
+\begin{table}[h]
+\centering
+\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark (numbers with * will be updated later)}
+\scalebox{0.8}{
+\begin{tabular}{|l r | r r r r|}
+\hline
+\multicolumn{2}{|c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
+\multirow{3}{*}{String-Number-Leetcode}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
+							& unsat    &  17088*  & 16377* & 16832* &  16034* \\
+							& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline 
+\multirow{3}{*}{String-Number-PythonLib}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
+& unsat    &  17088*  & 16377* & 16832* &  16034* \\
+& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline
+\multirow{3}{*}{String-Number-JavaScript}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
+& unsat    &  17088*  & 16377* & 16832* &  16034* \\
+& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline 							
+							\hline
+\multirow{3}{*}{Total}	& sat & 622*  &  330* &  100* &  85* \\ 
+& unsat    &  1054*  & 780* & 1043* &  634* \\
+& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
+\end{tabular}}
+\label{table:str_int_benchmark}
+\end{table}
+
+\hide{%3rd version
 \begin{table}[t]
@@
 			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{StrInt}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
+			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
 			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
 			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline
+
 				\multirow{3}{*}{leetcode-addStrings}	& sat & 622*  &  330* &  100* &  85* \\ 
@@
 				% 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
-\end{tabular}}
+			}
+		\end{tabular}
 		\label{table:str_int_benchmark}
 	\end{table}
+}
 
@@
 
-Our tool {\tool} is done by implementing the proposed string constraint solving procedure on top of the SMT solver Z3~\cite{z3} as a theory solver.
+We have implemented our string constraint solving procedure, in a tool called {\tool}, on top of the SMT solver Z3~\cite{z3} as a theory solver.
 In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
@@
 	\item StringFuzz~\cite{StringFuzz}  is generated from the fuzz testing tool of the same name.
-	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}. This benchmark also contains some string-number conversion constraints.
+	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}.
+These benchmarks contain a small amount of string-number conversion constraints (< $5\%$).
 \end{itemize}
@@
 We run it on several examples collected from the LeetCode platform and from Python core libraries.
+We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).
 
@@
 From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
-The number of failed cases is only a half to Z3, which is ranked the 2nd.
-In fact, most of the failed tests comes from the analysis of {lib-ipaddress\_ip\_int\_from\_string}, which converts an IPv6 address to a number.
-This function has a very long execution path and hence the size of each SMT file from this analysis is roughly 1MB.
-If we exclude results on this benchmark, then {\tool} has only $185$ failed case.
-This is significantly better than the 2nd place tool Z3, which fails $893$ cases.
+The total number of failed cases is only a half to Z3, which is ranked the 2nd.
+In fact, most of the failed tests comes from the analysis of one Python core library function that converts an IPv6 address to a number.
+We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
+If we exclude results on this function, then {\tool} has only $185$ failed case in total.
+This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total.
 

### 2019-11-20 draft.tex
update evaluation and minor update to intro
add experimental results to introduction

@@
 JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with Node.js---and it has conversions between strings and integers embedded in the core of its semantics.
-
+\smallskip
+\begin{center}
+	\begin{minipage}{5cm}
 		\begin{verbatim}
@@
 		\end{verbatim}
+	\end{minipage}
+\end{center}
+\smallskip
 
@@
 
+\medskip
 \hspace{-4mm}\begin{tabular}{l|l|c}
@@
 \end{tabular}
+\medskip
 
@@
 In this paper, we propose a framework that efficiently handles string constraints with string-number conversion.
-Due to the diffifulty of solving the problem exactly, our framework combines over and under-approximation of string constraints.
+Due to the difficulty of solving the problem exactly, our framework combines over and under-approximation of string constraints.
 The over-approximation is for proving UNSAT when possible, while the under-approximation is for proving SAT when possible.
@@
 Our choice of the  chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
-In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
 The over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
@@
 Such reduction based on PFA is the key to handling string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulae and can be solved efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulas and can be solved efficiently.
 
@@
 If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure changes the PFA instages to be more expressive (by adding more states and transitions) to systematically search for the solution.
+If not, our procedure changes the PFAs to be more expressive ones (by adding more states and transitions) to systematically search for a solution.
 Depending on the implementation, one may choose to report unknown after some certain steps.
@@
 
-To demonstrate the usefulness of our approach, we have implemented our decision procedure in an open source solver, called {\sc } ....
+To demonstrate the usefulness of our approach, we have implemented our decision procedure in an open source solver, called {\tool} and evaluated it on a large set of benchmarks obtained from literatures and from symbolic execution of real world programs.
+The experimental results show that {\tool} is among the best tools for solving basic string constraints and significantly outperforms all other tools on benchmarks with string-number conversion constraints.
+In this benchmark, the total amount of tests cannot be solved by {\tool} is only a half to the second best tool.
+
 \todo{Talk about experiments}

### 2019-11-20 draft.tex
resize figures and fix the corresponding text

@@
     for(var i = 0; i < 10; i++) {
-        arr[i] = 0
+        arr[i] = 0;
    }
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic array operation in Javascript, and so having only limited capability for handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
+This is a rather basic array operation in JavaScript, and so having only limited capability for handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
 
@@
 
-\begin{figure*}
+\begin{figure}
 	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
 			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+
+	\scalebox{0.7}{
 	\begin{tikzpicture} 
@@
 		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
-	\end{tikzpicture}
+	\end{tikzpicture} }
 
@@
 	\label{fig:sfa_def}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
 	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
@@
 
-	\begin{minipage}[t]{0.15\textwidth} 
+	\begin{minipage}[t]{0.1\textwidth} 
+			\scalebox{0.7}{
 		\begin{tikzpicture}
@@
 		\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
-		\end{tikzpicture}
+		\end{tikzpicture} }
 
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.15\textwidth} 
+	\begin{minipage}[t]{0.1\textwidth} 
+			\scalebox{0.7}{
 		\begin{tikzpicture} 
-		\node[state,initial,accepting] (q0) {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$p_1$};
+		\node[state,initial,accepting] (q0) {$q_2$};
+
+		\node[state] (q01) [above = 0.5cm of q0] {$q_3$};
 
@@
 		\draw[->] (q01) edge [bend left] node [right]{$v_3$} (q0) ;
-		\end{tikzpicture}
+		\end{tikzpicture} }
 
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.28\textwidth}
+	\begin{minipage}[t]{0.2\textwidth}
+			\scalebox{0.7}{
 		\begin{tikzpicture} 
 		\node[state,initial] (q0) {$q_0$};
-		\node[state,accepting] (q1) [right = 1.3cm of q0] {$p_0$};
+		\node[state,accepting] (q1) [right = 1.3cm of q0] {$q_2$};
 
@@
 
-		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(0)}$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(0)}$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(0)}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
-		\draw[->] (q0) edge node [below]{$v_{\epsilon_0}$} (q1) ;
-		\end{tikzpicture}
+		\draw[->] (q0) edge [bend left] node [left]{$v_0$} (q01) ;
+		\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
+
+		\node[state] (q11) [above = 0.5cm of q1] {$q_3$};
+
+		\draw[->] (q1) edge [bend left] node [left]{$v_3$} (q11) ;
+		\draw[->] (q11) edge [bend left] node [right]{$v_4$} (q1) ;
+		\draw[->] (q0) edge node [below]{$v_2$} (q1) ;
+		\end{tikzpicture}}
 
 		\centering
-		(c) $A_{xy}$
+		(c) $A'_{x}$
 	\end{minipage}
-	\ \ \ 
-	\begin{minipage}[t]{0.28\textwidth}
-		\begin{tikzpicture} 
-		\node[state,accepting] (q0) {$q_0$};
-		\node[state,initial] (q1) [left = 1.3cm of q0] {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(1)}$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(1)}$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(1)}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
-		\draw[->] (q1) edge node [below]{$v_{\epsilon_1}$ }(q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(d) $A_{yx}$
-	\end{minipage}
-
-	\caption{Parametric flat automata of $x$, $y$, $xy$ and $yx$}
+
+	\caption{Parametric flat automata of $x$ and $y$}
 	\label{fig:sfa}
-\end{figure*}
+\end{figure}
 
@@
 
-\todo{Talk about experiments}
-
 \smallskip
@@
 
-\begin{figure*}
-	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
-			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
-	\begin{tikzpicture} 
-		\node[state,initial] (q0)  {$\st{0}{0}$};
-		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
-		\node (q2) [right = 1.8cm of q1]{};
-		\node (q3) [right = 1cm of q2]{};
-		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
-
-		\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
-		\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
-		\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{3}$};
-
-		\node[state] (q11) [above left = 0.8cm of q1] {$\st{1}{1}$};
-		\node[state] (q12) [above right = 0.8cm of q1] {$\st{1}{2}$};
-
-		\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
-		\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
-		\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{3}$};
-
-  		\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
-  		\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
-  		\draw[->] (q02) edge [bend left] node [right]{$\sym{0}{2}$} (q03) ;
-  		\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{3}$} (q0) ;
-
-  		\draw[->] (q0) edge node [below]{$v_0$} (q1) ;
-  		\draw[->] (q1) edge node [below]{$v_1$} (q2) ;
-  		\draw[dotted] (q2) edge (q3) ;
-  		\draw[->] (q3) edge node [below]{$v_{m-1}$} (qm) ;
-
-  		\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
-		\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
-		\draw[->] (qm2) edge [bend left] node [right]{$\sym{m}{2}$} (qm3) ;
-		\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{3}$} (qm) ;
-
-  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
-		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
-	\end{tikzpicture}
-
-	\caption{An example of a parametric flat automaton}
-	\label{fig:sfa_def}
-\end{figure*}
-
 %A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a PFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
@@
 %
-The inductive argument needed in the proof of the correctness of the underapproximation then reads as
+The inductive argument needed in the proof of the correctness of the under-approximation then reads as
 $$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
 %
-In the nexr sections, 
-we will formulate the corresponding lemma for linear formulae constructed from each type of atomic string constraints.
+In the next sections, 
+we will formulate the corresponding lemma for linear formulas constructed from each type of atomic string constraints.
 %
@@
 \paragraph{Encoding epsilon.}
-A minor technical difficulty is that we wish to build underapproximation in the form of pure arithmetic formulas, 
+A minor technical difficulty is that we wish to build under-approximation in the form of pure arithmetic formulas, 
 but we may also wish to specify when a character variable is assigned $\epsilon$, but $\epsilon$ is not a number. 
@@
 \section{Flattening of Basic String Constraints}
-We will first discuss flattening of the basic string contraints, that is,
-regular, equality, and lenght constraints. We start by two needed operations over PA, synchronisation and concatenation.
+We will first discuss flattening of the basic string constraints, that is,
+regular, equality, and integer constraints. We start by two needed operations over PA, synchronization and concatenation.
 
@@
 The correctness of this construction is stated in Lemma~\ref{lemma:synccorrect} below. 
-The correctness of the construction of under-approximations of equality constraints and regular constarints in Sections~\ref{section:mem}, \ref{section:eq} rely on it. 
+The correctness of the construction of under-approximations of equality constraints and regular constraints in Sections~\ref{section:mem}, \ref{section:eq} rely on it. 
 %
@@
 
-Notice that if $\pa$ is flat (or, symmetrically, if $\pa'$ is flat), then the semantic intersection $\semof \pa \cap \semof {\pa'}$ can be still decoded from the synchronisation formula $\semof {\syncfof \pa {\pa'}}$.
+Notice that if $\pa$ is flat (or, symmetrically, if $\pa'$ is flat), then the semantic intersection $\semof \pa \cap \semof {\pa'}$ can be still decoded from the synchronization formula $\semof {\syncfof \pa {\pa'}}$.
 Namely, due to Corollary~\ref{corollary:pfa}, we have that if $\pa$ is a PFA, then
@@
 Since our automata do not allow transition directly labeled by $\epsilon$,
-the $\epsilon$-transition is labeled by a fresh variable $v_\epsilon$ contrained by the constraint $v_\epsilon = \epsilon$.
+the $\epsilon$-transition is labeled by a fresh variable $v_\epsilon$ restricted by the constraint $v_\epsilon = \epsilon$.
 
@@
 
-With syncrhonisation and concatenation of PA, we are ready to describe flattening of the basic string constraints.
+With synchronization and concatenation of PA, we are ready to describe flattening of the basic string constraints.
 
@@
 Let us first describe the construction of $\underf R {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
-In order to synchronise the FA $A$ with the PFA $R(x)$, 
+In order to synchronize the FA $A$ with the PFA $R(x)$, 
 we represent $A$ by a PA $\pa' = (A',\Psi_{\mathit{char}})$.
@@
 
-\begin{figure*}
-	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
-			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
-
-	\begin{minipage}[t]{0.15\textwidth} 
-		\begin{tikzpicture}
-		\node[state,initial,accepting] (q0)  {$q_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1$} (q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(a) $A_x$
-	\end{minipage}
-	\begin{minipage}[t]{0.15\textwidth} 
-		\begin{tikzpicture} 
-		\node[state,initial,accepting] (q0)  {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$p_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_2$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_3$} (q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(b) $A_y$
-	\end{minipage}
-	\begin{minipage}[t]{0.28\textwidth}
-		\begin{tikzpicture} 
-		\node[state,initial] (q0)  {$q_0$};
-		\node[state,accepting] (q1) [right = 1.3cm of q0] {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(0)}$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(0)}$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(0)}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(0)}$} (q1) ;
-		\draw[->] (q0) edge  node [below]{$v_{\epsilon_0}$} (q1) ;
-		\end{tikzpicture}
-
-		\centering
-		(c) $A_{xy}$
-	\end{minipage}
-	\ \ \ 
-	\begin{minipage}[t]{0.28\textwidth}
-		\begin{tikzpicture} 
-		\node[state,accepting] (q0)  {$q_0$};
-		\node[state,initial] (q1) [left = 1.3cm of q0] {$p_0$};
-
-		\node[state] (q01) [above = 0.5cm of q0] {$q_1$};
-
-		\draw[->] (q0) edge [bend left] node [left]{$v_0^{(1)}$} (q01) ;
-		\draw[->] (q01) edge [bend left] node [right]{$v_1^{(1)}$} (q0) ;
-
-		\node[state] (q11) [above = 0.5cm of q1] {$p_1$};
-
-		\draw[->] (q1) edge [bend left] node [left]{$v_2^{(1)}$} (q11) ;
-		\draw[->] (q11) edge [bend left] node [right]{$v_3^{(1)}$} (q1) ;
-		\draw[->] (q1) edge  node [below]{$v_{\epsilon_1}$ }(q0) ;
-		\end{tikzpicture}
-
-		\centering
-		(d) $A_{yx}$
-	\end{minipage}
-
-	\caption{Parametric flat automata of $x$, $y$, $xy$ and $yx$}
-	\label{fig:sfa}
-\end{figure*}
-
 \subsection{Flattening of Equality Constraints} \label{section:eq}
@@
 %
-To simplify the presentation, we assume that the varriables are pairwise different, i.e.
+To simplify the presentation, we assume that the variables are pairwise different, i.e.
 that $i\neq j \implies x_i \neq x_j$.
-We may make this assumption without loss of generality, since multiple occurences of variables in $\phi_e$ can be eliminated: whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoin the modified $\phi_e$ with a new equality $x_j = x_j'$.
+We may make this assumption without loss of generality, since multiple occurrences of variables in $\phi_e$ can be eliminated: whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoin the modified $\phi_e$ with a new equality $x_j = x_j'$.
 %
@@
 \end{eqnarray*}
-The underapproximation of $\phi_e$ is then obtained as their synchronisation formula
+The under-approximation of $\phi_e$ is then obtained as their synchronization formula
 $$
@@
 \subsection{Encoding Length Constraints}
-Length constraints are not underapproximated by flattenting. 
-Given a length constraint $\phi_l$ with string lenght variables $X$,
-we keep $\phi_l$ as is and add a formula to express the lenghts of strings $|x|$ in terms of character variables $V_x$ and Parikh variables $\# V_x$ of $R(x)$.
+Length constraints are not under-approximated by flattening. 
+Given a length constraint $\phi_l$ with string length variables $X$,
+we keep $\phi_l$ as is and add a formula to express the lengths of strings $|x|$ in terms of character variables $V_x$ and Parikh variables $\# V_x$ of $R(x)$.
 
 For every length variable $|x|\in X$, 
-we add a set of fresh auxiliary variables $\{|v|\mid v\in V_x\}$ to express the length by which $v$ contributes to the lenght of an $R$-encoded word. 
+we add a set of fresh auxiliary variables $\{|v|\mid v\in V_x\}$ to express the length by which $v$ contributes to the length of an $R$-encoded word. 
 That is, $|v|$ will be $0$ if $v$ is assigned $\noepsilon$,
@@
 $$
-The lenght of the encoded word $x$ is then the sum of the lenghts contributed by the individual character variables in $V_x$, 
+The lenght of the encoded word $x$ is then the sum of the lengths contributed by the individual character variables in $V_x$, 
 hence we let 
@@
 
-For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)}-1}{100-1}$.
-The constraint uses $\#(v_0)$ to capture the total number of loop traversals.
-Notice that the constraint above contains an exponential component $\frac{100^{\#(v_0)}}{100-1}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
+For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint (assume character variables are not assigned $\epsilon$) $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#v_0-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#v_0}-1}{100-1}$.
+The constraint uses $\#v_0$ to capture the total number of loop traversals.
+Notice that the constraint above contains an exponential component $\frac{100^{\#v_0}}{100-1}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
 
 Let us have a look at another example.
-If we restrict the domain of $x$ to the PFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0^{(0)}\times 10+ v_1^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0^{(0)})-1})\times 100^{\#(v_2^{(0)})}+(v_2^{(0)}\times 10+ v_3^{(0)}) \times (1+100 +100^2 + \ldots 100 ^{\#(v_2^{(0)})-1}) =  (v_0^{(0)}\times 10+ v_1^{(0)}) \times \frac{100^{\#(v_0^{(0)})}-1}{100-1}\times 100^{\#(v_2^{(0)})} + (v_2^{(0)}\times 10+ v_3^{(0)}) \times \frac{100^{\#(v_2^{(0)})}-1}{100-1}$.
-Observe that the formula has two exponential components $\frac{100^{\#(v_0^{(0)})}\times 100^{\#(v_2^{(0)})} }{100-1}$ and $\frac{100^{\#(v_2^{(0)})} }{100-1}$.
-
-It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula to defines the number $n$ contains $m$ exponential components, one for each loop.
+If we restrict the domain of $x$ to the PFA in Figure~\ref{fig:sfa} (c), for the case when $n$ is positive, we have the relation $n= (v_0 \times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#v_0-1})\times 10\times 100^{\#v_3}+ v_2 \times 100^{\#v_3}  +(v_3\times 10+ v_4) \times (1+100 +100^2 + \ldots 100 ^{\#v_3-1}) =  (v_0\times 10+ v_1) \times \frac{100^{\#v_0-1}}{100-1}\times 10\times 100^{\#v_3} + v_2 \times 100^{\#v_3}+ (v_3\times 10+ v_4) \times \frac{100^{\#v_3-1}}{100-1}$.
+Observe that the formula has multiple exponential components, including $\frac{100^{\#v_0}\times 100^{\#v_3} }{100-1}$ and $\frac{100^{\#v_3} }{100-1}$.
+
+It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula to defines the number $n$ contains at least $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 \begin{figure}
+	\scalebox{0.7}{
 	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
@@
 	\path (q0) edge [loop above] node {$v_0$} (q0);
-	\end{tikzpicture}
+	\end{tikzpicture} }
 

### 2019-11-20 draft.tex
add explaination for x=toStr(n)
smaller changes in the tecnical stuff

@@
 We define $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$. 
+\lh{should we somehow define the sematntics of the lengt constraints more precisely? That is, how is the value of $|x|$ related to the value of $x$. ?}
 
@@
 We define $\modelsof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.
+The \emph{number-string} conversion constraint $x=\its{n}$ is treated as a syntactic sugar for $n=\sti{x}$.
 
@@
 
-Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$, and a language $L\subseteq \Sigma^*$, we define the set of $\pa$-encodings of the words in $L$ as 
+Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
 $\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
@@
 
-To this end, we define an additional notation.
-For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$.
+To formalise this correctness argument, we define an additional notation.
+For an interpretation $I$ of string variables, 
+we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$ of interpretations of $V_R\cup \#V_R$, containing combinations of interpretations of character variables of each $R(x)$ that encode the $I$.
+%
+Further, if $I \cup I'$ is an ainterpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
+%
+then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variavbles $V_R \cup \#V_R \cup N$. 
+%
 We lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
@@
 %
-We also that all disequality constraint $t \neq t'$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
+We also assume that all disequality constraint $t \neq t'$ are already converted to equivalent equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
 %
@@
 $$
-\lh{a correctness lemma would be good here, but it needs some modification of encoding probably, to be done}
+and the following lemma states its correctness.
+\begin{lemma}\label{lemma:eqcorrect}
+$\semof {\underf R {\phi_l}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_l})$
+\end{lemma}
 
@@
 
-It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula to defines the number $n$ contains at least $m$ exponential components, one for each loop.
+It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
-We want an ``easy completeness'' property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satifiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+We want an ``easy'' completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satifiable assignments can be often found within the domain restriction of just few of numeric PFAs).
 %
@@
 Observe that $\sti{``00010"}=10$.
-The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many trailing `$0$'s at the front.
+The key is that even for a bounded integer, the corresponding numeral can be of an unbounded length with arbitrarily many trailing `$0$'s at the front.
 All numbers with up to $m$-digits can be however still handled without having to solve exponential constraints.
@@
 to hold the value $0$. 
-This transition ensures that the under-approximation handles all numerals with arbitrary number of trailing zeros.  
+This transition ensures that the under-approximation handles numerals with arbitrary number of trailing zeros.  
 The self-loop is followed by a chain of $m$ transitions $(q_{i-1},v_i,q_{i}),1\leq i \leq m$, leading towards the final state $q_m$. 
@@
 It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
-Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would easily and completely cover all numerals.
+Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily'' and completely cover all numerals.
 %
@@
 $$
-Last, since this restriction is meanigfull only when the string is indeed numeral,  
+Last, since this restriction is meanigfull only when the string is indeed a numeral,  
 we also define the constraint representing the strings which are not numerals, the formula
@@
 $
-\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R'(\semof{\phi_s})
+\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R(\semof{\phi_s})
 $
 \end{lemma}
-The lemma uses the encoding function generalised to assignments of string \emph{and integer} variables. 
-It is defined so that, for an interpretation $I$ of string variables $X$ and an interpetation $I'$ of integer variables $N$, $X\cap N = \emptyset$, 
-$\encode R' {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$, which is then lifted to sets in the standard manner.
 

### 2019-11-20 draft.tex
little polishing of technical things

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\newcommand{\st}[2]{q_{#1}^{#2}}
-%\newcommand{\sym}[2]{v_{#1}^{#2}}
-%We use $\cvar$ to denote a finite set of \emph{character variables}  ranging over $\Sigma_\epsilon$. 
-%Sometimes we use index to denote different set of variables over the same range, e.g., $\cvarone$ and $\cvartwo$. 
-%We use $v$ and its variants for character variables. We call a string over $\cvar$ (character variables) a \emph{symbolic string}.
-%An \emph{interpretation $I$ over $\cvar$} is a mapping from $\cvar$ to $\Sigma_\epsilon$.
-For a symbolic string $x= v_1v_2\cdots v_k$ over $\cvar$, $I(x)$ is defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 
@@
 every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$. 
-In fact, the the parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquelly decoded:
-%i.e., $\decode A (\parikhof w)) = w$, 
-%and analogously for the entire language of $A$, as formalized by the following lemma.
+In fact, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquelly decoded:
 
@@
 and $\paf$ is an \emph{interpretation constraint}, a linear formula over $\cvar$. 
-\emph{Parametric flat automaton (PFA)} then is a parametric automaton with its finite automaton flat.
-
-%A finite automaton $D=(Q,T',\Sigma,q_0,q_m)$ is an \emph{instance} of a PFA $S=(Q,T,\cvar,q_0,q_m)$, if there exists an interpretation $I: \cvar \cup \{\epsilon\} \rightarrow \Sigma_\epsilon$ satisfying $I(\epsilon)=\epsilon$ and $T'=\{(q,I(c),q')\mid (q,c,q')\in T\}$.
-We write $I(S)$ to denote the instance of $S$ wrt.
-$I$.
-The language of $S$ is defined as $L(S)= \cup\{L(D) \mid D \mbox{ is an instance of } S\}$.
-Notice that $L(S)$ is regular because every PFA has only finitely many instance and the finite union of regular languages are also regular.
-
-%Such automata are recognizers of symbolic strings, i.e., strings over $\cvar$.
+\emph{Parametric flat automaton (PFA)} is then a parametric automaton with its finite automaton flat.
+
 Parametric automata accept words over $\cvar$, called \emph{parametric words}, but we still use them as representations of languages over $\Sigma$. 
@@
 %
-a mapping $I:\cvar\rightarrow$ to $\Sigma_\epsilon$. 
-For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretaion $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
+a mapping $I:\cvar\rightarrow\Sigma_\epsilon$. 
+For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretation $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
 %
@@
 
-Since every word $w \in \semof{\pa}$ is uniquelly determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x$ is uniquelly determined by its Parikh image, i.e.,
-$\decode \pa(\parikhof x)$, 
-we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I:\cvar\rightarrow\nat$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$ \emph{$\pa$-encodes} $w$.
-Lemma~\ref{lemma:decoding} implies such $\pa$-encoding can be uniquelly decoded.
+Since every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$, and since $x$ is uniquely determined by its Parikh image, i.e.,
+$x = \decode \pa(\parikhof x)$, 
+we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I:\cvar\rightarrow\Sigma_\epsilon$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$ \emph{$\pa$-encodes} $w$.
+Lemma~\ref{lemma:decoding} implies that such $\pa$-encoding can be uniquely decoded.
 We may hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ 
 so that $\decode \pa(I \cup \parikhof x) = w$. 
-We again lift the decoding function into sets of united assighnments in the standard manner.
-The following corrolary of Lemma~\ref{lemma:decoding} states that encodings of words in $\semof{\pa}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$ that satisfy $\paf$:
+We again lift the decoding function to sets of united assignments in the standard manner.
+The following corollary of Lemma~\ref{lemma:decoding} states that encodings of words in $\semof{\pa}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$ that satisfy $\paf$:
 
 \begin{corollary}\label{corollary:pfa}
-For an PFA $\pa = (A,\paf)$,
+For a PFA $\pa = (A,\paf)$,
 \\
@@
 %
-Notice that only the words from $L\cap \semof \pa$ have an $\pa$-encoding, 
+Notice that only the words from $L\cap \semof \pa$ have a $\pa$-encoding, 
 hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
-%$\encode A (L) = \{(I\cup\pim) \mid \decode A (I\cup \pim) \in L \cap \semof{A}\}$. 
-%We have that $\decode A \circ \encode A$ equal the identity function.
-%
 
@@
 %
-In this section, we describe formally how to restrict the domain of string variables to patterns defined by PFA, 
-and start the description of the algorithm that converts a string constraint $\insc$ to a linear formula $\outlf$ representing the restricted set of solutions.  
-%
-
-The domain restriction is formally defined by restricting the domain of each string variable to a chosen flat language. 
+In this section, we describe formally how to restrict the domain of string variables to patterns defined by PFA. 
+We start the description of the algorithm that converts a string constraint $\insc$ to a linear formula $\outlf$, called the \emph{flattening} of $\insc$, representing the restricted set of solutions.
+%
+
+The domain restriction is formally defined by restricting the domain of each string variable by a chosen PFA. 
 %
@@
 The particular choice of a PFA 
-for each variable  depends on the stratedy used in the implementation, and will be discussed in Section~\ref{section:implementation}.
-%
-The formula $\outlf$ will be  built intuctively to the structure of $\insc$.
-Namely, in the followin subsections we show how to build a formula $\underf R {\phi}$ for every atomic string constraint $\phi$, 
+for each variable  depends on the strategy used in the implementation, and will be discussed in Section~\ref{section:implementation}.
+%
+The flattening $\outlf$ will be  built inductively to the structure of $\insc$.
+Namely, in the following subsections we show how to build a flattening $\underf R {\phi}$ for every atomic string constraint $\phi$, 
 and for a conjunction of string constraints, we let $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
-% and $\underf R {\neg\phi} \defeq \neg\underf R{\phi}$. The underapproximation formula is then in the form $\outlf \defeq \underf R {\insc}$.
+We then let $\outlf \defeq \underf R \insc$
 
@@
 $\semof{\phi}^R = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{R(x)}\}$. 
-The following sections will be devoded to describing the construction of the formula $\outlf$ representing the $R$-restriction of $\insc$, that is, such that the following theorem holds: 
-The correctness of this construction is expressed by  Theorem~\ref{theorem:correct}:
+The following sections will be devoted to describing the flattening of the atomic string constraints. 
+The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}:
 \begin{theorem}\label{theorem:correct}
-$\decode R (\semof {\outlf}) = \semof{\insc}_R$. 
+$\decode R (\semof {\outlf}) = \semof{\insc}_R$ 
 \end{theorem}
@@
 %
-Further, if $I \cup I'$ is an ainterpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
-%
-then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variavbles $V_R \cup \#V_R \cup N$. 
+Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
+%
+then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$. 
 %
@@
 In the next sections, 
-we will formulate the corresponding lemma for linear formulas constructed from each type of atomic string constraints.
-%
-We note that the restriction of the semantics of $\underf R \phi$ here is needed since $\underf R \phi$ is constructed with some auxiliary variables.
+we will formulate the corresponding correctness lemma for flattenings constructed from each type of atomic string constraints.
+%
+We note that the restriction of the semantics of $\underf R \phi$ here is needed since $\underf R \phi$ will be constructed with some auxiliary variables.
+
+\lh{do we want to discuss some sort of completeness? That is, every interpretation of every integer constraint is are covered by some flat restriction. ?}
 
 \paragraph{Encoding epsilon.}
-A minor technical difficulty is that we wish to build under-approximation in the form of pure arithmetic formulas, 
+A minor technical difficulty is that we wish to build flat under-approximation in the form of pure arithmetic formulas, 
 but we may also wish to specify when a character variable is assigned $\epsilon$, but $\epsilon$ is not a number. 
@@
 
-%\subsection{Handling Regular Constraints Symbolically} \label{section:mem}
 \section{Flattening of Basic String Constraints}
@@
 We will now discuss a construction of the \emph{synchronization formula} for two PAs $\pa$ and $\pa'$. 
-%over character variables $V$ and $V'$. 
 It is a linear formula $\syncfof \pa {\pa'}$ 
-%over $\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo$ 
 that specifies how each word in the semantic intersection $\semof \pa \cap \semof {\pa'}$ is encoded by $\pa$ and by $\pa'$.
@@
 $e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode \pa(w')$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
-%
+
 Particularly, the synchronization formula is built for two PAs  
@@
 Informally, the lemma states that the models of $\syncfof \pa {\pa'}$ encode precisely the pairs of equivalent encodings of words from $\semof{\pa}$ and $\semof{\pa'}$, that constitute the intersection $\semof{\pa} \cap \semof{\pa'}$.
-Since that the models of $\syncfof \pa {\pa'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$, the statement of the lemma,
-restrics the semantics of $\syncfof \pa {\pa'}$ to the original variables $\cvarone \cup \cvartwo \cup \pvarsof{\cvarone} \cup \pvarsof\cvartwo$.
-%This is  achieve by quantifying out the variables of $V_\times$.
-
-Notice that if $\pa$ is flat (or, symmetrically, if $\pa'$ is flat), then the semantic intersection $\semof \pa \cap \semof {\pa'}$ can be still decoded from the synchronization formula $\semof {\syncfof \pa {\pa'}}$.
+Since that the models of $\syncfof \pa {\pa'}$ include also an assignment to the auxiliary variables of $(\cvarone_\epsilon\times\cvartwo_\epsilon) \cup \pvarsof{(\cvarone_\epsilon\times\cvartwo_\epsilon)}$, the lemma restricts $\semof {\syncfof \pa {\pa'}}$ to ${\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo}$.
+
+Notice that if $\pa$ is flat (or, symmetrically, if $\pa'$ is flat), then the semantic intersection $\semof \pa \cap \semof {\pa'}$ can be still decoded from the synchronization formula $\syncfof \pa {\pa'}$.
 Namely, due to Corollary~\ref{corollary:pfa}, we have that if $\pa$ is a PFA, then
-%$\semof A \cap \semof {A'} = \{\decode A(I\cup \pim) \mid (I\cup \pim) \in \semof{\syncfof A {A'}}_{\cvarone\cup \pvarone}\}$.  
-$$\decode \pa (\semof{\syncfof \pa {\pa'}}_{\cvarone\cup \pvarone}) = \semof \pa \cap \semof {\pa'}$$
+$$
+\decode \pa (\semof{\syncfof \pa {\pa'}}_{\cvarone\cup \pvarone}) = \semof \pa \cap \semof {\pa'}
+$$
 
@@
 Since our automata do not allow transition directly labeled by $\epsilon$,
-the $\epsilon$-transition is labeled by a fresh variable $v_\epsilon$ restricted by the constraint $v_\epsilon = \epsilon$.
+the $\epsilon$-transition is labeled by a fresh variable $v_\epsilon$ forced by the constraint $v_\epsilon = \epsilon$ to take the value $\epsilon$.
 
@@
 \subsection{Flattening of Equality Constraints} \label{section:eq}
-%\subsection{Handling Equality Constraints Symbolically, Experimental version} \label{section:eq}
 
@@
 We also assume that all disequality constraint $t \neq t'$ are already converted to equivalent equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
-%
 
@@
 
-\subsection{Encoding Length Constraints}
-Length constraints are not under-approximated by flattening. 
-Given a length constraint $\phi_l$ with string length variables $X$,
+\subsection{Flattening of Integer Constraints}
+Length constraints are encoded precisely by flattening, not under-approximated. 
+Given a length constraint $\phi_l$ that talks about string length variables $|x|,x\in X$, 
 we keep $\phi_l$ as is and add a formula to express the lengths of strings $|x|$ in terms of character variables $V_x$ and Parikh variables $\# V_x$ of $R(x)$.
@@
 $$
-The lenght of the encoded word $x$ is then the sum of the lengths contributed by the individual character variables in $V_x$, 
+The length of the encoded word $x$ is then the sum of the lengths contributed by the individual character variables in $V_x$, 
 hence we let 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Handling String-Integer Conversion} \label{section:s2i}
 \section{Flattening of String-Integer Conversion} \label{section:s2i}
@@
 
-Last, we present a central part of this paper, the construction of $\underf R {\phi_s}$ for a string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
+Last, we a major contribution of this paper, 
+the construction of a flattening $\underf R {\phi_s}$ of string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
 
@@
 Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
-We want an ``easy'' completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satifiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+We want an ``easy'' completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
 %
@@
 %
-\lh{I am not sure whether it is really impossible to make a smlall formula}
-%
-This would lead to an exponentail expolostion of the size of the linear formula definig the value of $n$.
+\lh{I am not sure whether it is really impossible to make a small formula}
+%
+This would lead to an exponential explosion of the size of the linear formula defining the value of $n$.
 %
@@
 $$
-Last, since this restriction is meanigfull only when the string is indeed a numeral,  
+Last, since this restriction is meaningful only when the string is indeed a numeral,  
 we also define the constraint representing the strings which are not numerals, the formula

### 2019-11-20 draft.tex
Update draft.tex

@@
 
-\title{Handling String-Number Conversion in String Constraint Solving}
+\title{Efficient Handling of String-Number Conversion}
 \author{}
@@
 Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed.
-\cite{????}.
 The path feasibility problem is usually solved by a reduction to the satisfiability of a formula.
-More precisely, program statements in the path are usually translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{satisfiability module theory (SMT)} solvers.
-The types of constraints needed depend on the types of program expressions to be analyzed; therefore, SMT solvers must support different combinations of theories to handle a wide range of types.
-
-Among all types of program variables, \emph{string data type} is omnipresent in modern programming languages.
+More precisely, program statements in the path are  translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{Satisfiability Modulo Theory (SMT)} solvers.
+The types of constraints needed depend on the types of program expressions to be analyzed.
+Therefore, SMT solvers need to support different combinations of theories so that they can handle a wide range of  types.
+
+Among all data types, the \emph{string data type} is omnipresent in modern programming languages.
 Various security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.

### 2019-11-20 draft.tex
some minor changes

--- 2019-11-20 draft.tex
@@
 
-But if array indices are modelled as strings, we must handle arithmetic somehow.
+But if array indices are modeled as strings, we must handle arithmetic somehow.
 Let us look at the case of line 6, we need to update the value of \texttt{x["03"-1]}.
@@
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is a string of 1's and 2's.
+To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12''$.
 Notice that $\Phi$ is satisfiable.
@@
 We define $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.
-\lh{should we somehow define the sematntics of the lengt constraints more precisely? That is, how is the value of $|x|$ related to the value of $x$. ?}
 
@@
 
-Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
+Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$, and a language $L\subseteq \Sigma^*$, we define the set of $\pa$-encodings of the words in $L$ as 
 $\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
@@
 
-To formalise this correctness argument, we define an additional notation.
-For an interpretation $I$ of string variables, 
-we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$ of interpretations of $V_R\cup \#V_R$, containing combinations of interpretations of character variables of each $R(x)$ that encode the $I$.
-%
-Further, if $I \cup I'$ is an ainterpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
-%
-then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variavbles $V_R \cup \#V_R \cup N$. 
-%
+To this end, we define an additional notation.
+For an interpretation $I:X\rightarrow \Sigma^*$, we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$.
 We lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
@@
 %
-We also assume that all disequality constraint $t \neq t'$ are already converted to equivalent equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
+We also that all disequality constraint $t \neq t'$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
 %
@@
 $$
-and the following lemma states its correctness.
-\begin{lemma}\label{lemma:eqcorrect}
-$\semof {\underf R {\phi_l}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_l})$
-\end{lemma}
+\lh{a correctness lemma would be good here, but it needs some modification of encoding probably, to be done}
 
@@
 
-It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
+It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula to defines the number $n$ contains at least $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
-We want an ``easy'' completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satifiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+We want an ``easy completeness'' property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satifiable assignments can be often found within the domain restriction of just few of numeric PFAs).
 %
@@
 Observe that $\sti{``00010"}=10$.
-The key is that even for a bounded integer, the corresponding numeral can be of an unbounded length with arbitrarily many trailing `$0$'s at the front.
+The key is that even for a bounded integer, the corresponding string can be of unbounded length with arbitrarily many trailing `$0$'s at the front.
 All numbers with up to $m$-digits can be however still handled without having to solve exponential constraints.
@@
 to hold the value $0$. 
-This transition ensures that the under-approximation handles numerals with arbitrary number of trailing zeros.  
+This transition ensures that the under-approximation handles all numerals with arbitrary number of trailing zeros.  
 The self-loop is followed by a chain of $m$ transitions $(q_{i-1},v_i,q_{i}),1\leq i \leq m$, leading towards the final state $q_m$.
@@
 It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
-Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily'' and completely cover all numerals.
+Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would easily and completely cover all numerals.
 %
@@
 $$
-Last, since this restriction is meanigfull only when the string is indeed a numeral,  
+Last, since this restriction is meanigfull only when the string is indeed numeral,  
 we also define the constraint representing the strings which are not numerals, the formula
@@
 $
-\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R(\semof{\phi_s})
+\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R'(\semof{\phi_s})
 $
 \end{lemma}
+The lemma uses the encoding function generalised to assignments of string \emph{and integer} variables. 
+It is defined so that, for an interpretation $I$ of string variables $X$ and an interpetation $I'$ of integer variables $N$, $X\cap N = \emptyset$, 
+$\encode R' {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$, which is then lifted to sets in the standard manner.
 

### 2019-11-20 draft.tex
little change
little things

@@
 then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$.
+That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
 %
@@
 
-Formally, the asynchronous product automaton is a tuple $\syncof \pa {\pa'} = ((Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f')),\paf\land\paf')$, where the transition relation $\syncT$ is the minimal set satisfying the following:
+Formally, the asynchronous product automaton is a tuple $\syncof \pa {\pa'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'))$, where the transition relation $\syncT$ is the minimal set satisfying the following:
 %
@@
 $$
-\syncfof \pa {\pa'} \defeq \parikhfof{\syncof \pa {\pa'}} \land \Psi_{\#} \land \Psi_=
+\syncfof \pa {\pa'} \defeq \parikhfof{\syncof \pa {\pa'}} \land \Psi_{\#} \land \Psi_= \land \paf \land \paf'
 $$
@@
 \semof {\syncfof \pa {\pa'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e\cup e'\mid e \in \encode \pa (w),\\ e'\in\encode {\pa'} (w), w\in\semof \pa \cap \semof {\pa'}\} 
+\{e\cup e'\mid e \in \encode \pa (w), e'\in\encode {\pa'} (w), w\in\semof \pa \cap \semof {\pa'}\} 
 $

### 2019-11-20 draft.tex
little thing

@@
 We may hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ 
-so that $\decode \pa(I \cup \parikhof x) = w$. 
+so that $\decode \pa(I \cup \parikhof x) = w$ (recall that $\Sigma_\epsilon \subseteq \nat$). 
 We again lift the decoding function to sets of united assignments in the standard manner.

### 2019-11-20 draft.tex
Update draft.tex

@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{?}, Z3 \cite{?} and Z3Str3 \cite{?}.
-However,  solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{?} and Z3Str3 \cite{}.
+
+An important class of string operations is  the string-number conversions.
+While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from extremely limited support by the state-of-the-art string constraint solvers.
+In fact, for many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
+In many security vulnerable codes,  that receive input, tend to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
+For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
+
+%
+%However,  solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
 When there is support, it is often very limited.
-Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations that require stronger solver support to handle real code.
+Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations %
+%
 
@@
 
-In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
+%
+%In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
 However, code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
@@
 $$\begin{array}{lc}
-1&	value_0 \in [1,9]^+ \wedge 	sum_0 = 0 \wedge \\
-2&	i_0 = |value_0| -1 \wedge \\
+1&	{\it value_0} \in [1,9]^+ \wedge 	{\it sum_0} = 0 \wedge \\
+2&	i_0 = |{\it value_0}| -1 \wedge \\
 %	value_0 = prefix_0\cdot charAt_0 \cdot suffix_0 \wedge\\
@@
 3&	d_0 = \sti{\chatAt{value_0}{i_0}} \wedge \\
-4&	sum_1 = sum_0 + d_0 \wedge\\
-5&	i_1 = |value_0| -2 \wedge \\
-6&	d_1 = \sti{\chatAt{value_0}{i_1}} \wedge \\
-7&	sum_2 = sum_1 + \ite{d_1*2>9}{d_1*2 -9}{d_1*2} \wedge\\
+4&	{\it sum_1} = {\it sum_0} + d_0 \wedge\\
+5&	i_1 = |{\it value_0}| -2 \wedge \\
+6&	d_1 = \sti{\chatAt{{\it value_0}}{i_1}} \wedge \\
+7&	{\it sum_2} = {\it sum_1} + \ite{d_1*2>9}{d_1*2 -9}{d_1*2} \wedge\\
 8& i_2 = 0\\
-9&	last_0 = \chatAt{\its{sum_2}}{|\its{sum_2}|-1} \wedge\\
-10&	last_0 =``0"
+9&	{\it last_0} = \chatAt{\its{{\it sum_2}}}{|\its{{\it sum_2}}|-1} \wedge\\
+10&	{\it last_0} =``0"
 \end{array}$$
 
-Here $value_0$ and $last_0$ are string variables and the others are integer variables.
+Here ${\it value_0}$ and ${\it last_0}$ are string variables and the others are integer variables.
 The method $\chatAt{x}{i}$ returns the character at index $i$ in the string $x$ while $n=\ite{b}{e}{e'}$ assigns to $n$ the value of the expression $e$ if $b$ is true and the value of the expression $e'$ otherwise.
@@
 
-Currently, even for the above constraint, which is from a simple program, most solvers fail to provide a correct answer.
-Therefore, there is an urgent need for developing efficient techniques for solving such combinations of constraints.
-To make matters worse, JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, has conversions between strings and integers embedded in the core of its semantics.
+Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
+Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
+Therefore, there is an urgent  need for  the  developing efficient techniques for solving such combinations of constraints.
+
+%Currently, even for the above constraint, which is from a simple program, most of the-state-of-the art solvers fail to provide a correct answer.
+
+Even, more crucially, in many programming languages, the conversion between strings and integers is a part of the definition of the the core  semantics of the language. 
+ JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, is one of such languages.
 Other scripting languages do too, but we focus on JavaScript due to its prominence.
@@
 
-A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
-This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
-Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
+A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indices are converted to strings.
+This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
+Consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
 
@@
 
-Here \texttt{x[3]} in line 2, \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
+Here \texttt{x[3]} in line 2, \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]} (due to the implicit conversion of numeric indices to strings in JavaScript), but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
 So na\"ive modeling of array indices with integers will not work -- it cannot distinguish the indices \texttt{"3"} and \texttt{"03"}.
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic array operation in JavaScript, and so having only limited capability for handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
+This is a rather basic and frequently used  array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
+Thus, we need stronger solvers that are  able to handle string-number conversion operations in order to be able to analyse  real code.
 
@@
 
-Solving string constraint with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and our experiments (Section \ref{section:evaluation}) show that state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+%Solving string constraints with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and our experiments (Section \ref{section:evaluation}) show that state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+
+Solving string constraint with string-number conversion is a very challenging problem.
+From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
+From practical point of view,
+ our experimental results  (in Section \ref{section:evaluation}) show that the current  the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
 
 In this paper, we propose a framework that efficiently handles string constraints with string-number conversion.
-Due to the difficulty of solving the problem exactly, our framework combines over and under-approximation of string constraints.
+Since the problem is provably unsolvable, our framework combines over and under-approximation techniques.
 The over-approximation is for proving UNSAT when possible, while the under-approximation is for proving SAT when possible.
-Both over- and under-approximation fall in a decidable fragment of string constraints that can we can efficiently solve.
+Both over- and under-approximation fall in a decidable fragment of string constraints that  we can efficiently solve.
+
+%Observe that our main contribution lies in the
 
@@
 
-Our decision procedure has two steps: the first step is over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+Our decision procedure has two steps: the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Observe that we could  over-approximate the input constraint into any decidable fragment, e.g.
 the acyclic fragment~\cite{abdulla2014string} or the straight-line fragment~\cite{chen2019decision}.
-Our choice of the  chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
-In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+Our choice of the  chain-free fragment~\cite{abdulla2019chain} is only motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
+In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$  and replacing the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
 The over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some case, we could derive the value of $n=12$ from some integer constraints.
-Then we could further derive the value of $x$ is in the regular language $(0^*12)$.
+For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
+Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
 Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
-Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
+Surprisingly, despite its simplicity, our over-approximation procedure works very well in practice.
+Coming back to the formula $\Phi$, the over-approximation module will  return SAT  in this case.
 
@@
 
-The second step of our decision procedure is only enabled if the over-approximation is SAT.
+The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
+In this case, our decision procedure restricts the search domain of each string variable to strings that obey some predefined and parameterized pattern.
+To achieve our under-approximation technique (which is  our main contribution),  we propose to use patterns defined by \emph{parametric flat automata} (PFA).
+A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
+The size of the PFA is paramaterized by the length of the sequence of loops and the size of each loop.
+Adjusting these parameters enlarges or prunes the potential solution space.
+This approach based on PFA is very flexible yet allows very efficient manipulation.
+In fact, the PFA restricts the  search space for each  variable to the set of words accepted by the given PFA.
+
+Then, we show that given such restriction, one can  reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
+To gain in efficiency, we label each transition  of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
+This done by associating to each character in our alphabet a unique natural number.
+This allows us to  to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers and it is  the key for handling string-number conversion efficiently.
+
+%The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
 In this case, our decision procedure restricts the domain of each string variable to strings that obey some predefined and parameterized pattern.
@@
 We label each transition between two states of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
-Such reduction based on PFA is the key to handling string-number conversion efficiently.
+%Such reduction based on PFA is the key to handling string-number conversion efficiently.
 When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulas and can be solved efficiently.
@@
 
-\item The introduction of the class of \emph{parametric flat automata} which uses character variables as transition labels instead of characters.
-This allows us to avoid the {alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} when it comes to handle string-number conversion constraints.
+\item The class of \emph{parametric flat automata} which is the key for efficient handling of string-number conversion constraints.
 

### 2019-11-21 draft.tex
intro

@@
 In many security vulnerable codes,  that receive input, tend to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
-For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
+\yfc{some grammar error?} For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 
@@
 
-To check whether the program path that traverses both loop exactly once and finally passes this test has a valid input, we create the following (string) constraint:
+To check whether the program path that traverses both loop exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
 
@@
 Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
-Therefore, there is an urgent  need for  the  developing efficient techniques for solving such combinations of constraints.
+Therefore, there is an urgent  need for developing efficient techniques for solving such combinations of constraints.
 
@@
 
-Even, more crucially, in many programming languages, the conversion between strings and integers is a part of the definition of the the core  semantics of the language. 
+Even, more crucially, in many programming languages, the conversion between strings and integers is a part of the definition of the core semantics of the language. 
  JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, is one of such languages.
@@
 The program reads input value from users and use it as the array index.
-This program works perfectly no matter the input is in string form (e.g., ``1'', ``3'') or numerical form (e.g., $1$, $3$).
+This program works perfectly no matter the input is in string form (e.g., ``1", ``3") or numerical form (e.g., $1$, $3$).
 Both of them can pass though the range test (when the input is a string, it will be first convert to integer and then compared with $0$ and $M$).
@@
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12''$.
+To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12"$.
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x=``12''$ and $y=``1212''$.
+E.g., it has a model $x``12"$ and $y=``1212"$.
 
@@
 A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
-The size of the PFA is paramaterized by the length of the sequence of loops and the size of each loop.
+The size of the PFA is parameterized by the length of the sequence of loops and the size of each loop.
 Adjusting these parameters enlarges or prunes the potential solution space.
 This approach based on PFA is very flexible yet allows very efficient manipulation.
-In fact, the PFA restricts the  search space for each  variable to the set of words accepted by the given PFA.
+In fact, our procedure restricts the search space for each variable to the set of words accepted by the corresponding given PFA.
 
@@
 Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
+For example, from the formula $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
 
@@
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12''$ and $y=``1212''$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
-The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
+For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
 
 If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure changes the PFAs to be more expressive ones (by adding more states and transitions) to systematically search for a solution.
+If not, our procedure changes the PFAs to more expressive ones (by adding more states and transitions) to systematically search for a solution.
 Depending on the implementation, one may choose to report unknown after some certain steps.
@@
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x=``12''$ and $y=``1212''$.
+E.g., it has a model $x=``12"$ and $y=``1212"$.
 %
 %For proving UNSAT, our framework does not set any restriction on which decision procedure to use.
-One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
+One can select any decision procedure they want to use and ``over-approximate" the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
 For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
@@
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12''$ and $y=``1212''$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
 The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
 %
@@
 %We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
-%We drop the reference to $V$ and write just ``model of $\phi$'', $\modelsof \phi$, and $\models$ when no confusion may arise.
+%We drop the reference to $V$ and write just ``model of $\phi$", $\modelsof \phi$, and $\models$ when no confusion may arise.
 For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
@@
 This is the semantics used by most of the SMT solvers, and hence we follow it in this paper.
-The encoding has a benefit that it can also handle the case where $x$ is ``not a number'', using the condition $\sti{x} = -1$.
+The encoding has a benefit that it can also handle the case where $x$ is ``not a number", using the condition $\sti{x} = -1$.
 
 Supporting only positive integer is not a strong restriction, since conversing from negative integer can still be encoded using the positive only version.
-More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number'', which can also be encoded using more conditions):
+More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number", which can also be encoded using more conditions):
 $$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
@@
 %$$ % , to the output linear formulas $\phi_O$. 
-%Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_i}$.
-%We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
+%Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon" transition, i.e., one with the label $v_{\epsilon_i}$.
+%We use $V_\epsilon$ to denote the set of all variables used for ``epsilon" transitions.
 %
@@
 For the equality constraint $xy = yx$, assume that we restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon'' transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
+In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon" transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
 %
@@
 %
-%In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
+%In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product" automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
 %
@@
 Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
-We want an ``easy'' completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+We want an ``easy" completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
 %
@@
 Hence this PFA covers all numerals that encode numbers with at most $m$ digits.
-Although it still has a loop, it will not create any exponential component defining the value of $n$ because the loop only represents a sequence of ``0'' at the front of $x$.
+Although it still has a loop, it will not create any exponential component defining the value of $n$ because the loop only represents a sequence of ``0" at the front of $x$.
 It will not affect the integer value of $n=\sti{x}$.
@@
 It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
-Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily'' and completely cover all numerals.
+Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily" and completely cover all numerals.
 %
@@
 
-%The condition that when $x$ is ``not a number'' is specified by the following formula.
+%The condition that when $x$ is ``not a number" is specified by the following formula.
 %

### 2019-11-21 draft.tex
formulas to formulae globally

@@
 Our choice of the  chain-free fragment~\cite{abdulla2019chain} is only motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
-In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$  and replacing the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$  and replacing the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
 The over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
@@
 %Such reduction based on PFA is the key to handling string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulas and can be solved efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulae and can be solved efficiently.
 
@@
 %Such reduction based on PFA is the key to handle string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulas and can be solved efficiently.
+When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulae and can be solved efficiently.
 We can step-wisely enrich the PFAs and hence solve the satisfiability problem of string constraints in a systematic manner.
@@
 One can select any decision procedure they want to use and ``over-approximate" the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
-For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
-This produce new formulas that over-approximate the original ones and fall in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+For instance, we can convert $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+This produce new formulae that over-approximate the original ones and fall in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
@@
 
-%Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.  
+%Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.  
 %Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
@@
 
-Through the paper, we will use quantifier-free linear integer arithmetic formulas, and call them \emph{linear formulas} for short.  
+Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.  
 Given a linear formula $\phi$ over variables $V$ and an \emph{integer interpretation} of $V$, a function $I:V\rightarrow \integers$, 
@@
 %\section{Under-approximation} \label{section:under_approximate}
-%In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulas $\outlf$ in polynomial-time.
+%In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulae $\outlf$ in polynomial-time.
 We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
@@
 %We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
-In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulas $\outlf$.
+In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulae $\outlf$.
 We also add constraints to $\outlf$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
 %
-%More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulas $\outlf$.
+%More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulae $\outlf$.
 After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
@@
 \paragraph{Encoding epsilon.}
-A minor technical difficulty is that we wish to build flat under-approximation in the form of pure arithmetic formulas, 
+A minor technical difficulty is that we wish to build flat under-approximation in the form of pure arithmetic formulae, 
 but we may also wish to specify when a character variable is assigned $\epsilon$, but $\epsilon$ is not a number. 
-Hence, to allow purely arithmetic formulas talk about $\epsilon$, 
+Hence, to allow purely arithmetic formulae talk about $\epsilon$, 
 we encode $\epsilon$ as some fixed number $\noepsilon\in\nat\setminus\Sigma$.
-%In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulas constraining interpretations of character variables.
+%In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulae constraining interpretations of character variables.
 
@@
 %\Psi_\epsilon \defeq \bigwedge_{1\leq i \leq m} v_{\epsilon_i} = -1
-%$$ % , to the output linear formulas $\phi_O$. 
+%$$ % , to the output linear formulae $\phi_O$. 
 %Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon" transition, i.e., one with the label $v_{\epsilon_i}$.
@@
 For the equality constraint $xy = yx$, assume that we restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon" transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
+In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon" transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulae $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulae $\phi_O$.
 %
@@
 We use $\#(v_i)$ and $\#(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
-The following formulas establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
+The following formulae establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
 %\begin{enumerate}

### 2019-11-21 evaluation.tex
Update table
Update tables, add checkLuhn graph

@@
 
+\begin{table}[h]
+\centering
+\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraint benchmarks.}
+\scalebox{0.85}{
+\begin{tabular}{|l r | r r r r r|}
+\hline
+\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
+\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 20123 & 18490 &  3514 & 19149 \\ 
+							& UNSAT    &  3858*   &  3841 &  3855 &  4521 & 3828 \\
+							& $\times$ &  1977*   &  1457 &  3076 & 17386 & 2444 \\ \hline
+\multirow{3}{*}{APLAS}		& SAT      &   128*   &    51 &    19 &    52 & 132 \\
+							& UNSAT    &   287*   &   214 &   100 &   118 & 82 \\
+							& $\times$ &   185*   &   335 &   481 &   430 & 386 \\ \hline
+\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   871 &   881 &   651 & 778 \\
+							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
+							& $\times$ &    26*   &    10 &     0 &   228 & 61 \\ \hline
+\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   610 &   316 &   605 & 688 \\
+							& UNSAT    &   294*   &   255 &   206 &   217 & 339 \\
+							& $\times$ &   269*   &   200 &   543 &   243 & 38 \\\hline
+\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
+							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
+							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
+\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 9 &     6 &    16 & 311 \\
+							& UNSAT    &  1030*   &  1025 &  1020 &   962 & 596 \\
+							& $\times$ &     2*   &    11 &    19 &    67 & 138 \\ \hline
+\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21675 & 19724 &  4848 & 21305  \\
+							& UNSAT    &  8067*  &   7938 &  7773 &  8383 & 7172  \\
+							& $\times$ &  2464*  &  2019 &   4135 & 18401 & 3155  \\\hline	
+\end{tabular}}
+\label{table:base_benchmark}
+\end{table}
+
+\begin{table}[h]
+\centering
+\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark.}
+\scalebox{0.8}{
+\begin{tabular}{|l r | r r r r|}
+\hline
+\multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
+\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1766 &  1025  &   333 \\ 
+										 & UNSAT    &  16369*  & 15612 & 17234  & 15543 \\
+										 & $\times$ &    202*  &  1549 &   668  &  3051 \\ \hline 
+\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   586 &  1802  &   389 \\ 
+										 & UNSAT    &    720*  &   666 &   744  &   729 \\
+										 & $\times$ &   1014*  &  1394 &   100  &  1528 \\ \hline
+\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     5 &    16  &     4 \\ 
+										 & UNSAT    &      0   &     0 &     0  &     0 \\
+										 & $\times$ &      0   &    15 &     4  &    16 \\ \hline \hline
+\multirow{3}{*}{Total}					 & SAT      &   3288*  &  2357 &  2843  &   726 \\ 
+										 & UNSAT    &  17089*  & 16278 & 17978  & 16272 \\
+										 & $\times$ &   1216*  &  2958 &   772  &  4595 \\ \hline
+\end{tabular}}
+\label{table:str_int_benchmark}
+\end{table}
+
+\begin{figure}
+\begin{tikzpicture}
+\begin{axis}
+\addplot+[sharp plot]
+coordinates
+{
+(2,0.097)
+(3,0.078)
+(4,0.098)
+(5,0.098)
+(6,0.161)
+(7,0.236)
+(8,0.307)
+(9,0.26)
+(10,0.211)
+(11,0.228)
+(12,0.33)
+};
+\end{axis}
+\end{tikzpicture}
+\caption{checkLuhn: z3-trau}
+\end{figure}
+
+\begin{figure}
+\begin{tikzpicture}
+\begin{axis}
+\addplot+[sharp plot]
+coordinates
+{
+(2,0.266)
+(3,10.084)
+(4,48.791)
+(5,120)
+(6,120)
+(7,120)
+(8,120)
+(9,120)
+(10,120)
+(11,120)
+(12,120)
+};
+\end{axis}
+\end{tikzpicture}
+\caption{checkLuhn: cvc4 (SAT if not timeout)}
+\end{figure}
+
+\begin{figure}
+\begin{tikzpicture}
+\begin{axis}
+\addplot+[sharp plot]
+coordinates
+{
+(2,0.238)
+(3,0.128)
+(4,120)
+(5,120)
+(6,0.134)
+(7,120)
+(8,0.366)
+(9,120)
+(10,0.526)
+(11,0.374)
+(12,0.405)
+};
+\end{axis}
+\end{tikzpicture}
+\caption{checkLuhn: z3 (SAT if not timeout)}
+\end{figure}
+
+\begin{figure}
+\begin{tikzpicture}
+\begin{axis}
+\addplot+[sharp plot]
+coordinates
+{
+(2,0.4743)
+(3,0.56052)
+(4,0.36695)
+(5,0.60905)
+(6,22.06429)
+(7,53.77536)
+(8,118.41196)
+(9,0.50559)
+(10,120)
+(11,0.42953)
+(12,120)
+};
+\end{axis}
+\end{tikzpicture}
+\caption{checkLuhn: z3str3 (UNKNOWN if not timeout)}
+\end{figure}
+
+\hide{ % keep data of abc and ostrich
 \begin{table}[h]
@@
 \multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
-\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
-							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
-							& $\times$ &  1977*   &  1824* &  3211 &  18558*  & 2444 & 25421 & 24439 \\ \hline
+\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
+							& unsat    &  3858*   &  3834* &  3855 &   3839*  & 3828 & 0 & 871 \\
+							& $\times$ &  1977*   &  1824* &  3076 &  18558*  & 2444 & 25421 & 24439 \\ \hline
 \multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
@@
 							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
-\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
-							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
-							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\\hline
+\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   316 &    493*  & 688 & 439 & 0 \\
+							& unsat    &   294*   &   240* &   206 &    190*  & 339 & 158 & 0 \\
+							& $\times$ &   269*   &   148* &   543 &    382*  & 38 & 468 & 1065 \\\hline
 \multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
-							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
-							& $\times$ &     5*   &     6* &    15 &     55*  & 88 & 76 & 797 \\ \hline
+							& unsat    &   814*   &   818* &   807 &    772*  & 500 & 443 & 17 \\
+							& $\times$ &     5*   &     6* &    16 &     55*  & 88 & 76 & 797 \\ \hline
 \multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
-							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
-							& $\times$ &     2*   &   101* &    17 &     71*  & 137 & 120 & 978 \\ \hline
+							& unsat    &  1030*   &   936* &  1020 &    958*  & 596 & 349 & 22 \\
+							& $\times$ &     2*   &   101* &    19 &     71*  & 137 & 120 & 978 \\ \hline
 \multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
-							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
-							& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\ \hline
-							\hline
-\multirow{3}{*}{Total}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
-& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
-& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\\hline
+							& unsat    & 3391* & 2082* & 2824 & 2205* & 2079 & 1972 & 2079 \\
+							& $\times$ & 0* & 0* & 567 & 1186* & 84 & 383 & 13 \\ \hline \hline
+\multirow{3}{*}{Total} 		& sat      & * & * & 19724 & * &  &  &  \\
+							& unsat    & * & * & 10597 & * &  &  &  \\
+							& $\times$ & * & * &  4702 & * &  &  &  \\\hline
 \end{tabular}}
@@
 \end{table}
+}
 
-\begin{table}[h]
-\centering
-\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark (numbers with * will be updated later)}
-\scalebox{0.8}{
-\begin{tabular}{|l r | r r r r|}
-\hline
-\multicolumn{2}{|c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{String-Number-Leetcode}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
-							& unsat    &  17088*  & 16377* & 16832* &  16034* \\
-							& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline 
-\multirow{3}{*}{String-Number-PythonLib}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
-& unsat    &  17088*  & 16377* & 16832* &  16034* \\
-& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline
-\multirow{3}{*}{String-Number-JavaScript}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
-& unsat    &  17088*  & 16377* & 16832* &  16034* \\
-& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline 							
-							\hline
-\multirow{3}{*}{Total}	& sat & 622*  &  330* &  100* &  85* \\ 
-& unsat    &  1054*  & 780* & 1043* &  634* \\
-& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
-\end{tabular}}
-\label{table:str_int_benchmark}
-\end{table}
-
-\hide{%3rd version
+\hide{ %3rd version of tables
 \begin{table}[t]
@@
 \end{table*}
-}
 
-\hide{
 \begin{table*}[t]
@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{Z3-str3}~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4(Relese-1.7)~\cite{cvc4Tool}, Z3(master:dde8da853)~\cite{z3}, \textsf{Z3-str3}(master:109dfc5e8)~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.

### 2019-11-21 evaluation.tex
Add table of checkLuhn results

@@
 \centering
-\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraint benchmarks.}
+\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraint benchmarks.}
 \scalebox{0.85}{
@@
 \centering
-\caption{Results of {\tool}, CVC4, and Z3 on Basic String Constraints + String-Number Conversion benchmark.}
+\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraints + String-Number Conversion benchmark.}
 \scalebox{0.8}{
@@
 
+\begin{table}[h]
+\centering
+\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
+\scalebox{0.9}{
+\begin{tabular}{| c | c c c c|}
+\hline
+\# of Loops & {\tool} 	  &  CVC4    	 &       Z3   & Z3-str3 \\ \hline
+2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.27s)   & \textbf{SAT}(0.2s)  & $\times$ \\
+3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(10.1s)  & \textbf{SAT}(0.1s)  & $\times$ \\
+4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(48.7s) &   $\times$  & $\times$ \\
+5 			& \textbf{SAT}(<0.1s)  &  $\times$     &   $\times$  & $\times$ \\
+6 			& \textbf{SAT}(0.16s)  &  $\times$     & \textbf{SAT}(0.13s) & $\times$ \\
+7 			& \textbf{SAT}(0.24s)  &  $\times$     &   $\times$  & $\times$ \\
+8 			& \textbf{SAT}(0.31s)  &  $\times$     & \textbf{SAT}(0.37s) & $\times$ \\
+9 			& \textbf{SAT}(0.26s)  &  $\times$     &   $\times$  & $\times$ \\
+10 			& \textbf{SAT}(0.21s)  &  $\times$     & \textbf{SAT}(0.53s) & $\times$ \\
+11 			& \textbf{SAT}(0.23s)  &  $\times$     & \textbf{SAT}(0.37s) & $\times$ \\
+12 			& \textbf{SAT}(0.33s)  &  $\times$     & \textbf{SAT}(0.40s) & $\times$ \\ \hline
+\end{tabular}}
+\label{table:checkLuhn}
+\end{table}
+
+\hide{
 \begin{figure}
@@
 \end{figure}
+}
 
@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4(Relese-1.7)~\cite{cvc4Tool}, Z3(master:dde8da853)~\cite{z3}, \textsf{Z3-str3}(master:109dfc5e8)~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
@@
 
-All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test.
+All experiments were executed on a computer with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
 We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.

### 2019-11-21 draft.tex
Update tables, add checkLuhn graph
polish sec 4

@@
 \synctex=1
+\usepackage{pgfplots}
 
@@
 
-We introduce \emph{parametric flat automata} that will be used to define patterns 
-used by the under-approximation module to restrict the domain of string variables.
-
+We introduce \emph{parametric flat automata} that will be used to define patterns used by the under-approximation module to restrict the domain of string variables. 
+\scalebox{0.7}{
+	\tikzset{state/.style={circle,draw=green!80,fill=green!20,
+			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
+
+	\renewcommand{\sym}[2]{a_{#1}^{#2}}
+	\begin{tikzpicture} 
+	\node[state,initial] (q0) {$\st{0}{0}$};
+	\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
+	\node (q2) [right = 1.8cm of q1]{};
+	\node (q3) [right = 1cm of q2]{};
+	\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};
+
+	\node[state] (q01) [above left = 0.6cm of q0] {$\st{0}{1}$};
+	\node[state] (q02) [above = 1cm of q0] {$\st{0}{2}$};
+	\node[state] (q03) [above right = 0.6cm of q0] {$\st{0}{l_0}$};
+	\node   (m1) [above right = -0.4cm and -0.3cm of q03] {$\ ^{-1}$};
+
+	\node[state] (q11) [above left = 0.6cm of q1] {$\st{1}{1}$};
+	\node[state] (q12) [above = 1cm of q1] {$\st{1}{2}$};
+	\node[state] (q13) [above right = 0.6cm of q1] {$\st{1}{l_1}$};
+	\node   (m2) [above right = -0.4cm and -0.3cm of q13] {$\ ^{-1}$};
+
+	\node[state] (qm1) [above left = 0.6cm of qm] {$\st{m}{1}$};
+	\node[state] (qm2) [above = 1cm of qm] {$\st{m}{2}$};
+	\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{l_m}$};
+	\node   (mm) [above right = -0.4cm and -0.3cm of qm3] {$\ ^{-1}$};
+
+	\draw[->] (q0) edge [bend left] node [left]{$\sym{0}{0}$} (q01) ;
+	\draw[->] (q01) edge [bend left] node [left]{$\sym{0}{1}$} (q02) ;
+	\draw[->,dotted] (q02) edge [bend left] node [right]{} (q03) ;
+	\draw[->] (q03) edge [bend left] node [right]{$\sym{0}{l_0-1}$} (q0) ;
+
+	\draw[->] (q0) edge node [below]{$a_0$} (q1) ;
+	\draw[->] (q1) edge node [below]{$a_1$} (q2) ;
+	\draw[dotted] (q2) edge (q3) ;
+	\draw[->] (q3) edge node [below]{$a_{m-1}$} (qm) ;
+
+	\draw[->] (qm) edge [bend left] node [left]{$\sym{m}{0}$} (qm1) ;
+	\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
+	\draw[dotted] (qm2) edge [bend left] node [right]{} (qm3) ;
+	\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{l_m-1}$} (qm) ;
+
+	\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
+	\draw[->] (q11) edge [bend left] node [left]{$\sym{1}{1}$} (q12) ;
+	\draw[->,dotted] (q12) edge [bend left] node [right]{} (q13) ;
+	\draw[->] (q13) edge [bend left] node [right]{$\sym{1}{l_1-1}$} (q1) ;
+
+	\end{tikzpicture} }
 \paragraph{Flat automata} 
 First, we say that an FA 
-$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is \emph{flat} if it satisfies the following structural constraints:
+$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is \emph{flat} if it satisfies the following structural constraints (the figure above):
 \begin{enumerate}
@@
 The crucial feature of flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver. 
-\lh{, allowing to circumvent more costly automata algorithms and decision procedures. Concretize and justify this better?}
+\lh{, allowing to circumvent more costly automata algorithms and decision procedures.
+Concertize and justify this better?}\yfc{maybe we can say according to the experience of verification of concurrent system, flattening is usually faster than pure automata operation?
+Faouzi should know something.}
 %
@@
 every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$. 
-In fact, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquelly decoded:
+In fact, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquely decoded:
 
@@
 More concretely, the function $\decode A$ can be implemented as follows. 
-Given $\pim:\#\cvar\rightarrow\nat$,
-and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m-1}$, 
-$\decode A(\pim)$ is constructed as the word $w_0 a_{0} \ldots a_{m-1} w_{m-1}$ where for each $i\in [0,m-1]$,
-$w_i = (a_i^0 \cdots a_i^{l_{i-1}})^{\pvarsof {a_i^0}}$ if $l_i >0$ and $w_i = \epsilon$ if $l_i = 0$. 
+Given $\pim:\#\Sigma\rightarrow\nat$,
+and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m}$, 
+$\decode A(\pim)$ is constructed as the word $w_0 a_{0} \ldots a_{m-1} w_{m}$ where for each $i\in [0,m]$,
+$w_i = (a_i^0 \cdots a_i^{l_{i}-1})^{\pvarsof {a_i^0}}$ if $l_i >0$ and $w_i = \epsilon$ if $l_i = 0$. 
 \end{proof}
 %
-For example, in the automaton of Figure~\ref{fig:sfa_def}, 
-from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$.
+For example, in the automaton of the figure above, 
+from $\parikhwof x {a_0} = \parikhwof x {a_1} = \cdots = \parikhwof x {a_{m}}=1$ and $\parikhwof x {a^0_1}=\parikhwof x {a^1_1}=\parikhwof x {a^2_1}=2$ we derive that $x=a_0(a^0_1a^1_1a^2_1)^2a_1\cdots a_{m-1}$.
 
@@
 and $\paf$ is an \emph{interpretation constraint}, a linear formula over $\cvar$. 
-\emph{Parametric flat automaton (PFA)} is then a parametric automaton with its finite automaton flat.
+\emph{Parametric flat automaton (PFA)} is then a parametric automaton with its finite automaton flat. See Figure~\ref{fig:sfa_def} and~\ref{fig:sfa} for examples of PFAs (automaton part only).
 
@@
 We may hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ 
-so that $\decode \pa(I \cup \parikhof x) = w$ (recall that $\Sigma_\epsilon \subseteq \nat$). 
+so that $\decode \pa(I \cup \parikhof x) = w$ (recall that $\Sigma_\epsilon \subseteq \nat$). \yfc{true only if we move the semantic of $\epsilon$ to preliminary. Now it is a symbol.}
 We again lift the decoding function to sets of united assignments in the standard manner.
-The following corollary of Lemma~\ref{lemma:decoding} states that encodings of words in $\semof{\pa}$ are encodings of parametric words of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$ that satisfy $\paf$:
+The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
 

### 2019-11-21 draft.tex
little changeds

--- 2019-11-21 draft.tex
@@
 \newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
+\newcommand{\changed}[1]{{\color{orange}#1}}
 \newcommand{\yfc}[1]{{\color{blue}YFC: #1}}
@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{?} and Z3Str3 \cite{}.
-
-An important class of string operations is  the string-number conversions.
-While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from extremely limited support by the state-of-the-art string constraint solvers.
-In fact, for many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
-In many security vulnerable codes,  that receive input, tend to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
-\yfc{some grammar error?} For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
-
-%
-%However,  solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{?}, Z3 \cite{?} and Z3Str3 \cite{?}.
+However,  solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
 When there is support, it is often very limited.
-Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations %
-%
+Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations that require stronger solver support to handle real code.
 
@@
 
-%
-%In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
+In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
 However, code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
@@
 
-To check whether the program path that traverses both loop exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
+To check whether the program path that traverses both loop exactly once and finally passes this test has a valid input, we create the following (string) constraint:
 
 $$\begin{array}{lc}
-1&	{\it value_0} \in [1,9]^+ \wedge 	{\it sum_0} = 0 \wedge \\
-2&	i_0 = |{\it value_0}| -1 \wedge \\
+1&	value_0 \in [1,9]^+ \wedge 	sum_0 = 0 \wedge \\
+2&	i_0 = |value_0| -1 \wedge \\
 %	value_0 = prefix_0\cdot charAt_0 \cdot suffix_0 \wedge\\
@@
 3&	d_0 = \sti{\chatAt{value_0}{i_0}} \wedge \\
-4&	{\it sum_1} = {\it sum_0} + d_0 \wedge\\
-5&	i_1 = |{\it value_0}| -2 \wedge \\
-6&	d_1 = \sti{\chatAt{{\it value_0}}{i_1}} \wedge \\
-7&	{\it sum_2} = {\it sum_1} + \ite{d_1*2>9}{d_1*2 -9}{d_1*2} \wedge\\
+4&	sum_1 = sum_0 + d_0 \wedge\\
+5&	i_1 = |value_0| -2 \wedge \\
+6&	d_1 = \sti{\chatAt{value_0}{i_1}} \wedge \\
+7&	sum_2 = sum_1 + \ite{d_1*2>9}{d_1*2 -9}{d_1*2} \wedge\\
 8& i_2 = 0\\
-9&	{\it last_0} = \chatAt{\its{{\it sum_2}}}{|\its{{\it sum_2}}|-1} \wedge\\
-10&	{\it last_0} =``0"
+9&	last_0 = \chatAt{\its{sum_2}}{|\its{sum_2}|-1} \wedge\\
+10&	last_0 =``0"
 \end{array}$$
 
-Here ${\it value_0}$ and ${\it last_0}$ are string variables and the others are integer variables.
+Here $value_0$ and $last_0$ are string variables and the others are integer variables.
 The method $\chatAt{x}{i}$ returns the character at index $i$ in the string $x$ while $n=\ite{b}{e}{e'}$ assigns to $n$ the value of the expression $e$ if $b$ is true and the value of the expression $e'$ otherwise.
@@
 
-Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
-Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
+Currently, even for the above constraint, which is from a simple program, most solvers fail to provide a correct answer.
 Therefore, there is an urgent need for developing efficient techniques for solving such combinations of constraints.
-
-%Currently, even for the above constraint, which is from a simple program, most of the-state-of-the art solvers fail to provide a correct answer.
-
-Even, more crucially, in many programming languages, the conversion between strings and integers is a part of the definition of the core semantics of the language. 
- JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, is one of such languages.
+To make matters worse, JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, has conversions between strings and integers embedded in the core of its semantics.
 Other scripting languages do too, but we focus on JavaScript due to its prominence.
@@
 
-A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indices are converted to strings.
-This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
-Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
-Consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
+A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indexes are converted to strings.
+This conversion is mandated explicitly by JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly; consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
 
@@
 
-Here \texttt{x[3]} in line 2, \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]} (due to the implicit conversion of numeric indices to strings in JavaScript), but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
+Here \texttt{x[3]} in line 2, \texttt{x[03]} in line 3, and \texttt{x["3"]} in line 4 all denote the same array element of \texttt{x["3"]}, but \texttt{x["03"]} denotes a completely different element (which is stored at the index \texttt{"03"} of the array).
 So na\"ive modeling of array indices with integers will not work -- it cannot distinguish the indices \texttt{"3"} and \texttt{"03"}.
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic and frequently used  array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
-Thus, we need stronger solvers that are  able to handle string-number conversion operations in order to be able to analyse  real code.
+This is a rather basic array operation in JavaScript, and so having only limited capability for handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
 
@@
 The program reads input value from users and use it as the array index.
-This program works perfectly no matter the input is in string form (e.g., ``1", ``3") or numerical form (e.g., $1$, $3$).
+This program works perfectly no matter the input is in string form (e.g., ``1'', ``3'') or numerical form (e.g., $1$, $3$).
 Both of them can pass though the range test (when the input is a string, it will be first convert to integer and then compared with $0$ and $M$).
@@
 
-%Solving string constraints with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and our experiments (Section \ref{section:evaluation}) show that state-of-the-art string constraint solvers provide only limited support to string-number conversion.
-
-Solving string constraint with string-number conversion is a very challenging problem.
-From the theoretical point of view, this problem is already proven to be undecidable~\cite{day2018satisfiability}.
-From practical point of view,
- our experimental results  (in Section \ref{section:evaluation}) show that the current  the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+Solving string constraint with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and our experiments (Section \ref{section:evaluation}) show that state-of-the-art string constraint solvers provide only limited support to string-number conversion.
 
 In this paper, we propose a framework that efficiently handles string constraints with string-number conversion.
-Since the problem is provably unsolvable, our framework combines over and under-approximation techniques.
+Due to the difficulty of solving the problem exactly, our framework combines over and under-approximation of string constraints.
 The over-approximation is for proving UNSAT when possible, while the under-approximation is for proving SAT when possible.
-Both over- and under-approximation fall in a decidable fragment of string constraints that  we can efficiently solve.
-
-%Observe that our main contribution lies in the
+Both over- and under-approximation fall in a decidable fragment of string constraints that can we can efficiently solve.
 
@@
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12"$.
+To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12''$.
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x``12"$ and $y=``1212"$.
-
-Our decision procedure has two steps: the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+E.g., it has a model $x=``12''$ and $y=``1212''$.
+
+Our decision procedure has two steps: the first step is over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Observe that we could  over-approximate the input constraint into any decidable fragment, e.g.
 the acyclic fragment~\cite{abdulla2014string} or the straight-line fragment~\cite{chen2019decision}.
-Our choice of the  chain-free fragment~\cite{abdulla2019chain} is only motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
-In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$  and replacing the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+Our choice of the  chain-free fragment~\cite{abdulla2019chain} is motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
+In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
 The over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
-Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
+For instance, assume in some case, we could derive the value of $n=12$ from some integer constraints.
+Then we could further derive the value of $x$ is in the regular language $(0^*12)$.
 Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
-Surprisingly, despite its simplicity, our over-approximation procedure works very well in practice.
-Coming back to the formula $\Phi$, the over-approximation module will  return SAT  in this case.
+Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
 
@@
 
-The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure restricts the search domain of each string variable to strings that obey some predefined and parameterized pattern.
-To achieve our under-approximation technique (which is  our main contribution),  we propose to use patterns defined by \emph{parametric flat automata} (PFA).
-A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
-The size of the PFA is parameterized by the length of the sequence of loops and the size of each loop.
-Adjusting these parameters enlarges or prunes the potential solution space.
-This approach based on PFA is very flexible yet allows very efficient manipulation.
-In fact, our procedure restricts the search space for each variable to the set of words accepted by the corresponding given PFA.
-
-Then, we show that given such restriction, one can  reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-To gain in efficiency, we label each transition  of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
-This done by associating to each character in our alphabet a unique natural number.
-This allows us to  to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers and it is  the key for handling string-number conversion efficiently.
-
-%The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
+The second step of our decision procedure is only enabled if the over-approximation is SAT.
 In this case, our decision procedure restricts the domain of each string variable to strings that obey some predefined and parameterized pattern.
@@
 We label each transition between two states of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
-%Such reduction based on PFA is the key to handling string-number conversion efficiently.
+Such reduction based on PFA is the key to handling string-number conversion efficiently.
 When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulas and can be solved efficiently.
@@
 Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from the formula $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
+For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
 
@@
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
-The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
+For example, $x=``12''$ and $y=``1212''$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
 
 If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure changes the PFAs to more expressive ones (by adding more states and transitions) to systematically search for a solution.
+If not, our procedure changes the PFAs to be more expressive ones (by adding more states and transitions) to systematically search for a solution.
 Depending on the implementation, one may choose to report unknown after some certain steps.
@@
 
-\item The class of \emph{parametric flat automata} which is the key for efficient handling of string-number conversion constraints.
+\item The introduction of the class of \emph{parametric flat automata} which uses character variables as transition labels instead of characters.
+This allows us to avoid the {alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} when it comes to handle string-number conversion constraints.
 
@@
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x=``12"$ and $y=``1212"$.
+E.g., it has a model $x=``12''$ and $y=``1212''$.
 %
 %For proving UNSAT, our framework does not set any restriction on which decision procedure to use.
-One can select any decision procedure they want to use and ``over-approximate" the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
+One can select any decision procedure they want to use and ``over-approximate'' the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
 For instance, we can convert $xy=yx$ to two formulas $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
@@
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+For example, $x=``12''$ and $y=``1212''$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
 The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12''$.
 %
@@
 %We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
-%We drop the reference to $V$ and write just ``model of $\phi$", $\modelsof \phi$, and $\models$ when no confusion may arise.
+%We drop the reference to $V$ and write just ``model of $\phi$'', $\modelsof \phi$, and $\models$ when no confusion may arise.
 For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
@@
 This is the semantics used by most of the SMT solvers, and hence we follow it in this paper.
-The encoding has a benefit that it can also handle the case where $x$ is ``not a number", using the condition $\sti{x} = -1$.
+The encoding has a benefit that it can also handle the case where $x$ is ``not a number'', using the condition $\sti{x} = -1$.
 
 Supporting only positive integer is not a strong restriction, since conversing from negative integer can still be encoded using the positive only version.
-More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number", which can also be encoded using more conditions):
+More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number'', which can also be encoded using more conditions):
 $$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$. 
-%
-We require that these PFA operate over pairwise disjoint sets of character variables. 
+a \emph{flat domain restriction} for $\insc$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$ \changed{over character variables $V_x$.}
+string %
+We require that these PFA operate over pairwise disjoint sets of character variables\changed{, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.}
 %
@@
 %
-Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
-%
-then its $R$-encoding is defined as the set $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$.
+\changed{
+Further, we define an $R$-encoding for an interpretation $I \cup I'$ of a general string constraint, consiting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables.
+%
+An $R$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding where $e\in \encode R(I)$ and the original integer interpretation $I'$ which satisfies that for every string leght variable $|x|$ in the domain of $I'$,
+$|x| = \sum_{v\in V_x,I(v)\neq\epsilon}\#v$. 
+That is, the interpretation of string variables is encoded as usual, the interpretation of integer variables is kept as is, 
+and for each string legth variable $|x|$ in the domain of $I'$, 
+the value of $|x|$ is consistent with the encoding of $x$ by variables $V_x$ and $\#V_x$.
+The set of all $R$-encodings of $(I\cup I')$ is then denoted $\encode R {(I\cup I')}$}
+%
+%Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
+%%
+%then an $R$-encoding of $I \cup I'$ is any interpretation $e \cup I$ with  $e:V_R \cup \#V_R \cup \Simga_\epsilon$ 
+%such that $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$.
 That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
 %
-We lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
+%
+and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
 %
@@
 %$$ % , to the output linear formulas $\phi_O$. 
-%Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon" transition, i.e., one with the label $v_{\epsilon_i}$.
-%We use $V_\epsilon$ to denote the set of all variables used for ``epsilon" transitions.
+%Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon'' transition, i.e., one with the label $v_{\epsilon_i}$.
+%We use $V_\epsilon$ to denote the set of all variables used for ``epsilon'' transitions.
 %
@@
 For the equality constraint $xy = yx$, assume that we restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon" transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
+In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon'' transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulas $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulas $\phi_O$.
 %
@@
 %
-%In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product" automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
+%In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product'' automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
 %
@@
 Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
-We want an ``easy" completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+We want an ``easy'' completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
 %
@@
 Hence this PFA covers all numerals that encode numbers with at most $m$ digits.
-Although it still has a loop, it will not create any exponential component defining the value of $n$ because the loop only represents a sequence of ``0" at the front of $x$.
+Although it still has a loop, it will not create any exponential component defining the value of $n$ because the loop only represents a sequence of ``0'' at the front of $x$.
 It will not affect the integer value of $n=\sti{x}$.
@@
 It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
-Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily" and completely cover all numerals.
+Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily'' and completely cover all numerals.
 %
@@
 
-%The condition that when $x$ is ``not a number" is specified by the following formula.
+%The condition that when $x$ is ``not a number'' is specified by the following formula.
 %

### 2019-11-21 draft.tex
tiny change

@@
 %
-An $R$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding where $e\in \encode R(I)$ and the original integer interpretation $I'$ which satisfies that for every string leght variable $|x|$ in the domain of $I'$,
+An $R$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding $e\in \encode R(I)$ and the original integer interpretation $I'$ which satisfies that for every string leght variable $|x|$ in the domain of $I'$,
 $|x| = \sum_{v\in V_x,I(v)\neq\epsilon}\#v$. 

### 2019-11-21 draft.tex
some comments to section 5

@@
 \newcommand{\tool}{{\textsf{Z3-PFA}}}
-
+\newcommand{\dr}{\mathcal{R}}
 \newcommand{\nat}{\mathbb{N}}
@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $R$ that assigns to every variable $x\in X$ a PFA $R(x)$ \changed{over character variables $V_x$.}
-string %
-We require that these PFA operate over pairwise disjoint sets of character variables\changed{, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.}
+a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$.
+We require that these PFA operate over pairwise disjoint sets of character variables, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.
 %
 The particular choice of a PFA 
-for each variable  depends on the strategy used in the implementation, and will be discussed in Section~\ref{section:implementation}.
+for each variable  depends on the strategy used in the implementation, and will be discussed in Section~\ref{section:evaluation}.
 %
 The flattening $\outlf$ will be  built inductively to the structure of $\insc$.
-Namely, in the following subsections we show how to build a flattening $\underf R {\phi}$ for every atomic string constraint $\phi$, 
-and for a conjunction of string constraints, we let $\underf R {\phi \land \phi'} \defeq \underf R {\phi} \land \underf R {\phi'}$.
-We then let $\outlf \defeq \underf R \insc$
-
-The semantics of a string constraint $\phi$ restricted by $R$ is then defined as 
-$\semof{\phi}^R = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{R(x)}\}$. 
+Namely, in the following subsections we show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$, 
+and for a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
+We then let $\outlf \defeq \underf \dr \insc$
+
+The semantics of a string constraint $\phi$ restricted by $\dr$ is then defined as 
+$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
 The following sections will be devoted to describing the flattening of the atomic string constraints. 
@@
 \begin{theorem}\label{theorem:correct}
-$\decode R (\semof {\outlf}) = \semof{\insc}_R$ 
+$\decode R (\semof {\outlf}) = \semof{\insc}^\dr$ 
 \end{theorem}
 
-The theorem can be proved by induction to the structure of $\insc$,
-however, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf R \phi$ than just equality of their semantics. 
+The theorem can be proved by a structural induction over $\insc$.
+However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf \dr \phi$ than just equality of their semantics.
+\yfc{I do not understand the previous sentence}
 Particularly, we will need to
- ensure that $\underf R \phi$ captures exactly all $R$-encodings of $\semof \phi^R$
-(indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf R {\phi} \land \underf R {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^R$).
-
-To formalise this correctness argument, we define an additional notation.
+ ensure that $\underf \dr \phi$ captures exactly all $\dr$-encodings of $\semof \phi^\dr$
+(indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf \dr {\phi} \land \underf \dr {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^\dr$).
+
+To formalize this correctness argument, we define an additional notation.
 For an interpretation $I$ of string variables, 
-we define its $R$-encoding as the set $\encode R(I) = \bigcup_{x\in X} \encode \pa(I(x))$ of interpretations of $V_R\cup \#V_R$, containing combinations of interpretations of character variables of each $R(x)$ that encode the $I$.
+we define its $\dr$-encoding as the set $\encode \dr(I) = \bigcup_{x\in X} \encode {\dr(x)} (I(x))$ of interpretations of $V_\dr\cup \#V_\dr$, containing combinations of interpretations of character variables of each $\dr(x)$ that encode the $I$.
+\yfc{the sentence is difficult to parse.
+I did not find the definition of $V_\dr\cup \#V_\dr$.}
 %
 \changed{
-Further, we define an $R$-encoding for an interpretation $I \cup I'$ of a general string constraint, consiting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables.
-%
-An $R$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding $e\in \encode R(I)$ and the original integer interpretation $I'$ which satisfies that for every string leght variable $|x|$ in the domain of $I'$,
+Further, we define an $\dr$-encoding for an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables.
+%
+An $\dr$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding $e\in \encode \dr(I)$ and the original integer interpretation $I'$ which satisfies that for every string length variable $|x|$ in the domain of $I'$,
 $|x| = \sum_{v\in V_x,I(v)\neq\epsilon}\#v$. 
 That is, the interpretation of string variables is encoded as usual, the interpretation of integer variables is kept as is, 
-and for each string legth variable $|x|$ in the domain of $I'$, 
+and for each string length variable $|x|$ in the domain of $I'$, 
 the value of $|x|$ is consistent with the encoding of $x$ by variables $V_x$ and $\#V_x$.
-The set of all $R$-encodings of $(I\cup I')$ is then denoted $\encode R {(I\cup I')}$}
+The set of all $\dr$-encodings of $(I\cup I')$ is then denoted $\encode \dr {(I\cup I')}$}\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
 %
@@
 %
-and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode R (J) = \bigcup_{I \in J}\encode R (I)$ for a set of interpretations $J$.
-%
-The inductive argument needed in the proof of the correctness of the under-approximation then reads as
-$$\semof{\underf R \phi}_{V_R\cup V_{\#R}}  = \encode R{\semof{\phi}}$$ 
+and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
+%
+The inductive argument needed in the correctness proof of the under-approximation then reads as
+$$\semof{\underf \dr \phi}_{V_\dr\cup V_{\#\dr}}  = \encode \dr{\semof{\phi}}$$ 
 %
 In the next sections, 
-we will formulate the corresponding correctness lemma for flattenings constructed from each type of atomic string constraints.
-%
-We note that the restriction of the semantics of $\underf R \phi$ here is needed since $\underf R \phi$ will be constructed with some auxiliary variables.
+we will formulate the corresponding correctness lemma for flattening constructed from each type of atomic string constraints.
+%
+We note that the restriction of the semantics of $\underf \dr \phi$ here is needed since $\underf \dr \phi$ will be constructed with some auxiliary variables.
 

### 2019-11-21 draft.tex
Update draft.tex

--- 2019-11-21 draft.tex
@@
 
-Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed.
+Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a  program, i.e., determining the value of the inputs under which the given path can be executed.
 The path feasibility problem is usually solved by a reduction to the satisfiability of a formula.
@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{?} and Z3Str3 \cite{}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{zheng2013z3}.
 
@@
 While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from extremely limited support by the state-of-the-art string constraint solvers.
-In fact, for many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
-In many security vulnerable codes,  that receive input, tend to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
-\yfc{some grammar error?} For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
+
+For many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
+In fact,  a code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions of the utmost importance to check it.
+For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 

### 2019-11-21 draft.tex
Update draft.tex

@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{zheng2013z3}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{?}.
 
@@
 For many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
-In fact,  a code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions of the utmost importance to check it.
+In fact,  a code that receives input tends to need to convert at least some of that input into numbers,  which makes the handling of string-integer conversions of the utmost importance.
 For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.

### 2019-11-21 draft.tex
small typos

@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{?}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{berzish2017z3str3}.
 

### 2019-11-21 draft.tex
fixing encoding stuff, R to \dr

--- 2019-11-21 draft.tex
@@
 \newcommand{\rightV}{V^{\mathit{right}}}
-\newcommand\renvars{V_R^\mathsf{ver}}
+\newcommand\renvars{V_\dr^\mathsf{ver}}
 
@@
 
-Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a  program, i.e., determining the value of the inputs under which the given path can be executed.
+Symbolic execution is a very popular technique that allows programmers to check the feasibility of a path in a given program, i.e., determining the value of the inputs under which the given path can be executed.
 The path feasibility problem is usually solved by a reduction to the satisfiability of a formula.
@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{?}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{?} and Z3Str3 \cite{}.
 
@@
 While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from extremely limited support by the state-of-the-art string constraint solvers.
-
-For many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
-In fact,  a code that receives input tends to need to convert at least some of that input into numbers,  which makes the handling of string-integer conversions of the utmost importance.
-For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
+In fact, for many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
+In many security vulnerable codes,  that receive input, tend to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
+\yfc{some grammar error?} For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 
@@
 %
-
-Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
-$\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
-%
-Notice that only the words from $L\cap \semof \pa$ have a $\pa$-encoding, 
-hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
+\changed{removed definition of $\encode P (L)$.}
+
+%Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
+%$\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
+%%
+%Notice that only the words from $L\cap \semof \pa$ have a $\pa$-encoding, 
+%hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
 
@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$.
+a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ \changed{ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.}
 We require that these PFA operate over pairwise disjoint sets of character variables, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.
@@
 and for a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
-We then let $\outlf \defeq \underf \dr \insc$
+We then let $\outlf \defeq \underf \dr \insc$.
 
@@
 The theorem can be proved by a structural induction over $\insc$.
-However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf \dr \phi$ than just equality of their semantics.
+However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ then just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.
 \yfc{I do not understand the previous sentence}
+\lh{it is better?}
 Particularly, we will need to
@@
 
-To formalize this correctness argument, we define an additional notation.
-For an interpretation $I$ of string variables, 
-we define its $\dr$-encoding as the set $\encode \dr(I) = \bigcup_{x\in X} \encode {\dr(x)} (I(x))$ of interpretations of $V_\dr\cup \#V_\dr$, containing combinations of interpretations of character variables of each $\dr(x)$ that encode the $I$.
-\yfc{the sentence is difficult to parse.
-I did not find the definition of $V_\dr\cup \#V_\dr$.}
-%
 \changed{
-Further, we define an $\dr$-encoding for an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables.
-%
-An $\dr$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding $e\in \encode \dr(I)$ and the original integer interpretation $I'$ which satisfies that for every string length variable $|x|$ in the domain of $I'$,
-$|x| = \sum_{v\in V_x,I(v)\neq\epsilon}\#v$. 
-That is, the interpretation of string variables is encoded as usual, the interpretation of integer variables is kept as is, 
-and for each string length variable $|x|$ in the domain of $I'$, 
-the value of $|x|$ is consistent with the encoding of $x$ by variables $V_x$ and $\#V_x$.
-The set of all $\dr$-encodings of $(I\cup I')$ is then denoted $\encode \dr {(I\cup I')}$}\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
+To formalize this correctness argument, we need the notion of 
+%
+an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
+%
+An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
+}
+
+The set of all $\dr$-encodings of $(I\cup I')$ is then denoted $\encode \dr {(I\cup I')}$
+%\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
 %
@@
 
-Let us first describe the construction of $\underf R {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
-In order to synchronize the FA $A$ with the PFA $R(x)$, 
+Let us first describe the construction of $\underf \dr {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
+In order to synchronize the FA $A$ with the PFA $\dr(x)$, 
 we represent $A$ by a PA $\pa' = (A',\Psi_{\mathit{char}})$.
@@
 We then let 
-$$\underf R {\phi_r} = \syncfof{R(x)} {\pa'}$$
+$$\underf \dr {\phi_r} = \syncfof{\dr(x)} {\pa'}$$
 
@@
 It follows from Corollary~\ref{corollary:pfa} and Lemma~\ref{lemma:synccorrect}. 
-\begin{lemma}\label{lemma:memcorrect}  $\semof {\underf R {\phi_r}}_{V_R \cup V_{\#R}} = \encode {R} (\semof{\phi_r})$ . 
+\begin{lemma}\label{lemma:memcorrect}  $\semof {\underf \dr {\phi_r}}_{V_\dr \cup \#V_{\dr}} = \encode {\dr} (\semof{\phi_r})$ . 
 \end{lemma}
@@
 
-We now describe the construction of $\underf R {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$. 
+We now describe the construction of $\underf \dr {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$. 
 %
@@
 \begin{eqnarray*}
-\leftA \defeq& R(x_1)\cdot\ldots \cdot R(x_n)\\
-\rightA \defeq& R(x_{n+1})\cdot\ldots \cdot R(x_m)
+\leftA \defeq& \dr(x_1)\cdot\ldots \cdot \dr(x_n)\\
+\rightA \defeq& \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)
 \end{eqnarray*}
@@
 $$
-\underf R {\phi_e} = \syncfof \leftA \rightA
+\underf \dr {\phi_e} = \syncfof \leftA \rightA
 $$
@@
 \begin{lemma}\label{lemma:eqcorrect}
-$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
+$\semof {\underf \dr {\phi_e}}_{V_\dr  \cup \#V_\dr} = \encode \dr (\semof{\phi_e})$.
 \end{lemma}
@@
 \subsection{Flattening of Integer Constraints}
+\changed{
+\newcommand{\lx}{l_x}
+\newcommand{\lv}{l_v}
 Length constraints are encoded precisely by flattening, not under-approximated. 
-Given a length constraint $\phi_l$ that talks about string length variables $|x|,x\in X$, 
-we keep $\phi_l$ as is and add a formula to express the lengths of strings $|x|$ in terms of character variables $V_x$ and Parikh variables $\# V_x$ of $R(x)$.
-
-For every length variable $|x|\in X$, 
-we add a set of fresh auxiliary variables $\{|v|\mid v\in V_x\}$ to express the length by which $v$ contributes to the length of an $R$-encoded word. 
-That is, $|v|$ will be $0$ if $v$ is assigned $\noepsilon$,
+Given a length constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
+We use a version of $\phi_l$ where every occurence of every leght term $|x|$ is replaced by an auxiliary lenght variable $\lx$ and add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
+%
+%For every length variable $x\in X$, we add an auxiliary variable $\lx$ that records the length of $x$,   
+We will need a set auxiliary variables $\{l_v\mid v\in V_x\}$ to express the length by which the character variable $v$ contributes to the length of an $\dr$-encoded string $x$. 
+That is, $\lv$ will be $0$ if $v$ is assigned $\noepsilon$,
 otherwise it will equal the number $\#v$ of its occurrences in the word:
 $$
-\Psi_{\mathsf{|v|}} \defeq (v = \noepsilon \land |v|=0) \lor (v \neq \noepsilon \land |v| = \# v)
+\Psi_{\lv} \defeq (v = \noepsilon \land l_v=0) \lor (v \neq \noepsilon \land l_v = \# v)
 $$
@@
 $$
-\Psi_{|x|} \defeq |x| = \sum_{v\in V_x} |v| \land  \bigwedge_{v\in V_x} \Psi_{\mathsf{|v|}}\ .
+\Psi_{\lx} \defeq \lx = \sum_{v\in V_x} l_v \land  \bigwedge_{v\in V_x} \Psi_{\lv}\ .
 $$
@@
 $$
-\underf R {\phi_{l}} \defeq \phi_l \land \bigwedge_{|x|\in X} \Psi_{|x|}
+\underf \dr {\phi_{l}} \defeq \phi_l \land \bigwedge_{x\in X} \Psi_{\lx}
 $$
 and the following lemma states its correctness.
+}
 \begin{lemma}\label{lemma:eqcorrect}
-$\semof {\underf R {\phi_l}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_l})$
+$\semof {\underf \dr {\phi_l}}_{V_\dr  \cup \#V_\dr} = \encode \dr (\semof{\phi_l})$
 \end{lemma}
@@
 Last, we a major contribution of this paper, 
-the construction of a flattening $\underf R {\phi_s}$ of string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
+the construction of a flattening $\underf \dr {\phi_s}$ of string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
 
@@
 
-It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
+It is not difficult to see from the examples above that, if $\dr(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 We therefore do not expect that such constraint can be solved efficiently.
-Instead, we will define a special form of the flat restriction $R(x)$ of $x$ that leads to an easies linear formula.
+Instead, we will define a special form of the flat restriction $\dr(x)$ of $x$ that leads to an easies linear formula.
 
@@
 %An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving. 
-We will now discuss the special form of $R(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints that leads to efficient underapproximation.
-%
-Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
+We will now discuss the special form of $\dr(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints that leads to efficient underapproximation.
+%
+Besides simple induced linear formulae, we still want single $\dr(x)$ to cover as many numerals as possible.
 We want an ``easy" completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
@@
 $$
-Consequently, we design our domain restrictions $R$ so that for string variables $x$ that appear within string-integer constraints,  $R(x)$ is a number PFA $(A^m,\paf^m),m\in \nat$.
+Consequently, we design our domain restrictions $\dr$ so that for string variables $x$ that appear within string-integer constraints,  $\dr(x)$ is a number PFA $(A^m,\paf^m),m\in \nat$.
 
@@
 \begin{multline*}
-\underf R {\phi_s} 
+\underf \dr {\phi_s} 
 \defeq 
@@
 $
-\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R(\semof{\phi_s})
+\semof {\underf \dr {\psi_s} }_{V_\dr \cup \#V_\dr \cup \{n\}} = \encode  \dr(\semof{\phi_s})
 $

### 2019-11-21 draft.tex

@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{?}, OSTRICH \cite{}, Sloth \cite{},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{?} and Z3Str3 \cite{}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{berzish2017z3str3}.
 
@@
 While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from extremely limited support by the state-of-the-art string constraint solvers.
-In fact, for many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
-In many security vulnerable codes,  that receive input, tend to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
-\yfc{some grammar error?} For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
+
+For many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
+In fact,  a code that receives input tends to need to convert at least some of that input into numbers,  which makes the handling of string-integer conversions of the utmost importance.
+For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 

### 2019-11-21 draft.tex
Update draft.tex

--- 2019-11-21 draft.tex
@@
 In fact,  a code that receives input tends to need to convert at least some of that input into numbers,  which makes the handling of string-integer conversions of the utmost importance.
-For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
+For example, the program fragment below is a variant of the Luhn test algorithm that is often used in credit card or personal ID validation.
 
@@
 The input \verb|value| of the Luhn test algorithm is a sequence of digits.
-The algorithm process the digits in the reversed order.
+The algorithm processes the digits in the reversed order.
 The value of every odd digit (e.g., 1st, 3rd, etc.) is added to \verb|sum| directly.
-For the value of every even digit, the algorithm (1) doubles its value, (2) subtracts its value by $9$ if the doubled-value is bigger than $9$, and (3) adds the final result to \verb|sum|.
+For the value of every even digit, the algorithm (1) doubles its value, (2) subtracts its value by $9$ if the doubled-value is larger than $9$, and (3) adds the final result to \verb|sum|.
 At the end, the input is validated if the string value of \verb|sum| ends by an $0$ (i.e., \verb| sum mod 10=0|).
 
-To check whether the program path that traverses both loop exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
+To check whether the program path that traverses both loops exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
 

### 2019-11-21 draft.tex
minor

--- 2019-11-21 draft.tex
@@
 We will use four types of \emph{atomic string constraint}: 
-
-An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
+\smallskip
+
+$\bullet$ An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
 t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
@@
 
-An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a word $|x|$ for all $x \in \vars$.
+\smallskip
+$\bullet$ An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and values of $|x|$ for all $x \in \vars$, where $|\cdot|:\vars \rightarrow \nat$ is the string length function defined in the standard way.
 %Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
@@
 We define $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$. 
-\lh{should we somehow define the sematntics of the lengt constraints more precisely? That is, how is the value of $|x|$ related to the value of $x$. ?}
-
-A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
+\smallskip
+
+$\bullet$ A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
 The \emph{model} of $\phi_m$ is the set of interpretations $\modelsof{\phi_m}=\{I\mid
 I(x) \in L(A) \}$. 
-
-A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
+\smallskip
+
+$\bullet$ A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
 For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$.
@@
 The \emph{number-string} conversion constraint $x=\its{n}$ is treated as a syntactic sugar for $n=\sti{x}$.
+\smallskip
 
@@
 	\node[state] (q13) [above right = 0.6cm of q1] {$\st{1}{l_1}$};
-	\node   (m2) [above right = -0.4cm and -0.3cm of q13] {$\ ^{-1}$};
+	\node   (m2) [above right = -0.4cm and -0.25cm of q13] {$\ ^{-1}$};
 
@@
 	\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{l_m}$};
-	\node   (mm) [above right = -0.4cm and -0.3cm of qm3] {$\ ^{-1}$};
+	\node   (mm) [above right = -0.45cm and -0.2cm of qm3] {$\ ^{-1}$};
 
@@
 %
-\changed{removed definition of $\encode P (L)$.}
+%\changed{removed definition of $\encode P (L)$.}
 
@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ \changed{ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.}
+a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.
 We require that these PFA operate over pairwise disjoint sets of character variables, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.
@@
 \begin{theorem}\label{theorem:correct}
-$\decode R (\semof {\outlf}) = \semof{\insc}^\dr$ 
+$\decode \dr (\semof {\outlf}) = \semof{\insc}^\dr$ 
 \end{theorem}
@@
 However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ then just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.
-\yfc{I do not understand the previous sentence}
-\lh{it is better?}
 Particularly, we will need to

### 2019-11-21 draft.tex
aaaarghh

--- 2019-11-21 draft.tex
@@
 In fact,  a code that receives input tends to need to convert at least some of that input into numbers,  which makes the handling of string-integer conversions of the utmost importance.
-For example, the program fragment below is a variant of the Luhn test algorithm that is often used in credit card or personal ID validation.
+For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 
@@
 The input \verb|value| of the Luhn test algorithm is a sequence of digits.
-The algorithm processes the digits in the reversed order.
+The algorithm process the digits in the reversed order.
 The value of every odd digit (e.g., 1st, 3rd, etc.) is added to \verb|sum| directly.
-For the value of every even digit, the algorithm (1) doubles its value, (2) subtracts its value by $9$ if the doubled-value is larger than $9$, and (3) adds the final result to \verb|sum|.
+For the value of every even digit, the algorithm (1) doubles its value, (2) subtracts its value by $9$ if the doubled-value is bigger than $9$, and (3) adds the final result to \verb|sum|.
 At the end, the input is validated if the string value of \verb|sum| ends by an $0$ (i.e., \verb| sum mod 10=0|).
 
-To check whether the program path that traverses both loops exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
+To check whether the program path that traverses both loop exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
 
@@
 The following sections will be devoted to describing the flattening of the atomic string constraints.
-The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}:
+
+The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
+It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
+For an interpretation $e \cup I'$ consisting of an interpretaton $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation fo integer variavles $I'$, we let $\decode \dr (e\cup I') = (I \cup I')$ where $I$ is the interpretation of string variables such that for each $x\in X$,
+$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
+That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the $\decode {\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
+We lift $\decode \dr$ to sets of interpretations in the standard manner.
 \begin{theorem}\label{theorem:correct}
@@
 
-\changed{
-To formalize this correctness argument, we need the notion of 
-%
-an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
-%
-An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
-}
-
-The set of all $\dr$-encodings of $(I\cup I')$ is then denoted $\encode \dr {(I\cup I')}$
+%To formalize this correctness argument, we need the notion of 
+%%
+%an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
+%%
+%An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
+
+To formalize this correctness argument, we define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
+%
+namely, for a set $J$ of string/integer variables interpretations,  
+we let $\encode \dr (J) \defeq \{e\mid \decode \dr (e) \in J\}$.
 %\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
@@
 %
-and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
+%and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
 %

### 2019-11-21 draft.tex
add overapproximation section
typos

@@
 It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
-For an interpretation $e \cup I'$ consisting of an interpretaton $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation fo integer variavles $I'$, we let $\decode \dr (e\cup I') = (I \cup I')$ where $I$ is the interpretation of string variables such that for each $x\in X$,
+For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variavles $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
 $I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
-That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the $\decode {\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
+That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the ${\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
 We lift $\decode \dr$ to sets of interpretations in the standard manner.

### 2019-11-21 draft.tex
added citations

--- 2019-11-21 draft.tex
@@
 \newcommand{\rightV}{V^{\mathit{right}}}
-\newcommand\renvars{V_\dr^\mathsf{ver}}
+\newcommand\renvars{V_R^\mathsf{ver}}
 
@@
 %
-\changed{removed definition of $\encode P (L)$.}
-
-%Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
-%$\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
-%%
-%Notice that only the words from $L\cap \semof \pa$ have a $\pa$-encoding, 
-%hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
+
+Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
+$\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
+%
+Notice that only the words from $L\cap \semof \pa$ have a $\pa$-encoding, 
+hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
 
@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ \changed{ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.}
+a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$.
 We require that these PFA operate over pairwise disjoint sets of character variables, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.
@@
 and for a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
-We then let $\outlf \defeq \underf \dr \insc$.
+We then let $\outlf \defeq \underf \dr \insc$
 
@@
 The following sections will be devoted to describing the flattening of the atomic string constraints. 
-
-The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
-It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
-For an interpretation $e \cup I'$ consisting of an interpretaton $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation fo integer variavles $I'$, we let $\decode \dr (e\cup I') = (I \cup I')$ where $I$ is the interpretation of string variables such that for each $x\in X$,
-$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
-That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the $\decode {\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
-We lift $\decode \dr$ to sets of interpretations in the standard manner.
+The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}:
 \begin{theorem}\label{theorem:correct}
@@
 The theorem can be proved by a structural induction over $\insc$.
-However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ then just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.
+However, for the induction step to go through, we will need a more meticulous view into the correspondence of $\phi$ and $\underf \dr \phi$ than just equality of their semantics.
 \yfc{I do not understand the previous sentence}
-\lh{it is better?}
 Particularly, we will need to
@@
 
-%To formalize this correctness argument, we need the notion of 
-%%
-%an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
-%%
-%An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
-
-To formalize this correctness argument, we define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
-%
-namely, for a set $J$ of string/integer variables interpretations,  
-we let $\encode \dr (J) \defeq \{e\mid \decode \dr (e) \in J\}$.
-%\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
+To formalize this correctness argument, we define an additional notation.
+For an interpretation $I$ of string variables, 
+we define its $\dr$-encoding as the set $\encode \dr(I) = \bigcup_{x\in X} \encode {\dr(x)} (I(x))$ of interpretations of $V_\dr\cup \#V_\dr$, containing combinations of interpretations of character variables of each $\dr(x)$ that encode the $I$.
+\yfc{the sentence is difficult to parse.
+I did not find the definition of $V_\dr\cup \#V_\dr$.}
+%
+\changed{
+Further, we define an $\dr$-encoding for an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables.
+%
+An $\dr$-encoding of $I \cup I'$ is a union  $e \cup I'$ of an encoding $e\in \encode \dr(I)$ and the original integer interpretation $I'$ which satisfies that for every string length variable $|x|$ in the domain of $I'$,
+$|x| = \sum_{v\in V_x,I(v)\neq\epsilon}\#v$. 
+That is, the interpretation of string variables is encoded as usual, the interpretation of integer variables is kept as is, 
+and for each string length variable $|x|$ in the domain of $I'$, 
+the value of $|x|$ is consistent with the encoding of $x$ by variables $V_x$ and $\#V_x$.
+The set of all $\dr$-encodings of $(I\cup I')$ is then denoted $\encode \dr {(I\cup I')}$}\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
 %
@@
 %
-%and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
+and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
 %
@@
 
-Let us first describe the construction of $\underf \dr {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
-In order to synchronize the FA $A$ with the PFA $\dr(x)$, 
+Let us first describe the construction of $\underf R {\phi_r}$ for a regular constraint $\phi_r \defeq x \in L(A)$. 
+In order to synchronize the FA $A$ with the PFA $R(x)$, 
 we represent $A$ by a PA $\pa' = (A',\Psi_{\mathit{char}})$.
@@
 We then let 
-$$\underf \dr {\phi_r} = \syncfof{\dr(x)} {\pa'}$$
+$$\underf R {\phi_r} = \syncfof{R(x)} {\pa'}$$
 
@@
 It follows from Corollary~\ref{corollary:pfa} and Lemma~\ref{lemma:synccorrect}. 
-\begin{lemma}\label{lemma:memcorrect}  $\semof {\underf \dr {\phi_r}}_{V_\dr \cup \#V_{\dr}} = \encode {\dr} (\semof{\phi_r})$ . 
+\begin{lemma}\label{lemma:memcorrect}  $\semof {\underf R {\phi_r}}_{V_R \cup V_{\#R}} = \encode {R} (\semof{\phi_r})$ . 
 \end{lemma}
@@
 
-We now describe the construction of $\underf \dr {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$. 
+We now describe the construction of $\underf R {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$. 
 %
@@
 \begin{eqnarray*}
-\leftA \defeq& \dr(x_1)\cdot\ldots \cdot \dr(x_n)\\
-\rightA \defeq& \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)
+\leftA \defeq& R(x_1)\cdot\ldots \cdot R(x_n)\\
+\rightA \defeq& R(x_{n+1})\cdot\ldots \cdot R(x_m)
 \end{eqnarray*}
@@
 $$
-\underf \dr {\phi_e} = \syncfof \leftA \rightA
+\underf R {\phi_e} = \syncfof \leftA \rightA
 $$
@@
 \begin{lemma}\label{lemma:eqcorrect}
-$\semof {\underf \dr {\phi_e}}_{V_\dr  \cup \#V_\dr} = \encode \dr (\semof{\phi_e})$.
+$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
 \end{lemma}
@@
 \subsection{Flattening of Integer Constraints}
-\changed{
-\newcommand{\lx}{l_x}
-\newcommand{\lv}{l_v}
 Length constraints are encoded precisely by flattening, not under-approximated. 
-Given a length constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
-We use a version of $\phi_l$ where every occurence of every leght term $|x|$ is replaced by an auxiliary lenght variable $\lx$ and add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
-%
-%For every length variable $x\in X$, we add an auxiliary variable $\lx$ that records the length of $x$,   
-We will need a set auxiliary variables $\{l_v\mid v\in V_x\}$ to express the length by which the character variable $v$ contributes to the length of an $\dr$-encoded string $x$. 
-That is, $\lv$ will be $0$ if $v$ is assigned $\noepsilon$,
+Given a length constraint $\phi_l$ that talks about string length variables $|x|,x\in X$, 
+we keep $\phi_l$ as is and add a formula to express the lengths of strings $|x|$ in terms of character variables $V_x$ and Parikh variables $\# V_x$ of $R(x)$.
+
+For every length variable $|x|\in X$, 
+we add a set of fresh auxiliary variables $\{|v|\mid v\in V_x\}$ to express the length by which $v$ contributes to the length of an $R$-encoded word. 
+That is, $|v|$ will be $0$ if $v$ is assigned $\noepsilon$,
 otherwise it will equal the number $\#v$ of its occurrences in the word:
 $$
-\Psi_{\lv} \defeq (v = \noepsilon \land l_v=0) \lor (v \neq \noepsilon \land l_v = \# v)
+\Psi_{\mathsf{|v|}} \defeq (v = \noepsilon \land |v|=0) \lor (v \neq \noepsilon \land |v| = \# v)
 $$
@@
 $$
-\Psi_{\lx} \defeq \lx = \sum_{v\in V_x} l_v \land  \bigwedge_{v\in V_x} \Psi_{\lv}\ .
+\Psi_{|x|} \defeq |x| = \sum_{v\in V_x} |v| \land  \bigwedge_{v\in V_x} \Psi_{\mathsf{|v|}}\ .
 $$
@@
 $$
-\underf \dr {\phi_{l}} \defeq \phi_l \land \bigwedge_{x\in X} \Psi_{\lx}
+\underf R {\phi_{l}} \defeq \phi_l \land \bigwedge_{|x|\in X} \Psi_{|x|}
 $$
 and the following lemma states its correctness.
-}
 \begin{lemma}\label{lemma:eqcorrect}
-$\semof {\underf \dr {\phi_l}}_{V_\dr  \cup \#V_\dr} = \encode \dr (\semof{\phi_l})$
+$\semof {\underf R {\phi_l}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_l})$
 \end{lemma}
@@
 Last, we a major contribution of this paper, 
-the construction of a flattening $\underf \dr {\phi_s}$ of string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
+the construction of a flattening $\underf R {\phi_s}$ of string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
 
@@
 
-It is not difficult to see from the examples above that, if $\dr(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
+It is not difficult to see from the examples above that, if $R(x)$ is an arbitrary PFA with $m$ loops, the formula that defines the number $n$ contains at least $m$ exponential components, one for each loop.
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
@@
 We therefore do not expect that such constraint can be solved efficiently.
-Instead, we will define a special form of the flat restriction $\dr(x)$ of $x$ that leads to an easies linear formula.
+Instead, we will define a special form of the flat restriction $R(x)$ of $x$ that leads to an easies linear formula.
 
@@
 %An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving. 
-We will now discuss the special form of $\dr(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints that leads to efficient underapproximation.
-%
-Besides simple induced linear formulae, we still want single $\dr(x)$ to cover as many numerals as possible.
+We will now discuss the special form of $R(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints that leads to efficient underapproximation.
+%
+Besides simple induced linear formulae, we still want single $R(x)$ to cover as many numerals as possible.
 We want an ``easy" completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
@@
 $$
-Consequently, we design our domain restrictions $\dr$ so that for string variables $x$ that appear within string-integer constraints,  $\dr(x)$ is a number PFA $(A^m,\paf^m),m\in \nat$.
+Consequently, we design our domain restrictions $R$ so that for string variables $x$ that appear within string-integer constraints,  $R(x)$ is a number PFA $(A^m,\paf^m),m\in \nat$.
 
@@
 \begin{multline*}
-\underf \dr {\phi_s} 
+\underf R {\phi_s} 
 \defeq 
@@
 $
-\semof {\underf \dr {\psi_s} }_{V_\dr \cup \#V_\dr \cup \{n\}} = \encode  \dr(\semof{\phi_s})
+\semof {\underf R {\psi_s} }_{V_R \cup \#V_R \cup \{n\}} = \encode  R(\semof{\phi_s})
 $
@@
 \paragraph{Related works:} 
-Already in 1946, Quine \cite{Quine46} showed that the first order theory
+Already in 1946, Quine \cite{quine1946concatenation} showed that the first order theory
 of string equations is undecidable.
@@
 %
-The pioneering work by Makanin \cite{makanin} proposed a decision
+The pioneering work by Makanin \cite{makanin1977problem} proposed a decision
 procedure for quantifier-free word equations, i.e., Boolean combinations of
@@
 have been considered by several works, e.g.
-\cite{Plandowski99,Plandowski06,Matiyasevich08,Robson90,Schulz90,Ganesh13decide,DBLP:journals/corr/GaneshB16}.
+\cite{plandowski1999satisfiability,plandowski2006efficient,matiyasevich2008computation,robson1999quadratic,schulz1990makanin,ganesh2012word,ganesh2016undecidability}.
 Generalizations of the work of Makanin by adding
@@
 constraints of the form $\left|x\right|=\left|y\right|$ is open
-\cite{buchi:definability}.
+\cite{buchi1990definability}.
 %
@@
 %
-Adding these to the mix leads immediately to undecidability \cite{morvan}
-%
-and hence numerous decidable fragments were proposed \cite{string14,BFL13,BL16,Chen:2018,Chen:2019}. 
-%
-From these, the straight line fragment of \cite{BL16} is the most general decidable combination of concatenation and transducers.
-It is however incomparable to the acyclic fragment of \cite{string14} (which does not have transducers but could be extended with them in a straightforward manner).
-%
-Some works add also other syntactic features, such as \cite{Chen:2018,Chen:2019}, 
-but the limit of decidable combinations of the core string features---transducers/regular constraints, length constraints, and concatenation stays at \cite{BL16} and \cite{string14}.
+Adding these to the mix leads immediately to undecidability \cite{morvan2000rational}
+%
+and hence numerous decidable fragments were proposed \cite{abdulla2014string,barcelo2013graph,lin2016string,chen2017decidable,chen2019decision}. 
+%
+From these, the straight line fragment of \cite{lin2016string} is the most general decidable combination of concatenation and transducers.
+It is however incomparable to the acyclic fragment of \cite{abdulla2014string} (which does not have transducers but could be extended with them in a straightforward manner).
+%
+Some works add also other syntactic features, such as \cite{chen2017decidable,chen2019decision}, 
+but the limit of decidable combinations of the core string features---transducers/regular constraints, length constraints, and concatenation stays at \cite{lin2016string} and \cite{abdulla2014string}.
 %
@@
 translation to
-bit-vectors~\cite{Kiezun09hampi,Saxena10:kaluza,saxena:flax}, assuming
+bit-vectors~\cite{kiezun2009hampi,saxena2010symbolic,saxena2010flax}, assuming
 a fixed upper bound on the length of the possible solutions. 
@@
 restriction of strings of bounded length; this generation of solvers
-includes Z3-str3 \cite{Berzish2017Z3str3AS}, Z3-str2~\cite{Zheng13z3str}, 
-CVC4~\cite{LiaEtAl-CAV-14}, S3P~\cite{trinh2014:s3,Trinh2016},
-Norn~\cite{norn15}, 
-Trau~\cite{trau18}, 
+includes Z3-str3 \cite{berzish2017z3str3}, Z3-str2~\cite{zheng2017z3str2}, 
+CVC4~\cite{cvc4Tool}, S3P~\cite{trinh2014s3,trinh2016progressive},
+Norn~\cite{abdulla2015norn}, 
+Trau~\cite{abdulla2018trau}, 
 Sloth~\cite{sloth}, 
 and 
-Ostrich~\cite{Chen:2019}. DPLL(T)-based solvers
+Ostrich~\cite{chen2019decision}. DPLL(T)-based solvers
 handle a variety of string constraints, including word equations, regular expression membership, length constraints, and (more rarely)
@@
 %
-Our implementation is combining strong completeness guarantees of \cite{sloth} extended to handle the fragment proposed in this paper with an efficient approximation techniques of \cite{trau18} 
+Our implementation is combining strong completeness guarantees of \cite{sloth} extended to handle the fragment proposed in this paper with an efficient approximation techniques of \cite{abdulla2018trau}
 and its performance on existing benchmarks compares favourably with the most efficient of the above tools.
@@
 A further direction is {\it automata-based} solvers for analyzing
-string-manipulated programs. Stranger~\cite{fangyu:stranger} soundly
+string-manipulated programs. Stranger~\cite{yu2010stranger} soundly
 over-approximates string constraints using regular languages, and
 outperforms DPLL(T)-based solvers when checking single execution
-traces, according to some evaluations~\cite{KauslerS14}. It has
-recently also been observed~\cite{DBLP:conf/cav/WangTLYJ16,sloth} that
+traces, according to some evaluations~\cite{kausler2014evaluation}. It has
+recently also been observed~\cite{wang2016string,sloth} that
 automata-based algorithms can be combined with model checking

### 2019-11-21 draft.tex
Update draft.tex

--- 2019-11-21 draft.tex
@@
 Lines 2-4 and lines 5-7 describe one execution of the first and second loop, respectively.
-Line 8 describes the condition of $i_2$ before leaving the loop.
+Line 8 describes the condition on $i_2$ before leaving the loop.
 Finally, Lines 9-10 describe the condition that the last digit of $sum$ is zero.
@@
 
-Even, more crucially, in many programming languages, the conversion between strings and integers is a part of the definition of the core semantics of the language. 
+Even, more crucially, in many programming languages, string-number conversion is a part of the definition of the core semantics of the language. 
  JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, is one of such languages.
@@
 This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
-Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
+Therefore, any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
 Consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic and frequently used  array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
+This is a rather basic   array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
 Thus, we need stronger solvers that are  able to handle string-number conversion operations in order to be able to analyse  real code.
@@
 
-For ease of presentation, we will use the following toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
+For ease of presentation, we  use the following toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
 
@@
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x``12"$ and $y=``1212"$.
+E.g., it has a model $x=``12"$ and $y=``1212"$.
 
@@
 Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
-Surprisingly, despite its simplicity, our over-approximation procedure works very well in practice.
+Surprisingly, despite its simplicity, our over-approximation procedure works very well in practice as shown by our experimental results  (in Section \ref{section:evaluation}).
 Coming back to the formula $\Phi$, the over-approximation module will  return SAT  in this case.
@@
 The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure restricts the search domain of each string variable to strings that obey some predefined and parameterized pattern.
-To achieve our under-approximation technique (which is  our main contribution),  we propose to use patterns defined by \emph{parametric flat automata} (PFA).
+In this case, our decision procedure uses an under-approximation technique (which is  our main contribution) to restrict the search domain of each string variable to strings that obey some predefined and parameterized pattern.
+We propose to use patterns defined by \emph{parametric flat automata} (PFA).
 A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
@@
 Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from the formula $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
+For example, from  $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
 
@@
 If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure changes the PFAs to more expressive ones (by adding more states and transitions) to systematically search for a solution.
-Depending on the implementation, one may choose to report unknown after some certain steps.
+If not, our procedure changes the PFAs to a more expressive one (by adding more states and transitions) and repeat the analysis.
+We report unknown after failing to prove SAT using a certain number of PFAs.
 
@@
 \item An {\em efficient} procedure for checking satisfiability
-of string constraints with string-number conversion constraints.
-
-\item The class of \emph{parametric flat automata} which is the key for efficient handling of string-number conversion constraints.
-
-\item An algorithm that translates the satisfiability string constraints to the satisfiability of a linear formula  in polynomial-time when  the search space restricted by PFAs.
+of string constraints with string-number conversion.
+
+\item The class of \emph{parametric flat automata} which is the key for efficient handling of string constraints.
+
+\item An algorithm that translates the satisfiability problem of string constraints to the satisfiability problem of a linear formula  in polynomial-time when  the search space restricted by PFAs.
 
@@
 \end{itemize}
+
+\paragraph{Outline.}
+After recalling the  definition in Section \ref{section:sc}. 
+Section \ref{section:sfa} presents  the class of parametric flat automata. 
+Section \ref{section:under_approximate} describes how to use PFA to restrict the searching domain of string variables.
+Section \ref{sec:flattening} shows how to construct the linear formula for  basic string constraints (i.e., 
+regular, equality, and integer constraints). 
+ Section \ref{section:s2i} presents the construction of the linear formula for string-number conversion operations.
+Finally, Section \ref{section:evaluation} presents the details of our implementation and our experimental results.
 
@@
 We will use four types of \emph{atomic string constraint}:
-\smallskip
-
-$\bullet$ An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
+
+An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
 t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
@@
 
-\smallskip
-$\bullet$ An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and values of $|x|$ for all $x \in \vars$, where $|\cdot|:\vars \rightarrow \nat$ is the string length function defined in the standard way.
+An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and length of a word $|x|$ for all $x \in \vars$.
 %Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
@@
 We define $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$. 
-\smallskip
-
-$\bullet$ A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
+\lh{should we somehow define the sematntics of the lengt constraints more precisely? That is, how is the value of $|x|$ related to the value of $x$. ?}
+
+A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
 The \emph{model} of $\phi_m$ is the set of interpretations $\modelsof{\phi_m}=\{I\mid
 I(x) \in L(A) \}$.
-\smallskip
-
-$\bullet$ A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
+
+A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
 For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$.
@@
 The \emph{number-string} conversion constraint $x=\its{n}$ is treated as a syntactic sugar for $n=\sti{x}$.
-\smallskip
 
@@
 	\node[state] (q13) [above right = 0.6cm of q1] {$\st{1}{l_1}$};
-	\node   (m2) [above right = -0.4cm and -0.25cm of q13] {$\ ^{-1}$};
+	\node   (m2) [above right = -0.4cm and -0.3cm of q13] {$\ ^{-1}$};
 
@@
 	\node[state] (qm3) [above right = 0.6cm of qm] {$\st{m}{l_m}$};
-	\node   (mm) [above right = -0.45cm and -0.2cm of qm3] {$\ ^{-1}$};
+	\node   (mm) [above right = -0.4cm and -0.3cm of qm3] {$\ ^{-1}$};
 
@@
 %
-%\changed{removed definition of $\encode P (L)$.}
+\changed{removed definition of $\encode P (L)$.}
 
@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.
+a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ \changed{ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.}
 We require that these PFA operate over pairwise disjoint sets of character variables, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.
@@
 The following sections will be devoted to describing the flattening of the atomic string constraints. 
-
-The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
-It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
-For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variavles $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
-$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
-That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the ${\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
-We lift $\decode \dr$ to sets of interpretations in the standard manner.
+The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}:
 \begin{theorem}\label{theorem:correct}
-$\decode \dr (\semof {\outlf}) = \semof{\insc}^\dr$ 
+$\decode R (\semof {\outlf}) = \semof{\insc}^\dr$ 
 \end{theorem}
@@
 However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ then just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.
+\yfc{I do not understand the previous sentence}
+\lh{it is better?}
 Particularly, we will need to
@@
 
-%To formalize this correctness argument, we need the notion of 
-%%
-%an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
-%%
-%An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
-
-To formalize this correctness argument, we define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
-%
-namely, for a set $J$ of string/integer variables interpretations,  
-we let $\encode \dr (J) \defeq \{e\mid \decode \dr (e) \in J\}$.
+\changed{
+To formalize this correctness argument, we need the notion of 
+%
+an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
+%
+An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
+}
+
+The set of all $\dr$-encodings of $(I\cup I')$ is then denoted $\encode \dr {(I\cup I')}$
 %\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
@@
 \section{Flattening of Basic String Constraints}
+\label{sec:flattening}
 We will first discuss flattening of the basic string constraints, that is,

### 2019-11-21 draft.tex
removed double reference to the same paper

@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{berzish2017z3str3}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,abdulla2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{berzish2017z3str3}.
 
@@
 
-%For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
+%For over-approximation, there are a few existing algorithms~\cite{abdulla2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
 In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
-In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
+In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{abdulla2019chain}.
 

### 2019-11-21 draft.tex
add over-approximation

--- 2019-11-21 draft.tex
@@
 Lines 2-4 and lines 5-7 describe one execution of the first and second loop, respectively.
-Line 8 describes the condition on $i_2$ before leaving the loop.
+Line 8 describes the condition of $i_2$ before leaving the loop.
 Finally, Lines 9-10 describe the condition that the last digit of $sum$ is zero.
@@
 
-Even, more crucially, in many programming languages, string-number conversion is a part of the definition of the core semantics of the language. 
+Even, more crucially, in many programming languages, the conversion between strings and integers is a part of the definition of the core semantics of the language. 
  JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, is one of such languages.
@@
 This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
-Therefore, any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
+Any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
 Consider the following code snippet that manipulates an array \texttt{x}, with its value shown on the right:
@@
 Even for a simple example like this, the conversion between string and number is unavoidable.
-This is a rather basic   array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
+This is a rather basic and frequently used  array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
 Thus, we need stronger solvers that are  able to handle string-number conversion operations in order to be able to analyse  real code.
@@
 
-For ease of presentation, we  use the following toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
+For ease of presentation, we will use the following toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
 
@@
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x=``12"$ and $y=``1212"$.
+E.g., it has a model $x``12"$ and $y=``1212"$.
 
@@
 Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
-Surprisingly, despite its simplicity, our over-approximation procedure works very well in practice as shown by our experimental results  (in Section \ref{section:evaluation}).
+Surprisingly, despite its simplicity, our over-approximation procedure works very well in practice.
 Coming back to the formula $\Phi$, the over-approximation module will  return SAT  in this case.
@@
 The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure uses an under-approximation technique (which is  our main contribution) to restrict the search domain of each string variable to strings that obey some predefined and parameterized pattern.
-We propose to use patterns defined by \emph{parametric flat automata} (PFA).
+In this case, our decision procedure restricts the search domain of each string variable to strings that obey some predefined and parameterized pattern.
+To achieve our under-approximation technique (which is  our main contribution),  we propose to use patterns defined by \emph{parametric flat automata} (PFA).
 A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
@@
 Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from  $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
+For example, from the formula $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
 
@@
 If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure changes the PFAs to a more expressive one (by adding more states and transitions) and repeat the analysis.
-We report unknown after failing to prove SAT using a certain number of PFAs.
+If not, our procedure changes the PFAs to more expressive ones (by adding more states and transitions) to systematically search for a solution.
+Depending on the implementation, one may choose to report unknown after some certain steps.
 
@@
 \item An {\em efficient} procedure for checking satisfiability
-of string constraints with string-number conversion.
-
-\item The class of \emph{parametric flat automata} which is the key for efficient handling of string constraints.
-
-\item An algorithm that translates the satisfiability problem of string constraints to the satisfiability problem of a linear formula  in polynomial-time when  the search space restricted by PFAs.
+of string constraints with string-number conversion constraints.
+
+\item The class of \emph{parametric flat automata} which is the key for efficient handling of string-number conversion constraints.
+
+\item An algorithm that translates the satisfiability string constraints to the satisfiability of a linear formula  in polynomial-time when  the search space restricted by PFAs.
 
@@
 \end{itemize}
-
-\paragraph{Outline.}
-After recalling the  definition in Section \ref{section:sc}. 
-Section \ref{section:sfa} presents  the class of parametric flat automata. 
-Section \ref{section:under_approximate} describes how to use PFA to restrict the searching domain of string variables.
-Section \ref{sec:flattening} shows how to construct the linear formula for  basic string constraints (i.e., 
-regular, equality, and integer constraints). 
- Section \ref{section:s2i} presents the construction of the linear formula for string-number conversion operations.
-Finally, Section \ref{section:evaluation} presents the details of our implementation and our experimental results.
 
@@
 
-A \emph{string constraint} is then a conjunction of atomic string constraints, with the semantics defined in the standard manner. It is \emph{satisfiable} if its semantics is nonempty.
+A \emph{string constraint} is then a conjunction of atomic string constraints, with the semantics defined in the standard manner.
+It is \emph{satisfiable} if its semantics is nonempty.
+Often we refer to the first three types of atomic string constraints the \emph{basic string constraints}.
 
@@
 %\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Over-Approximation} \label{section:over}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our procedure has two steps.
+In the first step, it replaces all string-number conversion constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints.
+In the second step, it over-approximates $\Phi$ to a \emph{chain-free string constraint}~\cite{abdulla2019chain}, 
+which constitutes with only integer, membership, and \emph{chain-free} equality constraints.
+In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
+For two equality constraints, 
+$\begin{array}{rcll}
+	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
+	t_2&\defeq& \ldots y \ldots = \ldots&,
+\end{array}$\\
+we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$.
+A set of equality constraints has a \emph{chain}, informally, if we can find some circular dependency in the equality constraints.
+The way to break a chain is simple, one just needs to find any variable $x$ in the dependency circle, and replace it to a fresh variable.
+Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable to a fresh one, and repeats until all chains are broken.
 
@@
 \section{Flattening of Basic String Constraints}
-\label{sec:flattening}
 We will first discuss flattening of the basic string constraints, that is,

### 2019-11-21 draft.tex
add over-approximation

@@
 A set of equality constraints has a \emph{chain}, informally, if we can find some circular dependency in the equality constraints.
-The way to break a chain is simple, one just needs to find any variable $x$ in the dependency circle, and replace it to a fresh variable.
-Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable to a fresh one, and repeats until all chains are broken.
+Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable in the dependency circle to a fresh one, and repeats until all chains are broken.
 

### 2019-11-21 draft.tex
Update draft.tex

@@
 Operations such as \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,abdulla2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{berzish2017z3str3}.
+$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$), are widely supported by most state-of-the-art string constraint solvers such as, CVC4 \cite{cvc4Tool}, OSTRICH \cite{chen2019decision}, Sloth \cite{sloth},  Trau+ \cite{abdulla2018trau,parosh2019chain,abdulla2017flatten}, Z3 \cite{z3} and Z3Str3 \cite{berzish2017z3str3}.
 
@@
 
-%For over-approximation, there are a few existing algorithms~\cite{abdulla2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
+%For over-approximation, there are a few existing algorithms~\cite{parosh2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
 In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
-In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{abdulla2019chain}.
+In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{parosh2019chain}.
 
@@
 
-We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers (including 0) and 
+We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
 integers. For a set $A$, we use $|A|$ to denote its size. 
@@
 We use $w_1\cdot w_2$ to denote the \emph{concatenation} of words $w_1$ and $w_2$.
-$\Sigma^*$ is the set of all words over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$, and 
+$\Sigma^*$ is the set of all words over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$ and $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$.
 A \emph{language} over $\Sigma$ is a subset $L$ of $\Sigma^*$. 
@@
 %The semantics of finite automaton is defined in the standard manner. 
-A \emph{run} of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$.
-The run is \emph{accepting} if $q_0 = q_i$ and $q_i = q_f$ and $w$ then is \emph{accepted}.
-The \emph{language} of $A$ is the set $L(A)$ of all accepted words.
+A \emph{run} $\pi$ of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transitions $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$.
+The run $\pi$ (resp.
+the word $w$) is \emph{accepting} (resp.
+\emph{accepted}) if $q_0 = q_i$ and $q_n = q_f$.
+The \emph{language} of $A$ (denoted by $L(A)$) consists of  the set  of all accepted words.
 
@@
 
-The \emph{Parikh image} of a word $w\in \Sigma^*$ is the assignment 
-$\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$.
-Formally, let $\pvarsof S$ denote the set of Parikh variables $\{\#s \mid s\in S\}$ obtained from a set $S$. 
+The \emph{Parikh image} of a word $w\in \Sigma^*$ maps each \emph{Parikh variable} $\#a$, with $a \in \Sigma$ is a character, to the number of occurrences of $a$ in $w$.
+Formally, given a set $S$, let $\pvarsof S$ denote the set of Parikh variables $\{\#s \mid s\in S\}$. 
 The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$. 
-The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in L\}$.
+The Parikh image of a language $L$ is defined as folllows $\parikhof L = \{\parikhof w \mid w \in L\}$.
 %and the Parikh image of an FA $A$ is Parikh image of its language, $\parikhof{A} = \parikhof{L(A)}$.
 %
-It is well known that $\parikhof {L(A)}$ can be efficiently computed in the form of linear formula:
+It is well known that the Parikh image of a regular language  can be  charctaerized by a linear formula:
 
 \begin{lemma}[\cite{SeidlSMH04}]
-$\parikhof{L(A)}$ of an FA $A$ can be computed in the form of a linear formula $\parikhfof{A}$ such that 
-%$\modelsof{\parikhfof A}_{\#\Sigma} = \parikhof{L(A)}$, 
-$\modelsof{\parikhfof A} = \parikhof{L(A)}$, 
-in time linear to the size of $A$.
+Let $A$ be a FA over the alphabet $\Sigma$. Then, we can compute, in linear time,  a linear formula $\parikhfof{A}$, over $\pvarsof \Sigma$, such that $\modelsof{\parikhfof A} = \parikhof{L(A)}$.
+
 \end{lemma}
@@
 
-A \emph{string constraint} is then a conjunction of atomic string constraints, with the semantics defined in the standard manner.
-It is \emph{satisfiable} if its semantics is nonempty.
-Often we refer to the first three types of atomic string constraints the \emph{basic string constraints}.
+A \emph{string constraint} is then a conjunction of atomic string constraints, with the semantics defined in the standard manner. It is \emph{satisfiable} if its semantics is nonempty.
 
@@
 %\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Over-Approximation} \label{section:over}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our procedure has two steps.
-In the first step, it replaces all string-number conversion constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints.
-In the second step, it over-approximates $\Phi$ to a \emph{chain-free string constraint}~\cite{abdulla2019chain}, 
-which constitutes with only integer, membership, and \emph{chain-free} equality constraints.
-In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
-For two equality constraints, 
-$\begin{array}{rcll}
-	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
-	t_2&\defeq& \ldots y \ldots = \ldots&,
-\end{array}$\\
-we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$.
-A set of equality constraints has a \emph{chain}, informally, if we can find some circular dependency in the equality constraints.
-Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable in the dependency circle to a fresh one, and repeats until all chains are broken.
 

### 2019-11-21 evaluation.tex

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{parosh2019chain}, , and Ostrich~\cite{chen2019decision}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{abdulla2019chain}, , and Ostrich~\cite{chen2019decision}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
@@
 	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
-	\item StringFuzz~\cite{StringFuzz}  is generated from the fuzz testing tool of the same name.
+	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated from the fuzz testing tool of the same name.
 	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}.

### 2019-11-21 draft.tex
Update draft.tex

@@
 we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
-We use $\modelsof \phi$ to denote the set all models of $\phi$. 
-%
+We use $\modelsof \phi$ to denote the set all models of $\phi$.%
 %Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
@@
 In this section, we formally define string constraints.
-To begin with, we fix an finite alphabet $\Sigma \subseteq \mathbb{N}$.
-Note that here we assume the alphabet is a finite subset of natural numbers.
+To begin with, we fix a finite alphabet $\Sigma \subseteq \mathbb{N}$.
+Note that here we assume that the alphabet is a finite subset of natural numbers.
 Essentially, we try to capture the numerical encoding of the corresponding symbols in computers (e.g., in ASCII, `A' is encoded as $65$).
-We assume there is an one-one mapping between numbers in $\Sigma$ and the character it encodes.
-For the simplicity of presentation, we assume the character `$0$' is mapped to the number $0$, `$1$' to $1$,$\ldots$, and `$9$' to $9$.
+Hence, we can  assume w.l.o.g.
+that  there is a one-to-one mapping between numbers in $\Sigma$ and the character it encodes.
+For the simplicity of presentation, we assume that the character `$0$' is mapped to the number $0$, `$1$' to $1$,$\ldots$, and `$9$' to $9$.
 For other character $c$, we use $\enc{c}$ to denote the number that it maps to.
@@
 In this paper, we use $x,y$ (or their variants) to denote string variables and $n$ (or its variants) to denote integer variables.
-
-An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{N}$.
+An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{Z}$.
 A \emph{term} is an element in $(\vars\cup \Sigma)^*$.
@@
 $\bullet$ An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
-t_2$ are terms in $(\vars\cup \Sigma)^*$. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
+t_2$ are terms. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
 I(t_1)=I(t_2)\}$. A \emph{disequality constraint} $\phi_d$ is of the form $t_1 \neq 
@@
 A \emph{string constraint} is then a conjunction of atomic string constraints, with the semantics defined in the standard manner.
-It is \emph{satisfiable} if its semantics is nonempty.
+It is \emph{satisfiable} if there is an interpretation which evaluates the  constraint to $\true$.
 Often we refer to the first three types of atomic string constraints the \emph{basic string constraints}.
@@
 The encoding has a benefit that it can also handle the case where $x$ is ``not a number", using the condition $\sti{x} = -1$.
-
-Supporting only positive integer is not a strong restriction, since conversing from negative integer can still be encoded using the positive only version.
-More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number", which can also be encoded using more conditions):
-$$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
-Recall that $\enc{-}$ is the integer encoding of the minus symbol `$-$'. The \emph{number-string conversion function} $\its{n}$ is defined symmetrically. We have $x = \its{n}$ iff $y= \sti{n}$.
+Supporting only positive integer is not a strong restriction, since conversing from negative integer can still be encoded using only the positive  version.
+
+%More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number", which can also be encoded using more conditions):
+%$$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
+%Recall that $\enc{-}$ is the integer encoding of the minus symbol `$-$'. The \emph{number-string conversion function} $\its{n}$ is defined symmetrically. We have $x = \its{n}$ iff $y= \sti{n}$.
 

### 2019-11-21 draft.tex
Update draft.tex

@@
 \paragraph{Outline.}
-After recalling the  definition in Section \ref{section:sc}. 
-Section \ref{section:sfa} presents  the class of parametric flat automata. 
+After recalling the  definition in Section \ref{section:sc}. Section \ref{section:over} presents a brief overview of our decision procedure. 
+Section \ref{section:sfa} introduces  the class of parametric flat automata. 
 Section \ref{section:under_approximate} describes how to use PFA to restrict the searching domain of string variables.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Over-Approximation} \label{section:over}
+\section{Decision Procedure Overview} \label{section:over}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our procedure has two steps.
-In the first step, it replaces all string-number conversion constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints.
-In the second step, it over-approximates $\Phi$ to a \emph{chain-free string constraint}~\cite{abdulla2019chain}, 
-which constitutes with only integer, membership, and \emph{chain-free} equality constraints.
-In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
-For two equality constraints, 
-$\begin{array}{rcll}
-	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
-	t_2&\defeq& \ldots y \ldots = \ldots&,
-\end{array}$\\
-we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$.
-A set of equality constraints has a \emph{chain}, informally, if we can find some circular dependency in the equality constraints.
-Our procedure iteratively searches for chains in the equality constraints, breaks the chain by replacing some variable in the dependency circle to a fresh one, and repeats until all chains are broken.
-
+
+Our decision procedure has two steps: the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+The over-approximation module proceeds as follows: First,  it replaces all string-number conversion constraint $n=\sti{x}$ by $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints.
+Then, it over-approximates $\Phi$ to a \emph{chain-free string constraint}~\cite{abdulla2019chain}, 
+which  consists of only integer, membership, and \emph{chain-free} equality constraints.
+Informally, a set of equality constraints has a \emph{chain} if we can find some circular dependency between the string variables in the equality constraints.
+Our procedure iteratively searches for such dependency chains in the equality constraints.
+If a chain is found then we replace a variable appearing in that chain by a  fresh one.
+By doing this, we  break  that chain.
+We   repeat this procedure until there are no more chains.
+Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT.
+
+The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
+In this case, our decision procedure  restricts the search domain of each string variable to strings that obey some predefined and parameterized pattern.
+We propose to use patterns defined by \emph{parametric flat automata} (PFA).
+A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length.
+The size of the PFA is parameterized by the length of the sequence of loops and the size of each loop.
+Adjusting these parameters enlarges or prunes the potential solution space.
+This approach based on PFA is very flexible yet allows very efficient manipulation.
+Then, we show that given such restriction, one can  reduce the string constraint solving problem to a linear formula satisfiability problem.
+
+The rest of the paper will be mainly dedicated to the explanation of the under-approximation technique (which is our main contribution).
+
+%
+%In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
+%For two equality constraints, 
+%$\begin{array}{rcll}
+%	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
+%	t_2&\defeq& \ldots y \ldots = \ldots&,
+%\end{array}$\\
+%we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-11-21 draft.tex
sec 6

--- 2019-11-21 draft.tex
@@
 \newcommand\outlf{\Psi_{\mathit{out}}}
-\newcommand\noepsilon{|\!|\epsilon|\!|}
+\newcommand\noepsilon{\semof{\epsilon}}
 
@@
 
-We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
+We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers (including 0) and 
 integers. For a set $A$, we use $|A|$ to denote its size. 
@@
 We use $w_1\cdot w_2$ to denote the \emph{concatenation} of words $w_1$ and $w_2$.
-$\Sigma^*$ is the set of all words over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$ and $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$.
+$\Sigma^*$ is the set of all words over $\Sigma$, $\Sigma^+ = \Sigma^*\setminus \{\epsilon\}$, $\Sigma_\epsilon = \Sigma\cup\{\epsilon\}$, and 
 A \emph{language} over $\Sigma$ is a subset $L$ of $\Sigma^*$. 
@@
 %The semantics of finite automaton is defined in the standard manner. 
-A \emph{run} $\pi$ of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transitions $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$.
-The run $\pi$ (resp.
-the word $w$) is \emph{accepting} (resp.
-\emph{accepted}) if $q_0 = q_i$ and $q_n = q_f$.
-The \emph{language} of $A$ (denoted by $L(A)$) consists of  the set  of all accepted words.
+A \emph{run} of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$.
+The run is \emph{accepting} if $q_0 = q_i$ and $q_i = q_f$ and $w$ then is \emph{accepted}.
+The \emph{language} of $A$ is the set $L(A)$ of all accepted words.
 
@@
 
-The \emph{Parikh image} of a word $w\in \Sigma^*$ maps each \emph{Parikh variable} $\#a$, with $a \in \Sigma$ is a character, to the number of occurrences of $a$ in $w$.
-Formally, given a set $S$, let $\pvarsof S$ denote the set of Parikh variables $\{\#s \mid s\in S\}$. 
+The \emph{Parikh image} of a word $w\in \Sigma^*$ is the assignment 
+$\parikhof w$ that for every character $a\in\Sigma$ maps the \emph{Parikh variable} $\#a$ to the number of occurrences of $a$ in $w$.
+Formally, let $\pvarsof S$ denote the set of Parikh variables $\{\#s \mid s\in S\}$ obtained from a set $S$. 
 The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$. 
-The Parikh image of a language $L$ is defined as folllows $\parikhof L = \{\parikhof w \mid w \in L\}$.
+The Parikh image of a language $L$ is the set of Parikh images $\parikhof L = \{\parikhof w \mid w \in L\}$.
 %and the Parikh image of an FA $A$ is Parikh image of its language, $\parikhof{A} = \parikhof{L(A)}$.
 %
-It is well known that the Parikh image of a regular language  can be  charctaerized by a linear formula:
+It is well known that $\parikhof {L(A)}$ can be efficiently computed in the form of linear formula:
 
 \begin{lemma}[\cite{SeidlSMH04}]
-Let $A$ be a FA over the alphabet $\Sigma$. Then, we can compute, in linear time,  a linear formula $\parikhfof{A}$, over $\pvarsof \Sigma$, such that $\modelsof{\parikhfof A} = \parikhof{L(A)}$.
-
+$\parikhof{L(A)}$ of an FA $A$ can be computed in the form of a linear formula $\parikhfof{A}$ such that 
+%$\modelsof{\parikhfof A}_{\#\Sigma} = \parikhof{L(A)}$, 
+$\modelsof{\parikhfof A} = \parikhof{L(A)}$, 
+in time linear to the size of $A$.
 \end{lemma}
@@
 The flattening $\outlf$ will be built inductively to the structure of $\insc$.
-Namely, in the following subsections we show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$, 
-and for a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
-We then let $\outlf \defeq \underf \dr \insc$.
+For a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
+We do such decomposition until reached atomic string constraints.
+We show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$ in the following subsections.
+At the end we set $\outlf \defeq \underf \dr \insc$.
 
@@
 $\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
-The following sections will be devoted to describing the flattening of the atomic string constraints.
 
 The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
-It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
-For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variavles $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
+It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
+For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variables $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
 $I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
@@
 $\semof{\pa\cdot \pa'} = \semof{\pa}\cdot\semof{\pa'}$ and 
-$\encode{\pa\cdot \pa'}{\semof{\pa\cdot \pa}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e \cup e'\mid e \in \encode \pa (\semof{\pa}),\\ e' \in\encode {\pa'} (\semof{\pa'})\}$.
+$\encode{\pa\cdot \pa'}{(\semof{\pa\cdot \pa})}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+\{e \cup e'\mid e \in \encode \pa (\semof{\pa}) \wedge e' \in\encode {\pa'} (\semof{\pa'})\}$.
 \end{lemma}

### 2019-11-21 draft.tex
sec 4

@@
 The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure  restricts the search domain of each string variable to strings that obey some predefined and parameterized pattern.
-We propose to use patterns defined by \emph{parametric flat automata} (PFA).
-A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length.
-The size of the PFA is parameterized by the length of the sequence of loops and the size of each loop.
-Adjusting these parameters enlarges or prunes the potential solution space.
-This approach based on PFA is very flexible yet allows very efficient manipulation.
-Then, we show that given such restriction, one can  reduce the string constraint solving problem to a linear formula satisfiability problem.
-
+In this case, our decision procedure  under-approximate the string constraints by restricting the search domain of each string variable to the language defined by some PFA that will be introduced in the next section.
+This approach based on PFA allows very efficient manipulation.
+We will show that given such restriction, one can reduce the string constraint solving problem to a linear formula satisfiability problem.
 The rest of the paper will be mainly dedicated to the explanation of the under-approximation technique (which is our main contribution).

### 2019-11-21 draft.tex
Update draft.tex

--- 2019-11-21 draft.tex
@@
 \newcommand\outlf{\Psi_{\mathit{out}}}
-\newcommand\noepsilon{\semof{\epsilon}}
+\newcommand\noepsilon{|\!|\epsilon|\!|}
 
@@
 
+A minor technical difficulty is that sometimes  we may need to treat  $\epsilon$ as a  number. Therefore, we encode $\epsilon$ as some fixed number $\noepsilon\in\nat\setminus\Sigma$.
+
 We call $\vars$ the set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ the set of \emph{integer variables} ranging over $\mathbb{Z}$.
@@
 \paragraph{Flat automata} 
-First, we say that an FA 
-$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is \emph{flat} if it satisfies the following structural constraints (the figure above):
+A finite state automaton  
+$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is said to be \emph{flat} if it satisfies the following structural constraints (the figure above):
 \begin{enumerate}
@@
 The crucial feature of flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver.
-\lh{, allowing to circumvent more costly automata algorithms and decision procedures.
-Concertize and justify this better?}\yfc{maybe we can say according to the experience of verification of concurrent system, flattening is usually faster than pure automata operation?
-Faouzi should know something.}
-%
-This is facilitated by flatness, which guarantees that 
-every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$. 
-In fact, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquely decoded:
+Such encoding into linear formula  results in efficient algorithms and decision procedure for the class of flat automata and so we avoid dealing with costly standard automata operations (e.g., checking  the non-emptiness of the intersection of several regular languages
+ is known to be {\sc Pspace}-complete while it is in {\sc NP} for the class of flat automata).
+This is due to the fact that 
+every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$ due to the flatness. 
+More precisely, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquely decoded:
 
@@
 \begin{proof}
-Indeed, since every variable appears on at most one transition, then the $\parikhof w$ value of all variables appearing within the same cycle of $A$ is the same, and it is equal to the number of repetitions of that cycle in the accepting run.
-%
-The accepting run on $w$ (and so $w$ itself) can thus be reconstructed from $\parikhof w$.
-
+First observe that the $\parikhof w$ value of any variable appearing within the a cycle of $A$ is equal to the number of repetitions of that cycle in the accepting run.
+This is an immediate consequence of the fact that
+ every variable appears on at most one transition.
+Thus, the accepting run on $w$ (and so $w$ itself) can thus be reconstructed from $\parikhof w$.
 More concretely, the function $\decode A$ can be implemented as follows.
@@
 and assuming that the lengths of the loops of $A$ are $l_0,\ldots,l_{m}$, 
-$\decode A(\pim)$ is constructed as the word $w_0 a_{0} \ldots a_{m-1} w_{m}$ where for each $i\in [0,m]$,
+$\decode A(\pim)$ is constructed as the word $w_0 a_{0} w_1 \cdots a_{m-1} w_{m}$ where for each $i\in [0,m]$,
 $w_i = (a_i^0 \cdots a_i^{l_{i}-1})^{\pvarsof {a_i^0}}$ if $l_i >0$ and $w_i = \epsilon$ if $l_i = 0$. 
@@
 %
-For example, in the automaton of the figure above, 
-from $\parikhwof x {a_0} = \parikhwof x {a_1} = \cdots = \parikhwof x {a_{m}}=1$ and $\parikhwof x {a^0_1}=\parikhwof x {a^1_1}=\parikhwof x {a^2_1}=2$ we derive that $x=a_0(a^0_1a^1_1a^2_1)^2a_1\cdots a_{m-1}$.
+For example, in the automaton, given at the beginning of this section, 
+from $\parikhwof x {a_0} = \parikhwof x {a_1} = \cdots = \parikhwof x {a_{m-1}}=1$, $\parikhwof x {a^0_1}=\parikhwof x {a^1_1}=\parikhwof x {a^2_1}=2$ and $\parikhwof x {a^i_j}=0$ otherwise,  we derive that $x=a_0(a^0_1a^1_1a^2_1)^2a_1\cdots a_{m-1}$.
 
@@
 and $\paf$ is an \emph{interpretation constraint}, a linear formula over $\cvar$. 
-\emph{Parametric flat automaton (PFA)} is then a parametric automaton with its finite automaton flat. See Figure~\ref{fig:sfa_def} and~\ref{fig:sfa} for examples of PFAs (automaton part only).
+\emph{Parametric flat automaton (PFA)} is then a parametric automaton whose  automaton is flat.
+See Figure~\ref{fig:sfa_def} and~\ref{fig:sfa} for examples of PFAs (only the automata component is shown
+).
 
@@
 %
-a mapping $I:\cvar\rightarrow\Sigma_\epsilon$. 
+a mapping $I:\cvar\rightarrow\Sigma_\epsilon$ (recall that $\Sigma_\epsilon \subseteq \nat$). 
 For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretation $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
@@
 
-Since every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$, and since $x$ is uniquely determined by its Parikh image, i.e.,
-$x = \decode \pa(\parikhof x)$, 
-we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I:\cvar\rightarrow\Sigma_\epsilon$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$ \emph{$\pa$-encodes} $w$.
+Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$.
+
+Let us assume now that  $\pa$ is a PFA.
+We  say that the assignment $I \cup \parikhof x$, uniting the interpretation $I:\cvar\rightarrow\Sigma_\epsilon$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$, \emph{$\pa$-encodes} $w$  since $x$ is uniquely determined by its Parikh image.
+%$x = \decode \pa(\parikhof x)$.
+%we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I:\cvar\rightarrow\Sigma_\epsilon$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$ \emph{$\pa$-encodes} $w$.
  Lemma~\ref{lemma:decoding} implies that such $\pa$-encoding can be uniquely decoded. 
-We may hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ 
-so that $\decode \pa(I \cup \parikhof x) = w$ (recall that $\Sigma_\epsilon \subseteq \nat$). \yfc{true only if we move the semantic of $\epsilon$ to preliminary. Now it is a symbol.}
-We again lift the decoding function to sets of united assignments in the standard manner.
+We  hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ in the straightforward manner (i.e.,  $\decode \pa(I \cup \parikhof x) = w$).   
 The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
@@
 The flattening $\outlf$ will be  built inductively to the structure of $\insc$.
-For a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
-We do such decomposition until reached atomic string constraints.
-We show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$ in the following subsections.
-At the end we set $\outlf \defeq \underf \dr \insc$.
+Namely, in the following subsections we show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$, 
+and for a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
+We then let $\outlf \defeq \underf \dr \insc$.
 
@@
 $\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
+The following sections will be devoted to describing the flattening of the atomic string constraints.
 
 The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
-It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
-For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variables $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
+It uses the decoding function $\decode \dr$ parameterised by the domain restriction $\dr$. 
+For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variavles $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
 $I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
@@
 
-\paragraph{Encoding epsilon.}
-A minor technical difficulty is that we wish to build flat under-approximation in the form of pure arithmetic formulae, 
-but we may also wish to specify when a character variable is assigned $\epsilon$, but $\epsilon$ is not a number. 
-Hence, to allow purely arithmetic formulae talk about $\epsilon$, 
-we encode $\epsilon$ as some fixed number $\noepsilon\in\nat\setminus\Sigma$.
 %In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulae constraining interpretations of character variables.
@@
 $\semof{\pa\cdot \pa'} = \semof{\pa}\cdot\semof{\pa'}$ and 
-$\encode{\pa\cdot \pa'}{(\semof{\pa\cdot \pa})}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e \cup e'\mid e \in \encode \pa (\semof{\pa}) \wedge e' \in\encode {\pa'} (\semof{\pa'})\}$.
+$\encode{\pa\cdot \pa'}{\semof{\pa\cdot \pa}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+\{e \cup e'\mid e \in \encode \pa (\semof{\pa}),\\ e' \in\encode {\pa'} (\semof{\pa'})\}$.
 \end{lemma}

### 2019-11-21 draft.tex
Update draft.tex

@@
 Namely, assuming that $X$ is the set of string variables of $\insc$,
-a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to every variable $x\in X$ a PFA $\dr(x)$ over character variables $V_x$ and we let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.
+a \emph{flat domain restriction} for $\insc$ is a mapping $\dr$ that assigns to each variable $x\in X$, a PFA $\dr(x)$ over character variables $V_x$.
+Let $V_\dr = \bigcup_{x\in X} V_x$ be the set of all character variables used in $\dr$.
 We require that these PFA operate over pairwise disjoint sets of character variables, that is if $x\neq y$ then $V_x \cap V_y = \emptyset$.
@@
 %
-The flattening $\outlf$ will be built inductively to the structure of $\insc$.
+The flattening $\outlf$ will be built inductively following the structure of $\insc$.
 For a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
 We do such decomposition until reached atomic string constraints.
-We show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$ in the following subsections.
+We show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$ in the following sections.
 At the end we set $\outlf \defeq \underf \dr \insc$.
 
+%The semantics of a string constraint $\phi$ restricted by $\dr$ is then defined as 
+%$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
+
 The semantics of a string constraint $\phi$ restricted by $\dr$ is then defined as 
-$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
+$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\}$.
 
@@
 The theorem can be proved by a structural induction over $\insc$.
-However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ then just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.
+However, for the induction step to go through, we will need to guarantee a stronger correspondence of string constraints $\phi$ and their flattenings $\underf \dr \phi$ than just the semantic equality $\decode \dr (\semof {\underf \dr \phi}) = \semof{\phi}^\dr$.
 Particularly, we will need to
@@
 
-\lh{do we want to discuss some sort of completeness? That is, every interpretation of every integer constraint is are covered by some flat restriction. ?}
+%\lh{do we want to discuss some sort of completeness? That is, every interpretation of every integer constraint is are covered by some flat restriction. ?}
 

### 2019-11-21 draft.tex
remogin [[x]] and [[L]]

@@
 %
-We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, and the semantics of a PA is the semantics of its language restricted by the formula $\paf$, that is,
-$\semof {\pa} = \{I(w) \mid w\in L(A),I\in\semof \paf\}$.
+%We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, 
+%the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, 
+We then define the semantics of the PA $P$ as the set of strings   
+$\semof {\pa} = \{I(x) \mid x\in L(A),I\in\semof \paf\}$ of all interpretations satisfying $\paf$ of all parametric strings in the language of $A$.
 

### 2019-11-21 draft.tex
updating section 7

--- 2019-11-21 draft.tex
@@
 encodings 
-$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode \pa(w')$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
+$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode \pa(w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
 
@@
 it means the character variable $v$ and $v'$ should be assigned the same value,
-$\pa$ transitions under $v$ from state $q_1$ to state $q_2$ and ${\pa'}$ from $q_1'$ to $q_2'$ under $v'$.
+$\pa$ moves under $v$ from state $q_1$ to state $q_2$ and ${\pa'}$ from $q_1'$ to $q_2'$ under $v'$.
 %
@@
 it means that the character variable $v$ should be assigned $\epsilon$, 
-$\pa$ transitions under $v$ to $q_1$, and ${\pa'}$ takes no action, since no action is needed to match $\pa$'s reading of $\epsilon$ (hence consumes no symbol from the input word).
+$\pa$ moves under $v$ to $q_1$, and ${\pa'}$ takes no action, since no action is needed to match $\pa$'s reading of $\epsilon$ (hence consumes no symbol from the input word).
 Symmetrically, ${\pa'}$ might read a variable $v$ assigned $\epsilon$ and $\pa$ may stay.
@@
 \subsection{Flattening of Integer Constraints}
-\changed{
+{
 \newcommand{\lx}{l_x}
@@
 Given a length constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
-We use a version of $\phi_l$ where every occurence of every leght term $|x|$ is replaced by an auxiliary lenght variable $\lx$ and add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
+We use a version of $\phi_l$ where every occurrence of every length term $|x|$ is replaced by an auxiliary length variable $\lx$ and we add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
 %
@@
 That is, $\lv$ will be $0$ if $v$ is assigned $\noepsilon$,
-otherwise it will equal the number $\#v$ of its occurrences in the word:
+otherwise it will equal to the number $\#v$ of its occurrences in the word:
 $$

### 2019-11-21 draft.tex
Update draft.tex

@@
 
-Last, we a major contribution of this paper, 
+Last, we present the main contribution of this paper, 
 the construction of a flattening $\underf \dr {\phi_s}$ of string-number conversion constraint $\phi_s \defeq n=\sti{x}$.
@@
 The constraint uses $\#v_0$ to capture the total number of loop traversals.
-Notice that the constraint above contains an exponential component $\frac{100^{\#v_0}}{100-1}$. To solve the satisfiability of this formula, one need to solve an exponential constraint.
+Notice that the constraint above contains an exponential component $\frac{100^{\#v_0}}{100-1}$. To solve the satisfiability of this formula, one needs to solve an exponential constraint.
 
@@
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
-As said in the introduction, the problem is difficult even for the case that variables are real numbers.
+The problem is difficult even for the case that variables are real numbers.
 For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure which is double-exponential to the length of the input formula and hence cannot handle large instances.
 We therefore do not expect that such constraint can be solved efficiently.
-Instead, we will define a special form of the flat restriction $\dr(x)$ of $x$ that leads to an easies linear formula.
+Instead, we will define a special form of the flat restriction $\dr(x)$ of $x$ that leads to an easier linear formula.
 
@@
 %An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving. 
-We will now discuss the special form of $\dr(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints that leads to efficient underapproximation.
+We will now discuss the special form of $\dr(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints and that leads to efficient underapproximation technique.
 %
 Besides simple induced linear formulae, we still want single $\dr(x)$ to cover as many numerals as possible.
-We want an ``easy" completeness property, that is, that the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+We want an ``easy" completeness property, that is,  the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
 %
@@
 Although it still has a loop, it will not create any exponential component defining the value of $n$ because the loop only represents a sequence of ``0" at the front of $x$.
-It will not affect the integer value of $n=\sti{x}$.
+Thus, it will not affect the integer value of $n=\sti{x}$.
 
@@
 %
-A last problem still needs to be solved beofe they can be efficient in practice. 
+A last problem still needed to be solved beofe they can be efficient in practice. 
 %
@@
 %
-This would lead to an exponential explosion of the size of the linear formula defining the value of $n$.
-%
-In order to eliminate this blow-up in the size of the formula, we add to $\paf^m$ an additional constraint that forces all epsilons to be \emph{shifted} behind the least significant digit, effectively prohibiting all interleavings but one.
+This may  lead to a formula of   exponential size  when defining  the value of $n$.
+%
+In order to eliminate this potential blow-up in the size of the formula, we add to $\paf^m$ an additional constraint that forces all epsilons to be \emph{shifted} behind the least significant digit.
+This will leave us with only one interleaving.
 This is the formula

### 2019-11-22 draft.tex
abstract

@@
 
+\begin{abstract}
+String-number conversion is an important class of constraint needed for the symbolic execution for programs.
+It is particular important in the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of the language.
+However, the state-of-the-art constraint solvers have only very limited support to this type of constraint.
+In this paper, we propose an approach that can support a combination of string-number conversion as well as other common types of string constraints efficiently.
+Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
+\end{abstract}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\yfc{We need an abstract}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-11-22 evaluation.tex

@@
 \label{section:evaluation}
+
+We have implemented our string constraint solving procedure, in a tool called {\tool}, on top of the SMT solver Z3~\cite{z3} as a theory solver.
+In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
+It also enable us to solve not only formulas over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulas.
+
+In {\tool}, we use the following PFA selection strategy: we select PFA's of size $m$ for string variables occur a number-string conversion constraint and PFA's with $p$ loops of size $q$ for other variables.
+Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required.
+We set an upper bound $7$ for each parameters and report UNKNOWN if a solution cannot be found within the bound.
+\yfc{need to check with Diep for the parameters}.
+
+The way our theory solver and Z3 interacts is almost standard.
+Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure.
+For under-approximation, every time when a corresponding linear formula is created, we create a new Z3 solver instance to solve it.
+If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and tries another solution branch.
+If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.
+
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{abdulla2019chain}, , and Ostrich~\cite{chen2019decision}.
+We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
+We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.
+
+We perform two sets of experiments. In the first experiment, we compare with other tools on benchmarks over basic string constraints. We use the following benchmark examples in this experiments:
+\begin{itemize}
+	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
+	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
+	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
+	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated from the fuzz testing tool of the same name.
+	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}.
+These benchmarks contain a small amount of string-number conversion constraints (< $5\%$).
+\end{itemize}
+
+In the second experiment, we compare with tools supporting to string-number conversion on the  benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
+We run it on several examples collected from the LeetCode platform and from Python core libraries.
+We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).
+
+All experiments were executed on a computer with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
+We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
+Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test.
+To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtained a modified test, and re-evaluates the modified test by multiple solvers.
+If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results.
+Otherwise, we manually simplify and inspect the test until we get a conclusive result.
+
+The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
+Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas.
+Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
 
@@
 \multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 20123 & 18490 &  3514 & 19149 \\ 
-							& UNSAT    &  3858*   &  3841 &  3855 &  4521 & 3828 \\
-							& $\times$ &  1977*   &  1457 &  3076 & 17386 & 2444 \\ \hline
-\multirow{3}{*}{APLAS}		& SAT      &   128*   &    51 &    19 &    52 & 132 \\
-							& UNSAT    &   287*   &   214 &   100 &   118 & 82 \\
-							& $\times$ &   185*   &   335 &   481 &   430 & 386 \\ \hline
-\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   871 &   881 &   651 & 778 \\
+\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 19763 & 18490 &  3514 & 19149 \\ 
+							& UNSAT    &  3858*   &  3834 &  3855 &  4521 & 3828 \\
+							& $\times$ &  1977*   &  1824 &  3076 & 17386 & 2444 \\ \hline
+\multirow{3}{*}{APLAS}		& SAT      &   128*   &   205 &    19 &    52 & 132 \\
+							& UNSAT    &   287*   &   221 &   100 &   118 & 82 \\
+							& $\times$ &   185*   &   174 &   481 &   430 & 386 \\ \hline
+\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   859 &   881 &   651 & 778 \\
 							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
-							& $\times$ &    26*   &    10 &     0 &   228 & 61 \\ \hline
-\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   610 &   316 &   605 & 688 \\
-							& UNSAT    &   294*   &   255 &   206 &   217 & 339 \\
-							& $\times$ &   269*   &   200 &   543 &   243 & 38 \\\hline
+							& $\times$ &    26*   &    22 &     0 &   228 & 61 \\ \hline
+\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   671 &   316 &   605 & 688 \\
+							& UNSAT    &   294*   &   240 &   206 &   217 & 339 \\
+							& $\times$ &   269*   &   154 &   543 &   243 & 38 \\\hline
 \multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
@@
 							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
-\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 9 &     6 &    16 & 311 \\
-							& UNSAT    &  1030*   &  1025 &  1020 &   962 & 596 \\
-							& $\times$ &     2*   &    11 &    19 &    67 & 138 \\ \hline
-\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21675 & 19724 &  4848 & 21305  \\
-							& UNSAT    &  8067*  &   7938 &  7773 &  8383 & 7172  \\
-							& $\times$ &  2464*  &  2019 &   4135 & 18401 & 3155  \\\hline	
+\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 8 &     6 &    16 & 311 \\
+							& UNSAT    &  1030*   &   936 &  1020 &   962 & 596 \\
+							& $\times$ &     2*   &   101 &    19 &    67 & 138 \\ \hline
+\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21517 & 19724 &  4848 & 21305  \\
+							& UNSAT    &  8067*  &   7834 &  7773 &  8383 & 7172  \\
+							& $\times$ &  2464*  &   2281 &   4135 & 18401 & 3155  \\\hline	
 \end{tabular}}
@@
 \multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1766 &  1025  &   333 \\ 
-										 & UNSAT    &  16369*  & 15612 & 17234  & 15543 \\
-										 & $\times$ &    202*  &  1549 &   668  &  3051 \\ \hline 
-\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   586 &  1802  &   389 \\ 
-										 & UNSAT    &    720*  &   666 &   744  &   729 \\
-										 & $\times$ &   1014*  &  1394 &   100  &  1528 \\ \hline
-\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     5 &    16  &     4 \\ 
+\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1543 &  1025  &   333 \\ 
+										 & UNSAT    &  16369*  & 15676 & 17234  & 15543 \\
+										 & $\times$ &    202*  &  1708 &   668  &  3051 \\ \hline 
+\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   408 &  1802  &   389 \\ 
+										 & UNSAT    &    720*  &   660 &   744  &   729 \\
+										 & $\times$ &   1014*  &  1578 &   100  &  1528 \\ \hline
+\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     6 &    16  &     4 \\ 
 										 & UNSAT    &      0   &     0 &     0  &     0 \\
-										 & $\times$ &      0   &    15 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}					 & SAT      &   3288*  &  2357 &  2843  &   726 \\ 
-										 & UNSAT    &  17089*  & 16278 & 17978  & 16272 \\
-										 & $\times$ &   1216*  &  2958 &   772  &  4595 \\ \hline
+										 & $\times$ &      0   &    14 &     4  &    16 \\ \hline \hline
+\multirow{3}{*}{Total}					 & SAT      &   3288*  &  1957 &  2843  &   726 \\ 
+										 & UNSAT    &  17089*  & 16336 & 17978  & 16272 \\
+										 & $\times$ &   1216*  &  3300 &   772  &  4595 \\ \hline
 \end{tabular}}
@@
 \end{table}
+
+From Table~\ref{table:base_benchmark}, we can see that the performance  of {\tool} is as good as the most competitive tools such as CVC4 and Z3 on basic string constraints.
+In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases.
+If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases.
+But we believe this is not very important because both these two cases are artificial, either hand-crafted or randomly produced from a fuzzer.
+The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.
+
+From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
+The total number of failed cases is only a half to Z3, which is ranked the 2nd.
+In fact, most of the failed tests comes from the analysis of one Python core library function that converts an IPv6 address to a number.
+We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
+If we exclude results on this function, then {\tool} has only $185$ failed case in total.
+This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total.
 
@@
 \# of Loops & {\tool} 	  &  CVC4    	 &       Z3   & Z3-str3 \\ \hline
-2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.27s)   & \textbf{SAT}(0.2s)  & $\times$ \\
-3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(10.1s)  & \textbf{SAT}(0.1s)  & $\times$ \\
-4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(48.7s) &   $\times$  & $\times$ \\
-5 			& \textbf{SAT}(<0.1s)  &  $\times$     &   $\times$  & $\times$ \\
+2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.2s)  & $\times$ \\
+3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.1s)  & $\times$ \\
+4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
+5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
 6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.13s) & $\times$ \\
@@
 \end{table}
+
+\hide{
+\paragraph{Basic constraint benchmarks.}
+This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups.
+In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in some cases even better.
+
+The first benchmark is called PyEx~\cite{pyex} according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing.
+This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests.
+PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.
+
+The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}.
+The benchmark includes a total of 600 hand-drafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.
+
+The next benchmark is called LeetCode~\cite{LeetCode} that was obtained by extracting constraints from Python's testing solutions provided by LeetCode platform.
+They provide many programming examples and their solutions gathered from technical interviews for companies.
+Leetcode consists of 881 satisfiable and 1785 unsatisfiable tests that, like PyEx, contain diverse string constraints.
+
+StringFuzz is our next bechmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
+We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.
+
+The last two benchmarks, called $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$, are obtained from cvc4 group~\cite{termEQ}.
+This set of benchmarks consists of the verification of term equivalences over strings and includes various string constraints including string-number and number-string conversion constraints.
+
+\paragraph{String-number conversion constraint benchmarks.}
+Our second group of benchmarks was created in order that we could compare our proposed approach for solving string-number and number-string conversions with existing approaches.
+This group contains a total of 3 benchmarks: full\_str\_int, filtered\_str\_int and rec\_fun.
+None of these benchmarks were artificially generated but were created from real Python's and javascript's codes.
+
+The first benchmark in the group is full\_str\_int, which is a collection of SMT queries.
+This collection was generated by applying a tool for concolic testing to Python codes selected from the previously mentioned LeetCode platform and from Python core libraries.
+All selected Python codes use the \texttt{int()} function, which converts a string into a number system based on the specified base.
+The Benchmark consists of 21573 tests in total.
+
+The second benchmark, called filtered\_str\_int, is a subset of the previous full\_str\_int benchmark.
+The filtered\_str\_int benchmark was created by removing tests where cvc4 reported UNSAT and where cvc4's returned unsat core contained no conversion constraint.
+This benchmark was created in order that we better compare individual conversion approaches.
+A total of 7396 tests were left.
+
+The last benchmark in the group is rec\_fun, which is a collection of javascript functions that were handcrafted encoded into smt2 format using recursive functions.
+Besides running examples from the introduction, the benchmark also includes \texttt{split} and \texttt{replaceAll} functions.
+In total, we managed to create 43 tests that combine several SMT theory and contain conversion constrains.
+}
+
+\hide{
+In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation.
+To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[];
+LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[].
+Table~\ref{table:base_benchmark} shows the result of the comparison.
+The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS.
+We set the timeout is to 10 seconds.
+Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster.
+The results are either sat, unsat, timeout, or $\times$.
+In case $\times$, the result may be unknown, error, or exception.
+
+\textbf{Comparison according to Table 1......}
+
+To evaluate our strategy for string-number/number-string conversion, we also prepared a benchmark \texttt{str\_int}\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}.
+It is collected from two sources of Python programs that use ttexttt{int()} function: Leetcode solutions written in Python and Python core libraries.
+We concolic tested these Python programs by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs.
+The SMT queries during the concolic testing are collected as our benchmark.
+To be more precise in evalutation, we have two versions of \texttt{str\_int} benchmark: \texttt{full\_str\_int} and \texttt{filtered\_str\_int}.
+\texttt{full\_str\_int} is the original benchmark we collected (i.e.
+from Python programs using \texttt{int()}); \texttt{filtered\_str\_int} is a subset of \texttt{fill\_str\_int}.
+We filtered out problems that cvc4 says unsat while the unsat cores do not contain \texttt{str.to.int} or \texttt{int.to.str}.
+The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}.
+The experiments are conducted under the same condition as the experiments on other benchmarks.
+
+\textbf{Comparison according to Table 2.....}
+}
+
+\hide{
+\begin{table}[]
+\caption{Results of z3-Trau, cvc4, and z3 on full\_str\_int benchmark}
+\begin{tabular}{|r|r|r|r|r|r|r|}
+\hline
+Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
+z3-Trau		& 3289 & 17089 & 0 & 1195 & 0 & 0 \\ 
+cvc4		& 2185 & 16377 & 0 & 3011 & 0 & 0 \\ 
+z3seq		& 2716 & 16831 & 0 & 2026 & 0 & 0 \\ 
+z3str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
+\end{tabular}
+\label{table:full_str_int}
+\end{table}
+
+Table~\ref{table:filtered_str_int} shows the comparison on filtered\_str\_int.  The total amount of cases in filtered\_str\_int is 7396.
+
+\begin{table}[]
+\caption{Results of z3-Trau, cvc4, and z3 on filtered\_str\_int benchmark}
+\begin{tabular}{|r|r|r|r|r|r|r|}
+\hline
+Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
+z3-Trau		& 3281 & 2912 & 0 & 1203 & 0 & 0 \\ 
+cvc4		& 2210 & 2211 & 0 & 2975 & 0 & 0 \\ 
+z3seq		& 2729 & 2655 & 0 & 2012 & 0 & 0 \\ 
+z3str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
+\end{tabular}
+\label{table:filtered_str_int}
+\end{table}
+}
 
@@
 }
-
-We have implemented our string constraint solving procedure, in a tool called {\tool}, on top of the SMT solver Z3~\cite{z3} as a theory solver.
-In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
-It also enable us to solve not only formulas over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
-Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulas.
-
-In {\tool}, we use the following PFA selection strategy: we select PFA's of size $m$ for string variables occur a number-string conversion constraint and PFA's with $p$ loops of size $q$ for other variables.
-Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required.
-We set an upper bound $7$ for each parameters and report UNKNOWN if a solution cannot be found within the bound.
-\yfc{need to check with Diep for the parameters}.
-
-The way our theory solver and Z3 interacts is almost standard.
-Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure.
-For under-approximation, every time when a corresponding linear formula is created, we create a new Z3 solver instance to solve it.
-If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and tries another solution branch.
-If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.
-
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{abdulla2019chain}, , and Ostrich~\cite{chen2019decision}.
-We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
-We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.
-
-We perform two sets of experiments. In the first experiment, we compare with other tools on benchmarks over basic string constraints. We use the following benchmark examples in this experiments:
-\begin{itemize}
-	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
-	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
-	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
-	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated from the fuzz testing tool of the same name.
-	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}.
-These benchmarks contain a small amount of string-number conversion constraints (< $5\%$).
-\end{itemize}
-
-In the second experiment, we compare with tools supporting to string-number conversion on the  benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
-We run it on several examples collected from the LeetCode platform and from Python core libraries.
-We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).
-
-All experiments were executed on a computer with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
-We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
-Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test.
-To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtained a modified test, and re-evaluates the modified test by multiple solvers.
-If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results.
-Otherwise, we manually simplify and inspect the test until we get a conclusive result.
-
-The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
-Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas.
-Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
-From Table~\ref{table:base_benchmark}, we can see that the performance  of {\tool} is as good as the most competitive tools such as CVC4 and Z3 on basic string constraints.
-In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases.
-If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases.
-But we believe this is not very important because both these two cases are artificial, either hand-crafted or randomly produced from a fuzzer.
-The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.
-
-From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
-The total number of failed cases is only a half to Z3, which is ranked the 2nd.
-In fact, most of the failed tests comes from the analysis of one Python core library function that converts an IPv6 address to a number.
-We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
-If we exclude results on this function, then {\tool} has only $185$ failed case in total.
-This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total.
-
-\hide{
-\paragraph{Basic constraint benchmarks.}
-This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups.
-In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in some cases even better.
-
-The first benchmark is called PyEx~\cite{pyex} according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing.
-This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests.
-PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.
-
-The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}.
-The benchmark includes a total of 600 hand-drafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.
-
-The next benchmark is called LeetCode~\cite{LeetCode} that was obtained by extracting constraints from Python's testing solutions provided by LeetCode platform.
-They provide many programming examples and their solutions gathered from technical interviews for companies.
-Leetcode consists of 881 satisfiable and 1785 unsatisfiable tests that, like PyEx, contain diverse string constraints.
-
-StringFuzz is our next bechmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
-We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.
-
-The last two benchmarks, called $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$, are obtained from cvc4 group~\cite{termEQ}.
-This set of benchmarks consists of the verification of term equivalences over strings and includes various string constraints including string-number and number-string conversion constraints.
-
-\paragraph{String-number conversion constraint benchmarks.}
-Our second group of benchmarks was created in order that we could compare our proposed approach for solving string-number and number-string conversions with existing approaches.
-This group contains a total of 3 benchmarks: full\_str\_int, filtered\_str\_int and rec\_fun.
-None of these benchmarks were artificially generated but were created from real Python's and javascript's codes.
-
-The first benchmark in the group is full\_str\_int, which is a collection of SMT queries.
-This collection was generated by applying a tool for concolic testing to Python codes selected from the previously mentioned LeetCode platform and from Python core libraries.
-All selected Python codes use the \texttt{int()} function, which converts a string into a number system based on the specified base.
-The Benchmark consists of 21573 tests in total.
-
-The second benchmark, called filtered\_str\_int, is a subset of the previous full\_str\_int benchmark.
-The filtered\_str\_int benchmark was created by removing tests where cvc4 reported UNSAT and where cvc4's returned unsat core contained no conversion constraint.
-This benchmark was created in order that we better compare individual conversion approaches.
-A total of 7396 tests were left.
-
-The last benchmark in the group is rec\_fun, which is a collection of javascript functions that were handcrafted encoded into smt2 format using recursive functions.
-Besides running examples from the introduction, the benchmark also includes \texttt{split} and \texttt{replaceAll} functions.
-In total, we managed to create 43 tests that combine several SMT theory and contain conversion constrains.
-}
-
-\hide{
-In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation.
-To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[];
-LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[].
-Table~\ref{table:base_benchmark} shows the result of the comparison.
-The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS.
-We set the timeout is to 10 seconds.
-Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster.
-The results are either sat, unsat, timeout, or $\times$.
-In case $\times$, the result may be unknown, error, or exception.
-
-\textbf{Comparison according to Table 1......}
-
-To evaluate our strategy for string-number/number-string conversion, we also prepared a benchmark \texttt{str\_int}\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}.
-It is collected from two sources of Python programs that use ttexttt{int()} function: Leetcode solutions written in Python and Python core libraries.
-We concolic tested these Python programs by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs.
-The SMT queries during the concolic testing are collected as our benchmark.
-To be more precise in evalutation, we have two versions of \texttt{str\_int} benchmark: \texttt{full\_str\_int} and \texttt{filtered\_str\_int}.
-\texttt{full\_str\_int} is the original benchmark we collected (i.e.
-from Python programs using \texttt{int()}); \texttt{filtered\_str\_int} is a subset of \texttt{fill\_str\_int}.
-We filtered out problems that cvc4 says unsat while the unsat cores do not contain \texttt{str.to.int} or \texttt{int.to.str}.
-The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}.
-The experiments are conducted under the same condition as the experiments on other benchmarks.
-
-\textbf{Comparison according to Table 2.....}
-}
-
-\hide{
-\begin{table}[]
-\caption{Results of z3-Trau, cvc4, and z3 on full\_str\_int benchmark}
-\begin{tabular}{|r|r|r|r|r|r|r|}
-\hline
-Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
-z3-Trau		& 3289 & 17089 & 0 & 1195 & 0 & 0 \\ 
-cvc4		& 2185 & 16377 & 0 & 3011 & 0 & 0 \\ 
-z3seq		& 2716 & 16831 & 0 & 2026 & 0 & 0 \\ 
-z3str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
-\end{tabular}
-\label{table:full_str_int}
-\end{table}
-
-Table~\ref{table:filtered_str_int} shows the comparison on filtered\_str\_int.  The total amount of cases in filtered\_str\_int is 7396.
-
-\begin{table}[]
-\caption{Results of z3-Trau, cvc4, and z3 on filtered\_str\_int benchmark}
-\begin{tabular}{|r|r|r|r|r|r|r|}
-\hline
-Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
-z3-Trau		& 3281 & 2912 & 0 & 1203 & 0 & 0 \\ 
-cvc4		& 2210 & 2211 & 0 & 2975 & 0 & 0 \\ 
-z3seq		& 2729 & 2655 & 0 & 2012 & 0 & 0 \\ 
-z3str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
-\end{tabular}
-\label{table:filtered_str_int}
-\end{table}
-}

### 2019-11-22 draft.tex
abstract
related work and minor update to evalutaion

@@
 \end{abstract}
+ \setcopyright{none} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with Node.js---and it has conversions between strings and integers embedded in the core of its semantics.
-\smallskip
+
 \begin{center}
@@
 \end{center}
-\smallskip
 
@@
 Since we also need to distinguish the case when $x$ is not a number, in which case $n$ should equal $-1$, 
-the formula underapproximating $\phi_s$ is finally constructed as  
+the formula under-approximating $\phi_s$ is finally constructed as  
 \begin{multline*}
@@
 
-\paragraph{Related works:} 
-Already in 1946, Quine \cite{quine1946concatenation} showed that the first order theory
-of string equations is undecidable.
-%
-An important line of work has been to identify subclasses
-for which decidability can be achieved.
-%
-The pioneering work by Makanin \cite{makanin1977problem} proposed a decision
-procedure for quantifier-free word equations, i.e., Boolean combinations of
-equalities and disequalities, where the variables may denote words of 
-arbitrary lengths.
-%
-The decidability and complexity of different subclasses
-have been considered by several works, e.g.
-\cite{plandowski1999satisfiability,plandowski2006efficient,matiyasevich2008computation,robson1999quadratic,schulz1990makanin,ganesh2012word,ganesh2016undecidability}.
-Generalizations of the work of Makanin by adding
-new types of constraints have been difficult to achieve.
-%
-For instance, the satisfiability of word equations combined with length
-constraints of the form $\left|x\right|=\left|y\right|$ is open
-\cite{buchi1990definability}.
-%
-Recently, 
-regular and especially relational transducers constraints were identified
-%
-as a strongly desirable feature of string languages 
-%
-especially in the context software analysis with an emphasis on security. 
-%
-Adding these to the mix leads immediately to undecidability \cite{morvan2000rational}
-%
-and hence numerous decidable fragments were proposed \cite{abdulla2014string,barcelo2013graph,lin2016string,chen2017decidable,chen2019decision}. 
-%
-From these, the straight line fragment of \cite{lin2016string} is the most general decidable combination of concatenation and transducers.
-It is however incomparable to the acyclic fragment of \cite{abdulla2014string} (which does not have transducers but could be extended with them in a straightforward manner).
-%
-Some works add also other syntactic features, such as \cite{chen2017decidable,chen2019decision}, 
-but the limit of decidable combinations of the core string features---transducers/regular constraints, length constraints, and concatenation stays at \cite{lin2016string} and \cite{abdulla2014string}.
-%
-The weakly chaining decidable fragment present in this paper significantly generalises both these fragments in a practically relevant direction.
-
-The strong practical motivation in string solving led to a rise of a number of SMT solvers that do not always provide completeness guarantees but concentrate on solving practical problem instances, 
-through applying a variety of calculi and algorithms.
-%
-A number of tools handle string constraints by means of {\it length-based under-approximation} and
-translation to
-bit-vectors~\cite{kiezun2009hampi,saxena2010symbolic,saxena2010flax}, assuming
-a fixed upper bound on the length of the possible solutions. 
-%
-Our method on the other hand allows to analyse constraints without a length limit and with completeness guarantees.
-%
-More recently, also {\it DPLL(T)-based} string solvers lift the
-restriction of strings of bounded length; this generation of solvers
-includes Z3-str3 \cite{berzish2017z3str3}, Z3-str2~\cite{zheng2017z3str2}, 
-CVC4~\cite{cvc4Tool}, S3P~\cite{trinh2014s3,trinh2016progressive},
-Norn~\cite{abdulla2015norn}, 
-Trau~\cite{abdulla2018trau}, 
-Sloth~\cite{sloth}, 
-and 
-Ostrich~\cite{chen2019decision}. DPLL(T)-based solvers
-handle a variety of string constraints, including word equations, regular expression membership, length constraints, and (more rarely)
-regular/rational relations; the solvers are not complete for the full
-combination of those constraints though, and often only decide a (more
-or less well-defined) fragment of the individual constraints. 
-Equality constraints are normally handled by means of splitting into simpler
-sub-cases, in combination with powerful techniques for Boolean
-reasoning to curb the resulting exponential search space. 
-%
-Our implementation is combining strong completeness guarantees of \cite{sloth} extended to handle the fragment proposed in this paper with an efficient approximation techniques of \cite{abdulla2018trau}
-and its performance on existing benchmarks compares favourably with the most efficient of the above tools.
-%
+\section{Related works} 
+To the best of our knowledge, the study of solving string constraint traces back to 1946, when Quine \cite{quine1946concatenation} showed that the first-order theory of string equality constraints (a.k.a.
+word equations) is undecidable.
+Makanin achieves a milestone \cite{makanin1977problem} by showing that the class of quantifier-free string equality constraints is decidable.
+Since then, several works, e.g., \cite{plandowski1999satisfiability,plandowski2006efficient,matiyasevich2008computation,robson1999quadratic,schulz1990makanin,ganesh2012word,ganesh2016undecidability}, consider the decidability and complexity of different subclasses of string equality constraints.
+
+Satisfiability of string constraints is a challenging problem.
+The satisfiability of equality constraints combined with length constraints of the form $|x|=|y|$ is already opened for more than 20 years \cite{buchi1990definability}.
+Numerous decidable fragments were proposed\cite{abdulla2014string,barcelo2013graph,lin2016string,chen2017decidable,chen2019decision,abdulla2019chain}.
+Among them, the chain-free fragment \cite{abdulla2019chain} used by our over-approximation module is the largest known decidable fragment, which allows us to produce more precise over-approximation and hence solve many UNSAT instances efficiently.
+
+The strong practical motivation led to the rise of several string constraints solvers that concentrate on solving practical problem instances.
+Several tools handle string constraints assuming a fixed upper bound on the length of strings and translate them to boolean satisfiability problems~\cite{kiezun2009hampi,saxena2010symbolic,saxena2010flax}.
+Our method, on the other hand, allows analyzing constraints without a length limit and still with some completeness guarantees, i.e., within the language defined by PFAs.
+
+More recently,  {\it DPLL(T)-based} string solvers~\cite{berzish2017z3str3,zheng2017z3str2,cvc4Tool,trinh2014s3,trinh2016progressive,abdulla2015norn,abdulla2018trau,sloth,chen2019decision} lift the
+restriction of strings of bounded length. They usually support a variety of string constraints, including all basic string constraints, and sometimes also regular/rational relations. 
+The typical procedure they used for solving equality constraints is to split them into simpler sub-cases, in combination with powerful techniques for Boolean reasoning to curb the resulting exponential search space.
+In contrast, our approach uses a completely different search strategy.
+We restrict the solution space to some predefined pattern and step-wisely enrich the pattern in use.
+
+The most related work to ours is~\cite{abdulla2018trau} who proposed to project the solution space of variables to a generalization of flat automata.
+The main difference is that our approach works fully symbolically, thanks to the ideas of using character variables.
+The use of character variables enables our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.
+Moreover, the approach of~\cite{abdulla2018trau} is exponential to the alphabet size, and hence in the implementation, usually requires heuristics to prune out unnecessary symbols.
 
 A further direction is {\it automata-based} solvers for analyzing
-string-manipulated programs. Stranger~\cite{yu2010stranger} soundly
-over-approximates string constraints using regular languages, and
-outperforms DPLL(T)-based solvers when checking single execution
-traces, according to some evaluations~\cite{kausler2014evaluation}. It has
-recently also been observed~\cite{wang2016string,sloth} that
-automata-based algorithms can be combined with model checking
-algorithms, in particular IC3/PDR, for more efficient checking of the emptiness for automata. However, many kinds of constraints, including length
-constraints and word equations, cannot be
-handled by automata-based solvers in a complete manner.
+string-manipulated programs.
+ABC~\cite{aydin2018parameterized} and Stranger~\cite{yu2010stranger} soundly over-approximates string constraints using multi-tape automata~\cite{yu2016optimal}, and outperforms DPLL(T)-based solvers when checking single execution traces, according to some evaluations~\cite{kausler2014evaluation}.
+People also studied the combination of automata-based algorithms with with model checking
+algorithms, in particular, IC3/PDR, for more efficient checking of the emptiness for automata~\cite{wang2016string,sloth}.
+However, many kinds of constraints, including length constraints and word equations, cannot be entirely handled by automata-based solvers.
 

### 2019-11-22 evaluation.tex
related work and minor update to evalutaion

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, \textsf{Trau+}~\cite{abdulla2019chain}, , and Ostrich~\cite{chen2019decision}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
-We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), which over-approximates cases that cannot be modeled by \emph{aligned multi-track automata}~\cite{yu2016optimal} and hence cannot solve our benchmark examples precisely.
+We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints) and Ostrich~\cite{chen2019decision}, because most of our benchmarks contain non-trivial equality constraints, which is not fully supported by those solvers.
 

### 2019-11-22 evaluation.tex
Update table

@@
 
-We have implemented our string constraint solving procedure, in a tool called {\tool}, on top of the SMT solver Z3~\cite{z3} as a theory solver.
+We have implemented our string constraint solving procedure in a tool called {\tool}.
+{\tool} is implemented on top of the SMT solver Z3~\cite{z3} as a theory solver.
 In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
-It also enable us to solve not only formulas over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
-Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulas.
+It also enables us to solve not only formulae over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.
 
-In {\tool}, we use the following PFA selection strategy: we select PFA's of size $m$ for string variables occur a number-string conversion constraint and PFA's with $p$ loops of size $q$ for other variables.
+In {\tool}, we use the following PFA selection strategy: we select PFAs of size $m$ for string variables involved in a number-string conversion constraint and PFAs with $p$ loops of size $q$ for other variables.
 Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required.
@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{109dfc5e8})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{1a9dfc5e8})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
@@
 
-We perform two sets of experiments. In the first experiment, we compare with other tools on benchmarks over basic string constraints. We use the following benchmark examples in this experiments:
+We perform two sets of experiments.
+In the first set of experiment, we compare with other tools on benchmarks over basic string constraints.
+We use the following benchmark examples in this experiments:
 \begin{itemize}
@@
 
-In the second experiment, we compare with tools supporting to string-number conversion on the  benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
+In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
 We run it on several examples collected from the LeetCode platform and from Python core libraries.
@@
 
-All experiments were executed on a computer with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
+All experiments were executed on a machine with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
 We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
@@
 The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
-Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas.
-Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
+Columns with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
+Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
 
@@
 \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 19763 & 18490 &  3514 & 19149 \\ 
-							& UNSAT    &  3858*   &  3834 &  3855 &  4521 & 3828 \\
-							& $\times$ &  1977*   &  1824 &  3076 & 17386 & 2444 \\ \hline
-\multirow{3}{*}{APLAS}		& SAT      &   128*   &   205 &    19 &    52 & 132 \\
-							& UNSAT    &   287*   &   221 &   100 &   118 & 82 \\
-							& $\times$ &   185*   &   174 &   481 &   430 & 386 \\ \hline
-\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   859 &   881 &   651 & 778 \\
-							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
-							& $\times$ &    26*   &    22 &     0 &   228 & 61 \\ \hline
-\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   671 &   316 &   605 & 688 \\
-							& UNSAT    &   294*   &   240 &   206 &   217 & 339 \\
-							& $\times$ &   269*   &   154 &   543 &   243 & 38 \\\hline
-\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
-							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
-							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
-\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 8 &     6 &    16 & 311 \\
-							& UNSAT    &  1030*   &   936 &  1020 &   962 & 596 \\
-							& $\times$ &     2*   &   101 &    19 &    67 & 138 \\ \hline
-\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21517 & 19724 &  4848 & 21305  \\
-							& UNSAT    &  8067*  &   7834 &  7773 &  8383 & 7172  \\
-							& $\times$ &  2464*  &   2281 &   4135 & 18401 & 3155  \\\hline	
+\multirow{3}{*}{PyEx}		& SAT      &  21205  & 19763 & 18490 &  3514 & 19149 \\ 
+							& UNSAT    &   3963  &  3834 &  3855 &  4521 & 3828 \\
+							& $\times$ &    253  &  1824 &  3076 & 17386 & 2444 \\ \hline
+\multirow{3}{*}{APLAS}		& SAT      &    135  &   205 &    19 &    52 & 132 \\
+							& UNSAT    &    343  &   221 &   100 &   118 & 82 \\
+							& $\times$ &    122  &   174 &   481 &   430 & 386 \\ \hline
+\multirow{3}{*}{LeetCode}	& SAT      &    842  &   859 &   881 &   651 & 778 \\
+							& UNSAT    &   1824  &  1785 &  1785 &  1787 & 1827 \\
+							& $\times$ &      0  &    22 &     0 &   228 & 61 \\ \hline
+\multirow{3}{*}{StringFuzz}	& SAT      &    528  &   671 &   316 &   605 & 688 \\
+							& UNSAT    &    320  &   240 &   206 &   217 & 339 \\
+							& $\times$ &    217  &   154 &   543 &   243 & 38 \\\hline
+\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 13 & 11 &   12 &    10 & 247 \\
+							& UNSAT    &    820  &   818 &   807 &   778 & 500 \\
+							& $\times$ &      2  &     6 &    16 &    47 & 88 \\ \hline
+\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     6 &    16 & 311 \\
+							& UNSAT    &   1031  &   936 &  1020 &   962 & 596 \\
+							& $\times$ &      1  &   101 &    19 &    67 & 138 \\ \hline
+\multirow{3}{*}{Total} 		& SAT      &  22736  &  21517 & 19724 &  4848 & 21305  \\
+							& UNSAT    &   8301  &   7834 &  7773 &  8383 & 7172  \\
+							& $\times$ &    595  &   2281 &   4135 & 18401 & 3155  \\\hline	
 \end{tabular}}
@@
 \multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1543 &  1025  &   333 \\ 
-										 & UNSAT    &  16369*  & 15676 & 17234  & 15543 \\
-										 & $\times$ &    202*  &  1708 &   668  &  3051 \\ \hline 
-\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   408 &  1802  &   389 \\ 
-										 & UNSAT    &    720*  &   660 &   744  &   729 \\
-										 & $\times$ &   1014*  &  1578 &   100  &  1528 \\ \hline
+\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2413  &  1543 &  1025  &   333 \\ 
+										 & UNSAT    &  16511  & 15676 & 17234  & 15543 \\
+										 & $\times$ &      3  &  1708 &   668  &  3051 \\ \hline 
+\multirow{3}{*}{String-Number-PythonLib} & SAT      &    424  &   408 &  1802  &   389 \\ 
+										 & UNSAT    &   2056  &   660 &   744  &   729 \\
+										 & $\times$ &    166  &  1578 &   100  &  1528 \\ \hline
 \multirow{3}{*}{String-Number-JavaScript}& SAT      &     20  &     6 &    16  &     4 \\ 
@@
 										 & $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}					 & SAT      &   3288*  &  1957 &  2843  &   726 \\ 
-										 & UNSAT    &  17089*  & 16336 & 17978  & 16272 \\
-										 & $\times$ &   1216*  &  3300 &   772  &  4595 \\ \hline
+\multirow{3}{*}{Total}					 & SAT      &   2857  &  1957 &  2843  &   726 \\ 
+										 & UNSAT    &  18567  & 16336 & 17978  & 16272 \\
+										 & $\times$ &    169  &  3300 &   772  &  4595 \\ \hline
 \end{tabular}}
@@
 If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases.
-But we believe this is not very important because both these two cases are artificial, either hand-crafted or randomly produced from a fuzzer.
+But we believe this is not very important because both these two benchmarks are artificial, either hand-crafted or randomly produced from a fuzzer.
 The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.
@@
 From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
-The total number of failed cases is only a half to Z3, which is ranked the 2nd.
+The total number of failed cases is only one-fourth to Z3, which is ranked the 2nd.
 In fact, most of the failed tests comes from the analysis of one Python core library function that converts an IPv6 address to a number.
-We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
+We generated 2028 tests from this function, and among them around 150 cases that are too difficult for all solvers.
 If we exclude results on this function, then {\tool} has only $185$ failed case in total.
 This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total.
+\yfc{This paragraph needs to be revised when new data of Z3-Trau is available.
+Note that z3seq is much more better now.
+Also is z3-trau.}
+
+\hide{ % data for helping to write comparison
+benchmark_path: lib_int-ipaddress__ip_int_from_string
+benchmark_size: 2028
+(tool-check_date, #sat, #unsat, #timeout, #unknown, #exception/error, #misc)
+(cvc4-20191120, 96, 367, 1565, 0, 0, 0)
+(z3-trau-20191122, 135, 1739, 154, 0, 0, 0)
+(z3seq-20191118, 1509, 431, 88, 0, 0, 0)
+(z3str3-20191118, 191, 440, 1330, 5, 0, 62)
+
+benchmark_path: leetcode_int-
+benchmark_size: 18927
+(tool-check_date, #sat, #unsat, #timeout, #unknown, #exception/error, #misc)
+(z3seq-20191118, 1025, 17234, 668, 0, 0, 0)
+(cvc4-20191120, 1543, 15676, 1708, 0, 0, 0)
+(cvc4-20191118, 1766, 15612, 1549, 0, 0, 0)
+(z3-trau-20191122, 2413, 16511, 3, 0, 0, 0)
+(z3str3-20191118, 333, 15543, 2031, 952, 0, 68)
+
+benchmark_path: lib_int-
+benchmark_size: 2646
+(tool-check_date, #sat, #unsat, #timeout, #unknown, #exception/error, #misc)
+(cvc4-20191118, 586, 666, 1394, 0, 0, 0)
+(z3seq-20191118, 1802, 744, 100, 0, 0, 0)
+(cvc4-20191120, 408, 660, 1578, 0, 0, 0)
+(z3str3-20191118, 389, 729, 1392, 70, 0, 66)
+(z3-trau-20191122, 424, 2056, 166, 0, 0, 0)
+}
 

### 2019-11-22 draft.tex
Update draft.tex

@@
 \begin{abstract}
-String-number conversion is an important class of constraint needed for the symbolic execution for programs.
-It is particular important in the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of the language.
+String-number conversion is an important class of constraint needed for the symbolic execution of string-manipulating programs.
+In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages.
 However, the state-of-the-art constraint solvers have only very limited support to this type of constraint.
-In this paper, we propose an approach that can support a combination of string-number conversion as well as other common types of string constraints efficiently.
+To overcome these limitations, we propose, in this paper, an approach that can support a combination of string-number conversion as well as other common types of string constraints efficiently.
 Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.

### 2019-11-22 evaluation.tex
minor update to evalutaion
Update table; Revised evaluation.

@@
-\section{Evaluation}
+\section{Implementation and Evaluation}
 \label{section:evaluation}
@@
 We have implemented our string constraint solving procedure in a tool called {\tool}.
-{\tool} is implemented on top of the SMT solver Z3~\cite{z3} as a theory solver.
-In this way we can concentrate on solving constraints connected by conjunctions and let Z3 to handle other boolean connectives.
-It also enables us to solve not only formulae over string constraints, but also the combination of string constraints with constraints over other theories that Z3 supports.
+{\tool} is implemented as a theory solver of the SMT solver Z3~\cite{z3} .
+In this way, we can concentrate on solving constraints connected by conjunctions and let Z3 handle other boolean connectives.
+It also enables us to solve not only formulae over string constraints but also the combination of string constraints with constraints over other theories that Z3 supports.
 Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.
@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(relese-1.7)~\cite{cvc4Tool}, Z3~(\texttt{dde8da853})~\cite{z3}, \textsf{Z3-str3}~(\texttt{1a9dfc5e8})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
@@
 We perform two sets of experiments.
-In the first set of experiment, we compare with other tools on benchmarks over basic string constraints.
-We use the following benchmark examples in this experiments:
+In the first set of experiments, we compare with other tools on benchmarks over basic string constraints.
+We use the following benchmark examples in these experiments:
 \begin{itemize}
@@
 \centering
-\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraint benchmarks.}
+\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
 \scalebox{0.85}{
@@
 \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      &  21205  & 19763 & 18490 &  3514 & 19149 \\ 
-							& UNSAT    &   3963  &  3834 &  3855 &  4521 & 3828 \\
-							& $\times$ &    253  &  1824 &  3076 & 17386 & 2444 \\ \hline
-\multirow{3}{*}{APLAS}		& SAT      &    135  &   205 &    19 &    52 & 132 \\
-							& UNSAT    &    343  &   221 &   100 &   118 & 82 \\
-							& $\times$ &    122  &   174 &   481 &   430 & 386 \\ \hline
-\multirow{3}{*}{LeetCode}	& SAT      &    842  &   859 &   881 &   651 & 778 \\
-							& UNSAT    &   1824  &  1785 &  1785 &  1787 & 1827 \\
-							& $\times$ &      0  &    22 &     0 &   228 & 61 \\ \hline
-\multirow{3}{*}{StringFuzz}	& SAT      &    528  &   671 &   316 &   605 & 688 \\
-							& UNSAT    &    320  &   240 &   206 &   217 & 339 \\
-							& $\times$ &    217  &   154 &   543 &   243 & 38 \\\hline
-\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 13 & 11 &   12 &    10 & 247 \\
-							& UNSAT    &    820  &   818 &   807 &   778 & 500 \\
-							& $\times$ &      2  &     6 &    16 &    47 & 88 \\ \hline
-\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     6 &    16 & 311 \\
-							& UNSAT    &   1031  &   936 &  1020 &   962 & 596 \\
-							& $\times$ &      1  &   101 &    19 &    67 & 138 \\ \hline
-\multirow{3}{*}{Total} 		& SAT      &  22736  &  21517 & 19724 &  4848 & 21305  \\
-							& UNSAT    &   8301  &   7834 &  7773 &  8383 & 7172  \\
-							& $\times$ &    595  &   2281 &   4135 & 18401 & 3155  \\\hline	
+\multirow{3}{*}{PyEx}		& SAT      &  21205  & 19763 & 16528 &  3030 & 19149 \\ 
+							& UNSAT    &   3963  &  3834 &  3831 &  3836 & 3828 \\
+							& $\times$ &    253  &  1824 &  5062 & 18555 & 2444 \\ \hline
+\multirow{3}{*}{APLAS}		& SAT      &    135  &   205 &    12 &    37 & 132 \\
+							& UNSAT    &    343  &   221 &   100 &   111 & 82 \\
+							& $\times$ &    122  &   174 &   488 &   452 & 386 \\ \hline
+\multirow{3}{*}{LeetCode}	& SAT      &    842  &   859 &   881 &   670 & 778 \\
+							& UNSAT    &   1824  &  1785 &  1785 &  1780 & 1827 \\
+							& $\times$ &      0  &    22 &     0 &   216 & 61 \\ \hline
+\multirow{3}{*}{StringFuzz}	& SAT      &    528  &   671 &   264 &   491 & 688 \\
+							& UNSAT    &    320  &   240 &   186 &   192 & 339 \\
+							& $\times$ &    217  &   154 &   615 &   382 & 38 \\\hline
+\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 13 & 11 &   12 &     8 & 247 \\
+							& UNSAT    &    820  &   818 &   808 &   772 & 500 \\
+							& $\times$ &      2  &     6 &    15 &    55 & 88 \\ \hline
+\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 & 311 \\
+							& UNSAT    &   1031  &   936 &  1021 &   958 & 596 \\
+							& $\times$ &      1  &   101 &    19 &    70 & 138 \\ \hline
+\multirow{3}{*}{Total} 		& SAT      &  22736  & 21517 & 17702 &  4253 & 21305  \\
+							& UNSAT    &   8301  &  7834 &  7731 &  7649 & 7172  \\
+							& $\times$ &    595  &  2281 &  6199 & 19730 & 3155  \\\hline	
 \end{tabular}}
@@
 
+\hide{
+% wider table for 30s timeout data
 \begin{table}[h]
 \centering
-\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraints + String-Number Conversion benchmark.}
+\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
+\scalebox{0.8}{
+\begin{tabular}{|l r | r r r r|| r r r r|}
+\hline
+\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
+\multirow{3}{*}{Leetcode}		& SAT      &   2413  &  1543 &  1892  &   217 \\ 
+								& UNSAT    &  16511  & 15676 & 16105  & 15374 \\
+								& $\times$ &      3  &  1708 &   930  &  3336 \\ \hline 
+\multirow{3}{*}{PythonLib}		& SAT      &    424  &   408 &   797  &   201 \\ 
+								& UNSAT    &   2056  &   660 &   724  &   644 \\
+								& $\times$ &    166  &  1578 &  1125  &  1801 \\ \hline
+\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
+								& UNSAT    &      0  &     0 &     0  &     0 \\
+								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
+\multirow{3}{*}{Total}			& SAT      &   2857  &  1957 &  2705  &   422 \\ 
+								& UNSAT    &  18567  & 16336 & 16829  & 16018 \\
+								& $\times$ &    169  &  3300 &  2059  &  5153 \\ \hline
+\end{tabular}}
+\label{table:str_int_benchmark}
+\end{table}
+}
+
+% latest backup of table 2
+\begin{table}[h]
+\centering
+\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
 \scalebox{0.8}{
@@
 \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2413  &  1543 &  1025  &   333 \\ 
-										 & UNSAT    &  16511  & 15676 & 17234  & 15543 \\
-										 & $\times$ &      3  &  1708 &   668  &  3051 \\ \hline 
-\multirow{3}{*}{String-Number-PythonLib} & SAT      &    424  &   408 &  1802  &   389 \\ 
-										 & UNSAT    &   2056  &   660 &   744  &   729 \\
-										 & $\times$ &    166  &  1578 &   100  &  1528 \\ \hline
-\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20  &     6 &    16  &     4 \\ 
+\multirow{3}{*}{Leetcode}		& SAT      &   2413  &  1543 &  1892  &   217 \\ 
+								& UNSAT    &  16511  & 15676 & 16105  & 15374 \\
+								& $\times$ &      3  &  1708 &   930  &  3336 \\ \hline 
+\multirow{3}{*}{PythonLib}		& SAT      &    424  &   408 &   797  &   201 \\ 
+								& UNSAT    &   2056  &   660 &   724  &   644 \\
+								& $\times$ &    166  &  1578 &  1125  &  1801 \\ \hline
+\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
 								& UNSAT    &      0  &     0 &     0  &     0 \\
 								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}					 & SAT      &   2857  &  1957 &  2843  &   726 \\ 
-										 & UNSAT    &  18567  & 16336 & 17978  & 16272 \\
-										 & $\times$ &    169  &  3300 &   772  &  4595 \\ \hline
+\multirow{3}{*}{Total}			& SAT      &   2857  &  1957 &  2705  &   422 \\ 
+								& UNSAT    &  18567  & 16336 & 16829  & 16018 \\
+								& $\times$ &    169  &  3300 &  2059  &  5153 \\ \hline
 \end{tabular}}
@@
 If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases.
-But we believe this is not very important because both these two benchmarks are artificial, either hand-crafted or randomly produced from a fuzzer.
-The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.
+But we believe this is not very important because both these two benchmarks are artificial, either hand-crafted or randomly generated.
+The more critical ones are those come from program analysis, in which {\tool} has comparable performance to the best tool.
 
 From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
-The total number of failed cases is only one-fourth to Z3, which is ranked the 2nd.
-In fact, most of the failed tests comes from the analysis of one Python core library function that converts an IPv6 address to a number.
-We generated 2028 tests from this function, and among them around 150 cases that are too difficult for all solvers.
-If we exclude results on this function, then {\tool} has only $185$ failed case in total.
+The total number of failed cases is only a half to Z3, which is ranked the 2nd.
+In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number.
+We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
+If we exclude results on this function, then {\tool} has only $185$ failed cases in total.
 This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total.
-\yfc{This paragraph needs to be revised when new data of Z3-Trau is available.
-Note that z3seq is much more better now.
-Also is z3-trau.}
+\todo{Check and revise the numbers after table updated.}
 
-\hide{ % data for helping to write comparison
-benchmark_path: lib_int-ipaddress__ip_int_from_string
-benchmark_size: 2028
-(tool-check_date, #sat, #unsat, #timeout, #unknown, #exception/error, #misc)
-(cvc4-20191120, 96, 367, 1565, 0, 0, 0)
-(z3-trau-20191122, 135, 1739, 154, 0, 0, 0)
-(z3seq-20191118, 1509, 431, 88, 0, 0, 0)
-(z3str3-20191118, 191, 440, 1330, 5, 0, 62)
-
-benchmark_path: leetcode_int-
-benchmark_size: 18927
-(tool-check_date, #sat, #unsat, #timeout, #unknown, #exception/error, #misc)
-(z3seq-20191118, 1025, 17234, 668, 0, 0, 0)
-(cvc4-20191120, 1543, 15676, 1708, 0, 0, 0)
-(cvc4-20191118, 1766, 15612, 1549, 0, 0, 0)
-(z3-trau-20191122, 2413, 16511, 3, 0, 0, 0)
-(z3str3-20191118, 333, 15543, 2031, 952, 0, 68)
-
-benchmark_path: lib_int-
-benchmark_size: 2646
-(tool-check_date, #sat, #unsat, #timeout, #unknown, #exception/error, #misc)
-(cvc4-20191118, 586, 666, 1394, 0, 0, 0)
-(z3seq-20191118, 1802, 744, 100, 0, 0, 0)
-(cvc4-20191120, 408, 660, 1578, 0, 0, 0)
-(z3str3-20191118, 389, 729, 1392, 70, 0, 66)
-(z3-trau-20191122, 424, 2056, 166, 0, 0, 0)
-}
+\todo{Mention about (1) checkLuhn cases (2) out tool solves much more cases if timeout is set to 30s. (3) update table with data of timeout=30s}
 
@@
 \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3-str3 \\ \hline
-2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.2s)  & $\times$ \\
-3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.1s)  & $\times$ \\
+2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
+3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
 4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
 5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
-6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.13s) & $\times$ \\
+6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
 7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
@@
 9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
-10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.53s) & $\times$ \\
-11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.37s) & $\times$ \\
-12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.40s) & $\times$ \\ \hline
+10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
+11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
+12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
 \end{tabular}}

### 2019-11-22 evaluation.tex
Add one paragraph to evaluation.

@@
 In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
-We run it on several examples collected from the LeetCode platform and from Python core libraries.
+We ran it on several examples collected from the LeetCode platform and from Python core libraries.
 We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).
@@
 
-\todo{Mention about (1) checkLuhn cases (2) out tool solves much more cases if timeout is set to 30s. (3) update table with data of timeout=30s}
+To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the the timeout set to 30s.
+Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to about 100, while other tools got almost the same number of timouts with the results of timeout set to 10s.
+Also, we have encoded the checkLuhn algorithm in SMT-lib for cases of 2 to 12 loops (digits).
+These problems ask for a model of a valid credit card number as a string of length 2 to 12 each case.
+We ran these tests additionally to the experiments above with the timeout set to 120s.
+In these tests, {\tool} can solve all 11 problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve these problems (either timeout or UNKNOWN).
+However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops.
+It seems that Z3 has some strategies that can solve problems of even loops efficiently.
+\todo{Update table with data of timeout=30s}
 
+\hide{
 \begin{table}[h]
@@
 \end{table}
+}
 
@@
 \end{table}
-}
-
-\hide{
-\begin{figure}
-\begin{tikzpicture}
-\begin{axis}
-\addplot+[sharp plot]
-coordinates
-{
-(2,0.097)
-(3,0.078)
-(4,0.098)
-(5,0.098)
-(6,0.161)
-(7,0.236)
-(8,0.307)
-(9,0.26)
-(10,0.211)
-(11,0.228)
-(12,0.33)
-};
-\end{axis}
-\end{tikzpicture}
-\caption{checkLuhn: z3-trau}
-\end{figure}
-
-\begin{figure}
-\begin{tikzpicture}
-\begin{axis}
-\addplot+[sharp plot]
-coordinates
-{
-(2,0.266)
-(3,10.084)
-(4,48.791)
-(5,120)
-(6,120)
-(7,120)
-(8,120)
-(9,120)
-(10,120)
-(11,120)
-(12,120)
-};
-\end{axis}
-\end{tikzpicture}
-\caption{checkLuhn: cvc4 (SAT if not timeout)}
-\end{figure}
-
-\begin{figure}
-\begin{tikzpicture}
-\begin{axis}
-\addplot+[sharp plot]
-coordinates
-{
-(2,0.238)
-(3,0.128)
-(4,120)
-(5,120)
-(6,0.134)
-(7,120)
-(8,0.366)
-(9,120)
-(10,0.526)
-(11,0.374)
-(12,0.405)
-};
-\end{axis}
-\end{tikzpicture}
-\caption{checkLuhn: z3 (SAT if not timeout)}
-\end{figure}
-
-\begin{figure}
-\begin{tikzpicture}
-\begin{axis}
-\addplot+[sharp plot]
-coordinates
-{
-(2,0.4743)
-(3,0.56052)
-(4,0.36695)
-(5,0.60905)
-(6,22.06429)
-(7,53.77536)
-(8,118.41196)
-(9,0.50559)
-(10,120)
-(11,0.42953)
-(12,120)
-};
-\end{axis}
-\end{tikzpicture}
-\caption{checkLuhn: z3str3 (UNKNOWN if not timeout)}
-\end{figure}
 }

### 2019-11-22 draft.tex
some attempts to define encode and decode for PA

@@
 The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure  under-approximate the string constraints by restricting the search domain of each string variable to the language defined by some PFA that will be introduced in the next section.
+In this case, our decision procedure  under-approximates the string constraints by restricting the search domain of each string variable to the language defined by some PFA that will be introduced in the next section.
 This approach based on PFA allows very efficient manipulation.
@@
 	\draw[->] (qm1) edge [bend left] node [left]{$\sym{m}{1}$} (qm2) ;
-	\draw[dotted] (qm2) edge [bend left] node [right]{} (qm3) ;
+	\draw[->,dotted] (qm2) edge [bend left] node [right]{} (qm3) ;
 	\draw[->] (qm3) edge [bend left] node [right]{$\sym{m}{l_m-1}$} (qm) ;
@@
 This is due to the fact that 
-every parametric word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$ due to the flatness. 
+every word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$ due to the flatness. 
 More precisely, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquely decoded:
@@
 %
-For example, in the automaton, given at the beginning of this section, 
+For example, in the automaton given at the beginning of this section, 
 from $\parikhwof x {a_0} = \parikhwof x {a_1} = \cdots = \parikhwof x {a_{m-1}}=1$, $\parikhwof x {a^0_1}=\parikhwof x {a^1_1}=\parikhwof x {a^2_1}=2$ and $\parikhwof x {a^i_j}=0$ otherwise,  we derive that $x=a_0(a^0_1a^1_1a^2_1)^2a_1\cdots a_{m-1}$.
@@
 \emph{Parametric flat automaton (PFA)} is then a parametric automaton whose  automaton is flat.
-See Figure~\ref{fig:sfa_def} and~\ref{fig:sfa} for examples of PFAs (only the automata component is shown
-).
+See Figure~\ref{fig:sfa_def} and~\ref{fig:sfa} for examples of PFAs (without interpretation constraints, i.e., $\paf = \true$.).
 
@@
 $\semof {\pa} = \{I(x) \mid x\in L(A),I\in\semof \paf\}$ of all interpretations satisfying $\paf$ of all parametric strings in the language of $A$.
+
+\yfc{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess.
+I just found that we have not defined the restriction of the domain of functions such as $e_{V}$,  maybe need it somewhere.}
+\changed{
+	Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$.
+We call the union of $I$ and the Parikh image $\parikhof{x}$ a \emph{word encoding} of $w$ in $\pa$.
+More formally, a wording encoding of $\pa$ is mapping of the type $\cvar\cup\#\cvar \rightarrow \nat$ and the set of word encodings of $w$ in $\pa$ is defined as $\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$.
+For every word encoding $e\in \encode \pa( w )$, there must be a parametric word $x\in L(P)$ and some valid character assignment $I\in \semof \paf$ such that $I(x) =w$ and $e= I \cup \parikhof{x}$.
+When $e\in \encode \pa( w )$, we also say it \emph{$\pa$-encodes} $w$.
+We lift the encoding function $\encode \pa$ to set of word $W$ by defining  $\encode \pa(W) = \bigcup_{w\in W} \encode \pa(w)$.
+
+	Conversely, given a word encoding $e:\cvar\cup\#\cvar \rightarrow \nat$, the decoding of $e$ in $\pa$ is defined as the set $\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$.
+We lift the decoding function $\decode \pa$ to set of word encodings $E$ by defining  $\encode \pa(E) = \bigcup_{e\in E} \decode \pa(e)$.
+
+	When $\pa$ is flat, Lemma~\ref{lemma:decoding} implies that such $\pa$-encoding can be uniquely decoded.
+The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
+
+}
 
@@
 \\
-\centerline{$\semof {\pa} = \decode \pa \{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I\in\semof\paf\}$.}
+\centerline{$\semof {\pa} = \decode \pa (\{(I\cup \pim)\mid \pim\in\parikhof{L(A)} ,I\in\semof\paf\})$.}
 \end{corollary}
@@
 In this section, we describe formally how to restrict the domain of string variables to patterns defined by PFA. 
-We start the description of the algorithm that converts a string constraint $\insc$ to a linear formula $\outlf$, called the \emph{flattening} of $\insc$, representing the restricted set of solutions.
+We start the description of the algorithm that converts a string constraint $\insc$ to a linear formula, called the \emph{flattening} of $\insc$, representing the restricted set of solutions.  
 %
@@
 %
-The flattening $\outlf$ will be built inductively following the structure of $\insc$.
+The flattening $\underf \dr {\insc}$ (of the input string constraint $\insc$) will be built inductively following the structure of $\insc$.
 For a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
@@
 We show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$ in the following sections.
-At the end we set $\outlf \defeq \underf \dr \insc$.
 
@@
 
-The correctness of the entire construction of $\outlf$ is expressed by  Theorem~\ref{theorem:correct}. 
+The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
 It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
@@
 \begin{theorem}\label{theorem:correct}
-$\decode \dr (\semof {\outlf}) = \semof{\insc}^\dr$ 
+$\decode \dr (\semof {\underf \dr {\insc}}) = \semof{\insc}^\dr$ 
 \end{theorem}
@@
 The synchronization formula $\syncfof{\pa} {\pa'}$ is extracted from $\syncof \pa {\pa'}$ as follows.
-Its first part is the Parikh formula $\parikhfof {\syncof \pa {\pa'}}$ of the product, which encodes all runs of the product.
+Its first part is the Parikh formula $\parikhfof {\syncof \pa {\pa'}}$ of the product, which encodes all accepting runs of $\syncof \pa {\pa'}$.
 %
@@
 The correctness of this construction is stated in Lemma~\ref{lemma:synccorrect} below. 
-The correctness of the construction of under-approximations of equality constraints and regular constraints in Sections~\ref{section:mem}, \ref{section:eq} rely on it. 
+The correctness of the construction of under-approximations of equality constraints and regular constraints in Section~\ref{section:mem} and Section~\ref{section:eq} rely on it. 
 %
@@
 The interpretation restriction formula $\Psi_{\mathit{char}}$ of $\pa'$ then binds the fresh character variables to the character values they represent, 
-namely, $\Psi_{\mathit{char}} = \bigwedge_{a\in\Sigma_\epsilon} v_a = a$. Obviously, $L(A) = \semof{\pa'}$. 
+namely, $\Psi_{\mathit{char}} = \bigwedge_{a\in\Sigma_\epsilon} v_a = \semof{a}$. Obviously, $L(A) = \semof{\pa'}$. 
 We then let 
@@
 \newcommand{\lv}{l_v}
-Length constraints are encoded precisely by flattening, not under-approximated. 
-Given a length constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
+%Integer constraints are encoded precisely by flattening, not under-approximated. 
+Given a integer constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
 We use a version of $\phi_l$ where every occurrence of every length term $|x|$ is replaced by an auxiliary length variable $\lx$ and we add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Flattening of String-Integer Conversion} \label{section:s2i}
+\section{Flattening of String-Number Conversion} \label{section:s2i}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving. 
-We will now discuss the special form of $\dr(x)$, called numeric PFA, which we choose for string variables appearing in string-integer constraints and that leads to efficient underapproximation technique.
+We will now discuss the special form of $\dr(x)$, called \emph{numeric PFA}, which we choose for string variables appearing in string-integer constraints and that leads to efficient under-approximation technique.
 %
 Besides simple induced linear formulae, we still want single $\dr(x)$ to cover as many numerals as possible.
-We want an ``easy" completeness property, that is,  the space of all numerals can be covered completely by our special numeric PFAs, and that these numeric PFAs are generated easily, and each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
-%
-Particularly, we will proceed towards a definition of \emph{number PFA} $(A^m,\paf^m),m\in\nat$ which covers all numerals that encode integers with $m$ digits.
+We want an ``easy" completeness property, that is,  (1) the space of all numerals can be covered completely by our special numeric PFAs, (2) these numeric PFAs are generated easily, and (3) each of them covers a large and practically significant portion of numerals (so that satisfiable assignments can be often found within the domain restriction of just few of numeric PFAs).
+%
+Particularly, we will proceed towards a definition of \emph{numeric PFA} $(A^m,\paf^m),m\in\nat$ which covers all numerals that encode integers with $m$ digits.
 
@@
 %
-A last problem still needed to be solved beofe they can be efficient in practice. 
+A last problem still needed to be solved before they can be efficient in practice. 
 %
@@
 $
-\semof {\underf \dr {\psi_s} }_{V_\dr \cup \#V_\dr \cup \{n\}} = \encode  \dr(\semof{\phi_s})
+\semof {\underf \dr {\psi_s} }_{V_\dr \cup \#V_\dr} = \encode  \dr(\semof{\phi_s})
 $

### 2019-11-22 draft.tex
some attempts to define encode and decode for PA

@@
 $\semof {\pa} = \{I(x) \mid x\in L(A),I\in\semof \paf\}$ of all interpretations satisfying $\paf$ of all parametric strings in the language of $A$. 
+\yfc{I just found that we have not defined the restriction of the domain of functions such as $e_{V}$,  maybe need it somewhere. }
 
 \yfc{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess.
-I just found that we have not defined the restriction of the domain of functions such as $e_{V}$,  maybe need it somewhere.}
+It is planed to be a replacement of the text below him.
+One interesting observation: the definitions of both are almost the same
+	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
+	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
+	}
 \changed{

### 2019-11-22 draft.tex
added citation on Ecmascript

--- 2019-11-22 draft.tex
@@
 A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indices are converted to strings.
-This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{?} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{ecmascript2019ecmascript} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
 Therefore, any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.

### 2019-11-22 draft.tex
add definition of the project operation

--- 2019-11-22 draft.tex
@@
 we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
-We use $\modelsof \phi$ to denote the set all models of $\phi$.%
+We use $\modelsof \phi$ to denote the set all models of $\phi$ \changed{and use $\modelsof \phi_{V'}$ to denote all models of $\phi$ projected to the domain $V'$}.%
 %Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
@@
 The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$. 
-The Parikh image of a language $L$ is defined as folllows $\parikhof L = \{\parikhof w \mid w \in L\}$.
+The Parikh image of a language $L$ is defined as follows $\parikhof L = \{\parikhof w \mid w \in L\}$.
 %and the Parikh image of an FA $A$ is Parikh image of its language, $\parikhof{A} = \parikhof{L(A)}$.
 %
-It is well known that the Parikh image of a regular language  can be  charctaerized by a linear formula:
+It is well known that the Parikh image of a regular language  can be  characterized by a linear formula:
 

### 2019-11-22 draft.tex
add definition of the project operation

@@
 we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
-We use $\modelsof \phi$ to denote the set all models of $\phi$ \changed{and use $\modelsof \phi_{V'}$ to denote all models of $\phi$ projected to the domain $V'$}.%
+We use $\modelsof \phi$ to denote the set all models of $\phi$ \changed{and use $\modelsof \phi_{V'}$ to denote the same set but projected to the domain $V'$}.%
 %Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 

### 2019-11-22 draft.tex
add decode and encode for PA

@@
 we denote by $I\models \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$. 
-We use $\modelsof \phi$ to denote the set all models of $\phi$ \changed{and use $\modelsof \phi_{V'}$ to denote the same set but projected to the domain $V'$}.%
+We use $\modelsof \phi$ to denote the set all models of $\phi$.%
 %Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
@@
 $\semof {\pa} = \{I(x) \mid x\in L(A),I\in\semof \paf\}$ of all interpretations satisfying $\paf$ of all parametric strings in the language of $A$.
-\yfc{I just found that we have not defined the restriction of the domain of functions such as $e_{V}$,  maybe need it somewhere. }
-
-\yfc{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess.
+
+\hide{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess.
 It is planed to be a replacement of the text below him.
@@
 \changed{
+The function $\encode \pa$ below encodes a word $w$ to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
+	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
+	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
+Informally, a word encoding $e\in \encode \pa( w )$ means $w$ corresponds to a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$.
+Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple word, as formalized in the definition of $\decode \pa(e)$.
+For the case that $\pa$ is flat, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$.
+The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
+}
+
+\hide{
 	Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$.

### 2019-11-22 draft.tex
add decode and encode for PA

@@
 Informally, a word encoding $e\in \encode \pa( w )$ means $w$ corresponds to a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$.
-Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple word, as formalized in the definition of $\decode \pa(e)$.
-For the case that $\pa$ is flat, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$.
+Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.
+For the case that $\pa$ is a PFA, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$.
 The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
@@
 }
+\yfc{Plan to remove this one and use the orange one.
 
@@
 We  hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ in the straightforward manner (i.e.,  $\decode \pa(I \cup \parikhof x) = w$).   
-The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
+The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:}
 

### 2019-11-22 draft.tex
intro, work in progress

@@
  is known to be {\sc Pspace}-complete while it is in {\sc NP} for the class of flat automata).
-This is due to the fact that 
-every word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$ due to the flatness. 
+This is possible thanks to the flatness, which causes that 
+every word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$. 
 More precisely, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquely decoded:
@@
  every variable appears on at most one transition.
-Thus, the accepting run on $w$ (and so $w$ itself) can thus be reconstructed from $\parikhof w$.
+Thus, the accepting run on $w$ (and so $w$ itself) can be reconstructed from $\parikhof w$.
 More concretely, the function $\decode A$ can be implemented as follows.
@@
 \paragraph{Parametric (flat) automata}
-Next we define \emph{parametric automaton} (PA) as a pair  $\pa = (A,\paf)$ where 
+Next, we define \emph{parametric automaton} (PA) as a pair  $\pa = (A,\paf)$ where 
 $A$ is an automaton operating over an alphabet $\cvar$ of \emph{character variables}  

### 2019-11-22 draft.tex
typos and little poking of the orrange mess

@@
 \changed{
-The function $\encode \pa$ below encodes a word $w$ to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
+We say that a mapping $e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $e = \parikhof{x}\cup I$ for
+for some $x \in L(A)$ and $I\in\semof\paf$ such that $w = I(x)$.   
+%
+Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
+%
+We use $\encode \pa(w)$ below to denote all $\pa$-encoding of a word $w$,
+and $\decode \pa (e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
+% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
 	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
@@
 }
+
+%The function $\encode \pa$ below encodes a word $w$ to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
+%	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
+%	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
+%Informally, a word encoding $e\in \encode \pa( w )$ means $w$ corresponds to a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$.
+Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.
+For the case that $\pa$ is a PFA, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$.
+The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
 

### 2019-11-22 draft.tex
sec 6

--- 2019-11-22 draft.tex
@@
 
-\hide{Some attempts to define both encodes and decodes of PA, need more explanation of why we define them I guess.
-It is planed to be a replacement of the text below him.
-One interesting observation: the definitions of both are almost the same
-	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
-	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
-	}
 \changed{
@@
 
-\hide{
-	Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$.
-We call the union of $I$ and the Parikh image $\parikhof{x}$ a \emph{word encoding} of $w$ in $\pa$.
-More formally, a wording encoding of $\pa$ is mapping of the type $\cvar\cup\#\cvar \rightarrow \nat$ and the set of word encodings of $w$ in $\pa$ is defined as $\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$.
-For every word encoding $e\in \encode \pa( w )$, there must be a parametric word $x\in L(P)$ and some valid character assignment $I\in \semof \paf$ such that $I(x) =w$ and $e= I \cup \parikhof{x}$.
-When $e\in \encode \pa( w )$, we also say it \emph{$\pa$-encodes} $w$.
-We lift the encoding function $\encode \pa$ to set of word $W$ by defining  $\encode \pa(W) = \bigcup_{w\in W} \encode \pa(w)$.
-
-	Conversely, given a word encoding $e:\cvar\cup\#\cvar \rightarrow \nat$, the decoding of $e$ in $\pa$ is defined as the set $\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$.
-We lift the decoding function $\decode \pa$ to set of word encodings $E$ by defining  $\encode \pa(E) = \bigcup_{e\in E} \decode \pa(e)$.
-
-	When $\pa$ is flat, Lemma~\ref{lemma:decoding} implies that such $\pa$-encoding can be uniquely decoded.
-The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
-
-}
 \yfc{Plan to remove this one and use the orange one.
@@
 In this section, we describe formally how to restrict the domain of string variables to patterns defined by PFA. 
-We start the description of the algorithm that converts a string constraint $\insc$ to a linear formula, called the \emph{flattening} of $\insc$, representing the restricted set of solutions.  
+We start the description of the algorithm that converts a string constraint $\insc$ to a linear formula representing the set of solutions under the domain restriction.  
 %
@@
 %
-The flattening $\underf \dr {\insc}$ (of the input string constraint $\insc$) will be built inductively following the structure of $\insc$.
+The \emph{flattening} of the input string constraint $\insc$, denoted $\underf \dr {\insc}$, will be built inductively following the structure of $\insc$.
 For a conjunction of string constraints, we let $\underf \dr {\phi \land \phi'} \defeq \underf \dr {\phi} \land \underf \dr {\phi'}$.
@@
 The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
+\changed{
 It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$.
+The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint.
+Formally, $\dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
+$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
+
+}
+
+\yfc{It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
 For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variables $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
@@
 That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the ${\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
+}
 We lift $\decode \dr$ to sets of interpretations in the standard manner.

### 2019-11-22 draft.tex
more of orrange hell

--- 2019-11-22 draft.tex
@@
 	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
-Informally, a word encoding $e\in \encode \pa( w )$ means $w$ corresponds to a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$.
-Since $e$ has only the information of number of occurrences of character variables (Parikh image), the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.
-For the case that $\pa$ is a PFA, by Lemma~\ref{lemma:decoding} each word encoding $e\in \encode \pa( w )$ uniquely encodes the word $w$.
-The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
+Informally, that a word encoding $e$ belongs to $\encode \pa( w )$ means that $w$ is an interpretation of a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$.
+Since $e$ only records the numbers of occurrences of character variables (Parikh image), 
+the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.
+
+If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
+$$
+w = \decode \pa (\encode \pa (w))
+$$
+Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
+Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
+%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
 }

### 2019-11-22 draft.tex

--- 2019-11-22 draft.tex
@@
 \changed{
-The function $\encode \pa$ below encodes a word $w$ to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
+We say that a mapping $e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $e = \parikhof{x}\cup I$
+for some $x \in L(A)$ and $I\in\semof\paf$ such that $w = I(x)$.   
+%
+Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
+%
+We use $\encode \pa(w)$ below to denote all $\pa$-encoding of a word $w$,
+and $\decode \pa (e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
+% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
 	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
@@
 Formally, $\dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
-$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
+$I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
 

### 2019-11-22 draft.tex
sec 6
sec 5

@@
 \changed{
-We say that a mapping $e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $e = \parikhof{x}\cup I$
-for some $x \in L(A)$ and $I\in\semof\paf$ such that $w = I(x)$.   
+We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.
 %
@@
 %
-We use $\encode \pa(w)$ below to denote all $\pa$-encoding of a word $w$,
-and $\decode \pa (e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
+We use $\encode \pa(w)$ below to denote all $\pa$-encodings of a word $w$,
+and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
 % to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
-	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
-	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
-Informally, that a word encoding $e$ belongs to $\encode \pa( w )$ means that $w$ is an interpretation of a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$.
-Since $e$ only records the numbers of occurrences of character variables (Parikh image), 
-the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.
+	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
+	$$\decode \pa(I_e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$
+
+Since a word encoding $I_e$ only records the numbers of occurrences of character variables (Parikh image), 
+the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(I_e)$.
 
@@
 $$
-w = \decode \pa (\encode \pa (w))
+\{w\} = \decode \pa (\encode \pa (w))
 $$
@@
 The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint.
-Formally, $\dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
+Formally, $\decode  \dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
 $I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
@@
 encodings 
-$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode \pa(w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
+$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode {\pa'} (w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
 

### 2019-11-22 draft.tex
sec 5

@@
 
-\changed{
 We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.
@@
 %words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
-}
-
-\yfc{Plan to remove this one and use the orange one.
+
+\hide{Plan to remove this one and use the orange one.
 

### 2019-11-22 draft.tex
sec 5

@@
 %
-Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
+Conversely, $w$ is a \emph{$\pa$-decoding} of $I_e$.
 %
 We use $\encode \pa(w)$ below to denote all $\pa$-encodings of a word $w$,
-and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
+and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $I_e$. Namely,  
 % to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
-	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
+	$$\encode \pa( w ) = \{I_e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
 	$$\decode \pa(I_e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$
@@
 
-If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
+If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $I_e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
 $$

### 2019-11-22 draft.tex
sec 6

@@
 $$
-\{w\} = \decode \pa (\encode \pa (w))
+w = \decode \pa (\encode \pa (w))
 $$
@@
 The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
-\changed{
 It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
 The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint. 
-Formally, $\decode  \dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
-$I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
-
-}
-
-\yfc{It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
-For an interpretation $e \cup I'$ consisting of an interpretation $e$ of $V_\dr$ and $\#V_\dr$ and an interpretation of integer variables $I'$, we let $\decode \dr (e\cup I') = I \cup I'$ where $I$ is the interpretation of string variables such that for each $x\in X$,
-$I(x) = \decode {\dr(x)} (e_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.
-That is, $\decode \dr (e\cup I')$ returns the original integer interpretation $I'$ together with each string variable $x$ interpreted as the ${\dr(x)}$-decoding of the values of $V_{\dr(x)}$ and $\#V_{\dr(x)}$.
-}
-We lift $\decode \dr$ to sets of interpretations in the standard manner.
+Formally, 
+$\decode  \dr (I_e\cup I_z) = \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
+The condition says each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
+We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
+those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
+We define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
+%
+namely, for a model $I_s \cup I_z$ of a string constraint,  
+we let $\encode \dr (I_s \cup I_z) \defeq \{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
+We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
 \begin{theorem}\label{theorem:correct}
@@
 (indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf \dr {\phi} \land \underf \dr {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^\dr$).
-
 %To formalize this correctness argument, we need the notion of 
@@
 %An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
-
-To formalize this correctness argument, we define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
-%
-namely, for a set $J$ of string/integer variables interpretations,  
-we let $\encode \dr (J) \defeq \{e\mid \decode \dr (e) \in J\}$.
 %\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
@@
 encodings 
-$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode {\pa'} (w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
+$I_e$ and $I_e'$ such that $I_e\in\encode \pa(w)$ and $I_e'\in\encode {\pa'} (w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
 
@@
 \semof {\syncfof \pa {\pa'}}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e\cup e'\mid e \in \encode \pa (w), e'\in\encode {\pa'} (w), w\in\semof \pa \cap \semof {\pa'}\} 
+\{I_e\cup I_e'\mid I_e \in \encode \pa (w), I_e'\in\encode {\pa'} (w), w\in\semof \pa \cap \semof {\pa'}\} 
 $
@@
 For PFA $\pa$ and $\pa'$,  
-$\semof{\pa\cdot \pa'} = \semof{\pa}\cdot\semof{\pa'}$ and 
+%$\semof{\pa\cdot \pa'} = \semof{\pa}\cdot\semof{\pa'}$ and 
 $\encode{\pa\cdot \pa'}{(\semof{\pa\cdot \pa})}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{e \cup e'\mid e \in \encode \pa (\semof{\pa}) \wedge e' \in\encode {\pa'} (\semof{\pa'})\}$.
+\{I_e \cup I_e'\mid I_e \in \encode \pa (\semof{\pa}) \wedge I_e' \in\encode {\pa'} (\semof{\pa'})\}$.
 \end{lemma}

### 2019-11-22 draft.tex
sec 6

@@
 It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
-The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint. 
+The $\decode \dr$ function maps a \emph{ many-words encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint.
+Note that the many-words encoding $I_e$ is a union of ${\dr(x)}$-encodings for all $x$ in $X$.
 Formally, 
@@
 The condition says each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
-We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
+%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
 those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
@@
 namely, for a model $I_s \cup I_z$ of a string constraint,  
-we let $\encode \dr (I_s \cup I_z) \defeq \{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
+we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
 We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.

### 2019-11-22 draft.tex
little wording variant of R-decoding encoding

@@
 
+\changed{
+The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
+It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
+The function takes as an argument an $\dr$-encoding of a string constraint, an interpretation $I_e \cup I_z$ consisting of a \emph{many-word encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ and an integer variables $I_z$.
+Intuitively, the many-word encoding $I_e$ contains for each $x\in X$ a $\dr(x)$-encoding of its value. 
+The function then returns the set of string constraint interpretations 
+$\decode  \dr (I_e\cup I_z) \defeq \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
+The condition says that each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
+%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
+those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
+We also define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
+%
+namely, for a model $I_s \cup I_z$ of a string constraint,  
+we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
+We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
+}
+
 The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 

### 2019-11-23 evaluation.tex
Update table with z3-trau data

@@
 \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      &  21205  & 19763 & 16528 &  3030 & 19149 \\ 
-							& UNSAT    &   3963  &  3834 &  3831 &  3836 & 3828 \\
-							& $\times$ &    253  &  1824 &  5062 & 18555 & 2444 \\ \hline
-\multirow{3}{*}{APLAS}		& SAT      &    135  &   205 &    12 &    37 & 132 \\
-							& UNSAT    &    343  &   221 &   100 &   111 & 82 \\
-							& $\times$ &    122  &   174 &   488 &   452 & 386 \\ \hline
-\multirow{3}{*}{LeetCode}	& SAT      &    842  &   859 &   881 &   670 & 778 \\
-							& UNSAT    &   1824  &  1785 &  1785 &  1780 & 1827 \\
+\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 & 19149 \\ 
+							& UNSAT    &   3883  &  3834 &  3831 &  3836 & 3828 \\
+							& $\times$ &    128  &  1824 &  5062 & 18555 & 2444 \\ \hline
+\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 & 132 \\
+							& UNSAT    &    288  &   221 &   100 &   111 & 82 \\
+							& $\times$ &    181  &   174 &   488 &   452 & 386 \\ \hline
+\multirow{3}{*}{LeetCode}	& SAT      &    880  &   859 &   881 &   670 & 778 \\
+							& UNSAT    &   1786  &  1785 &  1785 &  1780 & 1827 \\
 							& $\times$ &      0  &    22 &     0 &   216 & 61 \\ \hline
-\multirow{3}{*}{StringFuzz}	& SAT      &    528  &   671 &   264 &   491 & 688 \\
-							& UNSAT    &    320  &   240 &   186 &   192 & 339 \\
-							& $\times$ &    217  &   154 &   615 &   382 & 38 \\\hline
-\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 13 & 11 &   12 &     8 & 247 \\
+\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 & 688 \\
+							& UNSAT    &    319  &   240 &   186 &   192 & 339 \\
+							& $\times$ &    248  &   154 &   615 &   382 & 38 \\\hline
+\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 & 247 \\
 							& UNSAT    &    820  &   818 &   808 &   772 & 500 \\
-							& $\times$ &      2  &     6 &    15 &    55 & 88 \\ \hline
+							& $\times$ &      4  &     6 &    15 &    55 & 88 \\ \hline
 \multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 & 311 \\
@@
 							& $\times$ &      1  &   101 &    19 &    70 & 138 \\ \hline
-\multirow{3}{*}{Total} 		& SAT      &  22736  & 21517 & 17702 &  4253 & 21305  \\
-							& UNSAT    &   8301  &  7834 &  7731 &  7649 & 7172  \\
-							& $\times$ &    595  &  2281 &  6199 & 19730 & 3155  \\\hline	
+\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 & 21305  \\
+							& UNSAT    &   8127  &  7834 &  7731 &  7649 & 7172  \\
+							& $\times$ &    562  &  2281 &  6199 & 19730 & 3155  \\\hline	
 \end{tabular}}
@@
 \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{Leetcode}		& SAT      &   2413  &  1543 &  1892  &   217 \\ 
-								& UNSAT    &  16511  & 15676 & 16105  & 15374 \\
-								& $\times$ &      3  &  1708 &   930  &  3336 \\ \hline 
-\multirow{3}{*}{PythonLib}		& SAT      &    424  &   408 &   797  &   201 \\ 
-								& UNSAT    &   2056  &   660 &   724  &   644 \\
-								& $\times$ &    166  &  1578 &  1125  &  1801 \\ \hline
+\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
+								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
+								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
+\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
+								& UNSAT    &    720  &   660 &   724  &   644 \\
+								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
 \multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
@@
 								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}			& SAT      &   2857  &  1957 &  2705  &   422 \\ 
-								& UNSAT    &  18567  & 16336 & 16829  & 16018 \\
-								& $\times$ &    169  &  3300 &  2059  &  5153 \\ \hline
+\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
+								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
+								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
 \end{tabular}}
@@
 \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{Leetcode}		& SAT      &   2413  &  1543 &  1892  &   217 \\ 
-								& UNSAT    &  16511  & 15676 & 16105  & 15374 \\
-								& $\times$ &      3  &  1708 &   930  &  3336 \\ \hline 
-\multirow{3}{*}{PythonLib}		& SAT      &    424  &   408 &   797  &   201 \\ 
-								& UNSAT    &   2056  &   660 &   724  &   644 \\
-								& $\times$ &    166  &  1578 &  1125  &  1801 \\ \hline
+\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
+								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
+								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
+\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
+								& UNSAT    &    720  &   660 &   724  &   644 \\
+								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
 \multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
@@
 We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
-If we exclude results on this function, then {\tool} has only $185$ failed cases in total.
-This is significantly better than the 2nd place tool Z3, which fails $893$ cases in total.
-\todo{Check and revise the numbers after table updated.}
+If we exclude results on this function, then {\tool} has only $218$ failed cases in total.
+This is significantly better than the 2nd place tool Z3, which fails $942$ cases in total.
 

### 2019-11-23 draft.tex
abstract wording

@@
 \begin{abstract}
-String-number conversion is an important class of constraint needed for the symbolic execution of string-manipulating programs.
+String-number conversion is an important class of constraints needed for the symbolic execution of string-manipulating programs.
 In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages.
 However, the state-of-the-art constraint solvers have only very limited support to this type of constraint.
-To overcome these limitations, we propose, in this paper, an approach that can support a combination of string-number conversion as well as other common types of string constraints efficiently.
+We propose to overcome these limitations with an approach that can efficiently support both string-number conversion and other common types of string constraints.
 Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.

### 2019-11-23 draft.tex
intro - upto the beginning of the technical part (of the intro sec)

@@
 
-For many languages such as Java, string-number conversions are core operations, and much symbolic execution can not been done without supporting it.
-In fact,  a code that receives input tends to need to convert at least some of that input into numbers,  which makes the handling of string-integer conversions of the utmost importance.
-For example, the program fragment below is a variant of the Luhn test algorithm that is often used in credit card or personal ID validation.
+%For many languages such as Java, string-number conversion is not a core operation, and much symbolic execution can be done without supporting it; however, this is not true of scripting languages, of which JavaScript is the most notable.
+%For many languages such as JavaScript, string-number conversions are core operations, and symbolic execution cannot be done without supporting it.
+In fact, a code that receives string input tends to need to convert at least some of that input into numbers.
+%,  which makes the handling of string-integer conversions of the utmost importance.  \yfc{maybe this is a too strong argument using this example}
+For example, the program fragment below is a variant of the Luhn test algorithm that is often used in credit card or ID validation.
 
@@
 For the value of every even digit, the algorithm (1) doubles its value, (2) subtracts its value by $9$ if the doubled-value is larger than $9$, and (3) adds the final result to \verb|sum|.
-At the end, the input is validated if the string value of \verb|sum| ends by an $0$ (i.e., \verb| sum mod 10=0|).
-
-To check whether the program path that traverses both loops exactly once, which corresponds to the case when $| \verb|value||=2$, and finally passes this test has a valid input, we create the following (string) constraint:
+At the end, the input is validated if the last digit of \verb|sum| is $0$ (i.e., \verb| sum mod 10=0|).
+
+To check whether the program path that traverses both loops exactly once and finally passes this test has a valid input, we create the following (string) constraint:
 
@@
 
-Even, more crucially, in many programming languages, string-number conversion is a part of the definition of the core semantics of the language. 
+Even, more crucially, in many programming languages, string-number conversion is a part of the definition of their core semantics. 
  JavaScript, which powers most interactive content on the Web and increasingly server-side code with Node.js, is one of such languages.
@@
 This is a rather basic   array operation in JavaScript, and not  handling string-number conversion operations will cripple any analysis of non-trivial JavaScript code.
-Thus, we need stronger solvers that are  able to handle string-number conversion operations in order to be able to analyse  real code.
+Thus, we need stronger solvers that are  able to handle string-number conversion operations in order to be able to analyze  real code.
 

### 2019-11-23 draft.tex
intro

@@
 In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$  and replacing the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
-The over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
-Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
 Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
@@
 Then, we show that given such restriction, one can  reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-To gain in efficiency, we label each transition  of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
+To gain in efficiency, we label each transition  of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between every two states for each symbol in the alphabet.
 This done by associating to each character in our alphabet a unique natural number.
-This allows us to  to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers and it is  the key for handling string-number conversion efficiently.
+This allows us to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers and it is  the key for handling string-number conversion efficiently.
 
@@
 
-\item An open source tool with experimental
+\item An open source tool {\tool} with experimental
 results that demonstrate the efficiency of

### 2019-11-23 draft.tex
sec 2

@@
 $\{k\mid n\leq k \leq m\}$. 
-The function $f$ with the domain restricted to $D$ is denoted by $\restrict f D$,
-and a set of functions $F$ restricted to $D$ is $\restrict F D = \{\restrict f D \mid f \in F\}$.
+The function $f$ with the domain restricted to a set $D$ is denoted by $\restrict f D$,
+and a set of functions $F$ restricted to a set $D$ is $\restrict F D = \{\restrict f D \mid f \in F\}$.
 An \emph{alphabet} is a finite set $\Sigma$ of \emph{characters} and a \emph{word} over $\Sigma$ is a sequence $w = a_1\ldots a_n$ of characters from $\Sigma$, with $\epsilon$ denoting the \emph{empty word}.
@@
 \begin{lemma}[\cite{SeidlSMH04}]
-Let $A$ be a FA over the alphabet $\Sigma$. Then, we can compute, in linear time,  a linear formula $\parikhfof{A}$, over $\pvarsof \Sigma$, such that $\modelsof{\parikhfof A} = \parikhof{L(A)}$.
-
+Let $A$ be a FA over the alphabet $\Sigma$.
+Then, we can compute, in linear time,  a linear formula $\parikhfof{A}$, over $\pvarsof \Sigma$, such that $\modelsof{\parikhfof A}_{\#\Sigma} = \parikhof{L(A)}$.
 \end{lemma}

### 2019-11-23 draft.tex
sec 3

@@
 \newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
-\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
-\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
+\newcommand{\varn}{\mbox{$V$}}
+\newcommand{\vars}{\mbox{$X$}}
 \newcommand{\cvars}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
@@
 
-We call $\vars$ the set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ the set of \emph{integer variables} ranging over $\mathbb{Z}$.
-For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$) its \emph{variants}.
-In this paper, we use $x,y$ (or their variants) to denote string variables and $n$ (or its variants) to denote integer variables.
-An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I$ from $\vars\cup \varn$ to $\Sigma^* \cup \mathbb{Z}$.
-A \emph{term} is an element in $(\vars\cup \Sigma)^*$.
-We lift the interpretation $I$ to terms and linear constraints in the standard manner.
+Assume that $\vars$ ia a set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ a set of \emph{integer variables} ranging over $\mathbb{Z}$.
+%For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$) its \emph{variants}.
+%In this paper, we use $x,y$ (or their variants) to denote string variables and $n$ (or its variants) to denote integer variables. 
+An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I:\vars\cup \varn\rightarrow\Sigma^* \cup \mathbb{Z}$.
+A \emph{word term} is an element in $\vars^*$.
+We lift the interpretation $I$ to word terms and linear constraints in the standard manner.
 
@@
 $\bullet$ An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
-t_2$ are terms. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
+t_2$ are word terms. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
 I(t_1)=I(t_2)\}$. A \emph{disequality constraint} $\phi_d$ is of the form $t_1 \neq 
@@
 \smallskip
-$\bullet$ An \emph{integer constraint} $\phi_i$ is a linear constraint over the variables in $\varn$ and values of $|x|$ for all $x \in \vars$, where $|\cdot|:\vars \rightarrow \nat$ is the string length function defined in the standard way.
+$\bullet$ An \emph{integer constraint} $\phi_i$ is a linear constraint over the integer variables in $\varn$ and values of $|x|$ for all $x \in \vars$, where $|\cdot|:\vars \rightarrow \nat$ is the string length function defined in the standard way.
 %Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.

### 2019-11-23 draft.tex
sec 3
sec 4 and rearrange the figures of intro

@@
 
+In the following, we explain the construction of the linear formula using $\Phi$ as an example.
+Assume that we project the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
+The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.
+Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
+For example, from  $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
+
+The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$, as well as the number of occurrences of each character variable $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+Each model of the linear formula encodes a model of the string constraint.
+For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
+Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
+
+If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
+If not, our procedure changes the PFAs to a more expressive one (by adding more states and transitions) and repeat the analysis.
+We report unknown after failing to prove SAT using a certain number of PFAs.
+
 \begin{figure}
@@
 \end{figure}
-
-In the following, we explain the construction of the linear formula using $\Phi$ as an example.
-Assume that we project the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.
-Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from  $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
-
-The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$, as well as the number of occurrences of each character variable $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
-Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
-The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
-
-If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure changes the PFAs to a more expressive one (by adding more states and transitions) and repeat the analysis.
-We report unknown after failing to prove SAT using a certain number of PFAs.
 
@@
 $\bullet$ A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
-For $a\in [0,9]$, we have $\sti{a}=a$ and for $s \cdot a \in [0,9]^+$, $\sti{s\cdot a} = 10\times \sti{s}+a$.
-For $s\notin [0,9]^+$, $\sti{s}=-1$.
+For $a\in [0,9]$, we have $\sti{a}=a$ and for $w \cdot a \in [0,9]^+$, $\sti{w\cdot a} = 10\times \sti{w}+a$.
+For $w\notin [0,9]^+$, $\sti{w}=-1$.
 We define $\modelsof{\phi_s}= \{I \mid I(n)= \sti{I(x)} \}$.
@@
 The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure  under-approximates the string constraints by restricting the search domain of each string variable to the language defined by some PFA that will be introduced in the next section.
+In this case, our decision procedure  under-approximates the string constraints by restricting the search domain of each string variable to the language defined by some PFA.
 This approach based on PFA allows very efficient manipulation.

### 2019-11-23 draft.tex
tiny fix in orange

--- 2019-11-23 draft.tex
@@
 It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
-The function takes as an argument an $\dr$-encoding of a string constraint, an interpretation $I_e \cup I_z$ consisting of a \emph{many-word encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ and an integer variables $I_z$.
+The function takes as an argument an $\dr$-encoding of a string constraint, an interpretation $I_e \cup I_z$ consisting of a \emph{many-word encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ and an integer variable interpretation $I_z$.
 Intuitively, the many-word encoding $I_e$ contains for each $x\in X$ a $\dr(x)$-encoding of its value. 

### 2019-11-23 draft.tex
sec 5

--- 2019-11-23 draft.tex
@@
 A finite state automaton  
-$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is said to be \emph{flat} if it satisfies the following structural constraints (the figure above):
+$A = (Q,T,\Sigma,\st{0}{0},\st{m}{0})$ is said to be \emph{flat} if it satisfies the following structural constraints (see also the figure above):
 \begin{enumerate}
@@
 The crucial feature of flat automata is that their semantics can be faithfully represented by a linear formula and handled efficiently by an SMT solver.
-Such encoding into linear formula results in efficient algorithms and decision procedure for the class of flat automata and so we avoid dealing with costly standard automata operations (e.g., checking  the non-emptiness of the intersection of several regular languages
- is known to be {\sc Pspace}-complete while it is in {\sc NP} for the class of flat automata).
-This is possible thanks to the flatness, which causes that 
-every word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$. 
+Such encoding into linear formula results in efficient algorithms and decision procedures.
+For instance, we avoid dealing with costly standard automata operations (e.g., checking  the non-emptiness of the intersection of several regular languages is known to be {\sc Pspace}-complete while it is in {\sc NP} for the class of flat automata).
+The encoding is possible due to the flat structure, which has the property that 
+``every word $w\in L(A)$ is uniquely determined by its Parikh image $\parikhof{w}$". 
 More precisely, the Parikh image of a word $w\in L(A)$ can be seen as an encoding of $w$ and can be uniquely decoded:
@@
 %
-\begin{proof}
-First observe that the $\parikhof w$ value of any variable appearing within the a cycle of $A$ is equal to the number of repetitions of that cycle in the accepting run.
+%\begin{proof}
+Observe that the $\parikhof w$ value of any variable appearing within the a cycle of $A$ is equal to the number of repetitions of that cycle in the accepting run.
 This is an immediate consequence of the fact that
- every variable appears on at most one transition.
-Thus, the accepting run on $w$ (and so $w$ itself) can be reconstructed from $\parikhof w$.
+ every variable appears on at most one transition. Thus, the accepting run on $w$ (and so $w$ itself) can be reconstructed from $\parikhof w$.
+
  More concretely, the function $\decode A$ can be implemented as follows. 
@@
 $w_i = (a_i^0 \cdots a_i^{l_{i}-1})^{\pvarsof {a_i^0}}$ if $l_i >0$ and $w_i = \epsilon$ if $l_i = 0$. 
-\end{proof}
-%
+%\end{proof}
+
 For example, in the automaton given at the beginning of this section, 
@@
 % to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
-	$$\encode \pa( w ) = \{I_e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
-	$$\decode \pa(I_e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$
+	$$\encode \pa( w ) \defeq \{I_e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
+	$$\decode \pa(I_e) \defeq\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$
 
@@
 
-If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $I_e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
-$$
-w = \decode \pa (\encode \pa (w))
-$$
-Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
+If we consider ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$, we have\\
+$\encode {\pa_x}( ``aaa" ) =\{ (Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3), Y{\rightarrow}(\semof{\epsilon},\semof{a},3,3)  \}$ and
+$\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
+
+If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, every word encoding $I_e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
+$$
+\{w\} = \decode \pa (\encode \pa (w))
+$$
+
+Similarly, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
 Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.

### 2019-11-23 draft.tex
sec 5

@@
 
-If we consider ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$, we have\\
+\begin{example}
+If we consider the PFA ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$, we have\\
 $\encode {\pa_x}( ``aaa" ) =\{ (Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3), Y{\rightarrow}(\semof{\epsilon},\semof{a},3,3)  \}$ and
 $\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
+\end{example}
 

### 2019-11-23 draft.tex
sec 5

@@
 \newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
-\newcommand{\varn}{\mbox{$V$}}
+\newcommand{\varn}{\mbox{$Z$}}
 \newcommand{\vars}{\mbox{$X$}}
@@
 
-We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$  (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.
+We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} of a word $w$  (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.
 %
@@
 
-\changed{
 The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
 It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
-The function takes as an argument an $\dr$-encoding of a string constraint, an interpretation $I_e \cup I_z$ consisting of a \emph{many-word encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ and an integer variable interpretation $I_z$.
-Intuitively, the many-word encoding $I_e$ contains for each $x\in X$ a $\dr(x)$-encoding of its value. 
-The function then returns the set of string constraint interpretations 
-$\decode  \dr (I_e\cup I_z) \defeq \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
-The condition says that each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
+Let $Z$ be the set of integer variables in $\insc$.
+The function maps an interpretations $I_e$ over $Z\cup V_\dr\cup\#V_\dr$
+to an interpretation over $Z \cup X$, if exists.
+Informally, it ``decodes" an interpretation of integer variables $Z\cup V_\dr\cup\#V_\dr$ to an interpretation of variables in the string constraint $\insc$.
+Formally,
+we define $\decode  \dr (I_e) \defeq \{I \mid \forall z\in Z: I(z) = I_e(z) \wedge\forall x\in X: \{I(x)\} = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
+The condition says that (1) $I$ and $I_e$ are consistent over the $Z$ and (2) $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$ is a word encoding that $\dr(x)$-encodes $I(x)$.
 %We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
@@
 %
-namely, for a model $I_s \cup I_z$ of a string constraint,  
-we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
-We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
-}
-
-The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
-It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. 
-The $\decode \dr$ function maps a \emph{ many-words encoding} $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint.
-Note that the many-words encoding $I_e$ is a union of ${\dr(x)}$-encodings for all $x$ in $X$.
-Formally, 
-$\decode  \dr (I_e\cup I_z) = \{I_s \cup I_z \mid \forall x\in X: I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
-The condition says each string variable $x$ is interpreted as the ${\dr(x)}$-decoding of the word encoding $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$.
-%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
-those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
-We define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
-%
-namely, for a model $I_s \cup I_z$ of a string constraint,  
-we let $\encode \dr (I_s \cup I_z) =\{I_e\cup I_z\mid \decode \dr (I_e\cup I_z) = I_s \cup I_z \}$.
+namely, for a interpretation $I$ of the string constraint $\insc$,  
+we let $\encode \dr (I) =\{I_e\mid \decode \dr (I_e) = I \}$.
 We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.

### 2019-11-23 draft.tex
sec 6

@@
 %
-We note that the restriction of the semantics of $\underf \dr \phi$ here is needed since $\underf \dr \phi$ will be constructed with some auxiliary variables.
+We note that the restriction of $\semof{\underf \dr \phi}$ to $V_\dr\cup V_{\#\dr}$ here is needed since $\underf \dr \phi$ will be constructed with some auxiliary variables.
 

### 2019-11-23 draft.tex
sec 7,8 10

@@
 \newcommand{\restrict}[2]{#1_{#2}}
-\newcommand{\underf}[2]{\mathit{under}_#1(#2)}
+\newcommand{\underf}[2]{\mathit{flatten}_#1(#2)}
 \newcommand{\paf}{\psi}
@@
 
-In the example above, we can detect the array-out-of-bound problem (that happens when \texttt{input} is a string) by checking the satisfiability of the string constraint below\footnote{The case \texttt{input} stores a integer value can be check by another formula.}.
+In the example above, we can detect the array-out-of-bound problem (that happens when \texttt{input} is a string) by checking the satisfiability of the string constraint below\footnote{The case \texttt{input} stores an integer value can be check by another formula.}.
 
@@
 The function maps an interpretations $I_e$ over $Z\cup V_\dr\cup\#V_\dr$
-to an interpretation over $Z \cup X$, if exists.
+to an interpretation over $Z \cup X$, following the domain restriction $\dr$.
 Informally, it ``decodes" an interpretation of integer variables $Z\cup V_\dr\cup\#V_\dr$ to an interpretation of variables in the string constraint $\insc$.
@@
 we define $\decode  \dr (I_e) \defeq \{I \mid \forall z\in Z: I(z) = I_e(z) \wedge\forall x\in X: \{I(x)\} = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})\}$.
-The condition says that (1) $I$ and $I_e$ are consistent over the $Z$ and (2) $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$ is a word encoding that $\dr(x)$-encodes $I(x)$.
+The condition says that (1) $I$ and $I_e$ are consistent over variables in $Z$ and (2) $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$ is a word encoding that $\dr(x)$-encodes $I(x)$.
 %We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
@@
 Particularly, the synchronization formula is built for two PAs  
-$\pa = ((Q,T,\cvarone,q_i,q_f),\paf)$ and ${\pa'} = ((Q',T',\cvartwo,q_i',q_f'),\paf')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
+$\pa {=} ((Q,T,\cvarone,q_i,q_f),\paf)$ and ${\pa'} {=} ((Q',T',\cvartwo,q_i',q_f'),\paf')$ such that $\cvarone \cap \cvartwo = \emptyset$. 
 %
@@
 a run of $\pa$ over a parametric word $x$ and a run of ${\pa'}$ over a parametric word $x'$. 
-The word accepted by the run of $\syncof \pa {\pa'}$ induces constraints on the interpretations of $I$ of $\cvarone$ and $I'$ of $\cvartwo$ under which the two parametric words have the same interpretation, i.e.
+The word accepted by the run of $\syncof \pa {\pa'}$ induces constraints on the interpretations of $I$ over $\cvarone$ and $I'$ over $\cvartwo$ under which the two parametric words have the same interpretation, i.e.
 $I(x) = I'(x')$.
@@
 \begin{lemma}
-For PFA $\pa$ and $\pa'$,  
 %$\semof{\pa\cdot \pa'} = \semof{\pa}\cdot\semof{\pa'}$ and 
-$\encode{\pa\cdot \pa'}{(\semof{\pa\cdot \pa})}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{I_e \cup I_e'\mid I_e \in \encode \pa (\semof{\pa}) \wedge I_e' \in\encode {\pa'} (\semof{\pa'})\}$.
+$\encode{\pa \cdot\pa'}{(\semof{\pa \cdot \pa})}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
+\{I_e \cup I_e'\mid I_e \in \encode \pa (\semof{\pa}) \wedge I_e' \in\encode {\pa'} (\semof{\pa'})\}$, for PFAs $\pa$ and $\pa'$.
 \end{lemma}
@@
 Having made these assumptions, we may proceed follows.
-First, we build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side term of the equality constraint $\phi_e$, respectively, by concatenating the restrictions of the individual variables.
+First, we build two PFAs $\leftA$ and $\rightA$ that encode the left and the right-hand side word term of the equality constraint $\phi_e$, respectively, by concatenating the restrictions of the individual variables.
 That is
@@
 %Integer constraints are encoded precisely by flattening, not under-approximated. 
-Given a integer constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
-We use a version of $\phi_l$ where every occurrence of every length term $|x|$ is replaced by an auxiliary length variable $\lx$ and we add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
+Given an integer constraint $\phi_l$ that talks about lengths $|x|$ of string variables $x\in X$. 
+We use a version of $\phi_l$ where every occurrence of every length function $|x|$ is replaced by an auxiliary length variable $\lx$ and we add a formula to ensure that the value of $\lx$ is equal to that of $|x|$ even when $x$ is encoded using the character variables $V_x$ and Parikh variables $\# V_x$ of $\dr(x)$.
 %
@@
 %
-\lh{I am not sure whether it is really impossible to make a small formula}
+%\lh{I am not sure whether it is really impossible to make a small formula}
 %
@@
 The satisfiability of equality constraints combined with length constraints of the form $|x|=|y|$ is already opened for more than 20 years \cite{buchi1990definability}.
-Numerous decidable fragments were proposed\cite{abdulla2014string,barcelo2013graph,lin2016string,chen2017decidable,chen2019decision,abdulla2019chain}.
+Numerous decidable fragments were proposed~\cite{abdulla2014string,barcelo2013graph,lin2016string,chen2017decidable,chen2019decision,abdulla2019chain}.
 Among them, the chain-free fragment \cite{abdulla2019chain} used by our over-approximation module is the largest known decidable fragment, which allows us to produce more precise over-approximation and hence solve many UNSAT instances efficiently.
@@
 
-The most related work to ours is~\cite{abdulla2018trau} who proposed to project the solution space of variables to a generalization of flat automata.
-The main difference is that our approach works fully symbolically, thanks to the ideas of using character variables.
-The use of character variables enables our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.
-Moreover, the approach of~\cite{abdulla2018trau} is exponential to the alphabet size, and hence in the implementation, usually requires heuristics to prune out unnecessary symbols.
+The most relevant work to ours is~\cite{abdulla2018trau} who proposed to project the solution space of variables to a generalization of flat automata.
+The main difference is that our approach works fully symbolically, which is enabled by to the ideas of using character variables and hence PFAs.
+The use of character variables allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.
+Moreover, the approach of~\cite{abdulla2018trau} is exponential to the alphabet size (we call this the alphabet-explosion problem in the introduction), and hence in the implementation, usually requires heuristics to prune out unnecessary symbols.
 

### 2019-11-23 evaluation.tex
update experiments

@@
 
-In {\tool}, we use the following PFA selection strategy: we select PFAs of size $m$ for string variables involved in a number-string conversion constraint and PFAs with $p$ loops of size $q$ for other variables.
-Initially, we set $(m,p,q)=(X,X,X)$, and increase each of them by one if more precise refinement is required.
-We set an upper bound $7$ for each parameters and report UNKNOWN if a solution cannot be found within the bound.
-\yfc{need to check with Diep for the parameters}.
+In {\tool}, we use the following PFA selection strategy.
+First, we use \emph{numeric PFAs} for string variables appeared in string-number conversion and \emph{standard PFAs} for others.
+Then we select size $m$ for numeric PFAs and $p$ loops of size $q$ for standard PFAs.
+Initially, we set $(m,p,q)=(5,2,q)$, where $q$ is dynamic and achieved from our internal static analysis.
+We double $m$, increase $p$ and $q$ by one if more precise refinement is required.
+We set an upper bound for each parameter and report UNKNOWN if a solution cannot be found within the bound.
 
@@
 Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure.
-For under-approximation, every time when a corresponding linear formula is created, we create a new Z3 solver instance to solve it.
-If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and tries another solution branch.
+For under-approximation, every time when a corresponding linear formula is created, we attach the current value of $m$, $p$, $q$ with the formula, and then push it to Z3 core.
+If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and either tries another solution branch, or the same solution branch with different value of $m$, $p$, $q$.
 If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.
 
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}, and \textsf{Trau+}~\cite{abdulla2019chain}.
+We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
-We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints) and Ostrich~\cite{chen2019decision}, because most of our benchmarks contain non-trivial equality constraints, which is not fully supported by those solvers.
+We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.
 
@@
 In the second experiment, we compare with tools supporting string-number conversion on the benchmarks collected from the symbolic executor \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, which has the supports of string-number conversion.
-We ran it on several examples collected from the LeetCode platform and from Python core libraries.
+We ran it on several examples collected from the LeetCode platform and from Python core libraries, which involve diverse usages of string-number conversion in Python such as parsing date-time, verifying and restoring IP addresses from strings, etc.
 We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).
@@
 \scalebox{0.85}{
-\begin{tabular}{|l r | r r r r r|}
+\begin{tabular}{|l r | r r r r |}
 \hline
-\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 & 19149 \\ 
-							& UNSAT    &   3883  &  3834 &  3831 &  3836 & 3828 \\
-							& $\times$ &    128  &  1824 &  5062 & 18555 & 2444 \\ \hline
-\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 & 132 \\
-							& UNSAT    &    288  &   221 &   100 &   111 & 82 \\
-							& $\times$ &    181  &   174 &   488 &   452 & 386 \\ \hline
-\multirow{3}{*}{LeetCode}	& SAT      &    880  &   859 &   881 &   670 & 778 \\
-							& UNSAT    &   1786  &  1785 &  1785 &  1780 & 1827 \\
-							& $\times$ &      0  &    22 &     0 &   216 & 61 \\ \hline
-\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 & 688 \\
-							& UNSAT    &    319  &   240 &   186 &   192 & 339 \\
-							& $\times$ &    248  &   154 &   615 &   382 & 38 \\\hline
-\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 & 247 \\
-							& UNSAT    &    820  &   818 &   808 &   772 & 500 \\
-							& $\times$ &      4  &     6 &    15 &    55 & 88 \\ \hline
-\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 & 311 \\
-							& UNSAT    &   1031  &   936 &  1021 &   958 & 596 \\
-							& $\times$ &      1  &   101 &    19 &    70 & 138 \\ \hline
-\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 & 21305  \\
-							& UNSAT    &   8127  &  7834 &  7731 &  7649 & 7172  \\
-							& $\times$ &    562  &  2281 &  6199 & 19730 & 3155  \\\hline	
+\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
+\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 \\ 
+							& UNSAT    &   3883  &  3834 &  3831 &  3836 \\
+							& $\times$ &    128  &  1824 &  5062 & 18555 \\ \hline
+\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
+							& UNSAT    &    288  &   221 &   100 &   111 \\
+							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
+\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
+							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
+							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
+\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
+							& UNSAT    &    319  &   240 &   186 &   192 \\
+							& $\times$ &    248  &   154 &   615 &   382 \\\hline
+\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
+							& UNSAT    &    820  &   818 &   808 &   772 \\
+							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
+\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
+							& UNSAT    &   1031  &   936 &  1021 &   958 \\
+							& $\times$ &      1  &   101 &    19 &    70 \\ \hline
+\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
+							& UNSAT    &   8127  &  7834 &  7731 &  7649 \\
+							& $\times$ &    562  &  2281 &  6199 & 19730 \\\hline	
 \end{tabular}}

### 2019-11-23 draft.tex
add a conclusion

@@
 
+\section{Conclusion and Future Works}
+In this paper, we report a novel approach for solving string constraints with string-number conversion and implemented it as an open-source tool {\tool}.
+For now, it support basic string constraints, string-number conversion, and also operations that can be encoded to them (e.g., \textsc{contains}, \textsc{prefixOf}).
+Since {\tool} is built inside the SMT solver Z3, we also get the power of processing formulae in the combination of different theories (e.g., array) and hence can support the encoding of a wide range of program expressions.
+There are several avenues for future works.
+We are planning to integrate it with the JavaScript symbolic executor \textsc{cosette}, such as the one in~\cite{santos2018symbolic}.
+We have discussed this possibility of such integration with some of its team members, and we believe it is feasible.
+We are also planning to merge it to the main branch of the Z3 solver, to increase the visibility of {\tool}.
+For technical development, we think it would be interesting to consider the flattening of an even larger set of string operations, such as \textsc{replaceALL} and \textsc{split}.
+
 \bibliographystyle{ACM-Reference-Format}

### 2019-11-23 evaluation.tex

@@
 The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
-Columns with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
+Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
 Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
@@
 \centering
-\caption{Results of {\tool}, CVC4, Z3, Z3-str3 and Trau+ on Basic String Constraint benchmarks.}
+\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on Basic String Constraint benchmarks.}
 \scalebox{0.85}{
@@
 							& UNSAT    &   1031  &   936 &  1021 &   958 \\
-							& $\times$ &      1  &   101 &    19 &    70 \\ \hline
+							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
 \multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
@@
 \end{table}
-
-\hide{
-% wider table for 30s timeout data
-\begin{table}[h]
-\centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
-\scalebox{0.8}{
-\begin{tabular}{|l r | r r r r|| r r r r|}
-\hline
-\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
-\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
-								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
-								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
-\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
-								& UNSAT    &    720  &   660 &   724  &   644 \\
-								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
-\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
-								& UNSAT    &      0  &     0 &     0  &     0 \\
-								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
-								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
-								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
-\end{tabular}}
-\label{table:str_int_benchmark}
-\end{table}
-}
 
@@
 
-To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the the timeout set to 30s.
-Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to about 100, while other tools got almost the same number of timouts with the results of timeout set to 10s.
+To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
+Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to 539, while CVC4 and Z3-str3 got almost the same number of timeouts with the results of timeout set to 10s.
+Z3 also managed to reduce the number of timeouts to 821.
+If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.
+
 Also, we have encoded the checkLuhn algorithm in SMT-lib for cases of 2 to 12 loops (digits).
@@
 It seems that Z3 has some strategies that can solve problems of even loops efficiently.
-\todo{Update table with data of timeout=30s}
+
+% \todo{Update table with data of timeout=30s}
 
@@
 }
+
+\hide{
+% wider table for 30s timeout data
+\begin{table}[h]
+\centering
+\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
+\scalebox{0.8}{
+\begin{tabular}{|l r | r r r r|| r r r r|}
+\hline
+\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
+\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
+								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
+								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
+\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
+								& UNSAT    &    720  &   660 &   724  &   644 \\
+								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
+\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
+								& UNSAT    &      0  &     0 &     0  &     0 \\
+								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
+\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
+								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
+								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
+\end{tabular}}
+\label{table:str_int_benchmark}
+\end{table}
+}

### 2019-11-23 draft.tex
add conclusion

@@
 \end{abstract}
- \setcopyright{none} 
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  Section \ref{section:s2i} presents the construction of the linear formula for string-number conversion operations.
-Finally, Section \ref{section:evaluation} presents the details of our implementation and our experimental results.
+Section \ref{section:evaluation} presents the details of our implementation and our experimental results.
+ Related works are discussed in Section \ref{section:related}. Finally, Section~\ref{section:conclusion} concludes the paper with a discussion of future works.
 
@@
 \section{Related works} 
+\label{section:related}
 To the best of our knowledge, the study of solving string constraint traces back to 1946, when Quine \cite{quine1946concatenation} showed that the first-order theory of string equality constraints (a.k.a.
@@
 \section{Conclusion and Future Works}
+\label{section:conclusion}
 In this paper, we report a novel approach for solving string constraints with string-number conversion and implemented it as an open-source tool {\tool}.

### 2019-11-23 draft.tex
add conclusion

@@
 We are also planning to merge it to the main branch of the Z3 solver, to increase the visibility of {\tool}.
-For technical development, we think it would be interesting to consider the flattening of an even larger set of string operations, such as \textsc{replaceALL} and \textsc{split}.
+For technical development, we think it would be interesting to consider the flattening of an even larger set of string operations, such as \textsc{replaceAll} and \textsc{split}.
 

### 2019-11-23 draft.tex
Update draft.tex

@@
 For now, it support basic string constraints, string-number conversion, and also operations that can be encoded to them (e.g., \textsc{contains}, \textsc{prefixOf}).
-Since {\tool} is built inside the SMT solver Z3, we also get the power of processing formulae in the combination of different theories (e.g., array) and hence can support the encoding of a wide range of program expressions.
+Since {\tool} is built inside the SMT solver Z3, we also get the power of processing formulae in the combination of different theories (e.g., array).
+Hence our tool can support the encoding of a wide range of program expressions.
 There are several avenues for future works.
-We are planning to integrate it with the JavaScript symbolic executor \textsc{cosette}, such as the one in~\cite{santos2018symbolic}.
-We have discussed this possibility of such integration with some of its team members, and we believe it is feasible.
-We are also planning to merge it to the main branch of the Z3 solver, to increase the visibility of {\tool}.
-For technical development, we think it would be interesting to consider the flattening of an even larger set of string operations, such as \textsc{replaceAll} and \textsc{split}.
+First, we are planning to integrate it with the JavaScript symbolic executor \textsc{cosette}~\cite{santos2018symbolic}.
+We  believe such integration  is feasible.
+%have discussed this possibility of such integration with some of its team members, and 
+We are also planning to merge  {\tool}  with the main branch of the Z3 solver.
+For technical development, we think it would be interesting to consider the (symbolic) flattening of an even larger set of string operations, such as the one containing  \textsc{replaceAll} and \textsc{split}.
 

### 2019-11-23 evaluation.tex
update experiments

@@
 We perform two sets of experiments.
-In the first set of experiments, we compare with other tools on benchmarks over basic string constraints.
-We use the following benchmark examples in these experiments:
+In the first set of experiments, we compare {\tool} with other tools on existing benchmarks over basic string constraints.
+Those benchmarks do not involve string-number conversion function.
+In the second set of experiments, we compare {\tool} with other tools on new suites focusing on string-number conversion.
+Our goals of experiments are the following:
+\begin{itemize}
+	\item {\tool} performs as good as, or better than other tools in solving satisfiability of basic string constraints.
+	\item {\tool} performs significantly better than other tools in solving satisfiability of basic string constraints, shows the efficiency of PFA in general and \emph{numeric} PFA in particular.
+\end{itemize}
+
+In the second experiment, we use the following benchmark examples:
 \begin{itemize}

### 2019-11-23 evaluation.tex
Update evaluation.tex

@@
 We have implemented our string constraint solving procedure in a tool called {\tool}.
-{\tool} is implemented as a theory solver of the SMT solver Z3~\cite{z3} .
+{\tool} is implemented as a theory solver of the SMT solver Z3~\cite{z3}.
 In this way, we can concentrate on solving constraints connected by conjunctions and let Z3 handle other boolean connectives.
@@
 In {\tool}, we use the following PFA selection strategy.
-First, we use \emph{numeric PFAs} for string variables appeared in string-number conversion and \emph{standard PFAs} for others.
+First, we use \emph{numeric PFAs} for string variables appearing in string-number conversion and \emph{standard PFAs} for others.
 Then we select size $m$ for numeric PFAs and $p$ loops of size $q$ for standard PFAs.
@@
 The way our theory solver and Z3 interacts is almost standard.
-Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it SAT or UNSAT using the aforementioned procedure.
+Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it is SAT or UNSAT using the aforementioned procedure.
 For under-approximation, every time when a corresponding linear formula is created, we attach the current value of $m$, $p$, $q$ with the formula, and then push it to Z3 core.
@@
 Our goals of experiments are the following:
+\smallskip
+
 \begin{itemize}
-	\item {\tool} performs as good as, or better than other tools in solving satisfiability of basic string constraints.
+	\item {\tool} performs as good as, or better than other tools in solving the  satisfiability problems of basic string constraints.
+
+		\smallskip
+
 	\item {\tool} performs significantly better than other tools in solving satisfiability of basic string constraints, shows the efficiency of PFA in general and \emph{numeric} PFA in particular.
@@
 In the second experiment, we use the following benchmark examples:
+
 \begin{itemize}
 	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
+
+	\smallskip
+
 	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
+
+		\smallskip
+
 	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
+
+		\smallskip
+
 	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated from the fuzz testing tool of the same name.
+
+		\smallskip
+
 	\item $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$ are obtained from the CVC4 group~\cite{termEQ}.

### 2019-11-23 draft.tex
add example

@@
 namely, for a interpretation $I$ of the string constraint $\insc$,  
-we let $\encode \dr (I) =\{I_e\mid \decode \dr (I_e) = I \}$.
+we let $\encode \dr (I) =\{I_e\mid \decode \dr (I_e) = \{I\} \}$.
 We lift $\decode \dr$ and $\encode \dr$ to sets of interpretations in the standard manner.
+\begin{example}
+We consider the domain restriction $\dr$ such that $\dr(x)	 =(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and $\dr(y) = (A_y,\true)$ from Figure~\ref{fig:sfa}~(b).
+We assume that the set of integer variables $Z=\{v_z\}$ and $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$.
+For the interpretation $I_e =(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2)$, we have $\decode \dr (I_e) = \{(z,x,y) \rightarrow(3, ``ababab",``cc") \}$.
+In the other direction, for $I=(z,x,y) \rightarrow(3, ``ababab",``cc")$, we have $\encode \dr (I) =\{
+(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2), (v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{c},3,3,1,1), \ldots\}$
+
+\end{example}
+
 \begin{theorem}\label{theorem:correct}
@@
 \item If $(q_1,v,q_2) \in T$ and $(q_1',v',q_2') \in T'$, then we have $((q_1,q_1'),(v,v'),(q_2,q_2'))\in \syncT$.
+
+\smallskip
+
 \item If $(q_1,v,q_2) \in T$, then for all states $q'\in Q'$, we have $((q_1,q'),(v,\epsilon),(q_2,q'))\in \syncT$.
+
+\smallskip
+
 \item If $(q_1',v',q_2') \in T'$, then for all states $q\in Q$, we have $((q,q_1'),(\epsilon,v'),(q,q_2'))\in \syncT$.

### 2019-11-23 draft.tex

@@
 For the interpretation $I_e =(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2)$, we have $\decode \dr (I_e) = \{(z,x,y) \rightarrow(3, ``ababab",``cc") \}$.
-In the other direction, for $I=(z,x,y) \rightarrow(3, ``ababab",``cc")$, we have $\encode \dr (I) =\{
-(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2), (v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{c},3,3,1,1), \ldots\}$
-
+In the other direction, for $I=(z,x,y) \rightarrow(3, ``ababab",``cc")$ and $Y=(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3)$, we have\\ $\encode \dr (I) =\left\{
+\begin{array}{l}
+Y \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2), \\
+Y \rightarrow (3,\semof{a}, \semof{b},\semof{\epsilon}, \semof{c},3,3,2,2), \\
+Y\rightarrow (3,\semof{a}, \semof{b},\semof{c},\semof{c},3,3,1,1)
+\end{array}
+ \right\}$
 \end{example}

### 2019-11-23 draft.tex
little things in example 6.1

@@
 We consider the domain restriction $\dr$ such that $\dr(x)	 =(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and $\dr(y) = (A_y,\true)$ from Figure~\ref{fig:sfa}~(b). 
-We assume that the set of integer variables $Z=\{v_z\}$ and $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$.
-For the interpretation $I_e =(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2)$, we have $\decode \dr (I_e) = \{(z,x,y) \rightarrow(3, ``ababab",``cc") \}$.
-In the other direction, for $I=(z,x,y) \rightarrow(3, ``ababab",``cc")$ and $Y=(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3)$, we have\\ $\encode \dr (I) =\left\{
+%We assume that the set of integer variables is $Z=\{v_z\}$ and $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
+Let the set of integer variables be $Z=\{v_z\}$ and let $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
+For the interpretation $I_e =(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2)$, we have $\decode \dr (I_e) = \{(z,x,y) \rightarrow(3, ``ababab",``cc") \}$.\\
+Conversely, for $I=(z,x,y) \rightarrow(3, ``ababab",``cc")$ and $Y=(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3)$, we have $\encode \dr (I) =\left\{ 
 \begin{array}{l}

### 2019-11-23 evaluation.tex

@@
 
-	\item {\tool} performs significantly better than other tools in solving satisfiability of basic string constraints, shows the efficiency of PFA in general and \emph{numeric} PFA in particular.
+	\item {\tool} performs significantly better than other tools in solving the satisfiability problems on string-number conversion benchmark, and this shows  the efficiency of PFA in general and \emph{numeric} PFA in particular.
 \end{itemize}
+		\smallskip
 
-In the second experiment, we use the following benchmark examples:
+In the first set of experiments, we use the following benchmark examples:
+
+		\smallskip
 
@@
 Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test.
-To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtained a modified test, and re-evaluates the modified test by multiple solvers.
+To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtain a modified test, and re-evaluates the modified test by multiple solvers.
 If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results.
@@
 
-The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively.
+The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}.
 Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
@@
 In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases.
-If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases.
+If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant difference between {\tool} and the top-ranked tool on the SAT cases.
 But we believe this is not very important because both these two benchmarks are artificial, either hand-crafted or randomly generated.
@@
 In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number.
-We generated 2028 tests from this function, and among them around 1000 cases that are too difficult for all solvers.
+We generated 2028 tests from this function, and among them around 1000 cases  are too difficult for all solvers.
 If we exclude results on this function, then {\tool} has only $218$ failed cases in total.

### 2019-11-23 draft.tex
fix of ex 5.2

@@
 \begin{example}
-If we consider the PFA ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$, we have\\
+Let use consider the PFA ${\pa_x}=(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and let $Y{=}(v_1,v_2,\#v_1,\#v_2)$. Then we have\\
 $\encode {\pa_x}( ``aaa" ) =\{ (Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3), Y{\rightarrow}(\semof{\epsilon},\semof{a},3,3)  \}$ and
 $\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
+\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
 \end{example}

### 2019-11-23 evaluation.tex

@@
 
-Also, we have encoded the checkLuhn algorithm in SMT-lib for cases of 2 to 12 loops (digits).
-These problems ask for a model of a valid credit card number as a string of length 2 to 12  each case.
+For further details of the experiment, we have encoded the checkLuhn algorithm introduced in Section~\ref{section:introduction} for cases of 2 to 12 loops (digits).
 We ran these tests additionally to the experiments above with the timeout set to 120s.
-In these tests, {\tool} can solve all 11 problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve these problems (either timeout or UNKNOWN).
+The result is summarized in Table~\ref{table:checkLuhn}.
+In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve any of these problems (either timeout or UNKNOWN).
 However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops.
-It seems that Z3 has some strategies that can solve problems of even loops efficiently.
+The behavior of Z3 is not unexpected, since all the problems are satisfiable and sometimes the solver are lucky and went into a branch with a correct model very quickly.
 
@@
 
-\hide{
 \begin{table}[h]
@@
 \end{table}
-}
 

### 2019-11-23 evaluation.tex
add heuristics for over-app to evaluation

@@
 If Z3 completes the search of all solution branches, it reports UNSAT if the flag \textsf{incomplete} is down, and UNKNOWN otherwise.
+
+Our over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
+For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
+Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
 
@@
 \centering
-\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
+\caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
 \scalebox{0.9}{

### 2019-11-23 draft.tex
asdf

@@
 $\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
-\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
+\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ to denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
 \end{example}

### 2019-11-23 evaluation.tex

@@
 
+Our over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
+For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
+Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
+
 The way our theory solver and Z3 interacts is almost standard.
@@
 
-Our over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
-Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
-
-We compare {\tool} with other state-of-the-art string solvers, namely CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We use the GitHub version stated in the parenthesis, and because their performance are in general better than the corresponding release version.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.

### 2019-11-23 evaluation.tex
minor

@@
 We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
-We use the GitHub version stated in the parenthesis, and because their performance are in general better than the corresponding release version.
+Foe these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.

### 2019-11-23 evaluation.tex
minor

--- 2019-11-23 evaluation.tex
@@
 We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
-We use the GitHub version stated in the parenthesis, and because their performance are in general better than the corresponding release version.
+For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.

### 2019-11-23 draft.tex
little things

--- 2019-11-23 draft.tex
@@
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
+For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4) \rightarrow (1,2,1,2,1,1,2,2)$.%
+\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ to denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
 The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
@@
 $\decode {\pa_x}((Y{\rightarrow}(\semof{a},\semof{\epsilon},3,3))=\{``aaa"\} $.
-\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
 \end{example}
@@
 $\encode{\pa \cdot\pa'}{(\semof{\pa \cdot \pa})}_{\cvarone\cup \cvartwo \cup \pvarone\cup\pvartwo} =
-\{I_e \cup I_e'\mid I_e \in \encode \pa (\semof{\pa}) \wedge I_e' \in\encode {\pa'} (\semof{\pa'})\}$, for PFAs $\pa$ and $\pa'$.
+\{I_e \cup I_e'\mid I_e \in \encode \pa (\semof{\pa}) \wedge I_e' \in\encode {\pa'} (\semof{\pa'})\}$, \mbox{for PFAs $\pa$ and $\pa'$.}
 \end{lemma}
@@
 %
-A last problem still needed to be solved before they can be efficient in practice. 
+A last problem still neededs to be solved before they can be efficient in practice. 
 %

### 2019-11-23 evaluation.tex
update experiments
minor

@@
 
-The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}.
+The results of the experiments are summarized in Table~\ref{table:base_benchmark}, Table~\ref{table:str_int_benchmark}, and Table~\ref{table:checkLuhn}.
 Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
@@
 \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      &  21410  & 19763 & 16528 &  3030 \\ 
-							& UNSAT    &   3883  &  3834 &  3831 &  3836 \\
-							& $\times$ &    128  &  1824 &  5062 & 18555 \\ \hline
+\multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
+							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
+							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
 \multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
@@
 							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
-\multirow{3}{*}{Total} 		& SAT      &  22943  & 21517 & 17702 &  4253 \\
-							& UNSAT    &   8127  &  7834 &  7731 &  7649 \\
-							& $\times$ &    562  &  2281 &  6199 & 19730 \\\hline	
+\multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
+							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
+							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
 \end{tabular}}
@@
 
-To address the effectiveness of our PFA strategy, we also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
-Provided more time for solving, {\tool} managed to obtain more results and the timeout number is reduced to 539, while CVC4 and Z3-str3 got almost the same number of timeouts with the results of timeout set to 10s.
-Z3 also managed to reduce the number of timeouts to 821.
-If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.
+We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
+Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3-str3 got almost the same number of failed cases.
+Z3 also managed to reduce the number of failed cases to 821.
+%If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.
 

### 2019-11-23 draft.tex

@@
 For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4) \rightarrow (1,2,1,2,1,1,2,2)$.%
-\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ to denote the function $\{x_1 \rightarrow n_1,\ldots, x_k\rightarrow n_k\}$.}
+\footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ to denote the function $\{x_1 \mapsto n_1,\ldots, x_k\mapsto n_k\}$.}
 The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.

### 2019-11-23 evaluation.tex
little fixes in experiments

--- 2019-11-23 evaluation.tex
@@
 {\tool} is implemented as a theory solver of the SMT solver Z3~\cite{z3}.
-In this way, we can concentrate on solving constraints connected by conjunctions and let Z3 handle other boolean connectives.
-It also enables us to solve not only formulae over string constraints but also the combination of string constraints with constraints over other theories that Z3 supports.
+In this way, we can concentrate on solving conjunctive constraints and let Z3 handle other boolean connectives.
+Secondly, it makes it possible to solve not only formulae over string constraints but also the combination of string constraints with other theories that Z3 supports.
 Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.

### 2019-11-23 evaluation.tex
tine thing in experiments

@@
 {\tool} is implemented as a theory solver of the SMT solver Z3~\cite{z3}.
-In this way, we can concentrate on solving conjunctive constraints and let Z3 handle other boolean connectives.
-Secondly, it makes it possible to solve not only formulae over string constraints but also the combination of string constraints with other theories that Z3 supports.
+In this way, we can concentrate on solving conjunctive constraints and let Z3 handle the other boolean connectives.
+Secondly, it makes it possible to solve not only formulae over string constraints but also combinations of string constraints with other theories that Z3 supports.
 Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.

### 2020-02-04 rebuttal/response.txt
rebuttal

Reviewer A

1. It is too bad that the experimental evaluation does not include some DPLL-based
string solvers.

Response: to the best of our knowledge, Z3 and CVC4 are the best DPLL-based string solver that are still well-maintained.

2. In Section 9, it would be nice to break down the X results further:
how many "unknown" vs timeouts vs incorrect results vs crashes? For
the latter two categories, did this work uncover new bugs in some of
the solvers? Please clarify.

Response: hlin

3. In Section 9, would using a timeout value different from 10 seconds
change the results significantly? This question is partly answered in
the text, but a scatter plot showing the solving time for each
instance and comparing Z3-PFA with other solvers would provide more
information.

Response: hlin

Reviewer B

1. The concept of flat automata for solving string constraints has already been proposed [1]. The solver framework based on both over- and under-approximation has also been proposed in [1]. I understand that this paper proposes a parametric version of flat automata (PFA). However, I do not see the key insight of the PFA. Why can't FA be applied in the problem domain since PFA is just FA plus recording the loop size/length?

Response: beside the loop size, the transition symbols are also made symbolic in PFA. For example, in the work [1], if unicode (>60000 symbols) is used, one would have >60000 transitions between two states of an FA, but we need only one for PFA. We call this the alphabet explosion problem of [1]. In [1], it uses some heuristics reduce the symbols required for solving. (should we give reason why PFA is good for str-int conversion?)

2. I can't entirely agree with the stated hardness of handling string-number conversion in solvers. In particular, lines 195-197 state that the challenge of dealing with string-number constraint is that the problem is undecidable. Well, undecidability is an over-used term in this context. Recall that the problem of solving string constraints itself is already very hard (see the undecidability discussion in section 2 of [1]). Therefore, the problem with string-number conversion, intuitively, is undecidable.

3. How significant is it to introduce the string-number conversion? With that said, the current paper does not give any constructive argument to discuss the hardness of the problem. I think perhaps a better way is to show that the popular solvers based on FA could not handle the string-number conversion. That gives a strong motivation for PFA as well as this work in general.

4. In the introduction, the description of the motivating example in Figure 2 is extremely confusing. When discussing the example for the first time (lines 285-300), I don't see why $A_x$ is projected in this way. In the example, we have only $y\in(12)^+$. How exactly do you infer that $A_x$ should have a similar structure?

5. In the evaluation, it is a bit unfortunate to see that there is no comparison with Trau [1-5]. This is critical. Lines 1039-1040 mention that it is because Trau does not ``support all string functions in our benchmarks, especially string-number conversion.'' This argument is unconvincing. In the evaluation, you can compare your approach against a vanilla Z3. And Trau is implemented on top of Z3 (see section 1 of [1]). Logically, Trau could be extended to handle the conversion (just by ``enabling'' some features in the vanilla Z3). If there is any principle limitation, it's worthwhile to justify it.

Reviewer C

1. I performed a very quick experiment in which I converted the function *checkLuhn* into C code, and find out KLEE works fine. This demonstrates that the state-of-the-art solvers are capable of handling the path constraints, which left me some negative feelings in the very beginning. Perhaps change the example program?

Response: use the argument the semantics between C and JS are different?

2. It would be better if the authors can provide more background to support your claim that string-number conversion is difficult for existing solvers. Is there an empirical study the authors can refer to? or educate the readers why those constraints are hard to solve.

3. I'm not clear about the "correct answer" (line 137), do you mean these solvers provide a wrong answer (e.g., return SAT for UNSAT constraints) or just return "unknown"? If they provide a wrong answer, why does it happen?

Response:

4. It is not clear to me how you construct a PFA that is aware of the domain of a constraint. For example, how do you infer that the domain of a constraint to be a binary number, octal number, decimal number or hexadecimal number? For a constraint "var[0] == var[1] && $\forall$ i in [0,len(var)-1], toNum(var[i]) > 9" that is only satisfiable for hexadecimal numbers, how do you know the domain is a hexadecimal number (i.e., [0, f]) as opposed to a decimal number (i.e., [0, 9])? Using PFA will simplify solving the string constraints. However, the performance of the under-approximation depends on the alphabet because the automaton consists of multiple one-way cycles (at line 1002). I can imagine the performance difference in a binary number, octal number, decimal number and hexadecimal number on which the size of each loop in PFA depends(e.g., the size of each loop is 8 for octal numbers). Therefore, would it be beneficial to convert different number systems to binary number systems?

5. At line 894, it is not clear to me how each numeric PFA covers a large and practically significant portion of numerals. In my view, each numeric PFA can only cover one number.

6. In the evaluation, you only give the run-time results for the evaluation on *checkLuhn* algorithm. This is rather strange, why don't you also provide solving time in table 1 or table 2? Additionally, why is its timeout budget (120s) different from the previous experiment (10s).

Response: We need to handle the time required for artifact evalution. For table 1 and table 2, it has too many instances that an 120s might requrie too much time to reproduce the same result. The evaluation of checkLuhn has only one instance so higher time budget is still possible.

7. I think "PASS: String Solving with Parameterized Array and Interval Automaton" is closely related, which I believe you should compare in your evaluation.

8. I am a bit struggling to learn the insight of your approach. In essence, why is your approach better than the existing solvers?

Reviewer D

1. - Although the solver is incomplete (which is not surprising for an undecidable problem in general), it would be useful to learn what heuristics were used in the iterative process of considering more expressive PFA. Was this process partially or fully automated? Do you prioritize among the PFAs of different variables?

2. - It also seems that there may be some wasted effort when considering larger PFAs iteratively. Is some work re-usable? Could your solver be made incremental over the PFAs?

3. - please explain requirement 3 that each character in \Sigma appears on at most one transition. Is it at most one transition in the full automata or in each loop?

Response: it is in the full automata

4.

### 2020-02-04 rebuttal/response.txt
update of rebuttal

@@
 
-Response: beside the loop size, the transition symbols are also made symbolic in PFA.
-For example, in the work [1], if unicode (>60000 symbols) is used, one would have >60000 transitions between two states of an FA, but we need only one for PFA.
-We call this the alphabet explosion problem of [1].
-In [1], it uses some heuristics reduce the symbols required for solving.
-(should we give reason why PFA is good for str-int conversion?)
+Response: the difference between PFA and FA is that (1) PFA handles the transition labels symbolically and hence avoided the alphabet explosion problem.
+For example, if Unicode (>60000 symbols) is used, one would have >60000 transitions between two states of an FA, but we need only one transition labelled with a variable for PFA.
+(2) In PFA, symbols are also natural numbers and hence can be used directly in the translation between strings and integers.
+In FA, one would need handle the translation using multpiple if-then-else statement in the form of ite(#T1 >0, x=1, ite(#T2>0, x=2, ite(...))), which will increase the loading of the DPLL engine of the SMT solver, because now (#T1>0),(#T2>0)...
+are new predicates and the DPLL engine need to guess if they are positive or negative.
 
@@
 
+Response:
+
 3.
@@
 That gives a strong motivation for PFA as well as this work in general.
+Response: FA-based approach can in theory be turned to support str-int conversion, but would be more expensive than using PFA.
+See the 2nd item of response 1.
+In practice, str-int conversion is not implemented in the existing FA-based tool Trau.
+(should we add more empirical suuport?
+saying that we tried FA+str-int conversion and PFA_str-int conversion is much faster?)
 
@@
 How exactly do you infer that $A_x$ should have a similar structure?
+
+Response: the structure is given by the main loop of the algorithm and is implementation dependent. We describe the PFA selection strategy of Z3-PFA in the 2nd paragraph of the sec 9.
 
@@
 If there is any principle limitation, it's worthwhile to justify it.
+
+Response: Z3 is a DPLL(T) based solver, i.e., a DPLL engine + multiple theory solvers.
+The implementation of Trau is done by substituing the string solver of Z3 with a comepletely new one.
+Str-int conversion is not implemented in the new string solver of Trau.
+If we run the str-int conversion benchmarks on Trau, we will only get exceptions.
 
@@
 
+Response: maybe we should answer the difficult and significancy of string-number conversion together at the beginning of the rebuttal.
+
 3.
@@
 
-Response:
+Response: We mean both.
+Sometime they just keep runnning without give any response.
+Sometimes, it provides a wrong answer.
+There might be several reasons that the answer is wrong.
+We checked the source code of Z3.
+One reason it gives wrong answer is that when both n and x in the constraint n=int(x) are variables, it over-approximates the int(x) function with an uninterpreted function.
+Sometimes Z3 gives a wrong model because of this over-approximation.
 
@@
 
+Response: ...
+
 5. At line 894, it is not clear to me how each numeric PFA covers a large and practically significant portion of numerals. In my view, each numeric PFA can only cover one number.
+
+Response, in PFA, transition are labelled by variables, c.f., Fig 3.
+Each assignement of the variables corresponds to a number.
+E.g., assigning v_0...v_{m-1} to 0 and v_m to 1 corresponds to the integer number 1.
 
@@
 Response: We need to handle the time required for artifact evalution.
-For table 1 and table 2, it has too many instances that an 120s might requrie too much time to reproduce the same result.
+For table 1 and table 2, it has too many instances that an 120s timeout would requrie too much time to reproduce the same result.
 The evaluation of checkLuhn has only one instance so higher time budget is still possible.
@@
 
+Response:
+
 8. I am a bit struggling to learn the insight of your approach. In essence, why is your approach better than the existing solvers?
+
+Response:
 
@@
 
+Response: the PFA selection is an implementation. We describe the PFA selection strategy of Z3-PFA in sec 9, 2nd paragraph.
+
 2. - It also seems that there may be some wasted effort when considering larger PFAs iteratively. Is some work re-usable? Could your solver be made incremental over the PFAs?
+
+Response: we consider this as a future work.
 
@@
 Response: it is in the full automata
-
-4.

### 2020-02-04 rebuttal/response.txt
update

@@
 The implementation of Trau is done by substituing the string solver of Z3 with a comepletely new one.
-Str-int conversion is not implemented in the new string solver of Trau.
-If we run the str-int conversion benchmarks on Trau, we will only get exceptions.
+Str-int conversion is not implemented in the new string solver of Trau, thus str-int convertion constraints will be internally discarded.
+If we run the str-int conversion benchmarks on Trau, we will either get exceptions or incorrect answers.
 
@@
 
-Response: the PFA selection is an implementation. We describe the PFA selection strategy of Z3-PFA in sec 9, 2nd paragraph.
+Response: the PFA selection is an implementation. We describe the PFA selection strategy of Z3-PFA in sec 9, 2nd paragraph. The process is fully automated.
 

### 2020-02-04 rebuttal/response.txt
JS comments

@@
 
-3.
-How significant is it to introduce the string-number conversion?
+3. How significant is it to introduce the string-number conversion?
+
+Response: JavaScript makes far more use of such conversions than other languages to which SMT solvers have traditionally been applied, such as C.
+Every access to the state of any modeled object relies on it, since array indices get turned into strings.
+Since JavaScript is pervasive, such checking is very significant.
+
+4.
 With that said, the current paper does not give any constructive argument to discuss the hardness of the problem.
@@
 
-4.
+5.
 In the introduction, the description of the motivating example in Figure 2 is extremely confusing.
@@
 
-5.
+6.
 In the evaluation, it is a bit unfortunate to see that there is no comparison with Trau [1-5].
@@
 
-Response: use the argument the semantics between C and JS are different?
+Response: Converting checkLuhn into C code will alter its semantics substantially.
+The function makes use of array accesses with charAt() calls (lines 4, 8, 12) and, which, in JavaScript, require string-integer conversions to handle since the array state must be indexed with strings (see discussion starting at line 150 of the subnission).
+A C translation that did this would be very unnatural.
 

### 2020-02-05 rebuttal/response.txt
Update response.txt

@@
+We thank the reviewers for their detailed and constructive feedback and suggestions. Below, we address the main points from the reviews:
+
 Reviewer A
 
-1. It is too bad that the experimental evaluation does not include some DPLL-based
-string solvers.
+1. Comparison with DPLL-based String Solver
 
@@
 
-1.
-The concept of flat automata for solving string constraints has already been proposed [1].
-The solver framework based on both over- and under-approximation has also been proposed in [1].
-I understand that this paper proposes a parametric version of flat automata (PFA).
-However, I do not see the key insight of the PFA.
-Why can't FA be applied in the problem domain since PFA is just FA plus recording the loop size/length?
+1. Why can't FA be applied in the problem domain since PFA is just FA plus recording the loop size/length?
 
@@
 (2) In PFA, symbols are also natural numbers and hence can be used directly in the translation between strings and integers.
-In FA, one would need handle the translation using multpiple if-then-else statement in the form of ite(#T1 >0, x=1, ite(#T2>0, x=2, ite(...))), which will increase the loading of the DPLL engine of the SMT solver, because now (#T1>0),(#T2>0)...
+In FA, one would need handle the translation using multiple if-then-else statement in the form of ite(#T1 >0, x=1, ite(#T2>0, x=2, ite(...))), which will increase the loading of the DPLL engine of the SMT solver, because now (#T1>0),(#T2>0)...
 are new predicates and the DPLL engine need to guess if they are positive or negative.
 
-2.
-I can't entirely agree with the stated hardness of handling string-number conversion in solvers.
-In particular, lines 195-197 state that the challenge of dealing with string-number constraint is that the problem is undecidable.
-Well, undecidability is an over-used term in this context.
-Recall that the problem of solving string constraints itself is already very hard (see the undecidability discussion in section 2 of [1]).
-Therefore, the problem with string-number conversion, intuitively, is undecidable.
+2.  The undecidability is an over-used term in this context to justify the stated hardness of handling string-number conversion in solvers.
 
-Response:
+Response: We agree and will reformulate this sentence by (1) refer the fact that the extension of existing FA based techniques boils down to solving the satisfiability problem of integer constraints with a mix
+of polynomials and exponentials which  is still open (see Section 8), and (2) refer to our experimental results.
 
@@
 That gives a strong motivation for PFA as well as this work in general.
+
 Response: FA-based approach can in theory be turned to support str-int conversion, but would be more expensive than using PFA.
@@
 In practice, str-int conversion is not implemented in the existing FA-based tool Trau.
-(should we add more empirical suuport?
+(should we add more empirical support?
 saying that we tried FA+str-int conversion and PFA_str-int conversion is much faster?)
@@
 
-Response: the structure is given by the main loop of the algorithm and is implementation dependent. We describe the PFA selection strategy of Z3-PFA in the 2nd paragraph of the sec 9.
+Response: the structure is given by the main loop of the algorithm and is implementation dependent.
+We describe the PFA selection strategy of Z3-PFA in the 2nd paragraph of the sec 9.
+We will make this more clear.
 
@@
 Response: Z3 is a DPLL(T) based solver, i.e., a DPLL engine + multiple theory solvers.
-The implementation of Trau is done by substituing the string solver of Z3 with a comepletely new one.
-Str-int conversion is not implemented in the new string solver of Trau, thus str-int convertion constraints will be internally discarded.
+The implementation of Trau is done by substituing the string solver of Z3 with a completely new one.
+Str-int conversion is not implemented in the new string solver of Trau, thus str-int conversion constraints will be internally discarded.
 If we run the str-int conversion benchmarks on Trau, we will either get exceptions or incorrect answers.
@@
 Response: Converting checkLuhn into C code will alter its semantics substantially.
-The function makes use of array accesses with charAt() calls (lines 4, 8, 12) and, which, in JavaScript, require string-integer conversions to handle since the array state must be indexed with strings (see discussion starting at line 150 of the subnission).
+The function makes use of array accesses with charAt() calls (lines 4, 8, 12) and, which, in JavaScript, require string-integer conversions to handle since the array state must be indexed with strings (see discussion starting at line 150 of the submission).
 A C translation that did this would be very unnatural.
@@
 Response: We mean both.
-Sometime they just keep runnning without give any response.
+Sometime they just keep running without give any response.
 Sometimes, it provides a wrong answer.
@@
 Response, in PFA, transition are labelled by variables, c.f., Fig 3.
-Each assignement of the variables corresponds to a number.
+Each assignment of the variables corresponds to a number.
 E.g., assigning v_0...v_{m-1} to 0 and v_m to 1 corresponds to the integer number 1.
@@
 
-Response: We need to handle the time required for artifact evalution.
-For table 1 and table 2, it has too many instances that an 120s timeout would requrie too much time to reproduce the same result.
+Response: We need to handle the time required for artifact evaluation.
+For table 1 and table 2, it has too many instances so that an 120s timeout would require too much time to reproduce the same result.
 The evaluation of checkLuhn has only one instance so higher time budget is still possible.

### 2020-02-05 rebuttal/response.txt
hm

--- 2020-02-04 rebuttal/response.txt
@@
 
-Response: the difference between PFA and FA is that (1) PFA handles the transition labels symbolically and hence avoided the alphabet explosion problem.
-For example, if Unicode (>60000 symbols) is used, one would have >60000 transitions between two states of an FA, but we need only one transition labelled with a variable for PFA.
-(2) In PFA, symbols are also natural numbers and hence can be used directly in the translation between strings and integers.
-In FA, one would need handle the translation using multpiple if-then-else statement in the form of ite(#T1 >0, x=1, ite(#T2>0, x=2, ite(...))), which will increase the loading of the DPLL engine of the SMT solver, because now (#T1>0),(#T2>0)...
-are new predicates and the DPLL engine need to guess if they are positive or negative.
+Response: the difference between PFA and FA is that 
+(1) PFA handle the transition labels symbolically and hence avoid the alphabet explosion problem.
+For example, if Unicode (>60000 symbols) is used, one PFA transition labeled by a variable might represent >60000 transitions of an FA.
+(2) In PFA, symbols are also natural numbers and hence can be used directly in the conversion between strings and integers.
+In FA, this requires multiple if-then-else statements, and these translate to predicates for which a DPLL engine must guess the truth values, which is costly.
+  As as simple experiment, we encoded the problem of finding an n-digit string whose integer value is larger than 42 using FA and also using PFA. 
+For the case of n=10 digits, the DPLL solver needed to make 90 decisions when run on the integer formula created by the FA-based approach, while with the one from the PFA-approach, no decision at all needed to be made (the actual runtimes were insignificant since in the time limited time given, we only managed to handcode FA encodings of a relatively small formula.
+However, the difference in the complexity of the SMT queries seems obvious, and the FA formulae that would be generated from our actual benchmark would be much larger).
 
@@
 Response: Z3 is a DPLL(T) based solver, i.e., a DPLL engine + multiple theory solvers.
-The implementation of Trau is done by substituing the string solver of Z3 with a comepletely new one.
-Str-int conversion is not implemented in the new string solver of Trau, thus str-int convertion constraints will be internally discarded.
+The implementation of Trau is done by substituting the string solver of Z3 with a completely new one.
+Str-int conversion is not implemented in the new string solver of Trau, thus str-int conversion constraints will be internally discarded.
 If we run the str-int conversion benchmarks on Trau, we will either get exceptions or incorrect answers.
@@
 
-Response: We need to handle the time required for artifact evalution.
-For table 1 and table 2, it has too many instances that an 120s timeout would requrie too much time to reproduce the same result.
+Response: We need to handle the time required for artifact evaluation.
+For table 1 and table 2, it has too many instances that an 120s timeout would require too much time to reproduce the same result.
 The evaluation of checkLuhn has only one instance so higher time budget is still possible.
@@
 7. I think "PASS: String Solving with Parameterized Array and Interval Automaton" is closely related, which I believe you should compare in your evaluation.
+
+Some notes from reading: He might be right.
+The PASS uses quantified logic over arrays where the array length is a parameter (they have special quant.
+elim.), and they use automata which they encode to this kind of constraints, it resembles Presburger, and they do int-to-string in a way close to ours perhaps.
+It is also well cited, although nobody who cites them compares with them, and they do not compare much with anybody themselves, and the tool is nowhere to be found.
+We can perhaps say that their approach produces quantified formulae that are supposedly much harder to solve, and that our approach is much more flexible since it relates on SMT.
 

### 2020-02-05 rebuttal/response.txt

--- 2020-02-05 rebuttal/response.txt
@@
 
-Response:
+Response: PASS handles most of  Java string operations including string-to-number conversions.
+PASS uses arrays with symbolic length to encode string and then reduce the sayisfiability problem to its corresponding one for quantified constraints over arrays.
+Such quantified constraints are then solved using a dedicated quantifier elimination procedure.
+Unfortunately, we were not able to compare our results with PASS since the later one is not available.
 

### 2020-03-22 draft.tex
revise according to our shepherd instruction

@@
 \newcommand{\hide}[1]{}
-\newcommand{\tool}{{\textsf{Z3-PFA}}}
+\newcommand{\tool}{{\textsf{Z3-Trau}}}
 \newcommand{\dr}{\mathcal{R}}
@@
 Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
-Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
+Even for simple constraints like the above one, most solvers already fail to provide a correct answer.
+\yfc{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve even the case of 2 loop iterations.}
 Therefore, there is an urgent  need for developing efficient techniques for solving such combinations of constraints.

### 2020-03-22 evaluation.tex
revise according to our shepherd instruction

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3-str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
@@
 
-	\item LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website.
+	\item \yfc{ LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check if a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check if an input string is an abbreviation of another input string, and decode a sequence of digits to strings according to a given mapping.}
 
@@
 \centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on Basic String Constraint benchmarks.}
+\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
 \scalebox{0.85}{
@@
 \hline
-\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3-str3 \\ \hline
+\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
 \multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
@@
 \centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
+\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
 \scalebox{0.8}{
@@
 \hline
-\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
+\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
 \multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
@@
 We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
-Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3-str3 got almost the same number of failed cases.
+Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3Str3 got almost the same number of failed cases.
 Z3 also managed to reduce the number of failed cases to 821.
@@
 The result is summarized in Table~\ref{table:checkLuhn}.
-In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3-str3 could not solve any of these problems (either timeout or UNKNOWN).
+In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3Str3 could not solve any of these problems (either timeout or UNKNOWN).
 However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops.
@@
 \hline
-\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3-str3 \\ \hline
+\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
 2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
@@
 
-StringFuzz is our next bechmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
+StringFuzz is our next benchmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
 We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.

### 2020-03-23 draft.tex
shepherd response

--- 2019-11-23 draft.tex
@@
 \newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
-\newcommand{\changed}[1]{{\color{orange}#1}}
+\newcommand{\changed}[1]{{\color{blue}#1}}
+
 \newcommand{\yfc}[1]{{\color{blue}YFC: #1}}
@@
 Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
-Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
+Even for simple constraints like the above one, most solvers already fail to provide a correct answer.
+\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve even the case of 2 loop iterations.}
 Therefore, there is an urgent  need for developing efficient techniques for solving such combinations of constraints.
@@
 %
-A last problem still neededs to be solved before they can be efficient in practice. 
+A last problem still needs to be solved before they can be efficient in practice. 
 %

### 2020-03-23 evaluation.tex
shepherd response

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{6ad261e24})~\cite{z3}, \textsf{Z3Str3}~(\texttt{6ad261e24})~\cite{zheng2013z3}.
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
@@
 
-	\item \yfc{ LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check if a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check if an input string is an abbreviation of another input string, and decode a sequence of digits to strings according to a given mapping.}
+	\item \changed{ LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check if a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check if an input string is an abbreviation of another input string, and decode a sequence of digits to strings according to a given mapping.}
 

### 2020-03-24 evaluation.tex
Update tables in evaluation

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28a)~\cite{cvc4Tool}, and Z3~(\texttt{6ad261e24})~\cite{z3}, \textsf{Z3Str3}~(\texttt{6ad261e24})~\cite{zheng2013z3}.
+We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
@@
 Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
-Rows with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).
+Rows with heading \texttt{UNKNOWN}, \texttt{TIMEOUT}, or \texttt{ERROR} indicate the number of instances the solver fails to return an answer.
+\texttt{INCORRECT} shows the number of cases that a tool gives wrong answer\footnote{A correct answer is decided by mainly CVC4, then the consensus of {\tool} or Z3.}.
 
@@
 \centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
-\scalebox{0.85}{
-\begin{tabular}{|l r | r r r r |}
-\hline
-\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
-\multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
-							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
-							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
-\multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
-							& UNSAT    &    288  &   221 &   100 &   111 \\
-							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
-\multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
-							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
-							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
-\multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
-							& UNSAT    &    319  &   240 &   186 &   192 \\
-							& $\times$ &    248  &   154 &   615 &   382 \\\hline
-\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
-							& UNSAT    &    820  &   818 &   808 &   772 \\
-							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
-\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
-							& UNSAT    &   1031  &   936 &  1021 &   958 \\
-							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
-\multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
-							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
-							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
-\end{tabular}}
-\label{table:base_benchmark}
-\end{table}
-
-% latest backup of table 2
-\begin{table}[h]
-\centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
+\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
 \scalebox{0.8}{
@@
 \hline
-\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
-\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
-								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
-								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
-\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
-								& UNSAT    &    720  &   660 &   724  &   644 \\
-								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
-\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
-								& UNSAT    &      0  &     0 &     0  &     0 \\
-								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
-								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
-								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
+\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
+\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
+								& UNSAT    & 16393& 15726& 16115& 15396 \\
+								& UNKNOWN  &     0&     0&     0&   623 \\
+								& TIMEOUT  &   142&  1480&   914&  2337 \\
+								& ERROR    &     0&     0&     0&   332 \\
+								& INCORRECT&     1&     0&     0&   108 \\ \hline 
+\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
+								& UNSAT    &   720&   667&   724&   644 \\
+								& UNKNOWN  &     0&     0&     0&    45 \\
+								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
+								& ERROR    &     0&     0&     0&    41 \\
+								& INCORRECT&     0&     0&     0&     2 \\ \hline
+\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
+								& UNSAT    &     0&     0&     0&     0 \\
+								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
+\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
+								& UNSAT    & 17113& 16393& 16839& 16040 \\
+								& UNKNOWN  &     0&     0&     0&   668 \\
+								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
+								& ERROR    &     0&     0&     0&   373 \\
+								& INCORRECT&     1&     0&     0&   110 \\ \hline
 \end{tabular}}
@@
 \end{table}
+
+\begin{table}[h]
+\centering
+\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
+\scalebox{0.8}{
+\begin{tabular}{|l r | r r r r|}
+\hline
+\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
+\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
+								& UNSAT    & 16393& 15726& 16115& 15396 \\
+								& UNKNOWN  &     0&     0&     0&   623 \\
+								& TIMEOUT  &   142&  1480&   914&  2337 \\
+								& ERROR    &     0&     0&     0&   332 \\
+								& INCORRECT&     1&     0&     0&   108 \\ \hline 
+\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
+								& UNSAT    &   720&   667&   724&   644 \\
+								& UNKNOWN  &     0&     0&     0&    45 \\
+								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
+								& ERROR    &     0&     0&     0&    41 \\
+								& INCORRECT&     0&     0&     0&     2 \\ \hline
+\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
+								& UNSAT    &     0&     0&     0&     0 \\
+								& UNKNOWN  &     0&     9&     0&     0 \\
+								& TIMEOUT  &     0&     8&     4&    10 \\
+								& ERROR    &     0&     0&     0&     6 \\
+								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
+\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
+								& UNSAT    & 17113& 16393& 16839& 16040 \\
+								& UNKNOWN  &     0&     0&     0&   668 \\
+								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
+								& ERROR    &     0&     0&     0&   373 \\
+								& INCORRECT&     1&     0&     0&   110 \\ \hline
+\end{tabular}}
+\label{table:str_int_benchmark}
+\end{table}
+
+% \begin{table}[h]
+% \centering
+% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
+% \scalebox{0.85}{
+% \begin{tabular}{|l r | r r r r |}
+% \hline
+% \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
+% \multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
+% 							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
+% 							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
+% \multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
+% 							& UNSAT    &    288  &   221 &   100 &   111 \\
+% 							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
+% \multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
+% 							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
+% 							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
+% \multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
+% 							& UNSAT    &    319  &   240 &   186 &   192 \\
+% 							& $\times$ &    248  &   154 &   615 &   382 \\\hline
+% \multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
+% 							& UNSAT    &    820  &   818 &   808 &   772 \\
+% 							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
+% \multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
+% 							& UNSAT    &   1031  &   936 &  1021 &   958 \\
+% 							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
+% \multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
+% 							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
+% 							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
+% \end{tabular}}
+% \label{table:base_benchmark}
+% \end{table}
+
+% \begin{table}[h]
+% \centering
+% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
+% \scalebox{0.8}{
+% \begin{tabular}{|l r | r r r r|}
+% \hline
+% \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
+% \multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
+% 								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
+% 								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
+% \multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
+% 								& UNSAT    &    720  &   660 &   724  &   644 \\
+% 								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
+% \multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
+% 								& UNSAT    &      0  &     0 &     0  &     0 \\
+% 								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
+% \multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
+% 								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
+% 								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
+% \end{tabular}}
+% \label{table:str_int_benchmark}
+% \end{table}
 
@@
 
-% \todo{Update table with data of timeout=30s}
-
 \begin{table}[h]
@@
 \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
-2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
-3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
-4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
-5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
-6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
-7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
-8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
-9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
-10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
-11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
-12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
+2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.89s) & \textbf{SAT}(0.45s) & \textbf{ERROR} \\
+3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(1.17s) & \textbf{SAT}(0.10s) & \textbf{ERROR} \\
+4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) & \textbf{TIMEOUT}    & \textbf{ERROR} \\
+5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(11.27s)& \textbf{TIMEOUT}    & \textbf{ERROR} \\
+6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.13s) & \textbf{UNKNOWN} \\
+7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
+8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.29s) & \textbf{ERROR} \\
+9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
+10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.48s) & \textbf{TIMEOUT} \\
+11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.36s) & \textbf{ERROR} \\
+12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.38s) & \textbf{TIMEOUT} \\ \hline
 \end{tabular}}
@@
 \end{table}
+
+% \todo{Update table with data of timeout=30s}
+
+% \begin{table}[h]
+% \centering
+% \caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
+% \scalebox{0.9}{
+% \begin{tabular}{| c | c c c c|}
+% \hline
+% \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
+% 2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
+% 3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
+% 4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
+% 5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
+% 6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
+% 7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
+% 8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
+% 9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
+% 10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
+% 11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
+% 12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
+% \end{tabular}}
+% \label{table:checkLuhn}
+% \end{table}
 

### 2020-03-29 final-version/main.tex
set-up

--- 2020-03-23 draft.tex
@@
-\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigplan,screen]{acmart}
+
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+\setcopyright{acmcopyright}
+\acmPrice{}
+\acmDOI{10.1145/3385412.3386034}
+\acmYear{2020}
+\copyrightyear{2020}
+\acmSubmissionID{pldi20main-p869-p}
+\acmISBN{978-1-4503-7613-6/20/06}
+\acmConference[PLDI '20]{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation}{June 15--20, 2020}{London, UK}
+\acmBooktitle{Proceedings of the 41st ACM SIGPLAN International Conference on Programming Language Design and Implementation (PLDI '20), June 15--20, 2020, London, UK}
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+
+%%
+%% end of the preamble, start of the body of the document source.
+
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{microtype}
 
@@
 \usepackage{pgfplots}
-
 \usetikzlibrary{positioning}
@@
 \title{Efficient Handling of String-Number Conversion}
-\author{}
+
+\author{Parosh Aziz Abdulla}
+\affiliation{
+  \institution{Uppsala University}
+    \state{Uppsala}
+     \country{Sweden}                    %% \country is recommended           
+}
+
+\email{parosh@it.uu.se}
+
+\author{Mohamed Faouzi Atig}
+\affiliation{
+  \institution{Uppsala University}
+      \state{Uppsala}
+    \country{Sweden}                    %% \country is recommended
+}
+\email{mohamed\_faouzi.atig@it.uu.se}
+
+\author{Yu-Fang Chen}
+\affiliation{
+  \institution{Academia Sinica}
+      \state{Taipei}
+    \country{Taiwan}                    %% \country is recommended
+}
+\email{yfc@iis.sinica.edu.tw}
+
+\author{Bui Phi Diep}
+\affiliation{
+  \institution{Uppsala University}
+      \state{Uppsala}
+    \country{Sweden}                    %% \country is recommended
+}
+\email{bui.phi-diep@it.uu.se}
+
+\author{Julian Dolby}
+\affiliation{
+  \institution{IBM Research}
+      \state{NY}
+    \country{USA}                    %% \country is recommended
+}
+\email{bui.phi-diep@it.uu.se}
+
+\author{Petr Janků}
+\affiliation{
+  \institution{Brno University of Technology}
+      \state{Brno}
+    \country{Czechia}                    %% \country is recommended
+}
+\email{ijanku@fit.vutbr.cz}
+
+\author{Hsin-Hung Lin}
+\affiliation{
+  \institution{Academia Sinica}
+      \state{Taipei}
+    \country{Taiwan}                    %% \country is recommended
+}
+\email{hlin@iis.sinica.edu.tw}
+
+\author{Lukáš Holík}
+\affiliation{
+  \institution{Brno University of Technology}
+      \state{Brno}
+    \country{Czechia}                    %% \country is recommended
+}
+\email{holik@fit.vutbr.cz}
+
+\author{Hsin-Hung Lin}
+\affiliation{
+  \institution{University of Southern California}
+      \state{CA}
+    \country{USA}                    %% \country is recommended
+}
+\email{wwu@isi.edu}
+
+\renewcommand{\shortauthors}{Abdulla, et al.}
 
@@
 In particular solving string constraints with string-number conversion  is necessary  for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages.
-However, the state-of-the-art constraint solvers have only very limited support to this type of constraint.
+However, the state-of-the-art constraint solvers have   limited support to this type of constraint.
 We propose to overcome these limitations with an approach that can efficiently support both string-number conversion and other common types of string constraints.
@@
 \end{abstract}
+
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10002978.10002986.10002990</concept_id>
+<concept_desc>Security and privacy~Logic and verification</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10011007.10010940.10010992.10010998</concept_id>
+<concept_desc>Software and its engineering~Formal methods</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+%\ccsdesc[500]{Theory of computation~Verification by model checking}
+\ccsdesc[500]{Security and privacy~Logic and verification}
+\ccsdesc[300]{Software and its engineering~Formal methods}
+%% Keywords
+%% comma separated list
+\keywords{String Solver, Formal Verification, Automata}  %% \keywords are mandatory in final camera-ready submission
 

### 2020-03-29 final-version/main.tex
shorting the names
update

@@
 
-\renewcommand{\shortauthors}{Abdulla, et al.}
+\renewcommand{\shortauthors}{P.A. Abdulla, M.F. Atig, Y-F. Chen, B.P. Diep, P. Janků, H-H. Lin, L. Holík and H-H. Lin}
 
@@
 
+ \clubpenalty = 10000
+          \widowpenalty = 10000
+          \displaywidowpenalty = 10000
+
+\usepackage{flushend} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 An important class of string operations is  the string-number conversions.
-While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from extremely limited support by the state-of-the-art string constraint solvers.
-
-%For many languages such as Java, string-number conversion is not a core operation, and much symbolic execution can be done without supporting it; however, this is not true of scripting languages, of which JavaScript is the most notable.
-%For many languages such as JavaScript, string-number conversions are core operations, and symbolic execution cannot be done without supporting it.
+While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from  limited support by the state-of-the-art string constraint solvers.
+
 In fact, a code that receives string input tends to need to convert at least some of that input into numbers.
-%,  which makes the handling of string-integer conversions of the utmost importance.  \yfc{maybe this is a too strong argument using this example}
 For example, the program fragment below is a variant of the Luhn test algorithm that is often used in credit card or ID validation.
-
-%
-%However,  solvers have limited support for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
-When there is support, it is often very limited.
-Thus, $n = \sti{\texttt{"2"}}$ or $x = \its{5}$ are handled but $n = \sti{x}$ (i.e., converting the string $x$ to the integer $n$) and $x = \its{n}$ (i.e., converting the integer $n$ to the string $x$) are core operations %
-%
-
-%The path feasibility problem is a critical module in the symbolic execution of string-manipulating programs.
-The problem is usually solved by a reduction to a string constraint satisfiability problem.
-Program statements in the path are translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{string constraint solvers}.
-Among all types of program statements, \emph{string-number conversion} is one of the core operations that requires stronger solver support.
-
-%The path feasibility problem is a critical module in the symbolic execution of string-manipulating programs.
-The problem is usually solved by a reduction to a string constraint satisfiability problem.
-Program statements in the path are translated to equivalent constraints in static single assignment (SSA) form and then solved by \emph{string constraint solvers}.
-Among all types of program statements, \emph{string-number conversion} is one of the core operations that requires stronger solver support.
-
-%
-%In fact, for many languages such as Java, string-number conversions are a niche operation, and much symbolic execution has been done without supporting it.
-However, code that receives input tends to need to convert at least some of that input into numbers, which makes string-integer conversions critical to checking it.
-For example, the program fragment below is a variant of the Luhn test algorithm \cite{?} that is often used in credit card or personal ID validation.
 
@@
 
-Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
+Most of the state-of-the-art string constraint solvers provide   limited support to the combination of above constraints.
 Even for simple constraints like the above one, most solvers already fail to provide a correct answer.
-\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve even the case of 2 loop iterations.}
-Therefore, there is an urgent  need for developing efficient techniques for solving such combinations of constraints.
-
-%Currently, even for the above constraint, which is from a simple program, most of the-state-of-the art solvers fail to provide a correct answer.
+\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve  the case of 2 loop iterations.}
 
@@
 
-%Most of the state-of-the-art string constraint solvers provide only very limited support to the combination of above constraints.
-Even for a simple constraint like the above one, most solvers already fail to provide a correct answer.
-
-\hide{String constraint solving has received considerable attention in the constraint solving community, with solvers such as CVC4 and Z3 implementing solvers of ever-increasing sophistication.
-Operations such as substring and string length are widely supported, and recent solvers such as Z3-str3 have shown impressive results.
-However, these solvers have limited for operations that convert between strings and integers; string length operations are sometimes well supported, but not parsing a string as an integer or turning an integer value into its string form.
-When there is support, it is often limited to ground terms, i.e.
-at least one side of the conversion must be a constant.
-Thus, $n = \sti{"15"}$ or $x = \its{5}$ are handled but $n = \sti{x}$ will fail.}
-
-%As solvers are applied to symbolic execution of programming languages, this is increasingly becoming a severe limitation.
-For many languages such as Java, conversion between integers and strings is a niche operation, and much symbolic execution can be done without supporting it; however, this is not true of some scripting languages, of which JavaScript is the most notable.
-JavaScript is a key language---it powers most interactive content on the Web, and increasingly server-side code with Node.js---and it has conversions between strings and integers embedded in the core of its semantics.
-
 \begin{center}
-	\begin{minipage}{5cm}
+	\begin{minipage}{\linewidth}
 		\begin{verbatim}
@@
 
-\medskip
-\hspace{-4mm}\begin{tabular}{l|l|c}
-1&	{\tt{x = [0, 0, 0, 0, 0]}} & [0, 0, 0, 0, 0] \\
-2&	{\tt{x[3] = 4}} & [0, 0, 0, 4, 0] \\
-3&	{\tt{x[03] = 2}} & [0, 0, 0, 2, 0] \\
-4&	{\tt{x["3"] = 5}} & [0, 0, 0, 5, 0] \\
-5&	{\tt{x["03"] = 7}} & [0, 0, 0, 5, 0] and x["03"] = 7\\
-6&	{\tt{x["03"-1] = 2}} & [0, 0, 2, 5, 0] and x["03"] = 7\\
+\begin{center}
+\begin{tabular}{l|l|c}
+1&{\tt{x = [0,0,0,0,0]}} & [0,0,0,0,0]\\
+2&{\tt{x[3] = 4}} & [0,0,0,4,0] \\
+3&{\tt{x[03] = 2}} & [0,0,0,2,0] \\
+4&{\tt{x["3"] = 5}} & [0,0,0,5,0] \\
+5&{\tt{x["03"] = 7}} & [0,0,0,5,0] and x["03"] = 7\\
+6&{\tt{x["03"-1] = 2}} & [0,0,2,5,0] and x["03"] = 7\\
 \end{tabular}
-\medskip
+\end{center}
 
@@
 
-\hide{
-
-The Line 4 of the code updates the length of \texttt{x} to $13$ and hence the \texttt{resetArray(x)} will update \texttt{x} to an array with $13$ zeros.
-Now suppose that the Line 4 of the code above becomes {\tt{x[k] = 5}}, where $\mathtt{k}$ is an user input string and we want to find an input such that $\mathtt{x[15]=0}$.
-In this case, one would need to know the value of $\sti{k}$ and hence whether it will affect the size of the array {\tt{x}}.
-More precisely, in the corresponding string constraint encoding, we use a shadow variable $xLen$ to remember the length of $x$ and update its value after all array assignment.
-For an assignment $\mathtt{x[k] = v}$, we update the array value and length using the following string constraint (combined the $select$ function from SMT array theory): $x_{i+1} = store(x_i,k, v)$ and $xLen_{i+1} = ite( xLen_{i}> \sti{k}, xLen_{i}, \sti{k})$.
-This is a rather straightforward array operation, and so having only limited capability for handling str/num conversion. will cripple any model of non-trivial JavaScript code.
-
-}
-
-\hide{In this code, string and integer values access the same array elements interchangeably, necessitating conversions between string and integers to faithfully model JavaScript semantics.
-
-Now observe that {\tt{resetArray}} assigns to the array in a loop of which the size cannot, in general, be known a priori; as such, it falls into the case where neither the string nor the integer in a conversion is constant and hence most SMT solvers will not be able to handle it.
-More specifically, in some program the assignment {\tt{x[k] = 5}} can happen before calling {\tt{resetArray(x)}}, where {\tt{k}} is an user input string.
-One would need to know the value of $\sti{k}$ and hence whether it will affect the size of the array {\tt{x}}.
-This is a rather straightforward array operation, and so this limit will cripple any model of non-trivial JavaScript code.
-}
-
-\hide{
-For the purpose of program analysis, string solver also needs to support \emph{equality constraints} (e.g.
-$x.y = y.x$), \emph{regular constraints} (e.g., $x \in (a.b)^*$), and \emph{integer constraints} (e.g., $|x|-|y|>3$).
-Most of the standard string operations can be encoded using the above three types of constraints.
-For instance, $y=x.charAt(i)$ can be encoded as $x=x_1.x_2.x_3 \wedge |x_1| = i \wedge |x_2| =1 \wedge y= x_2$.
-Those are also the type of constraints supported by most state-of-the-art string constraint solvers such as Z3, CVC4, Z3Str3, and Trau+.}
-
-\hide{
-Indeed, the analysis of string manipulating program is becoming more and more important nowadays.
-Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string input values.
-In the past, a significant amount of research efforts have been investigated to symbolic execution and test case generation of string manipulating programs~\cite{saxena2010symbolic,artzi2011framework,huang2004securing,sen2013jalangi} and string constraint solving~\cite{kiezun2009hampi,abdulla2014string,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2} is the core enabling technology.
-}
-
-\hide{Why this problem is important? Need to say it is used often, e.g., read 
-from text file or user input. Why this problem is challenging? It is undecidable. Some tricky cases 
-using string as array index. Bounded SAT-based encoding might not work even for 
-very simple constraints. e.g., $y=str2int(x) \wedge y>9999999$, if $x$ is a 
-ASCII string, then XXX Boolean variables are required. Or we can just propose 
-an example that all major solver fails.
-Maybe we still say our approach is still over-approximation + under-approximation, in this case, need to think how to present the over-approximation part.
-Maybe no CEGAR is fine.
-
-String data type is omnipresent in modern programming languages.
-Various infamous security vulnerabilities such as injection and cross-site scripting attack are caused by malicious string values.
-As a results, in the past, a significant amount of research efforts have been investigated to symbolic execution and test case generation of string manipulating programs~\cite{saxena2010symbolic,artzi2011framework,huang2004securing,sen2013jalangi}.
-The core enabling technology for these approaches is string constraint solving~\cite{kiezun2009hampi,abdulla2014string,zheng2013z3,abdulla2015norn,abdulla2017flatten,wang2016string,abdulla2018trau,chen2019decision,zheng2017z3str2}.
-However, all these modern solvers fall short when \textit{string-number conversion function} occurs in the program.
-
-String-number conversion function is very frequently used in string-manipulating programs.
-For example, often that programs read plain string input from text files, partition it according to some predefined separator symbol (e.g., the comma symbol), and then convert each string partition to the desired data type (often integers).
-In the reverse direction, programs also convert values in numerical data type back to string and store them as text files.
-
-Incorrect handling of string-number conversion can cause very subtle bugs.
-For example, in JavaScript, variables are untyped and (implicit) type conversion happens automatically to the stored values. Consider the following simple program
-
-\begin{lstlisting}[breaklines=true,language=JavaScript]
-var arr = [1,...,M];
-var input = //from user
-if(0<=input<M-1){
-	document.write(arr[input])
-}
-\end{lstlisting}
-
-The program reads input value from users and use it as the array index.
-This program works perfectly no matter the input is in string form (e.g., ``1", ``3") or numerical form (e.g., $1$, $3$).
-Both of them can pass though the range test (when the input is a string, it will be first convert to integer and then compared with $0$ and $M$).
-However, the programmer may find later that he wants to shift the index value by one, say, change \texttt{document.write(arr[input])} to \texttt{document.write(arr[input+1])}.
-In such case, the program is still correct if \texttt{input} is a number, but will behave incorrectly if \texttt{input} is a string.
-For example, when \texttt{input=="5"}, the \texttt{+} operator in \texttt{input+1} will be interpreted as string concatenation and the value $1$ will be converted to a string.
-Therefore, the program will output \texttt{arr["51"]} instead of \texttt{arr["6"]}.
-If one searches CVE (Common Vulnerabilities and Exposures), he/she can find a number of vulnerabilities (e.g., clauses array-out-of-bound) due to incorrect handling of string-number conversion.
-
-In the example above, we can detect the array-out-of-bound problem (that happens when \texttt{input} is a string) by checking the satisfiability of the string constraint below\footnote{The case \texttt{input} stores an integer value can be check by another formula.}.
-
-$$
-\begin{array}{c}
-0 \leq \sti{input}<M-1 \wedge \\
-\neg(index = input\cdot \its{1} \wedge 0 \leq \sti{index} <M-1)
-\end{array}
-$$
-
-Such constraint contains \textit{string-number conversion} functions (e.g., $\sti{input}$ and $\sti{index}$), \textit{equality constraints} (e.g., $index = input\cdot \its{1}$), and \textit{integer constraints} (e.g., $0 \leq \sti{input}<M$).
-}
-
-%Solving string constraints with string-number conversion has been proven undecidable~\cite{day2018satisfiability}, and our experiments (Section \ref{section:evaluation}) show that state-of-the-art string constraint solvers provide only limited support to string-number conversion.
-
 Solving string constraint with string-number conversion is a very challenging problem.
@@
 From practical point of view,
- our experimental results  (in Section \ref{section:evaluation}) show that the current  the state-of-the-art string constraint solvers provide only limited support to string-number conversion.
+ our experimental results  (in Section \ref{section:evaluation}) show that the current  the state-of-the-art string constraint solvers provide little support to string-number conversion.
 
@@
 Both over- and under-approximation fall in a decidable fragment of string constraints that  we can efficiently solve.
-
-%Observe that our main contribution lies in the
 
@@
 	\end{tikzpicture} }
-
 		\caption{An example of a parametric flat automaton}
+		\Description{An example of a parametric flat automaton}
 			\label{fig:sfa_def}
@@
 To gain in efficiency, we label each transition  of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between every two states for each symbol in the alphabet.
-This done by associating to each character in our alphabet a unique natural number.
+This is done by associating to each character in our alphabet a unique natural number.
 This allows us to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers and it is  the key for handling string-number conversion efficiently.
-
-%The second step of our decision procedure is only enabled if the over-approximation step returns SAT.
-In this case, our decision procedure restricts the domain of each string variable to strings that obey some predefined and parameterized pattern.
-Adjusting the parameters enlarges or prunes the potential solution space.
-In this paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA).
-A PFA is a {\em flat} finite state automaton consisting of a predefined sequence of loops, each of fixed length (see Figure \ref{fig:sfa_def}).
-The approach based on PFA is very flexible yet allows very efficient manipulation.
-One can pick PFA of \emph{arbitrary structure} for search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-Furthermore, we associate a unique natural number with each character.
-This allows us to assume that the input alphabet is a subset of natural numbers to avoid the \textit{alphabet explosion problem} from which the approach in~\cite{abdulla2017flatten} suffers.
-We label each transition between two states of a PFA with a unique \emph{character} variable (whose domain is the set of natural numbers) instead of having a transition between each two states for each symbol in the alphabet.
-%Such reduction based on PFA is the key to handling string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to the satisfiability problem of linear formulae and can be solved efficiently.
-
-%The battle field is in fact those SAT instances, for which we develop solutions using under-approximation.
-For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
-By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
-In paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA) (will be defined formally in Section~\ref{section:sfa}).
-The approach based on PFA is very flexible yet allows very efficiently manipulation.
-One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.
-%%In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation still encodes possibility an infinite number of models.
-%Such reduction based on PFA is the key to handle string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulae and can be solved efficiently.
-We can step-wisely enrich the PFAs and hence solve the satisfiability problem of string constraints in a systematic manner.
 
@@
 	\end{minipage}
-
+			\Description{Examples of parametric flat automata associated to the variables  $x$ and $y$}
 	\caption{Parametric flat automata of $x$ and $y$}
@@
 
-%For over-approximation, there are a few existing algorithms~\cite{abdulla2019chain,z3,chen2019decision}, our framework does not set any restriction on which algorithm to be used.
-In our experiences, the UNSAT instances in all available benchmarks are not that difficult, and the differences between the major algorithms are very small.
-In our tool \tool, we use a version that is a simple adaption of the algorithm in~\cite{abdulla2019chain}.
-
-%The battle field is in fact those SAT instances, for which we develop solutions using under-approximation.
-For under-approximation, we restrict the search space of each string variable to strings that obey some predefined and parameterized pattern.
-By adjusting the parameters, one can easily enlarge or prune out the potential solution space.
-In paper, we propose to use patterns defined by \emph{parametric flat automata} (PFA) (will be defined formally in Section~\ref{section:sfa}).
-The approach based on PFA is very flexible yet allows very efficiently manipulation.
-One can pick PFA of \emph{arbitrary structure} for the search space restriction and reduce the string constraint solving problem to a linear formula satisfiability problem in polynomial-time.
-Moreover, it avoids the \textit{alphabet explosion problem} that the approach in~\cite{abdulla2017flatten} suffers.
-%%In contrast to under-approximation based on bit-blasting~\cite{kiezun2009hampi} (i.e., limit the length of the strings and encode the string constraint to a Boolean formula), our linear formula for under-approximation still encodes possibility an infinite number of models.
-%Such reduction based on PFA is the key to handle string-number conversion efficiently.
-When we restrict the solution space to those defined by PFAs, the original undecidable problem (i.e., string constraint with string-number conversion) is reduced to linear formulae and can be solved efficiently.
-We can step-wisely enrich the PFAs and hence solve the satisfiability problem of string constraints in a systematic manner.
-
-\hide{More concretely, based on the PFA encoding, we manage to translate the string constraint with string-number function to an equisatisfiable pure numerical constraints.
-Thus the problem is significantly simplified.
-We show that if we restrict the variable to arbitrary PFA, one can convert the a string constraint with string-number function to an integer constraint consisting of both polynomials and exponentials.
-Solving such kind of constraints is a very difficult task.
-For simpler cases where the variables are real numbers, decision procedures for different subclass polynomial-exponential equations exists~\cite{gan2015decidability,kincaid2019closed,achatz2008deciding}.
-To the best of our knowledge, the satisfiability problem of polynomial-exponential equations is still open.
-For efficiency reason, we propose to use PFA with specific structural constraint to handle string-number conversion function.
-That is, if we encountered a constraint $y=\sti{x}$, then we always restrict the domain of $x$ to some specific kind of PFA, instead of allowing arbitrary PFAs.
-This allows us to convert a string constraint with string-number conversion function to an equisatisfiable linear formula, which can be solved very efficiently.
-}
-
-\hide{Our string constraint solving procedure can be easily integrated in a \emph{satisfiability module theory (SMT)} solver as a theory solver.
-The integration allows us to express string operations that cannot be reduced to the type of constraints (regular, equality, integer, string-number conversion) supported by our procedure.
-For example, we can encode \texttt{split} using the code fragment in Figure~\ref{fig:smt_string}.
-Other functions such as \texttt{replaceAll} and \texttt{reverse} can be encoded in a similar manner.
-The performance of such encoding might not be as good as those that provide direct support to those operations, but at least it works for some cases in our experiments.
-Further details of the combination as well as some other implementation details can be found in Section~\ref{section:implementation}.
-
-\begin{figure}
-	\begin{Verbatim}[fontsize=\scriptsize,xleftmargin=-4cm]
-				(define-fun-rec split ((x String)(y String)(xIdx Int)(aIdx Int)) 
-				(Array Int String)
-				(ite (= xIdx (str.len x))
-				 (store ((as const (Array Int String)) "") aIdx x)
-				 (ite (= y (str.at x xIdx)) 
-				  (store 
-				   (split (str.substr x (+ xIdx 1) (- (str.len x) 1) ) 
-				   0 (+ aIdx 1) y) 
-				   aIdx
-				   (str.substr str 0 xIdx)
-				  )
-				  (split x (+ xIdx 1) aIdx y)
-				 )
-				)
-			\end{Verbatim}
-
-	 	\caption{Encoding \texttt{Split(x,y)} to an SMTLIB2 formula using recursive functions and the array theory.
-The recursive function \texttt{split (x y 0 0)} returns an array of type \texttt{(Array Int String)} that maps an index $i$ to the $i$th component (separated by the character $y$ ) of $x$.}
-	 	\label{fig:smt_string}
-\end{figure}
-
-}
-
-To demonstrate the usefulness of our approach, we have implemented our decision procedure in an open source solver, called {\tool} and evaluated it on a large set of benchmarks obtained from literatures and from symbolic execution of real world programs.
+To demonstrate the usefulness of our approach, we have implemented our decision procedure in an open source solver, called {\tool} and evaluated it on a large set of benchmarks obtained from the literature and from symbolic execution of real world programs.
 The experimental results show that {\tool} is among the best tools for solving basic string constraints and significantly outperforms all other tools on benchmarks with string-number conversion constraints.
@@
 
-\smallskip
-
-\noindent
-{\bf Summary of the Contributions}
+\subsection*{Summary of the Contributions.}
 
@@
 
-\paragraph{Outline.}
-After recalling the  definition in Section \ref{section:sc}. Section \ref{section:over} presents a brief overview of our decision procedure. 
+\subsubsection*{Outline.}
+After recalling the  definition in Section \ref{section:sc}, Section \ref{section:over} presents a brief overview of our decision procedure. 
 Section \ref{section:sfa} introduces  the class of parametric flat automata. 
@@
 
-\hide{
-To ease presentation, in the paper, we only consider string constraints consisting of \emph{equality constraints (a.k.a.
-word equation)}, \emph{regular constraints}, \emph{length constraints}, and \emph{string-number conversion} functions.
-
-suggest restricting the string domain to $0^*[0-9]^k$, where $k$ is the maximum 
-digit allowed in the corresponding number value. In programming languages 
-such as JavaScript or Python, a number with $k$ digits can be converted from a 
-string of length arbitrarily longer than $k$. For example, $12 = 
-str2int(``0000012")$. That is why we use $0^*$ at the beginning of the pattern.
-Under this domain, we can convert the string-number conversion constraints to 
-linear integer constraints, which is much easier to solve. In our experience, 
-usually, it suffices to find a solution using a small $k$ for a satisfiable 
-constraint. Note that a 64-bit integer number corresponds to a word with 
-$k\leq 21$.
-
-Given a formula that is a boolean combination of different types of string constraints, e.g., $\phi=(|x| = |y| \vee \sti{x} = \sti{y})\wedge x = y$, an SMT solver based on the DPLL(T) algorithm~\cite{} treats each string constraint $|x| = |y|$, $\sti{x} = \sti{y}$, $xy=yx$ as a boolean variable, and systematically guesses possible solutions without considering their semantics as string constraints.
-E.g., the solver may guess $\neg(|x| = |y|)$, $(\sti{x} = \sti{y})$, and $(x =y)$.
-This is a valid guess if all the string constraints are just interpreted as boolean variables, but invalid when their semantics as string constraints are considered, because it cannot be the case that $x$ and $y$ are the same string $(x =y)$, but they are of different lengths $( \neg (|x| = |y|))$.
-
-The approach combines techniques from both automata theory and SMT solving to explore the model space of a string constraint systematically.
-More specifically, an SMT solver based on the DPLL(T) algorithm~\cite{} is used to convert the satisfiability of a string constraint, which is an arbitrary boolean combination of string predicates, to the satisfiability problem of a set of string constraints in the form of conjunctions of string predicates.
-
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Overview} \label{section:overview}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%Here we try to explain the approach using a toy example $\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$.
-Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x=``12"$ and $y=``1212"$.
-%
-%For proving UNSAT, our framework does not set any restriction on which decision procedure to use.
-One can select any decision procedure they want to use and ``over-approximate" the input constraint to one that falls in the decidable fragment, e.g., the acyclic fragment~\cite{abdulla2014string}, the straight-line fragment~\cite{chen2019decision}, or the chain-free fragment~\cite{abdulla2019chain}.
-For instance, we can convert $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$ using two auxiliary variables $x_1,x_2$ and replace the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
-This produce new formulae that over-approximate the original ones and fall in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
-Since $\Phi$ is satisfiable, the over-approximation module will not return UNSAT.
-In our implementation \tool, we further add heuristics trying to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some other cases, we can derive the value of $n=12$ from some integer constraints.
-In such case, we can further derive the value of $x$ is in the regular language $(0^*12)$.
-%
-%Then our procedure will restrict the domain of each string variables to the language defined by some parametric flat automata (PFA) and convert them to equisatisfiable linear formula.
-The details of the under-approximation component will be described in Section~\ref{section:under_approximate}.
-Here we try to explain what the linear formula looks like by an example.
-Assume that we project the domain of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.
-One special treatment we do in this paper is that we encoding characters as natural numbers.
-So $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from the formula $ y \in (12)^+$, we may derive $v_3=1$ and $v_4=2$.
-%
-%The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$, as well as, the number of occurrences of each character variables $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
-Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4)= (1,2,1,2,1,1,2,2)$.
-The assignment says, for example, that $x$ is the parametric word obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
-%
-%If a model of the produced linear formula is found, then the procedure concludes SAT with an assignment to the string variables.
-If not, our procedure step-wisely change the PFA to more expressive ones (by adding more states and transitions) to systematically search for the solution.
-Depending on the implementation, one may choose to report unknown after some certain steps.
-%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Preliminaries} \label{section:preliminary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%We use $\mathbb{N}$ and $\mathbb{Z}$ to denote the sets of natural numbers and 
-%integers. For a set $A$, we use $|A|$ to denote its size. For a string $w$, we 
-%use $|w|$ to denote its length and $|w|_a$ to denote the number of occurrences of $a$ in $w$.
-We $\epsilon$ to denote an empty string and use $w_1\cdot w_2$ to denote the concatenation of strings $w_1$ and $w_2$.
-Let $S$ be a finite set of symbols.
-We use $S^+$ to denote the set of string over $S$ and $S^* = S^+\cup \{\epsilon\}$.
-We define $S_\epsilon =S\cup\{\epsilon\}$.
-A language
-%$L$ over $S$ is a set of strings in $S^*$. 
-%
-%A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of states, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of transition relation, $\Sigma$ is the alphabet, $q_0$ is the initial state, and $q_m$ is the final state.
-The semantics of finite automaton is defined in the standard manner.
-We use $L(A)$ to denote the regular language, i.e., set of accepted strings, of the automaton $A$.
-
-%Given a finite automaton $A$ over $\{a_1,a_2,\ldots,a_n\}$, the Parikh image of $L$ is the set $\{(|w|_{a_1},\ldots, |w|_{a_n}) \mid w \in L(A) \}$, i.e., the number of occurrences of each symbol $\{a_1,a_2,\ldots,a_n\}$ of words in $L(A)$.
-Moreover, one can construct from $A$ in linear time a Presburger formula $\phi_A(v_1, \ldots,v_n)$ such that $\phi(c_1, \ldots,c_n) \iff (c_1, \ldots,c_n)$ in the Parikh image of $L$~\cite{SeidlSMH04}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-A \emph{finite automaton} (FA) is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_i$ is the \emph{initial state}, and $q_f$ is the \emph{final state}.
-%The semantics of finite automaton is defined in the standard manner. 
+A \emph{finite automaton} (FA) is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times (\Sigma \cup \{\epsilon\}) \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_i$ is the \emph{initial state}, and $q_f$ is the \emph{final state}.
 A \emph{run} $\pi$ of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transitions $(q_0,a_1,q_1),(q_1,a_1,q_2),\ldots,(q_{n-1},a_n,q_n)$.
-The run $\pi$ (resp.
-the word $w$) is \emph{accepting} (resp.
-\emph{accepted}) if $q_0 = q_i$ and $q_n = q_f$.
+ The run $\pi$ (resp. the word $w$) is \emph{accepting} (resp. \emph{accepted}) if $q_0 = q_i$ and $q_n = q_f$.
 The \emph{language} of $A$ (denoted by $L(A)$) consists of  the set  of all accepted words.
-
-%Through the paper, we will use quantifier-free linear integer arithmetic formulae, and call them \emph{linear formulae} for short.  
-%Given a linear formula $\phi$, a set of variables $V$, and an \emph{interpretation} of $V$, i.e., a function $I:V\rightarrow \nat$, 
-%we denote by $I\models_V \phi$ that $I$ satisfies $\phi$ (which is defined in the standard manner), and call $I$ a \emph{model} of $\phi$ over $V$. 
-%
-%\lh{Our use of indexing by $V$ in the text later is not very nice.
-Add this for clarity?: If $V$ contain additional variables not present in $\phi$, the these might be assigned arbitrary values by $I$.
-If $V$ is missing some of the variables of $\phi$, then it must be possible to complete $I$ with assignment of the missing variables into a satisfying assignment of $\phi$ (as in existential quantification).}
-%We use $\modelsof \phi$ to denote the set all models of $\phi$ over $V$. 
-%We drop the reference to $V$ and write just ``model of $\phi$", $\modelsof \phi$, and $\models$ when no confusion may arise.
-For a set of interpretations $S$, we use $S_\Sigma$ to denote the set of interpretations obtained from $S$ by projecting the domain to $\Sigma$.
 
@@
 We use $\modelsof \phi$ to denote the set all models of $\phi$.%
-%Let $J$ and $J'$ be two sets integer interpretations, $J$ containting interpretation of variables $V$ and $J'$ of variables $V'$. 
-%We say that $J$ and $J'$ are \emph{equivalent}, written $J\iequiv J'$, if their interpretations restricted to the common variables are the same, that is, if 
-%$\{\restrict I {V\cap V'} \mid I \in J\} = \{\restrict {I'} {V\cap V'} \mid I' \in J'\}$. We may write $J\eqwrt{V\cap V'} J'$ if we wish to made the common variables explicit.
 
@@
 Assume that $\vars$ ia a set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ a set of \emph{integer variables} ranging over $\mathbb{Z}$.
-%For a variable $x$, we call its primed version (e.g., $x'$) or indexed versions (e.g., $x_1$) its \emph{variants}.
-%In this paper, we use $x,y$ (or their variants) to denote string variables and $n$ (or its variants) to denote integer variables. 
 An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I:\vars\cup \varn\rightarrow\Sigma^* \cup \mathbb{Z}$.
@@
 
-We will use four types of \emph{atomic string constraint}: 
-\smallskip
-
-$\bullet$ An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
+We  use four types of \emph{atomic string constraint}: 
+\begin{itemize}
+
+\item An \emph{equality constraint} $\phi_e$ is of the form $t_1 = t_2$ where $t_1, 
 t_2$ are word terms. The \emph{model} of $\phi_e$ is the set of interpretations $\modelsof{\phi_e}=\{I\mid 
@@
 
-\smallskip
-$\bullet$ An \emph{integer constraint} $\phi_i$ is a linear constraint over the integer variables in $\varn$ and values of $|x|$ for all $x \in \vars$, where $|\cdot|:\vars \rightarrow \nat$ is the string length function defined in the standard way.
-%Formally, assume that $\vars=\{x_i,\ldots,x_n\}$ and $\varn=\{y_i,\ldots,y_m\}$, a length constraint is of the form $(\sum_{i\in[1,n]}(j_i \times \sti{x_i}+k_i\times |x_i|)+ \sum_{i\in[1,m]}(l_i \times y_i)) \odot k$, where $\odot \in \{>,\geq, =, \leq, <\}$, and $j_i,k_i,l_i,k\in \mathbb{Z}$.
-We define $\modelsof{\phi}= \{I \mid (\sum_{i\in[1,n]}(j_i \times \sti{I(x_i)}+k_i\times |I(x_i)|)+ \sum_{i\in[1,m]}(l_i \times I(y_i))) \odot k \}$.
+\item An \emph{integer constraint} $\phi_i$ is a linear constraint over the integer variables in $\varn$ and values of $|x|$ for all $x \in \vars$, where $|\cdot|:\vars \rightarrow \nat$ is the string length function defined in the standard way.
 We define $\modelsof{\phi_i}= \{I \mid I(\phi_i)= \true \}$.
-\smallskip
-
-$\bullet$ A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
+
+\item A \emph{regular constraint} $\phi_r$ is of the form $x \in L(A)$ where $x$ is a string variable and $A$ is a finite automaton.
 The \emph{model} of $\phi_m$ is the set of interpretations $\modelsof{\phi_m}=\{I\mid
 I(x) \in L(A) \}$.
-\smallskip
-
-$\bullet$ A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
+
+\item A \emph{string-number conversion constraint} $\phi_s$ is of the form $n=\sti{x}$, where the function $\sti{x}$ is defined as follows.
 For $a\in [0,9]$, we have $\sti{a}=a$ and for $w \cdot a \in [0,9]^+$, $\sti{w\cdot a} = 10\times \sti{w}+a$.
@@
 The \emph{number-string} conversion constraint $x=\its{n}$ is treated as a syntactic sugar for $n=\sti{x}$.
-\smallskip
+
+\end{itemize}
 
@@
 The encoding has a benefit that it can also handle the case where $x$ is ``not a number", using the condition $\sti{x} = -1$.
-Supporting only positive integer is not a strong restriction, since conversing from negative integer can still be encoded using only the positive  version.
-
-%More specifically, if we want to say $n \in \varn$ is the integer value of the string $x \in \Sigma^*$, we can write the following constraint (ignore the case that $x$ is ``not a number", which can also be encoded using more conditions):
-%$$(n= \sti{x}) \vee (n=-\sti{x'} \wedge x = \enc{-}\cdot x')$$
-%Recall that $\enc{-}$ is the integer encoding of the minus symbol `$-$'. The \emph{number-string conversion function} $\its{n}$ is defined symmetrically. We have $x = \its{n}$ iff $y= \sti{n}$.
-
-%\section{Under-approximation} \label{section:under_approximate}
-%In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulae $\outlf$ in polynomial-time.
-We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
-%
-%We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
-In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulae $\outlf$.
-We also add constraints to $\outlf$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
-%
-%More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulae $\outlf$.
-After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
-For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA.
-We do not set any restriction to the selection of PFA for other string variables.
-The selection is an implementation decision.
-We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
-%
-%After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\insc$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\outlf$.
-The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
-In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
-%
-%
-% 
-%
-%
-%
-%\hide{We replace it with the following constraints.
-%	
-%	$$
-%	\begin{array}{c}
-%	(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
-%	\left(
-%	\begin{array}{cccc}
-%	
-%	y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
-%	y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
-%	|y_2|&=&|y'_2|=1
-%	\end{array}
-%	
-%	\right)
-%	\end{array}
-%	$$
-%	
-%	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
-In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
-}
-%
-%
-%\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
+Supporting only positive integer is not a strong restriction, since converting from negative integer can still be encoded using only the positive  version.
 
@@
 
-%
-%In order to explain this step, we need to first describe what is a \emph{chain} in a set of equality constraints.
-%For two equality constraints, 
-%$\begin{array}{rcll}
-%	t_1&\defeq& \ldots x\ldots = \ldots y\ldots\\
-%	t_2&\defeq& \ldots y \ldots = \ldots&,
-%\end{array}$\\
-%we say the $x$ in $t_1$ \emph{depends on} the $y$ in $t_2$, because $y$ occurs on the other side of $x$ in $t_1$ and occurs on the same side of $x$ in $t_2$. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Parametric Flat Automata} \label{section:sfa}
@@
 We introduce \emph{parametric flat automata} that will be used to define patterns used by the under-approximation module to restrict the domain of string variables. 
-\scalebox{0.7}{
+\scalebox{0.65}{
 	\tikzset{state/.style={circle,draw=green!80,fill=green!20,
@@
 	\end{tikzpicture} }
-\paragraph{Flat automata} 
+
+\subsubsection*{Flat automata.} 
 A finite state automaton  
@@
 \begin{enumerate}
-	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a straight path of $m-1$ transitions $(\st{i}{0},a_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
+	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a straight path of $m-1$ transitions $(\st{i}{0},a_i,\st{i+1}{0}) \in T$ with $\st{i}{0} \in Q$ and $a_i \in \Sigma$ for $i\in[0,m-1]$.
 	\item  
-Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, a_{i}^{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$.
+Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, a_{i}^{j-1}, \st{i}{j \bmod l_i})$, with $a_{i}^{j-1} \in \Sigma$, for $j\in [1,l_i]$.
 Notice that the case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
-	\item Each character in $\Sigma$ appears on at most one transition. 
+	\item Each character in $\Sigma$ appears on at most one transition of the automaton $A$. 
 \end{enumerate}
@@
 %
-%\begin{proof}
-Observe that the $\parikhof w$ value of any variable appearing within the a cycle of $A$ is equal to the number of repetitions of that cycle in the accepting run.
+Observe that the $\parikhof w$ value of any variable appearing within  a cycle of $A$ is equal to the number of repetitions of that cycle in the accepting run.
 This is an immediate consequence of the fact that
- every variable appears on at most one transition. Thus, the accepting run on $w$ (and so $w$ itself) can be reconstructed from $\parikhof w$.
+ every character appears on at most one transition. Thus, the accepting run on $w$ (and so $w$ itself) can be reconstructed from $\parikhof w$.
 
@@
 $w_i = (a_i^0 \cdots a_i^{l_{i}-1})^{\pvarsof {a_i^0}}$ if $l_i >0$ and $w_i = \epsilon$ if $l_i = 0$.
-%\end{proof}
 
@@
 
-\paragraph{Parametric (flat) automata}
+\subsubsection*{Parametric (flat) automata}
 Next, we define \emph{parametric automaton} (PA) as a pair  $\pa = (A,\paf)$ where 
@@
 %
-a mapping $I:\cvar\rightarrow\Sigma_\epsilon$ (recall that $\Sigma_\epsilon \subseteq \nat$). 
+a mapping $I:\cvar\rightarrow\Sigma_\epsilon$ (recall that $\Sigma_\epsilon\defeq \Sigma \cup \{\epsilon\} \subseteq \nat$). 
 For a parametric word $x= v_1v_2\cdots v_k$ over $\cvar$, its interpretation $I(x)$ is then defined as $I(v_1)\cdot I(v_2)\cdot \ldots \cdot I(v_k)$.
-%
-%We define the semantics of $x$ as the set $\semof x$ of all possible interpretations of $x$, 
-%the semantics of a language $L\subseteq V^*$ is the union $\semof L = \cup_{x\in L} \semof{x}$ of semantics of its words, 
 We then define the semantics of the PA $P$ as the set of strings   
@@
 and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $I_e$. Namely,  
-% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
-	$$\encode \pa( w ) \defeq \{I_e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
-	$$\decode \pa(I_e) \defeq\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$
+	$$\encode \pa(w)=\{I_e |  x \in L(\pa), I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
+	$$\decode \pa(I_e)=\{ w | x \in L(\pa), I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$
 
@@
 Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
-%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
-
-\hide{Plan to remove this one and use the orange one.
-
-Observe that every word $w \in \semof{\pa}$ is uniquely determined by a parametric word $x\in L(A)$ and an interpretation $I\in\semof{\paf}$ such that $w = I(x)$.
-
-Let us assume now that  $\pa$ is a PFA.
-We  say that the assignment $I \cup \parikhof x$, uniting the interpretation $I:\cvar\rightarrow\Sigma_\epsilon$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$, \emph{$\pa$-encodes} $w$  since $x$ is uniquely determined by its Parikh image.
-%$x = \decode \pa(\parikhof x)$.
-%we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I:\cvar\rightarrow\Sigma_\epsilon$ and the Parikh image $\parikhof x:\#\cvar\rightarrow \nat$ \emph{$\pa$-encodes} $w$.
- Lemma~\ref{lemma:decoding} implies that such $\pa$-encoding can be uniquely decoded. 
-We  hence extend the decoding function $\decode \pa$ to united assignments $e:\cvar\cup\#\cvar \rightarrow \nat$ in the straightforward manner (i.e.,  $\decode \pa(I \cup \parikhof x) = w$).   
-The following corollary of Lemma~\ref{lemma:decoding} states that words in $\semof{\pa}$ are decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:}
 
@@
 
+\begin{acks}
+This research was  partially supported by the  Swedish Foundation for Strategic Research.
+\end{acks}
+
 \bibliographystyle{ACM-Reference-Format}

### 2020-03-29 final-version/main.tex
fixing typos

@@
 
-\author{Hsin-Hung Lin}
+\author{Wei-Cheng Wu}
 \affiliation{
@@
 
-\renewcommand{\shortauthors}{P.A. Abdulla, M.F. Atig, Y-F. Chen, B.P. Diep, P. Janků, H-H. Lin, L. Holík and H-H. Lin}
+\renewcommand{\shortauthors}{P.A. Abdulla, M.F. Atig, Y-F. Chen, B.P. Diep, P. Janků, H-H. Lin, L. Holík and W-C. Wu}
 
@@
 \end{corollary}
-%
-%\changed{removed definition of $\encode P (L)$.}
-
-%Last, we define the encoding function as a counterpart of the decoding. Given a PFA $\pa$ and a language $L\subseteq \Sigma^*$, the set of \emph{$\pa$-encodings} of the words in $L$ is defined as
-%$\encode \pa (L) = \{e \mid \decode \pa (e) \in L\}$. 
-%%
-%Notice that only the words from $L\cap \semof \pa$ have a $\pa$-encoding, 
-%hence $\encode \pa(L) = \encode \pa(L\cap\semof \pa)$, and so due to Corollary~\ref{corollary:pfa}, $\decode \pa({\encode \pa}(L)) = L\cap\semof \pa$.
-
-%\section{Under-approximation} \label{section:under_approximate}
-%In this section, we describe formally how to restrict the domain of string variables to patterns defined by \emph{parametric flat automata} (PFA) (Section~\ref{section:sfa}) and hence convert string constraints $\insc$ to a set of equisatisfiable linear formulae $\outlf$ in polynomial-time.
-We assume all disequality constraint $t_1 \neq t2$ are already converted to equal-satisfiable equality constraints and integer constraints in the standard way~\cite{abdulla2015norn}.
-%
-%We pick a PFA for each variable in $\vars$ at the beginning of the decision procedure and then construct the set of linear integer constraints in a stepwise manner.
-In each step, we take a string constraint from $\insc$ and depending on the type of the string constraint, we execute the corresponding procedure to produce the linear integer constraints and add them to the output linear formulae $\outlf$.
-We also add constraints to $\outlf$ to ensure all character variables of the PFAs only pick values from $\Sigma_\epsilon$.
-%
-%More concretely, at the beginning, we move all integer constraints in $\insc$ to the output linear formulae $\outlf$.
-After this step, $\insc$ is the union of the three sets of constraints: the equality constraints, the regular constraints, and the string-number conversion constraints.
-For all string variables $x$ that occurs in a string-number conversion constraint $n= \sti{x}$, we follow the rule that will be described in Section~\ref{section:s2i} to pick the corresponding PFA.
-We do not set any restriction to the selection of PFA for other string variables.
-The selection is an implementation decision.
-We will describe the PFA selection strategy of \tool in Section~\ref{section:implementation}.
-%
-%After the PFA for each variable is selected, we step-wisely pick and remove a string constraint from $\insc$, executing the corresponding procedure to create equisatisfiable linear constraints, and add all the results to $\outlf$.
-The procedures for regular, equality and string-number conversion constraints are in Sections~\ref{section:mem},~\ref{section:eq}, and~\ref{section:s2i}, respectively.
-In the rest of the section, we assume each string variable $x$ is restricted to a PFA $A_x$ with the set of character variables~$V_x$.
-%
-%
-% 
-%
-%
-%
-%\hide{We replace it with the following constraints.
-%	
-%	$$
-%	\begin{array}{c}
-%	(|x_1|+ |x_2|+ \cdots +|x_n| \neq |x_{n+1}| + |x_{n+2}|+ \cdots +|x_m|)\vee \\
-%	\left(
-%	\begin{array}{cccc}
-%	
-%	y_1\cdot y_2\cdot y_3 &=& x_1\cdot x_2 \cdots x_n &\wedge\\
-%	y_1 \cdot y'_2 \cdot y'_3 &=& x_{n+1}\cdot x_{n+2} \cdots x_m &\wedge\\
-%	|y_2|&=&|y'_2|=1
-%	\end{array}
-%	
-%	\right)
-%	\end{array}
-%	$$
-%	
-%	The second disjunct says that the constraints $x_1\cdot x_2 \cdots x_n$ and $x_{n+1}\cdot x_{n+2} \cdots x_m$ have a common prefix $y_1$, but the next character $y_2$ and $y'_2$ is different.
-In an more efficient implementation, one just project $y_2$ and $y'_2$ to a PFA that accept only symbolic words $v_1$ and $v'_1$, respectively (the PFA has no loop and only one transition).
-}
-%
-%
-%\yfc{say handling regular constraint can be exponential to the number of constraints, but in our under-approximation, it is polynomial.}
 
@@
 We show how to build a flattening $\underf \dr {\phi}$ for every atomic string constraint $\phi$ in the following sections.
-
-%The semantics of a string constraint $\phi$ restricted by $\dr$ is then defined as 
-%$\semof{\phi}^\dr = \{I\in\semof \phi \mid \forall x\in X:I(x)\in\semof{\dr(x)}\} \subseteq \vars\times \varn \rightarrow \Sigma^* \times\nat$.
 
@@
 The condition says that (1) $I$ and $I_e$ are consistent over variables in $Z$ and (2) $(I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}}$ is a word encoding that $\dr(x)$-encodes $I(x)$.
-%We define the output of $\decode  \dr (I_e\cup I_z)$ as a set so that \emph{invalid word encodings}, i.e.
-those do not corresponds to possible word encodings from PFAs, are mapped to empty sets and valid ones are mapped to singleton sets.
 We also define the $\dr$-encoding function as the counterpart of $\dr$-decoding,  
@@
 We consider the domain restriction $\dr$ such that $\dr(x)	 =(A_x,\true)$ from Figure~\ref{fig:sfa}~(a) and $\dr(y) = (A_y,\true)$ from Figure~\ref{fig:sfa}~(b). 
-%We assume that the set of integer variables is $Z=\{v_z\}$ and $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
 Let the set of integer variables be $Z=\{v_z\}$ and let $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
@@
 (indeed, notice that if it would be allowed to capture only some of the encodings, then for instance $\underf \dr {\phi} \land \underf \dr {\phi'}$ could only underapproximate $\semof{\phi\land\phi'}^\dr$).
-%To formalize this correctness argument, we need the notion of 
-%%
-%an \emph{$\dr$-encoding} of an interpretation $I \cup I'$ of a general string constraint, consisting of an interpretation $I$ of string variables and an interpretation $I'$ of integer variables:
-%%
-%An $\dr$-encoding of $I \cup I'$ is a union $e \cup I'$ of the original integer interpretation $I'$ and an interpretation $e : V_\dr \cup \#V_\dr \rightarrow \nat$ that encodes $I$, that is, it satisfies that for each string variable $x$ of $I$, $\decode {\dr(x)} (e_{V_x\cup\#V_x}) = I(x)$.
-%\yfc{need a serious rewrite :-) Maybe I need to know why you define so many encodings...}
-%
-%Further, if $I \cup I'$ is an interpretation of a general string constraint, that is, an interpretation $I$ of string variables $X$ united with an interpretation $I'$ of integer variables $N$,
-%%
-%then an $R$-encoding of $I \cup I'$ is any interpretation $e \cup I$ with  $e:V_R \cup \#V_R \cup \Simga_\epsilon$ 
-%such that $\encode R {(I\cup I')} \defeq \{e \cup I' \mid e\in \encode R(I)\}$ of interpretations of variables $V_R \cup \#V_R \cup N$.
-That is, the interpretation of string variables is encoded and the interpretation of integer variables is kept as is.
-%
-%
-%and we lift this notation to sets of interpretation in the standard manner, i.e., $\encode \dr (J) = \bigcup_{I \in J}\encode \dr (I)$ for a set of interpretations $J$.
-%
 The inductive argument needed in the correctness proof of the under-approximation then reads as
@@
 We note that the restriction of $\semof{\underf \dr \phi}$ to $V_\dr\cup V_{\#\dr}$ here is needed since $\underf \dr \phi$ will be constructed with some auxiliary variables.
-
-%\lh{do we want to discuss some sort of completeness? That is, every interpretation of every integer constraint is are covered by some flat restriction. ?}
-
-%In the further development, $\epsilon$ will mean $-1$ when working with arithmetic formulae constraining interpretations of character variables.
 
@@
 
-\paragraph{Synchronization of PAs}
+\subsubsection*{Synchronization of PAs}
 We will now discuss a construction of the \emph{synchronization formula} for two PAs $\pa$ and $\pa'$. 
@@
 
-\smallskip
-
 \item If $(q_1,v,q_2) \in T$, then for all states $q'\in Q'$, we have $((q_1,q'),(v,\epsilon),(q_2,q'))\in \syncT$.
-
-\smallskip
 
@@
 
-\paragraph{Concatenation of PFAs}
+\subsubsection*{Concatenation of PFAs}
 Concatenation of PFAs will be needed when flattening equality constraints.
@@
 
-%% After the set $\insc$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA.
-To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.
-%% 
-%% $$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$
-%% 
-%% 
-%% More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\outlf$. 
-%% 
-%% $$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
-%% 
-%% 
-%% \hide{The length of $x$ can be specified by the following formula.
-%% 
-%% $\begin{array}{ccc}
-%% 	(|x|&=& \#(v_0)+1 \wedge 0\leq v_1 \leq 9 \wedge v_2 = -1)\vee \\
-%% 	(|x|&=& \#(v_0)+2 \wedge 0\leq v_2 \leq 9 \wedge v_3 = -1)\vee \\
-%% 	& &\ldots\\
-%% 	(|x|&=& \#(v_0)+(m-1) \wedge 0\leq v_{m-1} \leq 9 \wedge v_m = -1)\vee\\
-%% 	(|x|&=& \#(v_0)+m \wedge 0\leq v_m \leq 9 )
-%% \end{array}$}
-
-%\subsection{Handling Equality Constraints Symbolically, old verion, not updated} \label{section:eq}
-%
-%We now describe the construction of $\underf R {\phi_e}$ for an equality constraint $\phi_e\defeq x_0\cdot x_1 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$.
-We first build two PFAs $\leftA$ and $\rightA$ that encode the left-hand side term and the right-hand side term of the equality constraint by concatenating the restrictions of the individual variables.
-%% Intuitively, this can be achieved by connecting the PFAs restricting the string variables with epsilon transitions. However, there are two technical issues. 
-%%First, our definition of PFA does not allow epsilon transition. %The second issue is more severe, 
-%Second,
-%some string variable might occur multiple times in an equality constraint, but the definition of PFA allows each character variable occurs in only one transition.
-We will need a way to force that all occurrences of the same string variable are assigned the same value.
-%
-%We circumvent the first problem by fresh character variables $v_{\epsilon_1},\ldots,v_{\epsilon_m}$, and forcing their value to be $\epsilon$ by adding the linear formula 
-%$$
-%\Psi_\epsilon \defeq \bigwedge_{1\leq i \leq m} v_{\epsilon_i} = -1
-%$$ % , to the output linear formulae $\phi_O$. 
-%Then we can connect the final state of $R(x_{i-1})$ and the initial state of $R(x_{i})$, $1\leq i \leq m$, with an ``epsilon" transition, i.e., one with the label $v_{\epsilon_i}$.
-%We use $V_\epsilon$ to denote the set of all variables used for ``epsilon" transitions.
-%
-%For the second issue, we rename the variables of $V_R$ on the transitions of PFAs for different occurrences of the same variable in one equality constraint.
-The renaming is done by adding a version number to the variable.
-Namely, we can rename $v_1$ to $v_1^{(0)}$, $v_1^{(1)}$, etc.
-In this case, $v_1$ is the \emph{original} variable and both $v_1^{(0)}$ and $v_1^{(1)}$ are \emph{version variables}.
-The set of all used version variables is denoted $\renvars$.
-%We will later define an arithmetic constraint $\Psi_{\mathit{rename}}$ to enforce that versions of the same variable are assigned the same value as the original. 
-%
-%
-%Here we give a concrete example.
-For the equality constraint $xy = yx$, assume that we restrict the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-In the construction of the PFA for $xy$ and $yx$ (Figure~\ref{fig:sfa} (c) and (d)), we rename the variables on the PFA of $X$ and $Y$ to some fresh variable for each different occurrence of $x$ and $y$ in $xy = yx$, connect the PFA after renaming with ``epsilon" transitions (those labeled $v_{\epsilon_0}$ and $v_{\epsilon_1}$), and add linear formulae $v_{\epsilon_0}=-1$ and $v_{\epsilon_1}=-1$ to the output linear formulae $\phi_O$.
-%
-%Now let $\leftA$ and $\rightA$ be the two PFAs obtained from the two sides of the equality constraint $\phi_e$, over character variables $\leftV$ and $\rightV$, respectively. 
-%The underapproximation formula for $\phi_e$ will be based on the synchronisation formula $\syncfof {\leftA} {\rightA}$ for $\leftA$ and $\rightA$ conjoined with $\Psi_\epsilon$.
-Recall that from Lemma~\ref{lemma:synccorrect}, each model of $\syncfof {\leftA} {\rightA}$ corresponds to a pair of words in $\semof{\leftA}$ and $\semof{\rightA}$.
-However, this does not directly correspond to a model of the equality constraint $\phi_e$.
-The reason is that different versions of the same string variable can be assigned different values in $\semof{\leftA}$ and $\semof{\rightA}$.
-We need to add an additional constraint to force all versions of the same variables have the same value and also occur the same number of times in the Parikh image.
-%%avoid this problem, we need to add the constraint $\Psi_{rename}$ that is defined below to $\Phi_O$ to ensure that all variables renamed from the same original variable are assigned the same value and are occurred equally often.
-%%$$ \Psi_{rename} \defeq
-%%\bigwedge_{v\in V_{x_1} \cup\ldots\cup V_{x_m} , v'\in R_v} v=v' \wedge \#v = \#v'
-%%$$
-%$$ \Psi_{\mathit{rename}} \defeq
-%\bigwedge_{v\in V_R,v^{(i)}\in\renvars} v=v^{(i)} \wedge \#v = \#v^{(i)}
-%$$
-%The underapproximation of $\phi_e$ is now constructed as
-%$$
-%\underf R {\phi_e} \defeq \Psi_\epsilon \land \Psi_{\mathit{rename}} \land \syncfof \leftA \rightA
-%$$
-%
-%\begin{lemma}\label{lemma:eqcorrect}
-%$\semof {\underf R {\phi_e}}_{V_R  \cup \#V_R} = \encode R (\semof{\phi_e})$.
-%\end{lemma}
-%
-%
-%%Here $R_v$ is the set of variables renamed from the the original variable $v$. 
-%%The correctness of this procedure is stated in Lemma~\ref{lemma:eqcorrect} below.
-In the lemma, each tuple of words $(w_1,\ldots, w_m) \in \semof{A_{x_1}}\times\ldots\times\semof{A_{x_m}}$ represents a model of the equality constraint.
-Each tuple $(w_1,\ldots, w_m)$ satisfies the condition that if $x_i$ and $x_j$ are the same variable, then $w_i$ and $w_j$ should be the same word.
-%%
-%%\begin{lemma}\label{lemma:eqcorrect}
-%%	$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \\
-%%	    \left\{\begin{array}{c|cl}
-%%			(I^1\cup\pim^1)\ \cup&w_1=\decode A_{x_1}(I^1\cup\pim^1) & \wedge \\
-%%			(I^2\cup\pim^2)\ \cup&w_2=\decode A_{x_2}(I^2\cup\pim^2) & \wedge \\
-%%			\ldots&\ldots\\
-%%%			(I^{m-1}\cup\pim^{m-1}) &\cup&w_{m-1}=\decode A_{x_{m-1}}(I^{m-1}\cup\pim^{m-1}) & \wedge \\
-%%			(I^m\cup\pim^m)      &w_m=\decode A_{x_m}(I^m\cup\pim^m) & \wedge \\
-%%			&w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m & \wedge \\
-%%			&\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j &  \\
-%%        \end{array}\right\}
-%%	$
-%%\end{lemma}
-%%
-%%(An alternative description)
-%%
-%%\begin{lemma}\label{lemma:eqcorrect} For all $w_1 \in \semof{A_{x_1}} \ldots w_m \in \semof{A_{x_m}}$ satisfying $\forall i,j \in [1,m]: x_i=x_j \Longrightarrow w_i=w_j$, we have 
-%%	
-%%	\begin{center}
-%%		$\exists (I^1\cup\pim^1)\cup\ldots\cup (I^m\cup\pim^m)$ in $\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} }$ s.t.
-$w_1=\decode A_{x_1}(I^1\cup\pim^1),\ldots,w_m=\decode A_{x_m}(I^m\cup\pim^m)$\\
-%%		iff\\
-%%		$w_1\cdot w_2 \cdots w_n = w_{n+1}\cdot w_{n+2} \cdots w_m$.
-%%	\end{center}
-%%\end{lemma}
-%%
-%%\lh{Assume that we were working with a domain restriction $R:[x_i]_1^m\rightarrow \text{PFAs}$.
-%%\begin{lemma}
-%%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_{x_1} \cup\ldots\cup V_{x_m}  \cup \#V_{x_1} \cup\ldots\cup \#V_{x_m} } = \encode R (\semof{\phi_e})$.
-%%\end{lemma}
-%%Also, we could denote by $V_R$ the varsiables $V_{x_1} \cup\ldots\cup V_{x_m}$ (these are the variables used by the domain restriction), 
-%%and use $\# V_R$, so the lemma becomes \\ 
-%%$\semof {\syncfof A {A'}  \wedge \Psi_{rename}}_{V_R \cup \# V_R} = \encode R (\semof{\phi_e})$.
-%%
-%%}
-%
-%
-%\hide{
-%Assume that $S_n=(Q,T,\cvarone,q_i,q_f)$ is the PFA of $x_1\cdot x_2 \cdots x_n$ and $S_m=(P,T',\cvartwo,p_i,p_f)$ is the PFA of $x_{n+1}\cdot x_{n+2} \cdots x_m$.
-Our next task is to find a model for $x_1\cdot x_2 \cdots x_n = x_{n+1}\cdot x_{n+2} \cdots x_m$ under the domain restriction specified by $S_n$ and $S_m$.
-%Note that $\cvarone \cap \cvartwo =\emptyset$, because all variables will be renamed to some fresh variable. 
-%
-%
-%This is equivalent to finding a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and a common interpretation $I$ such that 
-%\begin{enumerate}
-%	\item $I(w_n)=I(w_m)$
-%	\item $I$ assign to variants of the same variable the same value. For example, in Figure~\ref{fig:sfa} (c) and (d), $v_0^{(0)}$ and $v_0^{(1)}$ should be assigned the same value.
-%	\item different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
-For example, in Figure~\ref{fig:sfa} (c) and (d), $w_{xy}=v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $w_{yx}=v_0^{(1)}v_1^{(1)}v_0^{(1)}v_1^{(1)}$ is a pair of symbolic strings satisfying this condition.
-The number of occurrences of $v_i^{(0)}$ is the same to $v_i^{(1)}$ for $i\in[0,1]$ in the concatenation $w_{xy}\cdot w_{yx}$.
-%	But the pair $v_0^{(0)}v_1^{(0)}v_0^{(0)}v_1^{(0)}$ and $v_2^{(0)}v_3^{(0)}v_2^{(0)}v_3^{(0)}$ does not satisfy the condition. Observe that $v_0^{(0)}$ occurs twice, but $v_0^{(1)}$ is not there.
-%\end{enumerate}
-%
-%In order to find such a pair of symbolic strings $(w_n,w_m) \in L(S_n)\times L(S_m)$ and an interpretation $I$, we first build a ``product" automaton of $S_n$ and $S_m$ and then add some additional linear arithmetic constraints to enforce the above conditions.
-%
-%Such product automaton uses $Q\times P$ as the set of states and 
-%%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
-%$\cvarone\times\cvartwo$
-%as the alphabet.
-If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
-%
-%More precisely, the product automaton is a tuple $\syncof A B = (Q\times P, \syncT, (\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} ), (q_i,p_i),(q_f,p_f))$, where the transition relation $\syncT$ is the minimal set satisfying the following.
-%
-%\begin{itemize}
-%\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in \syncT$.
-%\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in \syncT$.
-%\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in \syncT$.
-%\end{itemize}	
-%The first two cases correspond to the situation when the character variable $v_i^{(j)}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
-%
-%For example, in the product automaton $A_{xy=yx}$ corresponds to $xy=yx$, we have the following transitions
-%\begin{itemize}
-%	\item $((q_0,p_0), (v_0^{(0)},\epsilon),(q_1,p_0))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$.
-%	\item $((q_0,p_0), (\epsilon,\epsilon),(q_0,q_0))$, because $(p_0,\epsilon,q_0)$ is a transition of $A_{yx}$.
-%	\item $((q_0,p_0), (v_0^{(0)},v_2^{(1)}),(q_1,q_1))$, because $(q_0,v_0^{(0)},q_1)$ is a transition of $A_{xy}$ and $(p_0,v_2^{(1)},p_1)$ is a transition of $A_{yx}$.
-%\end{itemize}
-%
-%Recall that for flat automata, the number of occurrences of each symbol uniquely characterizes an accepting string (Section~\ref{section:sfa}) and for any finite automaton we can construct a Presburger formula characterizing its Parikh image (Section~\ref{section:preliminary}).
-For a product automaton $A$ computed from the previous step, we compute a Presburger formula $\phi(A)$ over the set of variables $\{\#{(v_i^{(j)},v_{i'}^{(j')})}\mid (v_i^{(j)},v_{i'}^{(j')}) \in \cvarone \times \cvartwo\}$ characterizing the Parikh image of $A$.
-We use $\#(v_i)$ and $\#(v_i^{(j)})$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.
-The following formulae establish the relation of the number of occurrences of symbols between the PFAs and the product automaton.
-%\begin{enumerate}
-%	\item for all $v_i^{(j)} \in \cvarone$, $\#(v_i^{(j)}) = \sum_{v \in {\cvartwo \cup \{\epsilon\}}} \#{(v_i^{j},v)}$   
-%	\item for all $v_i^{(j)} \in \cvartwo$, $\#(v_i^{(j)}) = \sum_{v \in {\cvarone \cup \{\epsilon\}}} \#{(v,v_i^{j})}$ 
-%\end{enumerate}
-%
-%Then we add the following linear constraints to enforce  condition 1.
-and 2.
-required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$).
-%\begin{enumerate}
-%	\item for all $v_i^{(j)}\in \cvarone$ and $v_{i'}^{(j')}\in \cvartwo$, $\#{(v_i^{(j)},v_{i'}^{(j')})}>0 \rightarrow (v_i=v_{i'})$,\lh{typo?} 
-%	\item for all $v_i^{(j)}\in \cvarone$, $\#{(v_i^{(j)},\epsilon)}>0 \rightarrow (v_i=\epsilon)$, and
-%	\item for all $v_{i'}^{(j')}\in \cvartwo$,$\#{(\epsilon,v_{i'}^{(j')})}>0 \rightarrow (v_{i'}=\epsilon)$.
-%\end{enumerate}
-%We then add the linear constraints $\#(v_i) = \#(v_i^{(j)})$, for all $v_i\in \cvar$ and all different version numbers $j$ for $v_i$, to enforce condition 3, which says different versions of the same variable should occurs equally often in $w_n\cdot w_m$.
-%
-%From the model $M$ of the linear constraints, we can obtain $w_n$, $w_m$, and $I$.
-The interpretation $I$ is defined as $I(v)=M(v)$ for all $v\in (\cvarone \cup \cvartwo)$.
-The symbolic words $w_n$ and $w_m$ can be obtained by traverse the PFAs following the number of occurrences of each character variables.
-%More specifically, assume that the PFA $S_n$ is the one in Figure~\ref{fig:sfa_def}, then $$w_n = (v_0^0v_0^1v_0^2v_0^3)^{\#(v_0^0)}v_0(v_1^0v_1^1v_1^2)^{\#(v_1^0)}v_1\ldots(v_m^0v_m^1v_m^2v_m^3)^{\#(v_m^0)}$$
-%Note that $\#(v_0^0)=\#(v_0^1)=\#(v_0^2)=\#(v_0^3)$, so we just use $\#(v_0^0)$ to denote the number of times of first loop traversal.
-One can construct $w_m$ in a similar way.
-Using the same approach, one can derive the assignment to variables in $\vars$ using the corresponding count and values of variables in $\cvar$.
-%
-%
-%
-%
-%
-%
-%
-%}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\paragraph{PFA that allows efficient string-number conversion: } 
-%Now we know that it is unlikely to use arbitrary PFA and gain efficient solving procedure, due to the requirement to solve exponential integer constraints.
-The cause of the problem is that each loop in the PFA creates an exponential component in the constraint.
-%An immediate idea would be that maybe we can some pick some specific PFA that allow more efficient constraint solving. 
+\subsubsection*{PFA that allows efficient string-number conversion: } 
 We will now discuss the special form of $\dr(x)$, called \emph{numeric PFA}, which we choose for string variables appearing in string-integer constraints and that leads to efficient under-approximation technique.

### 2020-03-29 final-version/evaluation.tex
fixing the comments of reviewers A & D

--- 2020-03-24 evaluation.tex
@@
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
+\changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
 We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.

### 2020-03-30 final-version/evaluation.tex
update to address the comments of Reviewer B (and the PASS question by Reviewer C)

@@
 
-We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We compare {\tool} \changed{(\texttt{9831ad0cd})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
@@
 \begin{table}[h]
+\changed{
 \centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
+\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
+\scalebox{0.85}{
+\begin{tabular}{|l r | r r r r |}
+\hline
+\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
+\multirow{6}{*}{PyEx}		& SAT      & 19166& 19899& 16331&  3037 \\
+							& UNSAT    &  3877&  3848&  3831&  3830 \\
+							& UNKNOWN  &     0&     0&     0&     7 \\
+							& TIMEOUT  &  2378&  1674&  5259& 16872 \\
+							& ERROR    &     0&     0&     0&  1675 \\
+							& INCORRECT&     1&     0&     0&    14 \\ \hline
+\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
+							& UNSAT    &   286&   214&   100&   111 \\
+							& UNKNOWN  &     0&     0&     0&   345 \\
+							& TIMEOUT  &   188&   335&   487&    89 \\
+							& ERROR    &     0&     0&     0&    20 \\
+							& INCORRECT&     0&     0&     0&     0 \\ \hline
+\multirow{6}{*}{LeetCode}	& SAT      &   827&   865&   881&   661 \\
+							& UNSAT    &  1784&  1785&  1785&  1780 \\
+							& UNKNOWN  &     0&     0&     0&   122 \\
+							& TIMEOUT  &    55&    16&     0&    90 \\
+							& ERROR    &     0&     0&     0&    13 \\
+							& INCORRECT&     0&     0&     0&     0 \\ \hline
+\multirow{6}{*}{StringFuzz}	& SAT      &   478&   704&   267&   505 \\
+							& UNSAT    &   283&   245&   188&   192 \\
+							& UNKNOWN  &     0&     0&     0&     4 \\
+							& TIMEOUT  &   304&   116&   610&   364 \\
+							& ERROR    &     0&     0&     0&     0 \\
+							& INCORRECT&     0&     0&     0&     0 \\\hline
+\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
+							& UNSAT    &   818&   818&   808&   774 \\
+							& UNKNOWN  &     0&     0&     0&     4 \\
+							& TIMEOUT  &     4&     6&    15&    38 \\
+							& ERROR    &     0&     0&     0&     9 \\
+							& INCORRECT&     0&     0&     0&     0 \\ \hline
+\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    11&     8&     5&    16 \\
+							& UNSAT    &  1027&  1025&  1022&   957 \\
+							& UNKNOWN  &     0&     0&     0&     3 \\
+							& TIMEOUT  &     7&    12&    18&    58 \\
+							& ERROR    &     0&     0&     0&     8 \\
+							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
+\multirow{6}{*}{Total} 		& SAT      & 20621& 21538& 17509&  4262 \\
+							& UNSAT    &  8075&  7935&  7734&  7644 \\
+							& UNKNOWN  &     0&     0&     0&   485 \\
+							& TIMEOUT  &  2936&  2159&  6389& 17511 \\
+							& ERROR    &     0&     0&     0&  1725 \\
+							& INCORRECT&     1&     0&     0&    28 \\\hline
+\end{tabular}}
+\label{table:base_benchmark}}
+\end{table}
+
+\begin{table}[h]
+\changed{
+\centering
+\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
 \scalebox{0.8}{
@@
 \hline
-\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
+\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
 \multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
@@
 \label{table:str_int_benchmark}
-\end{table}
-
-\begin{table}[h]
-\centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
-\scalebox{0.8}{
-\begin{tabular}{|l r | r r r r|}
-\hline
-\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
-\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
-								& UNSAT    & 16393& 15726& 16115& 15396 \\
-								& UNKNOWN  &     0&     0&     0&   623 \\
-								& TIMEOUT  &   142&  1480&   914&  2337 \\
-								& ERROR    &     0&     0&     0&   332 \\
-								& INCORRECT&     1&     0&     0&   108 \\ \hline 
-\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
-								& UNSAT    &   720&   667&   724&   644 \\
-								& UNKNOWN  &     0&     0&     0&    45 \\
-								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
-								& ERROR    &     0&     0&     0&    41 \\
-								& INCORRECT&     0&     0&     0&     2 \\ \hline
-\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
-								& UNSAT    &     0&     0&     0&     0 \\
-								& UNKNOWN  &     0&     9&     0&     0 \\
-								& TIMEOUT  &     0&     8&     4&    10 \\
-								& ERROR    &     0&     0&     0&     6 \\
-								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
-\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
-								& UNSAT    & 17113& 16393& 16839& 16040 \\
-								& UNKNOWN  &     0&     0&     0&   668 \\
-								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
-								& ERROR    &     0&     0&     0&   373 \\
-								& INCORRECT&     1&     0&     0&   110 \\ \hline
-\end{tabular}}
-\label{table:str_int_benchmark}
+}
 \end{table}
@@
 
-We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
+%We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
 Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3Str3 got almost the same number of failed cases.
@@
 \begin{table}[h]
+\changed{
+
 \centering
 \caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
-\scalebox{0.9}{
+\scalebox{0.8}{
 \begin{tabular}{| c | c c c c|}
@@
 \end{tabular}}
-\label{table:checkLuhn}
+\label{table:checkLuhn}}
 \end{table}
@@
 \hline
-\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
@@
 			\hline
-			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
+			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3Str3 \\ \hline
 			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
@@
 \hline
-\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
@@
 \hline
-\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
+\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
 \multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
@@
 \hline
-\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3-str3 & {\tool} & CVC4  &    Z3  & Z3-str3 \\ \hline
+\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
 \multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 

### 2020-03-30 final-version/main.tex
fixing the comments of reviewers A & D
deleting files

@@
 
-\usepackage{flushend} 
+\usepackage{balance}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 However, the formula is satisfiable when $x=``00010"$.
-Observe that $\sti{``00010"}=10$.
+Observe that $\sti{``00010"}=10$ \changed{since PFAs accept  numeric words with least significant bit first}.
 The key is that even for a bounded integer, the corresponding numeral can be of an unbounded length with arbitrarily many trailing `$0$'s at the front.
@@
 	\label{fig:sfa_its}
+	\Description{Parametric flat automata  for string-number conversion constraints}
 \end{figure}
 
-%Such PFA handles bounded integers (e.g., 10-digits or 64-bits) precisely and under-approximate the possible values of unbounded integers.
-It works very efficiently because we just need to use linear constraints to characterize the relation between $x$ and $n$.
 Numeric PFA with these restrictions would satisfy our primary objective, that is, they would induce linear formulae and would ``easily" and completely cover all numerals.
@@
 
-%
-%
-%$$
-%\mathsf{toNumber(k)}\defeq (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
-%$$
-%
-%
-%
-%
-%$$\Psi_{\mathsf{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
-%where $ $
-%To explain this encoding, we first define two macro function:
-%
-%$$\begin{array}{rl}
-%\mathsf{epsilonAfter(k)}\defeq& (0\leq v_1,\ldots, v_k\leq 9) \wedge\\
-%&v_{k+1}=\ldots =v_m = -1\\
-%\mathsf{toNumber(k)}\defeq& (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
-%\end{array}
-%$$
-
-%The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$.
-Recall that we use $-1$ to represent $\epsilon$.
-The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
-\yfc{say shifting $\epsilon$ to the right will not change the language}
-
-%The condition that when $x$ is ``not a number" is specified by the following formula.
-%
-%$$
-%\Psi_{\mathit{NaN}} \defeq  \bigvee_{i\in [1,m]} v_i>9$$
-%
-%Then we can specify the relation between $n$ and the character variables as follows:
-%$$\Psi_n\defeq  (n=-1 \wedge \Psi_{\mathit{NaN}})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
-%It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
-%$$
-%\underf R {\psi_s} \defeq \Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {R(x)} 
-%$$
-%To formulate the correctness lemma similar to Lemmas~\ref{lemma:memcorrect} and \ref{lemma:eqcorrect}, we need to consider a modified semantics of $R(x)$.
-%Namely, we assume that $\semof{R(x)}$ is returns $\decode A(\parikhof{R(x)} \land )$
-
-%We add $\Psi_n$ to $\Phi_O$.
-%
-%
-%
-%The correctness of this procedure is expressed in Lemma~\ref{lemma:sticorrect} below. We separate the lemmas to cases where $n\neq -1$ and $n=-1$. 
-%
-%
-%\newcommand\restrict[1]{\raisebox{-.5ex}{$\big|$}_{#1}}
-
-%\begin{lemma}\label{lemma:sticorrect}
-%	
-%	The interpretation $(I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} $ if and only if 
-%	\begin{center}
-%	 $\left(\begin{array}{c} 
-%	 I_n(n)= \sti{\decode {A_x}(I\cup\pim)} \ \wedge \\
-%	 I(v_i)=-1 \wedge i<j \Longrightarrow  I(v_j)=-1
-%	 \end{array}\right)$\\ or\\
-%	 $\left(\begin{array}{c} 
-%	 I_n(n)= -1\ \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+
-%	 \end{array}\right)$
-%	\end{center}
-%
-%\end{lemma}
-%\yfc{sorry still ugly, the shifting of epsilon makes it a mess here}
-%(An alternative description)
-%\begin{lemma}\label{lemma:sticorrect}
-%	For all $w \in \semof{A_{x}}$ and $c \in \mathbb{Z}$, we have 
-%	\begin{center}
-%		$\exists (I\cup\pim \cup I_n)  \in \semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}}$ s.t. $w=\decode {A_x}(I\cup\pim)$ and $I_n(n)=c$\\
-%		iff\\
-%		$c= \sti{w}$.
-%	\end{center}
-%	
-%\end{lemma}
-%\hide{
-%\begin{lemma}\label{lemma:sticorrect_pos}
-%	$\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \{(I\cup\pim \cup I_n) \mid  I_n(n)= \sti{\decode {A_x}(I\cup\pim)}\} $. 
-%\end{lemma}
-%In this case, $x$ encodes a number. The lemma says when the models we add to $\Phi_O$ represents a word in $\semof{A_x}$ whose integer value is exactly the model for $n$.
-%
-%\begin{lemma}\label{lemma:sticorrect_neg}
-%	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
-%	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \not\in [0,9]^+  \}$
-%\end{lemma}
-%
-%In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.}
-%
-%\lh{
-%\begin{lemma}
-%$
-%\semof {\Psi_n \wedge \Psi_{v_0}\wedge \parikhfof {A_x} }_{V_x \cup \#V_x \cup \{n\}} = \encode  R(\semof{\phi_s})
-%$
-%\end{lemma}
-%The $n$ must somehow be handled properly by $\encode  R(\phi_s)$, I did not have time to think about it yet.
-%}
-
-% \section{Evaluation}
-% \label{section:evaluation}
-% \todo{copy a few tables from our test site to here}
-
 \input{evaluation}
@@
 
-The most relevant work to ours is~\cite{abdulla2018trau} who proposed to project the solution space of variables to a generalization of flat automata.
-The main difference is that our approach works fully symbolically, which is enabled by to the ideas of using character variables and hence PFAs.
-The use of character variables allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.
-Moreover, the approach of~\cite{abdulla2018trau} is exponential to the alphabet size (we call this the alphabet-explosion problem in the introduction), and hence in the implementation, usually requires heuristics to prune out unnecessary symbols.
+\changed{
+The most relevant work to ours is the FA-based approach~\cite{abdulla2018trau} that projects the solution space of variables to a generalization of flat automata.
+The main difference is that our approach works fully symbolically, which is enabled by to the ideas of using integer variables as characters and hence PFAs.
+The use of integer variables as characters allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.
+
+The straightforward extension of existing FA based techniques boils down to solving the satisfiability problem of integer polynomial-exponential constraints, whose decidability is still open (Section~\ref{section:s2i}).
+
+In principle, we can also extend FA-based solvers to support string-number conversion, but PFA are much more efficient.
+Extending FA-based approach to support string-number conversion would require multiple if-then-else statements (e.g., saying that if a transition labeled `0' is taken, then the corresponding number is $0$), which introduces a significant amount of additional predicates that the DPLL engine needs to decide their value.
+We have confirmed this in our preliminary experiment.}
+
+\changed{
+PASS\cite{goudong2013pass} uses quantified formulae over arrays with symbolic length to encode string constraints, and a specialized quantifier elimination to solve them.
+Though it differs from our approach significantly and handling the quantification is expensive, PASS is indeed similar in how finite automata and string-number conversion constraints are translated to formulae.
+But our translation is in general more efficient because it uses only linear arithmetics.
+In contrast, PASS translates string constraints to formulae with quantifier and array predicates.
+We did not compare with PASS empirically.
+The authors informed us that PASS is no longer maintained and is not open-source.
+}
 
@@
 We  believe such integration  is feasible.
-%have discussed this possibility of such integration with some of its team members, and 
 We are also planning to merge  {\tool}  with the main branch of the Z3 solver.
@@
 \begin{acks}
-This research was  partially supported by the  Swedish Foundation for Strategic Research.
+This research was  partially supported by the  Swedish Foundation for Strategic Research and Ministry of Science and Technology Project,Taiwan (no. 106-2221-E-001 -009 -MY3).
 \end{acks}
 
+ \balance
 \bibliographystyle{ACM-Reference-Format}

### 2020-03-30 final-version/evaluation.tex
little things in final cersion

@@
 
-	\item \changed{ LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check if a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check if an input string is an abbreviation of another input string, and decode a sequence of digits to strings according to a given mapping.}
+	\item \changed{ LeetCode is from running PyEx over a sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check whether a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check whether an input string is an abbreviation of another input string, and convert a sequence of digits to a string according to a given mapping.}
 

### 2020-03-30 final-version/main.tex
little things in final cersion

@@
 However, the formula is satisfiable when $x=``00010"$.
-Observe that $\sti{``00010"}=10$ \changed{since PFAs accept  numeric words with least significant bit first}.
+Observe that $\sti{``00010"}=10$ \changed{since PFAs accept  numerals with the least significant bit first}.
 The key is that even for a bounded integer, the corresponding numeral can be of an unbounded length with arbitrarily many trailing `$0$'s at the front.
@@
 The most relevant work to ours is the FA-based approach~\cite{abdulla2018trau} that projects the solution space of variables to a generalization of flat automata.
-The main difference is that our approach works fully symbolically, which is enabled by to the ideas of using integer variables as characters and hence PFAs.
-The use of integer variables as characters allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.
-
+The main difference is that our approach works fully symbolically, which is enabled through using integer variables as characters and hence PFAs.
+The use of integer variables as characters allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly converted to numbers in a linear formula.
+
+%HERE
 The straightforward extension of existing FA based techniques boils down to solving the satisfiability problem of integer polynomial-exponential constraints, whose decidability is still open (Section~\ref{section:s2i}).
 
-In principle, we can also extend FA-based solvers to support string-number conversion, but PFA are much more efficient.
-Extending FA-based approach to support string-number conversion would require multiple if-then-else statements (e.g., saying that if a transition labeled `0' is taken, then the corresponding number is $0$), which introduces a significant amount of additional predicates that the DPLL engine needs to decide their value.
+In principle, FA-based solvers can be extended to support string-number conversion too, but PFA are much more efficient.
+Extending FA-based approach would require multiple if-then-else statements (e.g., saying that if a transition labeled `0' is taken, then the corresponding number is $0$), which introduces a significant amount of additional predicates that the DPLL engine needs to evaluate.
 We have confirmed this in our preliminary experiment.}

### 2020-03-30 final-version/main.tex
minor

@@
 \begin{acks}
-This research was  partially supported by the  Swedish Foundation for Strategic Research and Ministry of Science and Technology Project,Taiwan (no. 106-2221-E-001 -009 -MY3).
+This research was  partially supported by the  Swedish Foundation for Strategic Research, Ministry of Science and Technology Project, Taiwan (no.
+106-2221-E-001 -009 -MY3), and Ministry of Education, Youth and Sports of Czech Republic (no.
+LL1908).
 \end{acks}

### 2020-03-30 final-version/evaluation.tex
little changes in the text

--- 2020-03-30 final-version/evaluation.tex
@@
 Secondly, it makes it possible to solve not only formulae over string constraints but also combinations of string constraints with other theories that Z3 supports.
-Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and eliminate the need to have our own parser for input formulae.
+Furthermore, this approach allows us to more effectively handle the arithmetic constraints that are generated by the under-approximation module and, lastly, it eliminates the need to have our own parser.
 
 In {\tool}, we use the following PFA selection strategy.
-First, we use \emph{numeric PFAs} for string variables appearing in string-number conversion and \emph{standard PFAs} for others.
-Then we select size $m$ for numeric PFAs and $p$ loops of size $q$ for standard PFAs.
-Initially, we set $(m,p,q)=(5,2,q)$, where $q$ is dynamic and achieved from our internal static analysis.
-We double $m$, increase $p$ and $q$ by one if more precise refinement is required.
+We use \emph{numeric PFAs} for string variables appearing in string-number conversion and \emph{standard PFAs} for others.
+We select a size $m$ for numeric PFAs, a number $p$ of their loops, and the length $q$ of the loops.
+Initially, we set $(m,p,q)=(5,2,q)$ where $q$ is dynamic and obtained from our internal static analysis.
+We double $m$ and increase $p$ and $q$ by one if refinement is required.
 We set an upper bound for each parameter and report UNKNOWN if a solution cannot be found within the bound.
 
-Our over-approximation module uses also some heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
-For instance, assume in some case, we could derive that the value of $n=12$ from some integer constraints.
-Then, we could further derive the value of $x$ is in the regular language $(0^*12)$.
+Our over-approximation module also uses heuristics to derive the constant value of any side of the constraint $n=\sti{x}$ to refine the over-approximation.
+For instance, assume we can derive that $n=12$ from some integer constraints.
+Then we can derive the value of $x$ belongs to the regular language $(0^*12)$.
+%HERE
 
-The way our theory solver and Z3 interacts is almost standard.
-Every time when Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it is SAT or UNSAT using the aforementioned procedure.
-For under-approximation, every time when a corresponding linear formula is created, we attach the current value of $m$, $p$, $q$ with the formula, and then push it to Z3 core.
+%more or less standard
+The way our theory solver and Z3 interact is almost standard.
+When Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it is SAT or UNSAT using the procedure discuss in this paper.
+For under-approximation, whenever a corresponding linear formula is created, we attach the current value of $m$, $p$, $q$ to the formula, and then push it to Z3 core.
 If our theory solver reports UNKNOWN, Z3 remembers it in a global flag \textsf{incomplete} and either tries another solution branch, or the same solution branch with different value of $m$, $p$, $q$.
@@
 Those benchmarks do not involve string-number conversion function.
-In the second set of experiments, we compare {\tool} with other tools on new suites focusing on string-number conversion.
+In the second set of experiments, we compare {\tool} with the other tools on new suites focusing on string-number conversion.
 Our goals of experiments are the following:
@@
 \begin{itemize}
-	\item {\tool} performs as good as, or better than other tools in solving the  satisfiability problems of basic string constraints.
+	\item {\tool} performs as good as or better than the other tools in solving the  satisfiability problems of basic string constraints.
 
@@
 
-	\item {\tool} performs significantly better than other tools in solving the satisfiability problems on string-number conversion benchmark, and this shows  the efficiency of PFA in general and \emph{numeric} PFA in particular.
+	\item {\tool} performs significantly better than the other tools in solving the satisfiability problems on string-number conversion benchmark, and this shows  the efficiency of PFA in general and \emph{numeric} PFA in particular.
 \end{itemize}
@@
 \begin{itemize}
-	\item PyEx~\cite{pyex} is from running the symbolic executor PyEx over some Python packages.
+	\item PyEx~\cite{pyex} comes from running the symbolic executor PyEx over some Python packages.
 
@@
 
-	\item \changed{ LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check if a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check if an input string is an abbreviation of another input string, and decode a sequence of digits to strings according to a given mapping.}
+	\item \changed{ LeetCode comes from running PyEx over a sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check whether a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check whether an input string is an abbreviation of another input string, and convert a sequence of digits to a string according to a given mapping.}
 
@@
 
-	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated from the fuzz testing tool of the same name.
+	\item StringFuzz~\cite{blotsky2018stringfuzz}  is generated by the fuzz testing tool of the same name.
 
@@
 We ran it on several examples collected from the LeetCode platform and from Python core libraries, which involve diverse usages of string-number conversion in Python such as parsing date-time, verifying and restoring IP addresses from strings, etc.
-We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulation).
+We also have examples that encode execution paths of some JavaScript programs (the Luhn algorithm and some array manipulations).
 
@@
 We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
-Occasionally, two of them report inconsistent (one SAT and one UNSAT) answers to the same test.
-To decide which solver reports the incorrect answer, we developed a validator, which takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtain a modified test, and re-evaluates the modified test by multiple solvers.
+Occasionally, two of them report inconsistent  answers (one SAT and one UNSAT).
+To decide which solver is right, we developed a validator.
+It takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtain a modified test, and re-evaluates the modified test by multiple solvers.
 If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results.
@@
 Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
-Rows with heading \texttt{UNKNOWN}, \texttt{TIMEOUT}, or \texttt{ERROR} indicate the number of instances the solver fails to return an answer.
-\texttt{INCORRECT} shows the number of cases that a tool gives wrong answer\footnote{A correct answer is decided by mainly CVC4, then the consensus of {\tool} or Z3.}.
+Rows with heading \texttt{UNKNOWN}, \texttt{TIMEOUT}, or \texttt{ERROR} indicate the number of instances for which the solver fails to return an answer.
+\texttt{INCORRECT} shows the number of cases where the tool gives a wrong answer\footnote{A correct answer is decided by mainly CVC4, then the consensus of {\tool} or Z3.}.
 
@@
 
-From Table~\ref{table:base_benchmark}, we can see that the performance of {\tool} is as good as the most competitive tools such as CVC4 and Z3 on basic string constraints.
+From Table~\ref{table:base_benchmark}, we can see that the performance of {\tool} is as good as that of the most competitive tools such as CVC4 and Z3 on basic string constraints.
 In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases.
-If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant difference between {\tool} and the top-ranked tool on the SAT cases.
-But we believe this is not very important because both these two benchmarks are artificial, either hand-crafted or randomly generated.
-The more critical ones are those come from program analysis, in which {\tool} has comparable performance to the best tool.
+On the APLAS and StringFuzz benchmarks that are SAT, {\tool} does not perfomr as well as the best performing tool.
+We however do not consider this crucial because both of these benchmarks are artificial, either hand-crafted or randomly generated.
+On the most important benchmarks, those that come from program analysis, {\tool} is comparable to the best performing tool.
 
 From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools.
-The total number of failed cases is only a half to Z3, which is ranked the 2nd.
+It fails on twice less cases then Z3, which is ranked the 2nd.
 In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number.
-We generated 2028 tests from this function, and among them around 1000 cases  are too difficult for all solvers.
-If we exclude results on this function, then {\tool} has only $218$ failed cases in total.
-This is significantly better than the 2nd place tool Z3, which fails $942$ cases in total.
+From around 2028 tests generated from this function, around 1000 tests are too difficult for all solvers.
+If we exclude the 2028 tests generated from this function, then {\tool} has only $218$ failed cases in total.
+This is significantly better than the 2nd place tool Z3, which fails on $942$ cases in total.
 
@@
 
-For further details of the experiment, we have encoded the checkLuhn algorithm introduced in Section~\ref{section:introduction} for cases of 2 to 12 loops (digits).
-We ran these tests additionally to the experiments above with the timeout set to 120s.
-The result is summarized in Table~\ref{table:checkLuhn}.
+As an addition experiment, we have encoded the checkLuhn algorithm introduced in Section~\ref{section:introduction} for the cases with 2 to 12 loops (digits). We ran these tests 
+%additionally to the experiments above 
+with the timeout set to 120s. The result is summarized in Table~\ref{table:checkLuhn}.
 In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3Str3 could not solve any of these problems (either timeout or UNKNOWN).
-However, Z3 can still solve 7 out of the 11 problems and the problems got timeout are cases for 4, 5, 7, and 9 loops.
-The behavior of Z3 is not unexpected, since all the problems are satisfiable and sometimes the solver are lucky and went into a branch with a correct model very quickly.
+However, Z3 can still solve 7 out of the 11 problems, while timeouting in the cases with 4, 5, 7, and 9 loops.
+The behavior of Z3 is not entirely unexpected.
+All the problems are satisfiable and the solver may be lucky to guess the solution quickly.
+% branch with a correct model quickly.
 
@@
 The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}.
-The benchmark includes a total of 600 hand-drafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.
+The benchmark includes a total of 600 hand-crafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.
 

### 2020-03-30 final-version/main.tex
little changes in the text

--- 2020-03-30 final-version/main.tex
@@
 
-%HERE
-The straightforward extension of existing FA based techniques boils down to solving the satisfiability problem of integer polynomial-exponential constraints, whose decidability is still open (Section~\ref{section:s2i}).
+%%%%This sounds like contradicting the next paragraph. I think it is not necessary here, it is not a related work, so I am just commenting out.
+%The straightforward extension of existing FA based techniques boils down to solving the satisfiability problem of integer polynomial-exponential constraints, whose decidability is still open (Section~\ref{section:s2i}).
 
@@
 \changed{
-PASS\cite{goudong2013pass} uses quantified formulae over arrays with symbolic length to encode string constraints, and a specialized quantifier elimination to solve them.
+PASS \cite{goudong2013pass} uses quantified formulae over arrays with symbolic length to encode string constraints, and a specialized quantifier elimination to solve them.
 Though it differs from our approach significantly and handling the quantification is expensive, PASS is indeed similar in how finite automata and string-number conversion constraints are translated to formulae.
-But our translation is in general more efficient because it uses only linear arithmetics.
+Our translation is in general more efficient because it uses only linear arithmetics.
 In contrast, PASS translates string constraints to formulae with quantifier and array predicates.
@@
 \begin{acks}
-This research was  partially supported by the  Swedish Foundation for Strategic Research and Ministry of Science and Technology Project,Taiwan (no. 106-2221-E-001 -009 -MY3).
+This research was  partially supported by the  Swedish Foundation for Strategic Research and Ministry of Science and Technology Project,Taiwan (no.
+106-2221-E-001 -009 -MY3), Ministry of Education, Youth and Sports of Czech Republic (no.
+LL1908).
 \end{acks}

### 2020-03-30 final-version/main.tex

@@
 \begin{acks}
-This research was  partially supported by the  Swedish Foundation for Strategic Research and Ministry of Science and Technology Project,Taiwan (no.
-106-2221-E-001 -009 -MY3), Ministry of Education, Youth and Sports of Czech Republic (no.
+This research was  partially supported by the  Swedish Foundation for Strategic Research, Ministry of Science and Technology Project, Taiwan (no.
+106-2221-E-001 -009 -MY3), and Ministry of Education, Youth and Sports of Czech Republic (no.
 LL1908).

### 2020-03-30 final-version/evaluation.tex
small fixes related to rev C and few other minor things

@@
 The way our theory solver and Z3 interact is almost standard.
-When Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it is SAT or UNSAT using the procedure discuss in this paper.
+When Z3 asks our theory solver a string constraint satisfiability problem, our solver tries to prove it is SAT or UNSAT using the procedure discussed in this paper.
 For under-approximation, whenever a corresponding linear formula is created, we attach the current value of $m$, $p$, $q$ to the formula, and then push it to Z3 core.

### 2020-03-30 final-version/main.tex
small fixes related to rev C and few other minor things

@@
 Assume that we project the domains of $x$ and $y$ to the PFA in Figure~\ref{fig:sfa} (a) and (b), respectively.
-The variables $v_1$, $v_2$, $v_3$, $v_4$ in the figure are \emph{character} variables.
-Thus, $v_1$, $v_2$, $v_3$, $v_4$ are also integer variables.
-For example, from  $ y \in (12)^+$, we may derive $v_2=1$ and $v_3=2$.
-
-The linear formula produced after the domain restriction will be over variables $v_1$, $v_2$, $v_3$, $v_4$, as well as the number of occurrences of each character variable $\#v_1$, $\#v_2$, $\#v_3$, $\#v_4$.
+The variables $v_0$, $v_1$, $v_2$, $v_3$ in the figure are \emph{character} variables.
+Thus, $v_0$, $v_1$, $v_2$, $v_3$ are also integer variables.
+For example, from  $ y \in (12)^+$, we may derive $v_1=1$ and $v_2=2$.
+
+The linear formula produced after the domain restriction will be over variables $v_0$, $v_1$, $v_2$, $v_3$, as well as the number of occurrences of each character variable $\#v_0$, $\#v_1$, $\#v_2$, $\#v_3$.
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_1,v_2,v_3,v_4,\#v_1,\#v_2,\#v_3,\#v_4) \rightarrow (1,2,1,2,1,1,2,2)$.%
+For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (1,2,1,2,1,1,2,2)$.%
 \footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ to denote the function $\{x_1 \mapsto n_1,\ldots, x_k\mapsto n_k\}$.}
-The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_1 = \#v_2 = 1$), which is $v_1v_2$.
-Under the assignment $v_1=1$ and $v_2=2$, we obtain $x=``12"$.
+The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_0 = \#v_1 = 1$), which is $v_0v_1$.
+Under the assignment $v_0=1$ and $v_1=2$, we obtain $x=``12"$.
 
@@
 
-The \emph{Parikh image} of a word $w\in \Sigma^*$ maps each \emph{Parikh variable} $\#a$, with $a \in \Sigma$ is a character, to the number of occurrences of $a$ in $w$.
+The \emph{Parikh image} of a word $w\in \Sigma^*$ maps each \emph{Parikh variable} $\#a$, where $a \in \Sigma$ is a character, to the number of occurrences of $a$ in $w$.
 Formally, given a set $S$, let $\pvarsof S$ denote the set of Parikh variables $\{\#s \mid s\in S\}$. 
-The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$. 
+The Parikh image of $w$ is a function $\parikhof w:\pvarsof \Sigma \rightarrow \nat$ such that $\parikhof w (\#a) = |w|_a$ for each $a\in\Sigma$.
 The Parikh image of a language $L$ is defined as follows $\parikhof L = \{\parikhof w \mid w \in L\}$.
@@
 
-Assume that $\vars$ ia a set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ a set of \emph{integer variables} ranging over $\mathbb{Z}$.
+Assume that $\vars$ is a set of \emph{string variables} ranging over $\Sigma^*$ and $\varn$ a set of \emph{integer variables} ranging over $\mathbb{Z}$.
 An \emph{interpretation over $\vars$ and $\varn$} is a mapping $I:\vars\cup \varn\rightarrow\Sigma^* \cup \mathbb{Z}$.
@@
 The \emph{number-string} conversion constraint $x=\its{n}$ is treated as a syntactic sugar for $n=\sti{x}$.
+We assume decimal encoding of numbers.
 
@@
 \begin{lemma}\label{lemma:decoding}
-For an flat FA $A$, there is a function $\decode A$ such that for each $w\in L(A)$, $\decode A(\parikhof w) = w$. 
+For a flat FA $A$, there is a function $\decode A$ such that for each $w\in L(A)$, $\decode A(\parikhof w) = w$. 
 \end{lemma}
@@
 
-Consequently, the automaton $A^m$ of our number PFA will have the following form illustrated in Figure~\ref{fig:sfa_its}. 
+Consequently, the automaton $A^m$ of our numeric PFA will have the following form illustrated in Figure~\ref{fig:sfa_its}. 
 It has a self-loop on the initial state labeled by the character variable $v_0$, 
@@
 $$
-Consequently, we design our domain restrictions $\dr$ so that for string variables $x$ that appear within string-integer constraints,  $\dr(x)$ is a number PFA $(A^m,\paf^m),m\in \nat$.
+Consequently, we design our domain restrictions $\dr$ so that for string variables $x$ that appear within string-integer constraints,  $\dr(x)$ is a numberic PFA $(A^m,\paf^m),m\in \nat$.
 

### 2020-03-31 final-version/main.tex
update our response and explain more on the meaning of limited support

@@
 In particular solving string constraints with string-number conversion  is necessary for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages.
-However, the state-of-the-art constraint solvers have   limited support to this type of constraint.
-We propose to overcome these limitations with an approach that can efficiently support both string-number conversion and other common types of string constraints.
-Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
+\changed{However, solving this type of constraint is very challenging for the state-of-the-art solvers.
+They usually cannot handle formulae corresponding to longer program traces.
+We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints.} Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
 \end{abstract}
@@
 An important class of string operations is  the string-number conversions.
-While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$)  suffer from  limited support by the state-of-the-art string constraint solvers.
+While string length operations are sometimes well supported, converting a string $x$ to an integer $n$ (e.g., using the operation $n = \sti{x}$) or turning an integer value $n$ into its string form $x$ (e.g., using the operation $x = \its{n}$) suffer from limited support \changed{(in terms of the scale of formulae they can handle)} by the state-of-the-art string constraint solvers.
 
@@
 Most of the state-of-the-art string constraint solvers provide limited support to the combination of above constraints.
-Even for simple constraints like the above one, most solvers already fail to provide a correct answer.
 \changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve  the case of 2 loop iterations.}

### 2020-03-31 final-version/main.tex
minor

@@
 $$
-Consequently, we design our domain restrictions $\dr$ so that for string variables $x$ that appear within string-integer constraints,  $\dr(x)$ is a numberic PFA $(A^m,\paf^m),m\in \nat$.
+Consequently, we design our domain restrictions $\dr$ so that for string variables $x$ that appear within string-integer constraints,  $\dr(x)$ is a numeric PFA $(A^m,\paf^m),m\in \nat$.
 

### 2020-03-31 final-version/evaluation.tex
minor

@@
 \centering
-\caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
+\caption{Comparison of {\tool}, CVC4, Z3, and Z3Str3 with checkLuhn problems of 2 to 12 loops.}
 \scalebox{0.8}{
@@
 % \centering
-% \caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
+% \caption{Comparison of {\tool}, CVC4, Z3, and Z3Str3 with checkLuhn problems of 2 to 12 loops.}
 % \scalebox{0.9}{
@@
 \hide{
-In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation.
+In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and Z3Str3 as evauation.
 To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[];
@@
 z3seq		& 2716 & 16831 & 0 & 2026 & 0 & 0 \\ 
-z3str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
+Z3Str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
 \end{tabular}
@@
 z3seq		& 2729 & 2655 & 0 & 2012 & 0 & 0 \\ 
-z3str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
+Z3Str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
 \end{tabular}
@@
 \hline
-\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
+\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{Z3Str3} \\
 			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline

### 2020-03-31 final-version/evaluation.tex
update of numbers in the experiments text, removal the story about most failures of Z3-Trau due to the one function.

@@
 
+\changed{
 From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. 
-It fails on twice less cases then Z3, which is ranked the 2nd.
+The second best tool, Z3, fails on 38\% more examples. 
+}
+%It fails on twice less cases then Z3, which is ranked the 2nd.
 In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number.

### 2020-03-31 final-version/evaluation.tex
article
table 2

@@
 
-We compare {\tool} \changed{(\texttt{9831ad0cd})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We compare {\tool} \changed{(\texttt{1e715b7dab})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
@@
 
-	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
+%	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
 
-		\smallskip
+	%	\smallskip
 
@@
 
-The results of the experiments are summarized in Table~\ref{table:base_benchmark}, Table~\ref{table:str_int_benchmark}, and Table~\ref{table:checkLuhn}.
+\changed{The results of the experiments are summarized in Table~\ref{table:base_benchmark}, Table~\ref{table:str_int_benchmark}, and Table~\ref{table:checkLuhn}.
 Rows with heading \texttt{SAT}/\texttt{UNSAT} show numbers of solved formulae.
-Rows with heading \texttt{UNKNOWN}, \texttt{TIMEOUT}, or \texttt{ERROR} indicate the number of instances for which the solver fails to return an answer.
-\texttt{INCORRECT} shows the number of cases where the tool gives a wrong answer\footnote{A correct answer is decided by mainly CVC4, then the consensus of {\tool} or Z3.}.
+Rows with heading \texttt{UNKNOWN} or \texttt{TIMEOUT} indicate the number of instances for which the solver fails to return an answer.
+\texttt{ERROR} means system crashes due to various reasons (usually out of memory).
+\texttt{INCORRECT} shows the number of cases where the tool gives a wrong answer.}
 
@@
 \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
-\multirow{6}{*}{PyEx}		& SAT      & 19166& 19899& 16331&  3037 \\
-							& UNSAT    &  3877&  3848&  3831&  3830 \\
+\multirow{6}{*}{PyEx}		& SAT      & 21377& 19899& 16331&  3037 \\
+							            & UNSAT    &  3860&  3848&  3831&  3830 \\
 							            & UNKNOWN  &     0&     0&     0&     7 \\
-							& TIMEOUT  &  2378&  1674&  5259& 16872 \\
+							            & TIMEOUT  &  184&  1674&  5259& 16872 \\
 							            & ERROR    &     0&     0&     0&  1675 \\
-							& INCORRECT&     1&     0&     0&    14 \\ \hline
-\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
-							& UNSAT    &   286&   214&   100&   111 \\
-							& UNKNOWN  &     0&     0&     0&   345 \\
-							& TIMEOUT  &   188&   335&   487&    89 \\
-							& ERROR    &     0&     0&     0&    20 \\
+							            & INCORRECT&     0&     0&     0&    14 \\ \hline
+%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
+%							& UNSAT    &   286&   214&   100&   111 \\
+%							& UNKNOWN  &     0&     0&     0&   345 \\
+%							& TIMEOUT  &   188&   335&   487&    89 \\
+%							& ERROR    &     0&     0&     0&    20 \\
+%							& INCORRECT&     0&     0&     0&     0 \\ \hline
+\multirow{6}{*}{LeetCode}	& SAT      &   877&   865&   881&   661 \\
+							& UNSAT    &  1785&  1785&  1785&  1780 \\
+							& UNKNOWN  &     0&     0&     0&   122 \\
+							& TIMEOUT  &    0&    16&     0&    90 \\
+							& ERROR    &     4&     0&     0&    13 \\
 							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{LeetCode}	& SAT      &   827&   865&   881&   661 \\
-							& UNSAT    &  1784&  1785&  1785&  1780 \\
-							& UNKNOWN  &     0&     0&     0&   122 \\
-							& TIMEOUT  &    55&    16&     0&    90 \\
-							& ERROR    &     0&     0&     0&    13 \\
-							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{StringFuzz}	& SAT      &   478&   704&   267&   505 \\
-							& UNSAT    &   283&   245&   188&   192 \\
+\multirow{6}{*}{StringFuzz}	& SAT      &   515&   704&   267&   505 \\
+							& UNSAT    &   301&   245&   188&   192 \\
 							& UNKNOWN  &     0&     0&     0&     4 \\
-							& TIMEOUT  &   304&   116&   610&   364 \\
+							& TIMEOUT  &   249&   116&   610&   364 \\
 							& ERROR    &     0&     0&     0&     0 \\
@@
 \multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
-							& UNSAT    &   818&   818&   808&   774 \\
+							& UNSAT    &   822&   818&   808&   774 \\
 							& UNKNOWN  &     0&     0&     0&     4 \\
-							& TIMEOUT  &     4&     6&    15&    38 \\
+							& TIMEOUT  &     0&     6&    15&    38 \\
 							& ERROR    &     0&     0&     0&     9 \\
 							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    11&     8&     5&    16 \\
-							& UNSAT    &  1027&  1025&  1022&   957 \\
+\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    16 \\
+							& UNSAT    &  1032&  1025&  1022&   957 \\
 							& UNKNOWN  &     0&     0&     0&     3 \\
-							& TIMEOUT  &     7&    12&    18&    58 \\
+							& TIMEOUT  &     3&    12&    18&    58 \\
 							& ERROR    &     0&     0&     0&     8 \\
 							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
-\multirow{6}{*}{Total} 		& SAT      & 20621& 21538& 17509&  4262 \\
-							& UNSAT    &  8075&  7935&  7734&  7644 \\
-							& UNKNOWN  &     0&     0&     0&   485 \\
-							& TIMEOUT  &  2936&  2159&  6389& 17511 \\
-							& ERROR    &     0&     0&     0&  1725 \\
-							& INCORRECT&     1&     0&     0&    28 \\\hline
+\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4227\\
+							& UNSAT    &  7800&  7721&  7634&  7533\\
+							& UNKNOWN  &     0&     0&     0&   140\\
+							& TIMEOUT  &  437&  1824&  151& 17422 \\
+							& ERROR    &     4&     0&     0&  1705 \\
+							& INCORRECT&     0&     0&     0&    28 \\\hline
 \end{tabular}}
@@
 \multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
-\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
-								& UNSAT    & 16393& 15726& 16115& 15396 \\
+\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1721&  1898&   239 \\ 
+								& UNSAT    & 16394& 15726& 16115& 15396 \\
 								& UNKNOWN  &     0&     0&     0&   623 \\
-								& TIMEOUT  &   142&  1480&   914&  2337 \\
+								& TIMEOUT  &   32&  1480&   914&  2337 \\
 								& ERROR    &     0&     0&     0&   332 \\
-								& INCORRECT&     1&     0&     0&   108 \\ \hline 
-\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
-								& UNSAT    &   720&   667&   724&   644 \\
+								& INCORRECT&     0&     0&     0&   108 \\ \hline 
+\multirow{6}{*}{PythonLib}		& SAT      &   1922&   579&   914&   206 \\ 
+								& UNSAT    &   724&   667&   724&   644 \\
 								& UNKNOWN  &     0&     0&     0&    45 \\
-								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
+								& TIMEOUT  &  0&  1400&  1008&  1710 \\
 								& ERROR    &     0&     0&     0&    41 \\
@@
 								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
-\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
-								& UNSAT    & 17113& 16393& 16839& 16040 \\
+\multirow{6}{*}{Total}			& SAT      &  4423&  2306&  2828&   449 \\ 
+								& UNSAT    & 17118& 16393& 16839& 16040 \\
 								& UNKNOWN  &     0&     0&     0&   668 \\
-								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
+								& TIMEOUT  &  32&  2894&  1926&  4063 \\
 								& ERROR    &     0&     0&     0&   373 \\
-								& INCORRECT&     1&     0&     0&   110 \\ \hline
+								& INCORRECT&     0&     0&     0&   110 \\ \hline
 \end{tabular}}
@@
 \changed{
-From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. 
+From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
 The second best tool, Z3, fails on 38\% more examples. 

### 2020-03-31 final-version/evaluation.tex
nevim

--- 2020-03-31 final-version/evaluation.tex
@@
 
+%\changed{
+%From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
+%The second best tool, Z3, fails on 38\% more examples. 
+%}
 \changed{
-From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. 
-The second best tool, Z3, fails on 38\% more examples. 
+From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
+The second best tool, Z3, fails on 50 times more examples. 
 }

### 2020-03-31 final-version/evaluation.tex
update 436 to 437 - table 1

--- 2020-03-31 final-version/evaluation.tex
@@
 							& UNKNOWN  &     0&     0&     0&   140\\
-							& TIMEOUT  &  437&  1824&  151& 17422 \\
+							& TIMEOUT  &  436&  1824&  151& 17422 \\
 							& ERROR    &     4&     0&     0&  1705 \\
@@
 
+%\changed{
+%From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
+%The second best tool, Z3, fails on 38\% more examples. 
+%}
 \changed{
 From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
-The second best tool, Z3, fails on 38\% more examples. 
+The second best tool, Z3, fails on 50 times more examples. 
 }

### 2020-03-31 final-version/evaluation.tex
fix table 1

--- 2020-03-31 final-version/evaluation.tex
@@
 							& UNKNOWN  &     0&     0&     0&   140\\
-							& TIMEOUT  &  437&  1824&  151& 17422 \\
+							& TIMEOUT  &  436&  1824&  5902& 17422 \\
 							& ERROR    &     4&     0&     0&  1705 \\

### 2020-03-31 final-version/evaluation.tex
debug

@@
 								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
-\multirow{6}{*}{Total}			& SAT      &  4423&  2306&  2828&   449 \\ 
+\multirow{6}{*}{Total}			& SAT      &  4443&  2306&  2828&   449 \\ 
 								& UNSAT    & 17118& 16393& 16839& 16040 \\

### 2020-03-31 final-version/evaluation.tex
debug

@@
 \multirow{6}{*}{Leetcode}		& SAT      &  2501&  1721&  1898&   239 \\ 
-								& UNSAT    & 16394& 15726& 16115& 15396 \\
+								& UNSAT    & 16394& 15726& 16115& 15288 \\
 								& UNKNOWN  &     0&     0&     0&   623 \\
@@
 \multirow{6}{*}{PythonLib}		& SAT      &   1922&   579&   914&   206 \\ 
-								& UNSAT    &   724&   667&   724&   644 \\
+								& UNSAT    &   724&   667&   724&   642 \\
 								& UNKNOWN  &     0&     0&     0&    45 \\
@@
 \multirow{6}{*}{Total}			& SAT      &  4443&  2306&  2828&   449 \\ 
-								& UNSAT    & 17118& 16393& 16839& 16040 \\
+								& UNSAT    & 17118& 16393& 16839& 15930 \\
 								& UNKNOWN  &     0&     0&     0&   668 \\
-								& TIMEOUT  &  32&  2894&  1926&  4063 \\
-								& ERROR    &     0&     0&     0&   373 \\
+								& TIMEOUT  &  32&  2894&  1926&  4057 \\
+								& ERROR    &     0&     0&     0&   379 \\
 								& INCORRECT&     0&     0&     0&   110 \\ \hline

### 2020-03-31 final-version/evaluation.tex
debug

@@
 \multirow{6}{*}{PyEx}		& SAT      & 21377& 19899& 16331&  3037 \\
-							            & UNSAT    &  3860&  3848&  3831&  3830 \\
+							            & UNSAT    &  3860&  3848&  3831&  3816 \\
 							            & UNKNOWN  &     0&     0&     0&     7 \\
@@
 							& TIMEOUT  &     0&     6&    15&    38 \\
-							& ERROR    &     0&     0&     0&     9 \\
+							& ERROR    &     0&     0&     0&     11 \\
 							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    16 \\
+\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    2 \\
 							& UNSAT    &  1032&  1025&  1022&   957 \\
@@
 							& TIMEOUT  &     3&    12&    18&    58 \\
-							& ERROR    &     0&     0&     0&     8 \\
+							& ERROR    &     0&     0&     0&     11 \\
 							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
-\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4227\\
-							& UNSAT    &  7800&  7721&  7634&  7533\\
+\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4213\\
+							& UNSAT    &  7800&  7721&  7634&  7519\\
 							& UNKNOWN  &     0&     0&     0&   140\\
 							& TIMEOUT  &  436&  1824&  5902& 17422 \\
-							& ERROR    &     4&     0&     0&  1705 \\
+							& ERROR    &     4&     0&     0&  1710\\
 							& INCORRECT&     0&     0&     0&    28 \\\hline

### 2020-03-31 final-version/evaluation.tex
debug

@@
 In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases.
-On the APLAS and StringFuzz benchmarks that are SAT, {\tool} does not perfomr as well as the best performing tool.
-We however do not consider this crucial because both of these benchmarks are artificial, either hand-crafted or randomly generated.
+On the StringFuzz benchmarks that are SAT, {\tool} does not perform as well as the best performing tool.
+We however do not consider this crucial because these benchmarks are just randomly generated for debugging.
 On the most important benchmarks, those that come from program analysis, {\tool} is comparable to the best performing tool.

### 2020-03-31 final-version/evaluation.tex
Update evaluation.tex

@@
 \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
-We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks.
-We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.
+We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occur in most of our benchmarks.
+We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support many of the string functions in our benchmarks, especially string-number conversion.
 
@@
 In the first set of experiments, we compare {\tool} with other tools on existing benchmarks over basic string constraints.
-Those benchmarks do not involve string-number conversion function.
+Those benchmarks do not involve string-number conversion functions.
 In the second set of experiments, we compare {\tool} with the other tools on new suites focusing on string-number conversion.

### 2020-03-31 final-version/evaluation.tex
typo table 2

@@
 								& UNKNOWN  &     0&     0&     0&   668 \\
-								& TIMEOUT  &  32&  2894&  1926&  4057 \\
-								& ERROR    &     0&     0&     0&   379 \\
+								& TIMEOUT  &  32&  2894&  1926&  4063 \\
+								& ERROR    &     0&     0&     0&   373 \\
 								& INCORRECT&     0&     0&     0&   110 \\ \hline

### 2020-03-31 final-version/evaluation.tex
Update table2

@@
 								& INCORRECT&     0&     0&     0&     2 \\ \hline
-\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
+\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
 								& UNSAT    &     0&     0&     0&     0 \\
-								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
-\multirow{6}{*}{Total}			& SAT      &  4443&  2306&  2828&   449 \\ 
+								& UNKNOWN  &     0&     9&     0&     0 \\
+								& TIMEOUT  &     0&     8&     4&    10 \\
+								& ERROR    &     0&     0&     0&     6 \\
+								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
+\multirow{6}{*}{Total}			& SAT      &  4443&  2303&  2828&   449 \\ 
 								& UNSAT    & 17118& 16393& 16839& 15930 \\
-								& UNKNOWN  &     0&     0&     0&   668 \\
-								& TIMEOUT  &  32&  2894&  1926&  4063 \\
-								& ERROR    &     0&     0&     0&   373 \\
+								& UNKNOWN  &     0&     9&     0&   668 \\
+								& TIMEOUT  &    32&  2888&  1926&  4057 \\
+								& ERROR    &     0&     0&     0&   379 \\
 								& INCORRECT&     0&     0&     0&   110 \\ \hline

### 2020-04-02 draft.tex
small fixes related to rev C and few other minor things
change running example

@@
 
-For ease of presentation, we  use the following toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
+For ease of presentation, we  use the following toy example $$\Phi = \{`0'x = x`0', \sti{x} = \sti{y} ,|y|>|x|, 1000<|y| \}$$
 
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12"$.
+To make our terminology explicit: $\Phi$ states that $`0'$ concatenated with $x$ is the same as $x$ with $`0'$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12"$.
 Notice that $\Phi$ is satisfiable.
@@
 %We assume that the set of integer variables is $Z=\{v_z\}$ and $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
-Let the set of integer variables be $Z=\{v_z\}$ and let $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
+For the purpose of this example, let the set of integer variables be $Z=\{v_z\}$. 
+We have $V_{\dr(x)} =\{v_0, v_1,v_2,v_3\}$. 
 For the interpretation $I_e =(v_z,v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (3,\semof{a}, \semof{b}, \semof{c},\semof{\epsilon},3,3,2,2)$, we have $\decode \dr (I_e) = \{(z,x,y) \rightarrow(3, ``ababab",``cc") \}$.\\

### 2020-04-02 final-version/main.tex
minor
change running example

@@
 \changed{However, solving this type of constraint is very challenging for the state-of-the-art solvers.
-They usually cannot handle formulae corresponding to longer program traces.
 We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints.} Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
@@
 
-For ease of presentation, we  use the following toy example $$\Phi = \{xy=yx, n = \sti{x}, n >3 ,|y|>|x|, y \in (12)^+\}$$
-
+For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x|, 1000\!<\!|y| \}$$}
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that $x$ concatenated with $y$ is the same as $y$ with $x$, $n$ is the numeric value of the string $x$, $n > 3$, $y$ is longer than $x$, and $y$ is a string in the form of a finite repetitions of $``12"$.
+To make our terminology explicit: $\Phi$ states that \changed{$``0''$ concatenated with $x$ is the same as $x$ with $``0''$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$.
 Notice that $\Phi$ is satisfiable.
-E.g., it has a model $x=``12"$ and $y=``1212"$.
+E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
 
@@
 Our choice of the chain-free fragment~\cite{abdulla2019chain} is only motivated by the fact that the chain-free fragment is the {\em largest} known decidable fragment for that class of string constraints.
-In our example, we over-approximate the formula $\Phi$ by converting $xy=yx$ to two formulae $\{x_1=xy, x_2=yx\}$  and replacing the constraint $n=\sti{x}$ with $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$).
+In our example, we over-approximate the formula $\Phi$ by converting \changed{$``0"x = x``0"$ to two formulae $\{x_1=``0"x, x_2=x``0"\}$  and replacing the constraint $\sti{x}=\sti{y}$ with $n_x = n_y \wedge (n_x=-1 \vee (n_x\neq -1 \wedge x\in [0-9]^*)) \wedge (n_y=-1 \vee (n_y\neq -1 \wedge y\in [0-9]^*))$)}.
 Observe that if the over-approximation is UNSAT then our decision procedure  declares that the original formula is also UNSAT and terminates.
@@
 Thus, $v_0$, $v_1$, $v_2$, $v_3$ are also integer variables.
-For example, from  $ y \in (12)^+$, we may derive $v_1=1$ and $v_2=2$.
-
-The linear formula produced after the domain restriction will be over variables $v_0$, $v_1$, $v_2$, $v_3$, as well as the number of occurrences of each character variable $\#v_0$, $\#v_1$, $\#v_2$, $\#v_3$.
+
+\changed{The linear formula produced after the domain restriction will be over variables $v_0$, $v_1$, $v_2$, $v_3$, as well as the number of occurrences of each character variable $\#v_0$, $\#v_1$, $\#v_2$, $\#v_3$.
 Each model of the linear formula encodes a model of the string constraint.
-For example, $x=``12"$ and $y=``1212"$ is encoded by the assignment $(v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (1,2,1,2,1,1,2,2)$.%
+For example, $x=``00"$ and $y=``0^{1002}"$ is encoded by the assignment $(v_0,v_1,v_2,v_3,\#v_0,\#v_1,\#v_2,\#v_3) \rightarrow (0,0,0,0,1,1,501,501)$.%
 \footnote{In these examples, we use the shorthand $(x_1,\ldots,x_k)\rightarrow(n_1,\ldots,n_k)$ to denote the function $\{x_1 \mapsto n_1,\ldots, x_k\mapsto n_k\}$.}
 The assignment says, for example, that $x$ is the \emph{parametric word} obtained by traversing the loop of $A_x$ once (because $\#v_0 = \#v_1 = 1$), which is $v_0v_1$.
-Under the assignment $v_0=1$ and $v_1=2$, we obtain $x=``12"$.
+Under the assignment $v_0=0$ and $v_1=0$, we obtain $x=``00"$.}
 

### 2020-04-02 final-version/main.tex
change running example
typo

@@
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that \changed{$``0''$ concatenated with $x$ is the same as $x$ with $``0''$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$.
+To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$ characteras.
 Notice that $\Phi$ is satisfiable.

### 2020-04-02 final-version/main.tex
typo

--- 2020-04-02 final-version/main.tex
@@
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that \changed{$``0''$ concatenated with $x$ is the same as $x$ with $``0''$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$.
+To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$ characters.
 Notice that $\Phi$ is satisfiable.
@@
 We report unknown after failing to prove SAT using a certain number of PFAs.
+
+\changed{Although this toy example is seemingly trivial, all the string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it with a long timeout (10 min).}
 

### 2020-04-02 final-version/main.tex
formulation

@@
 E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
-
-Our decision procedure has two steps: the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+\changed{Although this toy example is seemingly trivial, all the string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }
+
+%Our decision procedure has two steps: 
+\changed{
+Our new decision procedure solves the example in few seconds.
+%
+It proceeds in two steps:} the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Observe that we could  over-approximate the input constraint into any decidable fragment, e.g.
@@
 We report unknown after failing to prove SAT using a certain number of PFAs.
-
-\changed{Although this toy example is seemingly trivial, all the string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it with a long timeout (10 min).}
 

### 2020-04-02 final-version/main.tex
Update main.tex

@@
 
-For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x|, 1000\!<\!|y| \}$$}
+For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x| >1, 1000\!<\!|y| \}$$}
 to explain the main ideas behind our decision procedure.
-To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$, and $y$ is longer than $1000$ characters.
+To make our terminology explicit: $\Phi$ states that \changed{$``0"$ concatenated with $x$ is the same as $x$ with $``0"$, the numeric value of the string $x$ is equivalent to that of $y$, $y$ is longer than $x$,  $y$ is longer than $1000$ characters, and $x$ is longer than 1.
 Notice that $\Phi$ is satisfiable.
 E.g., it has a model $x=``00"$ and $y=``0^{1002}"$}.
-\changed{Although this toy example is seemingly trivial, all the string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }
+\changed{Although this toy example is seemingly trivial, all the state-of-the-art string constraint solvers we tried (including Z3, CVC4, and Z3Str3) cannot solve it within 10 minutes. }
 

### 2020-04-03 final-version/evaluation.tex
minor

@@
 
-All experiments were executed on a machine with 4-core CPU, 8 GiB RAM. The timeout was set to 10s for each test.
+	\changed{All experiments were executed on a machine with 4-core CPU, 16 GiB RAM, and MacOS 10.15.4.} The timeout was set to 10s for each test.
 We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
@@
 Table~\ref{table:base_benchmark} shows the result of the comparison.
-The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS.
-We set the timeout is to 10 seconds.
+\changed{The experiments are conducted with a machine of the following specifications: 4-core CPU, 16GB RAM, MacOS 10.15.4.} We set the timeout is to 10 seconds.
 Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster.

### 2020-04-04 final-version/main.tex
minor
remove widows and orphans

@@
 \begin{document}
+\clubpenalty = 10000000
+\widowpenalty = 10000000
+\displaywidowpenalty = 1000000
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
-\newcommand{\changed}[1]{{\color{blue}#1}}
+\newcommand{\changed}[1]{#1}
 
@@
 
-For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!>\!|x| >1, 1000\!<\!|y| \}$$}
+For ease of presentation, we  use the following toy example \changed{$$\Phi\!=\! \{``0"x\!=\! x``0", \sti{x} \!=\! \sti{y} ,|y|\!\!>\!\!|x| \!\!>\!\!1, 1000\!\!<\!\!|y| \}$$}
 to explain the main ideas behind our decision procedure.
@@
 That is
-\begin{eqnarray*}
-\leftA \defeq& \dr(x_1)\cdot\ldots \cdot \dr(x_n)\\
-\rightA \defeq& \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)
-\end{eqnarray*}
+	$$\leftA \defeq \dr(x_1)\cdot\ldots \cdot \dr(x_n)\ \ \  \rightA \defeq \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)$$
+
+%\begin{eqnarray*}
+%\leftA \defeq& \dr(x_1)\cdot\ldots \cdot \dr(x_n)\\
+%\rightA \defeq& \dr(x_{n+1})\cdot\ldots \cdot \dr(x_m)
+%\end{eqnarray*}
 The under-approximation of $\phi_e$ is then obtained as their synchronization formula

### 2020-04-04 final-version/evaluation.tex
remove widows and orphans

@@
 
-We compare {\tool} \changed{(\texttt{1e715b7dab})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
+We compare {\tool} (\texttt{1e715b7dab})\footnote{\url{https://github.com/guluchen/z3/tree/1e715b7dab}} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
 For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.

### 2020-04-04 final-version/evaluation.tex
fix email of Julian

--- 2020-04-03 final-version/evaluation.tex
@@
 
-We compare {\tool} \changed{(\texttt{1e715b7dab})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}.
-For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version.
+We compare {\tool} (\texttt{1e715b7dab})\footnote{\url{https://github.com/guluchen/z3/tree/1e715b7dab}} with other state-of-the-art string solvers, namely, CVC4~(version 1.7)~\cite{cvc4Tool}, Z3~(version 4.8.7)~\cite{z3}, and \textsf{Z3Str3}~(version 4.8.7)~\cite{zheng2013z3}.
+For these tools, the versions we used are the latest release versions.
 \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}

### 2020-04-04 final-version/evaluation.tex
update experiments to use release version of all tools

@@
 We compare {\tool} (\texttt{1e715b7dab})\footnote{\url{https://github.com/guluchen/z3/tree/1e715b7dab}} with other state-of-the-art string solvers, namely, CVC4~(version 1.7)~\cite{cvc4Tool}, Z3~(version 4.8.7)~\cite{z3}, and \textsf{Z3Str3}~(version 4.8.7)~\cite{zheng2013z3}.
-For these tools, the versions we used are the latest release versions.
+For these tools, the versions we used are the latest release version.
 \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
@@
 
-	\changed{All experiments were executed on a machine with 4-core CPU, 16 GiB RAM, and MacOS 10.15.4.} The timeout was set to 10s for each test.
+	\changed{All experiments were executed on a machine with 4-core CPU and 16 GiB RAM.} The timeout was set to 10s for each test.
 We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results.
@@
 \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
-\multirow{6}{*}{PyEx}		& SAT      & 21377& 19899& 16331&  3037 \\
-							& UNSAT    &  3860&  3848&  3831&  3816 \\
+\multirow{6}{*}{PyEx}		& SAT      & 21377& 20350& 18492&  3037 \\
+							& UNSAT    &  3860&  3841&  3847&  3816 \\
 							& UNKNOWN  &     0&     0&     0&     7 \\
-							& TIMEOUT  &   184&  1674&  5259& 16872 \\
+							& TIMEOUT  &   184&  1230&  3082& 16872 \\
 							& ERROR    &     0&     0&     0&  1675 \\
@@
 %							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{LeetCode}	& SAT      &   877&   865&   881&   661 \\
+\multirow{6}{*}{LeetCode}	& SAT      &   877&   874&   881&   661 \\
 							& UNSAT    &  1785&  1785&  1785&  1780 \\
 							& UNKNOWN  &     0&     0&     0&   122 \\
-							& TIMEOUT  &    0&    16&     0&    90 \\
+							& TIMEOUT  &    0&    7&     0&    90 \\
 							& ERROR    &     4&     0&     0&    13 \\
 							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{StringFuzz}	& SAT      &   515&   704&   267&   505 \\
-							& UNSAT    &   301&   245&   188&   192 \\
+\multirow{6}{*}{StringFuzz}	& SAT      &   515&   615&   338&   505 \\
+							& UNSAT    &   301&   255&   198&   192 \\
 							& UNKNOWN  &     0&     0&     0&     4 \\
-							& TIMEOUT  &   249&   116&   610&   364 \\
+							& TIMEOUT  &   249&   195&   529&   364 \\
 							& ERROR    &     0&     0&     0&     0 \\
@@
 							& INCORRECT&     0&     0&     0&     0 \\ \hline
-\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    2 \\
-							& UNSAT    &  1032&  1025&  1022&   957 \\
+\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     9&     7&    2 \\
+							& UNSAT    &  1032&  1026&  1022&   957 \\
 							& UNKNOWN  &     0&     0&     0&     3 \\
-							& TIMEOUT  &     3&    12&    18&    58 \\
+							& TIMEOUT  &     3&    10&    16&    58 \\
 							& ERROR    &     0&     0&     0&     11 \\
 							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
-\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4213\\
-							& UNSAT    &  7800&  7721&  7634&  7519\\
+\multirow{6}{*}{Total} 		& SAT      & 22792& 21859& 19730&  4213\\
+							& UNSAT    &  7800&  7725&  7550&  7519\\
 							& UNKNOWN  &     0&     0&     0&   140\\
-							& TIMEOUT  &  436&  1824&  5902& 17422 \\
+							& TIMEOUT  &  436&  1448&  3642& 17422 \\
 							& ERROR    &     4&     0&     0&  1710\\
@@
 \multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
-\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1721&  1898&   239 \\ 
-								& UNSAT    & 16394& 15726& 16115& 15288 \\
+\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1659 &  1993&   239 \\ 
+								& UNSAT    & 16394& 15604& 16124& 15288 \\
 								& UNKNOWN  &     0&     0&     0&   623 \\
-								& TIMEOUT  &    32&  1480&   914&  2337 \\
+								& TIMEOUT  &    32&  1664&   810&  2337 \\
 								& ERROR    &     0&     0&     0&   332 \\
 								& INCORRECT&     0&     0&     0&   108 \\ \hline 
-\multirow{6}{*}{PythonLib}		& SAT      &  1922&   579&   914&   206 \\ 
-								& UNSAT    &   724&   667&   724&   642 \\
+\multirow{6}{*}{PythonLib}		& SAT      &  1922&   560&   1839&   206 \\ 
+								& UNSAT    &   724&   666&   724&   642 \\
 								& UNKNOWN  &     0&     0&     0&    45 \\
-								& TIMEOUT  &     0&  1400&  1008&  1710 \\
+								& TIMEOUT  &     0&  1420&  83&  1710 \\
 								& ERROR    &     0&     0&     0&    41 \\
@@
 								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
-\multirow{6}{*}{Total}			& SAT      &  4443&  2303&  2828&   449 \\ 
-								& UNSAT    & 17118& 16393& 16839& 15930 \\
-								& UNKNOWN  &     0&     9&     0&   668 \\
-								& TIMEOUT  &    32&  2888&  1926&  4057 \\
-								& ERROR    &     0&     0&     0&   379 \\
-								& INCORRECT&     0&     0&     0&   110 \\ \hline
+\multirow{6}{*}{Total}			& SAT      &  4443&  2222     &  3848    &   449 \\ 
+								& UNSAT            & 17118 & 16270     & 16848   & 15930 \\
+								& UNKNOWN      &     0   &     9        &     0       &   668 \\
+								& TIMEOUT         &    32  &  3092     &  897     &  4057 \\
+								& ERROR             &     0   &     0        &     0        &   379 \\
+								& INCORRECT     &     0   &     0        &     0         &   110 \\ \hline
 \end{tabular}}

### 2020-04-04 final-version/evaluation.tex
update tables

@@
 with the timeout set to 120s. The result is summarized in Table~\ref{table:checkLuhn}.
-In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3Str3 could not solve any of these problems (either timeout or UNKNOWN).
-However, Z3 can still solve 7 out of the 11 problems, while timeouting in the cases with 4, 5, 7, and 9 loops.
+In these tests, {\tool} can solve all problems within 1s while CVC4 only returns a model for cases of 2 to 5 loops and Z3Str3 could not solve any of these problems (either TIMEOUT, ERROR, or UNKNOWN).
+However, Z3 can still solve 5 out of the 11 problems.
 The behavior of Z3 is not entirely unexpected.
@@
 \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
-2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.89s) & \textbf{SAT}(0.45s) & \textbf{ERROR} \\
-3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(1.17s) & \textbf{SAT}(0.10s) & \textbf{ERROR} \\
-4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) & \textbf{TIMEOUT}    & \textbf{ERROR} \\
-5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(11.27s)& \textbf{TIMEOUT}    & \textbf{ERROR} \\
-6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.13s) & \textbf{UNKNOWN} \\
+2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.17s) & \textbf{SAT}(0.11s) & \textbf{ERROR} \\
+3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(6.94s) & \textbf{SAT}(0.13s) & \textbf{ERROR} \\
+4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) &  \textbf{SAT}(0.24s)     & \textbf{ERROR} \\
+5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(30.86s)&  \textbf{SAT}(0.13s)     & \textbf{ERROR} \\
+6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    &\textbf{TIMEOUT} & \textbf{UNKNOWN} \\
 7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
-8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.29s) & \textbf{ERROR} \\
-9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
-10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.48s) & \textbf{TIMEOUT} \\
-11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.36s) & \textbf{ERROR} \\
-12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.38s) & \textbf{TIMEOUT} \\ \hline
+8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT} & \textbf{ERROR} \\
+9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    &\textbf{SAT}(0.31s)  & \textbf{ERROR} \\
+10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    &  \textbf{TIMEOUT} & \textbf{TIMEOUT} \\
+11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    &  \textbf{TIMEOUT} & \textbf{ERROR} \\
+12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    &  \textbf{TIMEOUT} & \textbf{ERROR} \\ \hline
 \end{tabular}}

### 2020-04-04 final-version/main.tex
fix email of Julian
update tables

@@
 }
-\email{bui.phi-diep@it.uu.se}
+\email{dolby@us.ibm.com}
 
@@
 Most of the state-of-the-art string constraint solvers provide limited support to the combination of above constraints.
-\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 fails to solve the cases corresponding to 4,5,7, and 9 loop iterations, and Z3Str3 fails to solve  the case of 2 loop iterations.}
+\changed{In Table~\ref{table:checkLuhn} of our evaluation (Section~\ref{section:evaluation}), CVC4 fails to solve constraints corresponding to checkLuhn of more than 6 loop iterations in 2 minutes, Z3 can only solve the cases corresponding to 2 to 5, and 9 loop iterations, and Z3Str3 fails to solve any case.}
 

### 2020-04-05 final-version/main.tex
add two references
more acks

@@
 To the best of our knowledge, the satisfiability problem of integer constraints with a mix of polynomials and exponentials is still open.
-The problem is difficult even for the case that variables are real numbers.
+The problem is difficult even for the case that variables are real numbers~\cite{GanCDXZ15,GanCLXZ18}.
 For example, the algorithm in~\cite{kincaid2019closed} involves a quantifier elimination procedure which is double-exponential to the length of the input formula and hence cannot handle large instances.
@@
 This research was  partially supported by the  Swedish Foundation for Strategic Research, Ministry of Science and Technology Project, Taiwan (no.
-106-2221-E-001 -009 -MY3), and Ministry of Education, Youth and Sports of Czech Republic (no.
-LL1908).
+106-2221-E-001 -009 -MY3), Ministry of Education, Youth and Sports of Czech Republic (project IT4Innovations excellence in science--LQ1602 and project LL1908), and FIT BUT internal grant FIT-S-20-6427.
+
 \end{acks}

### 2020-04-05 final-final/evaluation.tex
final version

--- 2020-04-04 final-version/evaluation.tex
@@
 
-%	\item APLAS~\cite{aplas} includes 600 hand-drafted tests consisting of only equality and integer length constraints.
-
-	%	\smallskip
-
 	\item \changed{ LeetCode comes from running PyEx over a sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check whether a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check whether an input string is an abbreviation of another input string, and convert a sequence of digits to a string according to a given mapping.}
@@
 							& INCORRECT&     0&     0&     0&    14 \\ \hline
-%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
-%							& UNSAT    &   286&   214&   100&   111 \\
-%							& UNKNOWN  &     0&     0&     0&   345 \\
-%							& TIMEOUT  &   188&   335&   487&    89 \\
-%							& ERROR    &     0&     0&     0&    20 \\
-%							& INCORRECT&     0&     0&     0&     0 \\ \hline
 \multirow{6}{*}{LeetCode}	& SAT      &   877&   874&   881&   661 \\
@@
 
-% \begin{table}[h]
-% \centering
-% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
-% \scalebox{0.85}{
-% \begin{tabular}{|l r | r r r r |}
-% \hline
-% \multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
-% \multirow{3}{*}{PyEx}		& SAT      &  19468  & 19763 & 16528 &  3030 \\ 
-% 							& UNSAT    &   3854  &  3834 &  3831 &  3836 \\
-% 							& $\times$ &   2099  &  1824 &  5062 & 18555 \\ \hline
-% \multirow{3}{*}{APLAS}		& SAT      &    131  &   205 &    12 &    37 \\
-% 							& UNSAT    &    288  &   221 &   100 &   111 \\
-% 							& $\times$ &    181  &   174 &   488 &   452 \\ \hline
-% \multirow{3}{*}{LeetCode}	& SAT      &    881  &   859 &   881 &   670 \\
-% 							& UNSAT    &   1785  &  1785 &  1785 &  1780 \\
-% 							& $\times$ &      0  &    22 &     0 &   216 \\ \hline
-% \multirow{3}{*}{StringFuzz}	& SAT      &    498  &   671 &   264 &   491 \\
-% 							& UNSAT    &    319  &   240 &   186 &   192 \\
-% 							& $\times$ &    248  &   154 &   615 &   382 \\\hline
-% \multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 11 & 11 &   12 &     8 \\
-% 							& UNSAT    &    820  &   818 &   808 &   772 \\
-% 							& $\times$ &      4  &     6 &    15 &    55 \\ \hline
-% \multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13 & 8 &     5 &    17 \\
-% 							& UNSAT    &   1031  &   936 &  1021 &   958 \\
-% 							& $\times$ &      1  &   101 &    19 &    70 \\ \hline \hline
-% \multirow{3}{*}{Total} 		& SAT      &  21002  & 21517 & 17702 &  4253 \\
-% 							& UNSAT    &   8097  &  7834 &  7731 &  7649 \\
-% 							& $\times$ &   2533  &  2281 &  6199 & 19730 \\\hline	
-% \end{tabular}}
-% \label{table:base_benchmark}
-% \end{table}
-
-% \begin{table}[h]
-% \centering
-% \caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
-% \scalebox{0.8}{
-% \begin{tabular}{|l r | r r r r|}
-% \hline
-% \multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
-% \multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
-% 								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
-% 								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
-% \multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
-% 								& UNSAT    &    720  &   660 &   724  &   644 \\
-% 								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
-% \multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
-% 								& UNSAT    &      0  &     0 &     0  &     0 \\
-% 								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-% \multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
-% 								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
-% 								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
-% \end{tabular}}
-% \label{table:str_int_benchmark}
-% \end{table}
-
 From Table~\ref{table:base_benchmark}, we can see that the performance of {\tool} is as good as that of the most competitive tools such as CVC4 and Z3 on basic string constraints.
@@
 
-%\changed{
-%From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all the other tools. 
-%The second best tool, Z3, fails on 38\% more examples. 
-%}
 \changed{
@@
 }
-%It fails on twice less cases then Z3, which is ranked the 2nd.
-In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number.
-From around 2028 tests generated from this function, around 1000 tests are too difficult for all solvers.
-If we exclude the 2028 tests generated from this function, then {\tool} has only $218$ failed cases in total.
-This is significantly better than the 2nd place tool Z3, which fails on $942$ cases in total.
-
-%We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s.
-Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3Str3 got almost the same number of failed cases.
-Z3 also managed to reduce the number of failed cases to 821.
-%If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.
 
@@
 \end{table}
-
-% \todo{Update table with data of timeout=30s}
-
-% \begin{table}[h]
-% \centering
-% \caption{Comparison of {\tool}, CVC4, Z3, and Z3Str3 with checkLuhn problems of 2 to 12 loops.}
-% \scalebox{0.9}{
-% \begin{tabular}{| c | c c c c|}
-% \hline
-% \# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
-% 2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.23s) & $\times$ \\
-% 3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.13s) & $\times$ \\
-% 4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
-% 5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
-% 6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.14s) & $\times$ \\
-% 7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
-% 8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
-% 9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
-% 10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.62s) & $\times$ \\
-% 11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.47s) & $\times$ \\
-% 12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.47s) & $\times$ \\ \hline
-% \end{tabular}}
-% \label{table:checkLuhn}
-% \end{table}
-
-\hide{
-\paragraph{Basic constraint benchmarks.}
-This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups.
-In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in some cases even better.
-
-The first benchmark is called PyEx~\cite{pyex} according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing.
-This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests.
-PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.
-
-The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}.
-The benchmark includes a total of 600 hand-crafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.
-
-The next benchmark is called LeetCode~\cite{LeetCode} that was obtained by extracting constraints from Python's testing solutions provided by LeetCode platform.
-They provide many programming examples and their solutions gathered from technical interviews for companies.
-Leetcode consists of 881 satisfiable and 1785 unsatisfiable tests that, like PyEx, contain diverse string constraints.
-
-StringFuzz is our next benchmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints.
-We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.
-
-The last two benchmarks, called $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$, are obtained from cvc4 group~\cite{termEQ}.
-This set of benchmarks consists of the verification of term equivalences over strings and includes various string constraints including string-number and number-string conversion constraints.
-
-\paragraph{String-number conversion constraint benchmarks.}
-Our second group of benchmarks was created in order that we could compare our proposed approach for solving string-number and number-string conversions with existing approaches.
-This group contains a total of 3 benchmarks: full\_str\_int, filtered\_str\_int and rec\_fun.
-None of these benchmarks were artificially generated but were created from real Python's and javascript's codes.
-
-The first benchmark in the group is full\_str\_int, which is a collection of SMT queries.
-This collection was generated by applying a tool for concolic testing to Python codes selected from the previously mentioned LeetCode platform and from Python core libraries.
-All selected Python codes use the \texttt{int()} function, which converts a string into a number system based on the specified base.
-The Benchmark consists of 21573 tests in total.
-
-The second benchmark, called filtered\_str\_int, is a subset of the previous full\_str\_int benchmark.
-The filtered\_str\_int benchmark was created by removing tests where cvc4 reported UNSAT and where cvc4's returned unsat core contained no conversion constraint.
-This benchmark was created in order that we better compare individual conversion approaches.
-A total of 7396 tests were left.
-
-The last benchmark in the group is rec\_fun, which is a collection of javascript functions that were handcrafted encoded into smt2 format using recursive functions.
-Besides running examples from the introduction, the benchmark also includes \texttt{split} and \texttt{replaceAll} functions.
-In total, we managed to create 43 tests that combine several SMT theory and contain conversion constrains.
-}
-
-\hide{
-In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and Z3Str3 as evauation.
-To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[];
-LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[].
-Table~\ref{table:base_benchmark} shows the result of the comparison.
-\changed{The experiments are conducted with a machine of the following specifications: 4-core CPU, 16GB RAM, MacOS 10.15.4.} We set the timeout is to 10 seconds.
-Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster.
-The results are either sat, unsat, timeout, or $\times$.
-In case $\times$, the result may be unknown, error, or exception.
-
-\textbf{Comparison according to Table 1......}
-
-To evaluate our strategy for string-number/number-string conversion, we also prepared a benchmark \texttt{str\_int}\footnote{\url{https://github.com/plfm-iis/str_int_benchmarks}}.
-It is collected from two sources of Python programs that use ttexttt{int()} function: Leetcode solutions written in Python and Python core libraries.
-We concolic tested these Python programs by \texttt{Py-Conbyte}\footnote{\url{https://github.com/spencerwuwu/py-conbyte}}, our concolic tester for Python programs.
-The SMT queries during the concolic testing are collected as our benchmark.
-To be more precise in evalutation, we have two versions of \texttt{str\_int} benchmark: \texttt{full\_str\_int} and \texttt{filtered\_str\_int}.
-\texttt{full\_str\_int} is the original benchmark we collected (i.e.
-from Python programs using \texttt{int()}); \texttt{filtered\_str\_int} is a subset of \texttt{fill\_str\_int}.
-We filtered out problems that cvc4 says unsat while the unsat cores do not contain \texttt{str.to.int} or \texttt{int.to.str}.
-The results of experiment on \texttt{str\_int} benchmark is listed in Table~\ref{table:str_int_benchmark}.
-The experiments are conducted under the same condition as the experiments on other benchmarks.
-
-\textbf{Comparison according to Table 2.....}
-}
-
-\hide{
-\begin{table}[]
-\caption{Results of z3-Trau, cvc4, and z3 on full\_str\_int benchmark}
-\begin{tabular}{|r|r|r|r|r|r|r|}
-\hline
-Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
-z3-Trau		& 3289 & 17089 & 0 & 1195 & 0 & 0 \\ 
-cvc4		& 2185 & 16377 & 0 & 3011 & 0 & 0 \\ 
-z3seq		& 2716 & 16831 & 0 & 2026 & 0 & 0 \\ 
-Z3Str3		& 422 & 16034 & 634 & 4131 & 347 & 5 \\ \hline
-\end{tabular}
-\label{table:full_str_int}
-\end{table}
-
-Table~\ref{table:filtered_str_int} shows the comparison on filtered\_str\_int.  The total amount of cases in filtered\_str\_int is 7396.
-
-\begin{table}[]
-\caption{Results of z3-Trau, cvc4, and z3 on filtered\_str\_int benchmark}
-\begin{tabular}{|r|r|r|r|r|r|r|}
-\hline
-Tool		& sat & unsat & u.k. & t.o. & err. & misc \\ \hline\hline
-z3-Trau		& 3281 & 2912 & 0 & 1203 & 0 & 0 \\ 
-cvc4		& 2210 & 2211 & 0 & 2975 & 0 & 0 \\ 
-z3seq		& 2729 & 2655 & 0 & 2012 & 0 & 0 \\ 
-Z3Str3		& 424 & 1944 & 587 & 4106 & 330 & 5 \\ \hline
-\end{tabular}
-\label{table:filtered_str_int}
-\end{table}
-}
-
-\hide{ % keep data of abc and ostrich
-\begin{table}[h]
-\centering
-\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
-\scalebox{0.7}{
-\begin{tabular}{|l r | r r r r r r r|}
-\hline
-\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
-\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
-							& unsat    &  3858*   &  3834* &  3855 &   3839*  & 3828 & 0 & 871 \\
-							& $\times$ &  1977*   &  1824* &  3076 &  18558*  & 2444 & 25421 & 24439 \\ \hline
-\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
-							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
-							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
-\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
-							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
-							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
-\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   316 &    493*  & 688 & 439 & 0 \\
-							& unsat    &   294*   &   240* &   206 &    190*  & 339 & 158 & 0 \\
-							& $\times$ &   269*   &   148* &   543 &    382*  & 38 & 468 & 1065 \\\hline
-\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
-							& unsat    &   814*   &   818* &   807 &    772*  & 500 & 443 & 17 \\
-							& $\times$ &     5*   &     6* &    16 &     55*  & 88 & 76 & 797 \\ \hline
-\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
-							& unsat    &  1030*   &   936* &  1020 &    958*  & 596 & 349 & 22 \\
-							& $\times$ &     2*   &   101* &    19 &     71*  & 137 & 120 & 978 \\ \hline
-\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
-							& unsat    & 3391* & 2082* & 2824 & 2205* & 2079 & 1972 & 2079 \\
-							& $\times$ & 0* & 0* & 567 & 1186* & 84 & 383 & 13 \\ \hline \hline
-\multirow{3}{*}{Total} 		& sat      & * & * & 19724 & * &  &  &  \\
-							& unsat    & * & * & 10597 & * &  &  &  \\
-							& $\times$ & * & * &  4702 & * &  &  &  \\\hline
-\end{tabular}}
-\label{table:base_benchmark}
-\end{table}
-}
-
-\hide{ %3rd version of tables
-\begin{table}[t]
-	\centering
-	\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
-	\scalebox{0.7}{
-		\begin{tabular}{l r | r r r r}
-			\hline
-			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3Str3 \\ \hline
-			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
-			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
-			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline
-
-				\multirow{3}{*}{leetcode-addStrings}	& sat & 622*  &  330* &  100* &  85* \\ 
-				& unsat    &  1054*  & 780* & 1043* &  634* \\
-				& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
-				\multirow{3}{*}{leetcode-add\_Binary}	& sat & 520*  &  530* &  531* &  11* \\ 
-				& unsat    &  1351*  & 1091* & 1091* &  1094* \\
-				& $\times$ &  11*  &  261* &  260* & 777* \\ \hline
-				\multirow{3}{*}{leetcode-numDecodings}	& sat & 166*  &  107* &  151* &  50* \\ 
-				& unsat    &  273*  & 269* & 283* &  269* \\
-				& $\times$ &  92*  &  155* &  97* & 212* \\ \hline
-				\multirow{3}{*}{leetcode-restoreIpAddresses}	& sat & 811*  &  462* &  864* &  55* \\ 
-				& unsat    &  13648*  & 13540* & 13648* &  13342* \\
-				& $\times$ &  54*  &  511* &  1* & 1116* \\ \hline
-				\multirow{3}{*}{leetcode-validIPAddress}	& sat & 54*  &  57* &  58* &  8* \\ 
-				& unsat    &  19*  & 19* & 19* &  19* \\
-				& $\times$ &  4*  &  1* &  0* & 50* \\ \hline
-				\multirow{3}{*}{leetcode-validWordAbbreviation}	& sat & 183*  &  193* &  188* &  8* \\ 
-				& unsat    &  24*  & 11* & 21* &  16* \\
-				& $\times$ &  39*  &  42* &  37* & 222* \\ \hline
-				\multirow{3}{*}{lib-datetime\_parse\_hh\_mm\_ss\_ff}	& sat &  133*  & 133* &  133* &  88* \\ 
-				& unsat    &  41*  & 41* & 41* &  43* \\
-				& $\times$ &  0*  &  0* &  0* & 43* \\ \hline
-				\multirow{3}{*}{lib-datetime\_parse\_isoformat\_date}	& sat & 32*  &  32* &  32* &  23* \\ 
-				& unsat    &  0*  & 0* & 0* &  0* \\
-				& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
-				\multirow{3}{*}{lib-distutils\_get\_build\_version}	& sat & 19*  &  19* &  19* &  4* \\ 
-				& unsat    &  24*  & 24* & 24* &  24* \\
-				& $\times$ &  0*  &  0* &  0* & 15* \\ \hline
-				\multirow{3}{*}{lib-email\_parsedate\_tz}	& sat & 68*  &  72* &  72* &  30* \\ 
-				& unsat    &  138*  & 138* & 138* &  138* \\
-				& $\times$ &  4*  &  0* &  0* & 42* \\ \hline
-				\multirow{3}{*}{lib-http\_parse\_request}	& sat & 24*  &  24* &  24* &  8* \\ 
-				& unsat    &  9*  & 9* & 9* &  7* \\
-				& $\times$ &  0*  &  0* &  0* & 18* \\ \hline
-				\multirow{3}{*}{lib-ipaddress\_ip\_int\_from\_string}	& sat & 595*  &  204* &  480* &  18* \\ 
-				& unsat    &  427*  & 373* & 431* &  357* \\
-				& $\times$ &  1006*  &  1451* &  1117* & 1653* \\ \hline
-				\multirow{3}{*}{lib-nntplib\_parse\_datetime}	& sat & 4*  &  8* &  0* &  0* \\ 
-				& unsat    &  0*  & 0* & 0* &  0* \\
-				& $\times$ &  4*  &  0* &  8* & 8* \\ \hline
-				\multirow{3}{*}{lib-smtpd\_parseargs}	& sat & 27*  &  27* &  27* &  24* \\ 
-				& unsat    &  72*  & 72* & 72* &  66* \\
-				& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
-				\multirow{3}{*}{lib-wsgiref\_check\_status}	& sat & 10*  &  10* &  10* &  6* \\ 
-				& unsat    &  9*  & 9* & 9* &  9* \\
-				& $\times$ &  0*  &  0* &  0* & 4* \\ \hline
-				% \multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* \\
-				% 									& unsat    &   2912*  &  2211* &  2655* &   1944* \\
-				% 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
-			}
-		\end{tabular}
-		\label{table:str_int_benchmark}
-	\end{table}
-}
-
-\hide{  % 2nd version of tables
-\begin{table*}[t]
-\centering
-\caption{Results of {\tool}, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
-\begin{tabular}{l r | r r r r r r r}
-\hline
-\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
-\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
-							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
-							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
-							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
-\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
-							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
-							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
-							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
-\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
-							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
-							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
-							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
-\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
-							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
-							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
-							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
-\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
-							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
-							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
-							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
-\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
-							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
-							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
-							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
-\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
-							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
-							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
-							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
-\end{tabular}
-\label{table:base_benchmark}
-\end{table*}
-
-\begin{table*}[t]
-\centering
-\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
-\begin{tabular}{l r | r r r r r r r}
-\hline
-\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
-\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
-									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
-									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
-									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
-\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
-									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
-									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
-									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
-\end{tabular}
-\label{table:str_int_benchmark}
-\end{table*}
-}
-
-\hide{  % 1st version of tables
-\begin{table*}[t]
-\centering
-\caption{Results of {\tool}, cvc4, and z3 on string benchmarks}
-\begin{tabular}{l | r r r | r r r | r r r | r r r}
-\hline
-\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{Z3Str3} \\
-			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
-PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
-APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
-LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
-StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
-cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
-cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
-\end{tabular}
-\label{table:base_benchmark}
-\end{table*}
-
-\begin{table*}[t]
-\centering
-\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
-\begin{tabular}{l | r r r | r r r | r r r | r r r}
-\hline
-\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{Z3Str3} \\
-			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
-full\_str\_int		& 3294 & 17088 & 1191/0 & 2185 & 16377 & 3011/0 & 422 & 16034 & 4131/986 & 2731 & 16832 & 2010/0 \\ 
-filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
-\end{tabular}
-\label{table:str_int_benchmark}
-\end{table*}
-}
-
-\hide{
-% wider table for 30s timeout data
-\begin{table}[h]
-\centering
-\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
-\scalebox{0.8}{
-\begin{tabular}{|l r | r r r r|| r r r r|}
-\hline
-\multicolumn{2}{|c}{}          			   & {\tool} & CVC4  &    Z3  & Z3Str3 & {\tool} & CVC4  &    Z3  & Z3Str3 \\ \hline
-\multirow{3}{*}{Leetcode}		& SAT      &   2349  &  1543 &  1892  &   217 \\ 
-								& UNSAT    &  16368  & 15676 & 16105  & 15374 \\
-								& $\times$ &    210  &  1708 &   930  &  3336 \\ \hline 
-\multirow{3}{*}{PythonLib}		& SAT      &    886  &   408 &   797  &   201 \\ 
-								& UNSAT    &    720  &   660 &   724  &   644 \\
-								& $\times$ &   1040  &  1578 &  1125  &  1801 \\ \hline
-\multirow{3}{*}{JavaScript}		& SAT      &     20  &     6 &    16  &     4 \\ 
-								& UNSAT    &      0  &     0 &     0  &     0 \\
-								& $\times$ &      0  &    14 &     4  &    16 \\ \hline \hline
-\multirow{3}{*}{Total}			& SAT      &   3255  &  1957 &  2705  &   422 \\ 
-								& UNSAT    &  17088  & 16336 & 16829  & 16018 \\
-								& $\times$ &   1250  &  3300 &  2059  &  5153 \\ \hline
-\end{tabular}}
-\label{table:str_int_benchmark}
-\end{table}
-}

### 2020-04-05 final-final/main.tex
final version

--- 2020-04-05 final-version/main.tex
@@
 \setcopyright{acmcopyright}
-\acmPrice{}
+\acmPrice{15.00}
 \acmDOI{10.1145/3385412.3386034}
@@
 In particular solving string constraints with string-number conversion  is necessary for the analysis of scripting languages such as JavaScript and Python, where string-number conversion is a part of the definition of the core semantics of these languages.
-\changed{However, solving this type of constraint is very challenging for the state-of-the-art solvers.
-We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints.} Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
+However, solving this type of constraint is very challenging for the state-of-the-art solvers.
+We propose in this paper an approach that can efficiently support both string-number conversion and other common types of string constraints.
+Experimental results show that it significantly outperforms other state-of-the-art tools on benchmarks that involves string-number conversion.
 \end{abstract}

### 2020-04-16 final-final/main.tex
updates
colons ??

@@
 
-\renewcommand{\shortauthors}{P.A. Abdulla, M.F. Atig, Y-F. Chen, B.P. Diep, P. Janků, H-H. Lin, L. Holík and W-C. Wu}
+\renewcommand{\shortauthors}{P.A. Abdulla, M.F. Atig, Y-F. Chen, B.P. Diep, P. Janků, H-H. Lin, L. Holík, and W-C. Wu}
 
@@
 
-A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: the arrays are indexed by strings, and numeric indices are converted to strings.
-This conversion is mandated explicitly by the JavaScript semantics: the 2019 edition of ECMAScript \cite{ecmascript2019ecmascript} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
+A casual glance at the above code reveals no use of strings at all, but the semantics of field access is somewhat unusual in JavaScript: The arrays are indexed by strings, and numeric indices are converted to strings.
+This conversion is mandated explicitly by the JavaScript semantics: The 2019 edition of ECMAScript \cite{ecmascript2019ecmascript} requires that $ToPropertyKey$ be called on the element expression (\S{12.3.2.1}), and $ToPropertyKey$ calls {\tt{ToString}} on that value in all but special cases (\S{7.1.14}).
 Therefore, any faithful symbolic execution of JavaScript must handle such conversions for even basic array operations to work correctly.
@@
 %
-It proceeds in two steps:} the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+It proceeds in two steps:} The first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 Observe that we could  over-approximate the input constraint into any decidable fragment, e.g.
@@
 
-Our decision procedure has two steps: the first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
+Our decision procedure has two steps: The first step consists in over-approximating the set of input constraints into a set that falls in the chain-free fragment~\cite{abdulla2019chain}, which is decidable.
 The over-approximation module proceeds as follows: First,  it replaces all string-number conversion constraint $n=\sti{x}$ by $n=-1 \vee (n\neq -1 \wedge x\in [0-9]^*$) to obtain an over-approximation $\Phi$ consisting of only basic string constraints.
@@
 that $i\neq j \implies x_i \neq x_j$.
-We may make this assumption without loss of generality, since multiple occurrences of variables in $\phi_e$ can be eliminated: whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoin the modified $\phi_e$ with a new equality $x_j = x_j'$.
+We may make this assumption without loss of generality, since multiple occurrences of variables in $\phi_e$ can be eliminated: Whenever $x_i = x_j$ for $i \neq j$, we may replace $x_j$ by a fresh variable $x_j'$ and conjoin the modified $\phi_e$ with a new equality $x_j = x_j'$.
 %
@@
 
-\section{Related works} 
+\section{Related Works} 
 \label{section:related}
